### 2017-06-28 literaturereview.Rmd
Literature Review

---
title: "“Question Quality in Community Q&A” Notes"
author: "Lisa Oshita"
date: "June 28, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Question Content
* length: word count and sentence count
* text: ngram features from title and body

###Global/local topic models
* global:
  + topic information considered as another predictor of question quality
  + reflects what the entire question is about
* local:
  + captures internal structural aspects of questions 
  + Sentence topic model: capture latent aspects at internal level

###Results
* some correlation between view count and question quality 
* content (length and text) gave signficant improvement in classification accuracy (over ViewCount)- indicates that words used capture quality 
* good questions tended to be shorter 
* prediction accuracy increased with global topics- latent topics can be predictive of quality
* content + local topic models = better performance over content + global - internal structures of a question indicate quality

###Discussion
* good questions: 
* aren't repeats (user has done research)
* receive more answers on average (5 compared to 2.5), also receive longer answers and more comments
* "live longer"
* "latent topical aspects shared between related questions are good predictors of question quality"

##Ideas for research
* consider question and title length (predict that concise questions will get answered quicker than lengthy ones)
* extract topic information from title and body of the question?

### 2017-06-29 new_variables.Rmd
creating response variable

---
title: "New Variables"
author: "Lisa Oshita"
date: "June 29, 2017"
output: html_document
---

##Creating time to event variable
```{r}
out$time_until_answer <- out$first_answer_date - out$post_date
```

### 2017-06-30 new_variables.Rmd
practicing with stringr functions

@@
 date: "June 29, 2017"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
 
-##Creating time to event variable
+### Creating time to event variable
+observation 15 has a negative value?
 ```{r}
+
 out$time_until_answer <- out$first_answer_date - out$post_date
+
+empty <- which(is.na(out$time_until_answer))
+for (i in empty) {
+  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
+}
+
 ```
+
+### Practicing with stringr 
+```{r}
+library(stringr)
+library(rebus)
+
+#variable indicating if title contains questionmark 
+out$contain_questionmark <- str_detect(out$title, pattern = QUESTION)
+```
+
+### Practicing with product categorization 
+```{r}
+# having problems with regex function, not giving same output that Data camp showed 
+x <- c("Cat", "CAT", "cAt")
+str_view(x, regex("cat", ignore_case = TRUE), match = TRUE)
+
+# not working
+phones <- regex("phone", ignore_case = TRUE)
+out$product_type[str_detect(out$device, pattern = phones)] <- "Phone"
+```

### 2017-07-04 new_variables.Rmd
practicing with dplyr

@@
 ---
-title: "New Variables"
+title: "Practicing with the data"
 author: "Lisa Oshita"
@@
 ```{r}
-
 out$time_until_answer <- out$first_answer_date - out$post_date
@@
 ```
+
+### Practicing with dplyr
+```{r}
+library(dplyr)
+
+#using only observations in English
+out1 <- out %>% 
+          tbl_df() %>% 
+          filter(langid == "en")
+
+#view average time until answered grouped by each category 
+out1 %>%
+  group_by(category) %>%
+  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
+  arrange(avg_time)
+
+#view average time until answered grouped by whether or not question contains "?"
+#seems like for a lot of categories, questions with question marks get answered faster
+out1$contain_questionmark <- str_detect(out1$title, pattern = QUESTION)
+out1 %>%
+  group_by(category, contain_questionmark) %>%
+  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
+  arrange(category, avg_time)
+
+#looking at average time until answered for intervals of title length
+library(stringr)
+title_length <- str_length(out1$title)
+out1$title_length_intervals <- cut(length, breaks = 8)
+#don't really see anything interesting here 
+out1 %>%
+  group_by(title_length_intervals) %>%
+  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n())
+
+```

### 2017-07-06 practice.Rmd
practice with ggplot2

---
title: "Practicing with the data"
author: "Lisa Oshita"
date: "June 29, 2017"
output:
  pdf_document: default
  html_document: default
---

### Creating time to event variable
observation 15 has a negative value?
answered will be the censoring indicator variable
```{r}
out$time_until_answer <- out$first_answer_date - out$post_date

empty <- which(is.na(out$time_until_answer))
for (i in empty) {
  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
}

```

### Practicing with stringr 
```{r}
library(stringr)
library(rebus)

#variable indicating if title contains questionmark 
out$contain_questionmark <- str_detect(out$title, pattern = QUESTION)
```

### Practicing with product categorization 
```{r}
# having problems with regex function, not giving same output that Data camp showed 
x <- c("Cat", "CAT", "cAt")
str_view(x, regex("cat", ignore_case = TRUE), match = TRUE)

# not working
phones <- regex("phone", ignore_case = TRUE)
out$product_type[str_detect(out$device, pattern = phones)] <- "Phone"
```

### Practicing with dplyr
```{r}
library(dplyr)

#using only observations in English
out_english <- out %>% 
                tbl_df() %>% 
                filter(langid == "en")

#view average time until answered grouped by each category 
out_english%>%
  group_by(category) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(avg_time)

#view average time until answered grouped by whether or not question contains "?"
#seems like for a lot of categories, questions with question marks get answered faster
out_english$contain_questionmark <- str_detect(out_english$title, pattern = QUESTION)
out_english %>%
  group_by(category, contain_questionmark) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(category, avg_time)

#looking at average time until answered for intervals of title length
library(stringr)
title_length <- str_length(out_english$title)
out_english$title_length_intervals <- cut(title_length, breaks = 8)
#don't really see anything interesting here 
out_english %>%
  group_by(title_length_intervals) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n())

```

### practicing with ggplot
```{r}
library(ggplot2)
library(stringr)

#using only observations with a positive time_until_answer value (26 observations have negative time until answer values)
out1_positive <- out_english %>% filter(time_until_answer > 0)

#histogram of time_until_answer
ggplot(out1_positive, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10)

#plot of number of tags and time_until_answer
ggplot(out1_positive, aes(x = factor(n_tags), y = time_until_answer)) + 
  geom_point(position = "jitter")

#plot with title length 
out1_positive$title_length <- str_length(out1_positive$title)

ggplot(out1_positive, aes(x = title_length, y = time_until_answer)) + 
  geom_point()

#looking at only data for phones category 
phones_only <- out1_positive %>% filter(category == "Phone")
ggplot(phones_only, aes(x = title_length, y = time_until_answer)) + 
  geom_point(size = 3, alpha = 0.5)
```

### 2017-07-06 practice.Rmd
added code to upload dataset

@@
 ---
+```{r}
+dir <- file.path(getwd(),"data")
+out <- read.csv(file.path(dir, "answers_data.csv"))
+```
 
 ### Creating time to event variable
-observation 15 has a negative value?
-answered will be the censoring indicator variable
+censoring indicator variable: answered
 ```{r}
 out$time_until_answer <- out$first_answer_date - out$post_date
-
+#filling in the NAs
 empty <- which(is.na(out$time_until_answer))
@@
 
+#26 observations in out dataframe have negative time to event variable
+length(which(out$time_until_answer < 0))
 ```
@@
 out$contain_questionmark <- str_detect(out$title, pattern = QUESTION)
-```
 
-### Practicing with product categorization 
-```{r}
-# having problems with regex function, not giving same output that Data camp showed 
-x <- c("Cat", "CAT", "cAt")
-str_view(x, regex("cat", ignore_case = TRUE), match = TRUE)
-
-# not working
+#practicing with product categorization
 phones <- regex("phone", ignore_case = TRUE)
@@
 ```{r}
+library(stringr)
 library(dplyr)
@@
 
-#view average time until answered grouped by whether or not question contains "?"
+#view average time until answered grouped by whether or not question contains "?", for each category
 #seems like for a lot of categories, questions with question marks get answered faster
@@
 #looking at average time until answered for intervals of title length
-library(stringr)
+#creating title length intervals
 title_length <- str_length(out_english$title)

### 2017-07-06 dplyr_cheatsheet.Rmd
data camp course cheatsheets

---
title: "dplyr"
author: "Lisa Oshita"
date: "July 1, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## dplyr package
### tbl 
* tbl formats how R displays your data, makes it easier to view and work with
* doesn't change underlying structure
* glimpse function also good for displaying data
```{r}
library(dplyr)
library(hflights)

hflights <- tbl_df(hflights)
hflights
```
### data cleaning
recoding variables using look up tables
```{r}
#using a look up table to recode the uniquecarrier variable
lut <- c("AA" = "American", "AS" = "Alaska", "B6" = "JetBlue", "CO" = "Continental", 
         "DL" = "Delta", "OO" = "SkyWest", "UA" = "United", "US" = "US_Airways", 
         "WN" = "Southwest", "EV" = "Atlantic_Southeast", "F9" = "Frontier", 
         "FL" = "AirTran", "MQ" = "American_Eagle", "XE" = "ExpressJet", "YV" = "Mesa")
#subsetting lookup table with a character string
hflights$Carrier <- lut[hflights$UniqueCarrier]
glimpse(hflights)
```

### 5 data manipulation tools in dplyr
* select(), which returns a subset of the columns
* filter(), that is able to return a subset of the rows
* arrange(), that reorders the rows according to single or multiple variables
* mutate(), used to add columns from existing data
* summarise(), which reduces each group to a single row by calculating aggregate measures

### select function
* examples: select(dataframe, var1, var2), select(df, 1:4, -2) (exclude variable 2)
* starts_with("X"): every name that starts with "X",
* ends_with("X"): every name that ends with "X",
* contains("X"): every name that contains "X",
* matches("X"): every name that matches "X", where "X" can be a regular expression,
* num_range("x", 1:5): the variables named x01, x02, x03, x04 and x05,
* one_of(x): every name that appears in x, which should be a character vector.
```{r}
#prints only ArrDelay and DepDelay
select(hflights, ends_with("Delay")) 
```

### mutate function
* creates new columns which are added to the dataframe/tbl
* mutate(df, z = x + y) z is the new column that will be added
* can add more than one column, just separate by a comma
```{r}
g1 <- mutate(hflights, ActualGroundTime = ActualElapsedTime - AirTime)
g1
```

### filter function
* filters out rows
* can use logical operators inside filter: <, >, ==, !=, >=, x %in% c(a,b,c) (TRUE if x is in the vector c(a,b,c))
* can use boolean operators: & (and), | (or), and ! (not)
* instead of using the & operator, you can also pass several logical tests to filter(), separated by commas (these are equivalent = filter(df, a > 0 & b > 0), filter(df, a > 0, b > 0))
* filter(df, !is.na(x)): keeps observations in df that are not NA
```{r}
#all flights flown by these specific airlines
filter(hflights, UniqueCarrier %in% c("JetBlue", "Southwest", "Delta"))

#all flights where taxiing took longer than flying
filter(hflights, TaxiIn + TaxiOut > AirTime)
```

### arrange function
* can be used to rearrange rows according to any type of data
* if character variable is passed to arrange, it will arrange rows in alphabetical order
* if factor variable passed, it will arrange rows according to the levels of the factor
* by default arranges the rows from smallest to largest, reverse this by using the desc() function
```{r}
#arrange according to carrier and decreasing departure delays
arrange(hflights, UniqueCarrier, desc(DepDelay))
#arrange according to total delay 
arrange(hflights, DepDelay + ArrDelay)
```

### summarise function
* same syntax as mutate, but outputs only a single row
* does not output an altered copy of the dataset, returns a new dataset that contains only the summarizing statistics 
```{r}
#prints a summary with new variables min_dist and max_dist
summarise(hflights, min_dist = min(Distance), max_dist = max(Distance))
#print out a summary with variable max_div for all diverted flights
summarise(filter(hflights, Diverted == 1), max_div = max(Distance))
```

### aggregate functions in base r 
* can use any function, as long as the function takes a vector and returns a single value
* min, max, mean, median, quantile, sd, var, IQR

### aggregate function in dplyr package
* first(x): first element in vector x
* last(x): last element
* nth(x, n): the nth element in vector x
* n():  number of rows in the dataframe or group of observations that summarise() describes (takes no argument)
* n_distinct(x): number of unique values in vector x
```{r}
#displays total number of observations, total number of carriers, total number of unique destinations
summarise(hflights,
          n_obs = n(),
          n_carrier = n_distinct(UniqueCarrier),
          n_dest = n_distinct(Dest))
```

### pipe operator
comes from the magrittr package, but don't have to install it 
```{r}
#takes the hflight dataset and then adds diff that is the result of subtracting TaxiIn from TaxiOut, and then picks all of rows whose diff value does not equal NA, and then summarise the data set with a value named avg that is the mean diff value
hflights %>%
  mutate(diff = TaxiOut - TaxiIn) %>%
  filter(!is.na(diff)) %>%
  summarise(avg = mean(diff))
```
examining if sometimes it's more efficient to drive than fly 
```{r}
#these results suggest that it might sometimes be better to drive than fly 
hflights %>% 
  mutate(RealTime = ActualElapsedTime + 100, mph = Distance / RealTime * 60) %>%
    filter(!is.na(mph) & mph < 70) %>%
      summarise(n_less = n(), n_dest = n_distinct(Dest), min_dist = min(Distance), 
                max_dist = max(Distance))
#looks at flights with an mph of less than 105, or flights that were cancelled or diverted
#indicates that almost 19% of flights appear to be less efficient than driving 
hflights %>%
  mutate(RealTime = ActualElapsedTime + 100, mph = Distance / RealTime * 60) %>%
    filter(mph < 105 | Cancelled == 1 | Diverted == 1) %>%
      summarise(n_non = n(), n_dest = n_distinct(Dest), min_dist = min(Distance),
                max_dist = max(Distance))
```

### group_by function
* when used with summarise function, summary statistics are calculated for each group
```{r}
#indicates that SkyWest had longest average Arrival Delay
hflights %>%
  mutate(RealTime = ActualElapsedTime + 100, mph = Distance / RealTime * 60) %>%
    filter(mph < 105 | Cancelled == 1 | Diverted == 1) %>%
      summarise(n_non = n(), n_dest = n_distinct(Dest), min_dist = min(Distance),
                max_dist = max(Distance))

```
* combining group_by with mutate
* useful when mutate uses rank function (takes a group of values and calculates rank of each)
```{r}
#filtered to keep only observations with nonmissing, positive ArrDelay, grouped by Carrier, average ArrDelay calculated for each Carrier group, new variable rank is added to the data, data that is output is arranged by rank 
hflights %>% 
  filter(!is.na(ArrDelay) & ArrDelay > 0) %>%
    group_by(UniqueCarrier) %>%
      summarise(avg = mean(ArrDelay)) %>%
        mutate(rank = rank(avg)) %>%
          arrange(rank)
```

### advanced group_by exercises
```{r}
#indicates how many airplanes flew to only one destination
hflights %>%
  group_by(TailNum) %>%
  summarise(ndest = n_distinct(Dest)) %>%
  filter(ndest == 1) %>%
  summarise(nplanes = n())

#finds the most visited destination for each carrier
hflights %>% 
  group_by(UniqueCarrier, Dest) %>%
  summarise(n = n()) %>%
  mutate(rank = rank(desc(n))) %>%
  filter(rank == 1)
```

### dplyr and different types
```{r}
#can work with data tables
library(data.table)
hflights2 <- as.data.table(hflights)
hflights2
```

### dplyr and SQL databases
* nycflights is a reference to data that lives outside of R, but can use the dplyr commands
* dplyr will convert the commands to the database's native language (in this case, SQL), and return the results
* allows you to pull data that is too large to fit in R (only the fraction of data that you need will actually be downloaded into R, which will usually fit into R without memory issues)
```{r}
library(dbplyr)
library(RMySQL)
library(DBI)
#sets up connection to mySQL database
my_db <- src_mysql(dbname = "dplyr", 
                   host = "courses.csrrinzqubik.us-east-1.rds.amazonaws.com", 
                   port = 3306, 
                   user = "student",
                   password = "datacamp")

#nycflights is a reference to a tbl in the remote database, but no difference in syntax
nycflights <- tbl(my_db, "dplyr")
glimpse(nycflights)

#ordered and grouped summary of nycflights
nycflights %>% 
  group_by(carrier) %>% 
  summarise(n_flights = n(), avg_delay = mean(arr_delay)) %>%
  arrange(avg_delay)
```

### 2017-07-06 stringr_cheatsheet.Rmd
data camp course cheatsheets

---
title: "stringr cheatsheet"
author: "Lisa Oshita"
date: "June 29, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basics
* writeLines(): default separates strings with a new line, use sep argument to change
* \\ : escape sequence
```{r}
format(1000000000, big.mark = ",", big.interval = 3, scientific = FALSE)
```
* formatC(): f for fixed, e for scientific, g for fixed unless scientific saves space
```{r}
x1 <- c(0.0011, 0.011, 1)
formatC(x1, format = "f", digits = 1)
```
* paste(): to put together strings

## stringr 
### str_c
like paste, but default separator is an empty string not a space
```{r}
library(stringr)
str_c(c("a","b","c"), "hi")
paste(c("a","b","c"), "hi")
```
### str_length
(also works on factors)
```{r}
str_length(c("hello", "hey", "what's up"))
```
### str_sub
extracts part of strings based on their location 
```{r}
str_sub(c("Bruce", "Wayne"), 1, 4)
str_sub(c("Bruce", "Wayne"), -4, -1)
```
### str_detect
Does the string contain the pattern? 
```{r}
pizzas <- c("cheese", "pepperoni", "sausage and green peppers")
str_detect(pizzas, pattern = fixed("pepper"))
```
### str_subset
detects strings with a pattern and then subsets it
```{r}
str_subset(pizzas, pattern = fixed("pepper"))
```
### str_count
counts number of times pattern occurs in each string
```{r}
str_count(pizzas, pattern = fixed("e"))
```
### str_split
* pull apart strings into more useful variables
* use simplify = TRUE to get a matrix with n columns as output (and not a list)
```{r}
date_ranges <- c("23.01.2017 - 29.01.2017", "30.01.2017 - 06.02.2017")
#as a list
str_split(date_ranges, pattern = fixed(" - "))
#as a matrix
split_dates_n <- str_split(date_ranges, pattern = fixed(" - "), simplify = TRUE, n = 2)
split_dates_n
```
### str_replace/str_replace_all
```{r}
phone_numbers <- c("510-555-0123", "541-555-0167")
#replace - with space
str_replace(phone_numbers, "-", " ")
str_replace_all(phone_numbers, "-", " ")
```
## Regular Expressions
### str_view
* %R% in rebus package gives you a way to combine regular expressions
* str_view is good for testing patterns, opens up an html window
* str_view_all to see all matching patterns
```{r}
library(rebus)
x2 <- c("cat", "coat", "scotland", "tic toc")
str_view(x2, pattern = START %R% "c")
```
### ANY_CHAR
```{r}
str_view(x2, pattern = "c" %R% ANY_CHAR %R% "t")
#match string with exactly 3 characters
str_view(x2, pattern = START %R% ANY_CHAR %R% ANY_CHAR %R% ANY_CHAR %R% END)
```
### str_extract
returns just the part of the string that matched the pattern
```{r}
pattern <- "c" %R% ANY_CHAR %R% "t"
str_extract(x2, pattern)
```
### or function in rebus
allows us to specify a set of alternatives 
```{r}
x3 <- c("grey sky", "gray elephant", "white elephant")
str_view(x3, pattern = or("grey", "gray"), match = TRUE)
#match = TRUE will only display elements that had a match
str_view(x3, pattern = "gr" %R% or("e", "a") %R% "y", match = TRUE)
```
### char_class
* way of specifying "match one (and only one) of the following characters"
* negated_char_class: any single character that isn't one of the following
```{r}
vowels <- char_class("AaEeIiOoUu")
str_view(x3, pattern = vowels)
str_view_all(x3, pattern = vowels)
```
### repetition
* one_or_more
* zero_or_more
* optional
```{r}
#negated char class that matches anything but a vowel
not_vowels <- negated_char_class("aeiouAEIOU")
#see items with only vowels
str_view(c("aaa", "aba", "dada", "ccc"), pattern = exactly(one_or_more(vowels)), match = TRUE)
#see items with no vowels 
str_view(c("aaa", "aba", "dada", "ccc"), pattern = exactly(one_or_more(not_vowels)), match = TRUE)
```
### example
```{r}
#pattern that matches 3 digits
three_digits <- DGT %R% DGT %R% DGT
four_digits <- three_digits %R% DGT
#separator pattern (character class that contains - . ( ) " ")
separator <- char_class("-.() ")
# Create phone pattern
phone_pattern <- optional(OPEN_PAREN) %R% 
  three_digits %R% 
  zero_or_more(separator) %R% 
  three_digits %R% 
  zero_or_more(separator) %R%
  four_digits
contact <- c("Call me at 555-555-0191", "123 Main St", "Phone: 555.555.0191 Mobile: 555.555.0192")
#test the pattern
str_view(contact, pattern = phone_pattern)
#extract phone numbers
str_extract(contact, phone_pattern)
#extract ALL phone numbers
str_extract_all(contact, phone_pattern)
```
### example 2
```{r}
#pattern to match 1 or 2 digits
age <- DGT %R% optional(DGT)
#pattern to match units
unit <- optional(SPC) %R% or("YO", "YR", "MO")
#can combine patterns
pattern = age %R% unit
```
## Advanced matching
### capture
used to capture part of a regular expression 
```{r}
email <- capture(one_or_more(WRD)) %R% "@" %R% one_or_more(WRD) %R% DOT %R% one_or_more(WRD) 
str_view("(wolverine@xmen.com)", pattern = email)
#using str_match allows you to access the captured piece
str_match("(wolverine@xmen.com)", pattern =  email)
```
### backreferences
* allow you to find repeated patterns or words
* requires: capture() and reference to it (REF1)
```{r}
str_view(c("hello", "sweet", "kitten"), pattern = capture(LOWER) %R% REF1)
#pattern to see repeated letters (ex: abab)
pair_of_repeated <- capture(lower(2)) %R% REF1
```
### replacing with backreferences
capture happens in pattern argument, backreference used in replacement argument
```{r}
x <- c("hello", "sweet", "kitten")
str_replace(x, capture(ANY_CHAR), str_c(REF1, REF1))

#pattern to match words ending in "ING"
pattern <- one_or_more(WRD) %R% "ING"
narratives <- "31 YOF FELL FROM TOILET HITITNG HEAD SUSTAINING A CHI "
# Test replacement
str_replace(narratives, capture(pattern), str_c("CARELESSLY", REF1, sep = " "))
```
### Unicode and patterns
* if code has more than 4 digits, use uppercase U - "\U..."
* as.hexmode(utf8ToInt("a")) to hexidecimal code for "a"
* stri_trans_ncf: composes characters with combining accents into a single character
* stri_trans_nfd: decomposes character with accents into separate letter and accent characters 
* match accents using rebus value - UP_DIACRITIC
```{r}
library(stringi)
library(stringr)
as.hexmode(utf8ToInt(stri_trans_nfd("\u00e8")))
as.hexmode(utf8ToInt(stri_trans_nfc("\u0065\u0300")))
```
### matching a single grapheme
* ANY_CHAR will only match character represented by single code point
* grapheme - represents a display character, but may be composed of many code points 
* use GRAPHEME to matche any grapheme
```{r}
x <- c("Adele", "Ad\u00e8le", "Ad\u0065\u0300le")
writeLines(x)
str_view(x, "Ad" %R% ANY_CHAR %R% "le")
str_view(x, "Ad" %R% GRAPHEME %R% "le")
```
### stri_isempty
* stringi function
* finds empty strings, returns logical

### or1()
* function in rebus package
* specifies alternatives, can pass in a vector of alternatives (rather than each alternative being an argument)

### changing case to ease matching
* whole_word will only match if pattern occurs as a word on it's own
* will match "The cat" but not "caterpillar"
* str_to_upper to change all to uppercase, str_to_lower to change all to lowercase 
```{r}
x <- c("Cat", "CAT", "cAt") 
str_view(x, "cat")
str_view(str_to_lower(x), "cat")
```
### ignoring case when matching
regex function in stringr allows you to specify that matching should be case insensitive
```{r}
library(stringr)
library(stringi)
x <- c("Cat", "CAT", "cAt") 
str_view(x, pattern = regex("cat", ignore_case = TRUE), match = TRUE)
```

```{r}
str_view(c("a", "A"), pattern = regex("a", ignore_case = TRUE), match = TRUE)
```

### fixing case problems
* str_to_title transforms to title case 
* stringi function stri_trans_totitle allows specification of type (default = "word"), can also change to "sentence"

### 2017-07-06 textmining_cheatsheet.Rmd
data camp course cheatsheets

---
title: "text mining"
author: "Lisa Oshita"
date: "July 5, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Basics
* text mining: process of deriving actionable insights from text
* bag of words text mining represents a way to count terms, or n-grams, across a collection of documents
* corpus: collection of documents
* 2 kinds of corpus data types: permanent corpus (PCorpus) and volatile corpus (VCorpus)
```{r}
library(qdap)
text <- "DataCamp is the first online learning platform that focuses on building the best learning experience specifically for Data Science. We have offices in Boston and Belgium and to date, we trained over 250,000 (aspiring) data scientists in over 150 countries. These data science enthusiasts completed more than 9 million exercises. You can take free beginner courses, or subscribe for $25/month to get access to all premium courses."
#finds 10 most frequent terms

#finds the 10 most frequent terms (doesn't mattern what kind of word, all words treated equally)
term_count <- freq_terms(new_text, 10)
plot(term_count)
```

### tm package and creating volatile corpus
* to make a volatile corpus, need to have R interpret each element in vector of text as a document, us tm package and its source functions to do this: VectorSource(), which outputs a source object
* example: coffee_source <- VectorSource(coffee_tweets) (to convert vector to a source object)
* then pass source to VCorpus(), which is a list of lists: at each element of the corpus, there is a plain text document, which is essentially a list that contains the actual text data (since it's a list of lists, need to subset twice to get to the actual text data)
* use DataframeSource() when making corpus from dataframe: treats entire row as a complete document (careful not to pick up non-text data)
```{r}
num  <- c(1,2,3)
Author1 <- c("Text mining is a great time.", "Text analysis provides insights", "qdap and tm are used in text mining")
Author2 <- c("R is a great language", "R has many uses", "DataCamp is cool!")
example_text <- cbind(num, Author1, Author2)

#create source based off of columns 2 and 3 (don't want 1)
df_source <- DataframeSource(example_text[, 2:3])
#convert to corpus
df_corpus <- VCorpus(df_source)
df_corpus

#create another source based off of only column 3 (a vector)
vec_source <- VectorSource(example_text[,3])
#convert to a corpus
vec_corpus <- VCorpus(vec_source)
vec_corpus
```

### common cleaning functions
* cleaning helps aggregate terms
* tolower(): Make all characters lowercase (from base r, others are from tm) 
* removePunctuation(): Remove all punctuation marks
* removeNumbers(): Remove numbers
* stripWhitespace(): Remove excess whitespace
* from qdap package: 
* bracketX(): Remove all text within brackets (e.g. "It's (so) cool" becomes "It's cool")
* replace_number(): Replace numbers with their word equivalents (e.g. "2" becomes "two")
* replace_abbreviation(): Replace abbreviations with their full text equivalents (e.g. "Sr" becomes "Senior")
* replace_contraction(): Convert contractions back to their base words (e.g. "shouldn't" becomes "should not")
* replace_symbol() Replace common symbols with their word equivalents (e.g. "$" becomes "dollar")

### stop words
* words that are frequent but provide little/no information
* tm package contains a list of 174 stop words
```{r}
library(tm)
text <- "<b>She</b> woke up at       6 A.M. It\'s so early!  She was only 10% awake and began drinking coffee in front of her computer."

#list of standard English stop words
stopwords("en")

#print text without standard english stopwords
removeWords(text, stopwords("en"))
#add coffee and bean to the stopwords list
new_stops <- c("coffee", "bean", stopwords("en"))
removeWords(text, new_stops)
```

### word stemming and stem completion
* stemDocument function gets to a words root, takes in either a character vector (outputs character vector) or PlainTextDocument (outputs PlainTextDocument)
```{r}
complicate <- c("complicated", "complication", "complicatedly")
#word stemming saved in stem_doc
library(SnowballC)
stem_doc <- stemDocument(complicate)
stem_doc
#completion dictionary
comp_dict <- "complicate"
#stem completion
complete_text <- stemCompletion(stem_doc, comp_dict)
complete_text
```

```{r}
#trying to apply stemDocument would treat text_data as one character, need to remove punctuation and split it up
text_data <- "In a complicated haste, Tom rushed to fix a new complication, too complicatedly."
# Remove punctuation: rm_punc
rm_punc <- removePunctuation(text_data)
# Create character vector: n_char_vec
n_char_vec <- unlist(strsplit(rm_punc, split = ' '))
# Perform word stemming: stem_doc
stem_doc <- stemDocument(n_char_vec)
stem_doc
# Re-complete stemmed document: complete_doc
complete_doc <- stemCompletion(stem_doc, comp_dict)
complete_doc
```

### preprocessing a corpus
* tm_map() applies preprocessing steps to a corpus
```{r}
#use custom functions to save time
clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "coffee", "mug"))
  return(corpus)
}
```

### tdm vs dtm
* document term matrix: use when you want each document represented as a row (useful if want to compare authors within rows, or want to preserve time series)
* make DTM: use DocumentTermMatrix(corpus), and then save as a matrix with as.matrix()
* term document matrix: transpose of DTM
* make TDM: use TermDocumentMatrix(corpus), save as matrix with as.matrix()

### frequent terms with tm
* can use rowSums(tdm) to find frequency of terms, arrange in decreasing order to find the words that appear the most, create barplot of top frequency words

### frequent terms with qdap
* fast way to get frequent terms (and give up some control over preprocessing steps), use freq_terms() function from qdap 
* accepts a text variable, top = top number of terms to show, stopwords = vector of stopwords to remove, at.least = minimum character length of a word to be included

### word clouds
* size is related to individual word frequency
* ex: wordcloud(words, frequencies, max.words = 500, colors = "blue")
```{r}
library(wordcloud)
library(RColorBrewer)
#stopwords and word clouds
#added chardonnay, wine, and glass to stopwords list
#apply function to corpus, convert to tdm, convert to matrix, 
clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, 
                   c(stopwords("en"), "amp", "chardonnay", "wine", "glass"))
  return(corpus)
}
```

### adding colors to wordclouds
* wordcloud(chardonnay_freqs$term, chardonnay_freqs$num, max.words = 100, color = c("grey80", "darkgoldenrod1", "tomato")) - will put most frequent terms in colors 
* using brewer.pal function in RColorBrewer allows you to select colors from a palette
```{r}
#specify number of colors to draw
green_pal <- brewer.pal(8, "Greens")
#most of the times the first couple colors are too faint to see 
green_pal <- green_pal[-(1:2)]
#then add green_pal to wordcloud function
```

### 2017-07-06 writingfunctions_cheatsheet.Rmd
data camp course cheatsheets

---
title: "Writing Functions in R"
author: "Lisa Oshita"
date: "June 30, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Basics
* typeof() is basically same as class()
* initializing output vector for for loops: output <- vector("double", length)
* must use output[[i]] in the body (use double brackets)
* use seq_along in the indexing statement, safer

## Functional programming
### purr package
* all map functions take a vector as the first argument, and return function applied to each element of vector
* type of object returned is determined by the function suffix
* map() returns a list or data frame
* map_lgl() returns a logical vector
* map_int() returns a integer vector
* map_dbl() returns a double vector
* map_chr() returns a character vector
```{r}
library(nycflights13)
library(purrr)
#finds mean of each column 
map_dbl(planes, mean, na.rm = TRUE)
#finds columns in planes that are numeric
map_lgl(planes, is.numeric)
#finds the type of each column
map_chr(planes, typeof)
```

### passing anonymous functions
```{r}
#regression for each value of cyl in the mtcars data set 
#splits data set according to cyl values
cyl <- split(mtcars, mtcars$cyl)
#applies regression to each group by using and anonymous function
map(cyl, function(df) lm(mpg ~ wt, data = df))

#using formulas and shortcuts
map_dbl(cyl, function(df) mean(df$disp))
#shortcut
map_dbl(cyl, ~ mean(.$disp))
```

### shortcuts for subsetting elements
strings as shortcuts
```{r}
#regression results from example above
models <- map(cyl, ~ lm(mpg ~ wt, data = .))
#get the coefficients for each model
coefs <- map(models, coef)
#Use string shortcut to extract the wt coefficient 
map(coefs, "wt")
```
numeric vectors as shortcuts
```{r}
#pull out second element in coefs
map_dbl(coefs, 2)
```

### pipes
* pipe operator: %>% included in purrr package
* simplifies code
* x %>% f(y) is another way of writing f(x, y)
* left-hand side of the piping becomes the first argument in the function
```{r}
#without piping
cyl <- split(mtcars, mtcars$cyl) 
map(cyl, ~ lm(mpg ~ wt, data = .))
#with piping, read as: split the data frame mtcars on cyl, then use map() on the result
split(mtcars, mtcars$cyl) %>% 
  map(~ lm(mpg ~ wt, data = .))
#with more piping
mtcars %>% 
  split(mtcars$cyl) %>%
  map(~ lm(mpg ~ wt, data = .)) %>%
  map(coef) %>% 
  map_dbl("wt")
```

## Advanced inputs and outputs
### safely, possibly, quietly
* safely takes a function as an argument and returns a function as its output
* function that is returned is modified so that it never throws an error, and never stops your computation 
*always returns a list with 2 elements: result and error
```{r}
safe_readLines <- safely(readLines)
safe_readLines("http://example.org")
```

### using map safely
```{r}
urls <- list( example = "http://example.org", rproj = "http://www.r-project.org", asdf = "http://asdfasdasdkfjlda")
safe_readLines <- safely(readLines)

# Use the safe_readLines with map()
html <- map(urls, safe_readLines)
str(html)

# Extract the result from one of the successful elements
html[["example"]][["result"]]

# Extract the error from the element that was unsuccessful
html[["asdf"]][["error"]]
```

### transpose
reshapes a list so the inner-most level becomes the outer-most level
```{r}
str(transpose(html))
#extracts results and errors
res <- transpose(html)[["result"]]
errs <- transpose(html)[["error"]]

#create a logical vector that is true when errs is null 
is_ok <- map_lgl(errs, is_null)
#use to extract successful results
res[is_ok]
#extract input from unsuccessful results
urls[!is_ok]
```

### mapping over 2 arguments
The first two arguments to map2() are the objects to iterate over and the third argument is the function to apply
```{r}
# want to vary sample size and mean for rnorm
# Initialize n
n <- list(5, 10, 20)
mu <- list(1, 5, 10)
map2(n, mu, rnorm)
```

### mapping over more than 2 arguments
* pmap() takes a list of arguments as its input
* default: matches the elements of the list to the arguments in the function by position
* provide names in list to avoid positional matching
```{r}
n <- list(5, 10, 20)
mu <- list(1, 5, 10)
sd <- list(0.1, 1, 0.1)
pmap(list(n, mu, sd), rnorm)
```

### mapping over functions and their arguments
* invoke_map: first argument is a list of functions, second argument specifies the arguments to the functions
* in simplest case, all functions take same argument and can use (...) to pass to each function
```{r}
f <- list("rnorm", "runif", "rexp")

rnorm_params <- list(mean = 10)
runif_params <- list(min = 0, max = 5)
rexp_params <- list(rate = 5)
params <- list(rnorm_params, runif_params, rexp_params)

invoke_map(f, params, n = 5)
```

### walk
* operates just like map but is designed for functions that don't return anything
* use for functions with side effects like printing, plotting, saving
```{r}
#list of functions
f <- list(Normal = "rnorm", Uniform = "runif", Exp = "rexp")
#Define params
params <- list(Normal = list(mean = 10), Uniform = list(min = 0, max = 5), Exp = list(rate = 5))

#simulated samples
sims <- invoke_map(f, params, n = 50)

# Use walk() to make a histogram of each element in sims
walk(sims, hist)
```

### walking over 2 or more arguments
```{r}
#varying 2 arguments in the histogram made above (vary x and breaks)
#change from default to reasonable breaks for each histogram
breaks_list <- list(
  Normal = seq(6, 16, 0.5),
  Uniform = seq(0, 5, 0.25),
  Exp = seq(0, 1.5, 0.1)
)

walk2(sims, breaks_list, hist)
```

### walking with many arguments
* pwalk, works just like pmap
* first argument should be a list that relies on matching arguments by name (not position) for the function to be iterated over
* this code varies sims, breaks, and titles for each histogram
```{r}
#finds the breaks for any user specifed arg
find_breaks <- function(x) {
  rng <- range(x, na.rm = TRUE)
  seq(rng[1], rng[2], length.out = 30)
}
#uses map to iterate find_breaks over sims
nice_breaks <- map(sims, find_breaks)
nice_titles <- c("Normal(10, 1)", "Uniform(0, 5)", "Exp(5)")
#pwalk iterates over multiple arguments 
pwalk(list(x = sims, breaks = nice_breaks, main = nice_titles), hist, xlab = "")
```

### walking with pipes
```{r}
#summary uses as .f argument in map
sims %>%
  walk(hist) %>%
    map(summary)
```

## Robust functions
### stopifnot
* quick way to have your function stop if a condition is not met 
* takes logical expressions as arguments, if any are false an error will occur
```{r}
x <- c(NA, NA, NA)
y <- c( 1, NA, NA, NA)
#function counts how many shared NAs
# both_na <- function(x, y) {
#  stopifnot(length(x) == length(y))
#  sum(is.na(x) & is.na(y))
#}
#both_na(x, y)
```

### stop
allows you to specify a more informative error message
```{r}
#both_na <- function(x, y) {
#  if (length(x) != length(y)) {
#    stop("x and y must have the same length", call. = FALSE)
#  }  
#  sum(is.na(x) & is.na(y))
#}
```

### side effects
* Side effects describe the things that happen when you run a function that alters the state of your R session
* If foo() is a function with no side effects (a.k.a. pure), then when we run x <- foo(), the only change we expect is that the variable x now has a new value. No other changes to anything else... know exactly the changes to the state of the session just by reading the call to the function

## Different classes of functions
### unstable types
* type of return object depends on input (type inconsistent)
* sapply is an example of inconsistent type
* use purrr package and map functions instead of sapply
* or fail early if something goes wrong
* note: any() is useful in conditional statements
* flatten_chr takes a list, removes heirarchy and will return either a character string or error message (indicated by chr)

### nonstandard evaluation
* functions that reference variables in a non-standard wway
* if you do need to use non-standard evaluation functions, make sure you include checks
```{r}
#this function uses filter function in dplyr (which is NSE function) to subset data based off of a threshold value in the variable x
#code includes checks to make sure that x is in the dataframe, and that there is no variable called threshold in the df

library(dplyr)
big_x <- function(df, threshold) {
  # Write a check for x not being in df
  if (!"x" %in% names(df)) { 
    stop("df must contain variable called x", call. = FALSE)
  }

  # Write a check for threshold being in df
  if ("threshold" %in% names(df)) {
    stop("df must not contain variable called threshold", call. = FALSE)
  }

  dplyr::filter(df, x > threshold)
}
```

### Hidden arguments
* hidden arguments are function inputs that may be different for different users or r sessions
* ex: argument defaults that depend on global options
* in general you want to avoid having the return value of your function depend on any global options
* it's okay to have side effects depend on global options (like printing output, calling the summary function on something...)

### 2017-07-06 cheatsheets/ggplot2_cheatsheet.Rmd
organized cheatsheets into a file

---
title: "Data Visualization with ggplot2"
author: "Lisa Oshita"
date: "July 3, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Basics of ggplot2
```{r}
library(ggplot2)
#must tell ggplot that cyl is a categorical variable by wrapping it in factor, otherwise will treat it as numeric
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) + geom_point()
```

### Grammar of graphics
* data: the data to be plotted
* aesthetics: the scales onto which we map our data
* geometries: visual elements used for our data
* facets, statistics...
```{r}
#adding geom_smooth() would place a smoothed line over the points
ggplot(mtcars, aes(x = wt, y = mpg, color = disp, size = disp)) +
  geom_point() 
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point(alpha = 0.4)
```
* alpha controls transparency of points/lines...
* setting se = FALSE in geom_smooth layer will remove any error shading

```{r}
#DOESN'T OUTPUT THE SAME!!!!
ggplot(mtcars, aes(x = wt, y = mpg, col = cyl)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_smooth(aes(group = 1), method = "lm", se = FALSE, linetype = 2)
```

### tidyr package
* a dataset is called tidy when every row is an observation and every column is a variable
* gather() function takes multiple columns and gathers them into a single column by adding rows
* separate() function splits one column into two or more columns according to a pattern you define
```{r}
library(tidyr)
#created a key column with gather, this column contains values like sepal.width..., want to separate this into part and measure
iris.tidy <- iris %>%
  gather(key, Value, -Species) %>%
  separate(key, c("Part", "Measure"), "\\.")
```

### aesthetics
* ONLY APPLICABLE TO CATEGORICAL VARIABLES
* color changes outline of points
* fill changes inside shading
* shape (default = 19) (shapes 1-20 can only accept a color aesthetic, shapes 21-25 can accept both color and fill aesthetics )
```{r}
#mapping a categorical variable to fill doesn't change the colors (legend is generated)
#use fill when you have another shape, or with shape = 21 (which has fill and color attribute)
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl, col = am)) +
  geom_point(shape = 21, size = 4, alpha = 0.6)

ggplot(mtcars, aes(x = wt, y = mpg, label = cyl)) +
  geom_text()
```

### attributes
* variables in a dataframe are mapped to aesthetics in ggplot statement, visual elements are set by attributes in geom layers
* if aesthetic and attribute are set with the same argument, attribute takes precedence
```{r}
#attributes in geom_point overwrite whats in aesthetics 
my_color <- "#4ABEFF"
ggplot(mtcars, aes(x = wt, y = mpg, color = cyl)) +
  geom_point(color = my_color)
#choosing different shape
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl)) +
  geom_point(size = 10, shape = 23, color = my_color)
```

### position
```{r}
cyl.am <- ggplot(mtcars, aes(x = factor(cyl), fill = factor(am)))
cyl.am +
  geom_bar(position = "dodge")

#cleaning up axes with scale_ functions
val = c("#E41A1C", "#377EB8")
lab = c("Manual", "Automatic")
cyl.am +
  geom_bar(position = "dodge") +
  scale_x_discrete("Cylinders") + 
  scale_y_continuous("Number") +
  scale_fill_manual("Transmission", 
                    values = val,
                    labels = lab) 
```

### dummy aesthetic
```{r}
ggplot(mtcars, aes(x = mpg, y = 0)) +
  geom_jitter()

#add the function to change the y axis limits
ggplot(mtcars, aes(x = mpg, y = 0)) +
  geom_jitter() +
  scale_y_continuous(limits = c(-2,2))
```

### overplotting 
* can also use geom_jitter instead of geom_point
```{r}
ggplot(diamonds, aes(x = clarity, y = carat, color = price)) + 
  geom_point(alpha= 0.5)
#with jittering
ggplot(diamonds, aes(x = clarity, y = carat, color = price)) + 
  geom_point(alpha= 0.5, position = "jitter")
```

### histograms
* default bindwidth = range/30
* ..count.. is mapped to the y axis (stored in the internal dataframe)
* ..density.. is the proportional frequency of a bin in relation to the whole data set
```{r}
#fill argument stayes outside aes since it's an attribute and not an aesthetic mapping
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 1, aes(y = ..density..), fill = "#377EB8")
```

### position arguments (geom_hist/geom_bar)
* stack: place the bars on top of each other. Counts are used. This is the default position.
* fill: place the bars on top of each other, but this time use proportions.
* dodge: place the bars next to each other. Counts are used.
```{r}
#default
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) +
  geom_bar(position = "stack")
#fill
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) +
  geom_bar(position = "fill")
#dodge
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) +
  geom_bar(position = "dodge")

#position_dodge to be used when you want to specify how much dodging (same goes for position_jitter)
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) + 
  geom_bar(position = "dodge")
posn_d <- position_dodge(width = 0.2)
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) + 
  geom_bar(position = posn_d, alpha = 0.6)
```

### overlapping histograms
```{r}
#default position is "stack"
ggplot(mtcars, aes(mpg, fill = as.factor(cyl))) +
  geom_histogram(binwidth = 1, position = "identity", alpha = 0.4)
#geom_freqpoly allows for overlapping (identity is the default)
ggplot(mtcars, aes(mpg, col = as.factor(cyl))) +
  geom_freqpoly(binwidth = 1)
```

### color ramps
* use scale_fill_brewer to set color palette (?brewer.pal for full list)
* use function colorRampPalette to generate all colors need 
* input is character vector of 2 or more color values (ex: #FFFFFF" (white) and "#0000FF" (pure blue))
* output is a function that takes one argument- the number of colors you want to extrapolate
```{r}
#working with Vocab dataframe from car package
library(car)

#this outputs an incomplete plot, since default gave has 9 colors, but variable has 11 categories
ggplot(Vocab, aes(x = education, fill = vocabulary)) +
  geom_bar(position = "fill") +
  scale_fill_brewer()

#Definition of a set of blue colors (from RColorBrewer package)
library(RColorBrewer)
blues <- brewer.pal(9, "Blues")
#makes a color range
blue_range <- colorRampPalette(blues)
#uses blue_range and scale_fill_manual to set color of bars
ggplot(Vocab, aes(x = as.factor(education), fill = as.factor(vocabulary))) +
  geom_bar(position = "fill") +
  scale_fill_manual(values = blue_range(11))

```

### line plots
* use geom_line()
* can use geom_rect to draw rectangles to highlight certain portions of a time-series line plot

### qplot
* good for simple plots
```{r}
qplot(wt, mpg, data = mtcars)

#categorical
qplot(wt, mpg, data = mtcars, size = factor(gear))
#continuous
qplot(wt, mpg, data = mtcars, color = hp)
#overplotting
qplot(x = factor(cyl), y = factor(vs), data = mtcars)
#using jitter to fix overplotting
qplot(x = factor(cyl), y = factor(vs), data = mtcars, geom = "jitter")

#dotplots (geom_dotplot uses a binning statistic)
ggplot(mtcars, aes(factor(cyl), wt, fill = factor(am))) +
  geom_dotplot(binaxis = "y", stackdir = "center")
#same plot with qplot()
qplot(
  factor(cyl), wt, 
  data = mtcars, 
  fill = factor(am), 
  geom = "dotplot", 
  binaxis = "y", 
  stackdir = "center"
)
```

### examples
```{r}
#ChickWeight dataset
ggplot(ChickWeight, aes(x = Time, y = weight, color = Diet)) + 
  geom_line(aes(group = Chick), alpha = 0.3) + 
  geom_smooth(lwd = 2, se = FALSE)
#titanic dataset 
library(titanic)
ggplot(titanic_train, aes(x = Pclass, fill = Sex)) + 
  geom_bar(position = "dodge") + 
  facet_grid(.~Survived)

posn.jd <- position_jitterdodge(0.5, 0, 0.6)
ggplot(titanic_train, aes(x = Pclass, y = Age, color = Sex)) + 
  geom_point(size = 3, alpha = 0.5, position = posn.jd) + 
  facet_grid(.~Survived)
```

### 2017-07-07 practice.Rmd
practice with text mining

@@
 length(which(out$time_until_answer < 0))
+library(dplyr)
+out %>% 
+  filter(time_until_answer < 0) %>%
+  select(post_date, first_answer_date, answered)
 ```
@@
 ```
+
+### practicing with text mining
+```{r}
+library(dplyr)
+#working only with the 2000 questions that were answered the fastest
+arranged <- out1_positive %>% arrange(time_until_answer)
+fastest <- arranged[1:2000,]
+
+library(qdap)
+library(tm)
+# INSTALLING RWEKA NOT WORKING
+# library(RWeka)
+# 
+# titles <- fastest$title
+# 
+# #clean titles 
+# qdap_clean <- function(x) {
+#   x <- replace_abbreviation(x)
+#   x <- replace_contraction(x)
+#   x <- replace_number(x)
+#   x <- replace_ordinal(x)
+#   x <- replace_symbol(x)
+#   x <- tolower(x)
+#   return(x)
+# }
+# tm_clean <- function(corpus) {
+#   tm_clean <- tm_map(corpus, removePunctuation)
+#   corpus <- tm_map(corpus, stripWhitespace)
+#   corpus <- tm_map(corpus, removeWords, stopwords("en"))
+#   return(corpus)
+# }
+# 
+# tokenizer <- function(x) {
+#   NGramTokenizer(x, Weka_control(min = 2, max = 3)) }
+# 
+# titles <- qdap_clean(titles)
+# titles_cor <- VCorpus(VectorSource(titles))
+# titles_corpus <- tm_clean(titles_cor)
+# 
+# titles_tdm <- TermDocumentMatrix(titles_corpus, )
+```

### 2017-07-07 cheatsheets/textmining_cheatsheet.Rmd
added notes

--- 2017-07-06 textmining_cheatsheet.Rmd
@@
 #finds the 10 most frequent terms (doesn't mattern what kind of word, all words treated equally)
-term_count <- freq_terms(new_text, 10)
+term_count <- freq_terms(text, 10)
 plot(term_count)
@@
 ```{r}
+library(tm)
 num  <- c(1,2,3)
@@
 ```
+
+### Visualizing common words (process for visualizing dissimilar words is similar to this)
+* visualize common words across multiple documents: commonality_cloud()
+* use paste function and collapse = " " to create a vector containing all documents
+* use VectorSource() to convert vector to vector source
+* use VCorpus() on the vector source to create corpus 
+* then clean corpus, convert it to TDM, convert it to matrix, then use commonality.cloud() with max.words and colors arguments
+
+### other visualizations 
+* create word networks with word_associate() function
+* can create dendrograms 
+* word associations: findAssocs(tdm, "word", 0.25), returns a list, for any given word, calculates its correlation with every other word in a TDM or DTM
+
+### term frequency-inverse document frequency
+* if a term appears frequently it must be important, but if it appears in all documents- not likely to be important:
+* TfIdf score increases by term occurrence but is penalized by the frequency of appearance among all documents
+* use: control = list(weighting = weightTfIdf) in TermDocumentMatrix function

### 2017-07-07 Hours.Rmd
hours

> Summer Research Hours Log

Date   | Hours | Time        | Description
------ | ----- | ----------- | -----------------------------------------
6/26/2017 | 1.5 | 2:30-4:00PM | Integrated R and Github, familiarized myself with GitHub
6/27/2017 | 1 | 11:00-12:00PM | Explored the Q&A forum, read and took notes on part of the study posted on GitHub
6/28/2017 | 3.5 | 11:30-3:00PM | Finished reading and taking notes on the study, learned how to upload to Github through R studio, started the stringr data camp course
6/28/2017 | 5 | 5:00-10:00PM | Continued with data camp courses
6/29/2017 | 3 | 7:00-10:00AM | Continued with data camp courses, brainstormed variables to consider in the model
6/29/2017 | 3.5 | 3:00-6:30PM | Responded to issues, redid stringr course and created a cheatsheet
6/30/2017 | 3.25 | 8:15-11:30AM | Redid/completed stringr course, practiced with stringr functions on the data set
6/30/2017 | 3 | 3:30-6:30PM | Ran into problems with stringr functions and the dataset- tried to get them to work, moved onto the next data camp course
6/30/2017 | 2 | 6:30-9:30PM | Writing functions data camp course + cheatsheet
7/1/2017 | 2 | 8:30-10:30AM | Completed writing functions course, started dplyr course 
7/2/2017 | 1 | 9:00-10:00PM | Continued working on the dplyr course + cheatsheet
7/3/2017 | 2.25 | 10:00-12:15PM | Finished dplyr course
7/3/2017 | 1.5 | 4:00-5:30PM | Practiced applying dplyr functions to the dataset, started on ggplot2 course
7/3/2017 | 2 | 6:30-8:30PM | Continued working on ggplot2 course + cheatsheet
7/4/2017 | 1.5 | 2:00-3:30PM | Continued with ggplot2 course
7/5/2017 | 3 | 9:30-12:30PM | Finished ggplot2 course, practiced using ggplot on the dataset, reviewed STAT 417 notes
7/5/2017 | 2.25 | 2:45-5:00PM | Started the text mining course + cheatsheet
7/6/2017 | 1.5 | 7:30-9:00AM | Continued with text mining course
7/6/2017 | 2.75 | 2:15-5:00PM | Finished text mining course + cheatsheet
7/6/2017 | 2.5 | 6:30-9:00PM | Tried to apply text mining techniques to the dataset, ran into problems with Java, uploaded hours timesheet to Github

>> __Total Hours: 48__

### 2017-07-07 practice_survivalanalysis.Rmd
practicing with survival analysis

---
title: "Practicing with Survival Analysis"
author: "Lisa Oshita"
date: "July 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### importing/setting up data, creating survival object
```{r}
#import data
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

#creating time to event variable
out$time_until_answer <- out$first_answer_date - out$post_date
#filling in the NAs
empty <- which(is.na(out$time_until_answer))
for (i in empty) {
  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
}

#subsetting to include only observations in english with positive time to event values
library(dplyr)
out1 <- out %>% 
          tbl_df() %>% 
          filter(langid == "en") %>%
          filter(time_until_answer > 0)

hist(out1$time_until_answer)

library(survival)

#creating survival object
surv_object <- Surv(out1$time_until_answer, out1$answered)
```

### km estimator
* to do KM estimate for different groups: survfit(surv_object ~ category_to_groupby)
* confidence intervals: CI for S(t) are pointwise intervals
* can use log-log approach (specify conf.type = "log-log") to prevent upper limits from exceeding 1
```{r}
#KM estimator
KM.obj <- survfit(surv_object ~ 1, conf.type = "plain")
str(KM.obj)
summary(KM.obj)

#cb <- confBands(surv_object, confLevel=0.95, type="hall") #for confidence bands
plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability")
#lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
#lines(cb$time, cb$upper, lty=3, type="s")

#estimate means survival time E(T)
#estimate percentiles of survival time
```

### instantaneous hazard using epiR package
```{r}
library(epiR)
h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s")
plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1500000), type = "s")

```

### estimating the cumulative hazard function
* H(t) = −log S(t), or can use the Nelson-Aalen estimator
* no function in survival package to do this
```{r}
#Kaplan Meier estimator of cumulative hazard
fit <- summary(survfit(surv_object ~ 1))
H.hat <- -log(fit$surv)
H.hat <- c(H.hat, tail(H.hat, 1)) #all this did was repeat the last entry?

#Nelson Aalen estimator
h <- fit$n.event / fit$n.risk
H.tilde <- cumsum(h)
H.tilde <- c(H.tilde, tail(H.tilde, 1))

#plotting both KM and Nelson Aalen on same graph
plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s")
points(c(fit$time, 6500000), H.tilde, lty=2, type="s")
legend("topleft", legend=c("H.hat","H.tilde"), lty=1:2)
#KM and Nelson Aalen estimators look the same- because large data set? 
```

### mean, medians, percentiles
```{r}
#at 30,158 seconds, 50% of the questions have been answered
#mean survival time = 2,748,083
#upper limit = largest observation in time to event var
print(KM.obj, print.rmean=TRUE)

#finding percentiles 
library(survival)
quantile(KM.obj, c(0.01, 0.10, 0.25, 0.50, 0.75, 0.95)) #Getting NA for 75 and 95 quantiles
quantile(KM.obj, 0.75)
```

### 2017-07-08 Hours.Rmd
7/7/17

@@
 7/6/2017 | 2.75 | 2:15-5:00PM | Finished text mining course + cheatsheet
-7/6/2017 | 2.5 | 6:30-9:00PM | Tried to apply text mining techniques to the dataset, ran into problems with Java, uploaded hours timesheet to Github
+7/6/2017 | 2.5 | 6:30-9:00PM | Tried to apply text mining techniques to the dataset, ran into RWeka package, uploaded hours timesheet to Github
+7/7/2017 | 4.75 | 11:15-5:00PM | Learned and practiced with functions in the survival package on the data set, came up with descriptive summaries, explored the response variable
 

### 2017-07-10 practice_survivalanalysis.Rmd
re-upload

@@
           filter(time_until_answer > 0)
-
-hist(out1$time_until_answer)
 
@@
 * no function in survival package to do this
+* working with instructions from OpenIntro Survival analysis in r pdf 
 ```{r}
@@
 ```{r}
-#at 30,158 seconds, 50% of the questions have been answered
-#mean survival time = 2,748,083
+#at 30,158 seconds (502.6 min), 50% of the questions have been answered
+#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)
 #upper limit = largest observation in time to event var
@@
 library(survival)
-quantile(KM.obj, c(0.01, 0.10, 0.25, 0.50, 0.75, 0.95)) #Getting NA for 75 and 95 quantiles
-quantile(KM.obj, 0.75)
+quantile(KM.obj, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.75))
+#getting NA for 0.75 because our lowest S(t) = 0.3410254
 ```
+
+* interpreting quantiles: 
+* at time = 138 seconds (2.3 min), 1% of the questions have been answered
+*           802 seconds (13.4 min), 10% of the questions have been answered
+*           2,883 seconds (48.1 min), 25% of the questions have been answered
+
+### exploring time_until_answered
+* largest time_until_answered = 89.97 days (obs = 7807), and is censored
+* shortest time_until_answered = 23 seconds (obs = 7485) 
+```{r}
+sum(out1$answered)/length(out1$answered)
+#64.4% of observations are complete
+#35.6% of observations are censored
+
+library(ggplot2)
+ggplot(out1, aes(x = time_until_answer)) + 
+  geom_histogram() + 
+  scale_x_continuous(limits = c(20, 30000))
+```

### 2017-07-11 Hours.Rmd
updated total hours
hours for 7/10

--- 2017-07-07 Hours.Rmd
@@
 7/6/2017 | 2.75 | 2:15-5:00PM | Finished text mining course + cheatsheet
-7/6/2017 | 2.5 | 6:30-9:00PM | Tried to apply text mining techniques to the dataset, ran into problems with Java, uploaded hours timesheet to Github
+7/6/2017 | 2.5 | 6:30-9:00PM | Tried to apply text mining techniques to the dataset, ran into RWeka package, uploaded hours timesheet to Github
+7/7/2017 | 4.75 | 11:15-5:00PM | Learned and practiced with functions in the survival package on the data set, came up with descriptive summaries, explored the response variable 
+7/10/2017 | 1 | 9:00-10:00AM | Started learning how to fit parametric distributions in r
+7/10/2017 | 4 | 1:00- 5:00PM | Experimented with calculating MLEs from the data for different parametric distributions, tried to create probability plots to assess the fits for each distribution
+7/10/2017 | 3 | 6:30-9:30PM | Continued working with parametric distributions, experimented with fitdistrplus package to fit parametric distributions
 
->> __Total Hours: 48__
+>> __Total Hours: 60.75__

### 2017-07-11 practice_survivalanalysis.Rmd
minor changes

@@
 #creating survival object
-surv_object <- Surv(out1$time_until_answer, out1$answered)
+surv_object <- Surv(out1$time_until_answer, out1$answered, type = "right")
 ```
@@
 #lines(cb$time, cb$upper, lty=3, type="s")
-
-#estimate means survival time E(T)
-#estimate percentiles of survival time
 ```
@@
 plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s")
-plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1500000), type = "s")
-
+plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s")
+#there is a spike in instantaneous hazard before 200,000 seconds (55.5 hours or 2.31 days)
 ```
@@
 points(c(fit$time, 6500000), H.tilde, lty=2, type="s")
-legend("topleft", legend=c("H.hat","H.tilde"), lty=1:2)
+legend("bottomright", legend=c("H.hat","H.tilde"), lty=1:2)
 #KM and Nelson Aalen estimators look the same- because large data set? 
+#Rate of increase in cumulative hazard spikes up drastically (immediately after question is posted)- indicating that hazard is increasing on that interval.
+Rate of increase in cumulative hazard after a certain point, levels out pretty quickly- indicating that hazard is decreasing
 ```
@@
 ```{r}
-#at 30,158 seconds (502.6 min), 50% of the questions have been answered
+#at 30,158 seconds (502.6 min, 8.38 hours), 50% of the questions have been answered
 #mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)

### 2017-07-11 practice_parametricdist.Rmd
fitting parametric distributions to the data

---
title: "Practice with parametric distributions"
author: "Lisa Oshita"
date: "July 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### import the data
```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

#creating time to event variable
out$time_until_answer <- out$first_answer_date - out$post_date
#filling in the NAs
empty <- which(is.na(out$time_until_answer))
for (i in empty) {
  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
}

#subsetting to include only observations in english with positive time to event values
library(dplyr)
out1 <- out %>% 
          tbl_df() %>% 
          filter(langid == "en") %>%
          filter(time_until_answer > 0)
```

### finding parameter estimates with flexsurv package
```{r}
library(flexsurv)

#weibull distribution
weibull <- flexsurvreg(surv_object~1, data = out1, dist = "weibull")
weibull
plot(weibull)
#shape = 0.228, scale = 1320000, AIC = 123791.7
qqplot(rweibull(1e+5, shape = 0.228, scale = 1320000), out1$time_until_answer)

#exponential distribution
exp <- flexsurvreg(surv_object~1, data = out1, dist = "exp")
exp
plot(exp)
#rate = 4.98e-07, AIC = 153610

#lognormal distribution
lnormal <- flexsurvreg(surv_object~1, data = out1, dist = "lnorm")
lnormal
plot(lnormal)
#meanlog = 12.05, sdlog = 4.86, AIC = 122112.1

#logistic distribution
logistic <- flexsurvreg(surv_object~1, data = out1, dist = "llogis")
logistic
plot(logistic)
#shape = 0.332, scale = 119000, AIC = 122482
```

### setting up probability plots to assess fit
```{r}
# library(car) #for the qqPlot function
# par(mfrow = c(2,2))
# qqPlot(out1$time_until_answer, distribution = "weibull", param.list = list(shape = 0.228, scale = 1320000), plot.type = "Q-Q")
qqplot(rweibull(n = 8000, shape = 0.228, scale = 1320000), out1$time_until_answer)
abline(0,1)
qqplot(rlnorm(n = 8000, meanlog = 12.05, sdlog = 4.86), out1$time_until_answer)
abline(0,1)
#are the plots actually following the line?- maybe scale too large to see it correctly 
```

### learning about flexsurvreg 
```{r}
time <- c(5,8,12,24,32,17,16,17,19,30)
censor <- c(1,1,1,1,1,1,0,0,0,0)
example <- data.frame(time, censor)

s <- Surv(example$time, example$censor, type = "right")
exponential <- flexsurvreg(s~1, data = example, dist = "exp")
exponential
survreg(s~1, data = example, dist = "exp")

data(ovarian)
fitg <- flexsurvreg(formula = Surv(futime, fustat) ~ 1, data = ovarian, dist="gengamma")
fitg
fitw <- flexsurvreg(formula = Surv(futime, fustat) ~ 1, data = ovarian, dist="weibull")
fitw
plot(fitg)
lines(fitw, col="blue", lwd.ci=1, lty.ci=1)
```

### parametric distributions using fitdistrplus package NOT WORKINGG
```{r}
library(fitdistrplus)

#creating the data frame to use in the function
left <- right <- out1$time_until_answer
right[out1$answered == 0] <- NA_integer_
censdata <- data.frame(left, right)

#fitweibull <- fitdistcens(censdata, distr = "weibull")

```

### practicing with fitdistcens function 
```{r}
data("salinity")
str(salinity)
data("smokedfish")

fsal.ln <- fitdistcens(salinity, "lnorm")
fsal.ln

log10EC50 <-log10(fluazinam)
fln <- fitdistcens(log10EC50,"norm")
fln
summary(fln)
plot(fln)
```

### 2017-07-12 Hours.Rmd
7/11 hours

--- 2017-07-07 Hours.Rmd
@@
 7/6/2017 | 2.75 | 2:15-5:00PM | Finished text mining course + cheatsheet
-7/6/2017 | 2.5 | 6:30-9:00PM | Tried to apply text mining techniques to the dataset, ran into problems with Java, uploaded hours timesheet to Github
+7/6/2017 | 2.5 | 6:30-9:00PM | Tried to apply text mining techniques to the dataset, ran into RWeka package, uploaded hours timesheet to Github
+7/7/2017 | 4.75 | 11:15-5:00PM | Learned and practiced with functions in the survival package on the data set, came up with descriptive summaries, explored the response variable 
+7/10/2017 | 1 | 9:00-10:00AM | Started learning how to fit parametric distributions in r
+7/10/2017 | 4 | 1:00- 5:00PM | Experimented with calculating MLEs from the data for different parametric distributions, tried to create probability plots to assess the fits for each distribution
+7/10/2017 | 3 | 6:30-9:30PM | Continued working with parametric distributions, experimented with fitdistrplus package to fit parametric distributions
+7/11/2017 | 4.25 | 10:45-3:00PM | Tried to get the probability plots to work, used techniques learned in data camp courses and survival analysis to explore the data set and get an idea of what variables may be important
+7/11/2017 | 3.75 | 6:00-9:45PM | Continued to explore the data set
 
->> __Total Hours: 48__
+>> __Total Hours: 68.75__

### 2017-07-12 data_exploration.Rmd
summarizing findings from variable exploration and from using survival analysis techniques

---
title: "Descriptive Statistics"
author: "Lisa Oshita"
date: "July 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic descriptive statistics/exploring the variables
### using out_english data set: 
* about 8000 observations
* around 64% of questions were answered (~ 36% unanswered/censored)

### examining distribution of time_until_answer
* min = 30 sec, max = 7772000 sec (~90 days) (id = 389776)
* mean = 1281000 sec (~15 days), median = 31650 sec (~8 hours)
* 1st quartile = 3134 sec (52.2 min), 3rd quartile = 1975000 (~23 days) (25% of the questions wre answered before 52 min, and 75% of the questions were answered after 23 days, middle 50% of the data falls between 52 min and 23 days)
* distibution of response is extremely skewed right 
* from distribution it seems like quite a bit of data falls between 30 sec and 1200000 (~14 days)

### examining time_until_answer by categories 
* phone, mac, tablet, pc, and electronics have the most questions (out of 15 total categories)
* Skills category has shortest average time_until_answer, but only has 5 in that category
* Mac has the second shortest average time_until_answer, with a good amount of observations (666)
* PC and then Phone have next shortest average times, with 413 and 2148 observations 
* Camera has the longest average time, with 269 observations
* looking at categories according to median time_until_answer gives similar results (skills, mac and phone have shortest median times)
* distributions of time_until_answer for Mac, PC, Phone are extremely skewed right (exactly like the distribution of time_until_answer for all categories)

### examining time_until_answer according to whether or not it contains a question mark
* 1193/7760 (15%) of the questions contain a question mark
* for almost all categories, questions that contain a question mark seem to get answered faster (lower average and median times) 
* but less than half of the total questions for each category contain question marks- may be contributing to the lower values 
* around 71% of the questions that contain question marks were answered 
* questions about Mac, PC, and skills (but only contains 5 obs), have the highest proportion of questions that contain "?"

### examining title length (look at length of text and device title as well)
* mean = 42 characters
* median = 40 characters
* longest title is 89 characters, shortest is 12 characters
* seems like questions with longer titles might have shorter average time_until_answer
* Mac has average title length of 44 characters, average time_until_answer = 453980.6 seconds (which is on the shorter end of values), while those with shorter titles seem to have longer times

### examining text length
* shortest text: 20 characters, longest text: 4814.0
* from histogram of text lengths, a bulk of the questions have text lengths between 20 and 1000 characters long (distribution skewed right)
* seems like categories with longer median text lengths have shorter time_until_answer values

### device length 
* min = 0, max = 136 (id = 390271), mean = 17, median = 16
* distribution of device lengths is skewed right
* didn't really see anything interesting here

### number of tags included in a question
* max number of tags = 4
* 56% of questions don't include any tags
* 43% of the questions that do have a tag only have 1 tag
* seems like there MAY be a slight tendency for questions with more tags to get answers quicker (shorter avg time_until_answer, but also have not as many observations)

### number of images included
* only 4% of the questions contain any images
* min = 0, max = 13 (id = 396580)
* there MAY be some evidence that questions that include images seems to get answers quicker

## Survival analysis statistics 
### KM estimator/curve
* from the KM curve, the survival probability drops drastically from 1 down to about 0.4 before 400,000 seconds (~5 days). After that point, survival curve seems to decrease slowly and remain around 0.3-0.4 (due to the largest times being censored) 
* lowest survival probability is 0.346

### quantiles
* (median) At 30,158 seconds (8.38 hours), 50% of the questions have been answered
* at 857 seconds (14.3 min), 10% of the questions have been answered
* at 3163 seconds (52.7 min), 25% of the questions have been answered
* there is no time for which 75th percentile (since the lowest survival probability = 0.346, and it never reaches 0) (means that we'll never get a total of 75% of questions answered, there will always be some questions that "survive")

### hazard rates
* instantaneous hazard drops pretty drastically after question is first posted, before 400,000 seconds (~4-5 days), it appears that hazard rate is really close to 0
* looking at the plot, there's a spike in instantaneous hazard around 200,000 seconds (~2.3 days)
* cumulative hazard rate: increases very quickly until about 400000 seconds (~4-5 days) (indicating that hazard is increasing on that interval), when it starts to even out until it coasts at 1 (indicating that hazard is decreasing
* do the Nelson Aalen and KM estimators of cumulative hazard look the same becasue the data set is so large?

#at 30,158 seconds (502.6 min, 8.38 hours), 50% of the questions have been answered
#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)

### 2017-07-12 practice.Rmd
more variable exploration

@@
 
-#26 observations in out dataframe have negative time to event variable
-length(which(out$time_until_answer < 0))
+#subsetting to include only questions in english
 library(dplyr)
-out %>% 
-  filter(time_until_answer < 0) %>%
-  select(post_date, first_answer_date, answered)
-```
-
-### Practicing with stringr 
-```{r}
-library(stringr)
-library(rebus)
-
-#variable indicating if title contains questionmark 
-out$contain_questionmark <- str_detect(out$title, pattern = QUESTION)
-
-#practicing with product categorization
-phones <- regex("phone", ignore_case = TRUE)
-out$product_type[str_detect(out$device, pattern = phones)] <- "Phone"
-```
-
-### Practicing with dplyr
-```{r}
-library(stringr)
-library(dplyr)
-
-#using only observations in English
 out_english <- out %>% 
@@
                 filter(langid == "en")
+```
+
+### exploring time to event variable
+```{r}
+summary(out_english$time_until_answer)
+
+library(ggplot2)
+
+#defining tick marks for x-axis
+min <- min(out_english$time_until_answer)
+max <- max(out_english$time_until_answer)
+
+require(scales)
+ggplot(out_english, aes(x = time_until_answer)) + 
+  geom_histogram(bins = 10) + 
+  scale_x_continuous(labels = comma, breaks = seq(min, max, by = (max-min)/10)) + 
+  theme(axis.text.x = element_text(angle=90, hjust=1))
+
+#zoomed in histogram of responses
+ggplot(out1, aes(x = time_until_answer)) + 
+  geom_histogram() + 
+  scale_x_continuous(limits = c(20, 30000))
+
+boxplot(out_english$time_until_answer)
+bstats <- boxplot.stats(out_english$time_until_answer)
+bstats
+#797 questions lie outside of the whiskers
+```
+
+### exploring the categories 
+```{r}
+table(out_english$category)
 
@@
 
-#view average time until answered grouped by whether or not question contains "?", for each category
-#seems like for a lot of categories, questions with question marks get answered faster
+#looking at median time_until_answer since data is skewed right
+out_english%>%
+  group_by(category) %>%
+  summarise(median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
+  arrange(median_time)
+
+#looking at time_until_answer distributions according to Mac, PC, Phone, showing whether or not the question contains a question mark
+ggplot(subset(out_english, category %in% c("Mac", "PC", "Phone")), aes(x = time_until_answer, fill = as.factor(contain_questionmark))) +
+  geom_histogram(bins = 10) + 
+  facet_grid(.~category)
+
+#looking at only data for phones category (nothing interesting here)
+phones_only <- out_english %>% filter(category == "Phone")
+ggplot(phones_only, aes(x = title_length, y = time_until_answer)) + 
+  geom_point(size = 3, alpha = 0.5)
+```
+
+### investigating whether a question mark is present or not
+```{r}
+library(stringr)
+library(rebus)
+
+#variable indicating if title contains questionmark 
 out_english$contain_questionmark <- str_detect(out_english$title, pattern = QUESTION)
+sum(out_english$contain_questionmark)
+
+#view average time_until_answered grouped by whether or not question contains "?", for each category
+#seems like for a majority of the categories, questions with question marks get answered faster
 out_english %>%
   group_by(category, contain_questionmark) %>%
-  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
+  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), median =
+              median(time_until_answer, na.rm = TRUE), num = n()) %>%
   arrange(category, avg_time)
 
-#looking at average time until answered for intervals of title length
+#calculating proportion of questions that contain a question mark that were answered
+q <- out_english %>%
+        filter(contain_questionmark == T)
+sum(q$answered)/nrow(q)
+
+#proportion of questions that contain ? for each category
+prop.table(table(out_english$category, out_english$contain_questionmark), 1)
+```
+
+### exploring title length
+```{r}
+#creating title_length variable
+out_english$title_length <- str_length(out_english$title)
+hist(out_english$title_length)
+summary(out_english$title_length)
+
+#viewing average/median title length for each category and comparing it to average time until answer
+out_english %>%
+  group_by(category) %>%
+  summarise(avg_length = mean(title_length), median_length = median(title_length), avg_time = mean(time_until_answer), n = n()) %>%
+  arrange(avg_length)
+
 #creating title length intervals
-title_length <- str_length(out_english$title)
-out_english$title_length_intervals <- cut(title_length, breaks = 8)
+out_english$title_length_intervals <- cut(out_english$title_length, breaks = 8)
 #don't really see anything interesting here 
@@
 
+#plot with title length 
+#randomly subset half of the data set to make easier to read
+#don't see any association 
+ggplot(sample_frac(out_english, size = 0.50, replace = FALSE), aes(x = title_length, y = time_until_answer)) + 
+  geom_point()
 ```
 
-### practicing with ggplot
+### exploring text length
 ```{r}
-library(ggplot2)
-library(stringr)
+out_english$text_length <- str_length(out_english$text)
+hist(out_english$text_length, xlim = c(0,3000))
+summary(out_english$text_length)
 
-#using only observations with a positive time_until_answer value (26 observations have negative time until answer values)
-out1_positive <- out_english %>% filter(time_until_answer > 0)
+#examining avg/median text length and comparing it to avg time_until_answer for each category
+out_english %>%
+  group_by(category) %>%
+  summarise(avg = mean(text_length), median = median(text_length), avg_time = mean(time_until_answer), n = n()) %>%
+  arrange(avg_time)
+```
 
-#histogram of time_until_answer
-ggplot(out1_positive, aes(x = time_until_answer)) + 
-  geom_histogram(bins = 10)
+### exploring device length (find another way to classify how detailed device is)
+*observation 7548 has a 136 character string for it's device
+```{r}
+out_english$device_length <- str_length(out_english$device)
+hist(out_english$device_length)
+summary(out_english$device_length)
 
-#plot of number of tags and time_until_answer
-ggplot(out1_positive, aes(x = factor(n_tags), y = time_until_answer)) + 
+#don't see anything interesting here
+out_english %>% 
+  group_by(category) %>%
+  summarise(avg = mean(device_length), median = median(device_length), avg_time = mean(time_until_answer), n = n()) %>%
+  arrange(avg_time)
+
+```
+
+### examining the number of tags for a question
+```{r}
+summary(out_english$n_tags)
+
+#proportion of questions that don't have any tags
+sum(out_english$n_tags == 0)/nrow(out_english)
+table(out_english$n_tags)
+
+#viewing average time_until_answer grouped by number of tags and category
+out_english %>%
+  group_by(category, as.factor(n_tags)) %>%
+  summarise(avg_time = mean(time_until_answer), n = n()) %>%
+  arrange(category)
+
+#plot of number of tags and time_until_answer (nothing interesting here)
+ggplot(out_english, aes(x = factor(n_tags), y = time_until_answer)) + 
   geom_point(position = "jitter")
+```
 
-#plot with title length 
-out1_positive$title_length <- str_length(out1_positive$title)
+### number of pictures included 
+```{r}
+summary(out_english$n_images)
+hist(out_english$n_images)
+table(out_english$n_images)
 
-ggplot(out1_positive, aes(x = title_length, y = time_until_answer)) + 
-  geom_point()
+#proportion of questions that include any images
+sum(out_english$n_images != 0)/nrow(out_english)
 
-#looking at only data for phones category 
-phones_only <- out1_positive %>% filter(category == "Phone")
-ggplot(phones_only, aes(x = title_length, y = time_until_answer)) + 
-  geom_point(size = 3, alpha = 0.5)
+#looking at mean time_until_answer grouped by n_images
+out_english %>% 
+  group_by(as.factor(n_images)) %>%
+  summarise(avg_time = mean(time_until_answer), n = n()) %>%
+  arrange(avg_time)
+
+#looking at mean time_until_answer grouped by categories and n_images
+out_english %>%
+  group_by(category, as.factor(n_images)) %>%
+  summarise(avg_time = mean(time_until_answer), median = median(time_until_answer), n = n()) %>%
+  arrange(category, avg_time)
 ```

### 2017-07-12 practice_parametricdist.Rmd
tried to construct probability plots

@@
 ```{r}
+surv_object <- Surv(out1$time_until_answer, out1$answered, type = "right")
+
 library(flexsurv)
 
-#weibull distribution
 weibull <- flexsurvreg(surv_object~1, data = out1, dist = "weibull")
@@
 plot(weibull)
-#shape = 0.228, scale = 1320000, AIC = 123791.7
-qqplot(rweibull(1e+5, shape = 0.228, scale = 1320000), out1$time_until_answer)
 
-#exponential distribution
 exp <- flexsurvreg(surv_object~1, data = out1, dist = "exp")
@@
 plot(exp)
-#rate = 4.98e-07, AIC = 153610
 
-#lognormal distribution
 lnormal <- flexsurvreg(surv_object~1, data = out1, dist = "lnorm")
@@
 plot(lnormal)
-#meanlog = 12.05, sdlog = 4.86, AIC = 122112.1
+#has lowest AIC of the 4 distributions
 
-#logistic distribution
 logistic <- flexsurvreg(surv_object~1, data = out1, dist = "llogis")
@@
 plot(logistic)
-#shape = 0.332, scale = 119000, AIC = 122482
+
 ```
@@
 ```{r}
-# library(car) #for the qqPlot function
-# par(mfrow = c(2,2))
-# qqPlot(out1$time_until_answer, distribution = "weibull", param.list = list(shape = 0.228, scale = 1320000), plot.type = "Q-Q")
-qqplot(rweibull(n = 8000, shape = 0.228, scale = 1320000), out1$time_until_answer)
+#are the plots actually following the line?- maybe scale too large to see it correctly 
+qqplot(rweibull(15000, shape = 2.26e-01, scale = 1.32e+06), out1$time_until_answer, xlab = "rweibull values", ylab = "seconds")
 abline(0,1)
-qqplot(rlnorm(n = 8000, meanlog = 12.05, sdlog = 4.86), out1$time_until_answer)
+
+#narrowed scope of x-axis to get a closer look at the plot-data does not fit a weibull distribution (not sure if did this correctly)
+qqplot(rweibull(15000, shape = 2.26e-01, scale = 1.32e+06), out1$time_until_answer, xlim = c(0,1e+8), xlab = "rweibull values", ylab = "seconds")
 abline(0,1)
-#are the plots actually following the line?- maybe scale too large to see it correctly 
+#data doesn't fit weibull distribution
+
+qqplot(rexp(15000, rate = 4.86e-07), out1$time_until_answer, xlab = "rexp values", ylab = "seconds")
+abline(0,1)
+#data doesn't fit an exponential distribution either
+
+qqplot(rlnorm(15000, meanlog = 12.1129, sdlog = 4.8951), out1$time_until_answer, xlab = "rlnorm values", ylab = "seconds", xlim = c(0, 5e+7))
+abline(0,1)
+#data doesn't fit lognormal distribution
+
+qqplot(rlogis(15000, location = 3.30e-01, scale = 1.28e+05), out1$time_until_answer)
+abline(0,1)
+#data does not fit logistic distribution 
 ```
 
-### learning about flexsurvreg 
+### learning about flexsurvreg (using different data)
 ```{r}
@@
 
-### parametric distributions using fitdistrplus package NOT WORKINGG
+### trying to apply fitdistrplus functions to data (NOT WORKING)
 ```{r}
@@
 
-### practicing with fitdistcens function 
+### practicing with fitdistcens function on different dataset 
 ```{r}

### 2017-07-12 practice_survivalanalysis.Rmd
changed formatting of axes in hazard and survival plots

@@
 
+#defining tick marks for x-axis
+min <- min(out_english$time_until_answer)
+max <- max(out_english$time_until_answer)
+
 #cb <- confBands(surv_object, confLevel=0.95, type="hall") #for confidence bands
-plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability")
+plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xaxt = "n")
+axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE) #adding more detailed x axis
 #lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
@@
 h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
-plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s")
-plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s")
+plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s", xaxt = "n")
+axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)
+
+plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s", xaxt = "n")
+axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)
+
 #there is a spike in instantaneous hazard before 200,000 seconds (55.5 hours or 2.31 days)
@@
 #plotting both KM and Nelson Aalen on same graph
-plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s")
-points(c(fit$time, 6500000), H.tilde, lty=2, type="s")
+plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s", xaxt = "n")
+points(c(fit$time, 6500000), H.tilde, lty=2, type="s", xaxt = "n")
 legend("bottomright", legend=c("H.hat","H.tilde"), lty=1:2)
+axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)
 #KM and Nelson Aalen estimators look the same- because large data set? 
@@
 ```{r}
-#at 30,158 seconds (502.6 min, 8.38 hours), 50% of the questions have been answered
-#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)
-#upper limit = largest observation in time to event var
+#to get mean and median
 print(KM.obj, print.rmean=TRUE)
@@
 ```
-
-* interpreting quantiles: 
-* at time = 138 seconds (2.3 min), 1% of the questions have been answered
-*           802 seconds (13.4 min), 10% of the questions have been answered
-*           2,883 seconds (48.1 min), 25% of the questions have been answered
-
-### exploring time_until_answered
-* largest time_until_answered = 89.97 days (obs = 7807), and is censored
-* shortest time_until_answered = 23 seconds (obs = 7485) 
-```{r}
-sum(out1$answered)/length(out1$answered)
-#64.4% of observations are complete
-#35.6% of observations are censored
-
-library(ggplot2)
-ggplot(out1, aes(x = time_until_answer)) + 
-  geom_histogram() + 
-  scale_x_continuous(limits = c(20, 30000))
-```

### 2017-07-13 Hours.Rmd
updating hours

--- 2017-07-08 Hours.Rmd
@@
 7/7/2017 | 4.75 | 11:15-5:00PM | Learned and practiced with functions in the survival package on the data set, came up with descriptive summaries, explored the response variable 
+7/10/2017 | 1 | 9:00-10:00AM | Started learning how to fit parametric distributions in r
+7/10/2017 | 4 | 1:00- 5:00PM | Experimented with calculating MLEs from the data for different parametric distributions, tried to create probability plots to assess the fits for each distribution
+7/10/2017 | 3 | 6:30-9:30PM | Continued working with parametric distributions, experimented with fitdistrplus package to fit parametric distributions
+7/11/2017 | 4.25 | 10:45-3:00PM | Tried to get the probability plots to work, used techniques learned in data camp courses and survival analysis to explore the data set and get an idea of what variables may be important
+7/11/2017 | 3.75 | 6:00-9:45PM | Continued to explore the data set 
+7/12/2017 | 2.33 | 9:40-12:00PM | Survival analysis interpretations
+7/12/2017 | 4.5 | 2:30-7:00PM | Summary statistics + survival curves for variables I haven't looked at yet
+7/12/2017 | 1 | 8:30-9:30PM | More on survival curves, ran into a problem with my code
+7/13/2017 | 3 | 7:40-10:40AM | More data set exploration, reviewed cox regression notes, prepared for meeting
 
->> __Total Hours: 48__
+>> __Total Hours: 79.58__

### 2017-07-13 data_exploration.Rmd
more notes on the data

@@
 
+### exploring data about the users (the people asking the questions)
+* ~80% of users who asked the question were new (member for less than 1 day when the question was posted)
+* continuing users (those who have been a member for longer than 1 day), get their questions answered faster than new users do (had lower mean/median time_until_answer)
+* KM curves showed that continuing users had a consistently lower survival probability 
+* log rank tests: Chisq= 212  on 1 degrees of freedom, p= 0
+
+### looking at the traffic of the questions
+### total_views
+* min total views: 0, max total views: > 23380
+* product categories: Phones, skills, Vehicle, Mac, and Tablet get the highest total views 
+* grouping the data by number of tags shows that including tags leads to more views on the question, which also seems like it leads to shorter answer times (lower mean/median avg_time until answer)
+* for a lot of the questions with 0 total views, it appears that there were a lot of NAs for the category variable (more so than for the questions with a large number of views), a lot of them also don't include any tags
+* maybe don't consider this variable as much as daily_views (because as time passes it's likely it will get more views)
+
+### daily_views
+* max daily_views = 320 (id = 393909, 24 question comments, 7 answer comments, 25 participants (which is also the highest number of participants on any question))
+* just from looking at the data set arranged in decreasing order, seems like most of the questions that have a really high amount of daily views fall into the phone cateogry, majority of the questions contain at least 1 tag, pretty much all are answered (answered variable = 1)
+* Mac, phone, tablet, vehicle have the highest average daily views
+* questions with at least one tag have higher average daily_views than questions with none, and also have a lower avg time_until_answer values
+* questions that were characterized correctly (are not NA in the category variable) have higher average daily_views, and lower avg time_until_response values
+
 ### examining distribution of time_until_answer
-* min = 30 sec, max = 7772000 sec (~90 days) (id = 389776)
+* min = 30 sec, max = 7,772,000 sec (~90 days) (id = 389776)
 * mean = 1281000 sec (~15 days), median = 31650 sec (~8 hours)
@@
 * distributions of time_until_answer for Mac, PC, Phone are extremely skewed right (exactly like the distribution of time_until_answer for all categories)
+* KM curve for survival experiences between product categories shows that: Mac, Phones, and PC have consistently the lowest survival probabilities (get answered quicker)
+* camera's have the highest survival probabilities 
+* skills category has only complete observed times, all less than 35000, so it's probability curve looks like just a line
+* Chisq= 409  on 14 degrees of freedom, p= 0 
+* looking at just whether or not a question was NA in the category variable, questions that were categorized correctly (categorized = 1), had a consistently lower survival curve than those that were not (categorized = 0): Chisq= 206  on 1 degrees of freedom, p= 0
+* questions that were categorized correctly have lower average time_until_answer and higher daily_views (consider this in the model?)
 
@@
 * questions about Mac, PC, and skills (but only contains 5 obs), have the highest proportion of questions that contain "?" 
+* KM curve for survival experiences between questions containing a question mark and questions that don't show that those with a question mark have consistently lower survival probabilities (they get answered faster)
+* chi-square = 72, p-value = 0
+
+### whether or not the text of the question includes "tried" or "searched"
+* this may be an indicator of whether or not the user has done research before asking the question
+* 15% of questions include "tried" or "searched" in the text 
+* looking at the avg time_until_answer grouped by questions with "tried" and questions without show that those with "tried" do tend to have a shorter average, also can see that they have higher average daily views
+* survival curves show that questions that include "tried/searched" in the text seem to have lower survival probabilities than those that do not, but log-rank test show no signifcant difference (p-value = 0.07)
 
@@
 * longest title is 89 characters, shortest is 12 characters
-* seems like questions with longer titles might have shorter average time_until_answer
-* Mac has average title length of 44 characters, average time_until_answer = 453980.6 seconds (which is on the shorter end of values), while those with shorter titles seem to have longer times
+* Doesn't seem to be anything interesting here
+
+### examining device name length
+* just from looking at the dataset, questions that have long device names seem like they tend to create NAs in the category variable
 
@@
 * from histogram of text lengths, a bulk of the questions have text lengths between 20 and 1000 characters long (distribution skewed right)
-* seems like categories with longer median text lengths have shorter time_until_answer values
+* seems like categories with longer avg/median text lengths have shorter time_until_answer values
 
@@
 * seems like there MAY be a slight tendency for questions with more tags to get answers quicker (shorter avg time_until_answer, but also have not as many observations)
+* from KM curve it appears that questions that include 2,3,4 have consistently lower survival probabilities than for the questions that don't include tags, or only include 1 (questions that include 1 tag still have consistently lower survival probabilities than those that don't include any)
+*Chisq= 48.6  on 4 degrees of freedom, p= 7.06e-10
 
@@
 * min = 0, max = 13 (id = 396580)
-* there MAY be some evidence that questions that include images seems to get answers quicker
+* don't see anything here (if looking at the mean time_until_answer grouped by n_images, and mean daily_views)
+* survival curves show that there might be a difference in survival experiences
+* signficant log-rank test:  Chisq= 44.5  on 11 degrees of freedom, p= 0.00000601 
+* after just looking at whether or not a question included any pic, found a signficant difference in survival probabilities (Chisq= 35.6  on 1 degrees of freedom, p= 0.00000000245)
+* only 4.4% of questions include any image
+* those who have at least one question have lower average time_until_answer values, and higher average daily_views
 
@@
 ### KM estimator/curve
-* from the KM curve, the survival probability drops drastically from 1 down to about 0.4 before 400,000 seconds (~5 days).
-After that point, survival curve seems to decrease slowly and remain around 0.3-0.4 (due to the largest times being censored)
-* lowest survival probability is 0.346
+* from the KM curve, the survival probability after a question is immediately posted is equal to 1.
+By ~8000 seconds (~2.2 hours) the survival probability has dropped to about 0.6.
+By ~ 23,000 seconds (~6.4 hours), survival probability is at about 0.5.
+By about 230,000 seconds (~2.7 days, 64 hours).
+After that point, it appears that the survival probability seems to level out at around 0.35-0.4
+* mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)
 
 ### quantiles
-* (median) At 30,158 seconds (8.38 hours), 50% of the questions have been answered
 * at 857 seconds (14.3 min), 10% of the questions have been answered
 * at 3163 seconds (52.7 min), 25% of the questions have been answered
+* (median) At 32,966 seconds (9.16 hours), 50% of the questions have been answered 
+* 95% confidence interval for median: (28844, 38535) or (8.01 hours, 10.7 hours)
 * there is no time for which 75th percentile (since the lowest survival probability = 0.346, and it never reaches 0) (means that we'll never get a total of 75% of questions answered, there will always be some questions that "survive")
 
-### hazard rates
-* instantaneous hazard drops pretty drastically after question is first posted, before 400,000 seconds (~4-5 days), it appears that hazard rate is really close to 0
+### instantaneous hazard rates
+* instantaneous hazard drops pretty drastically after question is first posted
+* By about 400,000 seconds (~4.6 days), it appears that hazard rate is really close to 0
 * looking at the plot, there's a spike in instantaneous hazard around 200,000 seconds (~2.3 days)
-* cumulative hazard rate: increases very quickly until about 400000 seconds (~4-5 days) (indicating that hazard is increasing on that interval), when it starts to even out until it coasts at 1 (indicating that hazard is decreasing
+
+### cumulative hazard rates
+* increases very quickly until about 400000 seconds (~4-5 days) (indicating that hazard is increasing on that interval), when it starts to even out until it coasts at 1 (indicating that hazard is decreasing)
 * do the Nelson Aalen and KM estimators of cumulative hazard look the same becasue the data set is so large?
-
-#at 30,158 seconds (502.6 min, 8.38 hours), 50% of the questions have been answered
-#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)

### 2017-07-13 practice.Rmd
looking at new variables: whether or not at least one image is included, daily_views, new_user...

@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
 ---
@@
 #zoomed in histogram of responses
-ggplot(out1, aes(x = time_until_answer)) + 
+ggplot(out_english, aes(x = time_until_answer)) + 
   geom_histogram() + 
@@
 
-boxplot(out_english$time_until_answer)
-bstats <- boxplot.stats(out_english$time_until_answer)
-bstats
+#changing y axis on the boxplot
+min <- min(out_english$time_until_answer)
+max <- max(out_english$time_until_answer)
+
+boxplot(out_english$time_until_answer, ylab = "Time until answer", yaxt = "n")
+axis(side = 2, at = seq(min, max, by = (max-min)/10), las = 2, cex.axis = 0.5)
+boxplot.stats(out_english$time_until_answer)
 #797 questions lie outside of the whiskers
-```
-
-### exploring the categories 
-```{r}
-table(out_english$category)
-
-#view average time until answered grouped by each category 
-out_english%>%
-  group_by(category) %>%
-  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
-  arrange(avg_time)
-
-#looking at median time_until_answer since data is skewed right
-out_english%>%
-  group_by(category) %>%
-  summarise(median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
-  arrange(median_time)
-
-#looking at time_until_answer distributions according to Mac, PC, Phone, showing whether or not the question contains a question mark
-ggplot(subset(out_english, category %in% c("Mac", "PC", "Phone")), aes(x = time_until_answer, fill = as.factor(contain_questionmark))) +
-  geom_histogram(bins = 10) + 
-  facet_grid(.~category)
-
-#looking at only data for phones category (nothing interesting here)
-phones_only <- out_english %>% filter(category == "Phone")
-ggplot(phones_only, aes(x = title_length, y = time_until_answer)) + 
-  geom_point(size = 3, alpha = 0.5)
 ```
@@
 
+### searching for "tried" and "searched" in text variable
+```{r}
+out_english$tried <- str_detect(as.character(out_english$text), pattern = or("tried", "searched"))
+sum(out_english$tried)/nrow(out_english)
+
+out_english %>%
+  group_by(tried) %>%
+  summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
+  arrange(avg_time)
+
+```
+
+### exploring the categories 
+```{r}
+table(out_english$category)
+
+#view average time until answered grouped by each category 
+out_english%>%
+  group_by(category) %>%
+  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
+  arrange(avg_time)
+
+#looking at median time_until_answer since data is skewed right
+out_english%>%
+  group_by(category) %>%
+  summarise(median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
+  arrange(median_time)
+
+#looking at time_until_answer distributions according to Mac, PC, Phone, showing whether or not the question contains a question mark
+ggplot(subset(out_english, category %in% c("Mac", "PC", "Phone")), aes(x = time_until_answer, fill = as.factor(contain_questionmark))) +
+  geom_histogram(bins = 10) + 
+  facet_grid(.~category)
+
+#looking at only data for phones category (nothing interesting here)
+phones_only <- out_english %>% filter(category == "Phone")
+ggplot(phones_only, aes(x = str_length(title), y = time_until_answer)) + 
+  geom_point(size = 3, alpha = 0.5)
+```
+
 ### exploring title length
@@
   summarise(avg_length = mean(title_length), median_length = median(title_length), avg_time = mean(time_until_answer), n = n()) %>%
-  arrange(avg_length)
+  arrange(avg_time)
 
 #creating title length intervals
-out_english$title_length_intervals <- cut(out_english$title_length, breaks = 8)
-#don't really see anything interesting here 
-out_english %>%
-  group_by(title_length_intervals) %>%
-  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n())
+# out_english$title_length_intervals <- cut(out_english$title_length, breaks = 5)
+# #don't really see anything interesting here 
+# out_english %>%
+#   group_by(title_length_intervals) %>%
+#   summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n())
 
@@
 
-### exploring device length (find another way to classify how detailed device is)
+### exploring device length 
 *observation 7548 has a 136 character string for it's device
@@
 out_english %>%
-  group_by(category, as.factor(n_tags)) %>%
+  group_by(as.factor(n_tags)) %>%
   summarise(avg_time = mean(time_until_answer), n = n()) %>%
-  arrange(category)
+  arrange(avg_time)
 
@@
   group_by(as.factor(n_images)) %>%
-  summarise(avg_time = mean(time_until_answer), n = n()) %>%
+  summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
   arrange(avg_time)
@@
   arrange(category, avg_time)
+
+#looking at whether or not a question included at least one pic
+#creating the variable
+sum(out_english$pic_included)/length(out_english$pic_included)
+
+out_english$pic_included <- 0
+out_english$pic_included[out_english$n_images != 0] <- 1
+
+out_english %>%
+  group_by(as.factor(pic_included)) %>%
+  summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
+  arrange(avg_time)
+
+```
+
+### examining if being a new user makes a difference in time_until_answer
+```{r}
+prop.table(table(as.factor(out_english$new_user)))
+
+#looking at average/median time until answer for new/continuing users
+out_english %>% 
+  group_by(as.factor(new_user)) %>%
+  summarise(avg_time = mean(time_until_answer), median = median(time_until_answer), n = n()) %>%
+  arrange(avg_time)
+
+#viewing histogram for new/continuing users
+ggplot(out_english, aes(x = time_until_answer)) +
+  geom_histogram(bins = 10) + 
+  facet_grid(.~as.factor(new_user))
+```
+
+### examining total views for a question
+```{r}
+summary(out_english$views)
+hist(out_english$views) #very skewed right
+summary(out_english$daily_views)
+
+#looking at avg time_until_answer, avg total view count, and median views grouped by number of tags
+out_english %>% 
+  tbl_df %>%
+  group_by(as.factor(n_tags)) %>%
+  summarise(avg_views = mean(views), median_views = median(views), avg_time = mean(time_until_answer)) %>%
+  arrange(avg_views)
+
+#which product categories get the most views
+out_english %>%
+  tbl_df() %>%
+  group_by(category) %>%
+  summarise(avg_views = mean(views), median_views = median(views), n = n()) %>%
+  arrange(desc(avg_views))
+```
+
+### examining daily_views
+```{r}
+hist(out_english$daily_views)
+summary(out_english$daily_views)
+#determining whcih categories have the most avg daily views 
+out_english %>%
+  tbl_df() %>%
+  group_by(category) %>%
+  summarise(avg_dailyviews = mean(daily_views), median = median(daily_views), n = n()) %>%
+  arrange(desc(avg_dailyviews))
+
+out_english %>% 
+  tbl_df %>%
+  group_by(as.factor(n_tags)) %>%
+  summarise(avg_dailyviews = mean(daily_views), median = median(daily_views), avg_time = mean(time_until_answer), n = n()) %>%
+  arrange(desc(avg_dailyviews))
+
+#indicator variable for whether or not the question was categorized correctly
+out_english$categorized <- 0
+out_english$categorized[!is.na(out_english$category)] <- 1
+out_english %>%
+  tbl_df %>%
+  group_by(as.factor(categorized)) %>%
+  summarise(avg_dailyviews = mean(daily_views), median = median(daily_views), avg_time = mean(time_until_answer), n = n()) %>%
+  arrange(desc(avg_dailyviews))
 ```
@@
 ```{r}
-library(dplyr)
-#working only with the 2000 questions that were answered the fastest
-arranged <- out1_positive %>% arrange(time_until_answer)
-fastest <- arranged[1:2000,]
-
-library(qdap)
-library(tm)
-# INSTALLING RWEKA NOT WORKING
-# library(RWeka)
+# library(dplyr)
+# #working only with the 2000 questions that were answered the fastest
+# arranged <- out_english %>% arrange(time_until_answer)
+# fastest <- arranged[1:2000,]
+# 
+# library(qdap)
+# library(tm)
+# RWEKA NOT INSTALLING!!
+#library(RWeka)
 # 

### 2017-07-13 practice_survivalanalysis.Rmd
compared survival experiences between groups

@@
 library(dplyr)
-out1 <- out %>% 
+out_english <- out %>% 
           tbl_df() %>% 
@@
 #creating survival object
-surv_object <- Surv(out1$time_until_answer, out1$answered, type = "right")
+surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
 ```
@@
 ```{r}
-#KM estimator
-KM.obj <- survfit(surv_object ~ 1, conf.type = "plain")
+#KM estimator based on log-log approach
+KM.obj <- survfit(surv_object ~ 1, conf.type = "log-log")
 str(KM.obj)
@@
 plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xaxt = "n")
-axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE) #adding more detailed x axis
+axis(side = 1, at = seq(min, max, by = (max-min)/15), tick = TRUE, las = 2) #adding more detailed x axis
 #lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
 #lines(cb$time, cb$upper, lty=3, type="s")
+
+#zoomed in to see behavior 
+plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xlim = c(0, 100000), xaxt = "n")
+axis(side = 1, at = seq(min, max, by = (max-min)/1000), tick = TRUE, las = 2)
+
+plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xlim = c(100000, 1000000), xaxt = "n")
+axis(side = 1, at = seq(min, max, by = (max-min)/100), tick = TRUE, las = 2)
 ```
@@
 ### instantaneous hazard using epiR package
+* epi.isthaz function computes instantenous hazard based off of KM survival function
 ```{r}
@@
 h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
+head(h.hat)
+#hazard = 4.3e-6 at time = 30 seconds
+#interpretation: Questions who have not been answered by 30 seconds, are expected to be answered 4.3e-6 times in the next 2 seconds
+
+#par(mfrow = c(1,3))
+#h(t) plots
 plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s", xaxt = "n")
-axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)
+axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE, las = 2)
 
+#zooming in to get a closer look
 plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s", xaxt = "n")
-axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)
+axis(side = 1, at = seq(min, max, by = (max-min)/60), tick = TRUE, las = 2)
 
-#there is a spike in instantaneous hazard before 200,000 seconds (55.5 hours or 2.31 days)
+#there is a spike in instantaneous hazard before 130,000 seconds
+
+plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,130000), type = "s", xaxt = "n")
+axis(side = 1, at = seq(min, max, by = (max-min)/200), tick = TRUE, las = 2)
+
 ```
@@
 #plotting both KM and Nelson Aalen on same graph
+min <- min(out_english$time_until_answer)
+max <- max(out_english$time_until_answer)
+
 plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s", xaxt = "n")
@@
 legend("bottomright", legend=c("H.hat","H.tilde"), lty=1:2)
-axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)
+axis(side = 1, at = seq(from = min, to = max, by = (max-min)/20), tick = TRUE, las = 2)
 #KM and Nelson Aalen estimators look the same- because large data set? 
@@
 #finding percentiles 
-library(survival)
 quantile(KM.obj, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.75))
@@
 ```
+
+### comparing survival experiences between groups
+```{r}
+library(stringr)
+library(rebus)
+
+#comparing survival experiences for questions with/without "?"
+#variable indicating if title contains questionmark 
+out_english$contain_questionmark <- str_detect(out_english$title, pattern = QUESTION)
+options(scipen=5)
+KM_obj_question <- survfit(surv_object~contain_questionmark, data = out_english)
+plot(KM_obj_question, lty = 1:2, xlab = "Time", ylab = "Survival Probability", main = "KM Curves for questions with and without a question mark")
+legend("topright", c("False", "True"), lty = 1:2)
+#for the log-rank test 
+survdiff(surv_object~contain_questionmark, data = out_english)
+
+#comparing survival experiences across product categories
+colors <- c("antiquewhite", "aquamarine", "azure4", "black", "blue", "blue4","burlywood4", "chartreuse", "coral", "cornflowerblue", "darkgoldenrod1", "darkgreen", "darkolivegreen1", "darkorchid", "deeppink")
+KM_obj_category <- survfit(surv_object~category, data = out_english)
+plot(KM_obj_category, col = colors, xlab = "Time", ylab = "Survival Prob", main = "KM Curves by product category")
+legend("topright", levels(out_english$category), col = colors, pch = 21, cex = 0.60)
+survdiff(surv_object~category, data = out_english)
+
+#comparing survival experiences across devices that were categorized correctly and those that were not
+out_english$categorized <- 0
+out_english$categorized[!is.na(out_english$category)] <- 1
+KM_obj_correct <- survfit(surv_object ~ as.factor(categorized), data = out_english)
+plot(KM_obj_correct, lty = 1:2, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for categorized variable")
+legend("topright", c("0", "1"), lty = 1:2)
+survdiff(surv_object~categorized, data = out_english)
+
+#comparing survival experiences for number of tags included
+KM_obj_tags <- survfit(surv_object~as.factor(n_tags), data = out_english)
+plot(KM_obj_tags, col = 1:5, xlab = "Time", ylab = "Survival Prob", main = "KM Curves by number of tags included")
+legend("topright", c("0", "1", "2", "3", "4"), col = 1:5, pch = 21)
+survdiff(surv_object~as.factor(n_tags), data = out_english)
+
+#comparing by title length intervals (no significant difference here)
+#creating title length intervals
+# out_english$title_length_intervals <- cut(as.numeric(out_english$title_length), breaks = 5)
+# KM_obj_title <- survfit(surv_object~as.factor(out_english$title_length_intervals), data = out_english)
+# plot(KM_obj_title, col = 1:5, xlab = "Time", ylab = "Survival Prob", main = "KM Curves by intervals of title length")
+# legend("topright", levels(out_english$title_length_intervals), col = 1:5, pch = 21)
+# survdiff(surv_object~as.factor(title_length_intervals), data = out_english)
+
+#comparing survival between new/continuing users
+KM_obj_users <- survfit(surv_object ~ as.factor(new_user), data = out_english)
+plot(KM_obj_users, lty = 1:2, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for new/continuing users")
+legend("topright", c("Continuing User", "New User"), lty = 1:2)
+survdiff(surv_object~as.factor(new_user), data = out_english)
+
+#comparing survival between number of pictures included
+KM_obj_pic <- survfit(surv_object ~ as.factor(n_images), data = out_english)
+plot(KM_obj_pic, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for n_images", col = colors)
+legend("topright", levels(as.factor(out_english$n_images)), col = colors, pch = 21)
+survdiff(surv_object ~ as.factor(n_images), data = out_english)
+
+#looking at whether or not including at least 1 picture makes a difference
+#creating the variable
+out_english$pic_included <- 0
+out_english$pic_included[out_english$n_images != 0] <- 1
+
+KM_obj_pic1 <- survfit(surv_object ~ as.factor(pic_included), data = out_english)
+plot(KM_obj_pic1, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for n_images", lty = 1:2)
+legend("topright", c("0", "1"), lty = 1:2)
+survdiff(surv_object ~ as.factor(pic_included), data = out_english)
+
+#looking survival experiences between questions with "tried" and without
+out_english$tried <- str_detect(as.character(out_english$text), or("tried", "searched"))
+KM_obj_tried <- survfit(surv_object ~ as.factor(tried), data = out_english)
+plot(KM_obj_tried, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for questions with/without 'tried'", lty = 1:2)
+legend("topright", c("0", "1"), lty = 1:2)
+survdiff(surv_object ~ as.factor(tried), data = out_english)
+```
+
+### practicing with cox regression 
+```{r}
+coxph(formula = surv_object ~ category + contain_questionmark + n_tags + as.factor(new_user) + as.factor(pic_included), data = out_english)
+```

### 2017-07-19 Hours.Rmd
updated hours

--- 2017-07-11 Hours.Rmd
@@
 7/10/2017 | 3 | 6:30-9:30PM | Continued working with parametric distributions, experimented with fitdistrplus package to fit parametric distributions
+7/11/2017 | 4.25 | 10:45-3:00PM | Tried to get the probability plots to work, used techniques learned in data camp courses and survival analysis to explore the data set and get an idea of what variables may be important
+7/11/2017 | 3.75 | 6:00-9:45PM | Continued to explore the data set 
+7/12/2017 | 2.33 | 9:40-12:00PM | Survival analysis interpretations
+7/12/2017 | 4.5 | 2:30-7:00PM | Summary statistics + survival curves for variables I haven't looked at yet
+7/12/2017 | 1 | 8:30-9:30PM | More on survival curves, ran into a problem with my code
+7/13/2017 | 3 | 7:40-10:40AM | More data set exploration, reviewed cox regression notes, prepared for meeting 
+7/13/2017 | 1 | 3:00-4:00PM | Appointment with librarian
+7/17/2017 | 1.5 | 2:00-3:30PM | Experimented with text mining techniques to figure out the 100 most frequently used words, ran into problems with RWeka package
+7/18/2017 | 2 | 8:30-10:30AM | Continued working with text mining techniques
+7/18/2017 | 3 | 1:00-4:00PM | Worked with Anthony on identifying most frequently used terms in answered/unanswered questions
+7/19/2017 | 2 | 9:40-11:40AM | Continued working on frequently used terms
 
->> __Total Hours: 60.75__
+>> __Total Hours: 79.58__

### 2017-07-19 freq_words.Rmd
exploring most frequently used terms in answered/unanswered questions

---
title: "New variables"
author: "Lisa Oshita"
date: "July 14, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### importing the data/setting up variables
```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

out$time_until_answer <- out$first_answer_date - out$post_date
#filling in the NAs
empty <- which(is.na(out$time_until_answer))
for (i in empty) {
  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
}

library(dplyr)
out_english <- out %>% 
                tbl_df() %>% 
                filter(langid == "en")
```

### finding most frequently used terms
```{r}
library(qdap)
library(tm)
#library(RWeka)

#function to clean the corpus
clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
  return(corpus)
}

freq_terms <- function(vec) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus)
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  return(freq)
}

titles_freq <- freq_terms(out_english$title)
head(titles_freq)
#this function changes "turn on" to just "turn", in our case "turn on" might be a significant term? -- do something about this in the function? like do bigrams? (observation 300)

top100 <- titles_freq[1:100]
top50 <- titles_freq[1:50]
top10 <- titles_freq[1:10]
plot(term_freq)
plot(top50)
```

### variable indicating if title contains at least one word in top50 words list
```{r}
library(stringr)
library(rebus)

out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
```

### exploring contain_top10
```{r}
sum(out_english$contain_top10)/nrow(out_english)
#41% of words contain at least one of the top 10 words

library(dplyr)
#not working correctly???
out_english %>%
  group_by(contain_top10) %>%
  summarise(median_time = median(time_until_answer), 
            avg_daily = mean(daily_views)) %>%
  arrange(median_time)

hist(unname(titles_freq))
hist(log(titles_freq))
hist(log(out_english$time_until_answer))

t.test(log(time_until_answer) ~ contain_top10, data = out_english)
```

### survival curves
```{r}
library(survival)

surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")

options(scipen=5)
KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
plot(KM_top10, lty = 1:2, xlab = "Time", ylab = "Survival Probability", main = "KM Curves for questions with and without top 10 terms")
legend("topright", c("False", "True"), lty = 1:2)

survdiff(surv_object~contain_top10, data = out_english)
```

### trying out TfIdf (counts occurrences of words but penalizes for appearing in too many documents) 
```{r}
freq_terms_weighted <- function(vec) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = function(x)
    weightTfIdf(x, normalize = TRUE)))
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  return(freq)
}

titles_freq_weighted <- freq_terms_weighted(out_english$title)
top10_weighted <- term_freq_weighted[1:10]
top10_weighted
top50_weighted <- term_freq_weighted[1:50]

hist(titles_freq_weighted)

#weighting didn't do much
```

### visualizing the frequency of the words

also look at the distribution of how often the appear (plot of 100 words verses percent of posts appeared in) 
top 20 words—might be in 80% of the words
add up words cumulatively? use a cumulative function in r, make own table manually (word number vs percent post appears in , then use cumulative function on that table to create plot) 
```{r}

plot(x = c(1:50), unname(top50)/nrow(out_english), xlab = "Top 10 terms", ylab = "Percentage of posts appeared in", xaxt = "n")
axis(1, at=1:50, labels=names(top50), las = 2)
#screen appears in 12% of questions

#cumulative distribution
cum_percent <- cumsum(unname(top10))
plot(x = c(1:10), cum_percent/nrow(out_english), xlab = "Top 10 Terms", ylab = "Cumulative Percentage of posts appeared in", xaxt = "n")
axis(1, at=1:10, labels=names(top10), las = 2)
# this is "double counting" questions? 
```

* find most frequent terms among answered/unanswered questions
* if any of these terms are present in a question, can use to predict the time_until_answer (think that questions that contain terms in frequent terms list in answered questions might get answered quicker, questions that contain terms in list for unanswered questions might get answered slower)
* noticed that there were shared common words among answered/unanswered questions (ex: screen, phone)
* wanted to find a way to find words unique to answered/unanswered 
* calculating proportion of times that each word in the most freq list occurs in its answered or unanswered category 
* finding the difference in these proportions to see if the word is more likely to be in answered/unanswered category 
*use these difference in proportions to determine which list the term should be included in (answered/unanswered)

```{r}
library(tidyverse) #contains all packages
library(plyr)
answered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 1)
unanswered <- out_english %>%
              tbl_df() %>% 
              filter(answered == 0)

answered_m <- freq_terms(answered$title)
unanswered_m <- freq_terms(unanswered$title)

answered_m[1:100]
unanswered_m[1:100]

str(answered_m)

#proportion of times each term occurs in answered/unanswered questions
answered_freq <- data.frame(term = names(answered_m), a_freq = unname(answered_m), a_prop = unname(answered_m)/length(answered_m))

unanswered_freq <- data.frame(term = names(unanswered_m), u_freq = unname(unanswered_m), u_prop = unname(unanswered_m)/length(unanswered_m))

combined <- join(answered_freq, unanswered_freq, by = "term", match = "all")
head(combined)
dim(combined)
```

```{r}
combined$difference <- abs(combined$a_prop - combined$u_prop)
combined$ratio <- combined$a_prop/combined$u_prop
head(combined)

combined %>%
  arrange(desc(ratio)) %>%
  select(-difference)
# ssd is 28.8 times more likely to appear in answered questions than it is in unanswered questions, only because it appears 40 times in a_freq questions and only once in unanswered 
# need to come up with min and max thresholds for which terms to include freq_words list

combined %>%
  arrange(desc(u_prop))

library(ggthemes)
ggplot(combined, aes(x = u_prop)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,500))

ggplot(combined, aes(x = a_prop)) +
  geom_histogram(bins = 50) + 
  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
  scale_y_continuous(limits = c(0,200)) 
```
* how many words to consider
* minimum/max occurence thresholds (how often show up to be able to use it) 
* create a function that takes in as parameter how many words to consider, and then 
*function to take in vector of text, return frequencies of top words, input = number of words to return 
*ggplot!!!!

### 2017-07-21 Hours.Rmd
updated hours

--- 2017-07-12 Hours.Rmd
@@
 7/11/2017 | 3.75 | 6:00-9:45PM | Continued to explore the data set 
+7/12/2017 | 2.33 | 9:40-12:00PM | Survival analysis interpretations
+7/12/2017 | 4.5 | 2:30-7:00PM | Summary statistics + survival curves for variables I haven't looked at yet
+7/12/2017 | 1 | 8:30-9:30PM | More on survival curves, ran into a problem with my code
+7/13/2017 | 3 | 7:40-10:40AM | More data set exploration, reviewed cox regression notes, prepared for meeting 
+7/13/2017 | 1 | 3:00-4:00PM | Appointment with librarian
+7/17/2017 | 1.5 | 2:00-3:30PM | Experimented with text mining techniques to figure out the 100 most frequently used words, ran into problems with RWeka package
+7/18/2017 | 2 | 8:30-10:30AM | Continued working with text mining techniques
+7/18/2017 | 3 | 1:00-4:00PM | Worked with Anthony on identifying most frequently used terms in answered/unanswered questions
+7/19/2017 | 2 | 9:40-11:40AM | Continued working on frequently used terms
+7/19/2017 | 3.5 | 1:00-4:30PM | Frequently used terms
+7/20/2017 | 3 | 8:00-12:00PM | Worked on plotting survival curves in ggplot + meeting with Dr. Pileggi
+7/20/2017 | 5.5 | 2:00-7:30PM | Frequently used terms, started on literature review, started trying to reorganize summary statistics report
 
->> __Total Hours: 68.75__
+>> __Total Hours: 89.08__

### 2017-07-21 freq_words.Rmd
reorganized, converted graphs to ggsurvplot, looked at survival curves based on only terms related to devices within frequently used terms in unanswered/answered questions

@@
 
-### importing the data/setting up variables
+### Importing the data/Setting up time to event variable
 ```{r}
@@
 out <- read.csv(file.path(dir, "answers_data.csv"))
-
-out$time_until_answer <- out$first_answer_date - out$post_date
-#filling in the NAs
-empty <- which(is.na(out$time_until_answer))
-for (i in empty) {
-  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
-}
 
@@
                 filter(langid == "en")
+
+out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
+empty <- which(is.na(out_english$time_until_answer))
+for (i in empty) {
+  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
+}
+
 ```
 
-### finding most frequently used terms
+### Finding most frequently used terms
 ```{r}
+
 library(qdap)
 library(tm)
-#library(RWeka)
 
-#function to clean the corpus
+#function to clean corpus
 clean_corpus <- function(corpus){
@@
 
+#function that returns vector of terms sorted from most to least frequent
 freq_terms <- function(vec) {
@@
 head(titles_freq)
-#this function changes "turn on" to just "turn", in our case "turn on" might be a significant term? -- do something about this in the function? like do bigrams? (observation 300)
+hist(titles_freq)
+hist(log(titles_freq))
 
-top100 <- titles_freq[1:100]
 top50 <- titles_freq[1:50]
 top10 <- titles_freq[1:10]
-plot(term_freq)
 plot(top50)
+
 ```
 
-### variable indicating if title contains at least one word in top50 words list
+### Variable indicating if title contains at least one word in top50 most frequent
+* no significant difference between questions containing these words and questions that don't
 ```{r}
+
 library(stringr)
@@
 out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
-```
 
-### exploring contain_top10
-```{r}
 sum(out_english$contain_top10)/nrow(out_english)
-#41% of words contain at least one of the top 10 words
 
-library(dplyr)
-#not working correctly???
 out_english %>%
@@
   summarise(median_time = median(time_until_answer), 
-            avg_daily = mean(daily_views)) %>%
+            avg_daily = mean(daily_views), n = n()) %>%
   arrange(median_time)
 
-hist(unname(titles_freq))
-hist(log(titles_freq))
-hist(log(out_english$time_until_answer))
-
-t.test(log(time_until_answer) ~ contain_top10, data = out_english)
 ```
 
-### survival curves
+### Survival curves for questions with/without top10 terms
 ```{r}
+
 library(survival) 
+library(survminer)
 
 surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
+KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
 
-options(scipen=5)
-KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
-plot(KM_top10, lty = 1:2, xlab = "Time", ylab = "Survival Probability", main = "KM Curves for questions with and without top 10 terms")
-legend("topright", c("False", "True"), lty = 1:2)
+ggsurvplot(KM_top10, data = out_english, risk.table = TRUE, pval = TRUE)
 
 survdiff(surv_object~contain_top10, data = out_english)
+
 ```
 
-### trying out TfIdf (counts occurrences of words but penalizes for appearing in too many documents) 
+### Trying out TfIdf (no difference)
 ```{r}
+
 freq_terms_weighted <- function(vec) {
@@
 
-titles_freq_weighted <- freq_terms_weighted(out_english$title)
-top10_weighted <- term_freq_weighted[1:10]
-top10_weighted
-top50_weighted <- term_freq_weighted[1:50]
+titles_weighted <- freq_terms_weighted(out_english$title)
+titles_freq_weighted[1:10]
 
@@
 
-#weighting didn't do much
 ```
 
-### visualizing the frequency of the words
-
-also look at the distribution of how often the appear (plot of 100 words verses percent of posts appeared in) 
-top 20 words—might be in 80% of the words
-add up words cumulatively? use a cumulative function in r, make own table manually (word number vs percent post appears in , then use cumulative function on that table to create plot) 
+### Visualizing word frequency 
+* Distribution of how often words appear (plot of top 100 most frequently used words vs. percent of posts appeared in) 
 ```{r}
@@
 axis(1, at=1:50, labels=names(top50), las = 2)
-#screen appears in 12% of questions
 
-#cumulative distribution
-cum_percent <- cumsum(unname(top10))
-plot(x = c(1:10), cum_percent/nrow(out_english), xlab = "Top 10 Terms", ylab = "Cumulative Percentage of posts appeared in", xaxt = "n")
-axis(1, at=1:10, labels=names(top10), las = 2)
-# this is "double counting" questions? 
 ```
 
-* find most frequent terms among answered/unanswered questions
-* if any of these terms are present in a question, can use to predict the time_until_answer (think that questions that contain terms in frequent terms list in answered questions might get answered quicker, questions that contain terms in list for unanswered questions might get answered slower)
-* noticed that there were shared common words among answered/unanswered questions (ex: screen, phone)
-* wanted to find a way to find words unique to answered/unanswered 
-* calculating proportion of times that each word in the most freq list occurs in its answered or unanswered category 
-* finding the difference in these proportions to see if the word is more likely to be in answered/unanswered category 
-*use these difference in proportions to determine which list the term should be included in (answered/unanswered)
+### Most frequent words within answered/unanswered questions
+```{r}
 
-```{r}
-library(tidyverse) #contains all packages
-library(plyr)
+library(tidyverse)
+
 answered <- out_english %>%
@@
 
-answered_m <- freq_terms(answered$title)
-unanswered_m <- freq_terms(unanswered$title)
+terms_a <- freq_terms(answered$title)
+terms_u <- freq_terms(unanswered$title)
 
-answered_m[1:100]
-unanswered_m[1:100]
+ans <- data.frame(term = names(terms_a), a_freq = unname(terms_a), a_prop = unname(terms_a) / length(terms_a))
+unans <- data.frame(term = names(terms_u), u_freq = unname(terms_u), u_prop = unname(terms_u) / length(terms_u))
 
-str(answered_m)
-
-#proportion of times each term occurs in answered/unanswered questions
-answered_freq <- data.frame(term = names(answered_m), a_freq = unname(answered_m), a_prop = unname(answered_m)/length(answered_m))
-
-unanswered_freq <- data.frame(term = names(unanswered_m), u_freq = unname(unanswered_m), u_prop = unname(unanswered_m)/length(unanswered_m))
-
-combined <- join(answered_freq, unanswered_freq, by = "term", match = "all")
-head(combined)
-dim(combined)
-```
-
-```{r}
-combined$difference <- abs(combined$a_prop - combined$u_prop)
-combined$ratio <- combined$a_prop/combined$u_prop
+combined <- full_join(ans, unans, by = "term")
+combined$ratio <- combined$a_prop / combined$u_prop
 head(combined)
 
+#interpretation: ssd is 28.8 times more likely to show up in answered questions than it is in unanswered questions (but it only shows up .7% of the time in answered questions, and .02% of the time in unanswered questions- probably not helpful)
 combined %>% 
-  arrange(desc(ratio)) %>%
-  select(-difference)
-# ssd is 28.8 times more likely to appear in answered questions than it is in unanswered questions, only because it appears 40 times in a_freq questions and only once in unanswered 
-# need to come up with min and max thresholds for which terms to include freq_words list
+  arrange(desc(ratio))
 
@@
 
-library(ggthemes)
+ggplot(combined, aes(x = a_prop)) +
+  geom_histogram(bins = 50) + 
+  scale_x_continuous("Proportion in answered questions",limits = c(0, 0.05), labels = scales::percent) + 
+  scale_y_continuous(limits = c(0,200))
+
 ggplot(combined, aes(x = u_prop)) +
   geom_histogram(bins = 50) + 
-  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
-  scale_y_continuous(limits = c(0,500))
+  scale_x_continuous("Proportion in unanswered questions", limits = c(0, 0.05), labels = scales::percent) + 
+  scale_y_continuous(limits = c(0,200))
 
-ggplot(combined, aes(x = a_prop)) +
-  geom_histogram(bins = 50) + 
-  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
-  scale_y_continuous(limits = c(0,200)) 
 ```
-* how many words to consider
-* minimum/max occurence thresholds (how often show up to be able to use it) 
-* create a function that takes in as parameter how many words to consider, and then 
-*function to take in vector of text, return frequencies of top words, input = number of words to return 
-*ggplot!!!!
+
+### Finding proportion and ratio thresholds 
+* find a set of words that show up frequently enough to be used as a set of predictors
+* want the ratio to be large enough to allow us to decide whether or not that word is more likely to show up in an answered/unanswered question
+```{r}
+
+#unanswered questions
+
+p_threshold <- 0.01
+ratio_threshold <- 1
+
+freq_terms_u <- combined %>%
+                  filter(u_prop > p_threshold) %>%
+                  filter(ratio < ratio_threshold)
+freq_terms_u
+
+#answered questions
+
+freq_terms_a <- combined %>%
+                  filter(a_prop > p_threshold) %>%
+                  filter(ratio > ratio_threshold)
+freq_terms_a
+
+```
+
+### Means/medians/survival curves for freq_terms_u
+```{r}
+
+out_english$contain_u <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_u$term))
+
+sum(out_english$contain_u)/nrow(out_english) #only 13% of questions contain these terms
+
+out_english %>%
+  group_by(contain_u) %>%
+  summarise(median_time = median(time_until_answer), avg_time = mean(time_until_answer), n = n(), avg_views = 
+              mean(daily_views)) %>%
+  arrange(median_time)
+
+KM_u <- survfit(surv_object ~ contain_u, data = out_english) 
+survdiff(surv_object ~ contain_u, data = out_english)
+
+ggsurvplot(KM_u, data = out_english, risk.table = TRUE, pval = TRUE)
+
+```
+
+### Means/medians/survival curves for freq_terms_a
+```{r}
+out_english$contain_a <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_a$term))
+
+sum(out_english$contain_a)/nrow(out_english) #63% of the questions contain these terms
+
+out_english %>%
+  group_by(contain_a) %>%
+  summarise(median_time = median(time_until_answer), avg_time = mean(time_until_answer), n = n(), avg_views = 
+              mean(daily_views)) %>%
+  arrange(median_time)
+
+KM_a <- survfit(surv_object ~ contain_freq_answered, data = out_english)
+survdiff(surv_object~contain_freq_answered, data = out_english)
+
+ggsurvplot(KM_a, data = out_english, risk.table = TRUE, pval = TRUE)
+
+```
+
+### Looking at only device terms within freq_terms_u
+```{r}
+
+unanswered_devices <- freq_terms_u %>%
+                        filter(term %in% c("camera", "sound", "tablet", "light", "wifi", "speaker", "sound"))
+
+out_english$contain_u_dev <- str_detect(as.character(out_english$title), pattern = or1(unanswered_devices$term))
+
+sum(out_english$contain_u_dev)/nrow(out_english) #only 5.6% of titles contain these terms
+
+KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = out_english)
+
+survdiff(surv_object ~ contain_u_dev, data = out_english)
+
+ggsurvplot(KM_u_dev, data = out_english, risk.table = TRUE, pval = TRUE)
+
+```
+
+### Looking at only device terms within freq_terms_a
+```{r}
+
+freq_terms_a
+
+answered_devices <- freq_terms_answered %>%
+                      filter(term %in% c("screen", "iphone", "phone", "battery", "button", "display", "macbook", "lcd",
+                                         "board", "keyboard", "laptop", "home", "pro", "drive"))
+
+out_english$contain_dev_a <- str_detect(as.character(out_english$title), pattern = or1(answered_devices$term))
+sum(out_english$contain_dev_a)/nrow(out_english) #33% of all questions contain these words
+
+KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = out_english)
+
+survdiff(surv_object ~ contain_dev_a, data = out_english)
+
+ggsurvplot(KM_dev_a, data = out_english, risk.table = TRUE, pval = TRUE)
+
+```
+
+### Function to return top n most frequently used words from a character vector
+```{r}
+
+n_freq_terms <- function(vector, n) {
+  source <- VectorSource(vector)
+  corp <- VCorpus(source)
+  cleaned <- clean_corpus(corp) 
+  dtm <- DocumentTermMatrix(cleaned)
+  m <- as.matrix(dtm) 
+  frequency <- colSums(m)
+  frequency <- sort(frequency, decreasing = TRUE)
+  terms <- frequency[1:n]
+}
+
+#testing
+answered <- out_english %>%
+              tbl_df() %>% 
+              filter(answered == 1)
+n_freq_terms(answered$title, 10)
+
+```
+
+### Plotting KM objects with ggplot
+*convert survfit object to data frame with fortify function, plot with ggplot()
+```{r}
+
+library(ggfortify)
+
+plot_surv <- function(survfit, data) {
+
+  df <- fortify(survfit, data = data)
+
+  if (!("strata" %in% names(df))) {
+    ggplot(df, aes(x = time, y = surv)) + 
+    geom_line() + 
+    ggtitle("Survival Curve")
+  }
+
+  if ("strata" %in% names(df)) {
+    ggplot(df, aes(x = time, y = surv, color = strata)) + 
+      geom_line() + 
+      ggtitle("Survival Curves")
+  }
+}
+
+plot_surv(KM_top10, data = out_english)
+
+```

### 2017-07-21 practice.Rmd
started making the code more reproducible

@@
 ---
+#### Importing the data/Setting up time to event variable
 ```{r}
+
 dir <- file.path(getwd(),"data")
 out <- read.csv(file.path(dir, "answers_data.csv"))
-```
 
-### Creating time to event variable
-censoring indicator variable: answered
-```{r}
-out$time_until_answer <- out$first_answer_date - out$post_date
-#filling in the NAs
-empty <- which(is.na(out$time_until_answer))
-for (i in empty) {
-  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
-}
-
-#subsetting to include only questions in english
 library(dplyr)
@@
                 filter(langid == "en")
+
+out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
+empty <- which(is.na(out_english$time_until_answer))
+for (i in empty) {
+  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
+}
+
+proportion_answered <- sum(out_english$answered)/nrow(out_english)
 ```
 
-### exploring time to event variable
+#### About the data set
+* `r nrow(out_english)` observations
+* `r proportion_answered * 100` % of questions were answered
+
+#### time until answer 
+* minimum: `r summary[1]` hrs
+* maximum: `r summary[6]` hrs
+* mean: `r summary[4]` hrs
+* median: `r summary[3]` hrs
+* first quartile: `r summary[2]`hrs
+    + 25% of the questions were answered by `r summary[2]` hrs
+* third quartile: `r summary[5]` hrs
+    + 75% of the questions were answered by `r summary[5]` hrs
+* IQR range: `r summary[5] - summary[2]` hrs
+
 ```{r}
-summary(out_english$time_until_answer)
+summary <- summary(out_english$time_until_answer)
 
@@
 
-#defining tick marks for x-axis
-min <- min(out_english$time_until_answer)
-max <- max(out_english$time_until_answer)
-
-require(scales)
 ggplot(out_english, aes(x = time_until_answer)) + 
   geom_histogram(bins = 10) + 
-  scale_x_continuous(labels = comma, breaks = seq(min, max, by = (max-min)/10)) + 
-  theme(axis.text.x = element_text(angle=90, hjust=1))
-
-#zoomed in histogram of responses
-ggplot(out_english, aes(x = time_until_answer)) + 
-  geom_histogram() + 
-  scale_x_continuous(limits = c(20, 30000))
-
-#changing y axis on the boxplot
-min <- min(out_english$time_until_answer)
-max <- max(out_english$time_until_answer)
-
-boxplot(out_english$time_until_answer, ylab = "Time until answer", yaxt = "n")
-axis(side = 2, at = seq(min, max, by = (max-min)/10), las = 2, cex.axis = 0.5)
-boxplot.stats(out_english$time_until_answer)
-#797 questions lie outside of the whiskers
+  scale_x_continuous("Time (hours)", labels = comma) 
 ```
@@
   group_by(category) %>%
-  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
+  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
   arrange(avg_time)
-
-#looking at median time_until_answer since data is skewed right
-out_english%>%
-  group_by(category) %>%
-  summarise(median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
-  arrange(median_time)
 
@@
   group_by(category) %>%
-  summarise(avg = mean(text_length), median = median(text_length), avg_time = mean(time_until_answer), n = n()) %>%
-  arrange(avg_time)
+  summarise(avg = mean(text_length), median = median(text_length), median_time = median(time_until_answer), n = n()) %>%
+  arrange(median_time)
 ```
@@
 ```{r}
-summary(out_english$n_images)
-hist(out_english$n_images)
-table(out_english$n_images)
-
-#proportion of questions that include any images
-sum(out_english$n_images != 0)/nrow(out_english)
-
-#looking at mean time_until_answer grouped by n_images
-out_english %>% 
-  group_by(as.factor(n_images)) %>%
-  summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
-  arrange(avg_time)
-
-#looking at mean time_until_answer grouped by categories and n_images
-out_english %>%
-  group_by(category, as.factor(n_images)) %>%
-  summarise(avg_time = mean(time_until_answer), median = median(time_until_answer), n = n()) %>%
-  arrange(category, avg_time)
-
-#looking at whether or not a question included at least one pic
-#creating the variable
-sum(out_english$pic_included)/length(out_english$pic_included)
-
-out_english$pic_included <- 0
-out_english$pic_included[out_english$n_images != 0] <- 1
-
-out_english %>%
-  group_by(as.factor(pic_included)) %>%
-  summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
-  arrange(avg_time)
+# summary(out_english$n_images)
+# hist(out_english$n_images)
+# table(out_english$n_images)
+# 
+# #proportion of questions that include any images
+# sum(out_english$n_images != 0)/nrow(out_english)
+# 
+# #looking at mean time_until_answer grouped by n_images
+# out_english %>% 
+#   group_by(as.factor(n_images)) %>%
+#   summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
+#   arrange(avg_time)
+# 
+# #looking at mean time_until_answer grouped by categories and n_images
+# out_english %>%
+#   group_by(category, as.factor(n_images)) %>%
+#   summarise(avg_time = mean(time_until_answer), median = median(time_until_answer), n = n()) %>%
+#   arrange(category, avg_time)
+# 
+# #looking at whether or not a question included at least one pic
+# #creating the variable
+# sum(out_english$pic_included)/length(out_english$pic_included)
+# 
+# out_english$pic_included <- 0
+# out_english$pic_included[out_english$n_images != 0] <- 1
+# 
+# out_english %>%
+#   group_by(as.factor(pic_included)) %>%
+#   summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
+#   arrange(avg_time)
 
@@
 #indicator variable for whether or not the question was categorized correctly
-out_english$categorized <- 0
-out_english$categorized[!is.na(out_english$category)] <- 1
-out_english %>%
-  tbl_df %>%
-  group_by(as.factor(categorized)) %>%
-  summarise(avg_dailyviews = mean(daily_views), median = median(daily_views), avg_time = mean(time_until_answer), n = n()) %>%
-  arrange(desc(avg_dailyviews))
+# out_english$categorized <- 0
+# out_english$categorized[!is.na(out_english$category)] <- 1
+# out_english %>%
+#   tbl_df %>%
+#   group_by(as.factor(categorized)) %>%
+#   summarise(avg_dailyviews = mean(daily_views), median = median(daily_views), avg_time = mean(time_until_answer), n = n()) %>%
+#   arrange(desc(avg_dailyviews))
 ```

### 2017-07-22 freq_words.Rmd
reorganized files and code, made code more reproducible, updated hours, deleted files

--- 2017-07-19 freq_words.Rmd
@@
 ---
-title: "New variables"
-author: "Lisa Oshita"
-date: "July 14, 2017"
+title: "Frequent Words"
 output: html_document
@@
 
-### importing the data/setting up variables
-```{r}
+* **Idea: there are words that show up frequently among answered questions and unanswered questions, which might be able to be used as predictors in the model**
+
+```{r, include = FALSE}
 dir <- file.path(getwd(),"data")
 out <- read.csv(file.path(dir, "answers_data.csv"))
-
-out$time_until_answer <- out$first_answer_date - out$post_date
-#filling in the NAs
-empty <- which(is.na(out$time_until_answer))
-for (i in empty) {
-  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
-}
 
@@
                 filter(langid == "en")
+
+out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
+empty <- which(is.na(out_english$time_until_answer))
+for (i in empty) {
+  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
+}
+
+library(stringr)
+library(rebus)
+library(survival) 
+library(survminer)
+library(tidyverse)
 ```
 
-### finding most frequently used terms
-```{r}
+```{r, include = FALSE}
 library(qdap)
 library(tm)
-#library(RWeka)
 
-#function to clean the corpus
+#function to clean corpus
 clean_corpus <- function(corpus){
+  library(tm)
   corpus <- tm_map(corpus, stripWhitespace)
@@
 
-freq_terms <- function(vec) {
+#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n is an optional argument 
+freq_terms <- function(vec, n = NULL) {
+  library(qdap)
+  library(tm)
   source <- VectorSource(vec)
@@
   freq <- sort(freq, decreasing = TRUE)
-  return(freq)
+  freq_df <- data.frame(word = names(freq), frequency = unname(freq))
+
+  if (is.null(n)) {
+    return(freq_df)
+  }
+  else if (!is.null(n)) {
+    return(freq_df[1:n,])
+  }
 }
 
-titles_freq <- freq_terms(out_english$title)
-head(titles_freq)
-#this function changes "turn on" to just "turn", in our case "turn on" might be a significant term? -- do something about this in the function? like do bigrams? (observation 300)
+#function to plot survival curves with ggplot
+plot_surv <- function(survfit, data, ...) {
+  library(ggfortify)
+  library(directlabels)
 
-top100 <- titles_freq[1:100]
-top50 <- titles_freq[1:50]
-top10 <- titles_freq[1:10]
-plot(term_freq)
-plot(top50)
+  df <- fortify(survfit, data = data)
+
+  if (!("strata" %in% names(df))) {
+    ggplot(df, aes(x = time, y = surv)) + 
+    geom_line() + 
+    scale_y_continuous("Survival Probability") +
+    scale_x_continuous("Time")
+    ggtitle("Survival Curve")
+  }
+
+  if ("strata" %in% names(df)) {
+    ggplot(df, aes(x = time, y = surv, color = strata)) + 
+      geom_line() + 
+      scale_y_continuous("Survival Probabilities") +
+      scale_x_continuous("Time") + 
+      ggtitle("Survival Curves") + 
+      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+  }
+}
 ```
 
-### variable indicating if title contains at least one word in top50 words list
-```{r}
-library(stringr)
-library(rebus)
+### finding top10 and top50 most frequently used terms in titles
 
-out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
+```{r, echo = FALSE}
+titles_freq <- freq_terms(out_english$title)
+
+ggplot(titles_freq, aes(x = frequency)) + 
+  geom_histogram() + 
+  ggtitle("Distribution of word frequencies")
 ```
 
-### exploring contain_top10
-```{r}
-sum(out_english$contain_top10)/nrow(out_english)
-#41% of words contain at least one of the top 10 words
+```{r, echo = FALSE}
+top50 <- titles_freq[1:50,]
+top50$word <- factor(top50$word, levels = top50$word)
 
-library(dplyr)
-#not working correctly???
+ggplot(top50, aes(x = word, y = frequency/nrow(out_english))) + 
+  geom_point() +
+  scale_y_continuous("Percentage of times the word appears", labels = scales::percent) + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
+  ggtitle("How often the 50 most frequently used words appear")
+```
+
+##### top10 most frequently used words
+
+```{r, echo = FALSE}
+top10 <- titles_freq[1:10,]
+out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
+prop_contain <- sum(out_english$contain_top10)/nrow(out_english)
+```
+
+* `r round(prop_contain * 100, 2)`% of questions contain at least 1 of the top 10 most frequent words in the title
+
+```{r, echo = FALSE}
+top10
+```
+
+##### median time and average daily views grouped by whether or not question contains top10
+
+```{r, echo = FALSE}
 out_english %>%
@@
   summarise(median_time = median(time_until_answer), 
-            avg_daily = mean(daily_views)) %>%
+            avg_daily = mean(daily_views), n = n()) %>%
   arrange(median_time)
-
-hist(unname(titles_freq))
-hist(log(titles_freq))
-hist(log(out_english$time_until_answer))
-
-t.test(log(time_until_answer) ~ contain_top10, data = out_english)
 ```
 
-### survival curves
-```{r}
-library(survival)
+* table indicates that questions with titles that don't contain the top10 words may get answered faster
 
+##### log-rank test
+
+```{r, echo = FALSE}
 surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
-
-options(scipen=5)
-KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
-plot(KM_top10, lty = 1:2, xlab = "Time", ylab = "Survival Probability", main = "KM Curves for questions with and without top 10 terms")
-legend("topright", c("False", "True"), lty = 1:2)
-
 survdiff(surv_object~contain_top10, data = out_english)
@@
 
-### trying out TfIdf (counts occurrences of words but penalizes for appearing in too many documents) 
-```{r}
-freq_terms_weighted <- function(vec) {
-  source <- VectorSource(vec)
-  corpus <- VCorpus(source)
-  cleaned_corpus <- clean_corpus(corpus) 
-  dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = function(x)
-    weightTfIdf(x, normalize = TRUE)))
-  m <- as.matrix(dtm) 
-  freq <- colSums(m)
-  freq <- sort(freq, decreasing = TRUE)
-  return(freq)
-}
-
-titles_freq_weighted <- freq_terms_weighted(out_english$title)
-top10_weighted <- term_freq_weighted[1:10]
-top10_weighted
-top50_weighted <- term_freq_weighted[1:50]
-
-hist(titles_freq_weighted)
-
-#weighting didn't do much
+```{r, echo = FALSE}
+surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
+KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
+plot_surv(KM_top10, data = out_english)
 ```
 
-### visualizing the frequency of the words
+### Most frequent words within answered and unanswered questions
 
-also look at the distribution of how often the appear (plot of 100 words verses percent of posts appeared in) 
-top 20 words—might be in 80% of the words
-add up words cumulatively? use a cumulative function in r, make own table manually (word number vs percent post appears in , then use cumulative function on that table to create plot) 
-```{r}
-
-plot(x = c(1:50), unname(top50)/nrow(out_english), xlab = "Top 10 terms", ylab = "Percentage of posts appeared in", xaxt = "n")
-axis(1, at=1:50, labels=names(top50), las = 2)
-#screen appears in 12% of questions
-
-#cumulative distribution
-cum_percent <- cumsum(unname(top10))
-plot(x = c(1:10), cum_percent/nrow(out_english), xlab = "Top 10 Terms", ylab = "Cumulative Percentage of posts appeared in", xaxt = "n")
-axis(1, at=1:10, labels=names(top10), las = 2)
-# this is "double counting" questions? 
-```
-
-* find most frequent terms among answered/unanswered questions
-* if any of these terms are present in a question, can use to predict the time_until_answer (think that questions that contain terms in frequent terms list in answered questions might get answered quicker, questions that contain terms in list for unanswered questions might get answered slower)
-* noticed that there were shared common words among answered/unanswered questions (ex: screen, phone)
-* wanted to find a way to find words unique to answered/unanswered 
-* calculating proportion of times that each word in the most freq list occurs in its answered or unanswered category 
-* finding the difference in these proportions to see if the word is more likely to be in answered/unanswered category 
-*use these difference in proportions to determine which list the term should be included in (answered/unanswered)
-
-```{r}
-library(tidyverse) #contains all packages
-library(plyr)
+```{r, echo = FALSE}
 answered <- out_english %>%
@@
 
-answered_m <- freq_terms(answered$title)
-unanswered_m <- freq_terms(unanswered$title)
+terms_a <- freq_terms(answered$title)
+terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
+colnames(terms_a)[2] <- "frequency_a"
 
-answered_m[1:100]
-unanswered_m[1:100]
+terms_u <- freq_terms(unanswered$title)
+terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
+colnames(terms_u)[2] <- "frequency_u"
 
-str(answered_m)
-
-#proportion of times each term occurs in answered/unanswered questions
-answered_freq <- data.frame(term = names(answered_m), a_freq = unname(answered_m), a_prop = unname(answered_m)/length(answered_m))
-
-unanswered_freq <- data.frame(term = names(unanswered_m), u_freq = unname(unanswered_m), u_prop = unname(unanswered_m)/length(unanswered_m))
-
-combined <- join(answered_freq, unanswered_freq, by = "term", match = "all")
+combined <- full_join(terms_a, terms_u, by = "word")
+combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
 head(combined)
-dim(combined)
 ```
 
-```{r}
-combined$difference <- abs(combined$a_prop - combined$u_prop)
-combined$ratio <- combined$a_prop/combined$u_prop
-head(combined)
+* data frame with frequency and proportion of times each word appears in both answered and unanswered questions, along with the ratio of proportion of times a word appears in answered questions to the proportion of times it appears in unanswered questions (ratio = prop_in_answered/prop_in_unanswered)
 
-combined %>%
-  arrange(desc(ratio)) %>%
-  select(-difference)
-# ssd is 28.8 times more likely to appear in answered questions than it is in unanswered questions, only because it appears 40 times in a_freq questions and only once in unanswered 
-# need to come up with min and max thresholds for which terms to include freq_words list
+##### viewing proportions/frequencies arranged by ratio in decreasing order
 
-combined %>%
-  arrange(desc(u_prop))
+* interpretation: "ssd" is 28.8 times more likely to show up in answered questions than it is in unanswered questions.
+But since it only shows up 0.7% of the time in answered questions, and 0.02% of the time in unanswered questions, this term might not be helpful in telling us whether or not a question is likely to be answered.
 
-library(ggthemes)
-ggplot(combined, aes(x = u_prop)) +
+```{r, echo = FALSE}
+head(combined %>% 
+  arrange(desc(ratio)))
+```
+
+##### viewing proportions/frequencies arranged by proportion in unanswered questions, decreasing order 
+```{r, echo = FALSE}
+head(combined %>%
+  arrange(desc(prop_in_unanswered)))
+```
+
+```{r, echo = FALSE}
+ggplot(combined, aes(x = prop_in_answered)) +
   geom_histogram(bins = 50) + 
-  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
-  scale_y_continuous(limits = c(0,500))
+  scale_x_continuous("Proportion in answered questions",limits = c(0, 0.05), labels = scales::percent) + 
+  scale_y_continuous(limits = c(0,200)) + 
+  ggtitle("Distribution of proportions in answered questions")
+```
 
-ggplot(combined, aes(x = a_prop)) +
+```{r, echo = FALSE}
+ggplot(combined, aes(x = prop_in_unanswered)) +
   geom_histogram(bins = 50) + 
-  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
-  scale_y_continuous(limits = c(0,200)) 
+  scale_x_continuous("Proportion in unanswered questions", limits = c(0, 0.05), labels = scales::percent) + 
+  scale_y_continuous(limits = c(0,200)) + 
+  ggtitle("Distribution of proportions in unanswered questions")
 ```
-* how many words to consider
-* minimum/max occurence thresholds (how often show up to be able to use it) 
-* create a function that takes in as parameter how many words to consider, and then 
-*function to take in vector of text, return frequencies of top words, input = number of words to return 
-*ggplot!!!!
+
+##### finding proportion and ratio thresholds
+
+* find a set of words that show up frequently enough to be used as a set of predictors
+* want the ratio to be large (or small) enough to allow us to decide whether or not that word is more likely to show up in an answered/unanswered question
+
+###### words that appear more than 1% of the time in unanswered questions and are more likely (ratio < 1) to be used in unanswered questions
+```{r, echo = FALSE}
+p_threshold <- 0.01
+ratio_threshold <- 1
+
+freq_terms_u <- combined %>%
+                  filter(prop_in_unanswered > p_threshold) %>%
+                  filter(ratio < ratio_threshold)
+freq_terms_u
+```
+
+###### words that appear more than 1% of the time in answered questions and are more likely (ratio > 1) to be used in answered questions
+
+```{r, echo = FALSE}
+freq_terms_a <- combined %>%
+                  filter(prop_in_answered > p_threshold) %>%
+                  filter(ratio > ratio_threshold)
+freq_terms_a
+```
+
+### Summary statistics/survival analysis for whether or not questions contain frequent unanswered terms
+
+```{r, echo = FALSE}
+out_english$contain_u <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_u$word))
+
+prop_contain_u <- sum(out_english$contain_u)/nrow(out_english)
+```
+
+* `r round(prop_contain_u * 100, 2)`% of questions contain at least one of the most frequent unanswered terms
+
+##### median answer time and average daily views grouped by whether or not question contains at least 1 uanswered term
+
+```{r, echo = FALSE}
+out_english %>%
+  group_by(contain_u) %>%
+  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
+  arrange(median_time)
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ contain_u, data = out_english)
+```
+
+```{r, echo = FALSE}
+KM_u <- survfit(surv_object ~ contain_u, data = out_english) 
+plot_surv(KM_u, data = out_english)
+```
+
+### Summary statistics/survival analysis for whether or not questions contain frequent answered terms
+
+```{r, echo = FALSE}
+out_english$contain_a <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_a$word))
+
+prop_contain_a <- sum(out_english$contain_a)/nrow(out_english)
+```
+
+* `r round(prop_contain_a * 100, 2)`% of questions contain at least one of the most frequent answered terms
+
+##### median answer time and average daily views grouped by whether or not question contains at least 1 answered term
+
+```{r, echo = FALSE}
+out_english %>%
+  group_by(contain_a) %>%
+  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
+  arrange(median_time)
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_object~contain_a, data = out_english)
+```
+
+```{r, echo = FALSE}
+KM_a <- survfit(surv_object ~ contain_a, data = out_english)
+plot_surv(KM_a, data = out_english)
+```
+
+#### looking at only device terms within freq_terms_u (discarding irrelevant words)
+```{r, echo = FALSE}
+unanswered_devices <- freq_terms_u %>%
+                        filter(word %in% c("camera", "sound", "tablet", "light", "wifi", "speaker", "sound"))
+
+out_english$contain_u_dev <- str_detect(as.character(out_english$title), pattern = or1(unanswered_devices$word))
+
+prop_contain_u_dev <- sum(out_english$contain_u_dev)/nrow(out_english)
+```
+
+* `r round(prop_contain_u_dev*100, 2)`% of titles contain at least 1 unanswered device terms
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ contain_u_dev, data = out_english)
+
+KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = out_english)
+plot_surv(KM_u_dev, data = out_english)
+```
+
+#### Looking at only device terms within freq_terms_a
+
+```{r, echo = FALSE}
+answered_devices <- freq_terms_a %>%
+                      filter(word %in% c("screen", "iphone", "phone", "battery", "button", "display", "macbook", "lcd", "board", "keyboard", "laptop", "home", "pro", "drive"))
+
+out_english$contain_dev_a <- str_detect(as.character(out_english$title), pattern = or1(answered_devices$word))
+prop_contain_a_dev <- sum(out_english$contain_dev_a)/nrow(out_english)
+```
+
+* `r round(prop_contain_a_dev*100, 2)`% of titles contain at least 1 answered device term
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ contain_dev_a, data = out_english)
+
+KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = out_english)
+plot_surv(KM_dev_a, data = out_english)
+```

### 2017-07-22 functions.Rmd
reorganized files and code, made code more reproducible, updated hours, deleted files

--- 2017-07-19 freq_words.Rmd
@@
 ---
-title: "New variables"
+title: "Functions Created"
 author: "Lisa Oshita"
-date: "July 14, 2017"
+date: "July 21, 2017"
 output: html_document
@@
 
-### importing the data/setting up variables
 ```{r}
+setup <- function() {
   dir <- file.path(getwd(),"data")
   out <- read.csv(file.path(dir, "answers_data.csv"))
-
-out$time_until_answer <- out$first_answer_date - out$post_date
-#filling in the NAs
-empty <- which(is.na(out$time_until_answer))
-for (i in empty) {
-  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
-}
 
@@
                   filter(langid == "en")
-```
 
-### finding most frequently used terms
-```{r}
-library(qdap)
-library(tm)
-#library(RWeka)
-
-#function to clean the corpus
-clean_corpus <- function(corpus){
-  corpus <- tm_map(corpus, stripWhitespace)
-  corpus <- tm_map(corpus, content_transformer(tolower))
-  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
-  return(corpus)
+  out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
+  empty <- which(is.na(out_english$time_until_answer))
+  for (i in empty) {
+    out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
+}
 }
 
-freq_terms <- function(vec) {
-  source <- VectorSource(vec)
-  corpus <- VCorpus(source)
-  cleaned_corpus <- clean_corpus(corpus) 
-  dtm <- DocumentTermMatrix(cleaned_corpus)
-  m <- as.matrix(dtm) 
-  freq <- colSums(m)
-  freq <- sort(freq, decreasing = TRUE)
-  return(freq)
-}
-
-titles_freq <- freq_terms(out_english$title)
-head(titles_freq)
-#this function changes "turn on" to just "turn", in our case "turn on" might be a significant term? -- do something about this in the function? like do bigrams? (observation 300)
-
-top100 <- titles_freq[1:100]
-top50 <- titles_freq[1:50]
-top10 <- titles_freq[1:10]
-plot(term_freq)
-plot(top50)
-```
-
-### variable indicating if title contains at least one word in top50 words list
-```{r}
-library(stringr)
-library(rebus)
-
-out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
-```
-
-### exploring contain_top10
-```{r}
-sum(out_english$contain_top10)/nrow(out_english)
-#41% of words contain at least one of the top 10 words
-
-library(dplyr)
-#not working correctly???
-out_english %>%
-  group_by(contain_top10) %>%
-  summarise(median_time = median(time_until_answer), 
-            avg_daily = mean(daily_views)) %>%
-  arrange(median_time)
-
-hist(unname(titles_freq))
-hist(log(titles_freq))
-hist(log(out_english$time_until_answer))
-
-t.test(log(time_until_answer) ~ contain_top10, data = out_english)
-```
-
-### survival curves
-```{r}
-library(survival)
-
-surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
-
-options(scipen=5)
-KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
-plot(KM_top10, lty = 1:2, xlab = "Time", ylab = "Survival Probability", main = "KM Curves for questions with and without top 10 terms")
-legend("topright", c("False", "True"), lty = 1:2)
-
-survdiff(surv_object~contain_top10, data = out_english)
-```
-
-### trying out TfIdf (counts occurrences of words but penalizes for appearing in too many documents) 
-```{r}
-freq_terms_weighted <- function(vec) {
-  source <- VectorSource(vec)
-  corpus <- VCorpus(source)
-  cleaned_corpus <- clean_corpus(corpus) 
-  dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = function(x)
-    weightTfIdf(x, normalize = TRUE)))
-  m <- as.matrix(dtm) 
-  freq <- colSums(m)
-  freq <- sort(freq, decreasing = TRUE)
-  return(freq)
-}
-
-titles_freq_weighted <- freq_terms_weighted(out_english$title)
-top10_weighted <- term_freq_weighted[1:10]
-top10_weighted
-top50_weighted <- term_freq_weighted[1:50]
-
-hist(titles_freq_weighted)
-
-#weighting didn't do much
-```
-
-### visualizing the frequency of the words
-
-also look at the distribution of how often the appear (plot of 100 words verses percent of posts appeared in) 
-top 20 words—might be in 80% of the words
-add up words cumulatively? use a cumulative function in r, make own table manually (word number vs percent post appears in , then use cumulative function on that table to create plot) 
-```{r}
-
-plot(x = c(1:50), unname(top50)/nrow(out_english), xlab = "Top 10 terms", ylab = "Percentage of posts appeared in", xaxt = "n")
-axis(1, at=1:50, labels=names(top50), las = 2)
-#screen appears in 12% of questions
-
-#cumulative distribution
-cum_percent <- cumsum(unname(top10))
-plot(x = c(1:10), cum_percent/nrow(out_english), xlab = "Top 10 Terms", ylab = "Cumulative Percentage of posts appeared in", xaxt = "n")
-axis(1, at=1:10, labels=names(top10), las = 2)
-# this is "double counting" questions? 
-```
-
-* find most frequent terms among answered/unanswered questions
-* if any of these terms are present in a question, can use to predict the time_until_answer (think that questions that contain terms in frequent terms list in answered questions might get answered quicker, questions that contain terms in list for unanswered questions might get answered slower)
-* noticed that there were shared common words among answered/unanswered questions (ex: screen, phone)
-* wanted to find a way to find words unique to answered/unanswered 
-* calculating proportion of times that each word in the most freq list occurs in its answered or unanswered category 
-* finding the difference in these proportions to see if the word is more likely to be in answered/unanswered category 
-*use these difference in proportions to determine which list the term should be included in (answered/unanswered)
-
-```{r}
-library(tidyverse) #contains all packages
-library(plyr)
-answered <- out_english %>%
-              tbl_df() %>% 
-              filter(answered == 1)
-unanswered <- out_english %>%
-              tbl_df() %>% 
-              filter(answered == 0)
-
-answered_m <- freq_terms(answered$title)
-unanswered_m <- freq_terms(unanswered$title)
-
-answered_m[1:100]
-unanswered_m[1:100]
-
-str(answered_m)
-
-#proportion of times each term occurs in answered/unanswered questions
-answered_freq <- data.frame(term = names(answered_m), a_freq = unname(answered_m), a_prop = unname(answered_m)/length(answered_m))
-
-unanswered_freq <- data.frame(term = names(unanswered_m), u_freq = unname(unanswered_m), u_prop = unname(unanswered_m)/length(unanswered_m))
-
-combined <- join(answered_freq, unanswered_freq, by = "term", match = "all")
-head(combined)
-dim(combined)
 ```
@@
 ```{r}
-combined$difference <- abs(combined$a_prop - combined$u_prop)
-combined$ratio <- combined$a_prop/combined$u_prop
-head(combined)
 
-combined %>%
-  arrange(desc(ratio)) %>%
-  select(-difference)
-# ssd is 28.8 times more likely to appear in answered questions than it is in unanswered questions, only because it appears 40 times in a_freq questions and only once in unanswered 
-# need to come up with min and max thresholds for which terms to include freq_words list
+plot_surv <- function(survfit, data) {
 
-combined %>%
-  arrange(desc(u_prop))
+  library(ggfortify)
+  library(directlabels)
 
-library(ggthemes)
-ggplot(combined, aes(x = u_prop)) +
-  geom_histogram(bins = 50) + 
-  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
-  scale_y_continuous(limits = c(0,500))
+  df <- fortify(survfit, data = data)
 
-ggplot(combined, aes(x = a_prop)) +
-  geom_histogram(bins = 50) + 
-  scale_x_continuous(limits = c(0, 0.05), labels = scales::percent) + 
-  scale_y_continuous(limits = c(0,200)) 
+  if (!("strata" %in% names(df))) {
+    ggplot(df, aes(x = time, y = surv)) + 
+    geom_line() + 
+    scale_y_continuous("Survival Probability") +
+    scale_x_continuous("Time")
+    ggtitle("Survival Curve")
+  }
+
+  if ("strata" %in% names(df)) {
+    ggplot(df, aes(x = time, y = surv, color = strata)) + 
+      geom_line() + 
+      scale_y_continuous("Survival Probabilities") +
+      scale_x_continuous("Time") + 
+      ggtitle("Survival Curves") + 
+      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+  }
+}
 ```
-* how many words to consider
-* minimum/max occurence thresholds (how often show up to be able to use it) 
-* create a function that takes in as parameter how many words to consider, and then 
-*function to take in vector of text, return frequencies of top words, input = number of words to return 
-*ggplot!!!!

### 2017-07-22 literature_reviews.Rmd
reorganized files and code, made code more reproducible, updated hours, deleted files

---
title: "Notes from studies/dissertations"
author: "Lisa Oshita"
date: "July 20, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### "Understanding and Classifying the Quality of Technical Forum Questions"
* published in: 2014 14th International Conference on Quality Software
* tries to model/predict the quality of questions on Stack Overflow

##### Metrics 
* Stack Overflow Metrics 
    + Body length
    + Emails count (number of email addresses found in the question)
    + Lowercase percentage (percentage of lowercase letters throughout the question)
    + Spaces count (total number of spaces throughout question)
    + Number of tags
    + Text Speak Count (number of text speak within the question, ex: doesnt', wat, rotfl)
    + Textual similarity between question and title
    + Capital title 
    + Uppercase percentage
* Readabiity metrics
    + Metric entropy = shannon entropy/length of the text: represents the randomness of the info in the question
    + Average terms entropy = average of the entropy for each term in questions text
    + Computed standardized readibility indexes- represent comprehension difficulty Stanford NLP Parser7 to extract sentences/words, TeX hyphenation [16] for syllables
* User popularity metrics
    + badges received concerning question and answers
    + coverage of author’s badges with respect to the tags assigned by the author to the new question
    + maybe consider including a variable about the reputation of an asker?

##### Data Analysis
* used decision trees to classify good/bad questions
    + found that the popularity of the author is more important than textual features to determine quality
* Learned quality function findings
    + found that users who received a lot of down votes were more likely to post good questions to up their reputation
    + having produced good answers in the past was indicative of good quality
    + up votes recieved in the past didn't influence quality
    + text speak indicates bad quality (low number of sentences in the question) (maybe do ratio of number of sentences to length of question)????

##### References to check
* M. Allamanis and C. Sutton. Why, when, and what: Analyzing stack overflow questions by topic, type, and code. In Proceedings of MSR2013 (10th Working Conference on Mining Software Repositories), pages 53–56. IEEE Press, 2013.
* K. Arai and A. N. Handayani. Prediting Quality of Answer in Collaborative Q\A Community. International Journal of Advanced Research in Artificial Intelligence, 2(3):21–25, 2013.
* M. Coleman and T. L. Liau. A computer readability formula designed for machine scoring. Journal of Applied Psychology, 60(2):283–284, April 1975.
* D. Correa and A. Sureka. Chaff from the Wheat : Characterization and Modeling of Deleted Questions on Stack Overflow. In Proceedings of WWW 2014 (23rd international conference on World Wide Web. ACM, 2014.
* M. J. David Blei, Andrew Ng. Latent Dirichlet Allocation. Journal of machine Learning research, 3:993–1022, 2003.
* J. Jeon, W. B. Croft, J. H. Lee, and S. Park. A framework to predict the quality of answers with non-textual features. In Proceedings of SIGIR 2006 (29th Annual International ACM SIGIR Conference on Research & Development on Information Retrieval), pages 228–235. ACM, 2006.
* C. Treude, O. Barzilay, and M.-A. Storey. How do programmers ask and answer questions on the web? (nier track). In Proceedings of ICSE 2011 (33rd International Conference on Software Engineering), pages 804–807. ACM, 2011.
* A. Barua, S. W. Thomas, and A. E. Hassan. What are developers talking about? an analysis of topics and trends in stack overflow. Empirical Software Engineering, 19(3):619-654, June 2014.

##### References from "Quality Questions Need Quality Code: Classifying Code Fragments on Stack Overflow" to look into
* V. Bhat, A. Gokhale, R. Jadhav, J. Pudipeddi, and L. Akoglu, “Min(e)d your tags: Analysis of question response time in stackoverflow,” in Proc. of ASONAM 2014, 2014, pp. 328–335.
*  J. Yang, C. Hauff, A. Bozzon, and G.-J. Houben, “Asking the right question in collaborative Q&A systems,” Proc. of Hypertext 2014, pp. 179–189.

### "Automatically Assessing the Post Quality in Online Discussions on Software" References
* Jihie Kim, Grace Chern, Donghui Feng, Erin Shaw, and Eduard Hovya. 2006a. Mining and assessing discussions on the web
through speech act analysis. In Proceedings of the Workshop on Web Content Mining with Human Language Technologies at the 5th International Semantic Web Conference.
* Mitchell P. Marcus, Beatrice Santorini, and Mary Ann Marcinkiewicz. 1994. Building a Large Annotated Corpus
of English: The Penn Treebank. Computational Linguistics, 19(2):313–330.

### 2017-07-22 summary_stats.Rmd
reorganized files and code, made code more reproducible, updated hours, deleted files

---
title: "Summary Statistics"
output:
  html_document: default
  pdf_document: default
---

```{r, Importing and setting up the data , include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
out_english <- out %>% 
                tbl_df() %>%
                filter(langid == "en")

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

library(ggplot2)
library(survival)
library(survminer)
library(epiR)

proportion_answered <- sum(out_english$answered)/nrow(out_english)
```

#### About the data set:

* `r nrow(out_english)` observations
* `r round(proportion_answered * 100, digits = 2)` % of questions were answered

#### Exploring the response: time_until_answer

```{r, time_until_answer, echo = FALSE}
summary <- summary(out_english$time_until_answer)
```

* **minimum:** `r round(min(out_english$time_until_answer), 2)` hrs
* **maximum:** `r round(max(out_english$time_until_answer), 2)` hrs
* **mean:** `r round(mean(out_english$time_until_answer), 2)` hrs
* **median:** `r round(median(out_english$time_until_answer), 2)` hrs
* **first quartile:** `r round(summary[2], 2)`hrs
* **third quartile:** `r round(summary[5], 2)` hrs
* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs

```{r, distribution of response, echo = FALSE}
ggplot(out_english, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous("Time (hours)") +
  ggtitle("Distribution of time_until_answer values")
```

### Survival Analysis Statistics

##### Survival Time Statistics based off of KM Estimator 
```{r, survival analysis statistics, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")

KM <- survfit(surv_object ~ 1, conf.type = "log-log")

s <- summary(KM)
round(s$table, 2)
```

* **Min survival probability:** `r round(min(s$surv), 2)`
* **Max survival probability:** `r round(max(s$surv), 2)`
* **rmean survival time:** `r round(s$table[5], 2)` hrs
* **SE of rmean:** `r round(s$table[6], 2)` hrs
* **Median survival time:** `r round(s$table[7], 2)` hrs
* **95% confidence interval for the median:** (`r round(s$table[8], 2)`,`r round(s$table[9], 2)`)

##### Percentiles

```{r, percentiles, echo = FALSE}
quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.75))
round(quant[[1]], 3)
```
* **Interpretations:**
    + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
    + By `r round(quant$quantile[2], 2)` hrs 10% of the questions have been answered
    + By `r round(quant$quantile[3], 2)` hrs 25% of the questions have been answered
    + By `r round(quant$quantile[4], 2)` hrs 30% of the questions have been answered
    + By `r round(quant$quantile[5], 2)` hrs 50% of the questions have been answered
    + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)

##### Survival Curves

* Survival curve shows that survival probability drops immediately after question is posted. Within a few hours after posting, survival probability levels out, hovers around 0.35 (never hits 0).

```{r, survival curves, echo = FALSE}
ggsurvplot(KM, data = out_english, risk.table = TRUE, xlab = "Time (hours)", main = "KM Curve")
ggsurvplot(KM, data = out_english, risk.table = FALSE, xlab = "Time (hours)", main = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
```

### Instantaneous Hazard Rates (based off of KM estimates)

```{r, instant hazard, echo = FALSE}
h.hat <- epi.insthaz(KM, conf.level = 0.95) #instantaneous hazard on basis of KM 
round(head(h.hat), 3)
```

* **Max instant hazard rate:** `r round(max(h.hat$est), 2)` at time: `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
* **Min instant hazard rate:** `r round(min(h.hat$est), 2)`

```{r, instant hazard plots, echo = FALSE}
ggplot(h.hat, aes(x = time, y = est)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)") + 
  scale_y_continuous("Instantaneous Hazard Rate") + 
  ggtitle("Instantaneous Hazard Rate Plot")

ggplot(h.hat, aes(x = time, y = est)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)", limits = c(0,50)) + 
  scale_y_continuous("Instantaneous Hazard Rate") + 
  ggtitle("Instantaneous Hazard Rate Plot (zoomed in)")
```

* Instant hazard rate of a question getting answered drops to 0 and stays there pretty consistently after about 45 hours
* Right before that 45th hour, hazard spikes up twice to about 1.25

### Cumulative Hazard Rates

* Nelson-Aalen plot: rate of increase of H(t) starts to decrease/levels out around ~50 hours (indicates that instantaneous hazard is decreasing)

```{r, cumulative hazard, echo = FALSE}
#KM estimator of cumulative hazard 
fit <- data.frame(surv = s$surv, time = s$time, n.event = s$n.event, n.risk = s$n.risk)
fit$H.hat <- -log(fit$surv)

ggplot(fit, aes(x = time, y = H.hat)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)") + 
  scale_y_continuous("Cumulative Hazard Rate based off of KM Estimates") + 
  ggtitle("Cumulative Hazard Plot (KM)")

#Nelson-Aalen estimator of cumulative hazard
fit$H.tilde <- cumsum(fit$n.event/fit$n.risk)

ggplot(fit, aes(x = time, y = H.tilde)) +
  geom_line() +
  scale_x_continuous("Time (hours)", limits = c(0,1000)) +
  scale_y_continuous("Cumulative Hazard Rate based off of Nelson Aalen Type") + 
  ggtitle("Cumulative Hazard Plot (Nelson-Aalen)")
```

### 2017-07-22 variable_exploration.Rmd
reorganized files and code, made code more reproducible, updated hours, deleted files

---
title: "Exploring variables in the data"
output: 
  html_document: default
  pdf_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, Importing and setting up the data , include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
out_english <- out %>% 
                tbl_df() %>%
                filter(langid == "en")

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

library(ggplot2)
library(survival)
library(survminer)
library(epiR)
library(stringr)
library(rebus)
```

```{r, function to plot KM curves with ggplot, include = FALSE}
#function to plot KM_curves with ggplot (use when it's hard to read ggsurvplot output)

plot_surv <- function(survfit, data, ...) {
  library(ggfortify)
  library(directlabels)

  df <- fortify(survfit, data = data)

  if (!("strata" %in% names(df))) {
    ggplot(df, aes(x = time, y = surv)) + 
    geom_line() + 
    scale_y_continuous("Survival Probability") +
    scale_x_continuous("Time")
    ggtitle("Survival Curve")
  }

  if ("strata" %in% names(df)) {
    ggplot(df, aes(x = time, y = surv, color = strata)) + 
      geom_line() + 
      scale_y_continuous("Survival Probabilities") +
      scale_x_continuous("Time") + 
      ggtitle("Survival Curves") + 
      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
  }
}

```

### Category

##### number of questions within each category

```{r, category1, echo = FALSE}
categories <- out_english %>%
                group_by(category) %>%
                summarise(n = n()) %>%
                arrange(desc(n))
categories
```

##### median/average time by category

```{r, category2, echo = FALSE}
sorted <- out_english %>% 
            group_by(category) %>%
            summarise(n = n(), avg_time = mean(time_until_answer), median_time = median(time_until_answer)) %>%
            arrange(median_time)
sorted
```

* **Categories with lowest median time_until_answer values:** `r as.character(sorted$category[1:5])`
* **Category with longest median time_until_answer:** `r last(as.character(sorted$category))`

##### log-rank test

```{r, category3, echo = FALSE}

surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")

survdiff(surv_object~category, data = out_english)
```

##### survival curves

```{r, echo = FALSE}
KM_category <- survfit(surv_object~category, data = out_english)

plot_surv(KM_category, data = out_english)
```

### Whether or not the question was categorized correctly

```{r, categorized correctly?, echo = FALSE}
prop_incorrect <- sum(is.na(out_english$category))/nrow(out_english)
```

* `r round(prop_incorrect*100, 2)`% of questions were categorized incorrectly

##### log-rank test

```{r, echo = FALSE}
out_english$categorized <- 0
out_english$categorized[!is.na(out_english$category)] <- 1

survdiff(surv_object~categorized, data = out_english)
```

##### survival curves

```{r, echo = FALSE}
KM_correct <- survfit(surv_object ~ as.factor(categorized), data = out_english)
plot_surv(KM_correct, data = out_english, xlim = c(0,100))
```

### Does the title contain a question mark

```{r, question mark, echo = FALSE}
out_english$contain_question <- str_detect(out_english$title, pattern = QUESTION)

prop_contain <- sum(out_english$contain_question)/nrow(out_english)

true <- out_english %>% 
  filter(contain_question == T)
prop_answered <- sum(true$answered)/nrow(true)
```
* `r round(prop_contain * 100, 2)`% of questions contain a question mark
* `r round(prop_answered * 100, 2)`% of questions with a question mark were answered

##### median time grouped by whether or not question contains: '?'

```{r, echo = FALSE}
out_english %>%
  group_by(contain_question) %>%
  summarise(median_time = median(time_until_answer), n = n()) %>%
  arrange(median_time)
```

* indicates that questions with a '?' tend to have shorter answer times than questions without

##### proportion of questions with '?' and median time grouped by category

```{r, echo = FALSE}
c <- out_english %>% 
    group_by(category) %>%
    summarise(n = n(), proportion_with_question = sum(contain_question)/n, median_time = median(time_until_answer)) %>%
    arrange(desc(proportion_with_question))
c
```

* **categories with highest proportion of questions containing question marks:** `r as.character(c$category[1:5])`

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_question, data = out_english)
```

##### survival curves

```{r, echo = FALSE}
KM_question <- survfit(surv_object ~ contain_question, data = out_english)
plot_surv(KM_question, data = out_english)
```

### Searching for "tried" and "searched" in the text variable
```{r, tried, echo = FALSE}
out_english$tried <- str_detect(as.character(out_english$text), pattern = or("tried", "searched"))
prop_tried <- sum(out_english$tried)/nrow(out_english)
```

* `r round(prop_tried * 100, 2)`% of questions contain either "tried" or "searched"

##### median time/average daily views grouped by whether or not question contains "tried"/"searched"
```{r, echo = FALSE}
out_english %>%
  group_by(tried) %>%
  summarise(median_time = median(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(tried), data = out_english)
```

##### survival curves

```{r, echo = FALSE}
KM_tried <- survfit(surv_object ~ as.factor(tried), data = out_english)

plot_surv(KM_tried, data = out_english)
```

### Title Length

##### distribution of title lengths

```{r, title length, echo = FALSE}
out_english$title_length <- str_length(out_english$title)

ggplot(out_english, aes(x = title_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Question Title") + 
  ggtitle("Distribution of Title Lengths")
```

```{r, echo = FALSE}
sum_length <- summary(out_english$title_length)
```

* **min title length:** `r sum_length[1]` characters
* **max title length:** `r sum_length[6]` characters
* **mean title length:** `r sum_length[4]`
* **median:** `r sum_length[3]`

##### average title length grouped by answered/unanswered questions

```{r, echo = FALSE}
out_english %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(title_length), n = n())
```

##### average title length and median time grouped by category

```{r, echo = FALSE}
out_english %>%
  group_by(category) %>%
  summarise(n = n(), avg_length = mean(title_length), median_time = median(time_until_answer)) %>%
  arrange(desc(avg_length))
```

### Text Length

```{r, text length, echo = FALSE}
out_english$text_length <- str_length(out_english$text)

ggplot(out_english, aes(x = text_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Text") + 
  ggtitle("Distribution of Text Lengths")

sum_text <- summary(out_english$text_length)
```

* **min text length:** `r sum_text[1]` characters
* **max text length:** `r sum_text[6]` characters
* **mean text length:** `r sum_text[4]`
* **median:** `r sum_text[3]`

##### average/median text length and median time grouped by answered/unanswered questions

* may be evidence that questions with longer text length tend to get answered

```{r, echo = FALSE}
out_english %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(text_length), median_length = median(text_length), median_time = median(time_until_answer), n = n())
```

##### determining which categories have the longest text lengths

```{r, echo = FALSE}
out_english %>%
  group_by(category) %>%
  summarise(avg_length = mean(text_length), median_length = median(text_length), n = n()) %>%
  arrange(desc(avg_length))
```

### Device length

```{r, device length, echo = FALSE}
out_english$device_length <- str_length(out_english$device)

ggplot(out_english, aes(x = device_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Device Name") + 
  ggtitle("Distribution of Device Name Lengths")

sum_device <- summary(out_english$device_length)
```

* **min length:** `r sum_device[1]`
* **max length:** `r sum_device[6]`
* **mean length:** `r sum_device[4]`
* **median length:** `r sum_device[3]`

##### average and median device length grouped by answered/unanswered questions

```{r, echo = FALSE}
out_english %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n())
```

##### which categories have the longest device name lengths

```{r, echo = FALSE}
out_english %>%
  group_by(category) %>%
  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n()) %>%
  arrange(desc(avg_length))
```

### n_tags

* n_tags included in questions: `r unique(out_english$n_tags)`
```{r, number tags, echo = FALSE}
prop_notags <- sum(out_english$n_tags == 0)/nrow(out_english)
```
* `r round(prop_notags * 100,2)`% of questions don't have any tags

##### proportion table for n_tags

```{r, echo = FALSE}
round(prop.table(table(out_english$n_tags)), 3)
```

##### median time and proportion of questions answered grouped by n_tags

* questions with more tags tend to have faster answer times and are more likely to get answers

```{r, echo = FALSE}
out_english %>%
  group_by(as.factor(n_tags)) %>%
  summarise(n = n(), median_time = median(time_until_answer), proportion_answered = sum(answered)/n) %>%
  arrange(median_time)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(n_tags), data = out_english)
```

##### survival curves

```{r, echo = FALSE}
KM_tags <- survfit(surv_object~as.factor(n_tags), data = out_english)
plot_surv(KM_tags, data = out_english)
```

### n_images

```{r, echo = FALSE}
prop_hasimage <- sum(out_english$n_images != 0)/nrow(out_english)
```

* `r round(prop_hasimage * 100, 2)`% of questions contain at least one image

##### frequency table for n_images

```{r, number images, echo = FALSE}
table(out_english$n_images)
```

##### median time and proportion answered grouped by whether or not question contains an image

* questions that include at least one image tend to have faster answer times

```{r, echo = FALSE}
out_english$pic_included <- 0
out_english$pic_included[out_english$n_images != 0] <- 1

out_english %>%
  group_by(as.factor(pic_included)) %>%
  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n) %>%
  arrange(desc(proportion_answered))
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(pic_included), data = out_english)
```

##### survival curves

```{r, echo = FALSE}
KM_pic <- survfit(surv_object~as.factor(pic_included), data = out_english)
plot_surv(KM_pic, data = out_english)
```

### new_user

```{r, echo = FALSE}
prop_new <- sum(out_english$new_user)/nrow(out_english)
```

* `r round(prop_new * 100, 2)`% of users asking a question were new

##### median time and proportion answered grouped by whether or not new user

```{r, echo = FALSE}
out_english %>% 
  group_by(as.factor(new_user)) %>%
  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n) %>%
  arrange(desc(proportion_answered))
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(new_user), data = out_english)
```

##### survival curves

```{r, echo = FALSE}
KM_new <- survfit(surv_object~as.factor(new_user), data = out_english)
plot_surv(KM_new, data = out_english)
```

### daily_views

```{r, echo = FALSE}
ggplot(out_english, aes(x = daily_views)) + 
  geom_histogram() + 
  scale_x_continuous("Average daily views for a question") + 
  ggtitle("Distribution of Daily Views")
```

* **max average daily views for a question:** `r max(out_english$daily_views)`
* **min average daily views for a question:** `r min(out_english$daily_views)`
* **mean:** `r round(mean(out_english$daily_views), 2)`
* **median:** `r round(median(out_english$daily_views), 2)`

##### median daily view and median time grouped by category

```{r, echo = FALSE}
out_english %>%
  group_by(category) %>%
  summarise(median_views = median(daily_views), n = n(), median_time = median(time_until_answer)) %>%
  arrange(desc(median_views))
```

##### median daily views and time grouped by n_tags

```{r, echo = FALSE}
out_english %>%
  group_by(as.factor(n_tags)) %>%
  summarise(median_views = median(daily_views), median_time = median(time_until_answer), n = n()) %>%
  arrange(desc(median_views))
```

##### median daily views and time grouped by whether or not image included

```{r, echo = FALSE}
out_english %>%
  group_by(as.factor(pic_included)) %>%
  summarise(median_views = median(daily_views), median_time = median(time_until_answer), n = n())
```

### 2017-07-24 literature_reviews.Rmd
finished literature reviews, updated hours

@@
 
+### "“Question Quality in Community Q&A” Notes"
+* some correlation between view count and question quality 
+* content (length and text) gave signficant improvement in classification accuracy (over ViewCount)- indicates that words used capture quality 
+* good questions tended to be shorter 
+* good questions: 
+    + aren't repeats (user has done research)
+    + receive more answers on average (5 compared to 2.5), also receive longer answers and more comments
+    + "live longer"
+    + "latent topical aspects shared between related questions are good predictors of question quality"
+
 ### "Understanding and Classifying the Quality of Technical Forum Questions"
@@
     + Body length
-    + Emails count (number of email addresses found in the question)
+    + Emails count
     + Lowercase percentage (percentage of lowercase letters throughout the question)
     + Spaces count (total number of spaces throughout question)
-    + Number of tags
-    + Text Speak Count (number of text speak within the question, ex: doesnt', wat, rotfl)
+    + Text Speak Count (number of text speak within the question, ex: doesnt', wat, rotfl): text speak indicates bad quality (low number of sentences in the question) (maybe do ratio of number of sentences to length of question)????
     + Textual similarity between question and title
@@
     + badges received concerning question and answers
-    + coverage of author’s badges with respect to the tags assigned by the author to the new question
-    + maybe consider including a variable about the reputation of an asker?
-
-##### Data Analysis
-* used decision trees to classify good/bad questions
-    + found that the popularity of the author is more important than textual features to determine quality
-* Learned quality function findings
-    + found that users who received a lot of down votes were more likely to post good questions to up their reputation
-    + having produced good answers in the past was indicative of good quality
-    + up votes recieved in the past didn't influence quality
-    + text speak indicates bad quality (low number of sentences in the question) (maybe do ratio of number of sentences to length of question)????
+    + users who recieved downvotes before more likely to post good questions to up their reputation 
+    + up votes recieved in the past didn't indicate quality
+    + found that popularity metrics were more important that others in predicting quality
 
@@
 
-##### References from "Quality Questions Need Quality Code: Classifying Code Fragments on Stack Overflow" to look into
-* V. Bhat, A. Gokhale, R. Jadhav, J. Pudipeddi, and L. Akoglu, “Min(e)d your tags: Analysis of question response time in stackoverflow,” in Proc. of ASONAM 2014, 2014, pp. 328–335.
+### References from "Quality Questions Need Quality Code: Classifying Code Fragments on Stack Overflow" to look into
+* **V. Bhat, A. Gokhale, R. Jadhav, J. Pudipeddi, and L. Akoglu, “Min(e)d your tags: Analysis of question response time in stackoverflow,” in Proc. of ASONAM 2014, 2014, pp. 328–335.**
 *  J. Yang, C. Hauff, A. Bozzon, and G.-J. Houben, “Asking the right question in collaborative Q&A systems,” Proc. of Hypertext 2014, pp. 179–189.
 
-### "Automatically Assessing the Post Quality in Online Discussions on Software" References
-* Jihie Kim, Grace Chern, Donghui Feng, Erin Shaw, and Eduard Hovya. 2006a. Mining and assessing discussions on the web
-through speech act analysis. In Proceedings of the Workshop on Web Content Mining with Human Language Technologies at the 5th International Semantic Web Conference.
-* Mitchell P. Marcus, Beatrice Santorini, and Mary Ann Marcinkiewicz. 1994. Building a Large Annotated Corpus
-of English: The Penn Treebank. Computational Linguistics, 19(2):313–330.
+### "Automatically Assessing the Post Quality in Online Discussions on Software"
+* Published in: ACL '07 Proceedings of the 45th Annual Meeting of the ACL on Interactive Poster and Demonstration Sessions Pages 125-128 
+* features used in the model 
+    + surface features: number of tokens in a post, percentage of sentences ending with "?", percentage of sentences ending with "!", percentage of words in CAPITAL
+    + lexical features: spelling error frequency, swear word frequency
+    + syntactic features
+    + similarity features: relatedness of post to the topic of a forum
+
+##### References 
+* Jihie Kim, Grace Chern, Donghui Feng, Erin Shaw, and Eduard Hovya.
+2006a.
+Mining and assessing discussions on the web through speech act analysis.
+In Proceedings of the Workshop on Web Content Mining with Human Language Technologies at the 5th International Semantic Web Conference.
+* Mitchell P. Marcus, Beatrice Santorini, and Mary Ann Marcinkiewicz. 1994. Building a Large Annotated Corpus of English: The Penn Treebank. Computational Linguistics, 19(2):313–330.
+
+### "Exploring Generic Features For Online Large-Scale Discussion Forum Comments" notes (dissertation)
+* used sentiment analysis- took the value of the comment sentiment (positivity, negativity, neutral)
+  + tags comments with lexicons
+* post-level syntactic features: Post length, time stamp, type of post, edit count, votes, constructiveness score (number of constructive word counts (constructive learning activities per post)), number of unique users commenting on a post, number of controversial comments
+* used regression models, one with votes as response and another with constructiveness
+* regression model for votes
+    + most unique users commenting, more votes
+    + presence of code/number of edits has positive relationship with votes
+    + mean comment entropy is positively related to votes (diversity is a good indicator of quality)
+* regression model for constructiveness
+    + number of unique users who comment, reputation, timing all relate to constructiveness
+
+## "Min(e)d your tags: Analysis of Question response time in StackOverflow" Notes
+* tag based features
+    + **average frequency of tags**
+    + **number of popular tags**
+    + average co-occurence rate of tags
+    + % active subscribers, number of responsive subscribers, % responsive subscribers
+* non-tag based features
+    + number of code segments/total code length
+    + number of images
+    + body length, title length
+    + whether title ends with question mark
+    + **whether title starts with "Wh" word**
+    + **whether question is posted on weekend** 
+    + **number of verbs that indicate action**
+    + **number of self references of asker**
+* tag popularity: popularity = frequency (num questions that contain t as one of its tags), compute the average popularity of all its tags
+* group tags into popular and unpopular based on frequency threshold, count number of popular tags a question contains 
+* number of action verbs: verbs that indicate action/research was taken by the person asking before posting the question: "tried", "did", "made", "used", "run"...
+* self references: presence of "I", "we", "me", "my", "myself" - indicate prior work/research done before posting question, maybe indicates question quality (normalize these values by question length)
+* specificity of tags positively correlated with response time (maybe consider the length of the hashtags)- if tag is too specific, not as easy for user to find the question
+* succinct questions seem to have faster response times
+*
+
+##### References
+* J. Mahmud, J. Chen, and J. Nichols, "When will you answer this? estimating response time in twitter." in ICWSM. The AAAI Press, 2013.
+* M.
+Asaduzzaman, A.
+Mashiyat, C.
+Roy, and K.
+Schneider, "Answering questions about unanswered questions of stack overflow, " in 10th Working Conference on Mining Software Repositories.
+Mining Challenge, 2013
+* A. Rechavi and S. Rafaeli, "Not all is gold that glitters: Response time & satisfaction rates in Yahoo! answers." in SocialCom/PASSAT. IEEE, 2011, pp. 904-909.
+* A.
+Anderson, D.
+P.
+Huttenlocher, J.
+M.
+Kleinberg, and J.
+Leskovec, "Discovering value from community activity on focused question answering sites: a case study of stack overflow." in KDD, 2012, pp.
+850-858.
+* F. M. Harper, D. R. Raban, S. Rafaeli, and J. A. Konstan, "Predictors of answer quality in online Q&A sites." in CHI. ACM, 2008, pp. 865-874.
+
+## "Answering questions about unanswered questions of stack overflow" notes
+* reasons questions go unanswered:  
+    + question is too short/unclear/hard to follow
+    + too specific/time consuming
+    + duplicate question
+    + fails to attract expert member (incorrect tagging) 
+* consider tag similarity: number of previous posts that contain tags similar to it
+
+## "Not all is gold that glitters: Response time & satisfaction rates in Yahoo! answers." notes
+* shortest response time found between askers and answerers who did not follow each other
+* longest response time found between askers and answerers who did (they were mutual friends)
+
+## "Discovering value from community activity on focused question answering sites: a case study of stack overflow." notes
+* since askers generally accept the first answer, there is an incentive to answer quickly- so the answerer will get their reputation raised: so maybe reputation plays a roll in response time
+
+## "Predictors of answer quality in online Q&A sites." notes
+* prior effort: may include statements like "I did a Google search..." or "I've asked our IT...", found that this had no statisitcally signficant effect on the quality of answers an asker received
+* On average prior effort actually decreased judged answer quality and judged answerer effort
+
+# Ideas:
+* consider more textual features:
+    + percentage of lowercase/uppercase, if first letter in title is capitalized
+    + "text speak" - indicates bad sentence quality or a low number of sentences in a question, maybe do ratio of sentences to length of question? 
+    + spelling error frequency??
+    + textual similarity between title and text
+    + shannon entropy (randomness of a question) 
+    + number of action verbs: verbs that indicate asker did something/researched before posting question: "tried", "did", "made", "used", "run"
+    + self references: use of "I", "me", "we"... another indicator of prior research/action
+    + whether title starts with "Wh" 
+* characteristics of the asker
+    + reputation
+* tags
+    + average frequency of tags, popularity of the tags
+    + average character length of tags (concise tags might get faster response times), might be able to show when askers use tagging incorrectly 
+* time of day when the question was posted, day of the week?

### 2017-07-28 Hours.Rmd
updated total hours
reorganized files and code, made code more reproducible, updated hours, deleted files
finished literature reviews, updated hours
finished work with tags, updated hours, tweaked functions/other files

@@
 7/20/2017 | 5.5 | 2:00-7:30PM | Frequently used terms, started on literature review, started trying to reorganize summary statistics report
-
->> __Total Hours: 89.08__
+7/21/2017 | 4.5 | 7:00-11:30AM | Re-organized summary statistics
+7/21/2017 | 6 | 3:30-9:30PM | Continued to re-organize, wrote functions/rewrote parts of code
+7/22/2017 | 2 | 10:00-12:00PM | Re-organzied freq words file
+7/22/2017 | 4 | 3:00-7:00PM | Literature reviews
+7/24/2017 | 1.5 | 8:30-10:00AM | Finished literature reviews
+7/24/2017 | 3 | 1:00-4:00PM | Explored tags, created new variables
+7/24/2017 | 3 | 6:00-9:00PM | Tried to create tag frequency variable, ran into problems, looked into creating own r package
+7/25/2017 | 2 | 9:00-11:00AM | Continued to work analyze tag variable
+7/25/2017 | 3 | 1:00-4:00PM | Wrote the code for tag variables, tried to fix Java problem
+7/27/2017 | 7 | 12:00-7:00 | Met with the Data Specialist to discuss data visualization ideas, finished working with tags, started with textual features of the data
+>> __Total Hours: 133.08__

### 2017-07-28 freq_words.Rmd
finished work with tags, updated hours, tweaked functions/other files

@@
 #function to plot survival curves with ggplot
-plot_surv <- function(survfit, data, ...) {
+plot_surv <- function(survfit, data, xlim = NULL) {
   library(ggfortify)
@@
   df <- fortify(survfit, data = data)
+
+  if (missing(xlim)) {
 
@@
         }
-
     if ("strata" %in% names(df)) {
@@
         geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+    }
+  } else {
+
+      if (!("strata" %in% names(df))) {
+        ggplot(df, aes(x = time, y = surv)) + 
+          geom_line() + 
+          scale_y_continuous("Survival Probability") +
+          scale_x_continuous("Time", limits = xlim)
+          ggtitle("Survival Curve")
+      }
+
+      if ("strata" %in% names(df)) {
+        ggplot(df, aes(x = time, y = surv, color = strata)) + 
+          geom_line() + 
+          scale_y_continuous("Survival Probabilities") +
+          scale_x_continuous("Time", limits = xlim) + 
+          ggtitle("Survival Curves") + 
+          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+      }
   }

### 2017-07-28 functions.Rmd
finished work with tags, updated hours, tweaked functions/other files

@@
 ```{r}
+library(dplyr)
+library(ggfortify)
+library(directlabels)
+library(tm)
+library(qdap)
+```
+
+```{r}
+#imports data set, includes only questions in English, creates time_until_answer (in hrs)
 setup <- function() {
@@
 
-  library(dplyr)
   out_english <- out %>% 
@@
 }
-
 ```
@@
 ```{r}
-
-plot_surv <- function(survfit, data) {
-
-  library(ggfortify)
-  library(directlabels)
+#function to plot survfit objects
+#input: survfit object, data, optional x-axis limits
+plot_surv <- function(survfit, data, xlim) {
 
   df <- fortify(survfit, data = data)
+
+  if (missing(xlim)) {
 
@@
     }
+  } else {
+
+      if (!("strata" %in% names(df))) {
+        ggplot(df, aes(x = time, y = surv)) + 
+          geom_line() + 
+          scale_y_continuous("Survival Probability") +
+          scale_x_continuous("Time", limits = xlim)
+          ggtitle("Survival Curve")
+      }
+
+      if ("strata" %in% names(df)) {
+        ggplot(df, aes(x = time, y = surv, color = strata)) + 
+          geom_line() + 
+          scale_y_continuous("Survival Probabilities") +
+          scale_x_continuous("Time", limits = xlim) + 
+          ggtitle("Survival Curves") + 
+          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+      }
+  }
 }
 ```
+
+```{r}
+#function to clean corpus
+clean_corpus <- function(corpus){
+
+  corpus <- tm_map(corpus, stripWhitespace)
+  corpus <- tm_map(corpus, content_transformer(tolower))
+  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
+  return(corpus)
+}
+
+#returns a data frame of words and frequencies sorted by most to least frequent
+#input: character vector of words, n is optional (to output top n most frequent words)
+freq_terms <- function(vec, n) {
+
+  source <- VectorSource(vec)
+  corpus <- VCorpus(source)
+  cleaned_corpus <- clean_corpus(corpus) 
+  dtm <- DocumentTermMatrix(cleaned_corpus)
+  m <- as.matrix(dtm) 
+  freq <- colSums(m)
+  freq <- sort(freq, decreasing = TRUE)
+  freq_df <- data.frame(word = names(freq), frequency = unname(freq))
+
+  if (missing(n)) {
+    return(freq_df)
+  }
+  else {
+    return(freq_df[1:n,])
+  }
+}
+```

### 2017-07-28 tag_exploration.Rmd
finished work with tags, updated hours, tweaked functions/other files

---
title: "Exploring n_tags"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
out_english <- out %>% 
                tbl_df() %>%
                filter(langid == "en")

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

library(stringr)
library(stringi)
library(ggplot2)
library(dplyr)
library(rebus)
#library(qdap)
library(forcats)
library(purrr)
library(survival)
library(ggfortify)
library(directlabels)
library(htmltools); library(htmlwidgets)
```

```{r, include = FALSE}
plot_surv <- function(survfit, data, xlim) {

  df <- fortify(survfit, data = data)

  if (missing(xlim)) {

    if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time")
          ggtitle("Survival Curve")
        }
    if ("strata" %in% names(df)) {
      ggplot(df, aes(x = time, y = surv, color = strata)) + 
        geom_line() + 
        scale_y_continuous("Survival Probabilities") +
        scale_x_continuous("Time") + 
        ggtitle("Survival Curves") + 
        geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
    }
  } else {

      if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time", limits = xlim)
          ggtitle("Survival Curve")
      }

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

```{r, echo = FALSE}
#matrix of tags (splitting up tags variable wherever there's a comma)
split_tags <- str_split(out_english$tags, ", ", simplify = TRUE)

#character vector of all tags (empty strings removed)
tag_vector <- as.vector(split_tags)
tag_vector <- tag_vector[which(tag_vector != "")]

unique_tags <- unique(tag_vector)
num_unique <- length(unique_tags)/length(tag_vector)

prop_notags <- sum(out_english$n_tags == 0)/nrow(out_english)
```

* create variable for incorrect tagging 
* create variable for popularity of tags (based off of average freq/popularity of tags)
* `r round(prop_notags*100, 2)`% of questions don't contain any tags
* `r round(num_unique*100, 2)`% of tags are unique

### avg_tag_length

* average length of tag for a question: total number of characters for all of a question's tags / number of tags the question has
* think that tags that are more concise (fewer characters) will have faster answer times

```{r, echo = FALSE}
#average tag length: 
out_english$avg_tag_length <- NA
not_na <- which(out_english$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  out_english$avg_tag_length[i] <- total_char / total_tags
}

ggplot(out_english, aes(x = avg_tag_length)) + 
  geom_histogram() + 
  scale_x_continuous("Average tag length for each question (characters)") + 
  ggtitle("Distribution of average tag lengths")

max_avg <- max(out_english$avg_tag_length, na.rm = TRUE)
min_avg <- min(out_english$avg_tag_length, na.rm = TRUE)
mean_length <- mean(out_english$avg_tag_length, na.rm = TRUE)
median_length <- median(out_english$avg_tag_length, na.rm = TRUE)
```

* longest average tag length: `r max_avg`
* shortest average tag length: `r min_avg`
* mean average tag length: `r mean_length`
* median average tag length: `r median_length`

##### average tag length grouped by product category 
```{r, echo = FALSE}
out_english %>%
  group_by(category) %>%
  summarise(avg_length = mean(avg_tag_length, na.rm = TRUE), median_length = median(avg_tag_length, na.rm = TRUE), n = n(), avg_views = mean(daily_views), median_time = median(time_until_answer)) %>%
  arrange(avg_length)
```

##### average tag length grouped by answered/unanswered questions
```{r, echo = FALSE}
out_english %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(avg_tag_length, na.rm = TRUE))
```

### frequency of tags (popularity)
```{r, echo = FALSE}

tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))

tag_freq <- tag_freq %>%
              arrange(desc(percent))

ggplot(tag_freq, aes(x = percent)) + 
  geom_histogram() + 
  ggtitle("Distribution of tag frequency")

top50 <- tag_freq[1:50,]
ggplot(top50, aes(x = fct_reorder(tag, -percent), y = percent)) + 
  geom_col() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("Distribution of top 50 tags and percentage of times they occur")
```

```{r, echo = FALSE}
#creating average frequency/popular score variable
out_english$tag1 <- split_tags[,1]
out_english$tag2 <- split_tags[,2]
out_english$tag3 <- split_tags[,3]
out_english$tag4 <- split_tags[,4]

assign_score <- function(data, variable) {
  score <- rep(0, nrow(data))
  notempty <- which(data[[variable]] != "")
  for (i in notempty) {
    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
  }
  return(score)
}

out_english$score1 <- assign_score(out_english, "tag1")
out_english$score2 <- assign_score(out_english, "tag2")
out_english$score3 <- assign_score(out_english, "tag3")
out_english$score4 <- assign_score(out_english, "tag4")

out_english$avg_score <- (out_english$score1 + out_english$score2 + out_english$score3 + out_english$score4)/out_english$n_tags
out_english$avg_score[is.nan(out_english$avg_score)] <- 0

ggplot(out_english, aes(x = avg_score)) + 
  geom_histogram() + 
  ggtitle("Distribution of average tag popularity/frequency scores")
```

#### Determining threshold for popular/unpopular tags

```{r, echo = FALSE}
median_score <- median(out_english$avg_score)
q_score <- quantile(out_english$avg_score, probs = seq(0, 1, by = 0.25))
percentile80 <- quantile(out_english$avg_score, probs = 0.80)

out_english$popular_tag <- FALSE
out_english$popular_tag[out_english$avg_score >= percentile80] <- TRUE

prop_popular <- sum(out_english$popular_tag)/sum(out_english$n_tags != 0)
```

* median average popularity/frequency score: `r median_score` 
* 75th percentile for scores: `r q_score[4]`
* popularity threshold based off of 80th percentile: `r percentile80`
* proportion of questions that contain a tag that are "popular": `r prop_popular`

##### Log-rank test

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
survdiff(surv_object ~ popular_tag, data = out_english)

KM_popular <- survfit(surv_object ~ popular_tag, data = out_english)
plot_surv(KM_popular, data = out_english)
```

### incorrect use of tags
* correct tags
    + don't begin with "#"
    + have no more than 3 words (?)
    + no spelling errors (ex: troubleshoot espressomaschine)
    + no punctuation marks (ex: !, ?, "", /) - since there are tags like: macbook pro 15", just one " is fine
    + should not end with a "."
    + doesn't contain links
    + if it contains numbers must also contain letters 
* regex
* look at probability a quesiton includes certain tag- chances it's answered (grab most frequent)
* maybe ignore tags that are also in device names
```{r, echo = FALSE}
out_english$correct_tag <- NA_character_
out_english$correct_tag[out_english$n_tags != 0] <- TRUE

#function to identify incorrect tagging, single tag taken as input
incorrect_tagging <- function(tag) {
  incorrect <- NA
  if (str_count(tag, pattern = "\\w+") > 3 |
      str_detect(tag, pattern = "[[:punct:]]") | 
      str_detect(tag, pattern = "^[[:digit:]]*$")) {
    incorrect <- TRUE 
  } else {
    incorrect <- FALSE
  }
  return(incorrect)
}

#function to assign t/f for incorrect tags
assign_incorrect <- function(tag_column) {
  new <- rep(NA, nrow(out_english))
  for (i in which(out_english[[tag_column]] != "")) {
    new[i] <- incorrect_tagging(out_english[[tag_column]][i])
  }
  return(new)
}

out_english$incorrect1 <- assign_incorrect("tag1")
out_english$incorrect2 <- assign_incorrect("tag2")
out_english$incorrect3 <- assign_incorrect("tag3")
out_english$incorrect4 <- assign_incorrect("tag4")

out_english$correctly_tag <- NA
out_english$correctly_tag[out_english$n_tags != 0] <- TRUE
notempty <- which(out_english$n_tags != 0)
for (k in notempty) {
  if (TRUE %in% c(out_english$incorrect1[k], out_english$incorrect2[k], out_english$incorrect3[k], out_english$incorrect4[k])) {
    out_english$correctly_tag[k] <- FALSE
  }
}

prop_correct <- sum(out_english$correctly_tag, na.rm = TRUE)/sum(out_english$n_tags != 0)
```

* out of all of the questions that contain tags, `r round(prop_correct * 100, 2)`% of them were tagged correctly

##### Log-rank test

```{r, echo = FALSE}
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
survdiff(surv_object ~ correctly_tag, data = out_english)

KM_correct <- survfit(surv_object ~ correctly_tag, data = out_english)
plot_surv(KM_correct, data = out_english)
```

### 2017-07-28 variable_exploration.Rmd
finished work with tags, updated hours, tweaked functions/other files

@@
 
-```{r, function to plot KM curves with ggplot, include = FALSE}
+```{r, functions, include = FALSE}
 #function to plot KM_curves with ggplot (use when it's hard to read ggsurvplot output)
+#takes survfit object, data set to work with, and optional x-axis limits as input, outputs ggplot KM curves
 
-plot_surv <- function(survfit, data, ...) {
+plot_surv <- function(survfit, data, xlim = NULL) {
   library(ggfortify)
@@
     }
+  } else {
+
+      if (!("strata" %in% names(df))) {
+        ggplot(df, aes(x = time, y = surv)) + 
+          geom_line() + 
+          scale_y_continuous("Survival Probability") +
+          scale_x_continuous("Time", limits = xlim)
+          ggtitle("Survival Curve")
       }
+
+      if ("strata" %in% names(df)) {
+        ggplot(df, aes(x = time, y = surv, color = strata)) + 
+          geom_line() + 
+          scale_y_continuous("Survival Probabilities") +
+          scale_x_continuous("Time", limits = xlim) + 
+          ggtitle("Survival Curves") + 
+          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+      }
+  }
+}
+
+#function to output logrank test and survival curves
+#takes in Surv object, data set, and categorical variable 
+# surv_analysis <- function(surv_object, group, data, xlim) {
+#   
+#   survdiff(surv_object ~ group, data)
+#   
+#   if (missing(xlim)) {
+#     KM <- survfit(surv_object ~ group, data)
+#     plot_surv(KM, data)
+#   } else {
+#     KM <- survfit(surv_object ~ group, data)
+#     plot_surv(KM, data, xlim)
+#   }
+# }
+# surv_analysis(surv_object, group = "category", data = out_english)
 

### 2017-07-31 Hours.Rmd
analyzed text, added to other files, updated hours

@@
 7/25/2017 | 3 | 1:00-4:00PM | Wrote the code for tag variables, tried to fix Java problem
-7/27/2017 | 7 | 12:00-7:00 | Met with the Data Specialist to discuss data visualization ideas, finished working with tags, started with textual features of the data
->> __Total Hours: 133.08__
+7/27/2017 | 7 | 12:00-7:00PM | Met with the Data Specialist to discuss data visualization ideas, finished working with tags, started with textual features of the data
+7/28/2017 | 10.5 | 10:30-9:00PM | Continued with textual features
+7/29/2017 | 4 | 5:00-9:00PM | Finished working with text, started on the datetime variable 
+7/30/2017 | 7 | 2:30-9:30| Finished datetime, finished all exploratory analyses, read articles from meeting with Data Specialist 
+>> __Total Hours: 1...__

### 2017-07-31 freq_words.Rmd
analyzed text, added to other files, updated hours

--- 2017-07-22 freq_words.Rmd
@@
 library(dplyr)
-out_english <- out %>% 
+x <- out %>% 
   tbl_df() %>%
@@
 
-out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
-empty <- which(is.na(out_english$time_until_answer))
+x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
+empty <- which(is.na(x$time_until_answer))
 for (i in empty) {
-  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
+  x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
 }
@@
 library(survival) 
-library(survminer)
-library(tidyverse)
 ```
@@
 
+  if (missing(xlim)) {
+
     if (!("strata" %in% names(df))) {
@@
           scale_y_continuous("Survival Probability") +
-    scale_x_continuous("Time")
+          scale_x_continuous("Time (hours)")
+          ggtitle("Survival Curve")
+        }
+    if ("strata" %in% names(df)) {
+      ggplot(df, aes(x = time, y = surv, color = strata)) + 
+        geom_line() + 
+        scale_y_continuous("Survival Probabilities") +
+        scale_x_continuous("Time (hours)") + 
+        ggtitle("Survival Curves") + 
+        geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+    }
+  } else {
+
+      if (!("strata" %in% names(df))) {
+        ggplot(df, aes(x = time, y = surv)) + 
+          geom_line() + 
+          scale_y_continuous("Survival Probability") +
+          scale_x_continuous("Time (hours)", limits = xlim)
           ggtitle("Survival Curve")
@@
           scale_y_continuous("Survival Probabilities") +
-      scale_x_continuous("Time") + 
+          scale_x_continuous("Time (hours)", limits = xlim) + 
           ggtitle("Survival Curves") + 
           geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
+      }
   }
@@
 ```{r, echo = FALSE}
-titles_freq <- freq_terms(out_english$title)
+titles_freq <- freq_terms(x$title)
 
@@
 
-ggplot(top50, aes(x = word, y = frequency/nrow(out_english))) + 
+ggplot(top50, aes(x = word, y = frequency/nrow(x))) + 
   geom_point() +
@@
 top10 <- titles_freq[1:10,]
-out_english$contain_top10 <- str_detect(as.character(out_english$title), pattern = or1(names(top10)))
-prop_contain <- sum(out_english$contain_top10)/nrow(out_english)
+x$contain_top10 <- str_detect(as.character(x$title), pattern = or1(names(top10)))
+prop_contain <- sum(x$contain_top10)/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(contain_top10) %>%
@@
 ```{r, echo = FALSE}
-surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
-survdiff(surv_object~contain_top10, data = out_english)
+surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
+survdiff(surv_object~contain_top10, data = x)
 ```
@@
 ```{r, echo = FALSE}
-surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
-KM_top10 <- survfit(surv_object ~ contain_top10, data = out_english)
-plot_surv(KM_top10, data = out_english)
+surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
+KM_top10 <- survfit(surv_object ~ contain_top10, data = x)
+plot_surv(KM_top10, data = x)
 ```
@@
 ```{r, echo = FALSE}
-answered <- out_english %>%
+answered <- x %>%
   tbl_df() %>% 
   filter(answered == 1)
-unanswered <- out_english %>%
+
+unanswered <- x %>%
   tbl_df() %>% 
@@
 ```{r, echo = FALSE}
-out_english$contain_u <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_u$word))
+x$contain_u <- str_detect(as.character(x$title), pattern = or1(freq_terms_u$word))
 
-prop_contain_u <- sum(out_english$contain_u)/nrow(out_english)
+prop_contain_u <- sum(x$contain_u)/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(contain_u) %>%
@@
 ```{r, echo = FALSE}
-survdiff(surv_object ~ contain_u, data = out_english)
+survdiff(surv_object ~ contain_u, data = x)
 ```
@@
 ```{r, echo = FALSE}
-KM_u <- survfit(surv_object ~ contain_u, data = out_english) 
-plot_surv(KM_u, data = out_english)
+KM_u <- survfit(surv_object ~ contain_u, data = x) 
+plot_surv(KM_u, data = x)
 ```
@@
 ```{r, echo = FALSE}
-out_english$contain_a <- str_detect(as.character(out_english$title), pattern = or1(freq_terms_a$word))
+x$contain_a <- str_detect(as.character(x$title), pattern = or1(freq_terms_a$word))
 
-prop_contain_a <- sum(out_english$contain_a)/nrow(out_english)
+prop_contain_a <- sum(x$contain_a)/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(contain_a) %>%
@@
 ```{r, echo = FALSE}
-survdiff(surv_object~contain_a, data = out_english)
+survdiff(surv_object~contain_a, data = x)
 ```
@@
 ```{r, echo = FALSE}
-KM_a <- survfit(surv_object ~ contain_a, data = out_english)
-plot_surv(KM_a, data = out_english)
+KM_a <- survfit(surv_object ~ contain_a, data = x)
+plot_surv(KM_a, data = x)
 ```
@@
 
-out_english$contain_u_dev <- str_detect(as.character(out_english$title), pattern = or1(unanswered_devices$word))
+x$contain_u_dev <- str_detect(as.character(x$title), pattern = or1(unanswered_devices$word))
 
-prop_contain_u_dev <- sum(out_english$contain_u_dev)/nrow(out_english)
+prop_contain_u_dev <- sum(x$contain_u_dev)/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-survdiff(surv_object ~ contain_u_dev, data = out_english)
+survdiff(surv_object ~ contain_u_dev, data = x)
 
-KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = out_english)
-plot_surv(KM_u_dev, data = out_english)
+KM_u_dev <- survfit(surv_object ~ contain_u_dev, data = x)
+plot_surv(KM_u_dev, data = x)
 ```
@@
 
-out_english$contain_dev_a <- str_detect(as.character(out_english$title), pattern = or1(answered_devices$word))
-prop_contain_a_dev <- sum(out_english$contain_dev_a)/nrow(out_english)
+x$contain_dev_a <- str_detect(as.character(x$title), pattern = or1(answered_devices$word))
+prop_contain_a_dev <- sum(x$contain_dev_a)/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-survdiff(surv_object ~ contain_dev_a, data = out_english)
+survdiff(surv_object ~ contain_dev_a, data = x)
 
-KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = out_english)
-plot_surv(KM_dev_a, data = out_english)
+KM_dev_a <- survfit(surv_object ~ contain_dev_a, data = x)
+plot_surv(KM_dev_a, data = x)
 ```

### 2017-07-31 summary_stats.Rmd
analyzed text, added to other files, updated hours

@@
 
-```{r, Importing and setting up the data , include = FALSE}
+```{r, include = FALSE}
 dir <- file.path(getwd(),"data")
@@
 library(survival)
+library(epiR)
 library(survminer)
-library(epiR)
 
-proportion_answered <- sum(out_english$answered)/nrow(out_english)
+proportion_answered <- sum(x$answered)/nrow(x)
 ```
@@
 
-* `r nrow(out_english)` observations
+* `r nrow(x)` observations
 * `r round(proportion_answered * 100, digits = 2)` % of questions were answered
@@
 
-```{r, time_until_answer, echo = FALSE}
-summary <- summary(out_english$time_until_answer)
+```{r, echo = FALSE}
+summary <- summary(x$time_until_answer)
 ```
 
-* **minimum:** `r round(min(out_english$time_until_answer), 2)` hrs
-* **maximum:** `r round(max(out_english$time_until_answer), 2)` hrs
-* **mean:** `r round(mean(out_english$time_until_answer), 2)` hrs
-* **median:** `r round(median(out_english$time_until_answer), 2)` hrs
+* **minimum:** `r round(min(x$time_until_answer), 2)` hrs
+* **maximum:** `r round(max(x$time_until_answer), 2)` hrs, `r round(max(x$time_until_answer)/24, 2)` days
+* **mean:** `r round(mean(x$time_until_answer), 2)` hrs, `r round(mean(x$time_until_answer)/24, 2)` days
+* **median:** `r round(median(x$time_until_answer), 2)` hrs
 * **first quartile:** `r round(summary[2], 2)`hrs
-* **third quartile:** `r round(summary[5], 2)` hrs
-* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs
+* **third quartile:** `r round(summary[5], 2)` hrs, `r round(summary[5]/24, 2)` days
+* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs, `r round((summary[5] - summary[2])/24, 2)` days
+* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions had been answered
+* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions had been answered
 
-```{r, distribution of response, echo = FALSE}
-ggplot(out_english, aes(x = time_until_answer)) + 
+```{r, echo = FALSE}
+ggplot(x, aes(x = time_until_answer)) + 
   geom_histogram(bins = 10) + 
@@
 ##### Survival Time Statistics based off of KM Estimator 
-```{r, survival analysis statistics, echo = FALSE}
-surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
+```{r, echo = FALSE}
+surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
 
@@
 * **Max survival probability:** `r round(max(s$surv), 2)`
-* **rmean survival time:** `r round(s$table[5], 2)` hrs
+* **rmean survival time:** `r round(s$table[5], 2)` hrs, `r round(s$table[5]/24, 2)` days
 * **SE of rmean:** `r round(s$table[6], 2)` hrs
@@
 ```{r, percentiles, echo = FALSE}
-quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.75))
+quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.64, 0.75))
 round(quant[[1]], 3)
@@
     + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
+    + highest quantile that exists: `r round(quant$quantile[6], 2)` hrs 64% of the questions have been answered
 
@@
 ```{r, survival curves, echo = FALSE}
-ggsurvplot(KM, data = out_english, risk.table = TRUE, xlab = "Time (hours)", main = "KM Curve")
-ggsurvplot(KM, data = out_english, risk.table = FALSE, xlab = "Time (hours)", main = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
+ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", main = "KM Curve")
+ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", main = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
+```
+
+##### Reversing the survival curves
+
+* at 100 hrs, the probability that a question is answered starts to level out at around ~0.63
+
+```{r, echo = FALSE}
+reversed <- data.frame(time = s$time, prob_ans = 1-s$surv)
+ggplot(reversed, aes(x = time, y = prob_ans)) + 
+  geom_line() + 
+  scale_x_continuous("Time (hours)", limits = c(0,100)) + 
+  scale_y_continuous("Probability a question is answered") + 
+  ggtitle("Probability a question is answered vs. time (hours)")
 ```
@@
 
-```{r, cumulative hazard, echo = FALSE}
+```{r, echo = FALSE}
 #KM estimator of cumulative hazard 

### 2017-07-31 tag_exploration.Rmd
analyzed text, added to other files, updated hours

@@
 
-```{r, include = FALSE}
+```{r, setting up the data, include = FALSE}
 dir <- file.path(getwd(),"data")
@@
 library(rebus)
-#library(qdap)
 library(forcats)
@@
 
-```{r, include = FALSE}
+```{r, functions, include = FALSE}
 plot_surv <- function(survfit, data, xlim) {
@@
           scale_y_continuous("Survival Probability") +
-          scale_x_continuous("Time")
+          scale_x_continuous("Time (hours)")
           ggtitle("Survival Curve")
@@
         scale_y_continuous("Survival Probabilities") +
-        scale_x_continuous("Time") + 
+        scale_x_continuous("Time (hours)") + 
         ggtitle("Survival Curves") + 
@@
           scale_y_continuous("Survival Probability") +
-          scale_x_continuous("Time", limits = xlim)
+          scale_x_continuous("Time (hours)", limits = xlim)
           ggtitle("Survival Curve")
@@
           scale_y_continuous("Survival Probabilities") +
-          scale_x_continuous("Time", limits = xlim) + 
+          scale_x_continuous("Time (hours)", limits = xlim) + 
           ggtitle("Survival Curves") + 
@@
 #matrix of tags (splitting up tags variable wherever there's a comma)
-split_tags <- str_split(out_english$tags, ", ", simplify = TRUE)
+split_tags <- str_split(x$tags, ", ", simplify = TRUE)
 
@@
 
-prop_notags <- sum(out_english$n_tags == 0)/nrow(out_english)
+prop_notags <- sum(x$n_tags == 0)/nrow(x)
 ```
@@
 #average tag length: 
-out_english$avg_tag_length <- NA
-not_na <- which(out_english$tags != "")
+x$avg_tag_length <- NA
+not_na <- which(x$tags != "")
 for (i in not_na) {
@@
   total_tags <- sum(as.vector(split_tags[i,]) != "")
-  out_english$avg_tag_length[i] <- total_char / total_tags
+  x$avg_tag_length[i] <- total_char / total_tags
 }
 
-ggplot(out_english, aes(x = avg_tag_length)) + 
+ggplot(x, aes(x = avg_tag_length)) + 
   geom_histogram() + 
@@
 
-max_avg <- max(out_english$avg_tag_length, na.rm = TRUE)
-min_avg <- min(out_english$avg_tag_length, na.rm = TRUE)
-mean_length <- mean(out_english$avg_tag_length, na.rm = TRUE)
-median_length <- median(out_english$avg_tag_length, na.rm = TRUE)
+max_avg <- max(x$avg_tag_length, na.rm = TRUE)
+min_avg <- min(x$avg_tag_length, na.rm = TRUE)
+mean_length <- mean(x$avg_tag_length, na.rm = TRUE)
+median_length <- median(x$avg_tag_length, na.rm = TRUE)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(category) %>%
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(as.factor(answered)) %>%
@@
 ### frequency of tags (popularity)
+
 ```{r, echo = FALSE}
-
 tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
@@
 #creating average frequency/popular score variable
-out_english$tag1 <- split_tags[,1]
-out_english$tag2 <- split_tags[,2]
-out_english$tag3 <- split_tags[,3]
-out_english$tag4 <- split_tags[,4]
+x$tag1 <- split_tags[,1]
+x$tag2 <- split_tags[,2]
+x$tag3 <- split_tags[,3]
+x$tag4 <- split_tags[,4]
 
@@
 
-out_english$score1 <- assign_score(out_english, "tag1")
-out_english$score2 <- assign_score(out_english, "tag2")
-out_english$score3 <- assign_score(out_english, "tag3")
-out_english$score4 <- assign_score(out_english, "tag4")
+x$score1 <- assign_score(x, "tag1")
+x$score2 <- assign_score(x, "tag2")
+x$score3 <- assign_score(x, "tag3")
+x$score4 <- assign_score(x, "tag4")
 
-out_english$avg_score <- (out_english$score1 + out_english$score2 + out_english$score3 + out_english$score4)/out_english$n_tags
-out_english$avg_score[is.nan(out_english$avg_score)] <- 0
+x$avg_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
+x$avg_score[is.nan(x$avg_score)] <- 0
 
-ggplot(out_english, aes(x = avg_score)) + 
+ggplot(x, aes(x = avg_score)) + 
   geom_histogram() + 
@@
 ```{r, echo = FALSE}
-median_score <- median(out_english$avg_score)
-q_score <- quantile(out_english$avg_score, probs = seq(0, 1, by = 0.25))
-percentile80 <- quantile(out_english$avg_score, probs = 0.80)
+median_score <- median(x$avg_score)
+q_score <- quantile(x$avg_score, probs = seq(0, 1, by = 0.25))
+percentile80 <- quantile(x$avg_score, probs = 0.80)
 
-out_english$popular_tag <- FALSE
-out_english$popular_tag[out_english$avg_score >= percentile80] <- TRUE
+x$popular_tag <- FALSE
+x$popular_tag[x$avg_score >= percentile80] <- TRUE
 
-prop_popular <- sum(out_english$popular_tag)/sum(out_english$n_tags != 0)
+prop_popular <- sum(x$popular_tag)/sum(x$n_tags != 0)
 ```
@@
 ```{r, echo = FALSE}
-surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
-survdiff(surv_object ~ popular_tag, data = out_english)
+surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
+survdiff(surv_object ~ popular_tag, data = x)
 
-KM_popular <- survfit(surv_object ~ popular_tag, data = out_english)
-plot_surv(KM_popular, data = out_english)
+KM_popular <- survfit(surv_object ~ popular_tag, data = x)
+plot_surv(KM_popular, data = x)
 ```
@@
 * maybe ignore tags that are also in device names
+
 ```{r, echo = FALSE}
-out_english$correct_tag <- NA_character_
-out_english$correct_tag[out_english$n_tags != 0] <- TRUE
+x$correct_tag <- NA_character_
+x$correct_tag[x$n_tags != 0] <- TRUE
 
@@
 assign_incorrect <- function(tag_column) {
-  new <- rep(NA, nrow(out_english))
-  for (i in which(out_english[[tag_column]] != "")) {
-    new[i] <- incorrect_tagging(out_english[[tag_column]][i])
+  new <- rep(NA, nrow(x))
+  for (i in which(x[[tag_column]] != "")) {
+    new[i] <- incorrect_tagging(x[[tag_column]][i])
   }
@@
 
-out_english$incorrect1 <- assign_incorrect("tag1")
-out_english$incorrect2 <- assign_incorrect("tag2")
-out_english$incorrect3 <- assign_incorrect("tag3")
-out_english$incorrect4 <- assign_incorrect("tag4")
+x$incorrect1 <- assign_incorrect("tag1")
+x$incorrect2 <- assign_incorrect("tag2")
+x$incorrect3 <- assign_incorrect("tag3")
+x$incorrect4 <- assign_incorrect("tag4")
 
-out_english$correctly_tag <- NA
-out_english$correctly_tag[out_english$n_tags != 0] <- TRUE
-notempty <- which(out_english$n_tags != 0)
+x$correctly_tag <- NA
+x$correctly_tag[x$n_tags != 0] <- TRUE
+notempty <- which(x$n_tags != 0)
 for (k in notempty) {
-  if (TRUE %in% c(out_english$incorrect1[k], out_english$incorrect2[k], out_english$incorrect3[k], out_english$incorrect4[k])) {
-    out_english$correctly_tag[k] <- FALSE
+  if (TRUE %in% c(x$incorrect1[k], x$incorrect2[k], x$incorrect3[k], x$incorrect4[k])) {
+    x$correctly_tag[k] <- FALSE
   }
@@
 
-prop_correct <- sum(out_english$correctly_tag, na.rm = TRUE)/sum(out_english$n_tags != 0)
+prop_correct <- sum(x$correctly_tag, na.rm = TRUE)/sum(x$n_tags != 0)
 ```
@@
 ```{r, echo = FALSE}
-surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
-survdiff(surv_object ~ correctly_tag, data = out_english)
+surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
+survdiff(surv_object ~ correctly_tag, data = x)
 
-KM_correct <- survfit(surv_object ~ correctly_tag, data = out_english)
-plot_surv(KM_correct, data = out_english)
+KM_correct <- survfit(surv_object ~ correctly_tag, data = x)
+plot_surv(KM_correct, data = x)
 ```
+
+### If a question contains top50 tags
+
+```{r, echo = FALSE}
+top50tag <- as.character(top50$tag)
+
+#function to check if tag in top50
+contain_tag <- function(tag, data) {
+  contain <- rep(NA, nrow(data))
+  for(i in which(data[[tag]] != "")) {
+    if (data[[tag]][i] %in% top50tag) {
+      contain[i] <- TRUE
+      } else {
+        contain[i] <- FALSE
+      }
+    }
+  return(contain)
+}
+
+containdf <- data.frame(c1 = contain_tag("tag1", data = x),
+                        c2 = contain_tag("tag2", data = x),
+                        c3 = contain_tag("tag3", data = x),
+                        c4 = contain_tag("tag4", data = x))
+
+x$contain_toptag <- rep(FALSE, nrow(x))
+for (j in which(!is.na(containdf$c1))) {
+  if (TRUE %in% containdf[j,]) {
+    x$contain_toptag[j] <- TRUE
+  } else {
+    x$contain_toptag[j] <- FALSE
+  }
+}
+
+prop_toptag <- sum(x$contain_toptag, na.rm = TRUE)/sum(!is.na(x$tags))
+```
+
+* `r round(prop_toptag*100, 2)`% of questions that contain tag, contain a tag that's in the top 50 tag list
+
+##### median time, prop answered and average daily views grouped by whether or not it contains a top50 tag
+```{r, echo = FALSE}
+x %>% 
+  group_by(contain_toptag) %>%
+  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n)
+```
+
+##### log-rank test 
+```{r, echo = FALSE}
+survdiff(surv_object ~ contain_toptag, data = x)
+KM_toptag <- survfit(surv_object ~ contain_toptag, data = x)
+plot_surv(KM_toptag, data = x)
+```
+
+### maximum number of words in a tag
+
+##### frequency table for number of words
+
+```{r, echo = FALSE}
+x$max_tagwords <- rep(NA, nrow(x))
+for (i in which(x$n_tags != 0)) {
+  tags <- as.vector(split_tags[i,])
+  x$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
+}
+
+#to find the mode
+Mode <- function(x) {
+  ux <- unique(x)
+  ux[which.max(tabulate(match(x, ux)))]
+}
+
+table(x$max_tagwords)
+```
+
+* max number of words in a tag: `r max(x$max_tagwords, na.rm = TRUE)`
+* median number of words: `r median(x$max_tagwords, na.rm = TRUE)`
+* mode number of words: `r Mode(subset(x$max_tagwords, !is.na(x$max_tagwords)))`
+
+##### Average number of max words in a tag grouped by answered/unanswered
+
+```{r, echo = FALSE}
+x %>%
+  group_by(answered) %>%
+  summarise(median_words = median(max_tagwords, na.rm = TRUE))
+```

### 2017-07-31 textual_analysis.Rmd
analyzed text, added to other files, updated hours

---
title: "Textual Features"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
x <- out %>% 
      tbl_df() %>%
      filter(langid == "en")

x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
empty <- which(is.na(x$time_until_answer))
for (i in empty) {
  x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
}

library(stringr)
library(rebus)
library(survival) 
library(ggplot2)
library(dplyr)
library(ggfortify)
library(directlabels)
library(openNLP)
```

```{r, include = FALSE}
#function to plot survival curves with ggplot
plot_surv <- function(survfit, data, xlim) {

  df <- fortify(survfit, data = data)

  if (missing(xlim)) {

    if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time (hours)")
          ggtitle("Survival Curve")
        }
    if ("strata" %in% names(df)) {
      ggplot(df, aes(x = time, y = surv, color = strata)) + 
        geom_line() + 
        scale_y_continuous("Survival Probabilities") +
        scale_x_continuous("Time (hours)") + 
        ggtitle("Survival Curves") + 
        geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
    }
  } else {

      if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time (hours)", limits = xlim)
          ggtitle("Survival Curve")
      }

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

* **question quality:** 
    + text speak: find corpus for text speak- presence/degree of presence/absence of text speak (lol, rofl, u, ur…)

### Length of sentence until first punctuation in text

```{r, echo = FALSE}
x$first_punct <- str_locate(x$text, pattern = "[.|,|?|!|;|:]")[,1]

max_pos <- max(x$first_punct, na.rm = TRUE)
min_pos <- min(x$first_punct, na.rm = TRUE)
mean_pos <- mean(x$first_punct, na.rm = TRUE)
median_pos <- median(x$first_punct, na.rm = TRUE)
prop_punct <- sum(!is.na(x$first_punct))/nrow(x)
```

* `r round(prop_punct*100, 2)`% of questions contain any punctuation marks (. , ? ! ; :)
* max position of first punc: `r max_pos`
* min position of first punc: `r min_pos`
* mean of first_punc: `r mean_pos`
* median of first_punc: `r median_pos`

```{r, echo = FALSE}
ggplot(x, aes(x = first_punct)) + 
  geom_histogram() + 
  ggtitle("Distribution of positions of first punctuation marks") + 
  scale_x_continuous("Position")
```

##### Average and median first_punc grouped by answered

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(avg_pos = mean(first_punct, na.rm = TRUE), median_pos = median(first_punct, na.rm = TRUE), n = n())
```

##### Average and median first_punct grouped by category

* notice that categories that have the shortest distance until first punctuation mark are also the categories who have the fastest time_until_answer values

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(avg_pos = mean(first_punct, na.rm = TRUE), median_pos = median(first_punct, na.rm = TRUE), n = n()) %>%
  arrange(median_pos)
```

### Whether or not the text contains punctuation

##### Median time_until_answer grouped by whether or not text contains punct

```{r, echo = FALSE}
x$contain_punct <- FALSE
x$contain_punct[!is.na(x$first_punct)] <- TRUE

x %>%
  group_by(contain_punct) %>%
  summarise(median_time = median(time_until_answer), n = n())
```

##### Proportion of answered/unanswered questions that contain punct

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_contain = sum(contain_punct)/n)
```

##### Proportion that contain punct grouped by categories

```{r}
x %>% 
  group_by(category) %>%
  summarise(n = n(), prop_contain = sum(contain_punct)/n, median_pos = median(first_punct, na.rm = TRUE)) %>% arrange(desc(prop_contain))
```

##### Log-rank test

```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
survdiff(surv_object ~ contain_punct, data = x)

KM_punct <- survfit(surv_object ~ contain_punct, data = x)
plot_surv(KM_punct, data = x)
```

### Whether or not the text ends in a punctuation mark

```{r, echo = FALSE}
x$end_punct <- str_detect(x$text, pattern = "[.|?|!]$")

prop_end <- sum(x$end_punct)/nrow(x)
```

* `r round(prop_end*100, 2)`% of question texts end with: . ! ?

##### Median time_until_answer grouped by whether or not text ends with punct

```{r, echo = FALSE}
x %>% 
  group_by(end_punct) %>%
  summarise(median_time = median(time_until_answer), n = n())
```

##### Proportion of answered/unanswered questions that end with punct

```{r, echo = FALSE}
x %>% 
  group_by(answered) %>%
  summarise(n = n(), prop_end = sum(end_punct)/n)
```

##### Proportion with end punct grouped by category

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(n = n(), prop_end = sum(end_punct)/n) %>%
  arrange(desc(prop_end))
```

##### Log-rank test
```{r, echo = FALSE}
survdiff(surv_object ~ end_punct, data = x)

KM_end <- survfit(surv_object ~ end_punct, data = x)
plot_surv(KM_end, data = x)
```

### Does the title contain a question mark

```{r, question mark, echo = FALSE}
x$contain_question <- str_detect(x$title, pattern = QUESTION)

prop_contain <- sum(x$contain_question)/nrow(x)

true <- x %>% 
  filter(contain_question == T)
prop_answered <- sum(true$answered)/nrow(true)
```
* `r round(prop_contain * 100, 2)`% of questions contain a question mark
* `r round(prop_answered * 100, 2)`% of questions with a question mark were answered

##### median time grouped by whether or not title contains: '?'

```{r, echo = FALSE}
x %>%
  group_by(contain_question) %>%
  summarise(median_time = median(time_until_answer), n = n()) %>%
  arrange(median_time)
```

* indicates that questions with a '?' tend to have shorter answer times than questions without

##### proportion of questions with '?' and median time grouped by category

```{r, echo = FALSE}
x %>% 
  group_by(category) %>%
  summarise(n = n(), proportion_with_question = sum(contain_question)/n, median_time = median(time_until_answer)) %>%
  arrange(desc(proportion_with_question))
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ contain_question, data = x)
KM_question <- survfit(surv_object ~ contain_question, data = x)
plot_surv(KM_question, data = x)
```

### If title begins with "Wh"

```{r, echo = FALSE}
x$begin_wh <- str_detect(str_to_lower(x$title), pattern = "^wh")

prop_beginwh <- sum(x$begin_wh)/nrow(x)
```

* `r round(prop_beginwh*100, 2)`% of titles begin with "wh"

##### median time and proportion answered grouped by begin_wh
```{r, echo = FALSE}
x %>%
  group_by(begin_wh) %>%
  summarise(median_time = median(time_until_answer), n = n(), prop_answered = sum(answered)/n)
```

##### log-rank test
```{r, echo = FALSE}
survdiff(surv_object ~ begin_wh, data = x)
KM_wh <- survfit(surv_object ~ begin_wh, data = x)
plot_surv(KM_wh, data = x)
```

### If first letter of title is capitalized

```{r, echo = FALSE}
x$capital_title <- str_detect(x$title, pattern = "^[[:upper:]]")

prop_titlec <- sum(x$capital_title)/nrow(x)
```

* `r round(prop_titlec*100, 2)`% of titles have the first letter capitalized

##### Log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ capital_title, data = x)
KM_titlecaps <- survfit(surv_object ~ capital_title, data = x)
plot_surv(KM_titlecaps, data = x)
```

### If first letter of text is capitalized
```{r, echo = FALSE}
x$capital_text <- str_detect(x$text, pattern = "^[[:upper:]]")

prop_captext <- sum(x$capital_text)/nrow(x)
```

* `r round(prop_captext*100, 2)`% of texts has the first letter capitalized

##### Proportion in answered/unanswered questions with capital letter in text
```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_capital = sum(capital_text)/n)
```

##### Log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ capital_text, data = x)
KM_textcaps <- survfit(surv_object ~ capital_text, data = x)
plot_surv(KM_textcaps, data = x)
```

### Checking if text is in single caps (all lower or upper case)

* since there are no questions with text in all caps, will only search for all lower case
```{r, echo = FALSE}
x$removed <- str_replace_all(x$text, " ", "")
x$removed <- str_replace_all(x$removed, "[[:punct:]]|[[:digit:]]", "")

x$all_lower <- str_detect(x$removed, pattern = "^[[:lower:]]+$")
x <- x[,-which(names(x) == "removed")]

prop_allLower <- sum(x$all_lower)/nrow(x)
```

* `r round(prop_allLower*100, 2)`% of questions contain text thats all lower case
* this is such a small proportion of questions can we still consider it significant?

##### Proportion all lower case grouped by answered/unanswered

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_allLower = sum(all_lower)/n)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ all_lower, data = x)
KM_lower <- survfit(surv_object ~ all_lower, data = x)
plot_surv(KM_lower, data = x)
```

### Searching for words that indicate prior effort in the text variable

```{r, tried, echo = FALSE}
x$prior_effort <- str_detect(str_to_lower(x$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
prop_effort <- sum(x$prior_effort)/nrow(x)
```

* `r round(prop_effort * 100, 2)`% of questions contain terms indicating prior effort

##### median time/average daily views grouped by whether or not question contains "tried"/"searched"
```{r, echo = FALSE}
x %>%
  group_by(prior_effort) %>%
  summarise(median_time = median(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

##### proportion within answered/unanswered questions that indicate prior effort

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_indicateeffort = sum(prior_effort)/n) 
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ prior_effort, data = x)
KM_effort <- survfit(surv_object ~ prior_effort, data = x)
plot_surv(KM_effort, data = x)
```

### Do manners matter when asking a question?

```{r, echo = FALSE}
x$gratitude <- str_detect(str_to_lower(x$text), pattern = or("please", "thank you", "thanks", "thankful", "appreciate", "appreciated", "grateful"))

prop_thanks <- sum(x$gratitude)/nrow(x)
```

* `r round(prop_thanks*100,2)`% of questions contain words that express gratitude/manners

##### Median time grouped by whether or not gratitude is expressed

```{r, echo = FALSE}
x %>%
  group_by(gratitude) %>%
  summarise(median_time = median(time_until_answer))
```

##### proportion in answered/unanswered questions that express gratitude

```{r, echo = FALSE}
x %>% 
  group_by(answered) %>%
  summarise(n = n(), prop_gratitude = sum(gratitude)/n)
```

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ gratitude, data = x)
KM_gratitude <- survfit(surv_object ~ gratitude, data = x)
plot_surv(KM_gratitude, data = x)
```

### Does greeting people matter? (presence of "hi")

```{r, echo = FALSE}
x$greeting <- str_detect(str_to_lower(x$text), pattern = START %R% or("hey", "hello", "greetings", "hi"))

prop_greet <- sum(x$greeting)/nrow(x)
```

* `r round(prop_greet*100, 2)`% of questions include greetings

##### log-rank test

```{r, echo = FALSE}
survdiff(surv_object ~ greeting, data = x)
KM_greet <- survfit(surv_object ~ greeting, data = x)
plot_surv(KM_greet, data = x)
```

### Ratio of sentences to question length (number of characters)

* figure out how to deal with "..." and "???" "!!!"
* observation 2247 is funky 
* is it worth it to even consider sentence count?

```{r, echo = FALSE}
x$cleaned <- str_replace_all(as.character(x$text), "\\(.*?\\)", " ")
x$cleaned <- str_replace_all(x$cleaned, "\\[.*?\\]", " ")
x$cleaned <- str_replace_all(x$cleaned, "\\{.*?\\}", " ")
x$cleaned <- str_replace_all(x$cleaned, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)", " ")
x$cleaned <- str_replace_all(x$cleaned, "([_+a-z0-9-]+(\\.[_+a-z0-9-]+)*@[a-z0-9-]+(\\.[a-z0-9-]+)*(\\.[a-z]{2,14}))", " ")
x$cleaned <- str_replace_all(str_to_lower(x$cleaned), ".com", " ")

x$count <- rep(0, nrow(x))
for (i in 1:nrow(x)) {
  text_split <- as.vector(str_split(x$cleaned[i], pattern = "[.|?|!]", simplify = TRUE))
  text_split <- text_split[which(text_split != "")]
  x$count[i] <- length(text_split)
}

ggplot(x, aes(x = count)) + 
  geom_histogram() + 
  ggtitle("Distribution of number of sentences contained in text") + 
  scale_x_continuous("Sentence Count")

max_count <- max(x$count)
min_count <- min(x$count)
mean_count <- mean(x$count)
median_count <- median(x$count)
prop_one <- sum(x$count == 1)/nrow(x)
```

* max number of sentences: `r max_count`
* minimum number of sentences: `r min_count`
* mean count: `r mean_count`
* median count: `r median_count`
* `r round(prop_one*100, 2)`% of texts have only 1 sentence

### 2017-07-31 variable_exploration.Rmd
analyzed text, added to other files, updated hours

--- 2017-07-22 variable_exploration.Rmd
@@
 library(survival)
-library(survminer)
 library(epiR)
@@
 
-```{r, category1, echo = FALSE}
-categories <- out_english %>%
+```{r, echo = FALSE}
+x %>%
   group_by(category) %>%
@@
   arrange(desc(n))
-categories
 ```
@@
 
-```{r, category2, echo = FALSE}
-sorted <- out_english %>% 
+```{r, echo = FALSE}
+sorted <- x %>% 
   group_by(category) %>%
-            summarise(n = n(), avg_time = mean(time_until_answer), median_time = median(time_until_answer)) %>%
+  summarise(n = n(), avg_time = mean(time_until_answer), median_time = median(time_until_answer), median_views = median(daily_views)) %>%
   arrange(median_time)
@@
 
-```{r, category3, echo = FALSE}
+```{r, echo = FALSE}
+surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
 
-surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
-
-survdiff(surv_object~category, data = out_english)
+survdiff(surv_object~category, data = x)
+KM_category <- survfit(surv_object~category, data = x)
+plot_surv(KM_category, data = x)
+```
+##### zoomed in 
+```{r, echo = FALSE}
+plot_surv(KM_category, data = x, xlim = c(0,100))
 ```
 
-##### survival curves
+##### Is there a difference between iphone and android users?
 
 ```{r, echo = FALSE}
-KM_category <- survfit(surv_object~category, data = out_english)
-
-plot_surv(KM_category, data = out_english)
+x %>% 
+  filter(subcategory == c("iPhone", "Android Phone")) %>%
+  group_by(subcategory) %>%
+  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views))
 ```
@@
 
-```{r, categorized correctly?, echo = FALSE}
-prop_incorrect <- sum(is.na(out_english$category))/nrow(out_english)
+```{r, echo = FALSE}
+prop_incorrect <- sum(is.na(x$category))/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-out_english$categorized <- 0
-out_english$categorized[!is.na(out_english$category)] <- 1
+x$categorized <- 0
+x$categorized[!is.na(x$category)] <- 1
 
-survdiff(surv_object~categorized, data = out_english)
+survdiff(surv_object~categorized, data = x)
 ```
@@
 ```{r, echo = FALSE}
-KM_correct <- survfit(surv_object ~ as.factor(categorized), data = out_english)
-plot_surv(KM_correct, data = out_english, xlim = c(0,100))
-```
-
-### Does the title contain a question mark
-
-```{r, question mark, echo = FALSE}
-out_english$contain_question <- str_detect(out_english$title, pattern = QUESTION)
-
-prop_contain <- sum(out_english$contain_question)/nrow(out_english)
-
-true <- out_english %>% 
-  filter(contain_question == T)
-prop_answered <- sum(true$answered)/nrow(true)
-```
-* `r round(prop_contain * 100, 2)`% of questions contain a question mark
-* `r round(prop_answered * 100, 2)`% of questions with a question mark were answered
-
-##### median time grouped by whether or not question contains: '?'
-
-```{r, echo = FALSE}
-out_english %>%
-  group_by(contain_question) %>%
-  summarise(median_time = median(time_until_answer), n = n()) %>%
-  arrange(median_time)
-```
-
-* indicates that questions with a '?' tend to have shorter answer times than questions without
-
-##### proportion of questions with '?' and median time grouped by category
-
-```{r, echo = FALSE}
-c <- out_english %>% 
-    group_by(category) %>%
-    summarise(n = n(), proportion_with_question = sum(contain_question)/n, median_time = median(time_until_answer)) %>%
-    arrange(desc(proportion_with_question))
-c
-```
-
-* **categories with highest proportion of questions containing question marks:** `r as.character(c$category[1:5])`
-
-##### log-rank test
-
-```{r, echo = FALSE}
-survdiff(surv_object ~ contain_question, data = out_english)
-```
-
-##### survival curves
-
-```{r, echo = FALSE}
-KM_question <- survfit(surv_object ~ contain_question, data = out_english)
-plot_surv(KM_question, data = out_english)
-```
-
-### Searching for "tried" and "searched" in the text variable
-```{r, tried, echo = FALSE}
-out_english$tried <- str_detect(as.character(out_english$text), pattern = or("tried", "searched"))
-prop_tried <- sum(out_english$tried)/nrow(out_english)
-```
-
-* `r round(prop_tried * 100, 2)`% of questions contain either "tried" or "searched"
-
-##### median time/average daily views grouped by whether or not question contains "tried"/"searched"
-```{r, echo = FALSE}
-out_english %>%
-  group_by(tried) %>%
-  summarise(median_time = median(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
-  arrange(median_time)
-```
-
-##### log-rank test
-
-```{r, echo = FALSE}
-survdiff(surv_object ~ as.factor(tried), data = out_english)
-```
-
-##### survival curves
-
-```{r, echo = FALSE}
-KM_tried <- survfit(surv_object ~ as.factor(tried), data = out_english)
-
-plot_surv(KM_tried, data = out_english)
+KM_correct <- survfit(surv_object ~ as.factor(categorized), data = x)
+plot_surv(KM_correct, data = x, xlim = c(0,100))
 ```
@@
 ```{r, title length, echo = FALSE}
-out_english$title_length <- str_length(out_english$title)
+x$title_length <- str_length(x$title)
 
-ggplot(out_english, aes(x = title_length)) + 
+ggplot(x, aes(x = title_length)) + 
   geom_histogram() + 
@@
   ggtitle("Distribution of Title Lengths")
-```
 
-```{r, echo = FALSE}
-sum_length <- summary(out_english$title_length)
+sum_length <- summary(x$title_length)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(as.factor(answered)) %>%
-  summarise(avg_length = mean(title_length), n = n())
+  summarise(avg_titlelength = mean(title_length), median_titlelength = median(title_length), n = n())
 ```
@@
 
-```{r, text length, echo = FALSE}
-out_english$text_length <- str_length(out_english$text)
+```{r, echo = FALSE}
+x$text_length <- str_length(x$text)
 
-ggplot(out_english, aes(x = text_length)) + 
+ggplot(x, aes(x = text_length)) + 
   geom_histogram() + 
@@
 
-sum_text <- summary(out_english$text_length)
+sum_text <- summary(x$text_length)
 ```
@@
 
-### Device length
+### Device name length
 
 ```{r, device length, echo = FALSE}
-out_english$device_length <- str_length(out_english$device)
+x$device_length <- str_length(x$device)
 
-ggplot(out_english, aes(x = device_length)) + 
+ggplot(x, aes(x = device_length)) + 
   geom_histogram() + 
@@
 
-sum_device <- summary(out_english$device_length)
+sum_device <- summary(x$device_length)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(category) %>%
-  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n()) %>%
+  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n(), median_time = median(time_until_answer)) %>%
   arrange(desc(avg_length))
@@
 
-* n_tags included in questions: `r unique(out_english$n_tags)`
-```{r, number tags, echo = FALSE}
-prop_notags <- sum(out_english$n_tags == 0)/nrow(out_english)
+* n_tags included in questions: `r unique(x$n_tags)`
+```{r, echo = FALSE}
+prop_notags <- sum(x$n_tags == 0)/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-round(prop.table(table(out_english$n_tags)), 3)
+round(prop.table(table(x$n_tags)), 3)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>%
+x %>%
   group_by(as.factor(n_tags)) %>%
-  summarise(n = n(), median_time = median(time_until_answer), proportion_answered = sum(answered)/n) %>%
+  summarise(n = n(), median_time = median(time_until_answer), proportion_answered = sum(answered)/n, median_views = median(daily_views)) %>%
   arrange(median_time)
@@
 ```{r, echo = FALSE}
-survdiff(surv_object ~ as.factor(n_tags), data = out_english)
-```
-
-##### survival curves
-
-```{r, echo = FALSE}
-KM_tags <- survfit(surv_object~as.factor(n_tags), data = out_english)
-plot_surv(KM_tags, data = out_english)
+survdiff(surv_object ~ as.factor(n_tags), data = x)
+KM_tags <- survfit(surv_object~as.factor(n_tags), data = x)
+plot_surv(KM_tags, data = x)
 ```
@@
 ```{r, echo = FALSE}
-prop_hasimage <- sum(out_english$n_images != 0)/nrow(out_english)
+prop_hasimage <- sum(x$n_images != 0)/nrow(x)
 ```
@@
 
-```{r, number images, echo = FALSE}
-table(out_english$n_images)
+```{r, echo = FALSE}
+table(x$n_images)
 ```
@@
 ```{r, echo = FALSE}
-out_english$pic_included <- 0
-out_english$pic_included[out_english$n_images != 0] <- 1
+x$pic_included <- 0
+x$pic_included[x$n_images != 0] <- 1
 
-out_english %>%
+x %>%
   group_by(as.factor(pic_included)) %>%
-  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n) %>%
+  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n, median_views = median(daily_views)) %>%
   arrange(desc(proportion_answered))
@@
 ```{r, echo = FALSE}
-survdiff(surv_object ~ as.factor(pic_included), data = out_english)
-```
-
-##### survival curves
-
-```{r, echo = FALSE}
-KM_pic <- survfit(surv_object~as.factor(pic_included), data = out_english)
-plot_surv(KM_pic, data = out_english)
+survdiff(surv_object ~ as.factor(pic_included), data = x)
+KM_pic <- survfit(surv_object~as.factor(pic_included), data = x)
+plot_surv(KM_pic, data = x)
 ```
@@
 ```{r, echo = FALSE}
-prop_new <- sum(out_english$new_user)/nrow(out_english)
+prop_new <- sum(x$new_user)/nrow(x)
 ```
@@
 ```{r, echo = FALSE}
-out_english %>% 
+x %>% 
   group_by(as.factor(new_user)) %>%
@@
 ```{r, echo = FALSE}
-survdiff(surv_object ~ as.factor(new_user), data = out_english)
-```
-
-##### survival curves
-
-```{r, echo = FALSE}
-KM_new <- survfit(surv_object~as.factor(new_user), data = out_english)
-plot_surv(KM_new, data = out_english)
+survdiff(surv_object ~ as.factor(new_user), data = x)
+KM_new <- survfit(surv_object~as.factor(new_user), data = x)
+plot_surv(KM_new, data = x)
 ```
@@
 
-```{r, echo = FALSE}
-ggplot(out_english, aes(x = daily_views)) + 
-  geom_histogram() + 
-  scale_x_continuous("Average daily views for a question") + 
-  ggtitle("Distribution of Daily Views")
+* **max average daily views for a question:** `r max(x$daily_views)`
+* **min average daily views for a question:** `r min(x$daily_views)`
+* **mean:** `r round(mean(x$daily_views), 2)`
+* **median:** `r round(median(x$daily_views), 2)`
+
+### Looking at when the question was posted
+
+* unix time stamp: seconds since Jan 01 1970. (UTC)
+
+```{r}
+x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
+x$post_d <- format(x$post_datetime, "%m/%d/%y")
+x$post_time <- format(x$post_datetime, " %H:%M:%S")
+x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
+x$post_hour <- as.numeric(format(x$post_datetime,"%H"))
+
+x$post_ampm <- "Night"
+x$post_ampm[x$post_hour >= 5 & x$post_hour < 12] <- "Morning"
+x$post_ampm[x$post_hour >= 12 & x$post_hour < 17] <- "Afternoon" #noon - 5pm 
+x$postampm[x$post_hour >= 17 & x$post_hour < 20] <- "Evening" #5pm - 8pm
+
+posn_d <- position_dodge(width = 0.2)
+ggplot(x, aes(x = post_weekday, fill = as.factor(answered))) + 
+  geom_bar(position = posn_d, alpha = 0.6) + 
+  scale_y_continuous("Number of Questions") +
+  ggtitle("Distribution of questions posted over a week")
+
+library(gridExtra)
+
+ggplot(x, aes(x = post_hour)) + 
+  geom_bar() + 
+  scale_y_continuous("Number of Questions") + 
+  ggtitle("Distribution of all questions posted over a day") + 
+  scale_x_continuous("Hour of the Day", breaks = seq(0, 23, by = 1))
+
+ggplot(x, aes(x = post_hour, fill = as.factor(answered))) + 
+  geom_bar(position = posn_d, alpha = 0.6) + 
+  scale_y_continuous("Number of Questions") + 
+  ggtitle("Distribution of questions posted over a day, grouped by answered/unanswered") +
+  scale_x_continuous("Hour of the Day", breaks = seq(0, 23, by = 1))
 ```
 
-* **max average daily views for a question:** `r max(out_english$daily_views)`
-* **min average daily views for a question:** `r min(out_english$daily_views)`
-* **mean:** `r round(mean(out_english$daily_views), 2)`
-* **median:** `r round(median(out_english$daily_views), 2)`
-
-##### median daily view and median time grouped by category
+##### Median time grouped by day of the week
 
 ```{r, echo = FALSE}
-out_english %>%
-  group_by(category) %>%
-  summarise(median_views = median(daily_views), n = n(), median_time = median(time_until_answer)) %>%
-  arrange(desc(median_views))
+x %>%
+  group_by(post_weekday) %>%
+  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n) %>%
+  arrange(median_time)
 ```
 
-##### median daily views and time grouped by n_tags
+##### Median time/avg views/prop answered grouped by hour
 
 ```{r, echo = FALSE}
-out_english %>%
-  group_by(as.factor(n_tags)) %>%
-  summarise(median_views = median(daily_views), median_time = median(time_until_answer), n = n()) %>%
-  arrange(desc(median_views))
+x %>%
+  group_by(as.factor(post_hour)) %>%
+  summarise(n = n(), median_time = median(time_until_answer), avg_views = mean(daily_views), prop_answered = sum(answered)/n) %>%
+  arrange(median_time)
+
 ```
 
-##### median daily views and time grouped by whether or not image included
+##### Median time grouped by morning/afternoon
 
 ```{r, echo = FALSE}
-out_english %>%
-  group_by(as.factor(pic_included)) %>%
-  summarise(median_views = median(daily_views), median_time = median(time_until_answer), n = n())
+x %>%
+  group_by(post_ampm) %>%
+  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n)
 ```
+
+##### log-rank test + survival curves for weekday
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ post_weekday, data = x)
+KM_weekday <- survfit(surv_object ~ post_weekday, data = x)
+plot_surv(KM_weekday, data = x)
+```
+
+##### log-rank test and survival curves for ampm
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ post_ampm, data = x)
+KM_ampm <- survfit(surv_object ~ post_ampm, data = x)
+plot_surv(KM_ampm, data = x)
+```
+
+### Looking at when answers are posted
+
+```{r, echo = FALSE}
+x$ans_datetime <- as.POSIXct(x$first_answer_date, origin="1970-01-01")
+x$ans_d <- format(x$ans_datetime, "%m/%d/%y")
+x$ans_time <- format(x$ans_datetime, " %H:%M:%S")
+x$ans_weekday <- factor(weekdays(x$ans_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
+x$ans_hour <- as.numeric(format(x$ans_datetime,"%H"))
+
+ggplot(subset(x, !is.na(ans_weekday)), aes(x = ans_weekday)) + 
+  geom_bar() + 
+  ggtitle("Distribution of answers posted over a week")
+
+plot1 <- ggplot(x, aes(x = post_hour)) + 
+  geom_bar() + 
+  ggtitle("Distribution of questions posted over a day") +
+  scale_x_continuous("Hour of the Day", breaks = seq(0, 23, by = 1))
+
+plot2 <- ggplot(subset(x, !is.na(ans_weekday)), aes(x = ans_hour)) + 
+  geom_bar() + 
+  ggtitle("Distribution of answers posted over a day") + 
+  scale_x_continuous("Hour of the Day", breaks = seq(0, 23, by = 1))
+
+grid.arrange(plot1, plot2, nrow=2, ncol=1)
+```

### 2017-08-03 Hours.Rmd
started fitting CR model, reorganized/added to files, updated hours

@@
 7/30/2017 | 7 | 2:30-9:30| Finished datetime, finished all exploratory analyses, read articles from meeting with Data Specialist 
+7/31/2017 | 2 | 10:00-12:00PM | Organized stuff, started thinking about the model 
+7/31/2017 | 2 | 3:00-5:00PM | Text mining and wordclouds on iPhone and Android Phone subcategories 
+8/1/2017 | 3.5 | 12:00-3:30PM | Started the process of fitting the model 
+8/1/2017 | 3 | 5:30-8:30PM | Organized/added to files
+8/2/2017 | 5 | 1:15-6:15PM | Fitted CR models, changes summary_stats files..
 >> __Total Hours: 1...__

### 2017-08-03 freq_words.Rmd
started fitting CR model, reorganized/added to files, updated hours

@@
 clean_corpus <- function(corpus){
-  library(tm)
   corpus <- tm_map(corpus, stripWhitespace)
@@
 freq_terms <- function(vec, n = NULL) {
-  library(qdap)
-  library(tm)
   source <- VectorSource(vec)
@@
 
-  if (is.null(n)) {
+  if (missing(n)) {
     return(freq_df)
   }
-  else if (!is.null(n)) {
+  else {
     return(freq_df[1:n,])
@@
 }
+
+#produces summary stats grouped by variable 
+sum_stats <- function(variable, data) {
+  tbl <- x %>%
+    group_by(data[[variable]]) %>%
+    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
+    arrange(median_time)
+  names(tbl)[1] <- variable
+  return(tbl)
+}
 ```
@@
   ggtitle("Distribution of word frequencies")
-```
 
-```{r, echo = FALSE}
 top50 <- titles_freq[1:50,]
@@
 
-ggplot(top50, aes(x = word, y = frequency/nrow(x))) + 
+library(forcats)
+
+ggplot(top50, aes(x = fct_reorder(word, -frequency), y = frequency/nrow(x))) + 
   geom_point() +
@@
 ```{r, echo = FALSE}
-x %>%
-  group_by(contain_top10) %>%
-  summarise(median_time = median(time_until_answer), 
-            avg_daily = mean(daily_views), n = n()) %>%
-  arrange(median_time)
+sum_stats("contain_top10", data = x)
 ```
@@
 survdiff(surv_object~contain_top10, data = x)
-```
 
-```{r, echo = FALSE}
-surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
 KM_top10 <- survfit(surv_object ~ contain_top10, data = x)
@@
 
-##### median answer time and average daily views grouped by whether or not question contains at least 1 uanswered term
+##### summary stats for contain_u
 
 ```{r, echo = FALSE}
-x %>%
-  group_by(contain_u) %>%
-  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
-  arrange(median_time)
+sum_stats("contain_u", data = x)
 ```
@@
 survdiff(surv_object ~ contain_u, data = x)
-```
-
-```{r, echo = FALSE}
 KM_u <- survfit(surv_object ~ contain_u, data = x) 
@@
 
-##### median answer time and average daily views grouped by whether or not question contains at least 1 answered term
+##### summary stats for contain_a
 
 ```{r, echo = FALSE}
-x %>%
-  group_by(contain_a) %>%
-  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
-  arrange(median_time)
+sum_stats("contain_a", data = x)
 ```
@@
 survdiff(surv_object~contain_a, data = x)
-```
-
-```{r, echo = FALSE}
 KM_a <- survfit(surv_object ~ contain_a, data = x)

### 2017-08-03 model_fitting.Rmd
started fitting CR model, reorganized/added to files, updated hours

---
title: "Model Fitting"
author: "Lisa Oshita"
date: "8/1/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
x <- out %>% 
  tbl_df() %>%
  filter(langid == "en")

x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
empty <- which(is.na(x$time_until_answer))
for (i in empty) {
  x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
}

library(stringr)
library(rebus)
library(survival) 
```

```{r, include = FALSE}
#function to get AIC statistics
get_aic <- function(cr_obj, num_parameters, data) {
  aic <- (-2*cr_obj$loglik[2]) + (2*num_parameters)
  return(aic)
}

#function to calculate r-square adjusted
get_r2adj <- function(cr_obj)
```

```{r, include = FALSE}
#changing NA's in category to other
x$category <- as.character(x$category)
x$category[is.na(x$category)] <- "Other"
x$category <- as.factor(x$category)

#pic included
x$pic_included <- 0
x$pic_included[x$n_images != 0] <- 1

#text_length
x$text_length <- str_length(x$text)

#title length
x$title_length <- str_length(x$title)

#device name length
x$device_length <- str_length(x$device)

#posting times
x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
x$post_d <- format(x$post_datetime, "%m/%d/%y")
x$post_time <- format(x$post_datetime, " %H:%M:%S")
x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
x$post_hour <- as.numeric(format(x$post_datetime,"%H"))

x$post_ampm <- "Night"
x$post_ampm[x$post_hour >= 5 & x$post_hour < 12] <- "Morning"
x$post_ampm[x$post_hour >= 12 & x$post_hour < 17] <- "Afternoon" #noon - 5pm 
x$postampm[x$post_hour >= 17 & x$post_hour < 20] <- "Evening" #5pm - 8pm

#whether or not it was cateogorized correctly
x$categorized <- 0
x$categorized[!is.na(x$category)] <- 1

#length of sentence till first punctuation mark 
x$first_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]

#if text contains punct
x$contain_punct <- FALSE
x$contain_punct[!is.na(x$first_punct)] <- TRUE

#if the text ends in a punctuation
x$end_punct <- str_detect(x$text, pattern = "[.|?|!]$")

#if the title ends in a question mark
x$contain_question <- str_detect(x$title, pattern = QUESTION %R% END)

#leaving out if title begins with "wh" (should i check if text is significant tho)
#if first letter of title is capitalized
x$capital_title <- str_detect(x$title, pattern = "^[[:upper:]]")

#if first letter of text is capitalized
x$capital_text <- str_detect(x$text, pattern = "^[[:upper:]]")

#if text is in all lower case
x$removed <- str_replace_all(x$text, " ", "")
x$removed <- str_replace_all(x$removed, "[[:punct:]]|[[:digit:]]", "")

x$all_lower <- str_detect(x$removed, pattern = "^[[:lower:]]+$")
x <- x[,-which(names(x) == "removed")]

#prior effort
x$prior_effort <- str_detect(str_to_lower(x$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))

#gratitude 
x$gratitude <- str_detect(str_to_lower(x$text), pattern = or("please", "thank you", "thanks", "thankful", "appreciate", "appreciated", "grateful"))

#greeting
x$greeting <- str_detect(str_to_lower(x$text), pattern = START %R% or("hey", "hello", "greetings", "hi"))

#update?
x$update <- str_detect(x$text, pattern = "===")

#tags
#indicator variable for tags/no tags included
x$tag_included <- 0
x$tag_included[x$n_tags != 0] <- 1

#matrix of tags (splitting up tags variable wherever there's a comma)
split_tags <- str_split(x$tags, ", ", simplify = TRUE)

#character vector of all tags (empty strings removed)
tag_vector <- as.vector(split_tags)
tag_vector <- tag_vector[which(tag_vector != "")]

unique_tags <- unique(tag_vector)

#average tag length
x$avg_tag_length <- NA
not_na <- which(x$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  x$avg_tag_length[i] <- total_char / total_tags
}

x$max_tagwords <- rep(0, nrow(x))
for (i in which(x$n_tags != 0)) {
  tags <- as.vector(split_tags[i,])
  x$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
}

#frequency of tags
tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))

tag_freq <- tag_freq %>%
              arrange(desc(percent))

x$tag1 <- split_tags[,1]
x$tag2 <- split_tags[,2]
x$tag3 <- split_tags[,3]
x$tag4 <- split_tags[,4]

assign_score <- function(data, variable) {
  score <- rep(0, nrow(data))
  notempty <- which(data[[variable]] != "")
  for (i in notempty) {
    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
  }
  return(score)
}

x$score1 <- assign_score(x, "tag1")
x$score2 <- assign_score(x, "tag2")
x$score3 <- assign_score(x, "tag3")
x$score4 <- assign_score(x, "tag4")

x$avg_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
x$avg_score[is.nan(x$avg_score)] <- 0

percentile80 <- quantile(x$avg_score, probs = 0.80)

x$frequent_tag <- FALSE
x$frequent_tag[x$avg_score >= percentile80] <- TRUE

top50tag <- as.character(top50$tag)

#function to check if tag in top50
contain_tag <- function(tag, data) {
  contain <- rep(NA, nrow(data))
  for(i in which(data[[tag]] != "")) {
    if (data[[tag]][i] %in% top50tag) {
      contain[i] <- TRUE
      } else {
        contain[i] <- FALSE
      }
    }
  return(contain)
}

containdf <- data.frame(c1 = contain_tag("tag1", data = x),
                        c2 = contain_tag("tag2", data = x),
                        c3 = contain_tag("tag3", data = x),
                        c4 = contain_tag("tag4", data = x))

x$contain_toptag <- rep(FALSE, nrow(x))
for (j in which(!is.na(containdf$c1))) {
  if (TRUE %in% containdf[j,]) {
    x$contain_toptag[j] <- TRUE
  } else {
    x$contain_toptag[j] <- FALSE
  }
}

#frequent terms in unanswered/answered questions
answered <- x %>%
  tbl_df() %>% 
  filter(answered == 1)

unanswered <- x %>%
  tbl_df() %>% 
  filter(answered == 0)

terms_a <- freq_terms(answered$title)
terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
colnames(terms_a)[2] <- "frequency_a"

terms_u <- freq_terms(unanswered$title)
terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
colnames(terms_u)[2] <- "frequency_u"

combined <- full_join(terms_a, terms_u, by = "word")
combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered

p_threshold <- 0.01
ratio_threshold <- 1

freq_terms_u <- combined %>%
                  filter(prop_in_unanswered > p_threshold) %>%
                  filter(ratio < ratio_threshold)
freq_terms_a <- combined %>%
                  filter(prop_in_answered > p_threshold) %>%
                  filter(ratio > ratio_threshold)

x$contain_u <- str_detect(as.character(x$title), pattern = or1(freq_terms_u$word))
x$contain_a <- str_detect(as.character(x$title), pattern = or1(freq_terms_a$word))

```

```{r, echo = FALSE}
cr1 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
               as.factor(post_hour) + category + as.factor(categorized) + first_punct + 
               contain_punct + end_punct + contain_question + capital_text + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + max_tagwords + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr1)
get_aic(cr1 , num_parameters = 70, data = x) #31604.12
```

```{r, echo = FALSE}
#removed categorized, contain_punct, end_punct, capital_text, max_tagwords
cr2 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
               as.factor(post_hour) + category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr2)
get_aic(cr2, 66, data = x) #31594.76
 70794.28
```

```{r, echo = FALSE}
#removed n_tags (-4) and added tag_included (+1), took out average_tag length (-1)
cr3 <- coxph(Surv(time_until_answer, answered)~as.factor(tag_included) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
               as.factor(post_hour) + category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr3)
get_aic(cr3, 61, data = x) #70794.28

#took out post_weekday (-6), added back in average tag length (+1), take out post_hour (-23)
cr4 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr4)
get_aic(cr4, 37, data = x) #31594.91 cr2 = 31594.76

#remove title and text length (-2) 
cr5 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr5)
get_aic(cr5, 35, data = x) #31591.15

#remove if pic included and gratitude 
cr6 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + 
               device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr6)
get_aic(cr6, 33, data = x) #31589.07

cr7 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               greeting + update + avg_tag_length + avg_score + 
               contain_u + contain_a, data = x)
summary(cr7)
get_aic(cr7, 27, data = x) #31580.82

#remove prior effort
cr8 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + 
               greeting + update + avg_tag_length + avg_score + 
               contain_u + contain_a, data = x)
summary(cr8)
get_aic(cr8, 26, data = x) #31581.15

#add prior effort back 
cr7 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               greeting + update + avg_score + 
               contain_u + contain_a, data = x)
summary(cr7)
get_aic(cr7, 27, data = x) #31,580.82 70,819.65

```

### 2017-08-03 summary_stats.Rmd
started fitting CR model, reorganized/added to files, updated hours

@@
 
-#### About the data set:
+### About the data set:
 
@@
 
-#### Exploring the response: time_until_answer
+### Exploring the response: time_until_answer
 
@@
 * **minimum:** `r round(min(x$time_until_answer), 2)` hrs
-* **maximum:** `r round(max(x$time_until_answer), 2)` hrs, `r round(max(x$time_until_answer)/24, 2)` days
-* **mean:** `r round(mean(x$time_until_answer), 2)` hrs, `r round(mean(x$time_until_answer)/24, 2)` days
+* **maximum:** `r round(max(x$time_until_answer), 2)` hrs (`r round(max(x$time_until_answer)/24, 2)` days)
+* **mean:** `r round(mean(x$time_until_answer), 2)` hrs (`r round(mean(x$time_until_answer)/24, 2)` days)
 * **median:** `r round(median(x$time_until_answer), 2)` hrs
 * **first quartile:** `r round(summary[2], 2)`hrs
-* **third quartile:** `r round(summary[5], 2)` hrs, `r round(summary[5]/24, 2)` days
-* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs, `r round((summary[5] - summary[2])/24, 2)` days
-* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions had been answered
-* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions had been answered
+* **third quartile:** `r round(summary[5], 2)` hrs (`r round(summary[5]/24, 2)` days)
+* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs (`r round((summary[5] - summary[2])/24, 2)` days)
+* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions have been answered
+* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions have been answered
 
@@
   scale_x_continuous("Time (hours)") +
-  ggtitle("Distribution of time_until_answer values")
+  ggtitle("Distribution of answer times")
 ```
@@
 
-##### Survival Time Statistics based off of KM Estimator 
+##### Based off of the Kaplan-Meier Estimator 
 ```{r, echo = FALSE}
@@
 s <- summary(KM)
-round(s$table, 2)
 ```
 
-* **Min survival probability:** `r round(min(s$surv), 2)`
-* **Max survival probability:** `r round(max(s$surv), 2)`
-* **rmean survival time:** `r round(s$table[5], 2)` hrs, `r round(s$table[5]/24, 2)` days
-* **SE of rmean:** `r round(s$table[6], 2)` hrs
-* **Median survival time:** `r round(s$table[7], 2)` hrs
-* **95% confidence interval for the median:** (`r round(s$table[8], 2)`,`r round(s$table[9], 2)`)
+* number of complete events/answered questions: `r s$table[4]` (`r nrow(x)` total questions) 
+* smallest survival probability: `r round(min(s$surv), 2)`
+* largest survival probability: `r round(max(s$surv), 2)`
+* mean survival time: `r round(s$table[5], 2)` hrs (`r round(s$table[5]/24, 2)` days)
+* SE of the mean: `r round(s$table[6], 2)` hrs
+* Median survival time: `r round(s$table[7], 2)` hrs
+* 95% confidence interval for the median: (`r round(s$table[8], 2)` hrs,`r round(s$table[9], 2)` hrs)
 
@@
 ```
-* **Interpretations:**
+* Interpretations:
     + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
@@
     + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
-    + highest quantile that exists: `r round(quant$quantile[6], 2)` hrs 64% of the questions have been answered
+    + highest quantile that exists: By `r round(quant$quantile[6], 2)` hrs (`r round(quant$quantile[6]/24, 2)` days) 64% of the questions have been answered
 
@@
 
-* Survival curve shows that survival probability drops immediately after question is posted. Within a few hours after posting, survival probability levels out, hovers around 0.35 (never hits 0).
+* Survival curve shows that survival probability drops immediately after question is posted. 
+* Within a few hours after posting, the survival probability levels out (though it still decreases at a slow rate), and hovers around 0.35 (never hits 0).
 
 ```{r, survival curves, echo = FALSE}
-ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", main = "KM Curve")
-ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", main = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
+ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", title = "KM Curve")
+```
+
+```{r, echo = FALSE}
+ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", title = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
 ```
@@
 
-* at 100 hrs, the probability that a question is answered starts to level out at around ~0.63
+* At around 100 hours, the probability a question is answered before time t starts to level out at around ~0.63
 
@@
   scale_x_continuous("Time (hours)", limits = c(0,100)) + 
-  scale_y_continuous("Probability a question is answered") + 
-  ggtitle("Probability a question is answered vs. time (hours)")
+  scale_y_continuous("Probability a question is answered before time t") + 
+  ggtitle("Probability a question is answered before a certain time vs. time (hours)")
 ```
 
-### Instantaneous Hazard Rates (based off of KM estimates)
+##### Instantaneous Hazard Rates (based off of KM estimates)
 
@@
 
-* **Max instant hazard rate:** `r round(max(h.hat$est), 2)` at time: `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
-* **Min instant hazard rate:** `r round(min(h.hat$est), 2)`
+* Max instant hazard rate: `r round(max(h.hat$est), 2)` at `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
+* Min instant hazard rate: `r round(min(h.hat$est), 2)`
+* Interpretations: 
+    +
 
@@
 
-### Cumulative Hazard Rates
+##### Cumulative Hazard Rates
 

### 2017-08-03 tag_exploration.Rmd
started fitting CR model, reorganized/added to files, updated hours

@@
 }
+
+sum_stats <- function(variable, data) {
+  tbl <- x %>%
+    group_by(data[[variable]]) %>%
+    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
+    arrange(median_time)
+  names(tbl)[1] <- variable
+  return(tbl)
+}
 ```
 
-```{r, echo = FALSE}
+```{r, include = FALSE}
 #matrix of tags (splitting up tags variable wherever there's a comma)
@@
 
-### avg_tag_length
+### Average Tag Length
 
-* average length of tag for a question: total number of characters for all of a question's tags / number of tags the question has
-* think that tags that are more concise (fewer characters) will have faster answer times
-
-```{r, echo = FALSE}
-#average tag length: 
+```{r, include = FALSE}
 x$avg_tag_length <- NA
@@
 
-ggplot(x, aes(x = avg_tag_length)) + 
-  geom_histogram() + 
-  scale_x_continuous("Average tag length for each question (characters)") + 
-  ggtitle("Distribution of average tag lengths")
-
 max_avg <- max(x$avg_tag_length, na.rm = TRUE)
@@
 
-* longest average tag length: `r max_avg`
-* shortest average tag length: `r min_avg`
-* mean average tag length: `r mean_length`
-* median average tag length: `r median_length`
+* average length of tag for a question: total number of characters for all of a question's tags / number of tags the question has
+* hypothesis: questions with longer average tag lengths will have slower answer times (tags that are concise and include only a word will have faster answer times)
+* **longest average tag length:** `r max_avg`
+* **shortest average tag length:** `r min_avg`
+* **mean average tag length:** `r mean_length`
+* **median average tag length:** `r median_length`
 
-##### average tag length grouped by product category 
+```{r, echo = FALSE}
+ggplot(x, aes(x = avg_tag_length)) + 
+  geom_histogram() + 
+  scale_x_continuous("Average tag length for each question (characters)") + 
+  ggtitle("Distribution of average tag lengths")
+```
+
+##### Average tag length grouped by category
+
 ```{r, echo = FALSE}
@@
   group_by(category) %>%
-  summarise(avg_length = mean(avg_tag_length, na.rm = TRUE), median_length = median(avg_tag_length, na.rm = TRUE), n = n(), avg_views = mean(daily_views), median_time = median(time_until_answer)) %>%
+  summarise(n = n(), median_views = median(daily_views), median_time = median(time_until_answer), avg_length = mean(avg_tag_length, na.rm = TRUE)) %>%
   arrange(avg_length)
@@
 
-##### average tag length grouped by answered/unanswered questions
+##### Average tag length grouped by answered
+
 ```{r, echo = FALSE}
@@
 
-### frequency of tags (popularity)
+### Maximum number of words in a tag
+
+* Another way to capture if the length of a tag is too long? 
+* Will show if a question contains a really long tag- indicates incorrect tagging
+
+##### frequency table for number of words
+
+```{r, echo = FALSE}
+x$max_tagwords <- rep(0, nrow(x))
+for (i in which(x$n_tags != 0)) {
+  tags <- as.vector(split_tags[i,])
+  x$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
+}
+
+#to find the mode
+Mode <- function(x) {
+  ux <- unique(x)
+  ux[which.max(tabulate(match(x, ux)))]
+}
+
+table(x$max_tagwords)
+```
+
+* max number of words in a tag: `r max(x$max_tagwords, na.rm = TRUE)`
+* median number of words: `r median(x$max_tagwords, na.rm = TRUE)`
+* mode number of words: `r Mode(subset(x$max_tagwords, !is.na(x$max_tagwords)))`
+
+##### Average number of max words in a tag grouped by answered/unanswered
+
+```{r, echo = FALSE}
+x %>%
+  group_by(answered) %>%
+  summarise(median_words = median(max_tagwords, na.rm = TRUE))
+```
+
+##### log-rank test (for each level of maximum words)
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ as.factor(max_tagwords), data = x)
+KM_maxwords <- survfit(surv_object ~ as.factor(max_tagwords), data = x)
+plot_surv(KM_maxwords, data = x)
+```
+
+### Frequency of tags (popularity?)
+
+* Took the unique tags, counted the number of times each tag occured in the data, and calculated the proportion of times it appeared = frequency of the tag 
+* Average frequency score for a question: average frequency score for each tag in a question
+
+##### First 6 of the tags that appear the most
 
@@
 
-ggplot(tag_freq, aes(x = percent)) + 
-  geom_histogram() + 
-  ggtitle("Distribution of tag frequency")
+head(tag_freq)
+
+library(forcats)
 
@@
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  ggtitle("Distribution of top 50 tags and percentage of times they occur")
+  scale_y_continuous(labels = scales::percent) + 
+  ggtitle("Distribution of the top 50 tags and percentage of times they occur in the data")
 ```
@@
 ```{r, echo = FALSE}
-#creating average frequency/popular score variable
+#creating average frequency score variable
 x$tag1 <- split_tags[,1]
@@
   geom_histogram() + 
-  ggtitle("Distribution of average tag popularity/frequency scores")
+  ggtitle("Distribution of average tag frequency scores for each question")
 ```
 
-#### Determining threshold for popular/unpopular tags
+##### Determining the threshold for what's considered frequent/unfrequent tags
 
-```{r, echo = FALSE}
+```{r, include = FALSE}
 median_score <- median(x$avg_score)
@@
 
-x$popular_tag <- FALSE
-x$popular_tag[x$avg_score >= percentile80] <- TRUE
+x$frequent_tag <- FALSE
+x$frequent_tag[x$avg_score >= percentile80] <- TRUE
 
-prop_popular <- sum(x$popular_tag)/sum(x$n_tags != 0)
+prop_frequent <- sum(x$frequent_tag)/sum(x$n_tags != 0)
 ```
@@
 * 75th percentile for scores: `r q_score[4]`
-* popularity threshold based off of 80th percentile: `r percentile80`
-* proportion of questions that contain a tag that are "popular": `r prop_popular`
+* **popularity threshold based off of 80th percentile:** `r percentile80`
+* proportion of questions that contain a tag that are "popular": `r prop_frequent`
 
-##### Log-rank test
+##### Log-rank test (for frequent/unfrequent tags)
 
@@
 
-### incorrect use of tags
+### Incorrect use of tags
 * correct tags
@@
     + if it contains numbers must also contain letters 
-* regex
-* look at probability a quesiton includes certain tag- chances it's answered (grab most frequent)
+* look at probability a question is answered if it contain's a certain tag
 * maybe ignore tags that are also in device names
 
-```{r, echo = FALSE}
+```{r, include = FALSE}
 x$correct_tag <- NA_character_
@@
 
-##### Log-rank test
+##### Log-rank test (for incorrect vs correctly tagged questions)
 
@@
 
-### If a question contains top50 tags
+### If a question contains at least one of the top 50 most frequent tags
 
-```{r, echo = FALSE}
+```{r, include = FALSE}
 top50tag <- as.character(top50$tag)
@@
 
-##### median time, prop answered and average daily views grouped by whether or not it contains a top50 tag
+##### Summary stats grouped by contain_toptag
 ```{r, echo = FALSE}
-x %>% 
-  group_by(contain_toptag) %>%
-  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n)
+sum_stats("contain_toptag", data = x)
 ```
 
-##### log-rank test 
+##### log-rank test (for questions that contain vs don't contain)
 ```{r, echo = FALSE}
@@
 ```
-
-### maximum number of words in a tag
-
-##### frequency table for number of words
-
-```{r, echo = FALSE}
-x$max_tagwords <- rep(NA, nrow(x))
-for (i in which(x$n_tags != 0)) {
-  tags <- as.vector(split_tags[i,])
-  x$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
-}
-
-#to find the mode
-Mode <- function(x) {
-  ux <- unique(x)
-  ux[which.max(tabulate(match(x, ux)))]
-}
-
-table(x$max_tagwords)
-```
-
-* max number of words in a tag: `r max(x$max_tagwords, na.rm = TRUE)`
-* median number of words: `r median(x$max_tagwords, na.rm = TRUE)`
-* mode number of words: `r Mode(subset(x$max_tagwords, !is.na(x$max_tagwords)))`
-
-##### Average number of max words in a tag grouped by answered/unanswered
-
-```{r, echo = FALSE}
-x %>%
-  group_by(answered) %>%
-  summarise(median_words = median(max_tagwords, na.rm = TRUE))
-```

### 2017-08-03 textual_analysis.Rmd
started fitting CR model, reorganized/added to files, updated hours

@@
 }
+
+#function that prints out summary stats grouped by that variable 
+sum_stats <- function(variable, data) {
+  tbl <- x %>%
+    group_by(data[[variable]]) %>%
+    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
+    arrange(median_time)
+  names(tbl)[1] <- variable
+  return(tbl)
+}
 ```
@@
 
+* search for : ; , ? or limit the search to just end punctuation?
+
 ```{r, echo = FALSE}
-x$first_punct <- str_locate(x$text, pattern = "[.|,|?|!|;|:]")[,1]
+x$first_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]
 
@@
 
-##### Average and median first_punc grouped by answered
+##### Median first_punc grouped by answered
 
@@
   group_by(answered) %>%
-  summarise(avg_pos = mean(first_punct, na.rm = TRUE), median_pos = median(first_punct, na.rm = TRUE), n = n())
+  summarise(median_pos = median(first_punct, na.rm = TRUE), n = n())
 ```
 
-##### Average and median first_punct grouped by category
+##### Median first_punct and time grouped by category
 
@@
   group_by(category) %>%
-  summarise(avg_pos = mean(first_punct, na.rm = TRUE), median_pos = median(first_punct, na.rm = TRUE), n = n()) %>%
-  arrange(median_pos)
+  summarise(median_pos = median(first_punct, na.rm = TRUE), n = n(), median_time = median(time_until_answer)) %>%
+  arrange(desc(median_pos))
 ```
@@
 
-##### Median time_until_answer grouped by whether or not text contains punct
+##### summary stats grouped by contain_punct
 
@@
 
-x %>%
-  group_by(contain_punct) %>%
-  summarise(median_time = median(time_until_answer), n = n())
+sum_stats("contain_punct", data = x)
 ```
 
-##### Proportion of answered/unanswered questions that contain punct
-
-```{r, echo = FALSE}
-x %>%
-  group_by(answered) %>%
-  summarise(n = n(), prop_contain = sum(contain_punct)/n)
-```
-
-##### Proportion that contain punct grouped by categories
+##### Proportion that contain any punctuation grouped by categories
 
@@
 
-##### Median time_until_answer grouped by whether or not text ends with punct
+##### summary stats for end_punct
 
 ```{r, echo = FALSE}
-x %>% 
-  group_by(end_punct) %>%
-  summarise(median_time = median(time_until_answer), n = n())
-```
-
-##### Proportion of answered/unanswered questions that end with punct
-
-```{r, echo = FALSE}
-x %>% 
-  group_by(answered) %>%
-  summarise(n = n(), prop_end = sum(end_punct)/n)
+sum_stats("end_punct", data = x)
 ```
@@
 ```{r, question mark, echo = FALSE}
-x$contain_question <- str_detect(x$title, pattern = QUESTION)
+x$contain_question <- str_detect(x$title, pattern = QUESTION %R% END)
 
@@
 
-##### median time grouped by whether or not title contains: '?'
+##### summary stats for contain_question
 
 ```{r, echo = FALSE}
-x %>%
-  group_by(contain_question) %>%
-  summarise(median_time = median(time_until_answer), n = n()) %>%
-  arrange(median_time)
+sum_stats("contain_question", data = x)
 ```
@@
 
-##### median time and proportion answered grouped by begin_wh
+##### summary stats for begin_wh
+
 ```{r, echo = FALSE}
-x %>%
-  group_by(begin_wh) %>%
-  summarise(median_time = median(time_until_answer), n = n(), prop_answered = sum(answered)/n)
+sum_stats("begin_wh", data = x)
 ```
@@
 ##### log-rank test
+
 ```{r, echo = FALSE}
@@
 ### If first letter of text is capitalized
+
 ```{r, echo = FALSE}
@@
 ```{r, echo = FALSE}
-x %>%
-  group_by(answered) %>%
-  summarise(n = n(), prop_capital = sum(capital_text)/n)
+sum_stats("capital_text", data = x)
 ```
@@
 
-##### Proportion all lower case grouped by answered/unanswered
+##### summary stats for all_lower
 
 ```{r, echo = FALSE}
-x %>%
-  group_by(answered) %>%
-  summarise(n = n(), prop_allLower = sum(all_lower)/n)
+sum_stats("all_lower", data = x)
 ```
@@
 
-##### median time/average daily views grouped by whether or not question contains "tried"/"searched"
-```{r, echo = FALSE}
-x %>%
-  group_by(prior_effort) %>%
-  summarise(median_time = median(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
-  arrange(median_time)
-```
-
-##### proportion within answered/unanswered questions that indicate prior effort
+##### summary stats for prior_effort
 
 ```{r, echo = FALSE}
-x %>%
-  group_by(answered) %>%
-  summarise(n = n(), prop_indicateeffort = sum(prior_effort)/n) 
+sum_stats("prior_effort", data = x)
 ```
@@
 
-##### Median time grouped by whether or not gratitude is expressed
+##### summary stats for gratitude
+
+```{r, echo = FALSE}
+sum_stats("gratitude", data = x)
+```
+
+##### New and continuing users and expressing gratitude
 
@@
 x %>% 
-  group_by(gratitude) %>%
-  summarise(median_time = median(time_until_answer))
-```
-
-##### proportion in answered/unanswered questions that express gratitude
-
-```{r, echo = FALSE}
-x %>% 
-  group_by(answered) %>%
+  group_by(new_user) %>%
   summarise(n = n(), prop_gratitude = sum(gratitude)/n)
@@
 
-### Does greeting people matter? (presence of "hi")
+### Does greeting people matter? (presence of ex: "hi")
 
@@
 
+##### summary stats grouped by greeting
+
+```{r, echo = FALSE}
+sum_stats("greeting", data = x)
+```
+
+##### New and continuing users and greetings 
+```{r, echo = FALSE}
+x %>%
+  group_by(greeting) %>%
+  summarise(n = n(), prop_new = sum(new_user)/n)
+```
+
 ##### log-rank test
@@
 plot_surv(KM_greet, data = x)
+```
+
+### If the asker updated the question
+
+```{r, echo = FALSE}
+x$update <- str_detect(x$text, pattern = "===")
+
+prop_update <- sum(x$update)/nrow(x)
+```
+
+* `r round(prop_update*100,2)`% of users updated their question after posting it
+
+##### summary statitics grouped by update
+
+```{r, echo = FALSE}
+sum_stats("update", data = x)
+```
+
+##### proportion of new/continuing users that updated their question
+
+```{r, echo = FALSE}
+x %>%
+  group_by(new_user) %>%
+  summarise(n = n(), prop_update = sum(update)/n)
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ update, data = x)
+KM_update <- survfit(surv_object ~ update, data = x)
+plot_surv(KM_update, data = x)
 ```

### 2017-08-03 variable_exploration.Rmd
started fitting CR model, reorganized/added to files, updated hours

@@
 library(rebus)
+library(qdap)
+library(tm)
 ```
@@
 #takes survfit object, data set to work with, and optional x-axis limits as input, outputs ggplot KM curves
-
 plot_surv <- function(survfit, data, xlim = NULL) {
@@
 
+#function that prints out summary stats grouped by that variable 
+sum_stats <- function(variable, data) {
+  tbl <- x %>%
+    group_by(data[[variable]]) %>%
+    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
+    arrange(median_time)
+  names(tbl)[1] <- variable
+  return(tbl)
+}
+
+#took out phone iphone and android
+
+#function to clean corpus (stopwrds is an optional argument)
+clean_corpus <- function(corpus, stopwrds = NULL){
+  if (is.null(stopwrds)) {
+    corpus <- tm_map(corpus, stripWhitespace)
+    corpus <- tm_map(corpus, content_transformer(tolower))
+    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+    return(corpus)    
+  } else {
+    corpus <- tm_map(corpus, stripWhitespace)
+    corpus <- tm_map(corpus, content_transformer(tolower))
+    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix", stopwrds))
+    return(corpus)
+  }
+}
+
+#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
+freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
+  source <- VectorSource(vec)
+  corpus <- VCorpus(source)
+
+  if (is.null(stopwrds)) {
+    cleaned_corpus <- clean_corpus(corpus) 
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
+    m <- as.matrix(dtm) 
+    freq <- colSums(m)
+    freq <- sort(freq, decreasing = TRUE)
+    freq_df <- data.frame(word = names(freq), frequency = unname(freq))    
+  } else {
+    cleaned_corpus <- clean_corpus(corpus, stopwrds) 
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
+    m <- as.matrix(dtm) 
+    freq <- colSums(m)
+    freq <- sort(freq, decreasing = TRUE)
+    freq_df <- data.frame(word = names(freq), frequency = unname(freq))
+  }
+
+  if (missing(n)) {
+    return(freq_df)
+  }
+  else {
+    return(freq_df[1:n,])
+  }
+}
 ```
@@
 
-##### number of questions within each category
+##### summary stats grouped by category, arranged by median time
+
+* NA's represent questions for devices that don't already exist on the website, treat as other?
 
 ```{r, echo = FALSE}
-x %>%
-  group_by(category) %>%
-  summarise(n = n()) %>%
-  arrange(desc(n))
+sum_stats("category", x)
 ```
-
-##### median/average time by category
-
-```{r, echo = FALSE}
-sorted <- x %>% 
-  group_by(category) %>%
-  summarise(n = n(), avg_time = mean(time_until_answer), median_time = median(time_until_answer), median_views = median(daily_views)) %>%
-  arrange(median_time)
-sorted
-```
-
-* **Categories with lowest median time_until_answer values:** `r as.character(sorted$category[1:5])`
-* **Category with longest median time_until_answer:** `r last(as.character(sorted$category))`
 
@@
 
-##### Is there a difference between iphone and android users?
+### Subcategories
+
+```{r, echo = FALSE}
+x %>%
+  group_by(subcategory) %>%
+  summarise(n = n(), proportion = n/nrow(x), prop_ans = sum(answered)/n, median_time = median(time_until_answer)) %>%
+  arrange(desc(n))
+```
+
+##### Is there a difference between iPhone and Android users?
 
@@
   group_by(subcategory) %>%
-  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views))
+  summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_ans = sum(answered)/n)
+```
+
+##### textmining on iPhone and Android Phone text
+
+##### Word cloud for most frequent terms among questions about iPhones
+
+```{r, echo = FALSE}
+android_data <- x %>%
+  filter(subcategory == "Android Phone")
+android_terms <- freq_terms(android_data$text, stopwrds = c("android", "phone"))
+
+iphone_data <- x %>%
+  filter(subcategory == "iPhone")
+iphone_terms <- freq_terms(iphone_data$text, stopwrds = c("iphone", "phone"))
+
+library(wordcloud)
+library(RColorBrewer)
+
+wordcloud(iphone_terms$word, iphone_terms$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
+```
+
+##### Word cloud for most frequent terms among questions involving Android Phones
+
+```{r, echo = FALSE}
+wordcloud(android_terms$word, android_terms$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
 ```
@@
 survdiff(surv_object~categorized, data = x)
-```
-
-##### survival curves
-
-```{r, echo = FALSE}
 KM_correct <- survfit(surv_object ~ as.factor(categorized), data = x)
@@
   geom_histogram() + 
-  scale_x_continuous("Length of Question Title") + 
+  scale_x_continuous("Length of Question Title", breaks = seq(0,100,10)) + 
   ggtitle("Distribution of Title Lengths")
-
-sum_length <- summary(x$title_length)
 ```
 
-* **min title length:** `r sum_length[1]` characters
-* **max title length:** `r sum_length[6]` characters
-* **mean title length:** `r sum_length[4]`
-* **median:** `r sum_length[3]`
+* **min title length:** `r min(x$title_length)` characters
+* **max title length:** `r max(x$title_length)` characters
+* **mean title length:** `r round(mean(x$title_length),2)`
+* **median:** `r median(x$title_length)`
 
@@
   group_by(as.factor(answered)) %>%
-  summarise(avg_titlelength = mean(title_length), median_titlelength = median(title_length), n = n())
+  summarise(avg_length = mean(title_length), n = n())
+
+f <- x %>%
+  filter(is.na(category))
 ```
@@
   ggtitle("Distribution of Text Lengths")
-
-sum_text <- summary(x$text_length)
 ```
 
-* **min text length:** `r sum_text[1]` characters
-* **max text length:** `r sum_text[6]` characters
-* **mean text length:** `r sum_text[4]`
-* **median:** `r sum_text[3]`
+* **min text length:** `r min(x$text_length)` characters
+* **max text length:** `r max(x$text_length)` characters
+* **mean text length:** `r round(mean(x$text_length),2)` characters
+* **median:** `r median(x$text_length)` characters
 
@@
   group_by(as.factor(answered)) %>%
-  summarise(avg_length = mean(text_length), median_length = median(text_length), median_time = median(time_until_answer), n = n())
+  summarise(median_length = median(text_length), n = n())
 ```
@@
   group_by(category) %>%
-  summarise(avg_length = mean(text_length), median_length = median(text_length), n = n()) %>%
-  arrange(desc(avg_length))
+  summarise(median_length = median(text_length), n = n(), median_time = median(time_until_answer)) %>%
+  arrange(desc(median_length))
 ```
@@
   ggtitle("Distribution of Device Name Lengths")
-
-sum_device <- summary(x$device_length)
 ```
 
-* **min length:** `r sum_device[1]`
-* **max length:** `r sum_device[6]`
-* **mean length:** `r sum_device[4]`
-* **median length:** `r sum_device[3]`
+* **min length:** `r min(x$device_length)` characters
+* **max length:** `r max(x$device_length)` characters
+* **mean length:** `r round(mean(x$device_length),2)` characters
+* **median length:** `r median(x$device_length)` characters
 
@@
   group_by(as.factor(answered)) %>%
-  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n())
+  summarise(avg_length = mean(device_length), n = n())
 ```
@@
   group_by(category) %>%
-  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n(), median_time = median(time_until_answer)) %>%
-  arrange(desc(avg_length))
+  summarise(avg_length = mean(device_length), n = n(), median_time = median(time_until_answer)) %>%
+  arrange(median_time)
 ```
@@
 ```
-* `r round(prop_notags * 100,2)`% of questions don't have any tags
+* `r round(prop_notags*100,2)`% of questions don't have any tags
 
@@
 ```{r, echo = FALSE}
-x %>%
-  group_by(as.factor(n_tags)) %>%
-  summarise(n = n(), median_time = median(time_until_answer), proportion_answered = sum(answered)/n, median_views = median(daily_views)) %>%
-  arrange(median_time)
+sum_stats("n_tags", x)
 ```
@@
 
-x %>%
-  group_by(as.factor(pic_included)) %>%
-  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n, median_views = median(daily_views)) %>%
-  arrange(desc(proportion_answered))
+sum_stats("pic_included", x)
 ```
@@
 plot_surv(KM_pic, data = x)
+plot_surv(KM_pic, data = x, xlim = c(0,250))
 ```
@@
 ```{r, echo = FALSE}
+sum_stats("new_user", x)
+```
+
+##### More summary statistics grouped by new_user
+
+```{r, echo = FALSE}
 x %>%
-  group_by(as.factor(new_user)) %>%
-  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n) %>%
-  arrange(desc(proportion_answered))
+  group_by(new_user) %>%
+  summarise(n = n(), include_tag = sum(n_tags != 0)/n, include_pic = sum(n_images != 0)/n, mean_title = mean(title_length), mean_text = mean(text_length), mean_device = mean(device_length))
+```
+
+##### wordclouds for new users
+
+* to see if there's a difference in the topics of the questions that new/continuing users ask
+
+```{r, echo = FALSE}
+new <- x %>%
+  filter(new_user == 1)
+
+new_freq <- freq_terms1(new$text)
+wordcloud(new_freq$word, new_freq$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
+```
+
+##### wordclouds for continuing users
+
+```{r, echo = FALSE}
+continuing <- x %>%
+  filter(new_user == 0)
+cont_freq <- freq_terms1(continuing$text)
+wordcloud(cont_freq$word, cont_freq$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
 ```
@@
 
-```{r}
+```{r, echo = FALSE}
 x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
@@
 
-library(gridExtra)
-
 ggplot(x, aes(x = post_hour)) + 
@@
 ```{r, echo = FALSE}
-x %>%
-  group_by(post_weekday) %>%
-  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n) %>%
-  arrange(median_time)
+sum_stats("post_weekday", x)
 ```
@@
 ```{r, echo = FALSE}
-x %>%
-  group_by(as.factor(post_hour)) %>%
-  summarise(n = n(), median_time = median(time_until_answer), avg_views = mean(daily_views), prop_answered = sum(answered)/n) %>%
-  arrange(median_time)
-
-```
-
-##### Median time grouped by morning/afternoon
-
-```{r, echo = FALSE}
-x %>%
-  group_by(post_ampm) %>%
-  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n)
+sum_stats("post_hour", x)
 ```
@@
 plot_surv(KM_weekday, data = x)
+```
+
+##### log-rank test and survival curves for hour of the day
+
+```{r, echo = FALSE}
+survdiff(surv_object ~ as.factor(post_hour), data = x)
+KM_hour <- survfit(surv_object ~ as.factor(post_hour), data = x)
+plot_surv(KM_hour, data = x)
 ```
@@
 
+library(gridExtra)
+
 plot1 <- ggplot(x, aes(x = post_hour)) + 

### 2017-08-04 Hours.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

@@
 8/1/2017 | 3 | 5:30-8:30PM | Organized/added to files
-8/2/2017 | 5 | 1:15-6:15PM | Fitted CR models, changes summary_stats files..
+8/2/2017 | 5 | 1:15-6:15PM | Fitted CR models, changed summary_stats files
+8/3/2017 | 5.5 | 12:00-5:30 | Added to summary stats, created ratio of newlines to textlength variable, tried to estimate MLEs, ran in to problems
+8/3/2017 | 2.75 | 8:00-10:45 | Continued to try out MLEs, looked into Tex and downloaded mendeley, continued fitting the model
+
 >> __Total Hours: 1...__

### 2017-08-04 calculatingMLEs.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

---
title: "MLEs of Parametric Distributions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
x <- out %>% 
  tbl_df() %>%
  filter(langid == "en")

x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
empty <- which(is.na(x$time_until_answer))
for (i in empty) {
  x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
}

library(fitdistrplus)
library(flexsurv)
library(survival)
library(mosaic)
library(ggplot2)
```

# Formatting data to work with fitdistrplus package

```{r}
df <- data.frame(left = x$time_until_answer, right = x$time_until_answer)
df[x$answered == 0,2] <- NA

```

# Identifying estimates

```{r}
#these distributions work
fit_logis <- fitdistcens(df, "logis")
summary(fit_logis)

fit_lnorm <- fitdistcens(df, "lnorm")
summary(fit_lnorm)

#this "producedNaNs"
fit_weibull <- fitdistcens(df, "weibull")
summary(fit_weibull)

#outputs Non-positive shape parameter over and over again
fit_llogis <- fitdistcens(df, "llogis", control=list(trace=1, REPORT=1))
summary(fit_llogis)
##output correct?

#exponential doesn't work
fit_exp <- fitdistcens(df, "exp", optim.method = "BFGS", lower = 0, start = NULL)
mledist(df, "exp", optim.method = "BFGS")

```

### 2017-08-04 model_fitting.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

@@
 #function to calculate r-square adjusted
-get_r2adj <- function(cr_obj)
+get_rsq_adj <- function(cr_obj, k) {
+  r <- unname(summary(cr_obj)$rsq[1])
+  n <- summary(cr_obj)$n
+  radj <- 1- (((1- (r**2)) * (n - 1))/(n-k-1))
+  return(radj)
+}
+
+#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
+freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
+  source <- VectorSource(vec)
+  corpus <- VCorpus(source)
+
+  if (is.null(stopwrds)) {
+    cleaned_corpus <- clean_corpus(corpus) 
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
+    m <- as.matrix(dtm) 
+    freq <- colSums(m)
+    freq <- sort(freq, decreasing = TRUE)
+    freq_df <- data.frame(word = names(freq), frequency = unname(freq))    
+  } else {
+    cleaned_corpus <- clean_corpus(corpus, stopwrds) 
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
+    m <- as.matrix(dtm) 
+    freq <- colSums(m)
+    freq <- sort(freq, decreasing = TRUE)
+    freq_df <- data.frame(word = names(freq), frequency = unname(freq))
+  }
+
+  if (missing(n)) {
+    return(freq_df)
+  }
+  else {
+    return(freq_df[1:n,])
+  }
+}
 ```
@@
 #length of sentence till first punctuation mark 
-x$first_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]
+x$text_till_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]
+x$text_till_punct[is.na(x$text_till_punct)] <- 5000
 
-#if text contains punct
+#if text contains end punctuation
 x$contain_punct <- FALSE
-x$contain_punct[!is.na(x$first_punct)] <- TRUE
+x$contain_punct[!is.na(x$text_till_punct)] <- TRUE
 
 #if the text ends in a punctuation
-x$end_punct <- str_detect(x$text, pattern = "[.|?|!]$")
+x$text_end_punct <- str_detect(x$text, pattern = "[.|?|!]$")
 
 #if the title ends in a question mark
-x$contain_question <- str_detect(x$title, pattern = QUESTION %R% END)
+x$title_questionmark <- str_detect(x$title, pattern = QUESTION %R% END)
 
-#leaving out if title begins with "wh" (should i check if text is significant tho)
+#if the title starts with "Wh"
+x$title_begin_wh <- str_detect(str_to_lower(x$title), pattern = "^wh")
+
 #if first letter of title is capitalized
@@
 
-x$all_lower <- str_detect(x$removed, pattern = "^[[:lower:]]+$")
+x$text_all_lower <- str_detect(x$removed, pattern = "^[[:lower:]]+$")
 x <- x[,-which(names(x) == "removed")]
@@
 }
+x$avg_tag_length[is.na(x$avg_tag_length)] <- 0
 
@@
               arrange(desc(percent))
+top50 <- tag_freq[1:50,]
 
@@
 
-x$avg_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
-x$avg_score[is.nan(x$avg_score)] <- 0
+x$avg_tag_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
+x$avg_tag_score[is.nan(x$avg_tag_score)] <- 0
 
-percentile80 <- quantile(x$avg_score, probs = 0.80)
+percentile80 <- quantile(x$avg_tag_score, probs = 0.80)
 
 x$frequent_tag <- FALSE
-x$frequent_tag[x$avg_score >= percentile80] <- TRUE
+x$frequent_tag[x$avg_tag_score >= percentile80] <- TRUE
 
@@
 
+library(qdap)
+library(tm)
 terms_a <- freq_terms(answered$title)
@@
 
-x$contain_u <- str_detect(as.character(x$title), pattern = or1(freq_terms_u$word))
-x$contain_a <- str_detect(as.character(x$title), pattern = or1(freq_terms_a$word))
+x$contain_unanswered <- str_detect(as.character(x$title), pattern = or1(freq_terms_u$word))
+x$contain_answered <- str_detect(as.character(x$title), pattern = or1(freq_terms_a$word))
+
+#ratio of newlines to length of text
+x$newline_ratio <- str_count(x$text, pattern = "\n")/str_length(x$text)
 
@@
 ```{r, echo = FALSE}
-cr1 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
-               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
-               as.factor(post_hour) + category + as.factor(categorized) + first_punct + 
-               contain_punct + end_punct + contain_question + capital_text + all_lower + prior_effort + 
-               gratitude + greeting + update + avg_tag_length + max_tagwords + avg_score + frequent_tag + 
-               contain_toptag + contain_u + contain_a, data = x)
-summary(cr1)
-get_aic(cr1 , num_parameters = 70, data = x) #31604.12
-```
+cr1 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
+                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
+                  text_end_punct + title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  greeting + update + avg_tag_length + max_tagwords + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
+s <- summary(cr1)
+s$rsq
+get_aic(cr1, 72, data = x) #83471.68
+get_rsq_adj(cr1, 72) #0.00513921
 
-```{r, echo = FALSE}
-#removed categorized, contain_punct, end_punct, capital_text, max_tagwords
-cr2 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
-               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
-               as.factor(post_hour) + category + first_punct + 
-               contain_question + all_lower + prior_effort + 
-               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
-               contain_toptag + contain_u + contain_a, data = x)
+#removed greeting and text_end punct (p-values > .8)
+cr2 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
+                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_length + max_tagwords + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
 summary(cr2)
-get_aic(cr2, 66, data = x) #31594.76
- 70794.28
-```
+get_aic(cr2, 70, data = x) #83467.71
+get_rsq_adj(cr2, 70) #0.005397121
 
-```{r, echo = FALSE}
-#removed n_tags (-4) and added tag_included (+1), took out average_tag length (-1)
-cr3 <- coxph(Surv(time_until_answer, answered)~as.factor(tag_included) + as.factor(pic_included) + 
-               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
-               as.factor(post_hour) + category + first_punct + 
-               contain_question + all_lower + prior_effort + 
-               gratitude + greeting + update + avg_score + frequent_tag + 
-               contain_toptag + contain_u + contain_a, data = x)
+#removed max_tagwords
+cr3 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
+                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_length + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
 summary(cr3)
-get_aic(cr3, 61, data = x) #70794.28
+get_aic(cr3, 69, data = x) #83465.91
+get_rsq_adj(cr3, 69) #0.005520927
 
-#took out post_weekday (-6), added back in average tag length (+1), take out post_hour (-23)
-cr4 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
-               text_length + title_length + device_length + as.factor(new_user) + 
-               category + first_punct + 
-               contain_question + all_lower + prior_effort + 
-               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
-               contain_toptag + contain_u + contain_a, data = x)
+#removed avg_tag_length
+cr4 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
+                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
 summary(cr4)
-get_aic(cr4, 37, data = x) #31594.91 cr2 = 31594.76
+get_aic(cr4, 68, data = x) #83463.95
+get_rsq_adj(cr4, 68) #0.005649183
 
-#remove title and text length (-2) 
-cr5 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
-               device_length + as.factor(new_user) + 
-               category + first_punct + 
-               contain_question + all_lower + prior_effort + 
-               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
-               contain_toptag + contain_u + contain_a, data = x)
+#removed text_till_punct
+cr5 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
+                  device_length + post_weekday + as.factor(post_hour) + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
 summary(cr5)
-get_aic(cr5, 35, data = x) #31591.15
+get_aic(cr5, 67, data = x) #83462.4
+get_rsq_adj(cr5, 67) #0.005766099
 
-#remove if pic included and gratitude 
-cr6 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + 
-               device_length + as.factor(new_user) + 
-               category + first_punct + 
-               contain_question + all_lower + prior_effort + 
-               greeting + update + avg_tag_length + avg_score + frequent_tag + 
-               contain_toptag + contain_u + contain_a, data = x)
+#removing n_tags
+cr6 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(pic_included) + text_length + title_length + 
+                  device_length + post_weekday + as.factor(post_hour) + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
 summary(cr6)
-get_aic(cr6, 33, data = x) #31589.07
+get_aic(cr6, 63, data = x) # 83455.8
+get_rsq_adj(cr6, 63) #0.00624444
 
-cr7 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
-               category + first_punct + 
-               contain_question + all_lower + prior_effort + 
-               greeting + update + avg_tag_length + avg_score + 
-               contain_u + contain_a, data = x)
+#remove text_length
+cr7 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(pic_included) + title_length + 
+                  device_length + post_weekday + as.factor(post_hour) + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
 summary(cr7)
-get_aic(cr7, 27, data = x) #31580.82
+get_aic(cr7, 62, data = x) #83455.28
+get_rsq_adj(cr7, 62) #0.006333204
 
-#remove prior effort
-cr8 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
-               category + first_punct + 
-               contain_question + all_lower + 
-               greeting + update + avg_tag_length + avg_score + 
-               contain_u + contain_a, data = x)
+#remove title_length
+cr8 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  as.factor(pic_included) + 
+                  device_length + post_weekday + as.factor(post_hour) + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
 summary(cr8)
-get_aic(cr8, 26, data = x) #31581.15
+get_aic(cr8, 61, data = x) #83454.54
+get_rsq_adj(cr8, 61) #0.006427927
 
-#add prior effort back 
-cr7 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
-               category + first_punct + 
-               contain_question + all_lower + prior_effort + 
-               greeting + update + avg_score + 
-               contain_u + contain_a, data = x)
-summary(cr7)
-get_aic(cr7, 27, data = x) #31,580.82 70,819.65
+#remove pic_included
+cr9 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  device_length + post_weekday + as.factor(post_hour) + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
+                  update + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
+summary(cr9)
+get_aic(cr9, 60, data = x) #83454.3
+get_rsq_adj(cr9, 60) #0.0065088
+
+#remove prior_effort
+cr10 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
+                  device_length + post_weekday + as.factor(post_hour) + 
+                  title_questionmark + title_begin_wh + 
+                  capital_title + capital_text + text_all_lower + gratitude + 
+                  update + avg_tag_score + 
+                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+                  newline_ratio, data = x)
+summary(cr10)
+get_aic(cr10, 59, data = x) #83454.39 aic went up 
+get_rsq_adj(cr10, 59) #0.00658092
 

### 2017-08-04 summary_stats.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

@@
 library(survminer)
-
-proportion_answered <- sum(x$answered)/nrow(x)
+library(dplyr)
 ```
@@
 * `r nrow(x)` observations
-* `r round(proportion_answered * 100, digits = 2)` % of questions were answered
+* `r ncol(x)` variables
 
@@
 summary <- summary(x$time_until_answer)
+proportion_answered <- sum(x$answered)/nrow(x)
 ```
 
-* **minimum:** `r round(min(x$time_until_answer), 2)` hrs
-* **maximum:** `r round(max(x$time_until_answer), 2)` hrs (`r round(max(x$time_until_answer)/24, 2)` days)
+* **Shortest answer time:** `r round(min(x$time_until_answer), 2)` hrs
+* **Longest answer time (not answered):** `r round(max(x$time_until_answer), 2)` hrs (`r round(max(x$time_until_answer)/24, 2)` days)
 * **mean:** `r round(mean(x$time_until_answer), 2)` hrs (`r round(mean(x$time_until_answer)/24, 2)` days)
 * **median:** `r round(median(x$time_until_answer), 2)` hrs
-* **first quartile:** `r round(summary[2], 2)`hrs
+* **first quartile:** `r round(summary[2], 2)` hrs
 * **third quartile:** `r round(summary[5], 2)` hrs (`r round(summary[5]/24, 2)` days)
 * **IQR range:** `r round(summary[5] - summary[2], 2)` hrs (`r round((summary[5] - summary[2])/24, 2)` days)
+* `r round(proportion_answered*100, digits = 2)`% of questions were answered (complete)
 * Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions have been answered
@@
 ##### Based off of the Kaplan-Meier Estimator 
-```{r, echo = FALSE}
+```{r, include = FALSE}
 surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
@@
 
+* Table of percentiles:
+
 ```{r, percentiles, echo = FALSE}
@@
     + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
-    + highest quantile that exists: By `r round(quant$quantile[6], 2)` hrs (`r round(quant$quantile[6]/24, 2)` days) 64% of the questions have been answered
+    + Highest quantile that exists: By `r round(quant$quantile[6], 2)` hrs (`r round(quant$quantile[6]/24, 2)` days) 64% of the questions have been answered
 
-##### Survival Curves
+##### Kaplan-Meier Survival Curve
 
-* Survival curve shows that survival probability drops immediately after question is posted. 
-* Within a few hours after posting, the survival probability levels out (though it still decreases at a slow rate), and hovers around 0.35 (never hits 0).
-
-```{r, survival curves, echo = FALSE}
-ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", title = "KM Curve")
+```{r, echo = FALSE}
+ggsurvplot(KM, data = x, 
+           risk.table = "abs_pct", risk.table.title = "Total number at risk (percentage at risk)",
+           cumevents = TRUE, 
+           censor = FALSE, 
+           conf.int = TRUE, conf.int.style = "step", 
+           surv.median.line = "hv", 
+           xlab = "Time (hours)", 
+           surv.plot.height = 1, ggtheme = theme_bw(),
+           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 3)
 ```
 
+##### Kaplan-Meier Survival Curve showing up to 100 hours
+
 ```{r, echo = FALSE}
-ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", title = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
+ggsurvplot(KM, data = x, 
+           risk.table = "abs_pct", risk.table.title = "Total number at risk (percentage at risk)", 
+           cumevents = TRUE, 
+           conf.int = TRUE, conf.int.style = "step", 
+           censor = FALSE,
+           surv.median.line = "hv", 
+           xlab = "Time (hours)", 
+           xlim = c(0, 100), break.x.by = 10,
+           ylim = c(0, 0.7), break.y.by = 0.1,
+           surv.plot.height = 1, ggtheme = theme_bw(), 
+           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE)
 ```
 
-##### Reversing the survival curves
+* KM survival curve shows that the probability a question survives (remains unanswered) past a certain time drops immediately after question is posted.
+* Within ~ 100 hours after posting, the survival probability levels out (though it still decreases at a slow rate), and hovers around 0.35 (never hits 0).
+* Dashed marks around the lines represent the point-wise 95% confidence intervals
+* Vertical dashed line on the plots indicates the median survival time
+
+##### Reversing the survival curve
 
@@
 ggplot(reversed, aes(x = time, y = prob_ans)) + 
-  geom_line() + 
+  geom_line(na.rm = TRUE) + 
   scale_x_continuous("Time (hours)", limits = c(0,100)) + 
@@
 
-##### Instantaneous Hazard Rates (based off of KM estimates)
+##### Kaplan-Meier Type Instantaneous Hazard
 
@@
 h.hat <- epi.insthaz(KM, conf.level = 0.95) #instantaneous hazard on basis of KM 
-round(head(h.hat), 3)
+round(h.hat[1:10,], 4)
 ```
 
-* Max instant hazard rate: `r round(max(h.hat$est), 2)` at `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
-* Min instant hazard rate: `r round(min(h.hat$est), 2)`
+* Max KM instant hazard rate: `r round(max(h.hat$est), 2)` at `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
+* Min KM instant hazard rate: `r round(min(h.hat$est), 2)`
 * Interpretations: 
-    +
+    + h(t = 0.0083) = 0.0155: Questions that have not been answered 0.0083 (0.498 min) hours after posting, are estimated to be answered 0.015 times within the next 0.0006 hours (0.036 min). 
+    + h(t = 0.0164) = 0.9289: Questions that have not been answered 0.0164 (0.984 min) hours after posting, are estimated to be answered 0.9289 times within the next 0.0008 hours (0.048 min).
 
@@
   scale_x_continuous("Time (hours)") + 
-  scale_y_continuous("Instantaneous Hazard Rate") + 
-  ggtitle("Instantaneous Hazard Rate Plot")
+  scale_y_continuous("Instantaneous Hazard") + 
+  ggtitle("KM Type Instantaneous Hazard Plot")
 
 ggplot(h.hat, aes(x = time, y = est)) + 
-  geom_line() + 
-  scale_x_continuous("Time (hours)", limits = c(0,50)) + 
-  scale_y_continuous("Instantaneous Hazard Rate") + 
-  ggtitle("Instantaneous Hazard Rate Plot (zoomed in)")
+  geom_line(na.rm = TRUE) + 
+  scale_x_continuous("Time (hours)", limits = c(0,500), breaks = seq(0, 500, by = 50)) + 
+  scale_y_continuous("Instantaneous Hazard") + 
+  ggtitle("KM Type Instantaneous Hazard Plot showing up to 500 hours")
 ```
 
-* Instant hazard rate of a question getting answered drops to 0 and stays there pretty consistently after about 45 hours
+* After about 150 hours, the KM instant hazard of a question getting answered drops to 0 and stays there pretty consistently, with a few small spikes here and there
 * Right before that 45th hour, hazard spikes up twice to about 1.25
 
-##### Cumulative Hazard Rates
+##### Nelson-Aalen Type Instantaneous Hazard Rate
+
+```{r, echo = FALSE}
+fit <- data.frame(surv = s$surv, time = s$time, n.event = s$n.event, n.risk = s$n.risk)
+fit$h.tilde <- fit$n.event/fit$n.risk
+
+a <- fit %>%
+  select(time = time, estimate = h.tilde, num_experience_event = n.event, num_at_risk = n.risk)
+a[1:10,]
+```
+
+* Max Nelson-Aalen Type Hazard: `r round(max(fit$h.tilde, na.rm = TRUE),5)` at `r round(fit$time[which(fit$h.tilde == max(fit$h.tilde, na.rm = TRUE))],2)` hours
+* Min Nelson-Aalen Type Hazard: `r min(fit$h.tilde, na.rm = TRUE)` at `r round(fit$time[which(fit$h.tilde == min(fit$h.tilde, na.rm = TRUE))],2)` hours
+* Interpretations:
+    + h(t = 0.0083) = 0.000129: Given that a randomly selected question has not been answered by 0.0083 hours (0.498 min), the estimated probability that a question is answered in the next 0.0006 hours is 0.000129.
+    + h(t = 0.0164) = 0.000258: Given that a randomly selected question has not been answered by 0.0164 hours (0.984 min), the estiamted probability that a question is answered in the next 0.0008 hours is 0.000258.
+
+```{r, echo = FALSE}
+ggplot(fit, aes(x = time, y = h.tilde)) + 
+  geom_line() + 
+  scale_x_continuous("Time (hours)") + 
+  scale_y_continuous("Instantaneous Hazard") + 
+  ggtitle("Nelson-Aalen Type Instantaneous Hazard Plot")
+
+ggplot(fit, aes(x = time, y = h.tilde)) + 
+  geom_line(na.rm = TRUE) + 
+  scale_x_continuous("Time (hours)", limits = c(0,25)) + 
+  scale_y_continuous("Instantaneous Hazard") + 
+  ggtitle("Nelson-Aalen Type Instantaneous Hazard Plot, showing up to 25 hours")
+```
+
+##### Cumulative Hazard
 
@@
 ```{r, echo = FALSE}
+#Nelson-Aalen estimator of cumulative hazard
+fit$H.tilde <- cumsum(fit$h.tilde)
+
+ggplot(fit, aes(x = time, y = H.tilde)) +
+  geom_line(na.rm = TRUE) +
+  scale_x_continuous("Time (hours)", limits = c(0,1000), breaks = seq(0, 1000, by = 100)) +
+  scale_y_continuous("Cumulative Hazard Rate based off of Nelson Aalen Type") + 
+  ggtitle("Cumulative Hazard Plot (Nelson-Aalen)")
+
 #KM estimator of cumulative hazard 
-fit <- data.frame(surv = s$surv, time = s$time, n.event = s$n.event, n.risk = s$n.risk)
 fit$H.hat <- -log(fit$surv)
@@
   ggtitle("Cumulative Hazard Plot (KM)")
-
-#Nelson-Aalen estimator of cumulative hazard
-fit$H.tilde <- cumsum(fit$n.event/fit$n.risk)
-
-ggplot(fit, aes(x = time, y = H.tilde)) +
-  geom_line() +
-  scale_x_continuous("Time (hours)", limits = c(0,1000)) +
-  scale_y_continuous("Cumulative Hazard Rate based off of Nelson Aalen Type") + 
-  ggtitle("Cumulative Hazard Plot (Nelson-Aalen)")
 ```

### 2017-08-04 textual_analysis.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

@@
 * `r round(prop_one*100, 2)`% of texts have only 1 sentence
+
+### Ratio of newlines to text length
+
+```{r, echo = FALSE}
+x$newline_ratio <- str_count(x$text, pattern = "\n")/str_length(x$text)
+prop_newline <- sum(x$newline_ratio != 0)/nrow(x)
+```
+
+* `r round(prop_newline*100,2)`% of questions contain any newlines 
+* largest ratio: `r max(x$newline_ratio)`
+* smallest ratio: `r min(x$newline_ratio)`
+* median ratio: `r median(x$newline_ratio)`
+* mean ratio: `r mean(x$newline_ratio)`
+
+```{r, echo = FALSE}
+ggplot(x, aes(x = newline_ratio)) + 
+  geom_histogram(bins = 30) + 
+  ggtitle("Distribution of newline_ratios")
+```
+
+##### median newline_ratio grouped by answered/unanswered
+
+```{r, echo = FALSE}
+x %>%
+  group_by(answered) %>%
+  summarise(mean_ratio = mean(newline_ratio), median_ratio = median(newline_ratio))
+```

### 2017-08-04 MLEs in R.Rmd

---
title: "MLEs and evaluating fit for survival data"
author: "Shannon Pileggi"
date: "July 7, 2017"
output: html_document
---

### Objective
The objective of this vignette is to re-create the Minitab results from Lab 3 in STAT 417.  This includes computing maximum likelihood estimates of parametric distributions for survival data subject to censoring, and evaluating the fit of different parametric distributions to observed data.

### Packages required: 
+ the fitdistrplus package allows you to obtain maximum likelihood estimates for censored data with the fitdistcens function
+ the flexsurv package has some parametric distributions that are used in survival analysis that aren't availabe in base R (loglogistic, gompertz, etc.)
+ the survival library allows you to compute the empirical distribution function (EDF) estimate by using the Kaplan-Meier’s product-limit estimator
+ use the mosaic package for favstats
+ use the ggplot package to make overlayed qqplot
+ the flexsurv and fitdistrplus packages were built under R version 3.3.3, may require an R update

```{r,message=F,warning=F}
library(fitdistrplus)
library(flexsurv)
library(survival)
library(mosaic)
library(ggplot2)
```

### Example data
+ Use the rearrest data from STAT 417.
+ the months variable indicates time until rearrest
+ the censor variable indicates 1 for observed value, 0 for censored value
```{r}
dir <- file.path(getwd(),"data")
rearrest <- read.table(file.path(dir, "Rearrest.txt"),header=T)
head(rearrest)
tail(rearrest)
```

### Format of the data:
+ assume that we are only working with right censored data
+ the data needs two columns, named "left" and "right"
+ the left value is the time value
+ the right value is (1) the time value if not censored, (2) NA if censored
```{r}
#re-format rearrest data for fitdistrplus package
df<-data.frame(left=rearrest$months,right=rearrest$months)
df[rearrest$censor==0,2]<-NA
head(df)
tail(df)
```

### Identifying estimates
Now we can use the fitdistcens function to compute maximum likelihood estimates of the data for various distributions.  The first argument of the function is the data set name, and the second argument of the function is the name of the distribution.  You can use any of these distributions by removing the d https://stat.ethz.ch/R-manual/R-devel/library/stats/html/Distributions.html.  If you want to use a distribution that is not in this list, you can write a function for it (see help file for fitdistcens for an example).

```{r}
fit_exp<-fitdistcens(df, "exp") #exponential fit
summary(fit_exp)
#value of 1/lambda that matches Minitab results for the exponential distribution.
1/fit_exp$estimate
```
Note that the expontial distribution is parameterized as lambda in R, but 1/lambda in Minitab.  To obtain the value that corresponds to the Minitab output, we just need to calculate 1 over the parameter estimate.

The MLE's for the log-logistic distribution also does not match those from Minitab.  The shape parameter is inversed, which also affects the scale parameter.
```{r}
fit_llogis<-fitdistcens(df, "llogis") #log-logistic fit
summary(fit_llogis)
names(fit_llogis)
1/fit_llogis$estimate
```

The remaining three distributions have the same parameterization as Minitab.

```{r}
fit_logis<-fitdistcens(df, "logis") #logistic fit
summary(fit_logis)
fit_lnorm<-fitdistcens(df, "lnorm") #lognormal fit
summary(fit_lnorm)
fit_weibull<-fitdistcens(df, "weibull") #weibull fit
summary(fit_weibull)
```

### Evaluating fit of the distribution through cdf plots
According to the qqplots from Minitab, the Weibull or loglogistic appears to fit the data best and the logistic distribution fits the data the worst.  The Anderson-Darling statistic is the smallest for the loglogistic distribution, so that is deemed best fit.  One way demonstrated in the fitdistrplus package (but not in Minitab) to evaluate fit is with a CDF plot (empirical vs theoretical).  Though from this CDF plot it is not immediately clear that the log-logistic or weibull distributions fit best (though it does appear that logistic fits worse.)

```{r}
cdfcompcens(list(fit_exp,fit_llogis,fit_logis,fit_lnorm,fit_weibull),
            legendtext=c("exponential","log-logistic","logistic","lognormal","weibull"))
```

### Evaluating fit of the distribution through qq plots
When dealing with censored data, the empirical quantiles are estimated from Kaplan-Meier curves.  We first demonstrate this with the Weibull distribution, which had a good fit.

```{r}
KM <- survfit(Surv(months,censor)~1,data=rearrest,conf.type="plain")
#summary(KM)
plot(KM)
eq<-quantile(KM,probs=seq(0.01,0.99,by=0.01))
favstats(eq$quantile)
```
Note that the empirical quantiles only have 67 valid estimates - 32 are missing.  This is because the KM survival curve levels out at about 30%.  The max empirical quantile is 28.9.

We can obtain theoretical quantiles using the fitted models.  This does not result in any missing estimates.  The max theoretical quantile is 169.7.

```{r}
tq<-quantile(fit_weibull,probs=seq(0.01,0.99,by=0.01))
theo.quant<-as.numeric(as.vector(tq$quantiles[1,]))
favstats(theo.quant)
plot(theo.quant[1:67],eq$quantile[1:67],xlab="Theoretical Quantile",ylab="KM Quantile",main="Weibull")
abline(a=0,b=1)
```

Let's try this also for the logistic fit, which had the worst fit.
```{r}
tq<-quantile(fit_logis,probs=seq(0.01,0.99,by=0.01))
theo.quant<-as.numeric(as.vector(tq$quantiles[1,]))
favstats(theo.quant)
plot(theo.quant[1:67],eq$quantile[1:67],xlab="Theoretical Quantile",ylab="KM Quantile",main="Logistic")
abline(a=0,b=1)
```

Create one plot of all fits.
```{r}
tq_weibull<-quantile(fit_weibull,probs=seq(0.01,0.99,by=0.01))
tq_logis<-quantile(fit_logis,probs=seq(0.01,0.99,by=0.01))
tq_exp<-quantile(fit_exp,probs=seq(0.01,0.99,by=0.01))
tq_llogis<-quantile(fit_llogis,probs=seq(0.01,0.99,by=0.01))
tq_lnorm<-quantile(fit_lnorm,probs=seq(0.01,0.99,by=0.01))
stacked<-data.frame(distribution=c(rep("Weibull",99),
                                   rep("Logistic",99),
                                   rep("Exponential",99),
                                   rep("Log-Logistic",99),
                                   rep("Log-Normal",99)),
                    theo.quantile=c(as.numeric(as.vector(tq_weibull$quantiles[1,])),
                               as.numeric(as.vector(tq_logis$quantiles[1,])),
                               as.numeric(as.vector(tq_exp$quantiles[1,])),
                               as.numeric(as.vector(tq_llogis$quantiles[1,])),
                               as.numeric(as.vector(tq_lnorm$quantiles[1,]))),
                    emp.quantile=rep(eq$quantile,5))

ggplot(stacked,aes(x=theo.quantile,y=emp.quantile,group=distribution)) + geom_line(aes(color=distribution)) +
geom_abline(slope=1,intercept=0) +
xlim(-30,30)

```

### Remaining to do
```{r}
#gofstat(list(fit_exp,fit_llogis,fit_logis,fit_lnorm,fit_weibull),
#            fitnames=c("exponential","log-logistic","logistic","lognormal","weibull"))
```

- compute Anderson Darling statistic

### 2017-08-05 stackoverflow_comparison.Rmd
set up a CR model similar to one described in literature review, compared results

---
title: "Stack Overflow Comparison"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, importing data, include = FALSE}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
x <- out %>% 
  tbl_df() %>%
  filter(langid == "en")

x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
empty <- which(is.na(x$time_until_answer))
for (i in empty) {
  x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
}

library(stringr)
library(rebus)
library(survival)
```

### Fitting a model similar to the one described in "Min(e)d Your Tags"

##### Variables including:
* avg_score: (describe what the variables are)
* num_pop_tags
* n_images
* text_length
* title_length
* title_questionmark
* title_begin_wh
* is_weekend
* prior_effort

```{r, creating variables, include = FALSE}
#setting up the variables for the model

#tag popularity (frequency)
split_tags <- str_split(x$tags, ", ", simplify = TRUE)
#character vector of all tags (empty strings removed)
tag_vector <- as.vector(split_tags)
tag_vector <- tag_vector[which(tag_vector != "")]
unique_tags <- unique(tag_vector)

tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))

tag_freq <- tag_freq %>%
              arrange(desc(percent))

#creating average popularity (frequency) score variable
x$tag1 <- split_tags[,1]
x$tag2 <- split_tags[,2]
x$tag3 <- split_tags[,3]
x$tag4 <- split_tags[,4]

assign_score <- function(data, variable) {
  score <- rep(0, nrow(data))
  notempty <- which(data[[variable]] != "")
  for (i in notempty) {
    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
  }
  return(score)
}

x$score1 <- assign_score(x, "tag1")
x$score2 <- assign_score(x, "tag2")
x$score3 <- assign_score(x, "tag3")
x$score4 <- assign_score(x, "tag4")

x$avg_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
x$avg_score[is.nan(x$avg_score)] <- 0

#number of popular tag a question contains
threshold <- 0.005

num_pop <- function(var, threshold) {
  num_pop <- rep(0, nrow(x))
  num_pop[x[[var]] >= threshold] <- 1
  return(num_pop)
}

numpop1 <- num_pop("score1", threshold)
numpop2 <- num_pop("score2", threshold)
numpop3 <- num_pop("score3", threshold)
numpop4 <- num_pop("score4", threshold)

x$num_pop_tags <- numpop1 + numpop2 + numpop3 + numpop4

#text length
x$text_length <- str_length(x$text)

#title length
x$title_length <- str_length(x$title)

#end question mark? 
x$title_questionmark <- str_detect(x$title, pattern = QUESTION %R% END)

#begin with "wh"?
x$title_begin_wh <- str_detect(str_to_lower(x$title), pattern = "^wh")

#is weekend?
x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
x$is_weekend <- FALSE
x$is_weekend[x$post_weekday == "Saturday" | x$post_weekday == "Sunday"] <- TRUE

#num_active verb
x$prior_effort <- str_detect(str_to_lower(x$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))

x$num_prior_effort <- str_count(str_to_lower(x$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
```

```{r, model, echo = FALSE}
crSO <- coxph(Surv(time_until_answer, answered) ~ avg_score + num_pop_tags + n_images + text_length + title_length + title_questionmark + title_begin_wh + is_weekend + prior_effort, data = x)

summary(crSO)
```

```{r, echo = FALSE}
#function to get medians grouped by variables within the data set (since you can't see it in the boxplot)
#input variable with ""
get_medians <- function(var) {
  if (class(var) != "character" | class(var) != "factor") {
    medians <- x %>%
      group_by(as.factor(x[[var]])) %>%
      summarise(median_time = median(time_until_answer), n = n())
  } else {
    medians <- x %>%
      group_by(x[[var]]) %>%
      summarise(median_time = median(time_until_answer), n = n())    
  }
  return(medians)
}
```

```{r, echo = FALSE}
#boxplots for number of popular/frequent tags a question contains
ggplot(x, aes(x = as.factor(num_pop_tags), y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("Number of popular tags in a question") + 
  scale_y_continuous("Answer time (hours)") + 
  ggtitle("Boxplots of answer times grouped by number of popular tags")

get_medians("num_pop_tags")

#logrank test
surv_ob <- Surv(x$time_until_answer, x$answered, type = "right")
survdiff(surv_ob ~ as.factor(num_pop_tags), data = x)
```

```{r, echo = FALSE}
#boxplots for n_images
table(x$n_images)

ggplot(x, aes(x = as.factor(n_images), y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("number of images") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots of answer times grouped by number of images") 
#maybe group 8-13 together

get_medians("n_images")

survdiff(surv_ob ~ as.factor(n_images), data = x)
```

```{r, echo = FALSE}
#creating boxplots for title lengths
#using cut function to divide range of title lengths into intervals 
x$title_ints <- cut(x$title_length, breaks = 5)
table(x$title_ints)

ggplot(x, aes(x = title_ints, y = time_until_answer)) +
  geom_boxplot() + 
  scale_x_discrete("Intervals of title length (characters)") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots of answer times grouped by intervals of title length")

#logrank test
survdiff(surv_ob ~ title_ints, data = x)
```

```{r, echo = FALSE}
#creating boxplots for text lengths
x$text_ints <- cut(x$text_length, breaks = 5)
table(x$text_ints)

ggplot(x, aes(x = text_ints, y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("Intervals of text length (characters)") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots of answer times grouped by intervals of text length")

#logrank test
survdiff(surv_ob ~ text_ints, data = x)
```

```{r, echo = FALSE}
#boxplots for prior effort
ggplot(x, aes(x = prior_effort, y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("If the question text indicates prior effort") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots for answer times grouped by whether or not the question indicated prior effort")

get_medians("prior_effort")

ggplot(x, aes(x = as.factor(num_prior_effort), y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("Number of prior effort references in a questionss text") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots for answer times grouped by number of prior effort references")

get_medians("num_prior_effort")

#logrank tests
survdiff(surv_ob ~ prior_effort, data = x)
survdiff(surv_ob ~ as.factor(num_prior_effort), data = x)
```

```{r, echo = FALSE}
#boxplots for is_weekend
ggplot(x, aes(x = is_weekend, y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("Whether or not the question was posted on the weekend") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots for answer times grouped by weekend or not")

get_medians("is_weekend")

#logrank test
survdiff(surv_ob ~ is_weekend, data = x)
```

```{r, echo = FALSE}
x$wh_q[x$title_questionmark == TRUE & x$title_begin_wh == TRUE] <- 1
x$wh_q[x$title_questionmark == FALSE & x$title_begin_wh == FALSE] <- 2
x$wh_q[x$title_questionmark == TRUE & x$title_begin_wh == FALSE] <- 3
x$wh_q[x$title_questionmark == FALSE & x$title_begin_wh == TRUE] <- 4

#1: title contains both a question mark and begins with "wh"
#2: title doesn't contain a question mark and doesn't begin with "wh"
#3: title contains question mark but doesn't begin with "wh"
#4: title doesn't contain question mark but does start with "wh"

ggplot(x, aes(x = as.factor(wh_q), y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("Interaction between title_questionmark and title_begin_wh") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots for answer times grouped by levels of interaction")

ggplot(x, aes(x = title_questionmark, y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("Whether or not the title contains a question mark") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots for answer times grouped by question mark")

ggplot(x, aes(x = title_begin_wh, y = time_until_answer)) + 
  geom_boxplot() + 
  scale_x_discrete("Whether or not the title begins with 'Wh'") + 
  scale_y_continuous("Time until answer (hours)") + 
  ggtitle("Boxplots for answer times grouped by 'Wh'")

get_medians("wh_q")
get_medians("title_questionmark")
get_medians("title_begin_wh")

#logrank tests
survdiff(surv_ob ~ as.factor(wh_q), data = x)
survdiff(surv_ob ~ title_questionmark, data = x)
survdiff(surv_ob ~ title_begin_wh, data = x)
```

# STILL NEED TO DO 
* figure out what's going on with the HR for avg_score
* compare how these results are different from stack overflows, why are they different?
* make boxplots easier to read, find a way to actually see the bottom halves of boxplots, ignore outliers? 
* for boxplots that only have 1 observation in them, figure out how to group it with a diff value? 
* make this report easier to read

### 2017-08-05 tag_exploration.Rmd
set up a CR model similar to one described in literature review, compared results

@@
 ggplot(top50, aes(x = fct_reorder(tag, -percent), y = percent)) + 
-  geom_col() + 
+  geom_point() + 
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
@@
 x$score4 <- assign_score(x, "tag4")
+
+ggplot(x, aes(x = score1)) + 
+  geom_histogram()
+ggplot(x, aes(x = score2)) + geom_histogram()
+ggplot(x, aes(x = score3)) + geom_histogram()
+ggplot(x, aes(x = score4)) + geom_histogram()
 
@@
 plot_surv(KM_popular, data = x)
+```
+
+##### Counting of popular tags a question has 
+```{r}
+threshold <- 0.005
+
+num_pop <- function(var, threshold) {
+  num_pop <- rep(0, nrow(x))
+  num_pop[x[[var]] >= threshold] <- 1
+  return(num_pop)
+}
+
+numpop1 <- num_pop("score1", threshold)
+numpop2 <- num_pop("score2", threshold)
+numpop3 <- num_pop("score3", threshold)
+numpop4 <- num_pop("score4", threshold)
+
+x$num_freq_tags <- numpop1 + numpop2 + numpop3 + numpop4
+
 ```

### 2017-08-08 model_fitting.Rmd
finished comparing results to stack overflow model, continued with model fitting, added interactions, updated hours

@@
 library(survival) 
+library(stats)
 ```
@@
 ```{r, include = FALSE}
-#function to get AIC statistics
-get_aic <- function(cr_obj, num_parameters, data) {
-  aic <- (-2*cr_obj$loglik[2]) + (2*num_parameters)
-  return(aic)
-}
 
@@
 x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
-x$post_d <- format(x$post_datetime, "%m/%d/%y")
-x$post_time <- format(x$post_datetime, " %H:%M:%S")
 x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
@@
 x$post_ampm[x$post_hour >= 12 & x$post_hour < 17] <- "Afternoon" #noon - 5pm 
-x$postampm[x$post_hour >= 17 & x$post_hour < 20] <- "Evening" #5pm - 8pm
-
-#whether or not it was cateogorized correctly
-x$categorized <- 0
-x$categorized[!is.na(x$category)] <- 1
+x$post_ampm[x$post_hour >= 17 & x$post_hour < 20] <- "Evening" #5pm - 8pm
 
@@
 #if text contains end punctuation
-x$contain_punct <- FALSE
-x$contain_punct[!is.na(x$text_till_punct)] <- TRUE
+x$text_contain_punct <- FALSE
+x$text_contain_punct[!is.na(x$text_till_punct)] <- TRUE
 
@@
 split_tags <- str_split(x$tags, ", ", simplify = TRUE)
-
 #character vector of all tags (empty strings removed)
@@
 tag_vector <- tag_vector[which(tag_vector != "")]
-
 unique_tags <- unique(tag_vector)
@@
 
+#number of "popular" tags a question contains
+#setting threshold to define popular tags: tag must occur 0.5% of the time to be considered "popular"
+threshold <- 0.005
+#function that sets num_pop to 1 if the tag is considered popular, 0 if not
+num_pop <- function(var, threshold) {
+  num_pop <- rep(0, nrow(x))
+  num_pop[x[[var]] >= threshold] <- 1
+  return(num_pop)
+}
+numpop1 <- num_pop("score1", threshold)
+numpop2 <- num_pop("score2", threshold)
+numpop3 <- num_pop("score3", threshold)
+numpop4 <- num_pop("score4", threshold)
+#finding the total number of popular tags for a question
+x$num_pop_tags <- numpop1 + numpop2 + numpop3 + numpop4
+
+x$is_weekend <- FALSE
+x$is_weekend[x$post_weekday == "Saturday" | x$post_weekday == "Sunday"] <- TRUE
+
 ```
@@
 ```{r, echo = FALSE}
-cr1 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
-                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
-                  text_end_punct + title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  greeting + update + avg_tag_length + max_tagwords + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+cr1 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + device_length + as.factor(n_tags) + as.factor(pic_included) + new_user + post_weekday + post_ampm + contain_unanswered + contain_answered + avg_tag_length + avg_tag_score + num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + capital_title + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio, data = x)
+
+summary(cr1)
+library(stats) #to get AIC
+AIC(cr1, k = 2) #83451.51
+```
+* fit model text_end_punct, compared AIC to that of model containing text_till_punct (text_till_punct had lower AIC)
+* fit model with max_tagwords instead of avg_tag_length (avg_tag_length had lower) 
+* fit model with post_hour instead of post_ampm (post_ampm had lower)
+* fit model with is_weekend instead of post_weekend (post_weekday lower)
+* fit with num_prior_effort, prior_effort is lower
+* fit with n_images instead of pic_included, n_images is better
+* fit with tag_included instead of n_tags, tag_included is better
+
+```{r, echo = FALSE}
+#the new full model (best combination of all variables) 
+cr2 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_length + avg_tag_score + 
+                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + gratitude + greeting + update + 
                  newline_ratio, data = x)
-s <- summary(cr1)
-s$rsq
-get_aic(cr1, 72, data = x) #83471.68
-get_rsq_adj(cr1, 72) #0.00513921
+AIC(cr2, k = 2) #83445.74
+summary(cr2)
+```
 
-#removed greeting and text_end punct (p-values > .8)
-cr2 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
-                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_length + max_tagwords + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+```{r, echo = FALSE}
+#remove avg_tag_length
+cr3 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + gratitude + greeting + update + 
                  newline_ratio, data = x)
-summary(cr2)
-get_aic(cr2, 70, data = x) #83467.71
-get_rsq_adj(cr2, 70) #0.005397121
+AIC(cr3, k = 2) #83443.75
+summary(cr3)
+```
 
-#removed max_tagwords
-cr3 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
-                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_length + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+```{r, echo = FALSE}
+#remove greeting
+cr4 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + gratitude + update + 
                  newline_ratio, data = x)
-summary(cr3)
-get_aic(cr3, 69, data = x) #83465.91
-get_rsq_adj(cr3, 69) #0.005520927
+AIC(cr4, k = 2) #83441.81
+summary(cr4)
+```
 
-#removed avg_tag_length
-cr4 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
-                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+```{r, echo = FALSE}
+#remove gratitude
+cr5 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
                  newline_ratio, data = x)
-summary(cr4)
-get_aic(cr4, 68, data = x) #83463.95
-get_rsq_adj(cr4, 68) #0.005649183
+AIC(cr5, k = 2) #83439.96
+summary(cr5)
+```
 
-#removed text_till_punct
-cr5 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
-                  device_length + post_weekday + as.factor(post_hour) + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+```{r, echo = FALSE}
+#remove text_till_punct
+cr6 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 num_pop_tags + title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
                  newline_ratio, data = x)
-summary(cr5)
-get_aic(cr5, 67, data = x) #83462.4
-get_rsq_adj(cr5, 67) #0.005766099
+AIC(cr6, k = 2) #83448.41
+summary(cr6)
+```
 
-#removing n_tags
-cr6 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(pic_included) + text_length + title_length + 
-                  device_length + post_weekday + as.factor(post_hour) + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+```{r, echo = FALSE}
+#remove num_pop_tags
+cr7 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
                  newline_ratio, data = x)
-summary(cr6)
-get_aic(cr6, 63, data = x) # 83455.8
-get_rsq_adj(cr6, 63) #0.00624444
+AIC(cr7, k = 2) #83437.22
+summary(cr7)
+```
 
+```{r, echo = FALSE}
+#remove title_length 
+cr8 <- coxph(Surv(time_until_answer, answered) ~ category + text_length + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
+                 newline_ratio, data = x)
+AIC(cr8, k = 2) #83436.49
+summary(cr8)
+```
+
+```{r, echo = FALSE}
 #remove text_length 
-cr7 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(pic_included) + title_length + 
-                  device_length + post_weekday + as.factor(post_hour) + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+cr9 <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
                  newline_ratio, data = x)
-summary(cr7)
-get_aic(cr7, 62, data = x) #83455.28
-get_rsq_adj(cr7, 62) #0.006333204
+AIC(cr9, k = 2) #83435.68
+summary(cr9)
+```
 
-#remove title_length
-cr8 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  as.factor(pic_included) + 
-                  device_length + post_weekday + as.factor(post_hour) + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
+```{r, echo = FALSE}
+#remove tag_included 
+cr10 <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
                  newline_ratio, data = x)
-summary(cr8)
-get_aic(cr8, 61, data = x) #83454.54
-get_rsq_adj(cr8, 61) #0.006427927
+AIC(cr10, k = 2) #83435.13
+summary(cr10)
+```
 
-#remove pic_included
-cr9 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  device_length + post_weekday + as.factor(post_hour) + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
-                  update + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
-                  newline_ratio, data = x)
-summary(cr9)
-get_aic(cr9, 60, data = x) #83454.3
-get_rsq_adj(cr9, 60) #0.0065088
+* next variable I would remove would be n_images, but doing this increases the AIC, removing any other variable increases the AIC
+* also need to think about if want to keep contain_answered and contain_unanswered (is there an issue with the category var)
 
-#remove prior_effort
-cr10 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
-                  device_length + post_weekday + as.factor(post_hour) + 
-                  title_questionmark + title_begin_wh + 
-                  capital_title + capital_text + text_all_lower + gratitude + 
-                  update + avg_tag_score + 
-                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
-                  newline_ratio, data = x)
-summary(cr10)
-get_aic(cr10, 59, data = x) #83454.39 aic went up 
-get_rsq_adj(cr10, 59) #0.00658092
+```{r, include = FALSE}
+#function to compare nested models 
+compare_nested <- function(crfull, crreduced, param_full, param_reduced) {
+  like_f <- crfull[[loglik]]
+  like_r <- crreduced[[loglik]]
+  stat <- 2*(like_f - like_r)
+}
+```
 
+```{r, echo = FALSE}
+#added interaction between title_questionmark and title_begin_wh
+cr11 <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
+                 newline_ratio + title_questionmark*title_begin_wh, data = x)
+AIC(cr11, k = 2) #83429.68
+summary(cr11)
 ```
+
+```{r, echo = FALSE}
+#added interaction between new_user and update
+cr12 <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
+                 newline_ratio + title_questionmark*title_begin_wh + new_user*update, data = x)
+AIC(cr12, k = 2) #83425.59
+summary(cr12)
+```
+
+```{r, echo = FALSE}
+#added interaction between new_user and newline_ratio
+cr13 <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
+                 newline_ratio + title_questionmark*title_begin_wh + new_user*update + 
+                 new_user*newline_ratio, data = x)
+AIC(cr13, k = 2) #83422.18
+summary(cr13)
+```
+
+```{r, echo = FALSE}
+#added interaction between category and device length
+cr14 <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
+                 newline_ratio + title_questionmark*title_begin_wh + new_user*update + 
+                 new_user*newline_ratio + category*device_length, data = x)
+AIC(cr14, k = 2) #83335.8
+summary(cr14)
+```

### 2017-08-08 stackoverflow_comparison.Rmd
finished comparing results to stack overflow model, continued with model fitting, added interactions, updated hours

@@
 library(survival)
+library(ggplot2)
 ```
 
-### Fitting a model similar to the one described in "Min(e)d Your Tags"
+## Fitting a model similar to the one described in "Min(e)d your tags" for Stack Overflow
 
-##### Variables including:
-* avg_score: (describe what the variables are)
-* num_pop_tags
-* n_images
-* text_length
-* title_length
-* title_questionmark
-* title_begin_wh
-* is_weekend
-* prior_effort
+##### Including variables: 
+* **avg_score:** The frequency score of a tag is defined as the proportion of times it occurs in the data (the proportion of questions that contain it as a tag).
+The avg_score (average score) for a question is equal to the average of the proportions for all of a question's tags.
+* **num_pop_tags:** Tags were grouped into popular/unpopular tags based on a threshold frequency score.
+num_pop_tags is equal to the number of popular tags (out of a maximum of 4) a question contains.
+* **n_images:** The number of images a question contains. (Most don't include any images)
+* **text_length:** The length (in characters) of a question's text. 
+* **title_length:** The length (in characters) of a question's title.
+* **title_questionmark:** Whether or not the title ends with a question mark. 
+* **title_begin_wh:** Whether or not the title begins with a "Wh".
+* **is_weekend:** Whether or not the question was posted over the weekend. 
+* **prior_effort:** Whether or not the question contains action verbs like "tried", "searched", "replaced", that indicate that the asker made an effort to research/solve their problem prior to posting the question.
+Prior effort may be an indicator of question quality.
 
-```{r, creating variables, include = FALSE}
-#setting up the variables for the model
+##### Variables I excluded:
+* **tag_specificity:** The "togetherness" of two tags, extent to which the two co-occur in a question. Measured using the point-wise mutual information. 
+* **num_subs_ans:** Average number of active subscribers for individual tags in each question. Excluded because currently there is no option to subscribe to a certain tag on Answers
+* **percent_subs_ans:** % of active subscribers
+* **num_subs_t, and percent_subs_t:** Number and percentage of responsive subscribers. 
+* **num_code_snippet and code_len:** Number of code segments and length of the code (in characters) a question contains.
+* **num_selfref:** Number of self references like "I", "myself", "we".
+Used in Stack Overflow analysis to indicate if the asker has done research/work prior to posting the question.
+After examining questions that contained self-references, I found that it would not be a good indicator of prior effort (ex: "I need help", "Help me").
 
+##### Differences between the Stack Overflow and iFixit Answers
+* Statistics: 
+    + proportion of questions answered on SO: 91.3%, Answers: 63.8%
+    + median time until answer for SO: 16 minutes, Answers: 9 hours
+    + Questions answered in <= 1 hour for SO: 63.5%, Answers: 26.6%
+
+* Tagging system:
+    + **SO:** can include a maximum of 5 tags (4 on Answers)
+    + **SO:** can subscribe to certain tags/favorite tags (can only subscribe to certain questions on Answers)
+
+* Analysis of tag-based features
+    + **S0:** tag-based features were the most powerful predictors of response time. 
+    + As tag popularity increased, or as the number of popular tags increased for a question, response time decreased
+    + **Answers:** found similar results.
+Questions that contain popular tags have faster median response times than questions without popular tags.
+However, tag based variables are barely signficant as predictors in the CR model (p-values = 0.05).
+Probably due to the inconsistent nature of Answers' tags.
+
+* Analysis of title and text length variables
+    + **SO:** as both post and title length increases, response time also increases (succinct questions tended to recieve faster responses). 
+    + **Answers:** didn't see as much of a clear-cut trend that SO analysis saw.
+Titles/texts that are not too long/short recieve the fastest response times (character length ranges in the middle have the lowest median answer times)
+    + Title_length is insignificant in the CR model, but text_length is
+
+* Analysis of action verbs
+    + **SO:** as number of action verbs increases, response time decreases slightly 
+    + **Answers:** found similar results. Questions that included more action verbs have lower median response times, but is insignficant in the CR model
+
+* Analysis of question mark and "Wh" 
+    + **SO:** questions that contain "?" or/and start with "wh" in their title are more likely to recieve faster responses. 
+    + **Answers:** found similar results. Questions that have titles that include ? and begin with "Wh" or don't begin with "Wh", have faster median response times. 
+    + This interaction term is signficant in the CR model (individual effects of title_begin_wh is not)
+
+* Other correlations found
+    + **SO:** n_images, and posting on weekend days were correlated with lower response times. 
+    + **Answers:** as questions include more images, response time decreases. But found that questions posted on weekend days have higher median response times.
+
+```{r, setting up the variables, include = FALSE}
 #tag popularity (frequency)
 split_tags <- str_split(x$tags, ", ", simplify = TRUE)
-#character vector of all tags (empty strings removed)
 tag_vector <- as.vector(split_tags)
@@
 
+#data frame of each unique tag along with the proportion of times it occurs in the dataset 
 tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
-
 tag_freq <- tag_freq %>%
@@
 x$tag4 <- split_tags[,4]
-
+#function to take each tag, match it with one in the tag_freq data frame, and return the proportion
 assign_score <- function(data, variable) {
@@
 }
-
 x$score1 <- assign_score(x, "tag1")
@@
 x$score4 <- assign_score(x, "tag4")
-
+#calculating the average score for each question
 x$avg_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
@@
 
-#number of popular tag a question contains
+#number of "popular" tags a question contains
+#setting threshold to define popular tags: tag must occur 0.5% of the time to be considered "popular"
 threshold <- 0.005
-
+#function that sets num_pop to 1 if the tag is considered popular, 0 if not
 num_pop <- function(var, threshold) {
@@
 }
-
 numpop1 <- num_pop("score1", threshold)
@@
 numpop4 <- num_pop("score4", threshold)
-
+#finding the total number of popular tags for a question
 x$num_pop_tags <- numpop1 + numpop2 + numpop3 + numpop4
@@
 
-#num_active verb
+#whether or not the question contains words indicating prior effort
 x$prior_effort <- str_detect(str_to_lower(x$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
 
+#the number of times a question uses action verbs to indicate prior effort 
 x$num_prior_effort <- str_count(str_to_lower(x$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
@@
 
-```{r, model, echo = FALSE}
-crSO <- coxph(Surv(time_until_answer, answered) ~ avg_score + num_pop_tags + n_images + text_length + title_length + title_questionmark + title_begin_wh + is_weekend + prior_effort, data = x)
+```{r, functions, include = FALSE}
+#function to get AIC statistics
+get_aic <- function(cr_obj, num_parameters, data) {
+  aic <- (-2*cr_obj$loglik[2]) + (2*num_parameters)
+  return(aic)
+}
 
-summary(crSO)
-```
+#function to calculate r-square adjusted
+get_rsq_adj <- function(cr_obj, k) {
+  r <- unname(summary(cr_obj)$rsq[1])
+  n <- summary(cr_obj)$n
+  radj <- 1- (((1- (r**2)) * (n - 1))/(n-k-1))
+  return(radj)
+}
 
-```{r, echo = FALSE}
-#function to get medians grouped by variables within the data set (since you can't see it in the boxplot)
-#input variable with ""
+#function to get median answer times grouped by specified variables (since you can't see it in the boxplot)
+#input var using ""
 get_medians <- function(var) {
@@
       group_by(as.factor(x[[var]])) %>%
-      summarise(median_time = median(time_until_answer), n = n())
+      summarise(median_time = round(median(time_until_answer), 2), n = n())
   } else {
@@
       group_by(x[[var]]) %>%
-      summarise(median_time = median(time_until_answer), n = n())    
+      summarise(median_time = round(median(time_until_answer), 2), n = n())    
   }
+  names(medians)[1] <- var
   return(medians)
 }
+
+#function to create boxplot 
+get_boxplot <- function(var, xaxis, title) {
+  if (class(var) != "character" | class(var) != "factor") {
+    ggplot(x, aes(x = as.factor(x[[var]]), y = time_until_answer)) + 
+      geom_boxplot() + 
+      scale_x_discrete(xaxis) + 
+      scale_y_continuous("Answer time (hours)") + 
+      ggtitle(paste("Boxplots of answer times grouped by", title))
+  } else {
+    ggplot(x, aes(x = x[[var]], y = time_until_answer)) + 
+      geom_boxplot() + 
+      scale_x_discrete(xaxis) + 
+      scale_y_continuous("Answer time (hours)") + 
+      ggtitle(paste("Boxplots of answer times grouped by", title))
+  }
+}
+
 ```
+
+## Cox Regression Model
+
+* look into the HR for avg_score
+* when avg_score is taken out of model, AIC shoots up
+
+```{r, model, echo = FALSE}
+crSO <- coxph(Surv(time_until_answer, answered) ~ avg_score + num_pop_tags + n_images + text_length + title_length + title_questionmark + title_begin_wh + is_weekend + prior_effort + title_questionmark*title_begin_wh, data = x)
+
+summary(crSO)
+# AIC(crSO, k = 2)
+# 
+# #took out prior_effort and added num_prior_effort
+# crSO1 <- coxph(Surv(time_until_answer, answered) ~ avg_score + num_pop_tags + n_images + text_length + title_length + title_questionmark + title_begin_wh + is_weekend + num_prior_effort + title_questionmark*title_begin_wh, data = x)
+# summary(crSO1)
+# AIC(crSO1, k = 2)
+```
+
+## Exploring each variable
+
+### num_pop_tags
 
@@
 #boxplots for number of popular/frequent tags a question contains
-ggplot(x, aes(x = as.factor(num_pop_tags), y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("Number of popular tags in a question") + 
-  scale_y_continuous("Answer time (hours)") + 
-  ggtitle("Boxplots of answer times grouped by number of popular tags")
+get_boxplot("num_pop_tags", xaxis = "Number of popular tags", title = "num_pop_tags")
+```
 
+##### Median answer times
+
+```{r, echo = FALSE}
 get_medians("num_pop_tags")
+```
 
-#logrank test
+##### log-rank test
+
+```{r, echo = FALSE}
 surv_ob <- Surv(x$time_until_answer, x$answered, type = "right")
@@
 ```
+
+### n_images
+
+##### frequency table
 
@@
 
-ggplot(x, aes(x = as.factor(n_images), y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("number of images") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots of answer times grouped by number of images") 
-#maybe group 8-13 together
+#creating a new variable for n_images to group questions that have over 6 images as one (>=8)
+x$new_n_images <- as.character(x$n_images)
+x$new_n_images[x$n_images >= 6] <- ">= 6"
+x$new_n_images <- factor(x$new_n_images, levels = c("0", "1", "2", "3", "4", "5", ">= 6"))
 
-get_medians("n_images")
+get_boxplot("new_n_images", xaxis = "Number of images", title = "n_images")
+```
 
+##### Median answer times
+
+```{r, echo = FALSE}
+get_medians("new_n_images")
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
 survdiff(surv_ob ~ as.factor(n_images), data = x)
@@
 
+### title_length
+
 ```{r, echo = FALSE}
-#creating boxplots for title lengths
 #using cut function to divide range of title lengths into intervals 
 x$title_ints <- cut(x$title_length, breaks = 5)
-table(x$title_ints)
 
-ggplot(x, aes(x = title_ints, y = time_until_answer)) +
-  geom_boxplot() + 
-  scale_x_discrete("Intervals of title length (characters)") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots of answer times grouped by intervals of title length")
+get_boxplot("title_ints", xaxis = "Intervals of title length (characters)", title = "title_ints")
+```
 
-#logrank test
+##### Median answer times
+
+```{r, echo = FALSE}
+get_medians("title_ints")
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
 survdiff(surv_ob ~ title_ints, data = x)
@@
 
+### text_length
+
 ```{r, echo = FALSE}
-#creating boxplots for text lengths
 x$text_ints <- cut(x$text_length, breaks = 5)
-table(x$text_ints)
 
-ggplot(x, aes(x = text_ints, y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("Intervals of text length (characters)") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots of answer times grouped by intervals of text length")
+get_boxplot("text_ints", xaxis = "Intervals of text length (characters)", title = "text_ints")
+#figure out how to make it not scientific notation 
+```
 
-#logrank test
+##### Median answer times
+
+```{r, echo = FALSE}
+get_medians("text_ints")
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
 survdiff(surv_ob ~ text_ints, data = x)
@@
 
+### prior_effort
+
 ```{r, echo = FALSE}
-#boxplots for prior effort
-ggplot(x, aes(x = prior_effort, y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("If the question text indicates prior effort") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots for answer times grouped by whether or not the question indicated prior effort")
-
-get_medians("prior_effort")
-
-ggplot(x, aes(x = as.factor(num_prior_effort), y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("Number of prior effort references in a questionss text") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots for answer times grouped by number of prior effort references")
-
-get_medians("num_prior_effort")
-
-#logrank tests
-survdiff(surv_ob ~ prior_effort, data = x)
-survdiff(surv_ob ~ as.factor(num_prior_effort), data = x)
+get_boxplot("prior_effort", xaxis = "Whether or not the question indicates prior effort",
+            title = "prior_effort")
 ```
 
+##### Median answer times
+
 ```{r, echo = FALSE}
-#boxplots for is_weekend
-ggplot(x, aes(x = is_weekend, y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("Whether or not the question was posted on the weekend") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots for answer times grouped by weekend or not")
+get_medians("prior_effort")
+```
 
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_ob ~ prior_effort, data = x)
+```
+
+### num_prior_effort
+
+```{r, echo = FALSE}
+x$new_num_prior <- as.character(x$num_prior_effort)
+x$new_num_prior[x$num_prior_effort >= 4] <- ">= 4"
+x$new_num_prior <- factor(x$new_num_prior, levels = c("0", "1", "2", "3", ">= 4"))
+
+get_boxplot("new_num_prior", xaxis = "Number of times an action verb is used", 
+            title = "num_prior_effort")
+```
+
+##### Median answer times
+
+```{r, echo = FALSE}
+get_medians("new_num_prior")
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_ob ~ as.factor(new_num_prior), data = x)
+```
+
+### is_weekend
+
+```{r, echo = FALSE}
+get_boxplot("is_weekend", xaxis = "Whether or not the question was posted over a weekend", 
+            title = "is_weekend")
+```
+
+##### Median answer times
+
+```{r, echo = FALSE}
 get_medians("is_weekend")
+```
 
-#logrank test
+##### log-rank test
+
+```{r, echo = FALSE}
 survdiff(surv_ob ~ is_weekend, data = x)
@@
 
+### title_questionmark
+
 ```{r, echo = FALSE}
+get_boxplot("title_questionmark", xaxis = "Whether or not the title ends with a questionmark", 
+            title = "title_questionmark")
+```
+
+##### Median answer times
+
+```{r, echo = FALSE}
+get_medians("title_questionmark")
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_ob ~ title_questionmark, data = x)
+```
+
+### title_begin_wh
+
+```{r, echo = FALSE}
+get_boxplot("title_begin_wh", xaxis = "Whether or not the title begins with `Wh`", 
+            title = "title_begin_wh")
+```
+
+##### Median answer times
+
+```{r, echo = FALSE}
+get_medians("title_begin_wh")
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_ob ~ title_begin_wh, data = x)
+```
+
+### Interaction between title_questionmark and title_begin_wh (wh_q)
+
+* Defining each level:
+    + 1: title begins with "Wh" and ends with ?
+    + 2: title contains neither
+    + 3: title doesn't begin with "Wh" but does end with ?
+    + 4: title begins with "Wh" but doesn't end with ?
+
+```{r, echo = FALSE}
+#creating the varaible
 x$wh_q[x$title_questionmark == TRUE & x$title_begin_wh == TRUE] <- 1
@@
 
-#1: title contains both a question mark and begins with "wh"
-#2: title doesn't contain a question mark and doesn't begin with "wh"
-#3: title contains question mark but doesn't begin with "wh"
-#4: title doesn't contain question mark but does start with "wh"
-
-ggplot(x, aes(x = as.factor(wh_q), y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("Interaction between title_questionmark and title_begin_wh") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots for answer times grouped by levels of interaction")
-
-ggplot(x, aes(x = title_questionmark, y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("Whether or not the title contains a question mark") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots for answer times grouped by question mark")
-
-ggplot(x, aes(x = title_begin_wh, y = time_until_answer)) + 
-  geom_boxplot() + 
-  scale_x_discrete("Whether or not the title begins with 'Wh'") + 
-  scale_y_continuous("Time until answer (hours)") + 
-  ggtitle("Boxplots for answer times grouped by 'Wh'")
-
-get_medians("wh_q")
-get_medians("title_questionmark")
-get_medians("title_begin_wh")
-
-#logrank tests
-survdiff(surv_ob ~ as.factor(wh_q), data = x)
-survdiff(surv_ob ~ title_questionmark, data = x)
-survdiff(surv_ob ~ title_begin_wh, data = x)
+get_boxplot("wh_q", xaxis = "Levels of the interaction", 
+            title = "title_questionmark*title_begin_wh")
 ```
 
-# STILL NEED TO DO 
-* figure out what's going on with the HR for avg_score
-* compare how these results are different from stack overflows, why are they different?
-* make boxplots easier to read, find a way to actually see the bottom halves of boxplots, ignore outliers? 
-* for boxplots that only have 1 observation in them, figure out how to group it with a diff value? 
-* make this report easier to read
+##### Median answer times
+
+```{r, echo = FALSE}
+get_medians("wh_q")
+```
+
+##### log-rank test
+
+```{r, echo = FALSE}
+survdiff(surv_ob ~ as.factor(wh_q), data = x)
+```

### 2017-08-08 tag_exploration.Rmd
finished comparing results to stack overflow model, continued with model fitting, added interactions, updated hours

@@
 surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
-survdiff(surv_object ~ popular_tag, data = x)
+survdiff(surv_object ~ frequent_tag, data = x)
 
-KM_popular <- survfit(surv_object ~ popular_tag, data = x)
-plot_surv(KM_popular, data = x)
+KM_frequent <- survfit(surv_object ~ frequent_tag, data = x)
+plot_surv(KM_frequent, data = x)
 ```

### 2017-08-08 exploratory analysis/freq_words.Rmd
reorganized files

--- 2017-08-03 freq_words.Rmd
@@
 
-#function to clean corpus
-clean_corpus <- function(corpus){
+#function to clean corpus, can specify stopwords to remove 
+clean_corpus <- function(corpus, stopwrds = NULL){
+  if (is.null(stopwrds)) {
     corpus <- tm_map(corpus, stripWhitespace)
     corpus <- tm_map(corpus, content_transformer(tolower))
-  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
+    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+    return(corpus)    
+  } else {
+    corpus <- tm_map(corpus, stripWhitespace)
+    corpus <- tm_map(corpus, content_transformer(tolower))
+    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix", stopwrds))
     return(corpus)
   }
+}
 
-#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n is an optional argument 
-freq_terms <- function(vec, n = NULL) {
+#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
+freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
   source <- VectorSource(vec)
   corpus <- VCorpus(source)
+
+  if (is.null(stopwrds)) {
     cleaned_corpus <- clean_corpus(corpus) 
-  dtm <- DocumentTermMatrix(cleaned_corpus)
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
     m <- as.matrix(dtm) 
@@
     freq_df <- data.frame(word = names(freq), frequency = unname(freq))    
+  } else {
+    cleaned_corpus <- clean_corpus(corpus, stopwrds) 
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
+    m <- as.matrix(dtm) 
+    freq <- colSums(m)
+    freq <- sort(freq, decreasing = TRUE)
+    freq_df <- data.frame(word = names(freq), frequency = unname(freq))
+  }
 
@@
 ###### words that appear more than 1% of the time in unanswered questions and are more likely (ratio < 1) to be used in unanswered questions
+
 ```{r, echo = FALSE}

### 2017-08-08 exploratory analysis/summary_stats.Rmd
reorganized files

--- 2017-08-04 summary_stats.Rmd
@@
 * Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions have been answered
+* Within 1 day, `r round((sum(x$time_until_answer <= 24)/nrow(x))*100,2)`% of the questions have been answered
 

### 2017-08-08 exploratory analysis/textual_analysis.Rmd
reorganized files

--- 2017-08-04 textual_analysis.Rmd
@@
 #function to plot survival curves with ggplot
-plot_surv <- function(survfit, data, xlim) {
+plot_surv <- function(survfit, data, xlim = NULL) {
+  library(ggfortify)
+  library(directlabels)
 
@@
 ##### Log-rank test
+
 ```{r, echo = FALSE}
@@
 
-### Checking if text is in single caps (all lower or upper case)
+### Checking if text is in single caps (all lower case)
 

### 2017-08-08 functions.Rmd
reorganized files

--- 2017-07-22 functions.Rmd
@@
 ```{r}
+library(tm)
+library(qdap)
+```
+
+```{r}
+#function to import and set up the data 
 setup <- function() {
@@
   library(dplyr)
-  out_english <- out %>% 
+  x <- out %>% 
     tbl_df() %>%
@@
 
-  out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
-  empty <- which(is.na(out_english$time_until_answer))
+  x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
+  empty <- which(is.na(x$time_until_answer))
   for (i in empty) {
-    out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
+    x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
 }
 }
-
 ```
@@
 ```{r}
+#functions used in exploratory analysis
 
-plot_surv <- function(survfit, data) {
-
+#function to plot survfit objects
+#input: survfit object, data, optional x-axis limits
+plot_surv <- function(survfit, data, xlim = NULL) {
   library(ggfortify)
@@
           scale_y_continuous("Survival Probabilities") +
-      scale_x_continuous("Time") + 
+          scale_x_continuous("Time (hours)", limits = xlim) + 
           ggtitle("Survival Curves") + 
@@
   }
+}
+
+#function that prints out summary stats grouped by that variable 
+sum_stats <- function(variable, data) {
+  tbl <- x %>%
+    group_by(data[[variable]]) %>%
+    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
+    arrange(median_time)
+  names(tbl)[1] <- variable
+  return(tbl)
+}
 ```
+
+```{r}
+#function to clean corpus, can specify stopwords to remove 
+clean_corpus <- function(corpus, stopwrds = NULL){
+  if (is.null(stopwrds)) {
+    corpus <- tm_map(corpus, stripWhitespace)
+    corpus <- tm_map(corpus, content_transformer(tolower))
+    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+    return(corpus)    
+  } else {
+    corpus <- tm_map(corpus, stripWhitespace)
+    corpus <- tm_map(corpus, content_transformer(tolower))
+    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix", stopwrds))
+    return(corpus)
+  }
+}
+
+#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
+freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
+  source <- VectorSource(vec)
+  corpus <- VCorpus(source)
+
+  if (is.null(stopwrds)) {
+    cleaned_corpus <- clean_corpus(corpus) 
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
+    m <- as.matrix(dtm) 
+    freq <- colSums(m)
+    freq <- sort(freq, decreasing = TRUE)
+    freq_df <- data.frame(word = names(freq), frequency = unname(freq))    
+  } else {
+    cleaned_corpus <- clean_corpus(corpus, stopwrds) 
+    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
+    m <- as.matrix(dtm) 
+    freq <- colSums(m)
+    freq <- sort(freq, decreasing = TRUE)
+    freq_df <- data.frame(word = names(freq), frequency = unname(freq))
+  }
+
+  if (missing(n)) {
+    return(freq_df)
+  }
+  else {
+    return(freq_df[1:n,])
+  }
+}
+```
+
+```{r}
+#functions used in model fitting
+
+#function to calculate r-square adjusted
+#k = number of independent predictors 
+get_rsq_adj <- function(cr_obj, k) {
+  r <- unname(summary(cr_obj)$rsq[1])
+  n <- summary(cr_obj)$n
+  radj <- 1- (((1- (r**2)) * (n - 1))/(n-k-1))
+  return(radj)
+}
+
+#add in function to compare nested models
+
+```
+
+```{r}
+#functions used to compare stackoverflow's model
+
+#function to get median answer times grouped by specified variables (since you can't see it in the boxplot)
+#input var using ""
+get_medians <- function(var) {
+  if (class(var) != "character" | class(var) != "factor") {
+    medians <- x %>%
+      group_by(as.factor(x[[var]])) %>%
+      summarise(median_time = round(median(time_until_answer), 2), n = n())
+  } else {
+    medians <- x %>%
+      group_by(x[[var]]) %>%
+      summarise(median_time = round(median(time_until_answer), 2), n = n())    
+  }
+  names(medians)[1] <- var
+  return(medians)
+}
+
+#function to create boxplot 
+get_boxplot <- function(var, xaxis, title) {
+  if (class(var) != "character" | class(var) != "factor") {
+    ggplot(x, aes(x = as.factor(x[[var]]), y = time_until_answer)) + 
+      geom_boxplot() + 
+      scale_x_discrete(xaxis) + 
+      scale_y_continuous("Answer time (hours)") + 
+      ggtitle(paste("Boxplots of answer times grouped by", title))
+  } else {
+    ggplot(x, aes(x = x[[var]], y = time_until_answer)) + 
+      geom_boxplot() + 
+      scale_x_discrete(xaxis) + 
+      scale_y_continuous("Answer time (hours)") + 
+      ggtitle(paste("Boxplots of answer times grouped by", title))
+  }
+}
+```

### 2017-08-08 literature reviews/literature_reviews.Rmd
reorganized files

--- 2017-07-24 literature_reviews.Rmd
@@
 
+## "Design Lessons from the Fastest Q&A Site in the West" notes
+* found that the stack overflow's reputation system, and strict guidelines for factual/informational answeres (as opposed to discussion) contributed to it's fast answer times  
+    + reputation system = competitive energy, led to short bursts of energy for some, and long-term participation for others
+    + prioritized information over conversation 
+* different approach to design: and external meta site allowed for discussion users had about the site, allowed for developers to push out new versions of the site daily 
+* most answer activity takes place in the first hours 
+* how did SO get it's fast answer time?- motivating users to return and participate is more improtant than total number of users 
+* classes of questions that go unanswered/answered slowly
+    + questions about obscure technologies (cuz there are few knowledgable users)
+    + questions that are tedious to answer
+    + problems that can't be easily reproduced with small code fragment
+    + questions that don't have a clear best answer and invite discussion 
+* fast questions tend to cover widely used technologies
+
 # Ideas:

### 2017-08-08 model fitting/model_fitting.Rmd
reorganized files

--- 2017-08-08 model_fitting.Rmd
@@
 #function to calculate r-square adjusted
+#k = number of independent predictors 
 get_rsq_adj <- function(cr_obj, k) {
@@
 
-summary(cr1)
 library(stats) #to get AIC
 AIC(cr1, k = 2) #83451.51
+
+summary(cr1)
 ```

### 2017-08-08 model fitting/stackoverflow_comparison.Rmd
reorganized files

--- 2017-08-08 stackoverflow_comparison.Rmd
@@
 ```{r, functions, include = FALSE}
-#function to get AIC statistics
-get_aic <- function(cr_obj, num_parameters, data) {
-  aic <- (-2*cr_obj$loglik[2]) + (2*num_parameters)
-  return(aic)
-}
-
 #function to calculate r-square adjusted

### 2017-08-08 model fitting/model_fitting.Rmd
copied data file folder

@@
 
-```{r, include = FALSE}
-#function to compare nested models 
-compare_nested <- function(crfull, crreduced, param_full, param_reduced) {
-  like_f <- crfull[[loglik]]
-  like_r <- crreduced[[loglik]]
-  stat <- 2*(like_f - like_r)
-}
-```
-
 ```{r, echo = FALSE}
@@
 summary(cr11)
+```
+
+```{r}
+#function to compare nested models
+#full and reduced = number of parameters 
+compare_nested <- function(crfull, crreduced, full, reduced) {
+  s_full <- summary(crfull)
+  s_red <- summary(crreduced)
+  like_f <- s_full[[loglik]]
+  like_r <- s_red[[loglik]]
+  stat <- 2*(like_f - like_r)
+  df <- param_full - param_reduced
+  pval <- 1 - pchisq(stat, df)
+  return(stat, pval)
+}
+
+#reduced model
+cr11_r <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
+                 newline_ratio, data = x)
+
+#not calling loglik 
+compare_nested("cr11", "cr11_r", full = 18, reduced = 17)
+
 ```

### 2017-08-10 functions.Rmd
updated hours, organized files

@@
 #function to import and set up the data 
-setup <- function() {
-  dir <- file.path(getwd(),"data")
-  out <- read.csv(file.path(dir, "answers_data.csv"))
-
-  library(dplyr)
-  x <- out %>% 
-    tbl_df() %>%
-    filter(langid == "en")
-
-  x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
-  empty <- which(is.na(x$time_until_answer))
-  for (i in empty) {
-    x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
-}
-}
+oshitar::setup()
 ```
@@
 #input: survfit object, data, optional x-axis limits
-plot_surv <- function(survfit, data, xlim = NULL) {
+get_survplot <- function(survfit, data, xlim = NULL) {
   library(ggfortify)
@@
 #function that prints out summary stats grouped by that variable 
-sum_stats <- function(variable, data) {
+get_summaries <- function(variable, data) {
   tbl <- x %>%
@@
 #function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
-freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
+get_freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
   source <- VectorSource(vec)
@@
 #k = number of independent predictors 
-get_rsq_adj <- function(cr_obj, k) {
-  r <- unname(summary(cr_obj)$rsq[1])
-  n <- summary(cr_obj)$n
-  radj <- 1- (((1- (r**2)) * (n - 1))/(n-k-1))
+get_rsq_adj <- function(cox, k) {
+  r <- unname(summary(cox)$rsq[1])
+  n <- summary(cox)$n
+  radj <- 1 - (((1 - (r**2)) * (n - 1))/(n-k-1))
   return(radj)
@@
 
-#add in function to compare nested models
+#function to compare nested models
+#full and reduced = number of parameters 
+compare_nested <- function(crfull, crreduced) {
+  loglik_f <- summary(crfull)[["loglik"]][2]
+  loglik_r <- summary(crreduced)[["loglik"]][2]
+  stat <- 2*(loglik_f - loglik_r)
+
+  full <- length(crfull[["coefficients"]])
+  reduced <- length(crreduced[["coefficients"]])
+
+  df <- full - reduced
+  pval <- 1 - pchisq(stat, df)
+  results <- data.frame(statistic = stat, pval = pval)
+  return(results)
+}
 

### 2017-08-10 model fitting/model_fitting.Rmd
updated hours, organized files

@@
 x$text_till_punct[is.na(x$text_till_punct)] <- 5000
+#categorize this- zero, small, short, long...
 
@@
 
+```{r}
+ggplot(x, aes(x = time_until_answer, y = avg_tag_score, color = as.factor(answered))) + 
+  geom_point()
+
+library(ggplot2)
+```
+
 ```{r, echo = FALSE}
@@
 #full and reduced = number of parameters 
-compare_nested <- function(crfull, crreduced, full, reduced) {
-  s_full <- summary(crfull)
-  s_red <- summary(crreduced)
-  like_f <- s_full[[loglik]]
-  like_r <- s_red[[loglik]]
-  stat <- 2*(like_f - like_r)
-  df <- param_full - param_reduced
+compare_nested <- function(crfull, crreduced) {
+  loglik_f <- summary(crfull)[["loglik"]][2]
+  loglik_r <- summary(crreduced)[["loglik"]][2]
+  stat <- 2*(loglik_f - loglik_r)
+
+  full <- length(crfull[["coefficients"]])
+  reduced <- length(crreduced[["coefficients"]])
+
+  df <- full - reduced
   pval <- 1 - pchisq(stat, df)
-  return(stat, pval)
+  results <- data.frame(statistic = stat, pval = pval)
+  return(results)
 }
+
+#full
+cr11 <- coxph(Surv(time_until_answer, answered) ~ category + 
+                 device_length + n_images + new_user + post_weekday + 
+                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
+                 title_questionmark + title_begin_wh + capital_text + 
+                 capital_title + text_all_lower + prior_effort + update + 
+                 newline_ratio + title_questionmark*title_begin_wh, data = x)
 
@@
 
-#not calling loglik 
-compare_nested("cr11", "cr11_r", full = 18, reduced = 17)
-
+compare_nested(cr11, cr11_r)
 ```
@@
 ```
+
+```{r}
+cr14 <- coxph(Surv(time_until_answer, answered) ~ avg_tag_score, data = x)
+summary(cr14)
+names(cr14)
+length(cr14$coefficients)
+```

### 2017-08-10 model fitting/stackoverflow_comparison.Rmd
updated hours, organized files

@@
 x$title_ints <- cut(x$title_length, breaks = 5)
+table(x$title_ints)
 
 get_boxplot("title_ints", xaxis = "Intervals of title length (characters)", title = "title_ints")
+
+cr5 <- coxph(Surv(time_until_answer, answered) ~ title_ints, data = x)
+summary(cr5)
 ```

### 2017-08-10 Hours.Rmd
set up a CR model similar to one described in literature review, compared results
finished comparing results to stack overflow model, continued with model fitting, added interactions, updated hours
copied data file folder
updated hours, organized files

@@
 8/3/2017 | 2.75 | 8:00-10:45 | Continued to try out MLEs, looked into Tex and downloaded mendeley, continued fitting the model
+8/4/2017 | 5.5 | 3:00-8:30PM | Fit a model similar to one found in literature reviews, compared results
+8/7/2017 | 4.5 | 11:00-3:30PM | Continued with comparing model results to Stack overflow. 
+8/7/2017 | 3 | 5:45-8:45 | Used AIC, fit model 
+8/8/2017 | 2.5 | 9:30-12:00PM | Model fitting research
+8/8/2017 | 3 | 1:00-4:00PM | Worked with Anthony on building an R package 
+8/9/2017 | 4.25 | 10:45-3:00PM | Predictive model fitting research, reviewed cox regression notes from STAT 417
+8/9/2017 | 3 | 9:30-12:30AM | Found predictive model article, researched terminology from the article, found r packages to use
+8/10/2017 | | 8:00- | Finished putting functions in r package, organized files, continued with model fitting research
 

### 2017-08-10 cheatsheets/modelvalidation_cheatsheet.Rmd
learned about cross validation and test/train split data

---
title: "Supervised Learning Notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Basic Regression notes

* predict(model, newdata) for lm to make predictions from model, using newdata values

##### Gain Curve

* WVPlots::GainCurvePlot(frame, xvar, truthvar, title)
    + frame is a data frame
    + xvar and truthvar are strings naming the prediction and actual outcome columns of frame
    + title is the title of the plot
* For situations where order is more important than exact values, the gain curve helps you check if the model's predictions sort in the same order as the true outcome.
* When the predictions sort in exactly the same order, the relative Gini coefficient is 1. When the model sorts poorly, the relative Gini coefficient is close to zero, or even negative.

##### RMSE

* An RMSE much smaller than the outcome's standard deviation suggests a model that predicts well.
* `residuals <- df$residuals`
* `RMSE <- sqrt(mean(residuals^2))`
* Compare it to the standard deviation of the model's outcome/response

### Training data

##### train a model using test/train split

* working with mpg data set, splitting it into train and test data sets

```{r}
library(ggplot2)

N <- nrow(mpg)
#how many rows 75% of N should be:
(target <- round(N * 0.75))
#vector of N uniform random variables
gp <- runif(N)
#using gp to split mpg 
mpg_train <- mpg[gp < 0.75, ] #should contain about 75% of N (the target) 
mpg_test <- mpg[gp >= 0.75, ]

#now train the model 
#formula to express cty as a function of hwy
(fmla <- cty ~ hwy)

#build mpg_model from mpg_train that predicts cty from hwy 
mpg_model <- lm(fmla, data = mpg_train)
summary(mpg_model)

#predict cty from hwy for the training set
mpg_train$pred <- predict(mpg_model)

#predict cty from hwy for the test set + add it as column to the test data 
mpg_test$pred <- predict(mpg_model, newdata = mpg_test)

#to evaluate performance, compute RMSE for training and test data and compare, do the same for r-square
```

##### cross validation plan

* vtreat::kWayCrossValidation(nRows, nSplits, dframe, y)
    + nrows: number of rows to be split
    + nSplits: desired number of cross-validation folds
    + can set other two arguments to null (aren't used for kWayCrossVal but for compatibility with vtreat)
* Cross-validation predicts how well a model built from all the data will perform on new data. As with the test/train split, for a good modeling procedure, cross-validation performance and training performance should be close
* if the estimated model performance looks good enough, then fit a final model with all of the data (performance between cv and full model should be similar), can't evaluate final model's future performance since there is no data to do so
    + cross validation validates the MODELING PROCESS, not the actual model (test/train split does test how the model will perform on future data)

```{r}
splitPlan <- vtreat::kWayCrossValidation(nrow(mpg), 3, NULL, NULL)
#splitPlan is a list of nSplits elements; each element contains two vectors: train: the indices of dframe that will form the training set, and app: the indices of dframe that will form the test (or application) set
str(splitPlan)

#================================================

#dframe is the training data, one way to add a column of cross validation predictions to a frame is:

# Initialize a column of the appropriate length
# dframe$pred.cv <- 0

# k is the number of folds
# splitPlan is the cross validation plan

# for(i in 1:k) {
  # Get the ith split
  # split <- splitPlan[[i]]
  # Build a model on the training data from this split (lm, in this case)
  # model <- lm(fmla, data = dframe[split$train,])
  # make predictions on the application data from this split
  # dframe$pred.cv[split$app] <- predict(model, newdata = dframe[split$app,])
}

#================================================

# Run the 3-fold cross validation plan from splitPlan
k <- 3 # Number of folds
mpg$pred.cv <- 0 #initialize column
for(i in 1:k) {
  split <- splitPlan[[i]]
  #build model on the training data
  model <- lm(cty ~ hwy, data = mpg[split$train, ]) 
  #make predictions on app data from the split
  mpg$pred.cv[split$app] <- predict(model, newdata = mpg[split$app, ]) 
}

#Predict from a full model
mpg$pred <- predict(lm(cty ~ hwy, data = mpg))

#Get the rmse of the full model's predictions : rmse(mpg$pred, mpg$cty) = 1.247045
#Get the rmse of the cross-validation predictions : rmse(mpg$pred.cv, mpg$cty) = 1.260323
```

### 2017-08-10 cheatsheets/modelvalidation_cheatsheet.Rmd
univariate analysis on training data

@@
 As with the test/train split, for a good modeling procedure, cross-validation performance and training performance should be close
-* if the estimated model performance looks good enough, then fit a final model with all of the data (performance between cv and full model should be similar), can't evaluate final model's future performance since there is no data to do so
+* all predictions from CV are essentially test set predictions- so RMSE and r-square calculated from these predictions should give an unbiased estimate of how a model fit to all the training data will perform on future data
+if the estimated model performance looks good enough, then fit a final model with all of the data (performance between cv and full model should be similar), can't evaluate final model's future performance since there is no data to do so
     + cross validation validates the MODELING PROCESS, not the actual model (test/train split does test how the model will perform on future data)
@@
   # dframe$pred.cv[split$app] <- predict(model, newdata = dframe[split$app,])
-}
+#}
 

### 2017-08-10 model fitting/cross_validation.Rmd
univariate analysis on training data

---
title: "Predictive modeling with cross validation"
author: "Lisa Oshita"
date: "8/10/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE}
x <- oshitar::setup()
library(survival)
library(stringr)
```

### Creating cross-validation plan with k = 5

```{r, echo = FALSE}
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
str(splitPlan)
```

### Building the model on one of the training data sets

##### Univariate analyses

```{r, echo = FALSE}
test1 <- x[splitPlan[[1]]$train, ]

#===================================================================
# Univariate analyses (select variables with p-value < 0.01)

# category 
x$category <- as.character(x$category)
x$category[is.na(x$category)] <- "Other"
x$category <- as.factor(x$category)
cr_cat <- coxph(Surv(time_until_answer, answered) ~ category, data = x)
summary(cr_cat) # p=0

# n_images
cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = x)
summary(cr_image) # p=4.27e-06
x$new_n_images <- as.character(x$n_images) # recoding to group questions with >= 6 images 
x$new_n_images[x$n_images >= 6] <- ">= 6"
cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = x)
summary(cr_image1) # p=1.064e-05

# n_tags
cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = x)
summary(cr_ntags) # p=1.729e-09

# new_user
cr_user <- coxph(Surv(time_until_answer, answered) ~ as.factor(new_user), data = x)
summary(cr_user) # p=0

# weekday 
x$datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
x$weekday <- factor(weekdays(x$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = x)
summary(cr_weekday) # p=0.0002063

# is_weekend
x$is_weekend <- FALSE
x$is_weekend[x$weekday == "Saturday" | x$weekday == "Sunday"] <- TRUE
cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = x)
summary(cr_weekend) # p=0.001501

# hour of the day
x$hour <- as.numeric(format(x$datetime,"%H"))
cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = x)
summary(cr_hour) # p=0.4161

# morning/noon/evening/night?
x$ampm <- "Night"
x$ampm[x$hour >= 5 & x$hour < 12] <- "Morning"
x$ampm[x$hour >= 12 & x$hour < 17] <- "Afternoon" #noon - 5pm 
x$ampm[x$hour >= 17 & x$hour < 20] <- "Evening" #5pm - 8pm 
cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = x)
summary(cr_ampm) # p=2.128e-06

# title length 
x$title_length <- str_length(x$title)
cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = x)
summary(cr_title_len) # p=0.4185

# text length
x$text_length <- str_length(x$text)
cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = x)
summary(cr_text_len) # p=3.442e-15

# device name length
x$device_length <- str_length(x$device)
cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = x)
summary(cr_device_len) # p=0.0008583

# length of sentence until first punctuation mark 
x$length <- str_locate(x$text, pattern = "[.|?|!]")[,1]
q <- quantile(x$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
x$text_till_punct <- "none"
x$text_till_punct[x$length <= q[2]] <- "short"
x$text_till_punct[x$length >= q[2] & x$length <= q[3]] <- "medium"
x$text_till_punct[x$length >= q[3] & x$length <= q[4]] <- "moderate"
x$text_till_punct[x$length >= q[4]] <- "long"
cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = x)
summary(cr_tillpunct) # p=0.01604

# if text contains any end punctuation
x$text_contain_punct <- FALSE
x$text_contain_punct[!is.na(x$text_till_punct)] <- TRUE
cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = x)
summary(cr_containpun) # p=7.862e-11

# if the text ends in a punctuation
x$text_end_punct <- str_detect(x$text, pattern = "[.|?|!]$")
cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = x)
summary(cr_endpunct) # p=0.02284

# if the title ends with a question mark
library(rebus)
x$title_questionmark <- str_detect(x$title, pattern = QUESTION %R% END)
cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = x)
summary(cr_title_q) # p=5.551e-16

# if title begins with "wh"
x$title_beginwh <- str_detect(str_to_lower(x$title), pattern = "^wh")
cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = x)
summary(cr_begin) # p=0.04327

# if first letter of title is capitalized
x$capital_title <- str_detect(as.character(x$title), pattern = "^[[:upper:]]")
cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = x)
summary(cr_title) # p=0.9636

# if first letter of text is capitalized
x$capital_text <- str_detect(x$text, pattern = "^[[:upper:]]")

```

### 2017-08-10 model fitting/cross_validation.Rmd
changed to correct data set

@@
 # category 
-x$category <- as.character(x$category)
-x$category[is.na(x$category)] <- "Other"
-x$category <- as.factor(x$category)
-cr_cat <- coxph(Surv(time_until_answer, answered) ~ category, data = x)
+test1$category <- as.character(test1$category)
+test1$category[is.na(test1$category)] <- "Other"
+test1$category <- as.factor(test1$category)
+cr_cat <- coxph(Surv(time_until_answer, answered) ~ category, data = test1)
 summary(cr_cat) # p=0
@@
 # n_images
-cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = x)
-summary(cr_image) # p=4.27e-06
-x$new_n_images <- as.character(x$n_images) # recoding to group questions with >= 6 images 
-x$new_n_images[x$n_images >= 6] <- ">= 6"
-cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = x)
-summary(cr_image1) # p=1.064e-05
+cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = test1)
+summary(cr_image) # p=2.23e-06
+test1$new_n_images <- as.character(test1$n_images) # recoding to group questions with >= 6 images 
+test1$new_n_images[test1$n_images >= 6] <- ">= 6"
+cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = test1)
+summary(cr_image1) # p=6.461e-06
 
 # n_tags
-cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = x)
-summary(cr_ntags) # p=1.729e-09
+cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = test1)
+summary(cr_ntags) # p=2.039e-09
 
 # new_user
-cr_user <- coxph(Surv(time_until_answer, answered) ~ as.factor(new_user), data = x)
+cr_user <- coxph(Surv(time_until_answer, answered) ~ as.factor(new_user), data = test1)
 summary(cr_user) # p=0
@@
 # weekday 
-x$datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
-x$weekday <- factor(weekdays(x$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
-cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = x)
-summary(cr_weekday) # p=0.0002063
+test1$datetime <- as.POSIXct(test1$post_date,origin="1970-01-01")
+test1$weekday <- factor(weekdays(test1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
+cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = test1)
+summary(cr_weekday) # p=0.0006061
 
 # is_weekend
-x$is_weekend <- FALSE
-x$is_weekend[x$weekday == "Saturday" | x$weekday == "Sunday"] <- TRUE
-cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = x)
-summary(cr_weekend) # p=0.001501
+test1$is_weekend <- FALSE
+test1$is_weekend[test1$weekday == "Saturday" | test1$weekday == "Sunday"] <- TRUE
+cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = test1)
+summary(cr_weekend) # p=0.001602
 
 # hour of the day
-x$hour <- as.numeric(format(x$datetime,"%H"))
-cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = x)
-summary(cr_hour) # p=0.4161
+test1$hour <- as.numeric(format(test1$datetime,"%H"))
+cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = test1)
+summary(cr_hour) # p=0.3994
 
 # morning/noon/evening/night?
-x$ampm <- "Night"
-x$ampm[x$hour >= 5 & x$hour < 12] <- "Morning"
-x$ampm[x$hour >= 12 & x$hour < 17] <- "Afternoon" #noon - 5pm 
-x$ampm[x$hour >= 17 & x$hour < 20] <- "Evening" #5pm - 8pm 
-cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = x)
-summary(cr_ampm) # p=2.128e-06
+test1$ampm <- "Night"
+test1$ampm[test1$hour >= 5 & test1$hour < 12] <- "Morning"
+test1$ampm[test1$hour >= 12 & test1$hour < 17] <- "Afternoon" #noon - 5pm 
+test1$ampm[test1$hour >= 17 & test1$hour < 20] <- "Evening" #5pm - 8pm 
+cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = test1)
+summary(cr_ampm) # p=0.0001333
 
 # title length 
-x$title_length <- str_length(x$title)
-cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = x)
-summary(cr_title_len) # p=0.4185
+test1$title_length <- str_length(test1$title)
+cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = test1)
+summary(cr_title_len) # p=0.4386
 
 # text length
-x$text_length <- str_length(x$text)
-cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = x)
-summary(cr_text_len) # p=3.442e-15
+test1$text_length <- str_length(test1$text)
+cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = test1)
+summary(cr_text_len) # p=1.477e-14
 
 # device name length
-x$device_length <- str_length(x$device)
-cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = x)
-summary(cr_device_len) # p=0.0008583
+test1$device_length <- str_length(test1$device)
+cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = test1)
+summary(cr_device_len) # p=0.0113
 
 # length of sentence until first punctuation mark 
-x$length <- str_locate(x$text, pattern = "[.|?|!]")[,1]
-q <- quantile(x$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
-x$text_till_punct <- "none"
-x$text_till_punct[x$length <= q[2]] <- "short"
-x$text_till_punct[x$length >= q[2] & x$length <= q[3]] <- "medium"
-x$text_till_punct[x$length >= q[3] & x$length <= q[4]] <- "moderate"
-x$text_till_punct[x$length >= q[4]] <- "long"
-cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = x)
-summary(cr_tillpunct) # p=0.01604
+test1$length <- str_locate(test1$text, pattern = "[.|?|!]")[,1]
+q <- quantile(test1$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
+test1$text_till_punct <- "none"
+test1$text_till_punct[test1$length <= q[2]] <- "short"
+test1$text_till_punct[test1$length >= q[2] & test1$length <= q[3]] <- "medium"
+test1$text_till_punct[test1$length >= q[3] & test1$length <= q[4]] <- "moderate"
+test1$text_till_punct[test1$length >= q[4]] <- "long"
+cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = test1)
+summary(cr_tillpunct) # p=1.017e-06
 
 # if text contains any end punctuation
-x$text_contain_punct <- FALSE
-x$text_contain_punct[!is.na(x$text_till_punct)] <- TRUE
-cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = x)
-summary(cr_containpun) # p=7.862e-11
+test1$text_contain_punct <- FALSE
+test1$text_contain_punct[!is.na(test1$length)] <- TRUE
+cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = test1)
+summary(cr_containpun) # p=8.269e-09
 
 # if the text ends in a punctuation
-x$text_end_punct <- str_detect(x$text, pattern = "[.|?|!]$")
-cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = x)
-summary(cr_endpunct) # p=0.02284
+test1$text_end_punct <- str_detect(test1$text, pattern = "[.|?|!]$")
+cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = test1)
+summary(cr_endpunct) # p=0.185
 
@@
 library(rebus)
-x$title_questionmark <- str_detect(x$title, pattern = QUESTION %R% END)
-cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = x)
-summary(cr_title_q) # p=5.551e-16
+test1$title_questionmark <- str_detect(test1$title, pattern = QUESTION %R% END)
+cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = test1)
+summary(cr_title_q) # p=6.55e-15
 
 # if title begins with "wh"
-x$title_beginwh <- str_detect(str_to_lower(x$title), pattern = "^wh")
-cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = x)
-summary(cr_begin) # p=0.04327
+test1$title_beginwh <- str_detect(str_to_lower(test1$title), pattern = "^wh")
+cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = test1)
+summary(cr_begin) # p=0.2241
 
 # if first letter of title is capitalized
-x$capital_title <- str_detect(as.character(x$title), pattern = "^[[:upper:]]")
-cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = x)
-summary(cr_title) # p=0.9636
+test1$capital_title <- str_detect(as.character(test1$title), pattern = "^[[:upper:]]")
+cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = test1)
+summary(cr_title) # p=0.6906
 
 # if first letter of text is capitalized
-x$capital_text <- str_detect(x$text, pattern = "^[[:upper:]]")
+test1$capital_text <- str_detect(test1$text, pattern = "^[[:upper:]]")
 

### 2017-08-10 model fitting/cross_validation.Rmd
updated p-values

@@
 cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = test1)
-summary(cr_image) # p=2.23e-06
+summary(cr_image) # p=0.0006857
 test1$new_n_images <- as.character(test1$n_images) # recoding to group questions with >= 6 images 
@@
 cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = test1)
-summary(cr_image1) # p=6.461e-06
+summary(cr_image1) # p=0.004347
 
@@
 cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = test1)
-summary(cr_ntags) # p=2.039e-09
+summary(cr_ntags) # p=5.701e-07
 
@@
 cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = test1)
-summary(cr_weekday) # p=0.0006061
+summary(cr_weekday) # p=0.04325
 
@@
 cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = test1)
-summary(cr_weekend) # p=0.001602
+summary(cr_weekend) # p=0.02989
 
@@
 cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = test1)
-summary(cr_hour) # p=0.3994
+summary(cr_hour) # p=0.6104
 
@@
 cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = test1)
-summary(cr_ampm) # p=0.0001333
+summary(cr_ampm) # p=0.0001601
 
@@
 cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = test1)
-summary(cr_title_len) # p=0.4386
+summary(cr_title_len) # p=0.8039
 
@@
 cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = test1)
-summary(cr_text_len) # p=1.477e-14
+summary(cr_text_len) # p=3.658e-10
 
@@
 cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = test1)
-summary(cr_device_len) # p=0.0113
+summary(cr_device_len) # p=0.003921
 
@@
 cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = test1)
-summary(cr_tillpunct) # p=1.017e-06
+summary(cr_tillpunct) # p=2.943e-05
 
@@
 cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = test1)
-summary(cr_containpun) # p=8.269e-09
+summary(cr_containpun) # p=7.733e-07
 
@@
 cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = test1)
-summary(cr_endpunct) # p=0.185
+summary(cr_endpunct) # p=0.07902
 
@@
 cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = test1)
-summary(cr_title_q) # p=6.55e-15
+summary(cr_title_q) # p=9.198e-13
 
@@
 cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = test1)
-summary(cr_begin) # p=0.2241
+summary(cr_begin) # p=0.1047
 
@@
 cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = test1)
-summary(cr_title) # p=0.6906
+summary(cr_title) # p=0.5077
 
@@
 test1$capital_text <- str_detect(test1$text, pattern = "^[[:upper:]]")
+cr_text <- coxph(Surv(time_until_answer, answered) ~ capital_text, data = test1)
+summary(cr_text) # p=0.0002079
 
+# if text is in all lower case
+test1$removed <- str_replace_all(test1$text, " ", "")
+test1$removed <- str_replace_all(test1$removed, "[[:punct:]]|[[:digit:]]", "")
+test1$text_all_lower <- str_detect(test1$removed, pattern = "^[[:lower:]]+$")
+test1 <- test1[,-which(names(x) == "removed")]
+cr_lower <- coxph(Surv(time_until_answer, answered) ~ text_all_lower, data = test1)
 ```

### 2017-08-11 model fitting/cross_validation.Rmd
fitted the model

--- 2017-08-10 model fitting/cross_validation.Rmd
@@
 library(stringr)
+library(rebus)
+library(dplyr)
+library(stats)
 ```
@@
 
-```{r, echo = FALSE}
-test1 <- x[splitPlan[[1]]$train, ]
+```{r, include = FALSE}
+train1 <- x[splitPlan[[1]]$train, ]
 
@@
 # Univariate analyses (select variables with p-value < 0.01)
-
 # category 
-x$category <- as.character(x$category)
-x$category[is.na(x$category)] <- "Other"
-x$category <- as.factor(x$category)
-cr_cat <- coxph(Surv(time_until_answer, answered) ~ category, data = x)
+train1$category <- as.character(train1$category)
+train1$category[is.na(train1$category)] <- "Other"
+train1$category <- as.factor(train1$category)
+cr_cat <- coxph(Surv(time_until_answer, answered) ~ category, data = train1)
 summary(cr_cat) # p=0
 
+#===================================================================
 # n_images
-cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = x)
-summary(cr_image) # p=4.27e-06
-x$new_n_images <- as.character(x$n_images) # recoding to group questions with >= 6 images 
-x$new_n_images[x$n_images >= 6] <- ">= 6"
-cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = x)
-summary(cr_image1) # p=1.064e-05
+cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = train1)
+summary(cr_image) # p=2.23e-06
+train1$new_n_images <- as.character(train1$n_images) # recoding to group questions with >= 6 images 
+train1$new_n_images[train1$n_images >= 6] <- ">= 6"
+cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = train1)
+summary(cr_image1) # p=6.461e-06
 
+#===================================================================
 # n_tags
-cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = x)
-summary(cr_ntags) # p=1.729e-09
+cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = train1)
+summary(cr_ntags) # p=2.039e-09
+train1$n_tags <- as.factor(train1$n_tags)
 
+#===================================================================
 # new_user
-cr_user <- coxph(Surv(time_until_answer, answered) ~ as.factor(new_user), data = x)
+cr_user <- coxph(Surv(time_until_answer, answered) ~ as.factor(new_user), data = train1)
 summary(cr_user) # p=0
+train1$new_user <- as.factor(train1$new_user)
 
+#===================================================================
 # weekday
-x$datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
-x$weekday <- factor(weekdays(x$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
-cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = x)
-summary(cr_weekday) # p=0.0002063
+train1$datetime <- as.POSIXct(train1$post_date,origin="1970-01-01")
+train1$weekday <- factor(weekdays(train1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
+cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = train1)
+summary(cr_weekday) # p=0.0006061
 
+#===================================================================
 # is_weekend
-x$is_weekend <- FALSE
-x$is_weekend[x$weekday == "Saturday" | x$weekday == "Sunday"] <- TRUE
-cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = x)
-summary(cr_weekend) # p=0.001501
+train1$is_weekend <- FALSE
+train1$is_weekend[train1$weekday == "Saturday" | train1$weekday == "Sunday"] <- TRUE
+cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = train1)
+summary(cr_weekend) # p=0.001602
 
+#===================================================================
 # hour of the day
-x$hour <- as.numeric(format(x$datetime,"%H"))
-cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = x)
-summary(cr_hour) # p=0.4161
+train1$hour <- as.numeric(format(train1$datetime,"%H"))
+cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = train1)
+summary(cr_hour) # p=0.3994
 
+#===================================================================
 # morning/noon/evening/night?
-x$ampm <- "Night"
-x$ampm[x$hour >= 5 & x$hour < 12] <- "Morning"
-x$ampm[x$hour >= 12 & x$hour < 17] <- "Afternoon" #noon - 5pm 
-x$ampm[x$hour >= 17 & x$hour < 20] <- "Evening" #5pm - 8pm 
-cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = x)
-summary(cr_ampm) # p=2.128e-06
+train1$ampm <- "Night"
+train1$ampm[train1$hour >= 5 & train1$hour < 12] <- "Morning"
+train1$ampm[train1$hour >= 12 & train1$hour < 17] <- "Afternoon" #noon - 5pm
+train1$ampm[train1$hour >= 17 & train1$hour < 20] <- "Evening" #5pm - 8pm
+cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = train1)
+summary(cr_ampm) # p=0.0001333
 
+#===================================================================
 # title length
-x$title_length <- str_length(x$title)
-cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = x)
-summary(cr_title_len) # p=0.4185
+train1$title_length <- str_length(train1$title)
+cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = train1)
+summary(cr_title_len) # p=0.4386
 
+#===================================================================
 # text length
-x$text_length <- str_length(x$text)
-cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = x)
-summary(cr_text_len) # p=3.442e-15
+train1$text_length <- str_length(train1$text)
+cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = train1)
+summary(cr_text_len) # p=1.477e-14
 
+#===================================================================
 # device name length
-x$device_length <- str_length(x$device)
-cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = x)
-summary(cr_device_len) # p=0.0008583
+train1$device_length <- str_length(train1$device)
+cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = train1)
+summary(cr_device_len) # p=0.0113
 
+#===================================================================
 # length of sentence until first punctuation mark
-x$length <- str_locate(x$text, pattern = "[.|?|!]")[,1]
-q <- quantile(x$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
-x$text_till_punct <- "none"
-x$text_till_punct[x$length <= q[2]] <- "short"
-x$text_till_punct[x$length >= q[2] & x$length <= q[3]] <- "medium"
-x$text_till_punct[x$length >= q[3] & x$length <= q[4]] <- "moderate"
-x$text_till_punct[x$length >= q[4]] <- "long"
-cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = x)
-summary(cr_tillpunct) # p=0.01604
+train1$length <- str_locate(train1$text, pattern = "[.|?|!]")[,1]
+q <- quantile(train1$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
+train1$text_till_punct <- "none"
+train1$text_till_punct[train1$length <= q[3]] <- "short"
+train1$text_till_punct[train1$length >= q[3] & train1$length <= q[4]] <- "medium"
+train1$text_till_punct[train1$length >= q[4]] <- "long"
 
+cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = train1)
+summary(cr_tillpunct) # p=2.769e-07
+
+#===================================================================
 # if text contains any end punctuation
-x$text_contain_punct <- FALSE
-x$text_contain_punct[!is.na(x$text_till_punct)] <- TRUE
-cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = x)
-summary(cr_containpun) # p=7.862e-11
+train1$text_contain_punct <- str_detect(train1$text, pattern = "[.|?|!]")
+cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = train1)
+summary(cr_containpun) # p=8.269e-09
+identical(train1$text_contain_punct, train1$contain_punct)
+#===================================================================
+# if the text ends in a punctuation
+train1$text_end_punct <- str_detect(train1$text, pattern = "[.|?|!]$")
+cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = train1)
+summary(cr_endpunct) # p=0.185
 
-# if the text ends in a punctuation
-x$text_end_punct <- str_detect(x$text, pattern = "[.|?|!]$")
-cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = x)
-summary(cr_endpunct) # p=0.02284
-
+#===================================================================
 # if the title ends with a question mark
 library(rebus)
-x$title_questionmark <- str_detect(x$title, pattern = QUESTION %R% END)
-cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = x)
-summary(cr_title_q) # p=5.551e-16
+train1$title_questionmark <- str_detect(train1$title, pattern = QUESTION %R% END)
+cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = train1)
+summary(cr_title_q) # p=6.55e-15
 
+#===================================================================
 # if title begins with "wh"
-x$title_beginwh <- str_detect(str_to_lower(x$title), pattern = "^wh")
-cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = x)
-summary(cr_begin) # p=0.04327
+train1$title_beginwh <- str_detect(str_to_lower(train1$title), pattern = "^wh")
+cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = train1)
+summary(cr_begin) # p=0.2241
 
+#===================================================================
 # if first letter of title is capitalized
-x$capital_title <- str_detect(as.character(x$title), pattern = "^[[:upper:]]")
-cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = x)
-summary(cr_title) # p=0.9636
+train1$capital_title <- str_detect(as.character(train1$title), pattern = "^[[:upper:]]")
+cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = train1)
+summary(cr_title) # p=0.6906
 
+#===================================================================
 # if first letter of text is capitalized
-x$capital_text <- str_detect(x$text, pattern = "^[[:upper:]]")
+train1$capital_text <- str_detect(as.character(train1$text), pattern = "^[[:upper:]]")
+cr_text <- coxph(Surv(time_until_answer, answered) ~ capital_text, data = train1)
+summary(cr_text) # p=6.642e-05
 
+#===================================================================
+# if text is in all lower case
+train1$cleaned <- str_replace_all(train1$text, " ", "")
+train1$cleaned <- str_replace_all(train1$cleaned, "[[:punct:]]|[[:digit:]]", "")
+train1$text_all_lower <- str_detect(train1$cleaned, pattern = "^[[:lower:]]+$")
+cr_lower <- coxph(Surv(time_until_answer, answered) ~ text_all_lower, data = train1)
+summary(cr_lower) # p=1.605e-05
+
+#===================================================================
+# prior_effort
+train1$prior_effort <- str_detect(str_to_lower(train1$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
+cr_prior <- coxph(Surv(time_until_answer, answered) ~ prior_effort, data = train1)
+summary(cr_prior) # p=0.0002236
+
+#===================================================================
+# num_prior_effort
+train1$num_prior_effort <- str_count(str_to_lower(train1$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
+cr_numprior <- coxph(Surv(time_until_answer, answered) ~ as.factor(num_prior_effort), data = train1)
+summary(cr_numprior) # p=0.000436 (lower p-value if treated as numeric)
+
+#===================================================================
+# expressing gratitude 
+train1$gratitude <- str_detect(str_to_lower(train1$text), pattern = or("please", "thank you", "thanks", "thankful", "appreciate", "appreciated", "grateful"))
+cr_gratitude <- coxph(Surv(time_until_answer, answered) ~ gratitude, data = train1)
+summary(cr_gratitude) # p=0.0001431
+
+#===================================================================
+# greeting
+train1$greeting <- str_detect(str_to_lower(train1$text), pattern = START %R% or("hey", "hello", "greetings", "hi"))
+cr_greeting <- coxph(Surv(time_until_answer, answered) ~ greeting, data = train1)
+summary(cr_greeting) # p=2.252e-08
+
+#===================================================================
+# update the question?
+train1$update <- str_detect(train1$text, pattern = "===")
+cr_up <- coxph(Surv(time_until_answer, answered) ~ update, data = train1)
+summary(cr_up) # p=3.398e-09
+
+#===================================================================
+# newline ratio to length of text
+train1$newline_ratio <- str_count(train1$text, pattern = "\n")/str_length(train1$text)
+cr_newline <- coxph(Surv(time_until_answer, answered) ~ newline_ratio, data = train1)
+summary(cr_newline) # p=1.228e-08
 ```
+
+```{r, include = FALSE}
+# tag-based variables
+#===================================================================
+# avg_tag_length
+split_tags <- str_split(train1$tags, ", ", simplify = TRUE)
+train1$avg_tag_length <- NA
+not_na <- which(train1$tags != "")
+for (i in not_na) {
+  total_char <- sum(str_length(as.vector(split_tags[i,])))
+  total_tags <- sum(as.vector(split_tags[i,]) != "")
+  train1$avg_tag_length[i] <- total_char / total_tags
+}
+cr_tagl <- coxph(Surv(time_until_answer, answered) ~ avg_tag_length, data = train1)
+summary(cr_tagl) # p=0.1948
+
+#===================================================================
+# maximum number of words for a question's tags
+train1$max_tagwords <- rep(0, nrow(train1))
+for (i in which(train1$n_tags != 0)) {
+  tags <- as.vector(split_tags[i,])
+  train1$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
+}
+cr_max <- coxph(Surv(time_until_answer, answered) ~ max_tagwords, data = train1)
+summary(cr_max) # p=0.0001012 (should I treat this as categorical?)
+
+#===================================================================
+# frequent tags
+tag_vector <- as.vector(split_tags)
+tag_vector <- tag_vector[which(tag_vector != "")]
+unique_tags <- unique(tag_vector)
+
+tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
+tag_freq <- tag_freq %>%
+              arrange(desc(percent))
+
+#creating average frequency score variable
+train1$tag1 <- split_tags[,1]
+train1$tag2 <- split_tags[,2]
+train1$tag3 <- split_tags[,3]
+train1$tag4 <- split_tags[,4]
+
+assign_score <- function(data, variable) {
+  score <- rep(0, nrow(data))
+  notempty <- which(data[[variable]] != "")
+  for (i in notempty) {
+    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
+  }
+  return(score)
+}
+train1$score1 <- assign_score(train1, "tag1")
+train1$score2 <- assign_score(train1, "tag2")
+train1$score3 <- assign_score(train1, "tag3")
+train1$score4 <- assign_score(train1, "tag4")
+train1$avg_tag_score <- (train1$score1 + train1$score2 + train1$score3 + train1$score4)/as.numeric(train1$n_tags)
+train1$avg_tag_score[is.nan(train1$avg_tag_score)] <- 0
+cr_score <- coxph(Surv(time_until_answer, answered) ~ avg_tag_score, data = train1)
+summary(cr_score) # p=2.614e-10 insanely high hazard ratio
+
+#===================================================================
+# if question contains "frequent" tag
+percentile80 <- quantile(train1$avg_tag_score, probs = 0.80)
+
+train1$frequent_tag <- FALSE
+train1$frequent_tag[train1$avg_tag_score >= percentile80] <- TRUE
+cr_frequent <- coxph(Surv(time_until_answer, answered) ~ frequent_tag, data = train1)
+summary(cr_frequent) # p=1.814e-13
+
+#===================================================================
+# number of "frequent" tags a question contains
+threshold <- 0.005
+num_pop <- function(var, threshold) {
+  num_pop <- rep(0, nrow(train1))
+  num_pop[train1[[var]] >= threshold] <- 1
+  return(num_pop)
+}
+numpop1 <- num_pop("score1", threshold)
+numpop2 <- num_pop("score2", threshold)
+numpop3 <- num_pop("score3", threshold)
+numpop4 <- num_pop("score4", threshold)
+train1$num_freq_tags <- numpop1 + numpop2 + numpop3 + numpop4
+cr_numfreq <- coxph(Surv(time_until_answer, answered) ~ num_freq_tags, data = train1)
+summary(cr_numfreq) # p=3.432e-10
+
+#==================================================================================
+#frequent terms in unanswered/answered questions
+answered <- train1 %>%
+  tbl_df() %>% 
+  filter(answered == 1)
+
+unanswered <- train1 %>%
+  tbl_df() %>% 
+  filter(answered == 0)
+
+library(qdap)
+library(tm)
+terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
+colnames(terms_a)[2] <- "frequency_a"
+
+terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
+colnames(terms_u)[2] <- "frequency_u"
+
+combined <- dplyr::full_join(terms_a, terms_u, by = "word")
+combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
+
+p_threshold <- 0.01
+ratio_threshold <- 1
+
+freq_terms_u <- combined %>%
+                  filter(prop_in_unanswered > p_threshold) %>%
+                  filter(ratio < ratio_threshold)
+freq_terms_a <- combined %>%
+                  filter(prop_in_answered > p_threshold) %>%
+                  filter(ratio > ratio_threshold)
+
+train1$contain_unanswered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_u$word))
+train1$contain_answered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_a$word))
+
+cr_unans <- coxph(Surv(time_until_answer, answered) ~ contain_unanswered, data = train1)
+summary(cr_unans) # p=1.11e-16
+cr_ans <- coxph(Surv(time_until_answer, answered) ~ contain_answered, data = train1)
+summary(cr_ans) # p=2.314e-08
+```
+
+### Backwards selection of variables
+
+* using selectCox function from pec package
+* choose between n_images or new_n_images, determine if should treat n_images as discrete (don't treat as discrete cuz beta goes to infinity)
+* weekday or is_weekend
+* text_till_punct or text_contain_punct? 
+* frequent_tag or num_freq_tags
+
+```{r}
+model1 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_till_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
+summary(model1)
+AIC(model1, k = 2) # 65065.97
+
+# with new_n_images instead of n_images: 65072.75
+
+# fitting is_weekend instead of weekday: 65066.88 - keep weekday
+model2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_till_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
+AIC(model2, k = 2)
+
+# fitting with text_contain_punct instead of text_till_punct: 65061.46
+model3 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
+AIC(model3, k = 2) #  (keep text_contain_punct)
+
+# text_contain_punct + is_weekend: 65063.91
+model4 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
+AIC(model4, k = 2) #  (keep text_contain_punct)
+
+# fitting with num_prior_effect instead of prior effect: 65063.25
+model5 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + num_prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
+AIC(model5, k = 2)
+
+# fitting with frequent_tag instead of avg_tag_score
+# final model 
+model6 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
+AIC(model6, k = 2) # keep avg_tag_score
+```
+
+```{r}
+model <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1, rule = "aic") # 65058.03
+
+#results:
+final1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + is_weekend + ampm + device_length + title_questionmark + update + avg_tag_score + contain_answered + contain_unanswered, data = train1)
+summary(final1)
+
+#added interaction term 
+final <- coxph(Surv(time_until_answer, answered) ~ category + new_user + is_weekend + ampm + device_length + title_questionmark + title_beginwh + update + avg_tag_score + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update, data = train1)
+AIC(final, k = 2) #65054.87  
+summary(final)
+```
+
+### trying out a different stepwise function
+```{r}
+# variables <- c("category", "n_images", "n_tags", "new_user", "is_weekend", "ampm", "text_length", "device_length", "text_contain_punct", "title_questionmark", "title_beginwh", "capital_text", "text_all_lower", "prior_effort", "gratitude", "greeting", "update", "newline_ratio", "max_tagwords", "avg_tag_score", "contain_answered", "contain_unanswered")
+# 
+# modell <- My.stepwise.coxph(Time = "time_until_answer", Status = "answered", variable.list = variables, data = train1)
+# #my.variable.list <- c("inst", "age", "sex", "ph.ecog", "ph.karno", "pat.karno", "meal.cal",
+# levels(train1$category)[4] <- "CarTruck"
+# levels(train1$category)[5] <- "ComputerHardware"
+# levels(train1$category)[10] <- "MediaPlayer"
+# levels(train1$category)[7] <- "GameConsole"
+```

### 2017-08-11 Hours.Rmd
updated hours

@@
 8/9/2017 | 3 | 9:30-12:30AM | Found predictive model article, researched terminology from the article, found r packages to use
-8/10/2017 | | 8:00- | Finished putting functions in r package, organized files, continued with model fitting research
+8/10/2017 | 8 | 8:00-4:00PM | Finished putting functions in r package, organized files, data camp course on cross validation, continued with model fitting research
+8/10/2017 | 2 | 6:00-8:00PM | Tried to figure out backwards selection function to fit model
 

### 2017-08-11 model fitting/cross_validation.Rmd
updated hours

@@
 * using selectCox function from pec package
-* choose between n_images or new_n_images, determine if should treat n_images as discrete (don't treat as discrete cuz beta goes to infinity)
+* choose between n_images or new_n_images
 * weekday or is_weekend

### 2017-08-11 model fitting/cross_validation.Rmd
used stepAIc with backwards/forward sepwise selection, added interaction terms, recoded category variable

@@
 identical(train1$text_contain_punct, train1$contain_punct)
+
 #===================================================================
@@
 
-### Backwards selection of variables
-
-* using selectCox function from pec package
-* choose between n_images or new_n_images
-* weekday or is_weekend
-* text_till_punct or text_contain_punct? 
-* frequent_tag or num_freq_tags
+### Fitting model with all significant variables (univariate analysis p-value < 0.01)
 
 ```{r}
-model1 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_till_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
-summary(model1)
-AIC(model1, k = 2) # 65065.97
+first <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1)
+summary(first)
+AIC(first, k = 2) # 65065.88
 
-# with new_n_images instead of n_images: 65072.75
+# backwards step-wise selection with selectCox function
+model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1, rule = "aic")
+cox
+#results
+results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + contain_answered + contain_unanswered, data = train1)
+AIC(results1, k = 2) #65059
+summary(results1)
 
-# fitting is_weekend instead of weekday: 65066.88 - keep weekday
-model2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_till_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
-AIC(model2, k = 2)
+# backward/forward step-wise selection with stepAIC function from MASS package
+model2 <- stepAIC(model, direction = "both", k = 2)
+# results
+results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1)
+AIC(results2, k = 2) # 65050.45
+summary(results2)
 
-# fitting with text_contain_punct instead of text_till_punct: 65061.46
-model3 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
-AIC(model3, k = 2) #  (keep text_contain_punct)
+# best subset selection with glmulti function
+# took out variables based off of p-value (function couldn't handle amount of predictors)
+# model3 <- glmulti(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + capital_text + text_all_lower + prior_effort + greeting + update + newline_ratio + frequent_tag,
+#                 data = train1,
+#                 level = 1, 
+#                 method = "g", 
+#                 crit = "aic",
+#                 fitfunction = "coxph",
+#                 confsetsize = 5
+#                 )
+# model3@formulas
+# #results
+# results3 <- coxph(Surv(time_until_answer,answered)~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + newline_ratio + frequent_tag, data = train1)
+# AIC(results3) # 65098.48
+# summary(results3)
 
-# text_contain_punct + is_weekend: 65063.91
-model4 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
-AIC(model4, k = 2) #  (keep text_contain_punct)
-
-# fitting with num_prior_effect instead of prior effect: 65063.25
-model5 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + num_prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
-AIC(model5, k = 2)
-
-# fitting with frequent_tag instead of avg_tag_score
-# final model 
-model6 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
-AIC(model6, k = 2) # keep avg_tag_score
+# trying out lasso regularization with the glmnet package
+# library(glmnet)
+# setting up matrix for function
+# mx <- as.matrix(train1 %>% 
+#   tbl_df() %>%
+#   dplyr::select(category, n_images, n_tags, new_user, weekday, ampm, text_length, device_length, text_contain_punct, title_questionmark, title_beginwh, capital_text, text_all_lower, prior_effort, gratitude, greeting, update, newline_ratio, max_tagwords, frequent_tag, contain_answered, contain_unanswered))
+# model4 <- glmnet(x, y = Surv(train1$time_until_answer, train1$answered, type = "right"), family = "cox")
+# summary(model4)
+# 
+# x <- model.matrix( ~ rx + sex + age + obstruct + perfor + adhere + surg - 1, d)
+# 
+# x <- model.matrix(~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered - 1, train1)
 ```
@@
 ```{r}
-model <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1, rule = "aic") # 65058.03
+# working with model from backward/forward stepwise selection
+results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1) # 65050.45
 
-#results:
-final1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + is_weekend + ampm + device_length + title_questionmark + update + avg_tag_score + contain_answered + contain_unanswered, data = train1)
-summary(final1)
-
-#added interaction term 
-final <- coxph(Surv(time_until_answer, answered) ~ category + new_user + is_weekend + ampm + device_length + title_questionmark + title_beginwh + update + avg_tag_score + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update, data = train1)
-AIC(final, k = 2) #65054.87  
-summary(final)
+# adding interaction terms
+r2_i <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
+AIC(r2_i, k = 2) # 65037.36
+summary(r2_i)
 ```
 
-### trying out a different stepwise function
+##### recoding category variable
+
+* separate iPhones/Androids (or group all apple products together?) - use str_detect to find categories with apple/iphone/mac (since there are apple watches in the apparel category)
+* keep Mac and PC the same
+* group all categories that have less than 100 questions together? 
+* group electronics + median player
+* group household + appliance
+* group car and truck + vehicle
+
 ```{r}
-# variables <- c("category", "n_images", "n_tags", "new_user", "is_weekend", "ampm", "text_length", "device_length", "text_contain_punct", "title_questionmark", "title_beginwh", "capital_text", "text_all_lower", "prior_effort", "gratitude", "greeting", "update", "newline_ratio", "max_tagwords", "avg_tag_score", "contain_answered", "contain_unanswered")
-# 
-# modell <- My.stepwise.coxph(Time = "time_until_answer", Status = "answered", variable.list = variables, data = train1)
-# #my.variable.list <- c("inst", "age", "sex", "ph.ecog", "ph.karno", "pat.karno", "meal.cal",
-# levels(train1$category)[4] <- "CarTruck"
-# levels(train1$category)[5] <- "ComputerHardware"
-# levels(train1$category)[10] <- "MediaPlayer"
-# levels(train1$category)[7] <- "GameConsole"
+# pie chart of product categories
+ggplot(train1, aes(x = factor(1), fill = category)) + geom_bar(width = 1) + 
+  coord_polar(theta = "y")
+
+train1 %>%
+  group_by(category) %>%
+  summarise(median_t = median(time_until_answer), n = n()) %>%
+  arrange(median_t)
+
+# recoding category variable
+train1$new_category <- as.character(train1$category)
+train1$new_category[train1$subcategory == "iPhone"] <- "iPhone"
+train1$new_category[train1$new_category == "Phone"] <- "Android/Other OS Phone"
+train1$new_category[train1$new_category == "Electronics" | train1$new_category == "Media Player"] <- "Electronics/Media"
+train1$new_category[train1$new_category == "Household" | train1$new_category == "Appliance"] <- "Home"
+train1$new_category[train1$new_category == "Car and Truck"] <- "Vehicle"
+
+#if there are less than 50 questions in a certain category, group with "Other"
+n <- train1 %>%
+  group_by(category) %>%
+  summarise(n = n())
+# fix this (not working correctly)
+for (i in nrow(n)) {
+  if (n$n[i] < 50) {
+    train1$new_category[train1$category == n$category[i]] <- "Other"
+  }
+}
+
+# model with new_category- AIC dropped 
+r2_new <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
+AIC(r2_new, k = 2) # 64743.48
+summary(r2_new)
 ```
+
+```{r}
+
+```

### 2017-08-11 model fitting/cross_validation.Rmd
finished recoding category variable

@@
 # adding interaction terms
-r2_i <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
+r2_i <- coxph(Surv(time_until_answer, answered) ~ category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
 AIC(r2_i, k = 2) # 65037.36
@@
 
-* separate iPhones/Androids (or group all apple products together?) - use str_detect to find categories with apple/iphone/mac (since there are apple watches in the apparel category)
-* keep Mac and PC the same
-* group all categories that have less than 100 questions together? 
-* group electronics + median player
-* group household + appliance
-* group car and truck + vehicle
+* group all apple products together (use str_detect to search for Apple, ipad, ipod)
+* recode left over Phones to Android/Other Phone
+* group household + appliance as "Home"
+* group car and truck + vehicle as "Vehicle"
+* set a rule: any category with less than 50 questions gets grouped with "Other"
 
@@
 train1 %>%
-  group_by(category) %>%
-  summarise(median_t = median(time_until_answer), n = n()) %>%
-  arrange(median_t)
+  filter(category == "Media Player") %>%
+  group_by(subcategory) %>%
+  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n)
 
+#===================================================
 # recoding category variable
 train1$new_category <- as.character(train1$category)
-train1$new_category[train1$subcategory == "iPhone"] <- "iPhone"
-train1$new_category[train1$new_category == "Phone"] <- "Android/Other OS Phone"
-train1$new_category[train1$new_category == "Electronics" | train1$new_category == "Media Player"] <- "Electronics/Media"
-train1$new_category[train1$new_category == "Household" | train1$new_category == "Appliance"] <- "Home"
-train1$new_category[train1$new_category == "Car and Truck"] <- "Vehicle"
 
-#if there are less than 50 questions in a certain category, group with "Other"
-n <- train1 %>%
-  group_by(category) %>%
+# grouping apple products together
+apple_terms <- c("apple", "ipod", "ipad")
+train1$apple <- str_detect(str_to_lower(train1$device), pattern = START %R% or1(apple_terms) %R% SPC)
+train1$new_category[train1$apple == TRUE | train1$subcategory == "iPhone" | train1$category == "Mac"] <- "Apple Product"
+
+# renaming left over phones 
+train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"
+train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"
+train1$new_category[train1$new_category == "Car and Truck" | train1$new_category == "Vehicle"] <- "Vehicle"
+
+# if there are less than 60 questions in a category, group them with other
+counts <- train1 %>%
+  group_by(new_category) %>%
   summarise(n = n())
-# fix this (not working correctly)
-for (i in nrow(n)) {
-  if (n$n[i] < 50) {
-    train1$new_category[train1$category == n$category[i]] <- "Other"
-  }
+for (i in which(counts$n <= 100)) {
+  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
 }
 
-# model with new_category- AIC dropped 
+table(train1$new_category)
+
+# model with new_category 
 r2_new <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
-AIC(r2_new, k = 2) # 64743.48
+AIC(r2_new, k = 2) # 64728.77
 summary(r2_new)
 ```
-
-```{r}
-
-```

### 2017-08-12 model fitting/cross_validation.Rmd
plotted residuals, updated hours

@@
 }
-
 table(train1$new_category)
+#===================================================
 
@@
 ```
+
+### residuals, PH assumption
+
+```{r}
+#=============================================
+#martingale residuals
+train1$mart <- residuals(r2_new, type = "martingale")
+
+plot_res <- function(var, residuals, data, title) {
+  ggplot(data, aes(x = data[[var]], y = residuals)) +
+    geom_point() +
+    geom_smooth() + 
+    ggtitle(title) + 
+    scale_x_continuous(var)
+}
+
+res_image <- plot_res(var = "n_images", residuals = mart, data = train1, title = "Martingale Residuals for n_images")
+res_dev <- plot_res("device_length", mart, data = train1, title = "Martingale Residuals for device_length")
+res_newline <- plot_res("newline_ratio", mart, data = train1, title = "Martingale Residuals for newline_ratio")
+
+gridExtra::grid.arrange(res_image, res_dev, res_newline, nrow=1, ncol=3)
+
+#=============================================
+#deviance residuals 
+train1$deviance <- residuals(r2_new, type = "deviance")
+ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
+  geom_point() + 
+  scale_x_continuous("Question index") + 
+  scale_y_continuous(breaks = seq(-4, 4, by = 0.5))
+# quite a few questions have a deviance residual of larger than 2.5
+
+#=============================================
+#schoenfeld residuals
+schoen <- as.data.frame(residuals(r2_new, type = "schoenfeld"))
+# complete event times sorted from shortest to longest
+schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)
+
+plot_schoen <- function(var) {
+  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Schoenfeld Residuals for", var)) + 
+    scale_y_continuous("Residuals")
+}
+names <- names(schoen)[-31]
+purrr::map(names, plot_schoen)
+
+#=============================================
+# score residuals
+score <- as.data.frame(residuals(r2_new, type = "score"))
+# function to plot score residuals
+plot_score <- function(column) {
+  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Score residuals for", column)) + 
+    scale_y_continuous("Score Residuals") + 
+    scale_x_continuous("Question index")
+}
+columns <- names(score)
+purrr::map(columns, plot_score)
+```
+
+### Predicting on the test data
+
+```{r}
+test1 <- x[splitPlan[[1]]$app, ]
+# predict.coxph
+```

### 2017-08-15 model fitting/cross_validation.Rmd
predicted on test data

--- 2017-08-11 model fitting/cross_validation.Rmd
@@
 library(stats)
+library(ggplot2)
 ```
@@
 
+##### Trying out different variable selection functions
+
 ```{r}
@@
 model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1, rule = "aic")
-cox
+
 #results
@@
 # backward/forward step-wise selection with stepAIC function from MASS package
-model2 <- stepAIC(model, direction = "both", k = 2)
+model2 <- MASS::stepAIC(first, direction = "both", k = 2)
 # results
@@
 }
-
 table(train1$new_category)
+#===================================================
 
 # model with new_category 
-r2_new <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
-AIC(r2_new, k = 2) # 64728.77
-summary(r2_new)
+final <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
+AIC(final, k = 2) # 64728.77
+summary(final)
 ```
+
+### residuals, PH assumption
+
+```{r}
+#=============================================
+#martingale residuals
+train1$mart <- residuals(final, type = "martingale")
+plot_mart <- function(var) {
+  ggplot(train1, aes(x = train1[[var]], y = mart)) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Martingale Residuals for", var)) + 
+    scale_x_continuous(var)
+}
+
+q_vars <- c("n_images", "device_length", "newline_ratio")
+purrr::map(q_vars, plot_mart)
+
+#=============================================
+#deviance residuals 
+train1$deviance <- residuals(final, type = "deviance")
+ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
+  geom_point() + 
+  scale_x_continuous("Question index") + 
+  scale_y_continuous(breaks = seq(-4, 4, by = 0.5))
+# quite a few questions have a deviance residual of larger than 2.5
+
+#=============================================
+#schoenfeld residuals
+schoen <- as.data.frame(residuals(final, type = "schoenfeld"))
+# complete event times sorted from shortest to longest
+schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)
+
+plot_schoen <- function(var) {
+  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Schoenfeld Residuals for", var)) + 
+    scale_y_continuous("Residuals")
+}
+names <- names(schoen)[-31]
+purrr::map(names, plot_schoen)
+
+#=============================================
+# score residuals
+score <- as.data.frame(residuals(final, type = "score"))
+# function to plot score residuals
+plot_score <- function(column) {
+  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Score residuals for", column)) + 
+    scale_y_continuous("Score Residuals") + 
+    scale_x_continuous("Question index")
+}
+columns <- names(score)
+purrr::map(columns, plot_score)
+```
+
+### Predicting on the test data
+
+```{r}
+test1 <- x[splitPlan[[1]]$app, ]
+
+#setting up variables in test1
+#=============================================
+test1$category <- as.character(test1$category)
+test1$category[is.na(test1$category)] <- "Other"
+#new_category
+test1$new_category <- test1$category
+apple_terms <- c("apple", "ipod", "ipad")
+test1$apple <- str_detect(str_to_lower(test1$device), pattern = START %R% or1(apple_terms) %R% SPC)
+test1$new_category[test1$apple == TRUE | test1$subcategory == "iPhone" | test1$category == "Mac"] <- "Apple Product"
+test1$new_category[test1$new_category == "Phone"] <- "Android/Other Phone"
+test1$new_category[test1$new_category == "Appliance" | test1$new_category == "Household"] <- "Home"
+test1$new_category[test1$new_category == "Car and Truck" | test1$new_category == "Vehicle"] <- "Vehicle"
+test1$new_category[test1$new_category == "Computer Hardware" | test1$new_category == "Media Player" | test1$new_category == "Apparel"] <- "Other"
+# counts <- test1 %>%
+#   group_by(new_category) %>%
+#   summarise(n = n(), prop = n/nrow(test1))
+# for (i in which(counts$prop <= 0.01)) {
+#   test1$new_category[test1$new_category == counts$new_category[i]] <- "Other"
+# }
+#=============================================
+#weekday
+test1$datetime <- as.POSIXct(test1$post_date,origin="1970-01-01")
+test1$weekday <- factor(weekdays(test1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
+#=============================================
+#ampm
+test1$hour <- as.numeric(format(test1$datetime,"%H"))
+test1$ampm <- "Night"
+test1$ampm[test1$hour >= 5 & test1$hour < 12] <- "Morning"
+test1$ampm[test1$hour >= 12 & test1$hour < 17] <- "Afternoon" #noon - 5pm
+test1$ampm[test1$hour >= 17 & test1$hour < 20] <- "Evening" #5pm - 8pm
+#=============================================
+# text length
+test1$text_length <- str_length(test1$text)
+#=============================================
+# device name length
+test1$device_length <- str_length(test1$device)
+#=============================================
+# if the title ends with a question mark
+library(rebus)
+test1$title_questionmark <- str_detect(test1$title, pattern = QUESTION %R% END)
+#=============================================
+# if title begins with "wh"
+test1$title_beginwh <- str_detect(str_to_lower(test1$title), pattern = "^wh")
+#=============================================
+test1$capital_text <- str_detect(as.character(test1$text), pattern = "^[[:upper:]]")
+#=============================================
+test1$update <- str_detect(test1$text, pattern = "===")
+#=============================================
+test1$newline_ratio <- str_count(test1$text, pattern = "\n")/str_length(test1$text)
+#=============================================
+# frequent tags
+split_tags <- str_split(test1$tags, ", ", simplify = TRUE)
+tag_vector <- as.vector(split_tags)
+tag_vector <- tag_vector[which(tag_vector != "")]
+unique_tags <- unique(tag_vector)
+
+tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
+tag_freq <- tag_freq %>%
+              arrange(desc(percent))
+
+#creating average frequency score variable
+test1$tag1 <- split_tags[,1]
+test1$tag2 <- split_tags[,2]
+test1$tag3 <- split_tags[,3]
+test1$tag4 <- split_tags[,4]
+
+assign_score <- function(data, variable) {
+  score <- rep(0, nrow(data))
+  notempty <- which(data[[variable]] != "")
+  for (i in notempty) {
+    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
+  }
+  return(score)
+}
+test1$score1 <- assign_score(test1, "tag1")
+test1$score2 <- assign_score(test1, "tag2")
+test1$score3 <- assign_score(test1, "tag3")
+test1$score4 <- assign_score(test1, "tag4")
+test1$avg_tag_score <- (test1$score1 + test1$score2 + test1$score3 + test1$score4)/as.numeric(test1$n_tags)
+test1$avg_tag_score[is.nan(test1$avg_tag_score)] <- 0
+#=============================================
+# if question contains "frequent" tag
+percentile80 <- quantile(test1$avg_tag_score, probs = 0.80)
+
+test1$frequent_tag <- FALSE
+test1$frequent_tag[test1$avg_tag_score >= percentile80] <- TRUE
+#=============================================
+#frequent terms in unanswered/answered questions
+answered <- test1 %>%
+  tbl_df() %>% 
+  filter(answered == 1)
+unanswered <- test1 %>%
+  tbl_df() %>% 
+  filter(answered == 0)
+
+library(qdap)
+library(tm)
+terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
+colnames(terms_a)[2] <- "frequency_a"
+
+terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
+colnames(terms_u)[2] <- "frequency_u"
+
+combined <- dplyr::full_join(terms_a, terms_u, by = "word")
+combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
+
+p_threshold <- 0.01
+ratio_threshold <- 1
+
+freq_terms_u <- combined %>%
+                  filter(prop_in_unanswered > p_threshold) %>%
+                  filter(ratio < ratio_threshold)
+freq_terms_a <- combined %>%
+                  filter(prop_in_answered > p_threshold) %>%
+                  filter(ratio > ratio_threshold)
+
+test1$contain_unanswered <- str_detect(as.character(test1$title), pattern = or1(freq_terms_u$word))
+test1$contain_answered <- str_detect(as.character(test1$title), pattern = or1(freq_terms_a$word))
+
+test1$new_user <- as.factor(test1$new_user)
+
+#356 NAs in the predictions
+test_predict <- predict(final, newdata = test1, type = "risk", se.fit = TRUE)
+test1$predictions <- test_predict[[1]]
+
+metric <- coxph(Surv(time_until_answer, answered) ~ predictions, data = test1)
+summary(metric)
+AIC(metric, k = 2)
+```

### 2017-08-15 model fitting/cross_validation.Rmd
created new markdown for univariate analysis, stratified model on new_category

@@
 ```{r, echo = FALSE}
+set.seed(444)
 splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
@@
 
-##### Univariate analyses
+##### Fitting model with all significant variables (univariate analysis p-value < 0.01), select variables using stepwise functions
 
-```{r, include = FALSE}
-train1 <- x[splitPlan[[1]]$train, ]
+```{r}
+first <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + contain_unanswered + title_questionmark + text_length + text_contain_punct + as.factor(num_freq_tags) + as.factor(n_tags) + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1)
+AIC(first, k = 2) #65294.56
 
-#===================================================================
-# Univariate analyses (select variables with p-value < 0.01)
-# category 
-train1$category <- as.character(train1$category)
-train1$category[is.na(train1$category)] <- "Other"
-train1$category <- as.factor(train1$category)
-cr_cat <- coxph(Surv(time_until_answer, answered) ~ category, data = train1)
-summary(cr_cat) # p=0
-
-#===================================================================
-# n_images
-cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = train1)
-summary(cr_image) # p=2.23e-06
-train1$new_n_images <- as.character(train1$n_images) # recoding to group questions with >= 6 images 
-train1$new_n_images[train1$n_images >= 6] <- ">= 6"
-cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = train1)
-summary(cr_image1) # p=6.461e-06
-
-#===================================================================
-# n_tags
-cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = train1)
-summary(cr_ntags) # p=2.039e-09
+# backwards step-wise selection with selectCox function
+# converting to factors since function doesn't work with as.factor
+train1$new_user <- as.factor(train1$new_user)
+train1$num_freq_tags <- as.factor(train1$num_freq_tags)
 train1$n_tags <- as.factor(train1$n_tags)
 
-#===================================================================
-# new_user
-cr_user <- coxph(Surv(time_until_answer, answered) ~ as.factor(new_user), data = train1)
-summary(cr_user) # p=0
-train1$new_user <- as.factor(train1$new_user)
-
-#===================================================================
-# weekday
-train1$datetime <- as.POSIXct(train1$post_date,origin="1970-01-01")
-train1$weekday <- factor(weekdays(train1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
-cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = train1)
-summary(cr_weekday) # p=0.0006061
-
-#===================================================================
-# is_weekend
-train1$is_weekend <- FALSE
-train1$is_weekend[train1$weekday == "Saturday" | train1$weekday == "Sunday"] <- TRUE
-cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = train1)
-summary(cr_weekend) # p=0.001602
-
-#===================================================================
-# hour of the day
-train1$hour <- as.numeric(format(train1$datetime,"%H"))
-cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = train1)
-summary(cr_hour) # p=0.3994
-
-#===================================================================
-# morning/noon/evening/night?
-train1$ampm <- "Night"
-train1$ampm[train1$hour >= 5 & train1$hour < 12] <- "Morning"
-train1$ampm[train1$hour >= 12 & train1$hour < 17] <- "Afternoon" #noon - 5pm
-train1$ampm[train1$hour >= 17 & train1$hour < 20] <- "Evening" #5pm - 8pm
-cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = train1)
-summary(cr_ampm) # p=0.0001333
-
-#===================================================================
-# title length
-train1$title_length <- str_length(train1$title)
-cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = train1)
-summary(cr_title_len) # p=0.4386
-
-#===================================================================
-# text length
-train1$text_length <- str_length(train1$text)
-cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = train1)
-summary(cr_text_len) # p=1.477e-14
-
-#===================================================================
-# device name length
-train1$device_length <- str_length(train1$device)
-cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = train1)
-summary(cr_device_len) # p=0.0113
-
-#===================================================================
-# length of sentence until first punctuation mark
-train1$length <- str_locate(train1$text, pattern = "[.|?|!]")[,1]
-q <- quantile(train1$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
-train1$text_till_punct <- "none"
-train1$text_till_punct[train1$length <= q[3]] <- "short"
-train1$text_till_punct[train1$length >= q[3] & train1$length <= q[4]] <- "medium"
-train1$text_till_punct[train1$length >= q[4]] <- "long"
-
-cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = train1)
-summary(cr_tillpunct) # p=2.769e-07
-
-#===================================================================
-# if text contains any end punctuation
-train1$text_contain_punct <- str_detect(train1$text, pattern = "[.|?|!]")
-cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = train1)
-summary(cr_containpun) # p=8.269e-09
-identical(train1$text_contain_punct, train1$contain_punct)
-
-#===================================================================
-# if the text ends in a punctuation
-train1$text_end_punct <- str_detect(train1$text, pattern = "[.|?|!]$")
-cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = train1)
-summary(cr_endpunct) # p=0.185
-
-#===================================================================
-# if the title ends with a question mark
-library(rebus)
-train1$title_questionmark <- str_detect(train1$title, pattern = QUESTION %R% END)
-cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = train1)
-summary(cr_title_q) # p=6.55e-15
-
-#===================================================================
-# if title begins with "wh"
-train1$title_beginwh <- str_detect(str_to_lower(train1$title), pattern = "^wh")
-cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = train1)
-summary(cr_begin) # p=0.2241
-
-#===================================================================
-# if first letter of title is capitalized
-train1$capital_title <- str_detect(as.character(train1$title), pattern = "^[[:upper:]]")
-cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = train1)
-summary(cr_title) # p=0.6906
-
-#===================================================================
-# if first letter of text is capitalized
-train1$capital_text <- str_detect(as.character(train1$text), pattern = "^[[:upper:]]")
-cr_text <- coxph(Surv(time_until_answer, answered) ~ capital_text, data = train1)
-summary(cr_text) # p=6.642e-05
-
-#===================================================================
-# if text is in all lower case
-train1$cleaned <- str_replace_all(train1$text, " ", "")
-train1$cleaned <- str_replace_all(train1$cleaned, "[[:punct:]]|[[:digit:]]", "")
-train1$text_all_lower <- str_detect(train1$cleaned, pattern = "^[[:lower:]]+$")
-cr_lower <- coxph(Surv(time_until_answer, answered) ~ text_all_lower, data = train1)
-summary(cr_lower) # p=1.605e-05
-
-#===================================================================
-# prior_effort
-train1$prior_effort <- str_detect(str_to_lower(train1$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
-cr_prior <- coxph(Surv(time_until_answer, answered) ~ prior_effort, data = train1)
-summary(cr_prior) # p=0.0002236
-
-#===================================================================
-# num_prior_effort
-train1$num_prior_effort <- str_count(str_to_lower(train1$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
-cr_numprior <- coxph(Surv(time_until_answer, answered) ~ as.factor(num_prior_effort), data = train1)
-summary(cr_numprior) # p=0.000436 (lower p-value if treated as numeric)
-
-#===================================================================
-# expressing gratitude 
-train1$gratitude <- str_detect(str_to_lower(train1$text), pattern = or("please", "thank you", "thanks", "thankful", "appreciate", "appreciated", "grateful"))
-cr_gratitude <- coxph(Surv(time_until_answer, answered) ~ gratitude, data = train1)
-summary(cr_gratitude) # p=0.0001431
-
-#===================================================================
-# greeting
-train1$greeting <- str_detect(str_to_lower(train1$text), pattern = START %R% or("hey", "hello", "greetings", "hi"))
-cr_greeting <- coxph(Surv(time_until_answer, answered) ~ greeting, data = train1)
-summary(cr_greeting) # p=2.252e-08
-
-#===================================================================
-# update the question?
-train1$update <- str_detect(train1$text, pattern = "===")
-cr_up <- coxph(Surv(time_until_answer, answered) ~ update, data = train1)
-summary(cr_up) # p=3.398e-09
-
-#===================================================================
-# newline ratio to length of text
-train1$newline_ratio <- str_count(train1$text, pattern = "\n")/str_length(train1$text)
-cr_newline <- coxph(Surv(time_until_answer, answered) ~ newline_ratio, data = train1)
-summary(cr_newline) # p=1.228e-08
-```
-
-```{r, include = FALSE}
-# tag-based variables
-#===================================================================
-# avg_tag_length
-split_tags <- str_split(train1$tags, ", ", simplify = TRUE)
-train1$avg_tag_length <- NA
-not_na <- which(train1$tags != "")
-for (i in not_na) {
-  total_char <- sum(str_length(as.vector(split_tags[i,])))
-  total_tags <- sum(as.vector(split_tags[i,]) != "")
-  train1$avg_tag_length[i] <- total_char / total_tags
-}
-cr_tagl <- coxph(Surv(time_until_answer, answered) ~ avg_tag_length, data = train1)
-summary(cr_tagl) # p=0.1948
-
-#===================================================================
-# maximum number of words for a question's tags
-train1$max_tagwords <- rep(0, nrow(train1))
-for (i in which(train1$n_tags != 0)) {
-  tags <- as.vector(split_tags[i,])
-  train1$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
-}
-cr_max <- coxph(Surv(time_until_answer, answered) ~ max_tagwords, data = train1)
-summary(cr_max) # p=0.0001012 (should I treat this as categorical?)
-
-#===================================================================
-# frequent tags
-tag_vector <- as.vector(split_tags)
-tag_vector <- tag_vector[which(tag_vector != "")]
-unique_tags <- unique(tag_vector)
-
-tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
-tag_freq <- tag_freq %>%
-              arrange(desc(percent))
-
-#creating average frequency score variable
-train1$tag1 <- split_tags[,1]
-train1$tag2 <- split_tags[,2]
-train1$tag3 <- split_tags[,3]
-train1$tag4 <- split_tags[,4]
-
-assign_score <- function(data, variable) {
-  score <- rep(0, nrow(data))
-  notempty <- which(data[[variable]] != "")
-  for (i in notempty) {
-    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
-  }
-  return(score)
-}
-train1$score1 <- assign_score(train1, "tag1")
-train1$score2 <- assign_score(train1, "tag2")
-train1$score3 <- assign_score(train1, "tag3")
-train1$score4 <- assign_score(train1, "tag4")
-train1$avg_tag_score <- (train1$score1 + train1$score2 + train1$score3 + train1$score4)/as.numeric(train1$n_tags)
-train1$avg_tag_score[is.nan(train1$avg_tag_score)] <- 0
-cr_score <- coxph(Surv(time_until_answer, answered) ~ avg_tag_score, data = train1)
-summary(cr_score) # p=2.614e-10 insanely high hazard ratio
-
-#===================================================================
-# if question contains "frequent" tag
-percentile80 <- quantile(train1$avg_tag_score, probs = 0.80)
-
-train1$frequent_tag <- FALSE
-train1$frequent_tag[train1$avg_tag_score >= percentile80] <- TRUE
-cr_frequent <- coxph(Surv(time_until_answer, answered) ~ frequent_tag, data = train1)
-summary(cr_frequent) # p=1.814e-13
-
-#===================================================================
-# number of "frequent" tags a question contains
-threshold <- 0.005
-num_pop <- function(var, threshold) {
-  num_pop <- rep(0, nrow(train1))
-  num_pop[train1[[var]] >= threshold] <- 1
-  return(num_pop)
-}
-numpop1 <- num_pop("score1", threshold)
-numpop2 <- num_pop("score2", threshold)
-numpop3 <- num_pop("score3", threshold)
-numpop4 <- num_pop("score4", threshold)
-train1$num_freq_tags <- numpop1 + numpop2 + numpop3 + numpop4
-cr_numfreq <- coxph(Surv(time_until_answer, answered) ~ num_freq_tags, data = train1)
-summary(cr_numfreq) # p=3.432e-10
-
-#==================================================================================
-#frequent terms in unanswered/answered questions
-answered <- train1 %>%
-  tbl_df() %>% 
-  filter(answered == 1)
-
-unanswered <- train1 %>%
-  tbl_df() %>% 
-  filter(answered == 0)
-
-library(qdap)
-library(tm)
-terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
-colnames(terms_a)[2] <- "frequency_a"
-
-terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
-colnames(terms_u)[2] <- "frequency_u"
-
-combined <- dplyr::full_join(terms_a, terms_u, by = "word")
-combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
-
-p_threshold <- 0.01
-ratio_threshold <- 1
-
-freq_terms_u <- combined %>%
-                  filter(prop_in_unanswered > p_threshold) %>%
-                  filter(ratio < ratio_threshold)
-freq_terms_a <- combined %>%
-                  filter(prop_in_answered > p_threshold) %>%
-                  filter(ratio > ratio_threshold)
-
-train1$contain_unanswered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_u$word))
-train1$contain_answered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_a$word))
-
-cr_unans <- coxph(Surv(time_until_answer, answered) ~ contain_unanswered, data = train1)
-summary(cr_unans) # p=1.11e-16
-cr_ans <- coxph(Surv(time_until_answer, answered) ~ contain_answered, data = train1)
-summary(cr_ans) # p=2.314e-08
-```
-
-### Fitting model with all significant variables (univariate analysis p-value < 0.01)
-
-##### Trying out different variable selection functions
-
-```{r}
-first <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1)
-summary(first)
-AIC(first, k = 2) # 65065.88
-
-# backwards step-wise selection with selectCox function
-model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1, rule = "aic")
-
-#results
-results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + contain_answered + contain_unanswered, data = train1)
-AIC(results1, k = 2) #65059
+model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + text_length + text_contain_punct + num_freq_tags + n_tags + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1, rule = "aic")
+# results
+results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + contain_answered + text_all_lower + update + ampm + device_length, data = train1)
+AIC(results1, k = 2) #65285.49
 summary(results1)
@@
 # results
-results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1)
-AIC(results2, k = 2) # 65050.45
-summary(results2)
+results2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
+AIC(results2, k = 2) # 65277.47
+s <- summary(results2)
+nrow(s$coefficients)
 
-# best subset selection with glmulti function
-# took out variables based off of p-value (function couldn't handle amount of predictors)
-# model3 <- glmulti(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + capital_text + text_all_lower + prior_effort + greeting + update + newline_ratio + frequent_tag,
-#                 data = train1,
-#                 level = 1, 
-#                 method = "g", 
-#                 crit = "aic",
-#                 fitfunction = "coxph",
-#                 confsetsize = 5
-#                 )
-# model3@formulas
-# #results
-# results3 <- coxph(Surv(time_until_answer,answered)~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + newline_ratio + frequent_tag, data = train1)
-# AIC(results3) # 65098.48
-# summary(results3)
+```
 
-# trying out lasso regularization with the glmnet package
-# library(glmnet)
-# setting up matrix for function
-# mx <- as.matrix(train1 %>% 
-#   tbl_df() %>%
-#   dplyr::select(category, n_images, n_tags, new_user, weekday, ampm, text_length, device_length, text_contain_punct, title_questionmark, title_beginwh, capital_text, text_all_lower, prior_effort, gratitude, greeting, update, newline_ratio, max_tagwords, frequent_tag, contain_answered, contain_unanswered))
-# model4 <- glmnet(x, y = Surv(train1$time_until_answer, train1$answered, type = "right"), family = "cox")
-# summary(model4)
-# 
-# x <- model.matrix( ~ rx + sex + age + obstruct + perfor + adhere + surg - 1, d)
-# 
-# x <- model.matrix(~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered - 1, train1)
-```
+### Adding interaction terms
 
@@
 # working with model from backward/forward stepwise selection
-results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1) # 65050.45
 
 # adding interaction terms
-r2_i <- coxph(Surv(time_until_answer, answered) ~ category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
-AIC(r2_i, k = 2) # 65037.36
-summary(r2_i)
+# adding title_questionmark*title_beginwh
+model2.o <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
+AIC(model2.o, k = 2) # 65274.49
+oshitar::compare_nested(model2.o, results2)
+
+# adding new_user*update
+model2.o1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*update, data = train1)
+AIC(model2.o1, k = 2) # 65272.55
+oshitar::compare_nested(model2.o1, results2)
+
+# adding new_user*ampm 
+model2.o2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
+AIC(model2.o2, k = 2) # 65271.84
+oshitar::compare_nested(model2.o2, results2)
+
+# all signficant interaction terms 
+model_i <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
+AIC(model_i, k = 2) # 65263.35
 ```
@@
 train1 %>%
-  filter(category == "Media Player") %>%
+  filter(new_category == "Electronics") %>%
   group_by(subcategory) %>%
-  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n)
+  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n) %>%
+  arrange(median)
+
+train1 %>%
+  group_by(new_category) %>%
+  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n) %>%
+  arrange(median)
 
@@
 train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"
+# merge household and appliance into "Home"
 train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"
+# merging Car and Truck with Vehicle 
 train1$new_category[train1$new_category == "Car and Truck" | train1$new_category == "Vehicle"] <- "Vehicle"
 
-# if there are less than 60 questions in a category, group them with other
+# if there are less than 100 questions in a category, group them with other
 counts <- train1 %>%
@@
 
+model_new <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
+AIC(model_new, k = 2) #64999.87
+
+#new_cateogry*new_user
+#new_cateogry*
+model_new1 <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_category*new_user, data = train1)
+AIC(model_new1, k = 2) # 64994.49
+oshitar::compare_nested(model_new1, model_new)
+
+# model with ALL interactions
 # model with new_category
-final <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
-AIC(final, k = 2) # 64728.77
-summary(final)
+model_full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1)
+AIC(model_full, k = 2) # 64978.87
+summary(model_full)
 ```
@@
 
+* Martingale residuals
+    + plot for each continuous predictor 
+    + assess adequacy of functional form of predictors, or suggest a potential form 
+* Deviance residuals
+    + check for outliers identify questions poorly predicted by the model 
+    + one plot, examine questions with |residuals| > 2.5
+* Schoenfeld residuals
+    + one plot for each predictor 
+    + if loess curve is flat, proportional hazard assumption is not violated, doesn't depend on time. Distinct pattern indicates violation of this assumption
+    + **from the plots:** new_user, title_questionmark, num_freq_tags (1), ampm (Morning, Night), weekday (Thursday, Saturday), new_user*AMPM (morning, night) may violate PH assumption 
+* Score residuals
+    + check for influential observations. ID quesitons who's predictor values highly effect parameter estimates
+    + plot for each predictor 
+* **figure out how to identify certain points on ggplots**
+* statified on new_category, AIC dropped drastically. But this means that I can't compare the different groups in new_category 
 ```{r}
@@
 #martingale residuals
-train1$mart <- residuals(final, type = "martingale")
-plot_mart <- function(var) {
-  ggplot(train1, aes(x = train1[[var]], y = mart)) + 
+train1$mart <- residuals(model_full, type = "martingale")
+
+ggplot(train1, aes(x = device_length, y = mart)) + 
   geom_point() + 
   geom_smooth() + 
-    ggtitle(paste("Martingale Residuals for", var)) + 
-    scale_x_continuous(var)
-}
-
-q_vars <- c("n_images", "device_length", "newline_ratio")
-purrr::map(q_vars, plot_mart)
+  ggtitle(paste("Martingale Residuals for device_length")) + 
+  scale_x_continuous("Device_length")
 
@@
 #deviance residuals 
-train1$deviance <- residuals(final, type = "deviance")
+train1$deviance <- residuals(model_full, type = "deviance")
 ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
@@
 #schoenfeld residuals
-schoen <- as.data.frame(residuals(final, type = "schoenfeld"))
+schoen <- as.data.frame(residuals(model_full, type = "schoenfeld"))
 # complete event times sorted from shortest to longest
@@
 }
-names <- names(schoen)[-31]
+names <- names(schoen)[-ncol(schoen)]
 purrr::map(names, plot_schoen)
@@
 # score residuals
-score <- as.data.frame(residuals(final, type = "score"))
+score <- as.data.frame(residuals(model_full, type = "score"))
 # function to plot score residuals
@@
 purrr::map(columns, plot_score)
+
+#=============================================
+# formal test of PH assumption
+ph_test <- data.frame(predictors = rownames(cox.zph(model_full)$table), cox.zph(model_full)$table) 
+rownames(ph_test) = NULL
+ph_test <- ph_test %>%
+  arrange(p)
+
+# stratifying on new_category
+strat_model <- coxph(Surv(time_until_answer, answered) ~ strata(new_category) + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
+AIC(strat_model, k = 2) # 49766.8
+summary(strat_model)
+
+# stratifying on new_user
+strat_model1 <- coxph(Surv(time_until_answer, answered) ~ new_category + strata(new_user) + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
+AIC(strat_model1, k = 2) # 60543.75
+summary(strat_model1)
+
+# final model: stratified on new_category
+final <- strat_model
 ```
@@
 ### Predicting on the test data
+
+##### variable set up in test data
+
+* categorical variables must be the same across data sets, but I want the categorical variable to change with each data set, any way to do this?
 
@@
 
+#=============================================
+# predicting on the test data
+
 #356 NAs in the predictions
-test_predict <- predict(final, newdata = test1, type = "risk", se.fit = TRUE)
+test_predict <- predict(model_full, newdata = test1, type = "risk", se.fit = TRUE)
 test1$predictions <- test_predict[[1]]
@@
 ```
+
+```{r}
+# function to set up variables for test data 
+variable_setup <- function(data) {
+  data$category <- as.character(data$category)
+  data$category[is.na(data$category)] <- "Other"
+
+  data$new_category <- data$category
+  apple_terms <- c("apple", "ipod", "ipad")
+  data$apple <- str_detect(str_to_lower(data$device), pattern = START %R% or1(apple_terms) %R% SPC)
+  data$new_category[data$apple == TRUE | data$subcategory == "iPhone" | data$category == "Mac"] <- "Apple Product"
+  data$new_category[data$new_category == "Phone"] <- "Android/Other Phone"
+  data$new_category[data$new_category == "Appliance" | data$new_category == "Household"] <- "Home"
+  data$new_category[data$new_category == "Car and Truck" | data$new_category == "Vehicle"] <- "Vehicle"
+  data$new_category[data$new_category == "Computer Hardware" | data$new_category == "Media Player" |
+                     data$new_category == "Apparel"] <- "Other"
+  #=============================================
+  #weekday
+  data$datetime <- as.POSIXct(data$post_date,origin="1970-01-01")
+  data$weekday <- factor(weekdays(data$datetime), levels = c("Monday", "Tuesday", "Wednesday", 
+                                                             "Thursday", "Friday", "Saturday", "Sunday"))
+  #=============================================
+  #ampm
+  data$hour <- as.numeric(format(data$datetime,"%H"))
+  data$ampm <- "Night"
+  data$ampm[data$hour >= 5 & data$hour < 12] <- "Morning"
+  data$ampm[data$hour >= 12 & data$hour < 17] <- "Afternoon" #noon - 5pm
+  data$ampm[data$hour >= 17 & data$hour < 20] <- "Evening" #5pm - 8pm
+  #=============================================
+  # text length
+  data$text_length <- str_length(data$text)
+  #=============================================
+  # device name length
+  data$device_length <- str_length(data$device)
+  #=============================================
+  # if the title ends with a question mark
+  library(rebus)
+  data$title_questionmark <- str_detect(data$title, pattern = QUESTION %R% END)
+  #=============================================
+  # if title begins with "wh"
+  data$title_beginwh <- str_detect(str_to_lower(data$title), pattern = "^wh")
+  #=============================================
+  data$capital_text <- str_detect(as.character(data$text), pattern = "^[[:upper:]]")
+  #=============================================
+  data$update <- str_detect(data$text, pattern = "===")
+  #=============================================
+  data$newline_ratio <- str_count(data$text, pattern = "\n")/str_length(data$text)
+  #=============================================
+  # frequent tags
+  split_tags <- str_split(data$tags, ", ", simplify = TRUE)
+  tag_vector <- as.vector(split_tags)
+  tag_vector <- tag_vector[which(tag_vector != "")]
+  unique_tags <- unique(tag_vector)
+
+  tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
+  tag_freq <- tag_freq %>%
+              arrange(desc(percent))
+
+  #creating average frequency score variable
+  data$tag1 <- split_tags[,1]
+  data$tag2 <- split_tags[,2]
+  data$tag3 <- split_tags[,3]
+  data$tag4 <- split_tags[,4]
+
+  assign_score <- function(data, variable) {
+    score <- rep(0, nrow(data))
+    notempty <- which(data[[variable]] != "")
+    for (i in notempty) {
+      score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
+    }
+    return(score)
+  }
+  data$score1 <- assign_score(data, "tag1")
+  data$score2 <- assign_score(data, "tag2")
+  data$score3 <- assign_score(data, "tag3")
+  data$score4 <- assign_score(data, "tag4")
+  data$avg_tag_score <- (data$score1 + data$score2 + data$score3 + 
+                            data$score4)/as.numeric(data$n_tags)
+  data$avg_tag_score[is.nan(data$avg_tag_score)] <- 0
+  #=============================================
+  # if question contains "frequent" tag
+  percentile80 <- quantile(data$avg_tag_score, probs = 0.80)
+
+  data$frequent_tag <- FALSE
+  data$frequent_tag[data$avg_tag_score >= percentile80] <- TRUE
+  #=============================================
+  #frequent terms in unanswered/answered questions
+  answered <- data %>%
+      tbl_df() %>% 
+      filter(answered == 1)
+  unanswered <- data %>%
+    tbl_df() %>% 
+    filter(answered == 0)
+
+  library(qdap)
+  library(tm)
+  terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+  terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
+  colnames(terms_a)[2] <- "frequency_a"
+
+  terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
+  terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
+  colnames(terms_u)[2] <- "frequency_u"
+
+  combined <- dplyr::full_join(terms_a, terms_u, by = "word")
+  combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
+
+  p_threshold <- 0.01
+  ratio_threshold <- 1
+
+  freq_terms_u <- combined %>%
+                    filter(prop_in_unanswered > p_threshold) %>%
+                    filter(ratio < ratio_threshold)
+  freq_terms_a <- combined %>%
+                    filter(prop_in_answered > p_threshold) %>%
+                    filter(ratio > ratio_threshold)
+
+  data$contain_unanswered <- str_detect(as.character(data$title), pattern = or1(freq_terms_u$word))
+  data$contain_answered <- str_detect(as.character(data$title), pattern = or1(freq_terms_a$word))
+
+  data$new_user <- as.factor(data$new_user)
+
+  return(data)
+}
+
+```

### 2017-08-15 model fitting/univariate_analysis.Rmd
created new markdown for univariate analysis, stratified model on new_category

---
title: "Univariate Analysis"
author: "Lisa Oshita"
date: "8/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
x <- oshitar::setup()
library(survival)
library(stringr)
library(rebus)
library(dplyr)
library(stats)
library(ggplot2)
```

### Setting up cross validation paths

* cross validation paths stored in splitPlan
* set seed for reproducible results

```{r, echo = FALSE}
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
str(splitPlan)
```

### Analysis on test data

```{r, data and text variables, include = FALSE}
train1 <- x[splitPlan[[1]]$train, ]

pvalues <- data.frame(variable = character(), pvalue = numeric())

#function to get summary of cox model + append pvalue of variable from loglik test to data frame
get_pvalue <- function(variable, factor = FALSE) {
  if (factor == FALSE){
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
  } else {
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
  }
  summary <- summary(coxmodel)
  print(summary)
  df <- data.frame(variable = variable, pvalue = unname(summary$logtest[[3]]))
  pvalues <- rbind(pvalues, df)
  return(pvalues)
}

#===================================================================
# Univariate analyses (select variables with p-value < 0.01)
# category 
train1$category <- as.character(train1$category)
train1$category[is.na(train1$category)] <- "Other"
train1$category <- as.factor(train1$category)
pvalues <- get_pvalue("category")
#===================================================================
# n_images
pvalues <- get_pvalue("n_images")

# new_n_images (recoding to group questions with >= 6 images) 
train1$new_n_images <- as.character(train1$n_images)
train1$new_n_images[train1$n_images >= 6] <- ">= 6"
pvalues <- get_pvalue("new_n_images")

#===================================================================
# n_tags
pvalues <- get_pvalue("n_tags")

#===================================================================
# new_user
pvalues <- get_pvalue("new_user", factor = TRUE)

#===================================================================
# weekday
train1$datetime <- as.POSIXct(train1$post_date,origin="1970-01-01")
train1$weekday <- factor(weekdays(train1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
pvalues <- get_pvalue("weekday")

#===================================================================
# is_weekend
train1$is_weekend <- FALSE
train1$is_weekend[train1$weekday == "Saturday" | train1$weekday == "Sunday"] <- TRUE
pvalues <- get_pvalue("is_weekend")

#===================================================================
# hour of the day
train1$hour <- as.numeric(format(train1$datetime,"%H"))
pvalues <- get_pvalue("hour", factor = TRUE)

#===================================================================
# morning/noon/evening/night?
train1$ampm <- "Night"
train1$ampm[train1$hour >= 5 & train1$hour < 12] <- "Morning"
train1$ampm[train1$hour >= 12 & train1$hour < 17] <- "Afternoon" #noon - 5pm
train1$ampm[train1$hour >= 17 & train1$hour < 20] <- "Evening" #5pm - 8pm
pvalues <- get_pvalue("ampm")

#===================================================================
# title length
train1$title_length <- str_length(train1$title)
pvalues <- get_pvalue("title_length", factor = FALSE)

#===================================================================
# text length
train1$text_length <- str_length(train1$text)
pvalues <- get_pvalue("text_length")

#===================================================================
# device name length
train1$device_length <- str_length(train1$device)
pvalues <- get_pvalue("device_length")

#===================================================================
# length of sentence until first punctuation mark
train1$length <- str_locate(train1$text, pattern = "[.|?|!]")[,1]
q <- stats::quantile(train1$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
train1$text_till_punct <- "none"
train1$text_till_punct[train1$length <= q[3]] <- "short"
train1$text_till_punct[train1$length >= q[3] & train1$length <= q[4]] <- "medium"
train1$text_till_punct[train1$length >= q[4]] <- "long"
pvalues <- get_pvalue("text_till_punct")

#===================================================================
# if text contains any end punctuation
train1$text_contain_punct <- str_detect(train1$text, pattern = "[.|?|!]")
pvalues <- get_pvalue("text_contain_punct")

#===================================================================
# if the text ends in a punctuation
train1$text_end_punct <- str_detect(train1$text, pattern = "[.|?|!]$")
pvalues <- get_pvalue("text_end_punct")

#===================================================================
# if the title ends with a question mark
train1$title_questionmark <- str_detect(train1$title, pattern = QUESTION %R% END)
pvalues <- get_pvalue("title_questionmark")

#===================================================================
# if title begins with "wh"
train1$title_beginwh <- str_detect(str_to_lower(train1$title), pattern = "^wh")
pvalues <- get_pvalue("title_beginwh")

#===================================================================
# if first letter of title is capitalized
train1$capital_title <- str_detect(as.character(train1$title), pattern = "^[[:upper:]]")
pvalues <- get_pvalue("capital_title")

#===================================================================
# if first letter of text is capitalized
train1$capital_text <- str_detect(as.character(train1$text), pattern = "^[[:upper:]]")
pvalues <- get_pvalue("capital_text")

#===================================================================
# if text is in all lower case
train1$cleaned <- str_replace_all(train1$text, " ", "")
train1$cleaned <- str_replace_all(train1$cleaned, "[[:punct:]]|[[:digit:]]", "")
train1$text_all_lower <- str_detect(train1$cleaned, pattern = "^[[:lower:]]+$")
pvalues <- get_pvalue("text_all_lower")

#===================================================================
# prior_effort
prior_terms <- c("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted")
train1$prior_effort <- str_detect(str_to_lower(train1$text), pattern = or1(prior_terms))
pvalues <- get_pvalue("prior_effort")

#===================================================================
# num_prior_effort
train1$num_prior_effort <- str_count(str_to_lower(train1$text), pattern = or1(prior_terms))
pvalues <- get_pvalue("num_prior_effort")

#===================================================================
# expressing gratitude 
gratitude_terms <- c("please", "thank you", "thanks", "thankful", "appreciate", "appreciated", "grateful")
train1$gratitude <- str_detect(str_to_lower(train1$text), pattern = or1(gratitude_terms))
pvalues <- get_pvalue("gratitude")

#===================================================================
# greeting
greeting_terms <- c("hey", "hello", "greetings", "hi")
train1$greeting <- str_detect(str_to_lower(train1$text), pattern = START %R% or1(greeting_terms))
pvalues <- get_pvalue("greeting")

#===================================================================
# update the question?
train1$update <- str_detect(train1$text, pattern = "===")
pvalues <- get_pvalue("update")

#===================================================================
# newline ratio to length of text
train1$newline_ratio <- str_count(train1$text, pattern = "\n")/str_length(train1$text)
pvalues <- get_pvalue("newline_ratio")
```

```{r, tag based and frequent term variables, include = FALSE}
# tag-based variables
#===================================================================
# avg_tag_length
split_tags <- str_split(train1$tags, ", ", simplify = TRUE)
train1$avg_tag_length <- NA
not_na <- which(train1$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  train1$avg_tag_length[i] <- total_char / total_tags
}
pvalues <- get_pvalue("avg_tag_length")

#===================================================================
# maximum number of words for a question's tags
train1$max_tagwords <- rep(0, nrow(train1))
for (i in which(train1$n_tags != 0)) {
  tags <- as.vector(split_tags[i,])
  train1$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
}
pvalues <- get_pvalue("max_tagwords")

#===================================================================
# frequent tags
tag_vector <- as.vector(split_tags)
tag_vector <- tag_vector[which(tag_vector != "")]
unique_tags <- unique(tag_vector)

tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
tag_freq <- tag_freq %>%
              arrange(desc(percent))

#creating average frequency score variable
train1$tag1 <- split_tags[,1]
train1$tag2 <- split_tags[,2]
train1$tag3 <- split_tags[,3]
train1$tag4 <- split_tags[,4]

assign_score <- function(data, variable) {
  score <- rep(0, nrow(data))
  notempty <- which(data[[variable]] != "")
  for (i in notempty) {
    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
  }
  return(score)
}
train1$score1 <- assign_score(train1, "tag1")
train1$score2 <- assign_score(train1, "tag2")
train1$score3 <- assign_score(train1, "tag3")
train1$score4 <- assign_score(train1, "tag4")
train1$avg_tag_score <- (train1$score1 + train1$score2 + train1$score3 + train1$score4)/as.numeric(train1$n_tags)
train1$avg_tag_score[is.nan(train1$avg_tag_score)] <- 0

pvalues <- get_pvalue("avg_tag_score")

#===================================================================
# if question contains "frequent" tag
percentile80 <- quantile(train1$avg_tag_score, probs = 0.80)

train1$frequent_tag <- FALSE
train1$frequent_tag[train1$avg_tag_score >= percentile80] <- TRUE

pvalues <- get_pvalue("frequent_tag")

#===================================================================
# number of "frequent" tags a question contains
threshold <- 0.005
num_pop <- function(var, threshold) {
  num_pop <- rep(0, nrow(train1))
  num_pop[train1[[var]] >= threshold] <- 1
  return(num_pop)
}
numpop1 <- num_pop("score1", threshold)
numpop2 <- num_pop("score2", threshold)
numpop3 <- num_pop("score3", threshold)
numpop4 <- num_pop("score4", threshold)
train1$num_freq_tags <- numpop1 + numpop2 + numpop3 + numpop4

pvalues <- get_pvalue("num_freq_tags")

#==================================================================================
#frequent terms in unanswered/answered questions
answered <- train1 %>%
  tibble::as_tibble() %>% 
  filter(answered == 1)

unanswered <- train1 %>%
  tibble::as_tibble() %>% 
  filter(answered == 0)

terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
colnames(terms_a)[2] <- "frequency_a"

terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
colnames(terms_u)[2] <- "frequency_u"

combined <- dplyr::full_join(terms_a, terms_u, by = "word")
combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered

p_threshold <- 0.01
ratio_threshold <- 1

freq_terms_u <- combined %>%
                  filter(prop_in_unanswered > p_threshold) %>%
                  filter(ratio < ratio_threshold)
freq_terms_a <- combined %>%
                  filter(prop_in_answered > p_threshold) %>%
                  filter(ratio > ratio_threshold)

train1$contain_unanswered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_u$word))
train1$contain_answered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_a$word))

pvalues <- get_pvalue("contain_unanswered")
pvalues <- get_pvalue("contain_answered")
```

### examining univariate analyses results

```{r, echo = FALSE}
options(scipen=999)
(pvalues <- pvalues %>%
  arrange(pvalue))
```

### 2017-08-16 model fitting/cross_validation.Rmd
cross validation, updated hours

@@
 ```{r}
+train1 <- x[splitPlan[[1]]$train, ]
+
 first <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + contain_unanswered + title_questionmark + text_length + text_contain_punct + as.factor(num_freq_tags) + as.factor(n_tags) + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1)
@@
 AIC(results2, k = 2) # 65277.47
-s <- summary(results2)
-nrow(s$coefficients)
 
@@
 # adding title_questionmark*title_beginwh
-model2.o <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
-AIC(model2.o, k = 2) # 65274.49
-oshitar::compare_nested(model2.o, results2)
+model2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
+AIC(model2, k = 2) # 65274.49
+compare_nested(model2, results2)
 
 # adding new_user*update
-model2.o1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*update, data = train1)
-AIC(model2.o1, k = 2) # 65272.55
-oshitar::compare_nested(model2.o1, results2)
+model2_1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*update, data = train1)
+AIC(model2_1, k = 2) # 65272.55
+compare_nested(model2_1, results2)
 
 # adding new_user*ampm 
-model2.o2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
-AIC(model2.o2, k = 2) # 65271.84
-oshitar::compare_nested(model2.o2, results2)
+model2_2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
+AIC(model2_2, k = 2) # 65271.84
+compare_nested(model2_2, results2)
 
@@
   coord_polar(theta = "y")
-
-train1 %>%
-  filter(new_category == "Electronics") %>%
-  group_by(subcategory) %>%
-  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n) %>%
-  arrange(median)
-
-train1 %>%
-  group_by(new_category) %>%
-  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n) %>%
-  arrange(median)
 
@@
 AIC(model_new1, k = 2) # 64994.49
-oshitar::compare_nested(model_new1, model_new)
+compare_nested(model_new1, model_new)
 
@@
 * statified on new_category, AIC dropped drastically. But this means that I can't compare the different groups in new_category
+
 ```{r}
@@
 
+### Performance metric on training data set
+
+```{r}
+train_predict <- predict(object = final, type = "risk", se.fit = TRUE)
+train1$predictions <- train_predict[[1]]
+performance <- coxph(Surv(time_until_answer, answered) ~ predictions, data = train1)
+summary(performance)
+AIC(performance, k = 2)
+
+#using cph from rms package to get Dxy and other performance metrics
+library(rms)
+options(scipen=999)
+(cox <- cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
+cox$stats
+```
+
 ### Predicting on the test data
-
-##### variable set up in test data
 
@@
 ```{r}
+
+#calculating root
+
 test1 <- x[splitPlan[[1]]$app, ]
+# setting up variables for model 
+test1 <- oshitar::variable_setup(test1)
 
-#setting up variables in test1
-#=============================================
-test1$category <- as.character(test1$category)
-test1$category[is.na(test1$category)] <- "Other"
-#new_category
-test1$new_category <- test1$category
-apple_terms <- c("apple", "ipod", "ipad")
-test1$apple <- str_detect(str_to_lower(test1$device), pattern = START %R% or1(apple_terms) %R% SPC)
-test1$new_category[test1$apple == TRUE | test1$subcategory == "iPhone" | test1$category == "Mac"] <- "Apple Product"
-test1$new_category[test1$new_category == "Phone"] <- "Android/Other Phone"
-test1$new_category[test1$new_category == "Appliance" | test1$new_category == "Household"] <- "Home"
-test1$new_category[test1$new_category == "Car and Truck" | test1$new_category == "Vehicle"] <- "Vehicle"
-test1$new_category[test1$new_category == "Computer Hardware" | test1$new_category == "Media Player" | test1$new_category == "Apparel"] <- "Other"
-# counts <- test1 %>%
-#   group_by(new_category) %>%
-#   summarise(n = n(), prop = n/nrow(test1))
-# for (i in which(counts$prop <= 0.01)) {
-#   test1$new_category[test1$new_category == counts$new_category[i]] <- "Other"
-# }
-#=============================================
-#weekday
-test1$datetime <- as.POSIXct(test1$post_date,origin="1970-01-01")
-test1$weekday <- factor(weekdays(test1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
-#=============================================
-#ampm
-test1$hour <- as.numeric(format(test1$datetime,"%H"))
-test1$ampm <- "Night"
-test1$ampm[test1$hour >= 5 & test1$hour < 12] <- "Morning"
-test1$ampm[test1$hour >= 12 & test1$hour < 17] <- "Afternoon" #noon - 5pm
-test1$ampm[test1$hour >= 17 & test1$hour < 20] <- "Evening" #5pm - 8pm
-#=============================================
-# text length
-test1$text_length <- str_length(test1$text)
-#=============================================
-# device name length
-test1$device_length <- str_length(test1$device)
-#=============================================
-# if the title ends with a question mark
-library(rebus)
-test1$title_questionmark <- str_detect(test1$title, pattern = QUESTION %R% END)
-#=============================================
-# if title begins with "wh"
-test1$title_beginwh <- str_detect(str_to_lower(test1$title), pattern = "^wh")
-#=============================================
-test1$capital_text <- str_detect(as.character(test1$text), pattern = "^[[:upper:]]")
-#=============================================
-test1$update <- str_detect(test1$text, pattern = "===")
-#=============================================
-test1$newline_ratio <- str_count(test1$text, pattern = "\n")/str_length(test1$text)
-#=============================================
-# frequent tags
-split_tags <- str_split(test1$tags, ", ", simplify = TRUE)
-tag_vector <- as.vector(split_tags)
-tag_vector <- tag_vector[which(tag_vector != "")]
-unique_tags <- unique(tag_vector)
-
-tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
-tag_freq <- tag_freq %>%
-              arrange(desc(percent))
-
-#creating average frequency score variable
-test1$tag1 <- split_tags[,1]
-test1$tag2 <- split_tags[,2]
-test1$tag3 <- split_tags[,3]
-test1$tag4 <- split_tags[,4]
-
-assign_score <- function(data, variable) {
-  score <- rep(0, nrow(data))
-  notempty <- which(data[[variable]] != "")
-  for (i in notempty) {
-    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
-  }
-  return(score)
-}
-test1$score1 <- assign_score(test1, "tag1")
-test1$score2 <- assign_score(test1, "tag2")
-test1$score3 <- assign_score(test1, "tag3")
-test1$score4 <- assign_score(test1, "tag4")
-test1$avg_tag_score <- (test1$score1 + test1$score2 + test1$score3 + test1$score4)/as.numeric(test1$n_tags)
-test1$avg_tag_score[is.nan(test1$avg_tag_score)] <- 0
-#=============================================
-# if question contains "frequent" tag
-percentile80 <- quantile(test1$avg_tag_score, probs = 0.80)
-
-test1$frequent_tag <- FALSE
-test1$frequent_tag[test1$avg_tag_score >= percentile80] <- TRUE
-#=============================================
-#frequent terms in unanswered/answered questions
-answered <- test1 %>%
-  tbl_df() %>% 
-  filter(answered == 1)
-unanswered <- test1 %>%
-  tbl_df() %>% 
-  filter(answered == 0)
-
-library(qdap)
-library(tm)
-terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
-colnames(terms_a)[2] <- "frequency_a"
-
-terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
-colnames(terms_u)[2] <- "frequency_u"
-
-combined <- dplyr::full_join(terms_a, terms_u, by = "word")
-combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
-
-p_threshold <- 0.01
-ratio_threshold <- 1
-
-freq_terms_u <- combined %>%
-                  filter(prop_in_unanswered > p_threshold) %>%
-                  filter(ratio < ratio_threshold)
-freq_terms_a <- combined %>%
-                  filter(prop_in_answered > p_threshold) %>%
-                  filter(ratio > ratio_threshold)
-
-test1$contain_unanswered <- str_detect(as.character(test1$title), pattern = or1(freq_terms_u$word))
-test1$contain_answered <- str_detect(as.character(test1$title), pattern = or1(freq_terms_a$word))
-
-test1$new_user <- as.factor(test1$new_user)
-
-#=============================================
-# predicting on the test data
-
-#356 NAs in the predictions
-test_predict <- predict(model_full, newdata = test1, type = "risk", se.fit = TRUE)
+test_predict <- predict(object = final, newdata = test1, type = "risk", se.fit = TRUE)
 test1$predictions <- test_predict[[1]]
@@
 
+### working with the rms package for cross validation
+
 ```{r}
-# function to set up variables for test data 
-variable_setup <- function(data) {
-  data$category <- as.character(data$category)
-  data$category[is.na(data$category)] <- "Other"
+library(rms)
+(cox <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
 
-  data$new_category <- data$category
-  apple_terms <- c("apple", "ipod", "ipad")
-  data$apple <- str_detect(str_to_lower(data$device), pattern = START %R% or1(apple_terms) %R% SPC)
-  data$new_category[data$apple == TRUE | data$subcategory == "iPhone" | data$category == "Mac"] <- "Apple Product"
-  data$new_category[data$new_category == "Phone"] <- "Android/Other Phone"
-  data$new_category[data$new_category == "Appliance" | data$new_category == "Household"] <- "Home"
-  data$new_category[data$new_category == "Car and Truck" | data$new_category == "Vehicle"] <- "Vehicle"
-  data$new_category[data$new_category == "Computer Hardware" | data$new_category == "Media Player" |
-                     data$new_category == "Apparel"] <- "Other"
-  #=============================================
-  #weekday
-  data$datetime <- as.POSIXct(data$post_date,origin="1970-01-01")
-  data$weekday <- factor(weekdays(data$datetime), levels = c("Monday", "Tuesday", "Wednesday", 
-                                                             "Thursday", "Friday", "Saturday", "Sunday"))
-  #=============================================
-  #ampm
-  data$hour <- as.numeric(format(data$datetime,"%H"))
-  data$ampm <- "Night"
-  data$ampm[data$hour >= 5 & data$hour < 12] <- "Morning"
-  data$ampm[data$hour >= 12 & data$hour < 17] <- "Afternoon" #noon - 5pm
-  data$ampm[data$hour >= 17 & data$hour < 20] <- "Evening" #5pm - 8pm
-  #=============================================
-  # text length
-  data$text_length <- str_length(data$text)
-  #=============================================
-  # device name length
-  data$device_length <- str_length(data$device)
-  #=============================================
-  # if the title ends with a question mark
-  library(rebus)
-  data$title_questionmark <- str_detect(data$title, pattern = QUESTION %R% END)
-  #=============================================
-  # if title begins with "wh"
-  data$title_beginwh <- str_detect(str_to_lower(data$title), pattern = "^wh")
-  #=============================================
-  data$capital_text <- str_detect(as.character(data$text), pattern = "^[[:upper:]]")
-  #=============================================
-  data$update <- str_detect(data$text, pattern = "===")
-  #=============================================
-  data$newline_ratio <- str_count(data$text, pattern = "\n")/str_length(data$text)
-  #=============================================
-  # frequent tags
-  split_tags <- str_split(data$tags, ", ", simplify = TRUE)
-  tag_vector <- as.vector(split_tags)
-  tag_vector <- tag_vector[which(tag_vector != "")]
-  unique_tags <- unique(tag_vector)
-
-  tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
-  tag_freq <- tag_freq %>%
-              arrange(desc(percent))
-
-  #creating average frequency score variable
-  data$tag1 <- split_tags[,1]
-  data$tag2 <- split_tags[,2]
-  data$tag3 <- split_tags[,3]
-  data$tag4 <- split_tags[,4]
-
-  assign_score <- function(data, variable) {
-    score <- rep(0, nrow(data))
-    notempty <- which(data[[variable]] != "")
-    for (i in notempty) {
-      score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
-    }
-    return(score)
-  }
-  data$score1 <- assign_score(data, "tag1")
-  data$score2 <- assign_score(data, "tag2")
-  data$score3 <- assign_score(data, "tag3")
-  data$score4 <- assign_score(data, "tag4")
-  data$avg_tag_score <- (data$score1 + data$score2 + data$score3 + 
-                            data$score4)/as.numeric(data$n_tags)
-  data$avg_tag_score[is.nan(data$avg_tag_score)] <- 0
-  #=============================================
-  # if question contains "frequent" tag
-  percentile80 <- quantile(data$avg_tag_score, probs = 0.80)
-
-  data$frequent_tag <- FALSE
-  data$frequent_tag[data$avg_tag_score >= percentile80] <- TRUE
-  #=============================================
-  #frequent terms in unanswered/answered questions
-  answered <- data %>%
-      tbl_df() %>% 
-      filter(answered == 1)
-  unanswered <- data %>%
-    tbl_df() %>% 
-    filter(answered == 0)
-
-  library(qdap)
-  library(tm)
-  terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-  terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
-  colnames(terms_a)[2] <- "frequency_a"
-
-  terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-  terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
-  colnames(terms_u)[2] <- "frequency_u"
-
-  combined <- dplyr::full_join(terms_a, terms_u, by = "word")
-  combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
-
-  p_threshold <- 0.01
-  ratio_threshold <- 1
-
-  freq_terms_u <- combined %>%
-                    filter(prop_in_unanswered > p_threshold) %>%
-                    filter(ratio < ratio_threshold)
-  freq_terms_a <- combined %>%
-                    filter(prop_in_answered > p_threshold) %>%
-                    filter(ratio > ratio_threshold)
-
-  data$contain_unanswered <- str_detect(as.character(data$title), pattern = or1(freq_terms_u$word))
-  data$contain_answered <- str_detect(as.character(data$title), pattern = or1(freq_terms_a$word))
-
-  data$new_user <- as.factor(data$new_user)
-
-  return(data)
-}
-
+(cv <- validate(cox, method = "crossvalidation", B = 10, dxy = TRUE, pr = TRUE))
 ```

### 2017-08-17 model fitting/cross_validation.Rmd
finished cross validation, wrote function to take data set, fit model and extract predicted survival probabilities

@@
 
-```{r, echo = FALSE}
+```{r, data setup, echo = FALSE}
 x <- oshitar::setup()
@@
 
-##### Fitting model with all significant variables (univariate analysis p-value < 0.01), select variables using stepwise functions
+##### Fitting model with all significant variables (univariate analysis p-value < 0.01)
 
-```{r}
+```{r, echo = FALSE}
 train1 <- x[splitPlan[[1]]$train, ]
@@
 # backwards step-wise selection with selectCox function
-# converting to factors since function doesn't work with as.factor
+# converting to factors since function doesn't work with as.factor()
 train1$new_user <- as.factor(train1$new_user)
@@
 AIC(results2, k = 2) # 65277.47
-
 ```
@@
 
-```{r}
-# working with model from backward/forward stepwise selection
+* working with model from backward/forward stepwise selection
 
-# adding interaction terms
+```{r, echo = FALSE}
 # adding title_questionmark*title_beginwh
@@
 
-* group all apple products together (use str_detect to search for Apple, ipad, ipod)
+* group all apple products together
+    + use str_detect to search for ipad, ipod, apple watch 
+    + group with iPhones and Macs 
 * recode left over Phones to Android/Other Phone
@@
 * group car and truck + vehicle as "Vehicle"
-* set a rule: any category with less than 50 questions gets grouped with "Other"
+* set a rule: any category with less than 100 questions gets grouped with "Other"
 
-```{r}
-# pie chart of product categories
-ggplot(train1, aes(x = factor(1), fill = category)) + geom_bar(width = 1) + 
-  coord_polar(theta = "y")
-
-#===================================================
-# recoding category variable
+```{r, echo = FALSE}
 train1$new_category <- as.character(train1$category)
@@
 train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"
+
 # merge household and appliance into "Home"
 train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"
+
 # merging Car and Truck with Vehicle 
@@
 
-# if there are less than 100 questions in a category, group them with other
+# if there are less than 100 questions in a category, group them with Other
 counts <- train1 %>%
@@
 table(train1$new_category)
+
 #===================================================
@@
 #new_cateogry*new_user
-#new_cateogry*
 model_new1 <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_category*new_user, data = train1)
@@
 * statified on new_category, AIC dropped drastically. But this means that I can't compare the different groups in new_category 
+    + Concordance statistic and rsquare dropped
 
-```{r}
+```{r, residuals, echo = FALSE}
 #=============================================
@@
 
+#=============================================
+# addression PH assumption violations
+
 # stratifying on new_category
@@
 
-# final model: stratified on new_category
-final <- strat_model
+# stratifying on ampm 
+strat_model2 <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + strata(ampm) + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
+AIC(strat_model2, k = 2) # 54447.8
+summary(strat_model2)
+
+# stratifying on ampm, new_user, new_category
+strat_model3 <- coxph(Surv(time_until_answer, answered) ~ strata(new_category) + strata(new_user) + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + strata(ampm) + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
+AIC(strat_model3, k = 2) # 35370.81
+summary(strat_model3)
 ```
@@
 
+* model not stratified on new_category has higher R2, higher Dxy than model stratified on new_category
+* survConcordance: 
+    + Concordance is defined as Pr(agreement) for any two randomly chosen observations, where in this case agreement means that the observation with the shorter survival time of the two also has the larger risk score.
+The predictor (or risk score) will often be the result of a Cox model or other regression
+    + some of the pairs are incomparable. For instance a pair of times (5+, 8), the first being a censored value. We do not know whether the first survival time is greater than or less than the second
+    + observations that are comparable, pairs may also be tied on survival time (but only if both are uncensored) or on the predictor.
+The final concondance is (agree + tied/2)/(agree + disagree + tied)
+    +
+
 ```{r}
-train_predict <- predict(object = final, type = "risk", se.fit = TRUE)
+# working with final model (stratified on new_category) 
+train_predict <- predict(object = strat_model, type = "risk", se.fit = TRUE)
 train1$predictions <- train_predict[[1]]
-performance <- coxph(Surv(time_until_answer, answered) ~ predictions, data = train1)
-summary(performance)
-AIC(performance, k = 2)
 
-#using cph from rms package to get Dxy and other performance metrics
-library(rms)
+(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.115
+AIC(performance, k = 2) # 65781.26
+
+survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train1) # Concordance = 0.5573537
+
+Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions, data = train1)
+
+#=============================================
+
+# working with full_model (not stratified on new_category)
+train_predict2 <- predict(object = model_full, type = "risk", se.fit = TRUE)
+train1$predictions2 <- train_predict2[[1]]
+(performance2 <- rms::cph(Surv(time_until_answer, answered) ~ predictions2, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.270
+
+survConcordance(Surv(time_until_answer, answered) ~ predictions2, data = train1) # Concordance = 0.634903
+
+Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions2, outx = TRUE, data = train1)
+
+#=============================================
+
+# working with strat_model1 (stratified on new_user)
+train_predict3 <- predict(object = strat_model1, type = "risk", se.fit = TRUE)
+train1$predictions3 <- train_predict3[[1]]
+(performance3 <- rms::cph(Surv(time_until_answer, answered) ~ predictions3, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.244
+
+survConcordance(Surv(time_until_answer, answered) ~ predictions3, data = train1) # Concordance = 0.6221597
+
+Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions3, data = train1)
+
+#=============================================
+
+# working with strat_model2 (stratified on ampm)
+train_predict4 <- predict(object = strat_model2, type = "risk", se.fit = TRUE)
+train1$predictions4 <- train_predict4[[1]]
+(performance4 <- rms::cph(Surv(time_until_answer, answered) ~ predictions4, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.258
+
+survConcordance(Surv(time_until_answer, answered) ~ predictions4, data = train1) # Concordance = 0.6289692
+
+Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions4, data = train1)
+```
+
+### working with the rms package for cross validation
+
+```{r, echo = FALSE}
+(cox <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
+
 options(scipen=999)
-(cox <- cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
-cox$stats
+(cv <- rms::validate(cox, method = "crossvalidation", B = 10, dxy = TRUE, pr = TRUE))
+
+# for calibrate function, had to add in surv = TRUE and time.inc = a constant (time at which to estimate survival probabilities)
+cox1 <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE, surv=TRUE, time.inc=1.5)
+
+calibrate <- rms::calibrate(cox1, method = "crossvalidation", B = 10, pr = TRUE)
 ```
@@
 
-```{r}
+```{r, echo = FALSE}
+# function to perform cross validation + compute performance metrics
+crossvalidate <- function(train, test) {
 
-#calculating root
+  # building model on training data set
+  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train)
 
-test1 <- x[splitPlan[[1]]$app, ]
-# setting up variables for model 
-test1 <- oshitar::variable_setup(test1)
+  # performance metrics for training data 
+  train[["predictions"]] <- predict(model, type = "risk")
+  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
+  train_metrics <- data.frame(HR = exp(metric$coefficients), 
+                              LR = round(metric$stats[3],2), 
+                              pval = round(metric$stats[5],2), 
+                              R2 = round(metric$stats[8],2), 
+                              Dxy = round(metric$stats[9],2), 
+                              AIC = stats::AIC(metric, k = 2), 
+                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
 
-test_predict <- predict(object = final, newdata = test1, type = "risk", se.fit = TRUE)
-test1$predictions <- test_predict[[1]]
+  # predicting on test data
+  test[["predictions"]] <- predict(model, newdata = test, type = "risk")
 
-metric <- coxph(Surv(time_until_answer, answered) ~ predictions, data = test1)
-summary(metric)
-AIC(metric, k = 2)
+  # computing performance metrics 
+  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
+  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
+                             LR = round(metric1$stats[3],2), 
+                             pval = round(metric1$stats[5],2), 
+                             R2 = round(metric1$stats[8],2), 
+                             Dxy = round(metric1$stats[9],2), 
+                             AIC = stats::AIC(metric1, k = 2), 
+                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
+
+  # returns data frame with train/test metrics 
+  statistics <- rbind(train_metrics, test_metrics)
+  rownames(statistics) <- c("Training Data", "Test Data")
+  return(statistics) 
+}
+
+#=============================================
+test1 <- oshitar::variable_setup(x[splitPlan[[1]]$app, ])
+(iteration1 <- crossvalidate(train1, test1))
+
+#=============================================
+train2 <- oshitar::variable_setup(x[splitPlan[[2]]$train, ])
+test2 <- oshitar::variable_setup(x[splitPlan[[2]]$app, ])
+(iteration2 <- crossvalidate(train2, test2))
+
+#=============================================
+train3 <- oshitar::variable_setup(x[splitPlan[[3]]$train, ])
+test3 <- oshitar::variable_setup(x[splitPlan[[3]]$app, ])
+test3$num_freq_tags <- as.character(test3$num_freq_tags)
+test3$num_freq_tags[test3$num_freq_tags == "4"] <- "3"
+(iteration3 <- crossvalidate(train3, test3))
+# make this more reproducible!!! rule: if a factors level has less than 3 observations in it, merge it with the nearest level
+
+#=============================================
+train4 <- oshitar::variable_setup(x[splitPlan[[4]]$train, ])
+test4 <- oshitar::variable_setup(x[splitPlan[[4]]$app, ])
+(iteration4 <- crossvalidate(train4, test4))
+
+#=============================================
+train5 <- oshitar::variable_setup(x[splitPlan[[5]]$train, ])
+test5 <- oshitar::variable_setup(x[splitPlan[[5]]$app, ])
+(iteration5 <- crossvalidate(train5, test5))
+
+iteration1
+iteration2
+iteration3
+iteration4
+iteration5
 ```
 
-### working with the rms package for cross validation
+# Fitting model to the full data set
+
+```{r, echo = FALSE}
+x <- oshitar::variable_setup(x)
+
+final <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = x)
+summary(final)
+AIC(final, k = 2) # 83051.61
+
+x$predictions <- predict(final, type = "risk")
+(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x))
+AIC(performance, k = 2)
+
+# extracting predicted survival probabilities
+prob <- pec::predictSurvProb(final, newdata = x, times = c(0.5, 1, 1.5, 2, quantile(x$time_until_answer)))
+
+#==================================================================================================
+# function to take in a data set, fit the model, output performance metrics, and allow you to specify times to predict survival probabilities
+
+predict_survprob <- function(dataset, times) {
+  # fitting the model 
+  data <- oshitar::variable_setup(dataset)
+  model <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = data)
+
+  # performance metrics
+  data[["predictions"]] <- predict(model, type = "risk")
+  p <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = data)
+  metrics <- data.frame(HR = exp(p$coefficients), 
+                             LR = round(p$stats[3],2), 
+                             pval = round(p$stats[5],2), 
+                             R2 = round(p$stats[8],2), 
+                             Dxy = round(p$stats[9],2), 
+                             AIC = stats::AIC(p, k = 2), 
+                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = data)$concordance)
+
+  # calculating predicted survival probabilities
+  probs <- pec::predictSurvProb(model, newdata = data, times)
+
+  # returns a list containing performance metrics, and data frame with predicted survival probabilities
+  output <- list(metrics, probs)
+  return(output)
+}
+
+```
 
 ```{r}
-library(rms)
-(cox <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
+b <- oshitar::variable_setup(b)
+counts <- b %>% 
+  select(new_user, weekday, num_freq_tags) %>%
+  purrr::map(~table(.))
 
-(cv <- validate(cox, method = "crossvalidation", B = 10, dxy = TRUE, pr = TRUE))
+# if a factor has less than 3 questions in a level, merge it with the nearest level 
+for (i in length(counts)) {
+  if (which(unname(counts[[i]]) < 3) != integer(0)) {
+    names(which(counts[[i]] < 3)) 
+  }
+}
+
+class(counts[[1]])
+which(unname(counts[[1]]) < 1)
 ```

### 2017-08-17 Hours.Rmd
used stepAIc with backwards/forward sepwise selection, added interaction terms, recoded category variable
plotted residuals, updated hours
cross validation, updated hours
updating hours

@@
 8/10/2017 | 2 | 6:00-8:00PM | Tried to figure out backwards selection function to fit model
+8/11/2017 | 5.5 | 10:30-4:00PM | Researched more model fitting functions, recoded category variable
+8/11/2017 | 2 | 8:00-10:00PM | Plotted residuals + predicted on test data set
+8/15/2017 | 9.5 | 11:00-8:30PM | Cross validation + model fitting 
+8/16/2017 | 5 | 10:30-3:30PM | Wrote function for cross validation 
+8/16/2017 | 2.5 | 7:00-9:30PM | Fit model to full data set, wrote function to take data, fit model, and get predicted survival probabilities
 

### 2017-08-17 model fitting/cross_validation.Rmd
updating hours
deleted chunk

@@
 ```
-
-```{r}
-b <- oshitar::variable_setup(b)
-counts <- b %>% 
-  select(new_user, weekday, num_freq_tags) %>%
-  purrr::map(~table(.))
-
-# if a factor has less than 3 questions in a level, merge it with the nearest level 
-for (i in length(counts)) {
-  if (which(unname(counts[[i]]) < 3) != integer(0)) {
-    names(which(counts[[i]] < 3)) 
-  }
-}
-
-class(counts[[1]])
-which(unname(counts[[1]]) < 1)
-```

### 2017-08-17 literature reviews/literature_reviews.tex
updated lit file

\documentclass[12pt]{article}
\usepackage{natbib}  % used for citations
\usepackage[parfill]{parskip} %used for formatting style of text

% Sets margins to 1 in
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

%-----------------------------------------------------------------------------------
\title{Literature Review of Online Question Forums}
\author{Lisa Oshita}
\date{}
%-----------------------------------------------------------------------------------

\begin{document}

\maketitle

\section{Introduction}

This really cool paper about stackoverflow said something cool \citep{Ponzanelli2014}.

\cite{Ponzanelli2014} said this awesome thing.

\bibliographystyle{ECA_jasa}
\bibliography{questions}

\end{document}

### 2017-08-21 model fitting/cross_validation.Rmd
fitted splines and square root transformations of quantitative variables

@@
 ```{r, echo = FALSE}
+# write a function to set up variables for this training data
+
 train1 <- x[splitPlan[[1]]$train, ]
@@
 AIC(results2, k = 2) # 65277.47
+summary(results2)
 ```
@@
 AIC(model2, k = 2) # 65274.49
-compare_nested(model2, results2)
+oshitar::compare_nested(model2, results2)
 
@@
 AIC(model2_2, k = 2) # 65271.84
-compare_nested(model2_2, results2)
+oshitar::compare_nested(model2_2, results2)
 
@@
 AIC(model_new, k = 2) #64999.87
+summary(model_new)
 
@@
   scale_x_continuous("Question index") + 
-  scale_y_continuous(breaks = seq(-4, 4, by = 0.5))
+  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
+  ggtitle("Deviance Residuals")
 # quite a few questions have a deviance residual of larger than 2.5
@@
 #=============================================
+# working with rms::which.influence to id influential points
+c <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, x = TRUE, y = TRUE, data = train1)
+influence <- rms::which.influence(c)
+rms::show.influence(influence, train1)
+
+#=============================================
 # formal test of PH assumption
+options(scipen=999)
 ph_test <- data.frame(predictors = rownames(cox.zph(model_full)$table), cox.zph(model_full)$table) 
@@
 summary(strat_model3)
+```
+
+### Checking multicolliniearity
+
+```{r, echo = FALSE}
+rms::vif()
 ```
@@
 
-#==================================================================================================
+#==================================================================================
 # function to take in a data set, fit the model, output performance metrics, and allow you to specify times to predict survival probabilities

### 2017-08-21 model fitting/univariate_analysis.Rmd
fitted splines and square root transformations of quantitative variables

@@
 # n_tags
-pvalues <- get_pvalue("n_tags")
+pvalues <- get_pvalue("n_tags", factor = TRUE)
 
@@
 pvalues <- get_pvalue("title_length", factor = FALSE)
+
+# splines
+fit <- coxph(Surv(time_until_answer, answered) ~ pspline(title_length, df = 0, method = "AIC"), data = train1)
+summary(fit) # p=0.2322
 
@@
 pvalues <- get_pvalue("newline_ratio")
+
+ggplot2::ggplot(train1, aes(x = time_until_answer, y = newline_ratio)) + 
+  geom_point()
 ```
@@
 ```
+
+### researching splines
+
+* spline: piecewise m - 1 degree polynomial that is continuous up to its first m - 2 derivatives
+* obtain more flexible curves: increase the degree of spline/add more knots
+* tradeoff: 
+    + few knots/low degree: class of functions may be too restrictive (bias)
+    + many knots/high degree: risk overfitting 
+* spline has m + K degrees of freedom 
+* types of splines
+    + cubic splines (most common)
+* truncated power basis - flawed
+* B-spline basis: much more stable, typically used 
+* Natural cubic splines
+    + polynomial fits tend to be erratic at boundaries of data (even worse for cubic splines)
+    + natural cubic splines fix this by adding 4 constraints that the function is linear beyond the boundaries of the data 
+    + because basis functions are fixed, model fitting and inference are straightforward exentsions to how the model would normally be without splines
+
+```{r, echo = FALSE}
+# fit splines + sqrt/log transformations on title_length, text_length, device_length, avg_tag_length, newline_ratio
+
+# title_length
+fit <- coxph(Surv(time_until_answer, answered) ~ pspline(title_length, df = 0, method = "AIC"), data = train1)
+summary(fit) # p=0.2322
+
+fit1 <- coxph(Surv(time_until_answer, answered) ~ sqrt(title_length), data = train1)
+summary(fit1) # p=0.4874
+
+# text_length
+fit2 <- coxph(Surv(time_until_answer, answered) ~ pspline(text_length, df = 0, method = "AIC"), data = train1)
+summary(fit1) # p=0
+fit3 <- coxph(Surv(time_until_answer, answered) ~ sqrt(text_length), data = train1)
+summary(fit2) # p=0.000000000000000111
+AIC(fit2, k = 2) # 65867.02
+fit4 <- coxph(Surv(time_until_answer, answered) ~ log10(text_length), data = train1)
+summary(fit3) # p=0.000000000000000111
+AIC(fit3, k = 2) # 65862.83
+
+# device_length
+fit5 <- coxph(Surv(time_until_answer, answered) ~ pspline(device_length, df = 0, method = "AIC"), data = train1)
+summary(fit5) # p=0 (original = 0.0065304314223657567)
+fit6 <- coxph(Surv(time_until_answer, answered) ~ sqrt(device_length), data = train1)
+summary(fit6) # p=0.0002291 (lower p-value than without sqrt)
+
+# newline_ratio
+fit7 <- coxph(Surv(time_until_answer, answered) ~ pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
+summary(fit7) # p=0.00000000008754 (original = 0.0000001398791481533)
+
+fit8 <- coxph(Surv(time_until_answer, answered) ~ sqrt(newline_ratio), data = train1)
+summary(fit8) # p=0.00000000001149
+AIC(fit8, k = 2) # 65890.28
+
+# avg_tag_length
+fit9 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+summary(fit9) # p=0.009088 (original = 0.05)
+fit10 <- coxph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_length), data = train1)
+summary(fit10) # p=0.1278
+
+# avg_tag_score
+fit10 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_score, df = 0, method = "AIC"), data = train1)
+summary(fit10) # p=0.0000000002831
+fit11 <- coxph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = train1)
+summary(fit11) # p=0.00000000003211 (original = 0.0000000166232489995)
+```

### 2017-08-22 model fitting/univariate_analysis.Rmd
univariate analysis for quadratic/cubic terms, square root transformations, splines

--- 2017-08-15 model fitting/univariate_analysis.Rmd
@@
   summary <- summary(coxmodel)
-  print(summary)
   df <- data.frame(variable = variable, pvalue = unname(summary$logtest[[3]]))
@@
 
+# Univariate analyses (select variables with p-value < 0.01)
 #===================================================================
-# Univariate analyses (select variables with p-value < 0.01)
 # category 
-train1$category <- as.character(train1$category)
-train1$category[is.na(train1$category)] <- "Other"
-train1$category <- as.factor(train1$category)
 pvalues <- get_pvalue("category")
+#===================================================================
+# new_category
+pvalues <- get_pvalue("new_category")
 #===================================================================
@@
 # new_user
-pvalues <- get_pvalue("new_user", factor = TRUE)
+pvalues <- get_pvalue("new_user")
 
@@
 # weekday
-train1$datetime <- as.POSIXct(train1$post_date,origin="1970-01-01")
-train1$weekday <- factor(weekdays(train1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
 pvalues <- get_pvalue("weekday")
@@
 #===================================================================
-# is_weekend
-train1$is_weekend <- FALSE
-train1$is_weekend[train1$weekday == "Saturday" | train1$weekday == "Sunday"] <- TRUE
-pvalues <- get_pvalue("is_weekend")
-
-#===================================================================
 # hour of the day
-train1$hour <- as.numeric(format(train1$datetime,"%H"))
 pvalues <- get_pvalue("hour", factor = TRUE)
@@
 # morning/noon/evening/night?
-train1$ampm <- "Night"
-train1$ampm[train1$hour >= 5 & train1$hour < 12] <- "Morning"
-train1$ampm[train1$hour >= 12 & train1$hour < 17] <- "Afternoon" #noon - 5pm
-train1$ampm[train1$hour >= 17 & train1$hour < 20] <- "Evening" #5pm - 8pm
 pvalues <- get_pvalue("ampm")
@@
 # title length
-train1$title_length <- str_length(train1$title)
-pvalues <- get_pvalue("title_length", factor = FALSE)
+pvalues <- get_pvalue("title_length")
 
@@
 # text length
-train1$text_length <- str_length(train1$text)
 pvalues <- get_pvalue("text_length")
@@
 # device name length
-train1$device_length <- str_length(train1$device)
 pvalues <- get_pvalue("device_length")
@@
 # length of sentence until first punctuation mark
-train1$length <- str_locate(train1$text, pattern = "[.|?|!]")[,1]
-q <- stats::quantile(train1$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
-train1$text_till_punct <- "none"
-train1$text_till_punct[train1$length <= q[3]] <- "short"
-train1$text_till_punct[train1$length >= q[3] & train1$length <= q[4]] <- "medium"
-train1$text_till_punct[train1$length >= q[4]] <- "long"
 pvalues <- get_pvalue("text_till_punct")
@@
 # if text contains any end punctuation
-train1$text_contain_punct <- str_detect(train1$text, pattern = "[.|?|!]")
 pvalues <- get_pvalue("text_contain_punct")
@@
 #===================================================================
-# if the text ends in a punctuation
-train1$text_end_punct <- str_detect(train1$text, pattern = "[.|?|!]$")
-pvalues <- get_pvalue("text_end_punct")
-
-#===================================================================
 # if the title ends with a question mark
-train1$title_questionmark <- str_detect(train1$title, pattern = QUESTION %R% END)
 pvalues <- get_pvalue("title_questionmark")
@@
 # if title begins with "wh"
-train1$title_beginwh <- str_detect(str_to_lower(train1$title), pattern = "^wh")
 pvalues <- get_pvalue("title_beginwh")
@@
 # if text is in all lower case
-train1$cleaned <- str_replace_all(train1$text, " ", "")
-train1$cleaned <- str_replace_all(train1$cleaned, "[[:punct:]]|[[:digit:]]", "")
-train1$text_all_lower <- str_detect(train1$cleaned, pattern = "^[[:lower:]]+$")
 pvalues <- get_pvalue("text_all_lower")
@@
 # prior_effort
-prior_terms <- c("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted")
-train1$prior_effort <- str_detect(str_to_lower(train1$text), pattern = or1(prior_terms))
 pvalues <- get_pvalue("prior_effort")
@@
 #===================================================================
-# num_prior_effort
-train1$num_prior_effort <- str_count(str_to_lower(train1$text), pattern = or1(prior_terms))
-pvalues <- get_pvalue("num_prior_effort")
-
-#===================================================================
 # expressing gratitude 
-gratitude_terms <- c("please", "thank you", "thanks", "thankful", "appreciate", "appreciated", "grateful")
-train1$gratitude <- str_detect(str_to_lower(train1$text), pattern = or1(gratitude_terms))
 pvalues <- get_pvalue("gratitude")
@@
 # greeting
-greeting_terms <- c("hey", "hello", "greetings", "hi")
-train1$greeting <- str_detect(str_to_lower(train1$text), pattern = START %R% or1(greeting_terms))
 pvalues <- get_pvalue("greeting")
@@
 # update the question?
-train1$update <- str_detect(train1$text, pattern = "===")
 pvalues <- get_pvalue("update")
@@
 # newline ratio to length of text
-train1$newline_ratio <- str_count(train1$text, pattern = "\n")/str_length(train1$text)
 pvalues <- get_pvalue("newline_ratio")
@@
 # avg_tag_length
-split_tags <- str_split(train1$tags, ", ", simplify = TRUE)
-train1$avg_tag_length <- NA
-not_na <- which(train1$tags != "")
-for (i in not_na) {
-  total_char <- sum(str_length(as.vector(split_tags[i,])))
-  total_tags <- sum(as.vector(split_tags[i,]) != "")
-  train1$avg_tag_length[i] <- total_char / total_tags
-}
 pvalues <- get_pvalue("avg_tag_length")
@@
 #===================================================================
-# maximum number of words for a question's tags
-train1$max_tagwords <- rep(0, nrow(train1))
-for (i in which(train1$n_tags != 0)) {
-  tags <- as.vector(split_tags[i,])
-  train1$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
-}
-pvalues <- get_pvalue("max_tagwords")
-
-#===================================================================
-# frequent tags
-tag_vector <- as.vector(split_tags)
-tag_vector <- tag_vector[which(tag_vector != "")]
-unique_tags <- unique(tag_vector)
-
-tag_freq <- data.frame(tag = unique_tags, percent = purrr::map_dbl(unique_tags, ~mean(rowSums(split_tags == .) > 0)))
-tag_freq <- tag_freq %>%
-              arrange(desc(percent))
-
-#creating average frequency score variable
-train1$tag1 <- split_tags[,1]
-train1$tag2 <- split_tags[,2]
-train1$tag3 <- split_tags[,3]
-train1$tag4 <- split_tags[,4]
-
-assign_score <- function(data, variable) {
-  score <- rep(0, nrow(data))
-  notempty <- which(data[[variable]] != "")
-  for (i in notempty) {
-    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
-  }
-  return(score)
-}
-train1$score1 <- assign_score(train1, "tag1")
-train1$score2 <- assign_score(train1, "tag2")
-train1$score3 <- assign_score(train1, "tag3")
-train1$score4 <- assign_score(train1, "tag4")
-train1$avg_tag_score <- (train1$score1 + train1$score2 + train1$score3 + train1$score4)/as.numeric(train1$n_tags)
-train1$avg_tag_score[is.nan(train1$avg_tag_score)] <- 0
-
+# avg_tag_score
 pvalues <- get_pvalue("avg_tag_score")
@@
 #===================================================================
-# if question contains "frequent" tag
-percentile80 <- quantile(train1$avg_tag_score, probs = 0.80)
-
-train1$frequent_tag <- FALSE
-train1$frequent_tag[train1$avg_tag_score >= percentile80] <- TRUE
-
-pvalues <- get_pvalue("frequent_tag")
-
-#===================================================================
 # number of "frequent" tags a question contains
-threshold <- 0.005
-num_pop <- function(var, threshold) {
-  num_pop <- rep(0, nrow(train1))
-  num_pop[train1[[var]] >= threshold] <- 1
-  return(num_pop)
-}
-numpop1 <- num_pop("score1", threshold)
-numpop2 <- num_pop("score2", threshold)
-numpop3 <- num_pop("score3", threshold)
-numpop4 <- num_pop("score4", threshold)
-train1$num_freq_tags <- numpop1 + numpop2 + numpop3 + numpop4
-
 pvalues <- get_pvalue("num_freq_tags")
@@
 #frequent terms in unanswered/answered questions
-answered <- train1 %>%
-  tibble::as_tibble() %>% 
-  filter(answered == 1)
-
-unanswered <- train1 %>%
-  tibble::as_tibble() %>% 
-  filter(answered == 0)
-
-terms_a <- oshitar::get_freq_terms(answered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
-colnames(terms_a)[2] <- "frequency_a"
-
-terms_u <- oshitar::get_freq_terms(unanswered$title, stopwords = c("can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
-terms_u$prop_in_unanswered <- terms_u$frequency/nrow(terms_u)
-colnames(terms_u)[2] <- "frequency_u"
-
-combined <- dplyr::full_join(terms_a, terms_u, by = "word")
-combined$ratio <- combined$prop_in_answered / combined$prop_in_unanswered
-
-p_threshold <- 0.01
-ratio_threshold <- 1
-
-freq_terms_u <- combined %>%
-                  filter(prop_in_unanswered > p_threshold) %>%
-                  filter(ratio < ratio_threshold)
-freq_terms_a <- combined %>%
-                  filter(prop_in_answered > p_threshold) %>%
-                  filter(ratio > ratio_threshold)
-
-train1$contain_unanswered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_u$word))
-train1$contain_answered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_a$word))
-
 pvalues <- get_pvalue("contain_unanswered")
 pvalues <- get_pvalue("contain_answered")
+```
+
+### researching splines + quadratic terms + square root transformations
+
+* spline: piecewise m - 1 degree polynomial that is continuous up to its first m - 2 derivatives
+* obtain more flexible curves: increase the degree of spline/add more knots
+* tradeoff: 
+    + few knots/low degree: class of functions may be too restrictive (bias)
+    + many knots/high degree: risk overfitting 
+* spline has m + K degrees of freedom 
+* types of splines
+    + cubic splines (most common)
+* truncated power basis - flawed
+* B-spline basis: much more stable, typically used 
+* Natural cubic splines
+    + polynomial fits tend to be erratic at boundaries of data (even worse for cubic splines)
+    + natural cubic splines fix this by adding 4 constraints that the function is linear beyond the boundaries of the data 
+    + because basis functions are fixed, model fitting and inference are straightforward exentsions to how the model would normally be without splines 
+* **use pspline and penalized spline smoothing method with AIC criteria**
+
+```{r, echo = FALSE}
+# fit splines + sqrt/log transformations on title_length, text_length, device_length, avg_tag_length, newline_ratio
+
+# new function to add p-values from these fits to pvalue data frame
+get_pvalue_new <- function(variable, fit) {
+  summary <- summary(fit)
+  df <- data.frame(variable = variable, pvalue = unname(summary$logtest[[3]]))
+  pvalues <- rbind(pvalues, df)
+  return(pvalues)
+}
+
+#===================================================================
+
+# title_length
+spline_title <- coxph(Surv(time_until_answer, answered) ~ pspline(title_length, df = 0, method = "AIC"), data = train1)
+pvalues <- get_pvalue_new("title_length_spline", fit = spline_title)
+
+sqrt_title <- coxph(Surv(time_until_answer, answered) ~ sqrt(title_length), data = train1)
+pvalues <- get_pvalue_new("title_length_sqrt", fit = sqrt_title)
+
+# quadratic/cubic terms
+
+title2 <- coxph(Surv(time_until_answer, answered) ~ title_length + I(title_length^2), data = train1)
+pvalues <- get_pvalue_new("quad_title", fit = title2)
+
+title3 <- coxph(Surv(time_until_answer, answered) ~ title_length + I(title_length^2) + I(title_length^3), data = train1)
+pvalues <- get_pvalue_new("cubic_title", fit = title3)
+
+#===================================================================
+
+# text_length
+spline_text <- coxph(Surv(time_until_answer, answered) ~ pspline(text_length, df = 0, method = "AIC"), data = train1)
+pvalues <- get_pvalue_new("text_length_spline", fit = spline_text)
+
+sqrt_text <- coxph(Surv(time_until_answer, answered) ~ sqrt(text_length), data = train1)
+pvalues <- get_pvalue_new("text_length_sqrt", fit = sqrt_text)
+
+logtext <- coxph(Surv(time_until_answer, answered) ~ log10(text_length), data = train1)
+pvalues <- get_pvalue_new("text_length_log10", fit = logtext)
+
+# quadratic/cubic terms
+
+text2 <- coxph(Surv(time_until_answer, answered) ~ text_length + I(text_length^2), data = train1)
+pvalues <- get_pvalue_new("quad_text", fit = text2)
+
+text3 <- coxph(Surv(time_until_answer, answered) ~ text_length + I(text_length^2) + I(text_length^3), data = train1)
+pvalues <- get_pvalue_new("cubic_text", fit = text3)
+
+#===================================================================
+
+# device_length
+spline_dev <- coxph(Surv(time_until_answer, answered) ~ pspline(device_length, df = 0, method = "AIC"), data = train1)
+pvalues <- get_pvalue_new("device_length_spline", fit = spline_dev)
+
+sqrt_dev <- coxph(Surv(time_until_answer, answered) ~ sqrt(device_length), data = train1)
+pvalues <- get_pvalue_new("device_length_sqrt", fit = sqrt_dev)
+
+# quadratic/cubic terms
+
+dev2 <- coxph(Surv(time_until_answer, answered) ~ device_length + I(device_length^2), data = train1)
+pvalues <- get_pvalue_new("quad_dev", fit = dev2)
+
+dev3 <- coxph(Surv(time_until_answer, answered) ~ device_length + I(device_length^2) + I(device_length^3), data = train1)
+pvalues <- get_pvalue_new("cubic_dev", fit = dev3)
+
+#===================================================================
+
+# newline_ratio
+fit7 <- coxph(Surv(time_until_answer, answered) ~ pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
+pvalues <- get_pvalue_new("newline_ratio_spline", fit = fit7)
+
+fit8 <- coxph(Surv(time_until_answer, answered) ~ sqrt(newline_ratio), data = train1)
+pvalues <- get_pvalue_new("newline_ratio_sqrt", fit = fit8)
+
+# quadratic/cubic terms
+
+newline2 <- coxph(Surv(time_until_answer, answered) ~ newline_ratio + I(newline_ratio^2), data = train1)
+pvalues <- get_pvalue_new("quad_newline", fit = newline2)
+
+newline3 <- coxph(Surv(time_until_answer, answered) ~ newline_ratio + I(newline_ratio^2) + I(newline_ratio^3), data = train1)
+pvalues <- get_pvalue_new("cubic_newline", fit = newline3)
+
+#===================================================================
+
+# avg_tag_length
+fit9 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+pvalues <- get_pvalue_new("avg_tag_length_spline", fit = fit9)
+
+fit10 <- coxph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_length), data = train1)
+pvalues <- get_pvalue_new("avg_tag_length_sqrt", fit = fit10)
+
+# quadratic/cubic terms
+
+tag2 <- coxph(Surv(time_until_answer, answered) ~ avg_tag_length + I(avg_tag_length^2), data = train1)
+pvalues <- get_pvalue_new("quad_tag", fit = tag2)
+
+tag3 <- coxph(Surv(time_until_answer, answered) ~ avg_tag_length + I(avg_tag_length^2) + I(avg_tag_length^3), data = train1)
+pvalues <- get_pvalue_new("cubic_tag", fit = tag3)
+
+#===================================================================
+
+# avg_tag_score
+fit11 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_score, df = 0, method = "AIC"), data = train1)
+pvalues <- get_pvalue_new("avg_tag_score_spline", fit = fit11)
+
+fit12 <- coxph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = train1)
+pvalues <- get_pvalue_new("avg_tag_score_sqrt", fit = fit12)
+
+# quadratic/cubic terms
+
+score2 <- coxph(Surv(time_until_answer, answered) ~ avg_tag_score + I(avg_tag_score^2), data = train1)
+pvalues <- get_pvalue_new("quad_score", fit = score2)
+
+score3 <- coxph(Surv(time_until_answer, answered) ~ avg_tag_score + I(avg_tag_score^2) + I(avg_tag_score^3), data = train1)
+pvalues <- get_pvalue_new("cubic_score", fit = score3)
 ```

### 2017-08-22 model fitting/cross_validation.Rmd
more work with splines + variable selection

@@
 ```{r, echo = FALSE}
-# write a function to set up variables for this training data
-
 train1 <- x[splitPlan[[1]]$train, ]
@@
 
+### splines/square root transformed variables
+
+```{r, echo = FALSE}
+fit3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday, data = train1)
+
+fit4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + sqrt(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday, data = train1)
+model4 <- MASS::stepAIC(fit4, direction = "both", k = 2)
+
+#AIC=64986.23
+model3 <- MASS::stepAIC(fit3, direction = "both", k = 2)
+
+resultsa <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday, data = train1)
+summary(resultsa)
+AIC(resultsa, k = 2) # 64965.19
+
+# adding in spline on device_length
+resultsb <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC"), data = train1)
+summary(resultsb)
+AIC(resultsb, k = 2) # 64908.37
+
+# adding in spline on
+
+results3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
+    pspline(device_length, df = 0, method = "AIC") + contain_unanswered + 
+    title_questionmark + sqrt(avg_tag_score) + contain_answered + 
+    text_all_lower + update + num_prior_effort + ampm + weekday + 
+    pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+summary(results3)
+AIC(results3, k = 2) # 64891.93
+
+results4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + pspline(device_length, df = 0, method = "AIC") + contain_unanswered + title_questionmark + sqrt(avg_tag_score) + contain_answered + text_all_lower + update + prior_effort + ampm + weekday + sqrt(newline_ratio) + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+summary(results4)
+
+AIC(results4, k = 2) # 64888.83
+summary(results4)
+
+```
+
 ### Adding interaction terms
@@
 AIC(model_i, k = 2) # 65263.35
+summary(model_i)
 ```

### 2017-08-22 model fitting/univariate_analysis.Rmd
reformatted the file

@@
 #===================================================================
-# category 
 pvalues <- get_pvalue("category")
-#===================================================================
-# new_category
 pvalues <- get_pvalue("new_category")
-#===================================================================
-# n_images
 pvalues <- get_pvalue("n_images")
@@
 
-#===================================================================
-# n_tags
 pvalues <- get_pvalue("n_tags", factor = TRUE)
-
-#===================================================================
-# new_user
 pvalues <- get_pvalue("new_user")
-
-#===================================================================
-# weekday
 pvalues <- get_pvalue("weekday")
-
-#===================================================================
-# hour of the day
 pvalues <- get_pvalue("hour", factor = TRUE)
-
-#===================================================================
-# morning/noon/evening/night?
 pvalues <- get_pvalue("ampm")
-
-#===================================================================
-# title length
 pvalues <- get_pvalue("title_length")
-
-#===================================================================
-# text length
 pvalues <- get_pvalue("text_length")
-
-#===================================================================
-# device name length
 pvalues <- get_pvalue("device_length")
-
-#===================================================================
-# length of sentence until first punctuation mark
 pvalues <- get_pvalue("text_till_punct")
-
-#===================================================================
-# if text contains any end punctuation
 pvalues <- get_pvalue("text_contain_punct")
-
-#===================================================================
-# if the title ends with a question mark
 pvalues <- get_pvalue("title_questionmark")
-
-#===================================================================
-# if title begins with "wh"
 pvalues <- get_pvalue("title_beginwh")
 
-#===================================================================
 # if first letter of title is capitalized 
@@
 
-#===================================================================
 # if first letter of text is capitalized
@@
 
-#===================================================================
-# if text is in all lower case
 pvalues <- get_pvalue("text_all_lower")
-
-#===================================================================
-# prior_effort
 pvalues <- get_pvalue("prior_effort")
-
-#===================================================================
-# expressing gratitude 
 pvalues <- get_pvalue("gratitude")
-
-#===================================================================
-# greeting
 pvalues <- get_pvalue("greeting")
-
-#===================================================================
-# update the question?
 pvalues <- get_pvalue("update")
-
-#===================================================================
-# newline ratio to length of text
 pvalues <- get_pvalue("newline_ratio")
-```
-
-```{r, tag based and frequent term variables, include = FALSE}
-# tag-based variables 
-#===================================================================
-# avg_tag_length
 pvalues <- get_pvalue("avg_tag_length")
-
-#===================================================================
-# avg_tag_score
 pvalues <- get_pvalue("avg_tag_score")
-
-#===================================================================
-# number of "frequent" tags a question contains
 pvalues <- get_pvalue("num_freq_tags")
-
-#==================================================================================
-#frequent terms in unanswered/answered questions
 pvalues <- get_pvalue("contain_unanswered")
@@
 
-### researching splines + quadratic terms + square root transformations
+### splines + quadratic/cubic terms + square root/log transformations
 
-* spline: piecewise m - 1 degree polynomial that is continuous up to its first m - 2 derivatives
-* obtain more flexible curves: increase the degree of spline/add more knots
-* tradeoff: 
-    + few knots/low degree: class of functions may be too restrictive (bias)
-    + many knots/high degree: risk overfitting 
-* spline has m + K degrees of freedom 
-* types of splines
-    + cubic splines (most common)
-* truncated power basis - flawed
-* B-spline basis: much more stable, typically used 
-* Natural cubic splines
-    + polynomial fits tend to be erratic at boundaries of data (even worse for cubic splines)
-    + natural cubic splines fix this by adding 4 constraints that the function is linear beyond the boundaries of the data 
-    + because basis functions are fixed, model fitting and inference are straightforward exentsions to how the model would normally be without splines 
 * **use pspline and penalized spline smoothing method with AIC criteria**
@@
 ```{r, echo = FALSE}
-# fit splines + sqrt/log transformations on title_length, text_length, device_length, avg_tag_length, newline_ratio
-
 # new function to add p-values from these fits to pvalue data frame

### 2017-08-23 model fitting/cross_validation.Rmd
added splines with psplines in coxph and rcs in cph fits

--- 2017-08-21 model fitting/cross_validation.Rmd
@@
 str(splitPlan)
+
+train1 <- x[splitPlan[[1]]$train, ]
 ```
@@
 ```{r, echo = FALSE}
-# write a function to set up variables for this training data
+fit <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday, data = train1)
 
-train1 <- x[splitPlan[[1]]$train, ]
+model <- MASS::stepAIC(fit, direction = "both", k = 2)
+#results of stepAIC (but keeping contain_answered)
+results <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday, data = train1)
+summary(results)
+AIC(results, k = 2) # 64965.89
 
-first <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + contain_unanswered + title_questionmark + text_length + text_contain_punct + as.factor(num_freq_tags) + as.factor(n_tags) + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1)
-AIC(first, k = 2) #65294.56
+# adding in spline on device_length
+model_spline <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC"), data = train1)
+AIC(model_spline, k = 2) # 64907.21
 
-# backwards step-wise selection with selectCox function
-# converting to factors since function doesn't work with as.factor()
-train1$new_user <- as.factor(train1$new_user)
-train1$num_freq_tags <- as.factor(train1$num_freq_tags)
-train1$n_tags <- as.factor(train1$n_tags)
+# adding in spline on text_length
+model_spline1 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC"), data = train1)
+AIC(model_spline1, k = 2) # 64894.01
 
-model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + text_length + text_contain_punct + num_freq_tags + n_tags + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1, rule = "aic")
-# results
-results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + contain_answered + text_all_lower + update + ampm + device_length, data = train1)
-AIC(results1, k = 2) #65285.49
-summary(results1)
+# adding in spline on avg_tag_length
+model_spline2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+summary(model_spline2)
+AIC(model_spline2, k = 2) # 64848.5
 
-# backward/forward step-wise selection with stepAIC function from MASS package
-model2 <- MASS::stepAIC(first, direction = "both", k = 2)
-# results
-results2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
-AIC(results2, k = 2) # 65277.47
-summary(results2)
+anova(model_spline2)
+
+#=====================================================
+# adding interaction between title_questionmark + title_beginwh (probably leave out)
+# probably leave interactions out, don't do much for the model
+
+resultse <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + title_questionmark + title_beginwh + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_questionmark*title_beginwh, data = train1)
+summary(resultse)
+AIC(resultse, k = 2) # 64843
 ```
 
-### Adding interaction terms
+# using rcs (restricted cubic spline) in rms package 
+* fit knots at quantiles of the predictor 
+* recommended in Regression Modeling Strategies to have 5 knots for large data sets 
+```{r}
+unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.725, 0.95)))
 
-* working with model from backward/forward stepwise selection
-
-```{r, echo = FALSE}
-# adding title_questionmark*title_beginwh
-model2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
-AIC(model2, k = 2) # 65274.49
-oshitar::compare_nested(model2, results2)
-
-# adding new_user*update
-model2_1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*update, data = train1)
-AIC(model2_1, k = 2) # 65272.55
-compare_nested(model2_1, results2)
-
-# adding new_user*ampm 
-model2_2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
-AIC(model2_2, k = 2) # 65271.84
-oshitar::compare_nested(model2_2, results2)
-
-# all signficant interaction terms 
-model_i <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
-AIC(model_i, k = 2) # 65263.35
-```
-
-##### recoding category variable
-
-* group all apple products together
-    + use str_detect to search for ipad, ipod, apple watch 
-    + group with iPhones and Macs 
-* recode left over Phones to Android/Other Phone
-* group household + appliance as "Home"
-* group car and truck + vehicle as "Vehicle"
-* set a rule: any category with less than 100 questions gets grouped with "Other"
-
-```{r, echo = FALSE}
-train1$new_category <- as.character(train1$category)
-
-# grouping apple products together
-apple_terms <- c("apple", "ipod", "ipad")
-train1$apple <- str_detect(str_to_lower(train1$device), pattern = START %R% or1(apple_terms) %R% SPC)
-train1$new_category[train1$apple == TRUE | train1$subcategory == "iPhone" | train1$category == "Mac"] <- "Apple Product"
-
-# renaming left over phones 
-train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"
-
-# merge household and appliance into "Home"
-train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"
-
-# merging Car and Truck with Vehicle 
-train1$new_category[train1$new_category == "Car and Truck" | train1$new_category == "Vehicle"] <- "Vehicle"
-
-# if there are less than 100 questions in a category, group them with Other
-counts <- train1 %>%
-  group_by(new_category) %>%
-  summarise(n = n())
-for (i in which(counts$n <= 100)) {
-  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
-}
-table(train1$new_category)
-
-#===================================================
-
-model_new <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
-AIC(model_new, k = 2) #64999.87
-summary(model_new)
-
-#new_cateogry*new_user
-model_new1 <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_category*new_user, data = train1)
-AIC(model_new1, k = 2) # 64994.49
-compare_nested(model_new1, model_new)
-
-# model with ALL interactions
-# model with new_category
-model_full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1)
-AIC(model_full, k = 2) # 64978.87
-summary(model_full)
+library(rms)
+model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
+AIC(model_spline, k = 2) # 64907.21
+model
 ```
@@
 * **figure out how to identify certain points on ggplots**
-* statified on new_category, AIC dropped drastically. But this means that I can't compare the different groups in new_category 
-    + Concordance statistic and rsquare dropped
 
@@
 
-### Checking multicolliniearity
-
-```{r, echo = FALSE}
-rms::vif()
-```
-
 ### Performance metric on training data set
 
-* model not stratified on new_category has higher R2, higher Dxy than model stratified on new_category
 * survConcordance: 
@@
 The final concondance is (agree + tied/2)/(agree + disagree + tied)
-    +
 
 ```{r}
-# working with final model (stratified on new_category) 
-train_predict <- predict(object = strat_model, type = "risk", se.fit = TRUE)
-train1$predictions <- train_predict[[1]]
+# working with model_spline2 (model with all splines)
+train1$predictions <- predict(object = model_spline2, type = "risk") # should I predict "lp" instead of "risk"
+(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
 
-(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.115
-AIC(performance, k = 2) # 65781.26
-
-survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train1) # Concordance = 0.5573537
-
+survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train1) # Concordance = 0.6382697
 Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions, data = train1)
 
-#=============================================
-
-# working with full_model (not stratified on new_category)
-train_predict2 <- predict(object = model_full, type = "risk", se.fit = TRUE)
-train1$predictions2 <- train_predict2[[1]]
-(performance2 <- rms::cph(Surv(time_until_answer, answered) ~ predictions2, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.270
-
-survConcordance(Surv(time_until_answer, answered) ~ predictions2, data = train1) # Concordance = 0.634903
-
-Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions2, outx = TRUE, data = train1)
-
-#=============================================
-
-# working with strat_model1 (stratified on new_user)
-train_predict3 <- predict(object = strat_model1, type = "risk", se.fit = TRUE)
-train1$predictions3 <- train_predict3[[1]]
-(performance3 <- rms::cph(Surv(time_until_answer, answered) ~ predictions3, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.244
-
-survConcordance(Surv(time_until_answer, answered) ~ predictions3, data = train1) # Concordance = 0.6221597
-
-Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions3, data = train1)
-
-#=============================================
-
-# working with strat_model2 (stratified on ampm)
-train_predict4 <- predict(object = strat_model2, type = "risk", se.fit = TRUE)
-train1$predictions4 <- train_predict4[[1]]
-(performance4 <- rms::cph(Surv(time_until_answer, answered) ~ predictions4, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.258
-
-survConcordance(Surv(time_until_answer, answered) ~ predictions4, data = train1) # Concordance = 0.6289692
-
-Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions4, data = train1)
-```
-
-### working with the rms package for cross validation
-
-```{r, echo = FALSE}
-(cox <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
-
-options(scipen=999)
-(cv <- rms::validate(cox, method = "crossvalidation", B = 10, dxy = TRUE, pr = TRUE))
-
-# for calibrate function, had to add in surv = TRUE and time.inc = a constant (time at which to estimate survival probabilities)
-cox1 <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE, surv=TRUE, time.inc=1.5)
-
-calibrate <- rms::calibrate(cox1, method = "crossvalidation", B = 10, pr = TRUE)
 ```
@@
   # building model on training data set
-  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train)
+  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train)
 
@@
                               pval = round(metric$stats[5],2), 
-                              R2 = round(metric$stats[8],2), 
                               Dxy = round(metric$stats[9],2), 
@@
                              pval = round(metric1$stats[5],2), 
-                             R2 = round(metric1$stats[8],2), 
                              Dxy = round(metric1$stats[9],2), 
@@
 #=============================================
-test1 <- oshitar::variable_setup(x[splitPlan[[1]]$app, ])
-(iteration1 <- crossvalidate(train1, test1))
+test1 <- x[splitPlan[[1]]$app, ]
+iteration1 <- crossvalidate(train1, test1)
 
 #=============================================
-train2 <- oshitar::variable_setup(x[splitPlan[[2]]$train, ])
-test2 <- oshitar::variable_setup(x[splitPlan[[2]]$app, ])
-(iteration2 <- crossvalidate(train2, test2))
+train2 <- x[splitPlan[[2]]$train, ]
+test2 <- x[splitPlan[[2]]$app, ]
+iteration2 <- crossvalidate(train2, test2)
 
 #=============================================
-train3 <- oshitar::variable_setup(x[splitPlan[[3]]$train, ])
-test3 <- oshitar::variable_setup(x[splitPlan[[3]]$app, ])
-test3$num_freq_tags <- as.character(test3$num_freq_tags)
-test3$num_freq_tags[test3$num_freq_tags == "4"] <- "3"
-(iteration3 <- crossvalidate(train3, test3))
-# make this more reproducible!!! rule: if a factors level has less than 3 observations in it, merge it with the nearest level
+train3 <- x[splitPlan[[3]]$train, ]
+test3 <- x[splitPlan[[3]]$app, ]
+iteration3 <- crossvalidate(train3, test3)
 
 #=============================================
-train4 <- oshitar::variable_setup(x[splitPlan[[4]]$train, ])
-test4 <- oshitar::variable_setup(x[splitPlan[[4]]$app, ])
-(iteration4 <- crossvalidate(train4, test4))
+train4 <- x[splitPlan[[4]]$train, ]
+test4 <- x[splitPlan[[4]]$app, ]
+iteration4 <- crossvalidate(train4, test4)
 
 #=============================================
-train5 <- oshitar::variable_setup(x[splitPlan[[5]]$train, ])
-test5 <- oshitar::variable_setup(x[splitPlan[[5]]$app, ])
-(iteration5 <- crossvalidate(train5, test5))
+train5 <- x[splitPlan[[5]]$train, ]
+test5 <- x[splitPlan[[5]]$app, ]
+iteration5 <- crossvalidate(train5, test5)
 
@@
 
+```{r}
+# without pspline on text_length (if take out pspline on text_length, pvalue for fifth iteration goes back down to 0 (from 0.53))
+crossvalidate1 <- function(train, test) {
+
+  # building model on training data set
+  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train)
+
+  # performance metrics for training data 
+  train[["predictions"]] <- predict(model, type = "risk")
+  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
+  train_metrics <- data.frame(HR = exp(metric$coefficients), 
+                              LR = round(metric$stats[3],2), 
+                              pval = round(metric$stats[5],2), 
+                              Dxy = round(metric$stats[9],2), 
+                              AIC = stats::AIC(metric, k = 2), 
+                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
+
+  # predicting on test data
+  test[["predictions"]] <- predict(model, newdata = test, type = "risk")
+
+  # computing performance metrics 
+  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
+  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
+                             LR = round(metric1$stats[3],2), 
+                             pval = round(metric1$stats[5],2), 
+                             Dxy = round(metric1$stats[9],2), 
+                             AIC = stats::AIC(metric1, k = 2), 
+                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
+
+  # returns data frame with train/test metrics 
+  statistics <- rbind(train_metrics, test_metrics)
+  rownames(statistics) <- c("Training Data", "Test Data")
+  return(statistics) 
+}
+
+i1 <- crossvalidate1(train1, test1)
+i2 <- crossvalidate1(train2, test2)
+i3 <- crossvalidate1(train3, test3)
+i4 <- crossvalidate1(train4, test4)
+i5 <- crossvalidate1(train5, test5)
+
+i1; i2; i3; i4; i5
+```
+
 # Fitting model to the full data set
@@
 
-final <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = x)
+final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = x)
 summary(final)

### 2017-08-23 Hours.Rmd
updated hours

@@
 8/16/2017 | 2.5 | 7:00-9:30PM | Fit model to full data set, wrote function to take data, fit model, and get predicted survival probabilities 
+8/17/2017 | 3.25 | 9:00-12:15PM | Met with Dr. Pileggi, started researching splines 
+8/17/2017 | 1 | 1:30-2:30PM | More spline research
+8/21/2017 | 4 | 2:00-6:00PM | Fit splines with univariate analysis, backward/forward selection on model including splines + square root + log transformed variables 
+8/22/2017 | 5.5 | 10:00-3:30PM  | Univariate analysis for quadratic terms of variables, fixed setup function, removed devices from frequently answered/answered terms list
+8/22/2017 | 3.75 | 6:15-10:00PM | More work with splines + cross validation
 

### 2017-08-23 model fitting/cross_validation.Rmd
fixed function for cross validation

@@
 library(stats)
-library(ggplot2)
+library(rms)
 ```
@@
 train1 <- x[splitPlan[[1]]$train, ]
+test1 <- x[splitPlan[[1]]$app, ]
+
+train2 <- x[splitPlan[[2]]$train, ]
+test2 <- x[splitPlan[[2]]$app, ]
+
+train3 <- x[splitPlan[[3]]$train, ]
+test3 <- x[splitPlan[[3]]$app, ]
+
+train4 <- x[splitPlan[[4]]$train, ]
+test4 <- x[splitPlan[[4]]$app, ]
+
+train5 <- x[splitPlan[[5]]$train, ]
+test5 <- x[splitPlan[[5]]$app, ]
 ```
@@
 
-##### Fitting model with all significant variables (univariate analysis p-value < 0.01)
+##### Fitting model with all significant variables
+
+* univariate analysis p-value < 0.01
+* using stepAIC to perform backwards and forwards stepwise variable selection with AIC criteria 
+* transformed text_length + avg_tag_length + newline_ratio all insignificant (don't include in model)
 
@@
 model <- MASS::stepAIC(fit, direction = "both", k = 2)
-#results of stepAIC (but keeping contain_answered)
+
+#results of stepAIC (including contain_answered even though it was dropped)
 results <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday, data = train1)
 summary(results)
-AIC(results, k = 2) # 64965.89
+AIC(results, k = 2) # 64969.63
+```
 
+##### Adding in splines
+
+* using penalized spline smoothing with AIC criteria 
+    + pspline function from survival package 
+* splines on device_length and avg_tag_length decreased the AIC the most 
+    + it seems like adding in any spline decreases the AIC (is the AIC valid to use) 
+* also fit using corrected AIC as criteria - no difference
+
+```{r}
 # adding in spline on device_length
@@
 AIC(model_spline, k = 2) # 64907.21
+summary(model_spline)
 
 # adding in spline on text_length
-model_spline1 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC"), data = train1)
-AIC(model_spline1, k = 2) # 64894.01
+model_spline1 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(text_length, df = 0, method = "AIC"), data = train1)
+AIC(model_spline1, k = 2) # 64914.27
 
 # adding in spline on avg_tag_length
-model_spline2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+model_spline2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
 summary(model_spline2)
-AIC(model_spline2, k = 2) # 64848.5
+AIC(model_spline2, k = 2) # 64893.52
 
-anova(model_spline2)
-
-#=====================================================
-# adding interaction between title_questionmark + title_beginwh (probably leave out)
-# probably leave interactions out, don't do much for the model
-
-resultse <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + title_questionmark + title_beginwh + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_questionmark*title_beginwh, data = train1)
-summary(resultse)
-AIC(resultse, k = 2) # 64843
+# adding in spline on newline_ratio
+model_spline3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
+summary(model_spline3)
+AIC(model_spline3, k = 2) # 64915.6
 ```
 
-# using rcs (restricted cubic spline) in rms package 
+##### Restricted cubic splines
+
+* using rcs (restricted cubic spline) in rms package
 * fit knots at quantiles of the predictor 
 * recommended in Regression Modeling Strategies to have 5 knots for large data sets 
+* estimates less parameters than penalized spline smoothing with AIC criteria 
+* **AIC is higher for these splines**
+
 ```{r}
-unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.725, 0.95)))
+library(rms)
+# fitting with spline on device_length
+model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
+AIC(model, k = 2) # 64968.39
 
-library(rms)
-model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
-AIC(model_spline, k = 2) # 64907.21
-model
+# fitting with spline on text_length
+model2 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
+AIC(model2, k = 2) # 64967.25
+
+# fitting with spline on avg_tag_length (output keeps giving errors)
+# model3 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(avg_tag_length, unname(quantile(train1$avg_tag_length, c(0.05, 0.35, 0.65, 0.95)))), data = train1)
+# AIC(model3, k = 2) # 64967.25
+
+# fitting with spline on newline_ratio (keep getting errors with this one too)
+# model4 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(newline_ratio, unname(quantile(train1$newline_ratio, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
+# AIC(model4, k = 2) # 64967.25
+
+# fitting with splines on device and text length
+model5 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))) + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
+AIC(model5, k = 2) # 64969.7
+
+# fitting model with spline on text_length + sqrt(device_length)
+model6 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(device_length) + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
+AIC(model6, k = 2) # 64967.95
+
+```
+
+##### Interactions
+
+* probably not going to include any interactions - don't do much for the model
+
+```{r, echo = FALSE}
+# adding interaction between title_questionmark + title_beginwh 
+reduced <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + title_beginwh + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday, data = train1) # title_beginwh was not included in result from stepAIC, added in this model to compare it to the model with the interaction
+
+interaction <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + title_beginwh + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + title_questionmark*title_beginwh, data = train1)
+summary(interaction)
+AIC(interaction, k = 2) # 64963.33 barely drops 
+oshitar::compare_nested(interaction, reduced)
 ```
@@
 
-* categorical variables must be the same across data sets, but I want the categorical variable to change with each data set, any way to do this?
+```{r, include = FALSE}
+# function to perform cross validation
+# vars is a string of variables, ex: "new_category + new_user..."
+# outputs df with performance metrics (for model on train and test data 
+crossval <- function(vars, train, test) {
+  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
+  model <- survival::coxph(as.formula(formula), data = train)
+
+  train[["predictions"]] <- predict(model, type = "risk")
+  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
+  train_metrics <- data.frame(HR = exp(metric$coefficients), 
+                              LR = round(metric$stats[3],2), 
+                              pval = round(metric$stats[5],2), 
+                              AIC = stats::AIC(metric, k = 2),
+                              Dxy = round(metric$stats[9],2), 
+                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
+
+  # predicting on test data
+  test[["predictions"]] <- predict(model, newdata = test, type = "risk")
+
+  # computing performance metrics 
+  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
+  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
+                             LR = round(metric1$stats[3],2), 
+                             pval = round(metric1$stats[5],2), 
+                             AIC = stats::AIC(metric1, k = 2),
+                             Dxy = round(metric1$stats[9],2), 
+                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
+
+  # returns data frame with train/test metrics 
+  statistics <- rbind(train_metrics, test_metrics)
+  rownames(statistics) <- c("Training Data", "Test Data")
+  return(statistics)
+
+}
+
+# function to get average performance metric for each iteration 
+# takes list of performance metrics 
+get_avgmetrics <- function(list) {
+  avg <- rbind(train_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][1,]))), test_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][2,]))))
+  return(avg)
+}
+
+```
+
+##### spline on device_length, text_length, avg_tag_length
 
@@
 # function to perform cross validation + compute performance metrics
-crossvalidate <- function(train, test) {
+cv_allsplines <- function(train, test) {
 
@@
 
-#=============================================
-test1 <- x[splitPlan[[1]]$app, ]
-iteration1 <- crossvalidate(train1, test1)
+trains <- list(train1, train2, train3, train4, train5)
+tests <- list(test1, test2, test3, test4, test5)
 
-#=============================================
-train2 <- x[splitPlan[[2]]$train, ]
-test2 <- x[splitPlan[[2]]$app, ]
-iteration2 <- crossvalidate(train2, test2)
-
-#=============================================
-train3 <- x[splitPlan[[3]]$train, ]
-test3 <- x[splitPlan[[3]]$app, ]
-iteration3 <- crossvalidate(train3, test3)
-
-#=============================================
-train4 <- x[splitPlan[[4]]$train, ]
-test4 <- x[splitPlan[[4]]$app, ]
-iteration4 <- crossvalidate(train4, test4)
-
-#=============================================
-train5 <- x[splitPlan[[5]]$train, ]
-test5 <- x[splitPlan[[5]]$app, ]
-iteration5 <- crossvalidate(train5, test5)
-
-iteration1
-iteration2
-iteration3
-iteration4
-iteration5
+allspline_models <- purrr::map2(trains, tests, ~cv_allsplines(.x, .y))
+allspline_models
+# 5th iteration: pvalue for loglikelihood ratio test = 0.51 on test data 
 ```
 
+##### spline on device_length only
+
 ```{r}
-# without pspline on text_length (if take out pspline on text_length, pvalue for fifth iteration goes back down to 0 (from 0.53))
-crossvalidate1 <- function(train, test) {
+varsdev <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC')"
 
-  # building model on training data set
-  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train)
+splinedev <- purrr::map2(trains, tests, ~crossval(varsdev, .x, .y))
+splinedev
+```
 
-  # performance metrics for training data 
-  train[["predictions"]] <- predict(model, type = "risk")
-  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
-  train_metrics <- data.frame(HR = exp(metric$coefficients), 
-                              LR = round(metric$stats[3],2), 
-                              pval = round(metric$stats[5],2), 
-                              Dxy = round(metric$stats[9],2), 
-                              AIC = stats::AIC(metric, k = 2), 
-                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
+##### spline on text_length only
 
-  # predicting on test data
-  test[["predictions"]] <- predict(model, newdata = test, type = "risk")
+```{r}
+varstext <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(text_length, df = 0, method = 'AIC')"
 
-  # computing performance metrics 
-  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
-  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
-                             LR = round(metric1$stats[3],2), 
-                             pval = round(metric1$stats[5],2), 
-                             Dxy = round(metric1$stats[9],2), 
-                             AIC = stats::AIC(metric1, k = 2), 
-                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
+splinetext <- purrr::map2(trains, tests, ~crossval(varstext, .x, .y))
+```
 
-  # returns data frame with train/test metrics 
-  statistics <- rbind(train_metrics, test_metrics)
-  rownames(statistics) <- c("Training Data", "Test Data")
-  return(statistics) 
-}
+##### spline on avg_tag_length only
 
-i1 <- crossvalidate1(train1, test1)
-i2 <- crossvalidate1(train2, test2)
-i3 <- crossvalidate1(train3, test3)
-i4 <- crossvalidate1(train4, test4)
-i5 <- crossvalidate1(train5, test5)
+```{r}
+varstag <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(avg_tag_length, df = 0, method = 'AIC')"
 
-i1; i2; i3; i4; i5
+splinetag <- purrr::map2(trains, tests, ~crossval(varstag, .x, .y))
+```
+
+##### spline on newline_ratio only
+
+```{r}
+varsnew <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = 'AIC')"
+
+splinenew <- purrr::map2(trains, tests, ~crossval(varsnew, .x, .y))
+```
+
+##### viewing all metrics
+
+```{r}
+splinedev_avg <- get_avgmetrics(splinedev)
+splinetext_avg <- get_avgmetrics(splinetext)
+splinetag_avg <- get_avgmetrics(splinetag)
+splinenew_avg <- get_avgmetrics(splinenew)
+```
+
+##### restricted cubic spline on text_length (had the smallest AIC)
+
+* predictions on test data not working
+
+```{r}
+#  cv_rcstext <- function(train, test) {
+# 
+#   # building model on training data set
+#   model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train)
+# 
+#   metric <- cph(Surv(time_until_answer, answered) ~ p, data = train)
+#   train_metrics
+# 
+#   # performance metrics for training data
+#   train[["predictions"]] <- exp(predict(model, type = "lp"))
+#   metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
+#   train_metrics <- data.frame(HR = exp(metric$coefficients),
+#                               LR = round(metric$stats[3],2),
+#                               pval = round(metric$stats[5],2),
+#                               Dxy = round(metric$stats[9],2),
+#                               AIC = stats::AIC(metric, k = 2),
+#                               Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
+# 
+#   # predicting on test data
+#   test[["predictions"]] <- exp(predict(model, newdata = test, type = "lp"))
+# 
+#   # computing performance metrics
+#   metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
+#   test_metrics <- data.frame(HR = exp(metric1$coefficients),
+#                              LR = round(metric1$stats[3],2),
+#                              pval = round(metric1$stats[5],2),
+#                              Dxy = round(metric1$stats[9],2),
+#                              AIC = stats::AIC(metric1, k = 2),
+#                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
+# 
+#   # returns data frame with train/test metrics
+#   statistics <- rbind(train_metrics, test_metrics)
+#   rownames(statistics) <- c("Training Data", "Test Data")
+#   return(statistics)
+# }
+# 
+# rcstext_models <- purrr::map2(trains, tests, ~cv_rcstext(.x, .y))
+# splinenew_models
+
 ```

### 2017-08-23 model fitting/cross_validation.Rmd
wrote function to average performance metrics

@@
 ```{r, echo = FALSE}
-# function to perform cross validation + compute performance metrics
-cv_allsplines <- function(train, test) {
-
-  # building model on training data set
-  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train)
-
-  # performance metrics for training data 
-  train[["predictions"]] <- predict(model, type = "risk")
-  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
-  train_metrics <- data.frame(HR = exp(metric$coefficients), 
-                              LR = round(metric$stats[3],2), 
-                              pval = round(metric$stats[5],2), 
-                              Dxy = round(metric$stats[9],2), 
-                              AIC = stats::AIC(metric, k = 2), 
-                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
-
-  # predicting on test data
-  test[["predictions"]] <- predict(model, newdata = test, type = "risk")
-
-  # computing performance metrics 
-  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
-  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
-                             LR = round(metric1$stats[3],2), 
-                             pval = round(metric1$stats[5],2), 
-                             Dxy = round(metric1$stats[9],2), 
-                             AIC = stats::AIC(metric1, k = 2), 
-                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
-
-  # returns data frame with train/test metrics 
-  statistics <- rbind(train_metrics, test_metrics)
-  rownames(statistics) <- c("Training Data", "Test Data")
-  return(statistics) 
-}
-
 trains <- list(train1, train2, train3, train4, train5)
@@
 
-allspline_models <- purrr::map2(trains, tests, ~cv_allsplines(.x, .y))
-allspline_models
+allvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC') + pspline(text_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC')"
+allsplines <- purrr::map2(trains, tests, ~crossval(allvars, .x, .y))
+
+allsplines
 # 5th iteration: pvalue for loglikelihood ratio test = 0.51 on test data 
@@
 
+##### with splines on device_length and text_length
+
+* splines on device_length and text_length ahd the most signficant p-values out of all splines in univariate analysis
+
+```{r}
+devtextvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC') + pspline(text_length, df = 0, method = 'AIC')"
+
+devtext <- purrr::map2(trains, tests, ~crossval(devtextvars, .x, .y))
+
+```
+
+```{r}
+sqrtdev <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(device_length) + pspline(text_length, df = 0, method = 'AIC')"
+
+sqrtdev <- purrr::map2(trains, tests, ~crossval(sqrtdev, .x, .y))
+sqrtdev
+
+sqrttext <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(text_length) + pspline(device_length, df = 0, method = 'AIC')"
+
+sqrttext <- purrr::map2(trains, tests, ~crossval(sqrttext, .x, .y))
+
+```
+
+##### without splines
+
+```{r}
+vars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday"
+
+nospline <- purrr::map2(trains, tests, ~crossval(vars, .x, .y))
+```
+
 ##### viewing all metrics
@@
 ```{r}
+allspline_avg <- get_avgmetrics(allsplines)
 splinedev_avg <- get_avgmetrics(splinedev)
@@
 splinenew_avg <- get_avgmetrics(splinenew)
+nospline_avg <- get_avgmetrics(nospline)
+devtext_avg <- get_avgmetrics(devtext)
+sqrtdev_avg <- get_avgmetrics(sqrtdev)
+sqrttext_avg <- get_avgmetrics(sqrttext)
+
+allspline_avg; splinedev_avg; splinetext_avg; splinetag_avg; splinenew_avg; nospline_avg; devtext_avg; sqrtdev_avg; sqrttext_avg
+```
+
+```{r}
+get_avgdiff <- function(list) {
+  list_diff <- purrr::map(1:length(list), ~diff(as.matrix(list[[.]], lag = 1)))
+  df <- plyr::ldply(list_diff, data.frame) %>%
+    select(HR, Dxy, Concordance) %>%
+    colMeans()
+  return(df)
+}
+
+list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext)
+names <- c("allsplines", "splinedev", "splinetext", "splinetag", "splinenew", "nospline", "devtext", "sqrtdev", "sqrttext") # change this to avoid hard coding
+
+l_diff <- purrr::map(list, ~get_avgdiff(.))
+df_diff <- plyr::ldply(purrr::map(1:length(l_diff), ~data.frame(as.list(l_diff[[.]]))), data.frame)
+rownames(df_diff) <- names
+df_diff
+
+#least amount of average change found in model with only the spline on newline_ratio 
 ```

### 2017-08-24 model fitting/cross_validation.Rmd
more model fitting

@@
 
+# spline = avg_tag_length + device_length
+model_spline3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+summary(model_spline3)
+AIC(model_spline3, k = 2) # 64865.95
+
 # adding in spline on newline_ratio
-model_spline3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
+model_spline4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
 summary(model_spline3)
-AIC(model_spline3, k = 2) # 64915.6
+AIC(model_spline4, k = 2) # 64915.6
+
+# log10(text_length), spline = avg_tag_length + device_length
+model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+AIC(model_spline5, k = 2) # 64865.73
+
+# log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
+model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+AIC(model_spline5, k = 2) # 64864.73
+
+# title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
+model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + title_questionmark*title_beginwh, data = train1)
+AIC(model_spline5, k = 2) # 64858.68
 ```
@@
 
+##### log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length + interaction between titlebeginwh*title_questionmark
+```{r}
+vars1 <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + title_beginwh + title_questionmark*title_beginwh"
+
+lots <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
+lots
+```
+
 ##### viewing all metrics
@@
 ```{r}
-allspline_avg <- get_avgmetrics(allsplines)
-splinedev_avg <- get_avgmetrics(splinedev)
-splinetext_avg <- get_avgmetrics(splinetext)
-splinetag_avg <- get_avgmetrics(splinetag)
-splinenew_avg <- get_avgmetrics(splinenew)
-nospline_avg <- get_avgmetrics(nospline)
-devtext_avg <- get_avgmetrics(devtext)
-sqrtdev_avg <- get_avgmetrics(sqrtdev)
-sqrttext_avg <- get_avgmetrics(sqrttext)
-
-allspline_avg; splinedev_avg; splinetext_avg; splinetag_avg; splinenew_avg; nospline_avg; devtext_avg; sqrtdev_avg; sqrttext_avg
+# turn avg_list into a data frame with rownames???
+list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext, lots)
+avg_list <- purrr::map(list, ~get_avgmetrics(.))
+avg_list
 ```
@@
 
-list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext)
-names <- c("allsplines", "splinedev", "splinetext", "splinetag", "splinenew", "nospline", "devtext", "sqrtdev", "sqrttext") # change this to avoid hard coding
+# find a way to put rownames on df_diff in a reproducible way 
+l_diff <- purrr::map(list, ~get_avgdiff(.))
+df_diff <- plyr::ldply(purrr::map(1:length(l_diff), ~data.frame(as.list(l_diff[[.]]))))
+df_diff
+#least amount of average change found in model with only the spline on newline_ratio 
+```
 
-l_diff <- purrr::map(list, ~get_avgdiff(.))
-df_diff <- plyr::ldply(purrr::map(1:length(l_diff), ~data.frame(as.list(l_diff[[.]]))), data.frame)
-rownames(df_diff) <- names
-df_diff
+```{r}
+newline_text <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + pspline(newline_ratio, df = 0, method = 'AIC')"
 
-#least amount of average change found in model with only the spline on newline_ratio 
+sqrtdev <- purrr::map2(trains, tests, ~crossval(newline_text, .x, .y))
+sqrtdev
 ```

### 2017-08-24 model fitting/cross_validation.Rmd
fit final model (?)

@@
 
-model <- MASS::stepAIC(fit, direction = "both", k = 2)
+fit2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+
+model <- MASS::stepAIC(fit2, direction = "both", k = 2)
 
@@
 AIC(results, k = 2) # 64969.63
+```
+
+```{r}
+results2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
+    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
+    text_all_lower + update + prior_effort + ampm + weekday + 
+    pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, 
+    df = 0, method = "AIC"), data = train1)
+AIC(results2, k = 2) # 64866.93
+
 ```
@@
 AIC(model_spline5, k = 2) # 64858.68
+
+# title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length + newline_ratio
+model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + pspline(newline_ratio, df = 0, method = "AIC") + title_questionmark*title_beginwh, data = train1)
+AIC(model_spline5, k = 2) # 64841.25
 ```
@@
 
+##### log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length, newline_ratio + interaction between titlebeginwh*title_questionmark
+
+```{r}
+vars2 <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + title_beginwh + pspline(newline_ratio, df = 0, method = 'AIC') + title_questionmark*title_beginwh"
+
+lots2 <- purrr::map2(trains, tests, ~crossval(vars2, .x, .y))
+lots2
+```
+
+##### splines on device_length and avg_tag_length (FINAL MODEL???)
+
+```{r}
+varsdevtag <- "new_category + as.factor(new_user) + 
+    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
+    text_all_lower + update + prior_effort + ampm + weekday + 
+    pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
+    df = 0, method = 'AIC')"
+devtag <- purrr::map2(trains, tests, ~crossval(varsdevtag, .x, .y))
+```
+
 ##### viewing all metrics
@@
 # turn avg_list into a data frame with rownames???
-list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext, lots)
+list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext, lots, lots2, devtag)
 avg_list <- purrr::map(list, ~get_avgmetrics(.))
@@
 
+### FINAL MODEL (?)
 ```{r}
-newline_text <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + pspline(newline_ratio, df = 0, method = 'AIC')"
+final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
+    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
+    text_all_lower + update + prior_effort + ampm + weekday + 
+    pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
+    df = 0, method = 'AIC'), data = x)
+summary(final)
+AIC(final, k = 2) # 82957.53
 
-sqrtdev <- purrr::map2(trains, tests, ~crossval(newline_text, .x, .y))
-sqrtdev
+x$predictions <- predict(final, type = "risk")
+performance <- cph(Surv(time_until_answer, answered) ~ predictions, data = x)
+AIC(performance, k = 2) # 83268.04
+
+final_metrics <- data.frame(HR = exp(performance$coefficients), 
+                              LR = round(performance$stats[3],2), 
+                              pval = round(performance$stats[5],2), 
+                              AIC = stats::AIC(performance, k = 2),
+                              Dxy = round(performance$stats[9],2), 
+                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
+final_metrics
+# performance metrics on entire data set are not different from cross validation 
 ```

### 2017-08-24 model fitting/cross_validation.Rmd
assessed residuals + PH assumption

@@
 AIC(results, k = 2) # 64969.63
-```
 
-```{r}
+# results of second stepAIC
 results2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
@@
 
+final_model <- results2
 ```
@@
 oshitar::compare_nested(interaction, reduced)
-```
-
-### residuals, PH assumption
-
-* Martingale residuals
-    + plot for each continuous predictor 
-    + assess adequacy of functional form of predictors, or suggest a potential form 
-* Deviance residuals
-    + check for outliers identify questions poorly predicted by the model 
-    + one plot, examine questions with |residuals| > 2.5
-* Schoenfeld residuals
-    + one plot for each predictor 
-    + if loess curve is flat, proportional hazard assumption is not violated, doesn't depend on time. Distinct pattern indicates violation of this assumption
-    + **from the plots:** new_user, title_questionmark, num_freq_tags (1), ampm (Morning, Night), weekday (Thursday, Saturday), new_user*AMPM (morning, night) may violate PH assumption 
-* Score residuals
-    + check for influential observations. ID quesitons who's predictor values highly effect parameter estimates
-    + plot for each predictor 
-* **figure out how to identify certain points on ggplots**
-
-```{r, residuals, echo = FALSE}
-#=============================================
-#martingale residuals
-train1$mart <- residuals(model_full, type = "martingale")
-
-ggplot(train1, aes(x = device_length, y = mart)) + 
-  geom_point() + 
-  geom_smooth() + 
-  ggtitle(paste("Martingale Residuals for device_length")) + 
-  scale_x_continuous("Device_length")
-
-#=============================================
-#deviance residuals 
-train1$deviance <- residuals(model_full, type = "deviance")
-ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
-  geom_point() + 
-  scale_x_continuous("Question index") + 
-  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
-  ggtitle("Deviance Residuals")
-# quite a few questions have a deviance residual of larger than 2.5
-
-#=============================================
-#schoenfeld residuals
-schoen <- as.data.frame(residuals(model_full, type = "schoenfeld"))
-# complete event times sorted from shortest to longest
-schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)
-
-plot_schoen <- function(var) {
-  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
-    geom_point() + 
-    geom_smooth() + 
-    ggtitle(paste("Schoenfeld Residuals for", var)) + 
-    scale_y_continuous("Residuals")
-}
-names <- names(schoen)[-ncol(schoen)]
-purrr::map(names, plot_schoen)
-
-#=============================================
-# score residuals
-score <- as.data.frame(residuals(model_full, type = "score"))
-# function to plot score residuals
-plot_score <- function(column) {
-  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
-    geom_point() + 
-    geom_smooth() + 
-    ggtitle(paste("Score residuals for", column)) + 
-    scale_y_continuous("Score Residuals") + 
-    scale_x_continuous("Question index")
-}
-columns <- names(score)
-purrr::map(columns, plot_score)
-
-#=============================================
-# working with rms::which.influence to id influential points
-c <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, x = TRUE, y = TRUE, data = train1)
-influence <- rms::which.influence(c)
-rms::show.influence(influence, train1)
-
-#=============================================
-# formal test of PH assumption
-options(scipen=999)
-ph_test <- data.frame(predictors = rownames(cox.zph(model_full)$table), cox.zph(model_full)$table) 
-rownames(ph_test) = NULL
-ph_test <- ph_test %>%
-  arrange(p)
-
-#=============================================
-# addression PH assumption violations
-
-# stratifying on new_category
-strat_model <- coxph(Surv(time_until_answer, answered) ~ strata(new_category) + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
-AIC(strat_model, k = 2) # 49766.8
-summary(strat_model)
-
-# stratifying on new_user
-strat_model1 <- coxph(Surv(time_until_answer, answered) ~ new_category + strata(new_user) + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
-AIC(strat_model1, k = 2) # 60543.75
-summary(strat_model1)
-
-# stratifying on ampm 
-strat_model2 <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + strata(ampm) + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
-AIC(strat_model2, k = 2) # 54447.8
-summary(strat_model2)
-
-# stratifying on ampm, new_user, new_category
-strat_model3 <- coxph(Surv(time_until_answer, answered) ~ strata(new_category) + strata(new_user) + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + strata(ampm) + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
-AIC(strat_model3, k = 2) # 35370.81
-summary(strat_model3)
 ```
@@
 
-##### restricted cubic spline on text_length (had the smallest AIC)
-
-* predictions on test data not working
-
-```{r}
-#  cv_rcstext <- function(train, test) {
-# 
-#   # building model on training data set
-#   model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train)
-# 
-#   metric <- cph(Surv(time_until_answer, answered) ~ p, data = train)
-#   train_metrics
-# 
-#   # performance metrics for training data
-#   train[["predictions"]] <- exp(predict(model, type = "lp"))
-#   metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
-#   train_metrics <- data.frame(HR = exp(metric$coefficients),
-#                               LR = round(metric$stats[3],2),
-#                               pval = round(metric$stats[5],2),
-#                               Dxy = round(metric$stats[9],2),
-#                               AIC = stats::AIC(metric, k = 2),
-#                               Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
-# 
-#   # predicting on test data
-#   test[["predictions"]] <- exp(predict(model, newdata = test, type = "lp"))
-# 
-#   # computing performance metrics
-#   metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
-#   test_metrics <- data.frame(HR = exp(metric1$coefficients),
-#                              LR = round(metric1$stats[3],2),
-#                              pval = round(metric1$stats[5],2),
-#                              Dxy = round(metric1$stats[9],2),
-#                              AIC = stats::AIC(metric1, k = 2),
-#                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
-# 
-#   # returns data frame with train/test metrics
-#   statistics <- rbind(train_metrics, test_metrics)
-#   rownames(statistics) <- c("Training Data", "Test Data")
-#   return(statistics)
-# }
-# 
-# rcstext_models <- purrr::map2(trains, tests, ~cv_rcstext(.x, .y))
-# splinenew_models
-
-```
-
-# Fitting model to the full data set
-
 ```{r, echo = FALSE}
-x <- oshitar::variable_setup(x)
-
-final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = x)
-summary(final)
-AIC(final, k = 2) # 83051.61
-
-x$predictions <- predict(final, type = "risk")
-(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x))
-AIC(performance, k = 2)
-
-# extracting predicted survival probabilities
-prob <- pec::predictSurvProb(final, newdata = x, times = c(0.5, 1, 1.5, 2, quantile(x$time_until_answer)))
-
-#==================================================================================
 # function to take in a data set, fit the model, output performance metrics, and allow you to specify times to predict survival probabilities
@@
 ```
+
+### residuals, PH assumption
+
+* Martingale residuals
+    + plot for each continuous predictor 
+    + assess adequacy of functional form of predictors, or suggest a potential form 
+* Deviance residuals
+    + check for outliers identify questions poorly predicted by the model 
+    + one plot, examine questions with |residuals| > 2.5
+* Schoenfeld residuals
+    + one plot for each predictor 
+    + if loess curve is flat, proportional hazard assumption is not violated, doesn't depend on time. Distinct pattern indicates violation of this assumption
+    + **from the plots:** new_user, title_questionmark, num_freq_tags (1), ampm (Morning, Night), weekday (Thursday, Saturday), new_user*AMPM (morning, night) may violate PH assumption 
+* Score residuals
+    + check for influential observations. ID quesitons who's predictor values highly effect parameter estimates
+    + plot for each predictor 
+* **figure out how to identify certain points on ggplots**
+
+```{r, residuals, echo = FALSE}
+# variables : new_category + as.factor(new_user) + 
+#     contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
+#     text_all_lower + update + prior_effort + ampm + weekday + 
+#     pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, 
+#     df = 0, method = "AIC") 
+#=============================================
+#martingale residuals
+train1$mart <- residuals(final_model, type = "martingale")
+train1$sqrt_score <- sqrt(train1$avg_tag_score)
+
+ggplot(train1, aes(x = sqrt_score, y = mart)) + 
+  geom_point() + 
+  geom_smooth() + 
+  ggtitle(paste("Martingale Residuals for device_length")) + 
+  scale_x_continuous("Device_length")
+# what do I assess for spline variables?
+
+#=============================================
+#deviance residuals 
+train1$deviance <- residuals(final_model, type = "deviance")
+ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
+  geom_point() + 
+  scale_x_continuous("Question index") + 
+  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
+  ggtitle("Deviance Residuals")
+# quite a few questions have a deviance residual of larger than 2.5 (use ggplotly to identify)
+
+#=============================================
+# schoenfeld residuals
+schoen <- as.data.frame(residuals(final_model, type = "schoenfeld"))
+# complete event times sorted from shortest to longest
+schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)
+
+plot_schoen <- function(var) {
+  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Schoenfeld Residuals for", var)) + 
+    scale_y_continuous("Residuals")
+}
+names <- names(schoen)[-ncol(schoen)]
+purrr::map(names, plot_schoen)
+
+# plots indicate that new_user, ampm and a few others may have violated ph assumption
+
+#=============================================
+# formal test of PH assumption
+options(scipen=999)
+ph_test <- data.frame(predictors = rownames(cox.zph(final_model)$table), cox.zph(final_model)$table) 
+rownames(ph_test) = NULL
+ph_test <- ph_test %>%
+  arrange(p)
+ph_test
+#=============================================
+# score residuals
+score <- as.data.frame(residuals(final_model, type = "score"))
+
+# function to plot score residuals
+plot_score <- function(column) {
+  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Score residuals for", column)) + 
+    scale_y_continuous("Score Residuals") + 
+    scale_x_continuous("Question index")
+}
+columns <- names(score)
+purrr::map(columns, plot_score)
+# score residuals show that there are quite a few points that may be influential (check with ggplotly)
+```

### 2017-08-25 Hours.Rmd
updated hours
update hours

@@
 8/22/2017 | 3.75 | 6:15-10:00PM | More work with splines + cross validation 
+8/23/2017 | 9.5 | 9:00-6:30 | More spline research, cross-validated on models with different splines, compared models, fit final model(?)
+8/23/2017 | 1 | 7:45-8:45PM | Plotted residuals, assessed PH assumption, researched effect of violation of PH assumption 
+8/24/2017 | 2 | 10:00-12:00AM | Read Regression Modeling Strategies text book
+8/24/2017 | 3.5 | 3:00-6:30PM | Continued reading regression modeling strategies book + other literature, tried to apply it to the data
+8/24/2017 | 1.5 | 7:30-9:00PM | Residuals, checked PH assumption, tried to address PH assumption violations
 

### 2017-08-25 model fitting/cross_validation.Rmd
reorganized file, fitted new models, looked at residuals, tried to address PH violation

@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-```{r, data setup, echo = FALSE}
 x <- oshitar::setup()
@@
 
-### Creating cross-validation plan with k = 5
-
-```{r, echo = FALSE}
+```{r, cross validation, echo = FALSE}
+# creating cross-validation plan with k = 5
 set.seed(444)
 splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
-str(splitPlan)
 
@@
 * using stepAIC to perform backwards and forwards stepwise variable selection with AIC criteria
-* transformed text_length + avg_tag_length + newline_ratio all insignificant (don't include in model)
 
 ```{r, echo = FALSE}
-fit <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday, data = train1)
+# fitted with penalized spline smoothing with AIC criteria on device_length and avg_tag_length
+fit <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
 
-fit2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+#model <- MASS::stepAIC(fit, direction = "both", k = 2)
 
-model <- MASS::stepAIC(fit2, direction = "both", k = 2)
-
-#results of stepAIC (including contain_answered even though it was dropped)
-results <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday, data = train1)
-summary(results)
-AIC(results, k = 2) # 64969.63
-
-# results of second stepAIC
-results2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
-    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
+# results of stepAIC (including contain_answered)
+results <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
+    contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + 
     text_all_lower + update + prior_effort + ampm + weekday + 
@@
 AIC(results2, k = 2) # 64866.93
-
-final_model <- results2
 ```
 
-##### Adding in splines
+##### Splines
 
-* using penalized spline smoothing with AIC criteria 
-    + pspline function from survival package 
-* splines on device_length and avg_tag_length decreased the AIC the most 
-    + it seems like adding in any spline decreases the AIC (is the AIC valid to use) 
-* also fit using corrected AIC as criteria - no difference
+* adding in splines one at a time
 
 ```{r}
-# adding in spline on device_length
-model_spline <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC"), data = train1)
-AIC(model_spline, k = 2) # 64907.21
-summary(model_spline)
+# spline on device_length
+spline <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC"), data = train1)
+AIC(spline, k = 2) # 64907.21
+summary(spline)
 
-# adding in spline on text_length
-model_spline1 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(text_length, df = 0, method = "AIC"), data = train1)
-AIC(model_spline1, k = 2) # 64914.27
+# spline on text_length
+spline1 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(text_length, df = 0, method = "AIC"), data = train1)
+AIC(spline1, k = 2) # 64914.27
 
-# adding in spline on avg_tag_length
-model_spline2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
-summary(model_spline2)
-AIC(model_spline2, k = 2) # 64893.52
+# spline on avg_tag_length
+spline2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+AIC(spline2, k = 2) # 64893.52
 
-# spline = avg_tag_length + device_length
-model_spline3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
-summary(model_spline3)
-AIC(model_spline3, k = 2) # 64865.95
+# spline on avg_tag_length + device_length
+spline3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+AIC(spline3, k = 2) # 64865.95
 
-# adding in spline on newline_ratio
-model_spline4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
-summary(model_spline3)
-AIC(model_spline4, k = 2) # 64915.6
+# spline on newline_ratio
+spline4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
+AIC(spline4, k = 2) # 64915.6
 
 # log10(text_length), spline = avg_tag_length + device_length
-model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
-AIC(model_spline5, k = 2) # 64865.73
+spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+AIC(spline5, k = 2) # 64865.73
 
 # log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
-model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
-AIC(model_spline5, k = 2) # 64864.73
+spline6 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
+AIC(spline6, k = 2) # 64864.73
 
 # title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
-model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + title_questionmark*title_beginwh, data = train1)
-AIC(model_spline5, k = 2) # 64858.68
+spline7 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + title_questionmark*title_beginwh, data = train1)
+AIC(spline7, k = 2) # 64858.68
 
 # title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length + newline_ratio
-model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + pspline(newline_ratio, df = 0, method = "AIC") + title_questionmark*title_beginwh, data = train1)
-AIC(model_spline5, k = 2) # 64841.25
+spline8 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + pspline(newline_ratio, df = 0, method = "AIC") + title_questionmark*title_beginwh, data = train1)
+AIC(spline8, k = 2) # 64841.25
 ```
@@
 library(rms)
-# fitting with spline on device_length
-model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
-AIC(model, k = 2) # 64968.39
-
-# fitting with spline on text_length
-model2 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
-AIC(model2, k = 2) # 64967.25
-
-# fitting with spline on avg_tag_length (output keeps giving errors)
-# model3 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(avg_tag_length, unname(quantile(train1$avg_tag_length, c(0.05, 0.35, 0.65, 0.95)))), data = train1)
-# AIC(model3, k = 2) # 64967.25
-
-# fitting with spline on newline_ratio (keep getting errors with this one too)
-# model4 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(newline_ratio, unname(quantile(train1$newline_ratio, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
-# AIC(model4, k = 2) # 64967.25
-
-# fitting with splines on device and text length
-model5 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))) + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
-AIC(model5, k = 2) # 64969.7
-
-# fitting model with spline on text_length + sqrt(device_length)
-model6 <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(device_length) + rcs(text_length, unname(quantile(train1$text_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
-AIC(model6, k = 2) # 64967.95
-
+model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, 5) + sqrt(avg_tag_score) + rcs(text_length, 3) + rcs(avg_tag_length, 3) + rcs(newline_ratio, 3), data = train1)
+AIC(model, k = 2) # 64977.65
+# with cph fits, keep getting errors with predict function 
 ```
@@
 
+### Final model(??)
+
+* Regression Modeling Strategies by Frank Harrell pointed out that full models perform the same/if not better than models from stepwise selection
+* this model:
+    + contains all variables
+    + puts splines on all quantitative variables (except for avg_tag_score)
+    + device_length might be a better predictor- set a spline with 5 knots, other variables not throught to be as signficant have 3 knots
+
+```{r}
+full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + ampm + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + pspline(text_length, 3) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = train1)
+AIC(full, k = 2)
+```
+
 ### Performance metric on training data set
-
-* survConcordance: 
-    + Concordance is defined as Pr(agreement) for any two randomly chosen observations, where in this case agreement means that the observation with the shorter survival time of the two also has the larger risk score.
-The predictor (or risk score) will often be the result of a Cox model or other regression
-    + some of the pairs are incomparable. For instance a pair of times (5+, 8), the first being a censored value. We do not know whether the first survival time is greater than or less than the second
-    + observations that are comparable, pairs may also be tied on survival time (but only if both are uncensored) or on the predictor.
-The final concondance is (agree + tied/2)/(agree + disagree + tied)
 
@@
 # working with model_spline2 (model with all splines)
-train1$predictions <- predict(object = model_spline2, type = "risk") # should I predict "lp" instead of "risk"
-(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))
+train1$predictions <- predict(object = full , type = "risk")
+performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)
+performance
 
@@
 Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions, data = train1)
-
 ```
@@
 
-# function to get average performance metric for each iteration 
-# takes list of performance metrics 
+# function to get average performance metric for each iteration of cv 
+# takes list of performance metrics (output from purrr::map(..crossval))
 get_avgmetrics <- function(list) {
@@
 
-##### spline on device_length, text_length, avg_tag_length
-
 ```{r, echo = FALSE}
@@
 
+# model with penalized AIC splines on device, text, tag length 
 allvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC') + pspline(text_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC')"
-allsplines <- purrr::map2(trains, tests, ~crossval(allvars, .x, .y))
-
-allsplines
+devtexttag <- purrr::map2(trains, tests, ~crossval(allvars, .x, .y))
+devtexttag
 # 5th iteration: pvalue for loglikelihood ratio test = 0.51 on test data 
@@
 
-##### spline on device_length only
+```{r}
+# penalized AIC spline on device length only 
+devvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC')"
+dev <- purrr::map2(trains, tests, ~crossval(devvars, .x, .y))
+dev
+```
 
 ```{r}
-varsdev <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC')"
+# penalized AIC spline on text length only
+varstext <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(text_length, df = 0, method = 'AIC')"
 
-splinedev <- purrr::map2(trains, tests, ~crossval(varsdev, .x, .y))
-splinedev
+text <- purrr::map2(trains, tests, ~crossval(varstext, .x, .y))
 ```
 
-##### spline on text_length only
+```{r}
+# penalized AIc spline on tag length only 
+varstag <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(avg_tag_length, df = 0, method = 'AIC')"
+
+tag <- purrr::map2(trains, tests, ~crossval(varstag, .x, .y))
+```
 
 ```{r}
-varstext <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(text_length, df = 0, method = 'AIC')"
+# penalized AIc spline on newline ratio only 
+varsnew <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = 'AIC')"
 
-splinetext <- purrr::map2(trains, tests, ~crossval(varstext, .x, .y))
+newline <- purrr::map2(trains, tests, ~crossval(varsnew, .x, .y))
 ```
 
-##### spline on avg_tag_length only
-
 ```{r}
-varstag <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(avg_tag_length, df = 0, method = 'AIC')"
-
-splinetag <- purrr::map2(trains, tests, ~crossval(varstag, .x, .y))
-```
-
-##### spline on newline_ratio only
-
-```{r}
-varsnew <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = 'AIC')"
-
-splinenew <- purrr::map2(trains, tests, ~crossval(varsnew, .x, .y))
-```
-
-##### with splines on device_length and text_length
-
-* splines on device_length and text_length ahd the most signficant p-values out of all splines in univariate analysis
-
-```{r}
+# penalized splines on dev and text length (both had most signficant p values out of all splines in univariate analysis)
 devtextvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC') + pspline(text_length, df = 0, method = 'AIC')"
@@
 ```{r}
-sqrtdev <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(device_length) + pspline(text_length, df = 0, method = 'AIC')"
+# with log10(text_length) and spline on dev length (going off of univariate p-values) 
+logtextvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + pspline(device_length, df = 0, method = 'AIC')"
 
-sqrtdev <- purrr::map2(trains, tests, ~crossval(sqrtdev, .x, .y))
-sqrtdev
-
-sqrttext <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(text_length) + pspline(device_length, df = 0, method = 'AIC')"
-
-sqrttext <- purrr::map2(trains, tests, ~crossval(sqrttext, .x, .y))
-
+logtext <- purrr::map2(trains, tests, ~crossval(logtextvars, .x, .y))
 ```
 
-##### without splines
-
 ```{r}
+# no splines
 vars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday"
-
 nospline <- purrr::map2(trains, tests, ~crossval(vars, .x, .y))
@@
 
-##### log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length + interaction between titlebeginwh*title_questionmark
 ```{r}
+# log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length + interaction between titlebeginwh*title_questionmark
 vars1 <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + title_beginwh + title_questionmark*title_beginwh"
@@
 lots <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
-lots
 ```
 
-##### log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length, newline_ratio + interaction between titlebeginwh*title_questionmark
-
 ```{r}
+# log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length, newline_ratio + interaction between titlebeginwh*title_questionmark 
 vars2 <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + title_beginwh + pspline(newline_ratio, df = 0, method = 'AIC') + title_questionmark*title_beginwh"
@@
 lots2 <- purrr::map2(trains, tests, ~crossval(vars2, .x, .y))
-lots2
 ```
 
-##### splines on device_length and avg_tag_length (FINAL MODEL???)
-
 ```{r}
+# splines on device_length and avg_tag_length (FINAL MODEL???)
 varsdevtag <- "new_category + as.factor(new_user) + 
@@
 
+##### full model (all variables) with splines on all continuous variables except for avg_tag_score
+
+```{r}
+full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + ampm + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + pspline(text_length, 3) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = train1)
+
+fullvars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + ampm + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + pspline(text_length, 3) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3)"
+full <- purrr::map2(trains, tests, ~crossval(fullvars, .x, .y))
+full
+```
+
 ##### viewing all metrics
@@
 # turn avg_list into a data frame with rownames???
-list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext, lots, lots2, devtag)
+list <- list(dev, text, tag, newline, devtext, logtext, nospline, lots, lots2, devtag, full)
 avg_list <- purrr::map(list, ~get_avgmetrics(.))
@@
 ```{r}
+# function to get the average difference between performance metrics for training and test data 
 get_avgdiff <- function(list) {
@@
 ```{r}
-final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
-    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
-    text_all_lower + update + prior_effort + ampm + weekday + 
-    pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
-    df = 0, method = 'AIC'), data = x)
-summary(final)
-AIC(final, k = 2) # 82957.53
+# final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
+#     contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
+#     text_all_lower + update + prior_effort + ampm + weekday + 
+#     pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
+#     df = 0, method = 'AIC'), data = x)
+# summary(final)
+# AIC(final, k = 2) # 82957.53
 
-x$predictions <- predict(final, type = "risk")
+full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + ampm + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + pspline(text_length, 3) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = x)
+AIC(full, k = 2) # 82974.66
+
+x$predictions <- predict(full, type = "risk")
 performance <- cph(Surv(time_until_answer, answered) ~ predictions, data = x)
-AIC(performance, k = 2) # 83268.04
+AIC(performance, k = 2) # 83243.04
 
@@
 # performance metrics on entire data set are not different from cross validation 
+```
+
+```{r}
+# plotting predictions against observed values (calibration plot?)
+# final_train1 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
+#     contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
+#     text_all_lower + update + prior_effort + ampm + weekday + 
+#     pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
+#     df = 0, method = 'AIC'), data = train1)
+# train1$predictions <- predict(final_train1, type = "risk")
+# 
+# ggplot(train1, aes(x = time_until_answer, y = predictions)) + 
+#   geom_point() + 
+#   ggtitle("Calibration plot")
+# # identify the point at around t = 0 with an incorrect prediction
+# 
+# test1$predictions <- predict(final_train1, newdata = test1, type = "risk")
+# ggplot(train1, aes(x = time_until_answer, y = predictions)) + 
+#   geom_point()
 ```
@@
     + assess adequacy of functional form of predictors, or suggest a potential form
-* Deviance residuals
-    + check for outliers identify questions poorly predicted by the model 
-    + one plot, examine questions with |residuals| > 2.5
+
 * Schoenfeld residuals
@@
 ```{r, residuals, echo = FALSE}
-# variables : new_category + as.factor(new_user) + 
-#     contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
-#     text_all_lower + update + prior_effort + ampm + weekday + 
-#     pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, 
-#     df = 0, method = "AIC") 
+full <- coxph(Surv(time_until_answer, answered) ~ strata(new_category) + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + strata(ampm) + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + poly(text_length, 2) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = train1)
+# If i fit text_length with poly (orthogonal polynomial), text_length doesn't violate ph anymore 
 #=============================================
 #martingale residuals
-train1$mart <- residuals(final_model, type = "martingale")
+train1$mart <- residuals(full, type = "martingale")
 train1$sqrt_score <- sqrt(train1$avg_tag_score)
@@
 #=============================================
-#deviance residuals 
-train1$deviance <- residuals(final_model, type = "deviance")
-ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
+# deviance residuals 
+# check for outliers identify questions poorly predicted by the model
+
+train1$deviance <- residuals(full, type = "deviance")
+plotly::ggplotly(ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
   geom_point() + 
@@
   scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
-  ggtitle("Deviance Residuals")
+  ggtitle("Deviance Residuals"))
 # quite a few questions have a deviance residual of larger than 2.5 (use ggplotly to identify)
+
+# looking at points with deviance residuals > |2.5| (suggested in 417 notes)
+outliers <- train1[abs(train1$deviance) > 2.5,]
+# only 2 of these outliers were not answered
 
@@
 # schoenfeld residuals
-schoen <- as.data.frame(residuals(final_model, type = "schoenfeld"))
+schoen <- as.data.frame(residuals(full, type = "schoenfeld"))
 # complete event times sorted from shortest to longest
@@
 
+plotly::ggplotly(plot_schoen("ampmMorning")) # comptime 2020.89 (id = 390866) is pulling it up? 
+plotly::ggplotly(plot_schoen("new_categoryApple Product")) # same question
+plotly::ggplotly(plot_schoen("ps(text_length)8")) # same question
+plotly::ggplotly(plot_schoen("title_questionmarkTRUE")) # same question!!! 
 # plots indicate that new_user, ampm and a few others may have violated ph assumption
@@
 options(scipen=999)
-ph_test <- data.frame(predictors = rownames(cox.zph(final_model)$table), cox.zph(final_model)$table) 
+ph_test <- data.frame(predictors = rownames(cox.zph(full)$table), cox.zph(full)$table) 
 rownames(ph_test) = NULL
@@
 # score residuals
-score <- as.data.frame(residuals(final_model, type = "score"))
+score <- as.data.frame(residuals(full, type = "score"))
 

### 2017-08-25 model fitting/final_model.Rmd
moved to model fitting folder

---
title: "Final Model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
x <- oshitar::setup()
```

```{r}
# cross validation plan with k = 5
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
```

#### Variables including:

* new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + n_images + sqrt(avg_tag_score) + poly(text_length, degree = 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC')

```{r}
# building model on train1 data set
trainmodel <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC'), data = train1)

summary(trainmodel)
AIC(trainmodel) # 54303.59
```

##### Assessing residuals/PH assumption

```{r}
#----Martingale residuals----------------------------------------------
train1$mart <- residuals(trainmodel, type = "martingale")

ggplot(train1, aes(x = sqrt(avg_tag_score), y = mart)) + 
  geom_point() + 
  geom_smooth(method = "loess") + 
  ggtitle(paste("Martingale Residuals for sqrt(average_tag_score)")) + 
  scale_x_continuous("Average Tag Score (square root)") 
# functional form seems adequate

#----Deviance residuals------------------------------------------------
train1$deviance <- residuals(trainmodel, type = "deviance")
ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
  geom_point() + 
  scale_x_continuous("Question index") + 
  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
  ggtitle("Deviance Residuals")
# identify questions with residuals > |2.5| (questions poorly predicted by the model)

# examining all questions with > |2.5|
outliers <- train1 %>%
  dplyr::filter(abs(deviance) > 2.5)
# 112 questions in training data set have deviance residuals > 2.5 
# all were answered with time_until_answer < 1 hr (except for 2 which have time_until_answer > 1050 hours)

#----Schoenfeld residuals----------------------------------------------
schoen <- as.data.frame(residuals(trainmodel, type = "schoenfeld"))
schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)

# function to plot schoenfeld residuals for each predictor
plot_schoen <- function(var) {
  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Schoenfeld Residuals for", var)) + 
    scale_y_continuous("Residuals")
}
purrr::map(names(schoen)[-ncol(schoen)], plot_schoen)

# formal test of PH assumption 
options(scipen=999)
ph_test <- data.frame(predictors = rownames(cox.zph(trainmodel)$table), cox.zph(trainmodel)$table) 
rownames(ph_test) = NULL
ph_test <- ph_test %>% arrange(p) 
# linear term of text_length violates PH assumption (quadratic term doesn't)
# new_category violates, but stratifying on it decreases predictive ability

#----Score residuals--------------------------------------------------
# check for influential observations
score <- as.data.frame(residuals(trainmodel, type = "score"))

# function to plot score residuals
plot_score <- function(column) {
  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Score residuals for", column)) + 
    scale_y_continuous("Score Residuals") + 
    scale_x_continuous("Question index")
}

purrr::map(names(score), ~plot_score(.))
# tried removing influential questions and doing cross validation: models fit on data with influential questions removed didn't perform as well on the test data compared to models fit on full data

```

##### Cross validation

```{r}
# function to perform cross validation, vars should be string: "new_category + new_user..."
crossval <- function(vars, train, test) {
  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
  model <- survival::coxph(as.formula(formula), data = train)

  train[["predictions"]] <- predict(model, type = "risk")
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

  # predicting on test data
  test[["predictions"]] <- predict(model, newdata = test, type = "risk")

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             AIC = stats::AIC(metric1, k = 2),
                             Dxy = round(metric1$stats[9],2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

  # returns data frame with train/test metrics 
  statistics <- rbind(train_metrics, test_metrics)
  rownames(statistics) <- c("Training Data", "Test Data")
  return(statistics)
}

# function to average performance metrics, takes list of output from crossval
get_avgmetrics <- function(list) {
  avg <- rbind(train_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][1,]))), test_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][2,]))))
  return(avg)
}

# function to get average differences between training and test data metrics for each cv iteration
get_avgdiff <- function(list) {
  list_diff <- purrr::map(1:length(list), ~diff(as.matrix(list[[.]], lag = 1)))
  df <- plyr::ldply(list_diff, data.frame) %>%
    select(HR, Dxy, Concordance) %>%
    colMeans()
  return(df)
}
```

```{r}
vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC')"

trains <- list(train1, train2, train3, train4, train5)
tests <- list(test1, test2, test3, test4, test5)

(cv_results <- purrr::map2(trains, tests, ~crossval(vars, .x, .y)))

get_avgmetrics(cv_results)

get_avgdiff(cv_results) # metrics don't change that much between fitting model on training and test data sets
```

```{r, not using these functions}
# not using these functions
# function to delete overly influential questions (used in function below)
delete_influential <- function(var) {
  thresh <- mean(score[[var]]) + (sd(score[[var]]) * 30)
  delete <- which(abs(score[[var]]) > thresh)
  return(delete)
}

# fits model on training data, identifies overly influential questions, removes questions according to threshold, refits model to that data, uses that model to make predictions and computes performance metrics 
newcrossval <- function(vars, train, test) {
  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
  model <- survival::coxph(as.formula(formula), data = train)

  score <- as.data.frame(residuals(model, type = "score"))

  to_delete <- unique(unlist(purrr::map(names(score), ~delete_influential(.))))
  newdata <- train[-to_delete,]

  newmodel <- survival::coxph(as.formula(formula), data = newdata)

  newdata[["predictions"]] <- predict(newmodel, type = "risk")
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = newdata)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = newdata)$concordance)

  # predicting on test data
  test[["predictions"]] <- predict(newmodel, newdata = test, type = "risk")

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             AIC = stats::AIC(metric1, k = 2),
                             Dxy = round(metric1$stats[9],2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

  # returns data frame with train/test metrics 
  statistics <- rbind(train_metrics, test_metrics)
  rownames(statistics) <- c("Training Data", "Test Data")
  return(statistics)
}
```

##### Fitting the model to the full data set

```{r}
model <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC'), data = x)
summary(model)
AIC(model, k = 2) # 69830.21

surv_probs <- pec::predictSurvProb(model, times = c(0.5, 1, 10))
```

### 2017-08-26 model fitting/final_model.Rmd
predicted survival probabilities

@@
 ---
-title: "Final Model"
+title: "Final Model Analysis"
 output: html_document
@@
 knitr::opts_chunk$set(echo = TRUE)
-x <- oshitar::setup()
+x <- as.data.frame(oshitar::setup())
+library(survival); library(dplyr); library(rms)
 ```
 
-```{r}
+```{r, echo = FALSE}
 # cross validation plan with k = 5
@@
 
-#### Variables including:
+#### Variables:
 
@@
 
-```{r}
-# building model on train1 data set
-trainmodel <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC'), data = train1)
-
-summary(trainmodel)
-AIC(trainmodel) # 54303.59
+```{r, echo = FALSE}
+# building model on train1
+trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
+AIC(trainmodel, k = 2) # 54428.62
+trainmodel
 ```
@@
 
-```{r}
+```{r, echo = FALSE}
 #----Martingale residuals----------------------------------------------
@@
   dplyr::filter(abs(deviance) > 2.5)
-# 112 questions in training data set have deviance residuals > 2.5 
+# 117 questions in training data set have deviance residuals > 2.5 
 # all were answered with time_until_answer < 1 hr (except for 2 which have time_until_answer > 1050 hours)
@@
 ph_test <- ph_test %>% arrange(p) 
-# linear term of text_length violates PH assumption (quadratic term doesn't)
-# new_category violates, but stratifying on it decreases predictive ability
+# first term of device_length, Apple Product, Camera, Game Console violate PH (stratifying on new_category decreases predictive ability)
 
@@
 
-```{r}
+```{r, echo = FALSE}
 # function to perform cross validation, vars should be string: "new_category + new_user..."
@@
   formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
-  model <- survival::coxph(as.formula(formula), data = train)
+  model <- rms::cph(as.formula(formula), data = train)
 
-  train[["predictions"]] <- predict(model, type = "risk")
+  train[["predictions"]] <- exp(predict(model, type = "lp"))
   metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
@@
   # predicting on test data
-  test[["predictions"]] <- predict(model, newdata = test, type = "risk")
+  test[["predictions"]] <- exp(predict(model, newdata = test, type = "lp"))
 
@@
 
-```{r}
-vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC')"
+```{r, echo = FALSE}
+vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"
 
@@
 
-```{r}
-model <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC'), data = x)
-summary(model)
-AIC(model, k = 2) # 69830.21
+```{r, echo = FALSE}
+model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
 
-surv_probs <- pec::predictSurvProb(model, times = c(0.5, 1, 10))
+x$predictions <- predict(model, type = "lp")
+
+metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
+AIC(metric, k = 2) # 83023
+
+final_metrics <- data.frame(HR = exp(metric$coefficients), 
+                              LR = round(metric$stats[3],2), 
+                              pval = round(metric$stats[5],2), 
+                              AIC = stats::AIC(metric, k = 2),
+                              Dxy = round(metric$stats[9],2), 
+                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
+final_metrics # metrics on the full data set are similar to the metrics from cross validation
 ```
+
+```{r, echo = FALSE}
+# getting estimated survival probabilites
+surv_prob <- model$surv # list of 4 (one list for each stratification level)
+
+# allows you to get estimated survival probability at specific time (for each strat level)
+summary(survfit(model), time = c(0.5, 1, 3))
+
+# gives one survival probability (not split up into strat levels)
+# either specify newdata, linear.predictors or x
+# number on the rows of the surv matrix is the index 
+# function is very slow if full data set is used
+rms::survest(model, newdata = test1[1:3,], times = c(0.5, 1, 10), conf.int = FALSE)
+
+# using different function
+pec::predictSurvProb(model, newdata = test1[1:3,], times = c(0.5, 1, 10))
+
+# plot prediction error curves, calibration plots, c index, fix cv function, plot predicted survival curve ?? 
+# turn this into a function 
+```

### 2017-08-26 model fitting/cross_validation.Rmd
model fitting

@@
 ---
-title: "Predictive modeling with cross validation"
+title: "Predictive modeling with cross validation (this file is a mess)"
 author: "Lisa Oshita"
@@
 x <- oshitar::setup()
-library(survival)
-library(stringr)
-library(rebus)
-library(dplyr)
-library(stats)
-library(rms)
+library(survival); library(stringr); library(rebus); library(dplyr); library(stats); library(rms)
 ```
@@
 
-train1 <- x[splitPlan[[1]]$train, ]
-test1 <- x[splitPlan[[1]]$app, ]
+train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
 
-train2 <- x[splitPlan[[2]]$train, ]
-test2 <- x[splitPlan[[2]]$app, ]
+train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
 
-train3 <- x[splitPlan[[3]]$train, ]
-test3 <- x[splitPlan[[3]]$app, ]
+train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
 
-train4 <- x[splitPlan[[4]]$train, ]
-test4 <- x[splitPlan[[4]]$app, ]
+train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
 
-train5 <- x[splitPlan[[5]]$train, ]
-test5 <- x[splitPlan[[5]]$app, ]
+train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
 ```
@@
 full
+
+ugh <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + ampm + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 0, method = 'AIC') + pspline(text_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC'), data = train1)
+
+summary(ugh) 
+AIC(ugh, k = 2)
 ```
@@
 ```{r}
+# model I came to while trying to correct PH assumption violation 
+# stratified on ampm, orthogonal polynomial on text_length (new_category still violates PH)
+fullvars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + strata(ampm) + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + poly(text_length, 2) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3)"
+fullcv <- purrr::map2(trains, tests, ~crossval(fullvars, .x, .y))
+
 # turn avg_list into a data frame with rownames???
@@
 avg_list <- purrr::map(list, ~get_avgmetrics(.))
-avg_list
 ```
@@
 
-* Martingale residuals
-    + plot for each continuous predictor 
-    + assess adequacy of functional form of predictors, or suggest a potential form
-
-* Schoenfeld residuals
-    + one plot for each predictor 
-    + if loess curve is flat, proportional hazard assumption is not violated, doesn't depend on time. Distinct pattern indicates violation of this assumption
-    + **from the plots:** new_user, title_questionmark, num_freq_tags (1), ampm (Morning, Night), weekday (Thursday, Saturday), new_user*AMPM (morning, night) may violate PH assumption 
-* Score residuals
-    + check for influential observations. ID quesitons who's predictor values highly effect parameter estimates
-    + plot for each predictor 
-* **figure out how to identify certain points on ggplots**
-
 ```{r, residuals, echo = FALSE}
-full <- coxph(Surv(time_until_answer, answered) ~ strata(new_category) + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + strata(ampm) + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + poly(text_length, 2) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = train1)
+full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + strata(ampm) + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + poly(text_length, 2) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = train1)
 # If i fit text_length with poly (orthogonal polynomial), text_length doesn't violate ph anymore 
@@
 #martingale residuals
+# plot for each continuous predictor, assess adequacy of functional form of predictors, or suggest a potential form 
 train1$mart <- residuals(full, type = "martingale")
@@
 # looking at points with deviance residuals > |2.5| (suggested in 417 notes)
-outliers <- train1[abs(train1$deviance) > 2.5,]
+
 # only 2 of these outliers were not answered
@@
 #=============================================
+
+spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
 # schoenfeld residuals
@@
     geom_point() + 
-    geom_smooth() + 
+    geom_smooth(method = "loess") + 
     ggtitle(paste("Schoenfeld Residuals for", var)) + 
@@
 options(scipen=999)
-ph_test <- data.frame(predictors = rownames(cox.zph(full)$table), cox.zph(full)$table) 
+ph_test <- data.frame(predictors = rownames(cox.zph(spline5)$table), cox.zph(spline5)$table) 
 rownames(ph_test) = NULL
@@
   arrange(p)
-ph_test
+
+# plots of variables that violated PH assumption in cox.zph test
+plot_schoen("new_categoryApple Product")
+plot_schoen("new_categoryElectronics")
+plot_schoen("new_categoryCamera")
+plot_schoen("new_categoryGame Console")
+plot_schoen("title_questionmarkTRUE")
+
 #=============================================
-# score residuals
+# score residuals: check for influential observations. ID quesitons who's predictor values highly effect
 score <- as.data.frame(residuals(full, type = "score"))

### 2017-08-26 model fitting/final_model.Rmd
calibration/validation with rms and pec package

@@
 
-```{r, echo = FALSE}
+```{r, cross validation plan, echo = FALSE}
 # cross validation plan with k = 5
@@
                               pval = round(metric$stats[5],2),
+                              R2 = round(metric$stats[8], 2),
                               AIC = stats::AIC(metric, k = 2),
@@
 get_avgdiff(cv_results) # metrics don't change that much between fitting model on training and test data sets
+```
+
+```{r, echo = FALSE}
+# validation and calibration with rms package
+
+valmodel <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
+
+validation <- rms::validate(calmodel, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
+validation
+# output: 
+# Dxy = Somers' Dxy (2 ∗ (C − 0.5), where C is the concordance probability)
+# R2: RN2 index
+# Slope: Calibration slope (slope of predicted log odds vs true log odds) optimism value is a value of overfitting
+# D: Discrimination index — likelihood ratio χ2 divided by the sample size
+# U: Unreliability index — unitless index of how far the logit calibration curve intercept and slope are from (0, 1)
+# Q: Logarithmic accuracy score - scaled version of the log-likelihood achieved by the predictive model
+# g: g index (?)
+
+# validate the model for calibration accuracy in predicting probability at 0.5 hours 
+calibration <- rms::calibrate(calmodel, method = "crossvalidation", B = 100, bw = FALSE, u = 0.5)
+calibration
+plot(calibration)
+# predicts and calibrates at 0.5 hours for each iteration of the bootstrap
+# plot gives mean absolute error in predictions, mean squared error, and the 0.9 quantile of the absolute error
+# error =  difference between the predicted values and the corresponding bias-corrected calibrated values
+
 ```
@@
 
-x$predictions <- predict(model, type = "lp")
+x$predictions <- exp(predict(model, type = "lp"))
 
@@
 ```
+
+##### Getting estimated survival probabilities
 
@@
 pec::predictSurvProb(model, newdata = test1[1:3,], times = c(0.5, 1, 10))
-
-# plot prediction error curves, calibration plots, c index, fix cv function, plot predicted survival curve ?? 
-# turn this into a function 
 ```

### 2017-08-27 literature reviews/literature_reviews.tex
set up/learned about tex and mendeley
first draft of literature reviews/introduction

@@
 
-This really cool paper about stackoverflow said something cool \citep{Ponzanelli2014}.
+    Community driven question and answer forums are becoming increasingly popular and more widely used.
+These forums provide a way for anyone with a question to get an answer no matter where they are, and from people of all backgrounds and levels of expertise.
+One such forum is iFixit's Answers.
+This forum features questions regarding the repair of devices.
+Devices range anywhere from a broken zipper or a cracked iPhone screen, to even an overheated engine.
+The questions asked on this forum cover an expansive range of devices--almost 9,000 with over 100,000 solutions and answers.
+Creating a community like this allows individuals to learn how to fix their broken devices themselves, and save money.
+If they run into any problems, they can always trust that they have a large community of people they can turn to for help.
+Thus it's important, for both the individuals as well as the forum, that askers get prompt answers.
+Fast respone times will drive up user engagement and generate more traffice, which in turn is great for the reputation and longevity of the forum.
+As such, investigation of response times would be both beneficial and informative.
+Analysis can reveal factors within the forum that affect how quickly questions get answers.
+Suggestions for how users can ask questions to minimize answer times, as well as suggestions for how the forum design can be improved, can be derived from such analysis.
 
-\cite{Ponzanelli2014} said this awesome thing.
+    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model (?
+is that what it's called) to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
+
+    \citep{Mamykina2011} found that the swift answer times of Stack Overflow's community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.
+
+    \citep{Asaduzzaman2013} analyzed unanswered questions on Stack Overflow to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.
+
+    However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers.
+A majority of the research focuses on assessing and predicting the question and answer quality.
+As such, there is a need for further analysis of resposne times in these forums.
+This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum.
+It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the survival probability of a question.
 

### 2017-08-27 model fitting/final_model.Rmd
started writing function to predict survival probabilities

@@
 
-* new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + n_images + sqrt(avg_tag_score) + poly(text_length, degree = 2) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + pspline(newline_ratio, df = 0, method = 'AIC')
+* new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, degree = 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)
+* device_length has 5 knots since hypothesized that it's a better predictor, others only have 4 (reccomended in Regression Modelling Strategies text)
 
@@
 
-```{r, echo = FALSE}
+```{r, functions for cv, echo = FALSE}
 # function to perform cross validation, vars should be string: "new_category + new_user..."
@@
 get_avgmetrics(cv_results)
-
 get_avgdiff(cv_results) # metrics don't change that much between fitting model on training and test data sets
@@
 
+##### Validation with rms::validate for Somers’ Dxy rank correlation between pre-dicted log hazard and observed survival time, + slope shrinkage
+
+###### output: 
+* Dxy = Somers' Dxy (2 ∗ (C − 0.5), where C is the concordance probability)
+* R2: RN2 index
+* Slope: Calibration slope (slope of predicted log odds vs true log odds) optimism value is a value of overfitting
+* D: Discrimination index — likelihood ratio χ2 divided by the sample size
+* U: Unreliability index — unitless index of how far the logit calibration curve intercept and slope are from (0, 1)
+* Q: Logarithmic accuracy score - scaled version of the log-likelihood achieved by the predictive model
+* g: g index (?)
+
+###### interpreting:
+* optimism is small- model is a good fit (?)
+* slope shrinkage = 0.0163, indicates over-fitting not present
+
 ```{r, echo = FALSE}
-# validation and calibration with rms package
-
 valmodel <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
 
-validation <- rms::validate(calmodel, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
+validation <- rms::validate(valmodel, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
 validation
-# output: 
-# Dxy = Somers' Dxy (2 ∗ (C − 0.5), where C is the concordance probability)
-# R2: RN2 index
-# Slope: Calibration slope (slope of predicted log odds vs true log odds) optimism value is a value of overfitting
-# D: Discrimination index — likelihood ratio χ2 divided by the sample size
-# U: Unreliability index — unitless index of how far the logit calibration curve intercept and slope are from (0, 1)
-# Q: Logarithmic accuracy score - scaled version of the log-likelihood achieved by the predictive model
-# g: g index (?)
 
-# validate the model for calibration accuracy in predicting probability at 0.5 hours 
+```
+
+##### Validating the model for calibration accuracy with rms::calibrate
+
+* outputs mean absolute error in predictions, mean squared error, and the 0.9 quantile of the absolute error
+* error =  difference between the predicted values and the corresponding bias-corrected calibrated values
+
+```{r, echo = FALSE}
+# calibration accuracy in predicting probability at 0.5 hours (predicts and calibrates at 0.5 hours for each iteration of the bootstrap?)
 calibration <- rms::calibrate(calmodel, method = "crossvalidation", B = 100, bw = FALSE, u = 0.5)
@@
 plot(calibration)
-# predicts and calibrates at 0.5 hours for each iteration of the bootstrap
-# plot gives mean absolute error in predictions, mean squared error, and the 0.9 quantile of the absolute error
-# error =  difference between the predicted values and the corresponding bias-corrected calibrated values
-
 ```
@@
 ```{r, echo = FALSE}
-# getting estimated survival probabilites
 surv_prob <- model$surv # list of 4 (one list for each stratification level)
@@
 
-# gives one survival probability (not split up into strat levels)
 # either specify newdata, linear.predictors or x
@@
 pec::predictSurvProb(model, newdata = test1[1:3,], times = c(0.5, 1, 10))
+
+times <- sort(unique(x$time_until_answer))
+
+pec::plotPredictSurvProb(model, newdata = x[1:4,], times = times) # this is ugly, figure out how to do this in ggplot?
 ```
+
+##### Describing the final model
+
+* predicted survival curve + curves for certain variables (rms functions to do this keep outputting errors about datadist)
+* nomograms?
+
+##### Function to output survival probabilities
+
+* input data set with any combination of predictors + times to predict on 
+* output corresponding survival probabilities
+
+```{r}
+# input vector of times to predict on + data set to be used in predictions
+# function runs really slowly because it has to set up the data + fit the model everytime 
+# outputs matrix of predicted survival 
+# also include some kind of performance metric? measure of how accurately its predicting 
+# sets up variables needed in the new data 
+get_survival <- function(times, data) {
+  newdata <- oshitar::variable_setup(data)
+  x <- oshitar::setup()
+  model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
+  surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
+  return(surv_probs)
+}
+
+get_survival(times = c(0.5, 1, 10), data = out)
+
+```

### 2017-08-27 model fitting/cross_validation.Rmd
deleted code

@@
 train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
-
 train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
-
 train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
-
 train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
-
 train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
@@
 AIC(model, k = 2) # 64977.65
-# with cph fits, keep getting errors with predict function 
 ```
@@
 ```{r}
-# working with model_spline2 (model with all splines)
 train1$predictions <- predict(object = full , type = "risk")
@@
 
-### FINAL MODEL (?)
-```{r}
-# final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
-#     contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
-#     text_all_lower + update + prior_effort + ampm + weekday + 
-#     pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
-#     df = 0, method = 'AIC'), data = x)
-# summary(final)
-# AIC(final, k = 2) # 82957.53
-
-full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + ampm + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + pspline(text_length, 3) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = x)
-AIC(full, k = 2) # 82974.66
-
-x$predictions <- predict(full, type = "risk")
-performance <- cph(Surv(time_until_answer, answered) ~ predictions, data = x)
-AIC(performance, k = 2) # 83243.04
-
-final_metrics <- data.frame(HR = exp(performance$coefficients), 
-                              LR = round(performance$stats[3],2), 
-                              pval = round(performance$stats[5],2), 
-                              AIC = stats::AIC(performance, k = 2),
-                              Dxy = round(performance$stats[9],2), 
-                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
-final_metrics
-# performance metrics on entire data set are not different from cross validation 
-```
-
 ```{r}
@@
 ```
-
-### residuals, PH assumption
-
-```{r, residuals, echo = FALSE}
-full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + strata(ampm) + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + poly(text_length, 2) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = train1)
-# If i fit text_length with poly (orthogonal polynomial), text_length doesn't violate ph anymore 
-#=============================================
-#martingale residuals
-# plot for each continuous predictor, assess adequacy of functional form of predictors, or suggest a potential form 
-train1$mart <- residuals(full, type = "martingale")
-train1$sqrt_score <- sqrt(train1$avg_tag_score)
-
-ggplot(train1, aes(x = sqrt_score, y = mart)) + 
-  geom_point() + 
-  geom_smooth() + 
-  ggtitle(paste("Martingale Residuals for device_length")) + 
-  scale_x_continuous("Device_length")
-# what do I assess for spline variables?
-
-#=============================================
-# deviance residuals 
-# check for outliers identify questions poorly predicted by the model
-
-train1$deviance <- residuals(full, type = "deviance")
-plotly::ggplotly(ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
-  geom_point() + 
-  scale_x_continuous("Question index") + 
-  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
-  ggtitle("Deviance Residuals"))
-# quite a few questions have a deviance residual of larger than 2.5 (use ggplotly to identify)
-
-# looking at points with deviance residuals > |2.5| (suggested in 417 notes)
-
-# only 2 of these outliers were not answered
-
-#=============================================
-
-spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
-# schoenfeld residuals
-schoen <- as.data.frame(residuals(full, type = "schoenfeld"))
-# complete event times sorted from shortest to longest
-schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)
-
-plot_schoen <- function(var) {
-  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
-    geom_point() + 
-    geom_smooth(method = "loess") + 
-    ggtitle(paste("Schoenfeld Residuals for", var)) + 
-    scale_y_continuous("Residuals")
-}
-names <- names(schoen)[-ncol(schoen)]
-purrr::map(names, plot_schoen)
-
-plotly::ggplotly(plot_schoen("ampmMorning")) # comptime 2020.89 (id = 390866) is pulling it up? 
-plotly::ggplotly(plot_schoen("new_categoryApple Product")) # same question
-plotly::ggplotly(plot_schoen("ps(text_length)8")) # same question
-plotly::ggplotly(plot_schoen("title_questionmarkTRUE")) # same question!!! 
-# plots indicate that new_user, ampm and a few others may have violated ph assumption
-
-#=============================================
-# formal test of PH assumption
-options(scipen=999)
-ph_test <- data.frame(predictors = rownames(cox.zph(spline5)$table), cox.zph(spline5)$table) 
-rownames(ph_test) = NULL
-ph_test <- ph_test %>%
-  arrange(p)
-
-# plots of variables that violated PH assumption in cox.zph test
-plot_schoen("new_categoryApple Product")
-plot_schoen("new_categoryElectronics")
-plot_schoen("new_categoryCamera")
-plot_schoen("new_categoryGame Console")
-plot_schoen("title_questionmarkTRUE")
-
-#=============================================
-# score residuals: check for influential observations. ID quesitons who's predictor values highly effect
-score <- as.data.frame(residuals(full, type = "score"))
-
-# function to plot score residuals
-plot_score <- function(column) {
-  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
-    geom_point() + 
-    geom_smooth() + 
-    ggtitle(paste("Score residuals for", column)) + 
-    scale_y_continuous("Score Residuals") + 
-    scale_x_continuous("Question index")
-}
-columns <- names(score)
-purrr::map(columns, plot_score)
-# score residuals show that there are quite a few points that may be influential (check with ggplotly)
-```

### 2017-08-27 Hours.Rmd
updated hours

@@
 8/24/2017 | 1.5 | 7:30-9:00PM | Residuals, checked PH assumption, tried to address PH assumption violations 
+8/25/2017 | 3 | 8:15-11:15AM | Addressed PH assumption violations, meeting with Dr. Pileggi
+8/25/2017 | 4.5 | 12:00-4:30PM | Worked with final model, checked residuals/PH, cross validation, fitted to the full data set
+8/25/2017 | 3 | 5:30-8:30PM | Ran into problems trying to predict survival probabilities 
+8/26/2017 | 3.25 | 9:15-12:30PM | Predicted survival probabilites, calibration/validation with rms package, started writing function to predict
+8/26/2017 | 6 | 3:00-9:00PM | Tried to make variable_setup function more reproducible, ran into problems, worked on Mendeley and tex
 

### 2017-08-27 model fitting/final_model.Rmd
fixed get_survival function

@@
 knitr::opts_chunk$set(echo = TRUE)
-x <- as.data.frame(oshitar::setup())
+x <- oshitar::setup()
 library(survival); library(dplyr); library(rms)
+```
+
+```{r}
+dir <- file.path(getwd(),"data")
+out <- read.csv(system.file("extdata/answers_data.csv", package = "oshitar"))
+
+finaldata <- oshitar::variable_setup(out)
+identical(finaldata$contain_answered, x$contain_answered)
+
+write.csv(finaldata, file = "final_data.csv")
 ```
@@
 
-##### Validation with rms::validate for Somers’ Dxy rank correlation between pre-dicted log hazard and observed survival time, + slope shrinkage
+##### Validation with rms::validate for Somers’ Dxy rank correlation between predicted log hazard and observed survival time + slope shrinkage
 
@@
 validation
-
 ```
@@
 # input vector of times to predict on + data set to be used in predictions
-# function runs really slowly because it has to set up the data + fit the model everytime 
-# outputs matrix of predicted survival 
+# function runs really slow
+# outputs matrix of predicted survival probabilities 
 # also include some kind of performance metric? measure of how accurately its predicting 
@@
 get_survival <- function(times, data) {
+  # setting up necessary variables in new data 
   newdata <- oshitar::variable_setup(data)
-  x <- oshitar::setup()
+
+  # imports data to build model on 
+  x <- read.csv("final_data.csv", head = TRUE)
+  # builds model 
   model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
+  # gets survival probabilities 
   surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
@@
 
-get_survival(times = c(0.5, 1, 10), data = out)
-
 ```

### 2017-08-27 model fitting/final_model.Rmd
plotted predicted survival estimates

@@
 knitr::opts_chunk$set(echo = TRUE)
-x <- oshitar::setup()
+x <- read.csv("final_data.csv", head = TRUE)
 library(survival); library(dplyr); library(rms)
-```
-
-```{r}
-dir <- file.path(getwd(),"data")
-out <- read.csv(system.file("extdata/answers_data.csv", package = "oshitar"))
-
-finaldata <- oshitar::variable_setup(out)
-identical(finaldata$contain_answered, x$contain_answered)
-
-write.csv(finaldata, file = "final_data.csv")
 ```
@@
 ```{r, echo = FALSE}
-# building model on train1
-trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
-AIC(trainmodel, k = 2) # 54428.62
+# building model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
+trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
+AIC(trainmodel, k = 2) # 54421.53
 trainmodel
@@
                              pval = round(metric1$stats[5],2), 
+                             R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric1, k = 2),
@@
 ```{r, echo = FALSE}
-vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"
+vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"
 
@@
 ###### output:
+
 * Dxy = Somers' Dxy (2 ∗ (C − 0.5), where C is the concordance probability)
@@
 ###### interpreting:
+
 * optimism is small- model is a good fit (?)
@@
 ```{r, echo = FALSE}
-valmodel <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
+dd = datadist(x)
+options(datadist = "dd")
 
-validation <- rms::validate(valmodel, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
+final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
+
+validation <- rms::validate(final, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
 validation
@@
 # calibration accuracy in predicting probability at 0.5 hours (predicts and calibrates at 0.5 hours for each iteration of the bootstrap?)
-calibration <- rms::calibrate(calmodel, method = "crossvalidation", B = 100, bw = FALSE, u = 0.5)
+calibration <- rms::calibrate(final, method = "crossvalidation", B = 100, bw = FALSE, u = 0.5)
 calibration
@@
 ```{r, echo = FALSE}
-model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
-
-x$predictions <- exp(predict(model, type = "lp"))
+x$predictions <- exp(predict(final, type = "lp"))
 
@@
 ```{r, echo = FALSE}
-surv_prob <- model$surv # list of 4 (one list for each stratification level)
+surv_prob <- final$surv # list of 4 (one list for each stratification level)
 
 # allows you to get estimated survival probability at specific time (for each strat level)
-summary(survfit(model), time = c(0.5, 1, 3))
+summary(survfit(final), time = c(0.5, 1, 3))
 
@@
 # function is very slow if full data set is used
-rms::survest(model, newdata = test1[1:3,], times = c(0.5, 1, 10), conf.int = FALSE)
+rms::survest(final, newdata = test1[1:3,], times = c(0.5, 1, 10), conf.int = FALSE)
 
 # using different function
-pec::predictSurvProb(model, newdata = test1[1:3,], times = c(0.5, 1, 10))
+pec::predictSurvProb(final, newdata = test1[1:3,], times = c(0.5, 1, 10))
+```
+
+##### Estimated survival probability curves
+
+* predicted survival curve + curves for certain variables (rms functions keep outputting errors about data dist)
+* nomograms?
+
+```{r}
+# plots log hazard for each variable 
+plots <- ggplot(Predict(final)) # output is messy, figure out how to access each plot separately
 
 times <- sort(unique(x$time_until_answer))
+pec::plotPredictSurvProb(final, newdata = x[1:4,], times = times) # ugly output
 
-pec::plotPredictSurvProb(model, newdata = x[1:4,], times = times) # this is ugly, figure out how to do this in ggplot?
+# must specify a variable 
+rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE)
+
+# plot the effects of predictors
+plot(Predict(final, new_category))
+plot(Predict(final, new_user))
+plot(Predict(final, new_user, new_category))
+
 ```
-
-##### Describing the final model
-
-* predicted survival curve + curves for certain variables (rms functions to do this keep outputting errors about datadist)
-* nomograms?
 
@@
 # outputs matrix of predicted survival probabilities 
-# also include some kind of performance metric? measure of how accurately its predicting 
 # sets up variables needed in the new data 
@@
 
+get_survival(times = c(0.5, 1, 10), data = out[1:10,])
 ```

### 2017-08-28 model fitting/final_model.Rmd
worked with survplot function

@@
 
+x$text_length2 <- x$text_length**2 # for future use
+x$sqrt_tag_score <- sqrt(x$avg_tag_score)
+
 final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
+final
 
@@
 
-##### Fitting the model to the full data set
+##### Assessing model fit on full data
+
+* significant predictors (pvalues < 0.05):
+    + new_category: Apple Product, Camera, game console, other, pc, vehicle
+    + new_user
+    + contain_unanswered
+    + text_all_lower
+    + update
+    + prior_effort 
+    + weekday: Thursday
+    + avg_tag_score (sqrt)
+    + spline on avg_tag_length
+* Interpretations of signficant predictors
+    + Apple Product: (beta = 0.93) log hazard of getting answered for apple products is 0.93 higher than for android/othe phones, controlling for other predictors.
+(HR = exp(beta) = 2.554) Hazard of getting answered is 155% higher for apple products compared to android/other phones, controlling for other predictors
+    + avg_tag_score (sqrt): (beta = 2.8764) log hazard of getting answered increases by 2.88 for every 1 unique increase in the square root of avg_tag_score, adjusting for other predictors.
+HR = 17.75, the hazard of getting answered increases by 167.5% for each one unit increase in the square root of the average tag score, adjusting for other predictors
 
@@
 pec::predictSurvProb(final, newdata = test1[1:3,], times = c(0.5, 1, 10))
+# interpretation:
+#   for question 380, the probability that it remains unanswered beyond 30 minutes is 0.53
+#   for question 2195, the probability that it remains unanswered byond 30 minutes is 0.85
 ```
@@
 ```{r}
-# plots log hazard for each variable 
-plots <- ggplot(Predict(final)) # output is messy, figure out how to access each plot separately
+# plots log hazard for individual predictors 
+ggplot(Predict(final, new_category))  
+ggplot(Predict(final, device_length))
+ggplot(Predict(final, text_length))
+ggplot(Predict(final, avg_tag_length))
+ggplot(Predict(final, newline_ratio))
 
@@
 # must specify a variable 
-rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE)
-
-# plot the effects of predictors
-plot(Predict(final, new_category))
-plot(Predict(final, new_user))
-plot(Predict(final, new_user, new_category))
-
+rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE, xlab = "Hours")
+rms::survplot(final, new_category, time.inc = 100, col = 1:length(levels(x$new_category)), xlab = "hour")
+rms::survplot(final, new_user = 0, conf.int = .95, time.inc = 100) # can change variable it plots 
 ```
@@
   newdata <- oshitar::variable_setup(data)
-
   # imports data to build model on 

### 2017-08-28 app/server.R
started making shiny app to compute survival pr

@@ -1,0 +1,31 @@
+library(shiny)
+library(survival)
+library(rms)
+x <- read.csv("data/final_data.csv", head = TRUE)
+model <-   model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
+                               contain_unanswered + contain_answered + title_questionmark + 
+                               title_beginwh + text_contain_punct + text_all_lower + update + 
+                               greeting + gratitude + prior_effort + weekday + strat(ampm) + 
+                               sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + 
+                               rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
+                             data = x, x = TRUE, 
+                             y = TRUE, surv = TRUE)
+
+shinyServer(
+  function(input, output) {
+    
+    output$contents <- renderTable({
+      req(input$file1)
+      df <- read.csv(input$file1$datapath,
+                     header = input$header)
+      
+      if(input$disp == "head") {
+        return(head(df))
+      }
+      else {
+        return(df)
+      }
+    })
+})
+
+

### 2017-08-28 app/ui.R

@@ -1,0 +1,28 @@
+library(shiny)
+
+# Define UI for application that draws a histogram
+shinyUI(fluidPage(
+  
+  # Application title
+  titlePanel("Survival Probabilities"),
+  
+  # Sidebar with a slider input for the number of bins
+  sidebarLayout(
+    
+    sidebarPanel(
+      fileInput("file1", "Choose CSV file",
+                multiple = TRUE,
+                accept = c("text/csv",
+                           "text/comma-separated-values,text/plain",
+                           ".csv")),
+      tags$hr(),
+      
+      checkboxInput("header", "Header", TRUE),
+      
+      tags$hr()
+      ),
+    mainPanel(
+      tableOutput("contents")
+    )
+  )
+))

### 2017-08-28 app/server.R
added to code for shiny app

@@ -10,22 +10,57 @@ model <-   model <- cph(Surv(time_until_answer, answered) ~ new_category + new_u
                                rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                              data = x, x = TRUE, 
                              y = TRUE, surv = TRUE)
-
+#------------------------------------------------------------------------------------------------
 shinyServer(
   function(input, output) {
     
+    #-------Renders head of input data ---------------------------------------
     output$contents <- renderTable({
-      req(input$file1)
-      df <- read.csv(input$file1$datapath,
-                     header = input$header)
       
-      if(input$disp == "head") {
-        return(head(df))
+      req(input$file1)
+      df <- read.csv(input$file1$datapath)
+      data <- oshitar::variable_setup(df)
+      return(head(data))
       }
-      else {
-        return(df)
+      )
+    
+    #-------Renders summary statistics of input data-------------------------- 
+    output$sum_stats <- renderTable({
+      
+      if(input$summary == TRUE) {
+        req(input$file1)
+        df <- read.csv(input$file1$datapath)
+        data <- oshitar::variable_setup(df)
+        
+        summarydf <- data.frame(num = nrow(data), 
+                            median_time = round(median(data$time_until_answer),2), 
+                            mean = round(mean(data$time_until_answer),2))
+        return(summarydf)
       }
-    })
+    }
+    )
+    
+    #-------Renders predicted survival probabilities-------------------------- 
+    timesInput <- eventReactive(input$predict, {
+      as.numeric(stringr::str_split(input$times, pattern = ",", simplify = TRUE))
+    }
+    )
+
+    output$surv_probs <- renderPrint({
+      req(input$file1)
+      df <- read.csv(input$file1$datapath)
+      data <- oshitar::variable_setup(df)
+      
+      predictions <- pec::predictSurvProb(model, newdata = data_touse, times = timesInput())
+      return(predictions)
+      }
+      )
 })
+
+
+      
+
+
+
 
 

### 2017-08-28 app/ui.R

@@ -1,28 +1,48 @@
 library(shiny)
 
-# Define UI for application that draws a histogram
 shinyUI(fluidPage(
   
-  # Application title
-  titlePanel("Survival Probabilities"),
+  # App title
+  titlePanel("Predict Survival Probabilities"),
   
-  # Sidebar with a slider input for the number of bins
+  # Sidebar layout with input and output definitions
   sidebarLayout(
     
+    # Sidebar panel for inputs
     sidebarPanel(
-      fileInput("file1", "Choose CSV file",
+      
+      # Input: Select a file
+      fileInput("file1", "Choose CSV File",
                 multiple = TRUE,
                 accept = c("text/csv",
                            "text/comma-separated-values,text/plain",
                            ".csv")),
-      tags$hr(),
+
+      checkboxInput("summary", "Display Summary", FALSE),
       
-      checkboxInput("header", "Header", TRUE),
+      tags$hr(), # -------------
       
-      tags$hr()
-      ),
+      # Input: times at which to predict survival probabilities
+      textInput("times", "Time(s) to Predict:", value = "", placeholder = "ex: 0.5, 1, 10"),
+      
+      actionButton("predict", "Predict"),
+      
+      tags$hr(),# -------------
+      
+      # Summary output
+      tableOutput("sum_stats")
+      
+    ),
+    
+    # Main panel for displaying outputs ----
     mainPanel(
-      tableOutput("contents")
+      
+      tabsetPanel(
+        tabPanel("Calculate Survival Probability", verbatimTextOutput("surv_probs")),
+        tabPanel("Input Data", tableOutput("contents"))
+      )
+      
     )
+    
   )
 ))

### 2017-08-28 model fitting/final_model.Rmd
moved datadist to correct place

@@
 x <- read.csv("final_data.csv", head = TRUE)
+x <- as.data.frame(x)
 library(survival); library(dplyr); library(rms)
@@
 # building model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
+dd = datadist(x)
+options(datadist = "dd")
+
 trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
@@
 ```{r, echo = FALSE}
-dd = datadist(x)
-options(datadist = "dd")
-
 x$text_length2 <- x$text_length**2 # for future use

### 2017-08-31 model fitting/final_model.Rmd
reorganized code

--- 2017-08-28 model fitting/final_model.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE)
-x <- read.csv("final_data.csv", head = TRUE)
+
+```
+
+```{r}
+dir <- file.path(getwd(),"data")
+out <- read.csv(file.path(dir, "answers_data.csv"))
+x <- oshitar::variable_setup(out)
+
 library(survival); library(dplyr); library(rms)
@@
 ```{r, echo = FALSE}
-# building model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
+# build model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
+
 trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
-AIC(trainmodel, k = 2) # 54421.53
+AIC(trainmodel, k = 2) # 54421.88
 trainmodel
@@
 
-```{r, functions for cv, echo = FALSE}
+```{r, functions for cv, include = FALSE}
 # function to perform cross validation, vars should be string: "new_category + new_user..."
@@
 ```{r, echo = FALSE}
-dd = datadist(x)
+dd <- datadist(x)
 options(datadist = "dd")
-
-x$text_length2 <- x$text_length**2 # for future use
-x$sqrt_tag_score <- sqrt(x$avg_tag_score)
-
-final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)
+final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
+                               contain_unanswered + contain_answered + title_questionmark + 
+                               title_beginwh + text_contain_punct + text_all_lower + update + 
+                               greeting + gratitude + prior_effort + weekday + strat(ampm) + 
+                               sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + 
+                               rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
+                             data = x, x = TRUE, 
+                             y = TRUE, surv = TRUE)
 final
+AIC(final, k = 2) # 69945.32
 
@@
 
-```{r, not using these functions}
+```{r, not using these functions, include = FALSE}
 # not using these functions
@@
 metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
-AIC(metric, k = 2) # 83023
+AIC(metric, k = 2) # 83125.55
 
@@
 rms::survest(final, newdata = test1[1:3,], times = c(0.5, 1, 10), conf.int = FALSE)
+rms::survest(final, times = c(0.5, 1, 10), conf.int = FALSE)
 
@@
 # plots log hazard for individual predictors 
+dd = datadist(x)
+options(datadist="dd")
+
 ggplot(Predict(final, new_category))  
@@
 times <- sort(unique(x$time_until_answer))
-pec::plotPredictSurvProb(final, newdata = x[1:4,], times = times) # ugly output
+pec::plotPredictSurvProb(final, newdata = x[1:4,], times = c(1, 10, 12, 13, 14)) # ugly output
 
@@
 rms::survplot(final, ampm, time.inc = 100, col = 1:4, n.risk = TRUE, xlab = "Hours")
-rms::survplot(final, new_category, time.inc = 100, col = 1:length(levels(x$new_category)), xlab = "hour")
+rms::survplot(final, new_category, time.inc = 100, col = 1:length(levels(x$new_category)), xlab = "hour", label.curves=list(keys=1:length(levels(x$new_category))))
 rms::survplot(final, new_user = 0, conf.int = .95, time.inc = 100) # can change variable it plots 
 ```
-
-##### Function to output survival probabilities
-
-* input data set with any combination of predictors + times to predict on 
-* output corresponding survival probabilities
-
-```{r}
-# input vector of times to predict on + data set to be used in predictions
-# function runs really slow
-# outputs matrix of predicted survival probabilities 
-# sets up variables needed in the new data 
-get_survival <- function(times, data) {
-  # setting up necessary variables in new data 
-  newdata <- oshitar::variable_setup(data)
-  # imports data to build model on 
-  x <- read.csv("final_data.csv", head = TRUE)
-  # builds model 
-  model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE)
-  # gets survival probabilities 
-  surv_probs <- pec::predictSurvProb(model, newdata = newdata, times)
-  return(surv_probs)
-}
-
-get_survival(times = c(0.5, 1, 10), data = out[1:10,])
-```

### 2017-08-31 app/server.R
created shiny app

@@ -1,18 +1,40 @@
-library(shiny)
-library(survival)
-library(rms)
-x <- read.csv("data/final_data.csv", head = TRUE)
-model <-   model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
+library(shiny); library(survival); library(rms)
+
+# data to build the cox regression model on 
+x <- as.data.frame(read.csv("data/finaldata.csv", head = TRUE)); x <- x[,-1]
+
+model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                                contain_unanswered + contain_answered + title_questionmark + 
                                title_beginwh + text_contain_punct + text_all_lower + update + 
                                greeting + gratitude + prior_effort + weekday + strat(ampm) + 
-                               sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + 
+                               sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + 
                                rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                              data = x, x = TRUE, 
                              y = TRUE, surv = TRUE)
-#------------------------------------------------------------------------------------------------
+
+#-----------------------------------------------------------------------------
 shinyServer(
   function(input, output) {
+    
+    #-------Renders summary statistics of input data-------------------------- 
+    output$sum_stats <- renderTable({
+      req(input$file1)
+      df <- as.data.frame(read.csv(input$file1$datapath)) # look into reactive function
+      data <- oshitar::variable_setup(df)
+        
+      summarydf <- data.frame(nrow(data), 
+                              round(median(data$time_until_answer),2), 
+                              round(sum(data$answered)/nrow(data),2),
+                              round(mean(data$time_until_answer),2),
+                              round(max(data$time_until_answer), 2),
+                              round(min(data$time_until_answer), 2)
+                              )
+      colnames(summarydf) <- c("Number of Questions", "Proportion Answered","Median Answer Time (hrs)",
+                               "Mean Answer Time", "Longest Answer Time", "Shortest Answer Time"
+                               )
+      return(summarydf)
+    }
+    )
     
     #-------Renders head of input data ---------------------------------------
     output$contents <- renderTable({
@@ -21,24 +43,24 @@ shinyServer(
[…]

### 2017-08-31 app/ui.R

@@ -3,46 +3,73 @@ library(shiny)
 shinyUI(fluidPage(
   
   # App title
-  titlePanel("Predict Survival Probabilities"),
-  
-  # Sidebar layout with input and output definitions
-  sidebarLayout(
+  titlePanel("Predict Failure Probabilities"),
+  helpText("Failure is defined as the event of a question recieving an answer. This app predicts the 
+           probability that a question posted on iFixit's Answers forum fails, or recieves an answer 
+           before a certain time. The time (in hours) is specified by the user."),
     
-    # Sidebar panel for inputs
-    sidebarPanel(
+  tabsetPanel(
       
-      # Input: Select a file
-      fileInput("file1", "Choose CSV File",
-                multiple = TRUE,
-                accept = c("text/csv",
-                           "text/comma-separated-values,text/plain",
-                           ".csv")),
-
-      checkboxInput("summary", "Display Summary", FALSE),
-      
-      tags$hr(), # -------------
-      
-      # Input: times at which to predict survival probabilities
-      textInput("times", "Time(s) to Predict:", value = "", placeholder = "ex: 0.5, 1, 10"),
-      
-      actionButton("predict", "Predict"),
-      
-      tags$hr(),# -------------
-      
-      # Summary output
-      tableOutput("sum_stats")
-      
-    ),
-    
-    # Main panel for displaying outputs ----
-    mainPanel(
-      
-      tabsetPanel(
-        tabPanel("Calculate Survival Probability", verbatimTextOutput("surv_probs")),
-        tabPanel("Input Data", tableOutput("contents"))
+      tabPanel("Input Data Summary",
+               br(),
+               sidebarLayout(
+                 sidebarPanel(
+                   helpText("Upload the CSV file from which predicted failure probabilities are desired. This app will set up
+                            the variables in the data set required (e.g. time_until_answer, text_length...)"),
+                   fileInput("file1", "Upload CSV File",
+                             multiple = TRUE,
+                             accept = c(".csv")),
+                   tags$hr(),
+                   checkboxInput("km", "Display Kaplan-Meier Estimated Failure Probabilities", FALSE),
+                   tags$hr(),
+                   p("Kaplan-Meier Estimated failure probabilities adjust to the presence of censoring, or in this 
+                            case, the presence of unanswered questions."),
+                   p(strong("Example Interpretation:")),
+                   p("KM Estimated Failure probability at 3 hours: 0.10"),
+                   p("The probability that a question recieves an answer before 3 hours have passed since it was posted
+                     is 0.10. ")
[…]

### 2017-08-31 function_demonstration.Rmd
created a markdown that demonstrates how to use functions to predict failure

---
title: "Example use of prediction functions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This markdown demonstrates how to use functions fit_model, variable_setup and predict_failure to get failure probability predictions for questions posted on iFixit's Answers forum.

#### Setting up the data

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

# separating into data frames for model fitting and predictions for demonstration purposes
data_for_fit <- out[1:4000,]
for_predict <- out[4001:nrow(out),]
```

#### Fitting the model

```{r}
model <- oshitar::fit_model(data_for_fit, summary = TRUE)
```

#### Setting up the prediction data

* setting up the variables required for predictions
* call variable_setup with forpredicting = TRUE so the function won't try and set up the time_until_answer variable

```{r}
for_predict <- oshitar::variable_setup(for_predict, forpredicting = TRUE)
str(for_predict)
```

#### Predicting failure probabilities

##### predicting failure probabilities at default times, for each question's linear predictor/strata values (not predicting on any new data)

```{r}
predict <- oshitar::predict_failure(model)
head(predict)
```

##### predicting failure probabilities at default times for each question in the new data set

```{r}
predict1 <- oshitar::predict_failure(model, newdata = for_predict)
head(predict1)
```

* Interpretations: 
    + The probability that question 1 of the new data set recieves an answer before 30 minutes have passed since it was posted is `r round(predict1[1,1], 2)`
    + The probability that question 1 of the new data set recieves an answer before 1000 hours (~42 days) have passed since it was posted is `r round(predict1[1,6], 2)`

##### predicting failure probabilities at user-specified times for each question in the new data set

```{r}
predict2 <- oshitar::predict_failure(model, newdata = for_predict, times = c(1, 7, 30, 500))
head(predict2)
```

* Interpretations:
    + The probability that question 6 of the new data set recieves an answer before 500 hours (~21 days) have passed since it was posted is `r round(predict2[6,4], 2)`
    + The probability that question 1 of the new data set recieves an answer before 500 hours (~21 days) have passed since it was posted is `r round(predict2[1,4], 2)`

### 2017-08-31 Hours.Rmd
updated hours

@@
 8/26/2017 | 6 | 3:00-9:00PM | Tried to make variable_setup function more reproducible, ran into problems, worked on Mendeley and tex 
-
->> __Total Hours: 1...__
+8/27/2017 | 5.75 | 10:15-4:00PM | Finished with variable_setup function, started learning about the shiny app
+8/27/2017 | 2.5 | 7:30-10:00PM | Continued working on the shiny app
+8/28/2017 | 7.5 | 8:00-3:30PM | Worked on shiny app, met with Dr. Pileggi
+8/29/2017 | 8 | 7:30-3:30PM | Added interpretations/explanations to the shiny app, met with Anthony
+8/29/2017 | 2 | 5:30-7:30PM | Worked on streamlining code
+8/30/2017 | 4 | 7:45-11:45AM | Continued working on code + started writing functions to fit model and get predictions 
+8/30/2017 | 4 | 6:00-10:00PM | Edited documentation for functions + planned function to plot predictions
+8/31/2017 |  | 8:30- | Organized code, updated hours 
+>> __Total Hours: 334.58.__

### 2017-09-01 function_demonstration.Rmd
added code to demonstrate how to use plot_failure function

@@
 
-This markdown demonstrates how to use functions fit_model, variable_setup and predict_failure to get failure probability predictions for questions posted on iFixit's Answers forum.
+This markdown demonstrates how to use fit_model, variable_setup, predict_failure and plot_failure to get failure probability predictions for questions posted on iFixit's Answers forum, and plot the failure probability curves for specific questions.
 
@@
     + The probability that question 1 of the new data set recieves an answer before 500 hours (~21 days) have passed since it was posted is `r round(predict2[1,4], 2)`
+
+##### plotting predicted failure probabilities for specific questions
+
+```{r}
+# plotting the failure curve for the first question of the prediction data
+question <- for_predict[1,]
+oshitar::plot_failure(model, question)
+```
+
+```{r}
+# plotting the failure curve for the 50th question of the prediction data
+question50 <- for_predict[50,]
+oshitar::plot_failure(model, question50)
+```

### 2017-09-25 literature reviews/roughdraft.tex
rough draft

\documentclass[12pt]{article}
\usepackage{natbib}  % used for citations
\usepackage[parfill]{parskip} %used for formatting style of text

% Sets margins to 1 in
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

%-----------------------------------------------------------------------------------
\title{Literature Review of Online Question Forums}
\author{Lisa Oshita}
\date{}
%-----------------------------------------------------------------------------------

\begin{document}

\maketitle

\section{Introduction}

    Community-driven online question and answer forums (CQA) are becoming widley used sources of information. These online platforms allow for anyone to ask or answer a question. It provides a place for people of all backgrounds and levels of expertise to provide input on a certain question. One popular CQA is Yahoo! Answers. This platform features questions of all topics, from politics, to food and drink, and even mathematics. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. This forum reiceves around 40 million visits every month. This platforms ultimately provide people with a place to share their knowlege, and clearly are becoming increasingly popular sources of information.

    The CQA discussed in this paper is iFixit's Answers forum. iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo. What began as a small business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions. iFixit also sells the specialized tools and parts used in their repair guides, specialized tools like an iPhone 7 batter adhesive strip or a Nexus 9 LCD screen and digitizer. The main goal of this company is to teach people how to fix their own devices, and in extending the lifetime of their own devices, they save money and cut down on electronic waste. As such, this company helps thousands of people fix their devices everyday.

    Along with repair guides and tool sales, another important component of this company is their online question and answer forum called Answers. This platform features questions related to device repair, featuring over 9,000 devices and over 100,000 solutions and answers. Questions on this forum range from broken devices like a jammed zipper on a Patagonia jacket, to a shattered iPhone 6 plus screen. This forum is an integral part in teaching people how to fix their own devices. If people run into problems, they can always trust that they have a large community to turn to for help. Thus it's important, for both the individuals as well as iFixit, that askers get prompt answers. Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of Answers and iFixit. As such, investigation of response times would be both beneficial and informative. Analysis can reveal factors within the forum that affect how quickly questions get answers.

    Suggestions for how users can ask questions to minimize answer times, as well as suggestions for how the forum design can be improved, can be derived from such analysis. However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers. A majority of the research focuses on assessing and predicting the question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the survival probability of a question.

\section{Related Work}

    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model (? is that what it's called) to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.

    \citep{Mamykina2011} found that the swift answer times of Stack Overflow's community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.

    \citep{Asaduzzaman2013} analyzed unanswered questions on Stack Overflow to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.

\section{Materials and Methods}

    The data set analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017. 63.8\% of the questions recieved an answer before the data was downloaded. The distribution of answer times is highly right skewed, shown in figure a. The mean answer time was 355.93 hours, or 14.83 days, and the median answer time is 8.79 hours. These values factor in questions that did not recieve an answer. Within an hour, 26.59\% of the questions received an answer. After one day, 57.35\% of questions recieved an answer. Variables within the data set included information about the questions, like the title, the body text, device, date it was posted, and information about the user like whether or not the user was considered new (or a member for less than 24 hours) at the time the question was posted.

    Variables created in the model:

The time until event variable used in the cox regression model is defined as the time until a question receives its first answer. If a question received an answer, this was calculated as the time from the date the question was posted to the date the first answer was received. If the question did not receive an answer, this was calculated as the time from the date the question was posted, to the date the date set was downloaded. The censoring variable needed in a cox regression model, is 0 if the question remained unanswered by the time the data set was downloaded, and 1 if the question received an answer.

Newcategory

This variable categorized the devices of the questions based off of the existing category variable as well as several other factors. The original category variable had NAs, which were a result of the asker creating a question for a device not already featured on the website, and were coded to “Other”. All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category. After pulling out iPhones from the original “Phones” category, the remaining phones were categorized as “Android/Other Phone”. Appliance and Household categories of the original variable were merged into “Home”. “Car and Truck” were added to the “Vehicle”. Lastly, any category that contained less than 2% of the questions were categorized as “Other”.

Containanswered and contain_unanswered were created based off of the idea that certain key words would be more likely to catch an user’s eye, and would make them get answered more quickly. This was also based on the idea that certain words might also not be as popular, and would be common amongst questions that remained unanswered. As such, contain_answered and contain_unanswered are logical variables indicating true if a question’s title contains a term that is considered frequently used among answered or unanswered questions, respectively. To create these variables, the data set was separated between answered and unanswered questions. For each set, the occurrence of each word in every title was summed to get the frequencies of each word. Thus, we had a two lists of words—one consisting of the words within answered questions’ titles and their frequencies, and the other consisting of the words within unanswered questions’ titles and their frequencies. From these two lists, rules were applied to determine if a word can be considered “frequently used”.  For frequently used words in answered questions, that word would have to appear in more than 1percent of the titles, and would have to have a ratio of greater than 1. For a word to be considered “frequently used” among unanswered questions, that word would have to appear in more than 1percent of the question, and would have to have a ratio of less th san 1. Thus, we ended up with two sets of words, one set contained the most frequently used words in answered questions, and the other set contained the most freuqnelty used words in unanswered questions. Since there was some overlap between the words and the devices and category levels, any words that matched with a category were removed. That resulted in lists of 111 words for answered questions, and 32 words for unanswered questions. Contain_answered indicated true if a question’s title contained at least one of the words from the frequently used words among the answered questions. Contain_unanswered indicated true if a questions title contained at least one of the words from the frequently used words among the answered questions.

Title_questionmark and title_beginwh 
These two variables were created to determine if stating the title in the form of a question is associated with faster answer times. Title_questionmark is a logical variable indicating true if the question ends in a question mark. Title_beginwh is a logical variable indicating true if the title begins with a “wh” word, like “what” or “when”. These variables were taken from mined your own tags

Text_contain_punct.
This is a logical variable indicating true if the question’s text contains any end punctuation marks (. ? !). This variable was created to investigate if run-on sentences (sentences with no end punctuation marks) take longer to receive an answer.

Text_all_lower
This is a logical variable indicating true if the text of the question is in all lower case.

Update 
This is a logical variable indicating true if the asker updated the question (edited or added information about the question) after posting it.

Greeting
Logical variable indicating true if the asker included a greeting (e.g. “Hello”, “Hi”) as the first word of the text
Gratitude
Logical variable indicating true if the asker used manners in the question of the text (e.g. “Thank you”, “please”, “appreciate”)

Prior_effort 
Logical variable indicating true if the asker used language that indicates that prior effort or research was done before asking the question. (e.g. “tried”, “attempted”, “tested”). This variable was inspired by

Weekday 
The day of the week the question was posted

Ampm 
The time of day the question was posted. If the question was posted between 5am and 12pm, it was categorieze das morning. If it was posted between 12pm and 5pm, it was categorized as afternoon, between 5pm and 8am- “evening”, and 8pm and 5 am, “night”

Avg_tag_score
The frequency or “score” of a tag is defined as the proportion of times that tag appears in the data set. This variable is the average of all of a question’s tag “scores” or frequencies. This variable was created to investigate if questions that include popular tags, or tags that are used frequently, have faster answer times. This variable was inspired by

Text_length
The number of characters in the text

Device_length
The number of characters in the user-defined device variable. This variable was included to capture when a user incorrectly inputs their device. For example, question 390271 includes a device that is 136 characters long--“Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”. 11 questions also didn’t include any device name. this variable was created to capture these user errors

Avg_tag_length
The average number of characters in the user-defined tags. This variable, like the device-length variable, was created to capture when a user incorrectly used the tagging system. An example of an incorrect tag is question 390989 and says: “i need to repair the headset because i can not find the bluetoot” and comes ot 64 charahcters. If a question did not include a tag, this variable was set to 0.

Newline_ratio
This variable is calculated as the ratio of the number of newlines a question includes, over the number of characters in the questions text. This variable was included on the assumption that questions with text that is more readable get faster answer times. Questions with long text and also include newlines are generally easier to read than questions that don’t include any newlines.

Variables included in the final model

The above variables were all entered into the final model. The final model was stratified on ampm, as prior analysis indicated that this variable violated the proproitnal hazard assumption. The square root of the avg_tag_score was entered. Viewing the plot of answer times against the avg_tag_screo variable indicated heavy skewing. Taking the square root of this variable helped pull in the larger values. The quadratic term was included for text_length. This was included, since it was hypothesized that texts that were either too short or too long would have higher answer times. In other words, there might be a sweet spot on the text_lenght. Restricted cubic splines were included for device_length, avg_tag_length, and newline_ratio. The method for fitting these variables was taken from frank harrels text book. These variables were fit as restricted cubic splines with 5 knots initially. The final includes 5, 4, and 4 knots, as this model with this number of knots had the lowest Aic.

Methods

Univariate analysis for each of the variables of interest was carried out on one of the training data sets. Variables with a p-value of less than 0.01 were entered into the final model. Since this is a predictive model, it was decided that all variables would be kept in the model, to maintain predictive power. After building the model on one of the training data sets, assumptions and residuals were checked.

Initally, ampm was put in the model without any stratification. Checking the proportional hazards assumption, by both examinging the schoenfeld residuals as well as the cox.zph function in r, indicated that ampm violated the proportional hazard assumption. It was decided that this variable would be stratified on.

Checking the plot of martingale residuals shows that there doesn’t appear to be any obvious pattern, indicating that the functional form seems adequate (how to check residuals for splines??)

Checking the deviance residuals shows that a considerable amount of questions have residuals with an absolute value of well over 2.5. Taking those questions out of the data set and refitting the model and performing cross validation, showed that fitting the model without these questions resulted in worse predictive performance.

Looking at the score resiudals for each predictor indicated that there may be a couple points that can be considered influential. Experimentation with those questions, and refitting the model without those certain points, along with performing cross validation, showed that refitting the model without those question resulted in worse predictive performance, similar to how it did for the deivcance resiudals. 
After determining that the model did not grossly violate any assumptions or have any weird residuals, a cross-validation scheme was carried out.

A cross-validation scheme was used for this analysis. The data set was split into 5 training and test data sets. Training data sets had 6,208 questions and test data sets had 1,552 questions. The model was built on the training data sets, and tested on the corresponding test data sets. To assess the prediction performance of this model, metrics similar to /cite{Chen} were computed. The model and it’s coefficients, built on the training data sets, were then use to calculate the predicted hazard ratios for questions in the test data sets. Those predicted hazard ratios were then entered into another cox regression model with the time until answer as the survival time variable. Metrics calculated were the hazard ratio for this model, along with the partial loglikelihood score and respective p-value. The AIC and R-square was also evaluated (explain what this is in survival analysis). Somers Dxy along with a concordance statistic were also calculated as performance metrics. This process was repeated each time a model built on a training data set was fit and predicted on the test data set. The metrics taken into consideration was the average of all of the metrics computed on the test data sets. The same metrics were also computed for predictions on the training data set itself. Although the metrics were not considerably high or impressive, they did not change from training data set to test data set.

Lastly, the model was fit to the full data set. The same process and metrics were calculated. Metrics for the full data set are not different from the results of our cross validation plan.

Results and Discussion (or separate the two).

The final model gave an AIC value of 69945.32. The partial loglikelihood ratio test statistic was 1307.15 with a p-value of 0. The R-squared value for this model is 0.1555. Variables that proved to be significant predictors with a p-value of less than 0.01 are: new_category (apple product, camera, game console, home, pc, and vehical), contain_unanswered, title_quesitonmark, update, prior_effort, avg_tag_score and the spline on avg_tag_length.

While the model itself overall is significant, the metrics for the models predictive accuracy are not impressive. This indicates that perhaps a different model might perform better as a model to predict the survival time for questions. Or, a model with more quantitative variables might preform better as well.

\bibliographystyle{ECA_jasa}
\bibliography{questions}

\end{document}

### 2017-09-25 model fitting/final_model.Rmd
minor edits

@@
 knitr::opts_chunk$set(echo = TRUE)
-
 ```
@@
 x <- oshitar::variable_setup(out)
+x <- x[[1]]
 

### 2017-09-25 literature reviews/roughdraft.tex
revised materials/methods section

@@
     The data set analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017.
-63.8\% of the questions recieved an answer before the data was downloaded.
-The distribution of answer times is highly right skewed, shown in figure a.
-The mean answer time was 355.93 hours, or 14.83 days, and the median answer time is 8.79 hours.
-These values factor in questions that did not recieve an answer.
-Within an hour, 26.59\% of the questions received an answer.
-After one day, 57.35\% of questions recieved an answer.
+We worked exclusively with questions in English.
+Of the questions in the data set, 4,951, or 63.8\%, recieved an answer before the data was downloaded.
+Questions that remained unanswered were considered left censored.
+The time until event value used in survival analysis methods was defined as the time until a question recieves an answer.
+Comments posted on the question are not considered answers, and an answer does not have to be accepted as the chosen solution from the asker to be considered the answer.
+We are only considering the time until the question recieves its first answer.
+This time until answer variable was calculated as the time from the date it was posted to the date it recieved its first answer, in hours.
+For left-censored questions, questions that remained unanswered, this value was calculated as the time from the date it was posted to the date the data was downloaded, in hours.
+Figure a shows the distribution of the answer times for all questions in the data set.
+
+    The following statistics were calculated from Kaplan Meier estimates of the survival probabilities.
+In our case, survival probability is defined as the probability that a question remains unanswered after a certain time t.
+The mean survival time, or the average time for questions in the data set to recieve an answer, is 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions recieved an answer is 9.16 hours.
+By 0.88 hours, 52.8 minutes, 25\% of the questions received an answer.
+By 683.19 hrs, 28.47 days, 64\% of the questions have been answered.
+Beyond that time point,
+
     Variables within the data set included information about the questions, like the title, the body text, device, date it was posted, and information about the user like whether or not the user was considered new (or a member for less than 24 hours) at the time the question was posted.

### 2017-09-30 article_graphics.Rmd
created a markdown containing graphics to use in article

---
title: "Tables for Journal Article"
author: "Lisa Oshita"
date: "9/30/2017"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
x <- oshitar::variable_setup(out)

library(ggplot2); library(survival); library(rms); library(magrittr)
```

### Distribution of Answer Times

```{r}
x$Answered <- NA
x$Answered[x$answered == 1] <- "Answered"
x$Answered[x$answered == 0] <- "Unanswered"

ggplot(x, aes(x = time_until_answer, fill = Answered)) + 
  geom_histogram(bins = 20) + 
  scale_x_continuous("Time (hours)") +
  scale_y_continuous("Number of Questions") + 
  ggtitle("Distribution of Answer Times") + 
  theme(legend.title = element_blank()) # edit position of axis labels + title
```

### Table of KM estimate percentiles

```{r}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
KM <- survfit(surv_object ~ 1, conf.type = "log-log")

q <- quantile(KM, c(0.01, 0.05, 0.10, 0.25, 0.30, 0.40, 0.50, 0.55, 0.58, 0.60, 0.64))
quantiles <- q[[1]]
quantilesdf <- data.frame(Percent = names(quantiles), Time = quantiles)
colnames(quantilesdf) <- c("Percent Answered", "Time (Hours)")
quantilesdf

# add caption with example interpretation?: At 0.042 hours or 2.52 minutes, 1 percent of question posted recieved an Answer
# explain the jump in the data? 
```

### KM Curve

```{r}
library(survminer)
ggsurvplot(KM, data = x, 
           risk.table = "abs_pct", risk.table.title = "Total number at risk (percentage at risk)", 
           cumevents = TRUE, 
           conf.int = TRUE, conf.int.style = "step", 
           censor = FALSE,
           surv.median.line = "hv", 
           xlab = "Time (hours)", 
           xlim = c(0, 100), break.x.by = 10,
           ylim = c(0, 1), break.y.by = 0.1,
           surv.plot.height = 1, ggtheme = theme_bw(), 
           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE,
           title = "Kaplan-Meier Curve for all Questions",
           legend = "none")

# include caption: Dotted line on graph indicates the median answer time (time at which 50% of question recieved an answer)

ggsurvtable(KM, data = x, risk.table.type = "abs_pct",
            ggtheme = theme_bw())
```

### Device Categories

```{r}
dev <- prop.table(table(x$new_category))

devdf <- data.frame(Device = names(dev), Percent = round(as.numeric(unname(dev))*100,2))
devdf <- devdf %>% dplyr::arrange(desc(Percent))
colnames(devdf)[2] <- "Percent of all Questions"
devdf
```

### 2017-09-30 literature reviews/roughdraft.tex
edited materials, methods, results sections

--- 2017-09-25 literature reviews/roughdraft.tex
@@
 %-----------------------------------------------------------------------------------
-\title{Literature Review of Online Question Forums}
+\title{Rough Draft}
 \author{Lisa Oshita}
@@
 One popular CQA is Yahoo!
-Answers.
-This platform features questions of all topics, from politics, to food and drink, and even mathematics.
+Answers, featuring questions of all topics and expertise levels.
 On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers.
-This forum reiceves around 40 million visits every month.
-This platforms ultimately provide people with a place to share their knowlege, and clearly are becoming increasingly popular sources of information.
+Forums liek these 2 recieve around 40 million visits every month.
+These online question and answer forums are clearnly becoming popular sources of information.
 
-    The CQA discussed in this paper is iFixit's Answers forum.
+    The CQA analyzed in this paper is iFixit's Answers forum.
 iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo.
@@
 
-    Suggestions for how users can ask questions to minimize answer times, as well as suggestions for how the forum design can be improved, can be derived from such analysis.
+    Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.
 However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers.
@@
 
-    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model (?
-is that what it's called) to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
+    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
 
@@
 
-\section{Materials and Methods}
+\section{Materials}
 
-    The data set analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017.
-63.8\% of the questions recieved an answer before the data was downloaded.
-The distribution of answer times is highly right skewed, shown in figure a.
-The mean answer time was 355.93 hours, or 14.83 days, and the median answer time is 8.79 hours.
-These values factor in questions that did not recieve an answer.
-Within an hour, 26.59\% of the questions received an answer.
-After one day, 57.35\% of questions recieved an answer.
-Variables within the data set included information about the questions, like the title, the body text, device, date it was posted, and information about the user like whether or not the user was considered new (or a member for less than 24 hours) at the time the question was posted.
+    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017.
+We worked exclusively with questions in English.
+Of the questions in the data set, 4,951, or 63.8\%, recieved an answer before the data was downloaded.
+Questions that remained unanswered were considered right-censored.
+The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum recieves an answer.
+Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer.
+We are only considering the time until the question recieves its first answer.
+The time until answer value for right-censored questions, questions that did not recieve an answer, is defined as the time from when the question was posted, to the time the data was downloaded.
+Figure a shows the distribution of answer times for all questions in the data set.
 
-    Variables created in the model:
+    The following statistics were calculated from Kaplan-Meier estimates of survival probabilities for each question in the data.
+As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions.
+In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t.
+For questions in this data set, the mean survival time, or the average time until a question recieves its first answer is 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions in the data recieved an answer is 9.16 hours.
+Table 1 provides more percentiles of survival time.
+    Figure A shows the Kaplan-Meier Curve for all questions in the data.
+The curve indicates that around 100 hours, the probability that a question recieves an answer after that time hovers around 0.35.
+The survival probability never reaches 0 due to the large amount of unanswered questions.
 
-The time until event variable used in the cox regression model is defined as the time until a question receives its first answer.
-If a question received an answer, this was calculated as the time from the date the question was posted to the date the first answer was received.
-If the question did not receive an answer, this was calculated as the time from the date the question was posted, to the date the date set was downloaded.
-The censoring variable needed in a cox regression model, is 0 if the question remained unanswered by the time the data set was downloaded, and 1 if the question received an answer.
+    Variables created:
 
-Newcategory
+    The data contained information about each question's title, text, and device, from which we created the following variables to use in the cox regression model.
 
-This variable categorized the devices of the questions based off of the existing category variable as well as several other factors.
-The original category variable had NAs, which were a result of the asker creating a question for a device not already featured on the website, and were coded to “Other”.
-All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category.
-After pulling out iPhones from the original “Phones” category, the remaining phones were categorized as “Android/Other Phone”.
-Appliance and Household categories of the original variable were merged into “Home”.
-“Car and Truck” were added to the “Vehicle”.
-Lastly, any category that contained less than 2% of the questions were categorized as “Other”.
+The time until a question recieves its first answer, as described above, was calculated as the time from the time the question was posted to the time the first answer was received in hours.
+If the question did not receive an answer, the time until answer value was calculated as the time from when the question was posted, to the time the data was downloaded, July 7, 2017 at 2:41 PM PDT.
+The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered by the time the data set was downloaded.
 
-Containanswered and contain_unanswered were created based off of the idea that certain key words would be more likely to catch an user’s eye, and would make them get answered more quickly.
-This was also based on the idea that certain words might also not be as popular, and would be common amongst questions that remained unanswered.
-As such, contain_answered and contain_unanswered are logical variables indicating true if a question’s title contains a term that is considered frequently used among answered or unanswered questions, respectively.
-To create these variables, the data set was separated between answered and unanswered questions.
-For each set, the occurrence of each word in every title was summed to get the frequencies of each word.
-Thus, we had a two lists of words—one consisting of the words within answered questions’ titles and their frequencies, and the other consisting of the words within unanswered questions’ titles and their frequencies.
-From these two lists, rules were applied to determine if a word can be considered “frequently used”.
-For frequently used words in answered questions, that word would have to appear in more than 1percent of the titles, and would have to have a ratio of greater than 1.
-For a word to be considered “frequently used” among unanswered questions, that word would have to appear in more than 1percent of the question, and would have to have a ratio of less th san 1.
-Thus, we ended up with two sets of words, one set contained the most frequently used words in answered questions, and the other set contained the most freuqnelty used words in unanswered questions.
-Since there was some overlap between the words and the devices and category levels, any words that matched with a category were removed.
-That resulted in lists of 111 words for answered questions, and 32 words for unanswered questions.
-Contain_answered indicated true if a question’s title contained at least one of the words from the frequently used words among the answered questions.
-Contain_unanswered indicated true if a questions title contained at least one of the words from the frequently used words among the answered questions.
+Categorical Variables:
 
-Title_questionmark and title_beginwh 
-These two variables were created to determine if stating the title in the form of a question is associated with faster answer times.
-Title_questionmark is a logical variable indicating true if the question ends in a question mark.
-Title_beginwh is a logical variable indicating true if the title begins with a “wh” word, like “what” or “when”.
-These variables were taken from mined your own tags
+Questions were categorized based off of the devices it pertains to.
+Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other.
+Home, Vehicle, Other.
+Table B shows the percentage of questions within each device category.
 
-Text_contain_punct.
-This is a logical variable indicating true if the question’s text contains any end punctuation marks (.
-?
-!).
-This variable was created to investigate if run-on sentences (sentences with no end punctuation marks) take longer to receive an answer.
+Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.
 
-Text_all_lower
-This is a logical variable indicating true if the text of the question is in all lower case.
+Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question.
 
-Update 
-This is a logical variable indicating true if the asker updated the question (edited or added information about the question) after posting it.
+Whether or not the question's title ends in a question mark.
 
-Greeting
-Logical variable indicating true if the asker included a greeting (e.g. “Hello”, “Hi”) as the first word of the text
-Gratitude
-Logical variable indicating true if the asker used manners in the question of the text (e.g. “Thank you”, “please”, “appreciate”)
+Whether or not the question's title begins with a "Wh" word (e.g. "What", "Where").
 
-Prior_effort 
-Logical variable indicating true if the asker used language that indicates that prior effort or research was done before asking the question.
-(e.g.
-“tried”, “attempted”, “tested”).
-This variable was inspired by
+Whether or not the question's text contains any end punctuation marks (. ? !).
 
-Weekday 
-The day of the week the question was posted
+Whether or not the question's text is in all lower case.
 
-Ampm 
-The time of day the question was posted.
-If the question was posted between 5am and 12pm, it was categorieze das morning.
-If it was posted between 12pm and 5pm, it was categorized as afternoon, between 5pm and 8am- “evening”, and 8pm and 5 am, “night”
+Whether or not the asker updated the question's text (e.g., edited or added information) sometime after posting it.
 
-Avg_tag_score
-The frequency or “score” of a tag is defined as the proportion of times that tag appears in the data set.
-This variable is the average of all of a question’s tag “scores” or frequencies.
-This variable was created to investigate if questions that include popular tags, or tags that are used frequently, have faster answer times.
-This variable was inspired by
+Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
 
-Text_length
-The number of characters in the text
+Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please'').
 
-Device_length
-The number of characters in the user-defined device variable.
-This variable was included to capture when a user incorrectly inputs their device.
-For example, question 390271 includes a device that is 136 characters long--“Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”.
-11 questions also didn’t include any device name.
-this variable was created to capture these user errors
+Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
 
-Avg_tag_length
-The average number of characters in the user-defined tags.
-This variable, like the device-length variable, was created to capture when a user incorrectly used the tagging system.
-An example of an incorrect tag is question 390989 and says: “i need to repair the headset because i can not find the bluetoot” and comes ot 64 charahcters.
-If a question did not include a tag, this variable was set to 0.
+The day of the week the question was posted.
 
-Newline_ratio
-This variable is calculated as the ratio of the number of newlines a question includes, over the number of characters in the questions text.
-This variable was included on the assumption that questions with text that is more readable get faster answer times.
-Questions with long text and also include newlines are generally easier to read than questions that don’t include any newlines.
+The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night.
 
-Variables included in the final model
+Numeric Variables:
 
-The above variables were all entered into the final model.
-The final model was stratified on ampm, as prior analysis indicated that this variable violated the proproitnal hazard assumption.
-The square root of the avg_tag_score was entered.
-Viewing the plot of answer times against the avg_tag_screo variable indicated heavy skewing.
-Taking the square root of this variable helped pull in the larger values.
-The quadratic term was included for text_length.
-This was included, since it was hypothesized that texts that were either too short or too long would have higher answer times.
-In other words, there might be a sweet spot on the text_lenght.
-Restricted cubic splines were included for device_length, avg_tag_length, and newline_ratio.
-The method for fitting these variables was taken from frank harrels text book.
-These variables were fit as restricted cubic splines with 5 knots initially.
-The final includes 5, 4, and 4 knots, as this model with this number of knots had the lowest Aic.
+The average frequency, or proportion of times a tag appeared in all of the data, for all of a question's user-defined tags. Questions without tags were assigned a value of 0 for this variable.
 
-Methods
+The average number of characters in each question's tags.
 
-Univariate analysis for each of the variables of interest was carried out on one of the training data sets.
+The number of characters in the question's text.
+
+The number of characters in the user-defined device name.
+
+The ratio of the number of newlines to the number of characters in the question's text.
+
+\section{Methods}
+
+Univariate analyses for each variable of interest were performed on one of the training data sets.
 Variables with a p-value of less than 0.01 were entered into the final model.
-Since this is a predictive model, it was decided that all variables would be kept in the model, to maintain predictive power.
-After building the model on one of the training data sets, assumptions and residuals were checked.
+As the goal of this model is prediction, it was decided that all variables would be kept in the model to maintain predictive power.
 
-Initally, ampm was put in the model without any stratification.
-Checking the proportional hazards assumption, by both examinging the schoenfeld residuals as well as the cox.zph function in r, indicated that ampm violated the proportional hazard assumption.
-It was decided that this variable would be stratified on.
+5-fold cross-validation was used to assess predictive performance metrics. Each training data set contained 6,208 questions. Test data sets contained 1,552 questions.
 
-Checking the plot of martingale residuals shows that there doesn’t appear to be any obvious pattern, indicating that the functional form seems adequate (how to check residuals for splines??)
+For each iteration of cross-validation, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data.
+To assess prediction performance, those predicted ratios were entered into a separate cox regression model as the explanatory variable with the question's answer times as the survival time value.
+The resulting hazard ratio, R-square statistic, partial loglikelihood and p-value, Somers' Dxy and Concordance statistic for that model were used as indicators of the prediction model's performance.
+If the performance assessing model gave a significant results, this would indicate that the predicted hazard ratio is signficantly associated with survival time, and that our prediction model performs well.
+Somers' Dxy and Concordance statistics are measures of how well the model can rank predictions.
+(add to this) The concept behind these metrics came from \cite{Chen}.
+These metrics were also computed for predictions on the training data itself.
+For each iteration, there was no signficant difference between the metrics computed on the training data predictions, and the metrics computed on the test data.
+Table C shows average metrics for training and test data predictions.
+The metrics taken into consideration was the average of all metrics computed on test data.
+Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.
 
-Checking the deviance residuals shows that a considerable amount of questions have residuals with an absolute value of well over 2.5.
-Taking those questions out of the data set and refitting the model and performing cross validation, showed that fitting the model without these questions resulted in worse predictive performance.
+\section{Results and Discussion}
 
-Looking at the score resiudals for each predictor indicated that there may be a couple points that can be considered influential.
-Experimentation with those questions, and refitting the model without those certain points, along with performing cross validation, showed that refitting the model without those question resulted in worse predictive performance, similar to how it did for the deivcance resiudals.
-After determining that the model did not grossly violate any assumptions or have any weird residuals, a cross-validation scheme was carried out.
+The final model, including all variables described above, was fit to the full data set.
+The proportional hazards assumption was assessed by using the cox.zph function of the survival package in R.
+This test is based on the correlation between scaled Schoenfeld residuals and a function of time.
+Signficant p-values of this test indicate a possible violation of the proportional hazard assumption.
+For our model, the "Apple Product" level of the device category variable had the lowest p-value of 0.01.
+The next lowest p-values hovered around 0.04, for variables like device_length, and the Camera and Game Console levels of category.
+As Apple Product was the only major violation of this assumption, and stratifying on this variable substantially decreased the predictive power, this assumption was considered to be fine (rewrite this).
 
-A cross-validation scheme was used for this analysis.
-The data set was split into 5 training and test data sets.
-Training data sets had 6,208 questions and test data sets had 1,552 questions.
-The model was built on the training data sets, and tested on the corresponding test data sets.
-To assess the prediction performance of this model, metrics similar to /cite{Chen} were computed.
-The model and it’s coefficients, built on the training data sets, were then use to calculate the predicted hazard ratios for questions in the test data sets.
-Those predicted hazard ratios were then entered into another cox regression model with the time until answer as the survival time variable.
-Metrics calculated were the hazard ratio for this model, along with the partial loglikelihood score and respective p-value.
-The AIC and R-square was also evaluated (explain what this is in survival analysis).
-Somers Dxy along with a concordance statistic were also calculated as performance metrics.
-This process was repeated each time a model built on a training data set was fit and predicted on the test data set.
-The metrics taken into consideration was the average of all of the metrics computed on the test data sets.
-The same metrics were also computed for predictions on the training data set itself.
-Although the metrics were not considerably high or impressive, they did not change from training data set to test data set.
+Assessing the martingale residuals for each quantitative predictor indicated that the functional form appears to be adequate.
 
-Lastly, the model was fit to the full data set. The same process and metrics were calculated. Metrics for the full data set are not different from the results of our cross validation plan.
+Assessing the deviance residuals shows that a considerable amount of questions have residuals with an absolute value of well over 2.5.
+However, removing those questions from the data set and and refitting the model with cross-validation techniques resulted in worse predictive accuracy.
 
-Results and Discussion (or separate the two).
+Assessing the score residuals for each predictor indicated that some questions might a strong influence on the fit of the model.
+However, similar to the case with the deviance residuals, refitting the model without those certain questions with cross-validation techniques resulted in worse predictive performance.
+
+The final model included all variables described above, along with the following transformations:
+
+Stratification on the time of day the question was posted.
+
+Square root of the average frequency of a question's tags.
+
+Quadratic polynomial on the length of the question's text.
+
+Restricted cubic splines on the number of characters in the device name, the average length of a question's tags, and the ratio of newlines to number of characters in a question's text.
+Knots assigned to these variables were 5, 4, 4, respectively.
 
@@
 Variables that proved to be significant predictors with a p-value of less than 0.01 are: new_category (apple product, camera, game console, home, pc, and vehical), contain_unanswered, title_quesitonmark, update, prior_effort, avg_tag_score and the spline on avg_tag_length.
+Include some interpretations of the hazard ratio?
 
@@
 
+The variables described above were entered into the final cox regression model with these variable transformation
+
+Stratification on ampm: prior analysis of initial cox regression models indicated that this variable violated the proportional hazard assumption. Stratification resolved this violation.
+
+Square root of avg\_tag\_score: Viewing the distribution of answer times against the original avg\_tag\_score variable indicated heavy right skewing.
+Taking the square root of this variable decreases some of this skewing.
+
+Quadratic polynomial on text_length
+
+Restricted cubic splines were included for device_length, avg_tag_length, and newline_ratio.
+The method for fitting these variables was applied from \citep{Harrell2015}.
+Initially, these variables were fit as restricted cubic splines with 5 knots.
+The model with the lowest AIC included 5, 4, and 4 knots for device_length, avg_tag_length and newline_ratio, respectively.
+As such, this was the final form for these quantitative variables.
+
+\section{Appendix}
+
+device
+
+The data contained the original category variable as defined by iFixit.
+This category variable contained NAs (how many), a result of the asker creating a question for a device not already in the website's data base.
+These missing values were coded to ``Other'' in the new categorization variable.
+All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category.
+After pulling out iPhones from the original ``Phones'' category, the remaining phones were categorized as ``AndroidOther Phone''.
+Appliance and Household categories of the original variable were merged into ``Home''.
+``Car and Truck'' were added to the ``Vehicle''.
+Lastly, any category that contained less than 2\% of the questions were categorized as ``Other''.
+All other categories remained the same as the original category.
+The final categories in the new categorization variable were Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.
+
+contain answered and unanswered
+
+  These variables were created based on the intuition that certain topics might be more popular among the answering community, and that questions concerning these topics might recieve an answer faster than questions that don't.
+It was also based on the flip side of this idea, that certain topics might not be popular, or that some topics might be too narrow or specific and would be common among questions with long answer times or those that remained unanswered.
+To investigate this intuition, contain_answered and contain_unanswered were created.
+
+  To create these variables, the data was separated between answered and unanswered questions.
+Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions.
+These lists contained every word within the question's titles and the frequency, or number of times they occured in their respective data set.
+For each of these lists, rules were applied to determine if a word could be considered ``frequently use''.
+For frequently used words in answered questions, that word would have to appear in more than 1\% of the titles, and would have to appear in answered questions more than it appeared in unanswered questions.
+To determine the latter part, a ratio of proportions was calculated.
+This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
+As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20).
+As for unanswered questions, to be considered ``frequently'' used, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1).
+Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list.
+The resulting list for answered questions was 111 words, and 32 words in uanswered questions.
+Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, repsectively.
+
+  Title\_questionmark and title\_beginwh
+
+These two variables were created to determine if stating the title in the form of a question is associated with faster answer times.
+Title_questionmark is a logical variable indicating true if the question's title ends with a question mark.
+Title_beginwh is a logical variable indicating true if the title begins with a “wh” word (e.g.
+"what", "when").
+These variables were created based off of the findings from \citep{Bhat2014}.
+
+  Text\_contain\_punct
+
+A logical variable indicating true if the question’s text contains any end punctuation marks (.
+?
+!).
+This variable was created to investigate the intuition that run-on sentences, or sentences with no end punctuation marks, may take longer to receive an answer.
+
+Text\_all\_lower
+
+A logical variable indicating true if the text of the question is in all lower case.
+
+Prior\_effort
+
+Logical variable indicating true if the asker used words that indicate prior effort or research was done before asking the question (e.g.
+``tried'', ``attempted'', ``tested'').
+This variable was created based off of findings from \cite{Bhat2014}.
+
+Ampm (change name)
+
+The time of day the question was posted.
+If the question was posted between 5am and 12pm, it was categorized as ``morning''.
+If it was posted between 12pm and 5pm, it was categorized as ``afternoon'', between 5pm and 8am- ``evening'', and 8pm and 5 am, ``night''
+
+Avg\_tag\_score
+
+The frequency or “score” of a tag is defined as the proportion of times that tag appears in the entire data set.
+Avg\_tag\_score is the average of all of a question’s tag “scores” or frequencies.
+This variable was created to investigate if questions that include popular tags, or tags that are frequently used and thus have a high "score", also have faster answer times.
+This variable was created based off of findings from \cite{Bhat2014}.
+
+Avg\_tag\_length
+
+The average number of characters in each question's user-defined tags.
+If a question did not include a tag, this variable was set to 0.
+This variable, like the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
+For example, question 390989 includes tag: “i need to repair the headset because i can not find the bluetoot” and is 64 characters long, while question 410254 includes tags "sound", "sound driver" and "speaker" and has an average tag length of 8 characters.
+It's hypothesized that users who use the tagging system correctly, as in the latter example, recieve answers quicker than the user in the former.
+
+Device\_length
+
+The number of characters in the user-defined device variable.
+This variable was included to capture when a user incorrectly inputs the device name.
+For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One” and is 136 characters long.
+11 questions in this data set also didn’t include any device.
+This variable was created based on the intuition that users who incorrectly define their devices make it harder for answerers to discern the topic of their question, and thus have longer answer times or might not recieve an answer.
+
+Newline\_ratio
+
+This ratio of the number of newlines to the number of characters in the question's text.
+This variable was based on the intuition that question's that include newlines in the text, are easier to read and thus have faster answer times.
+long text and also include newlines are generally easier to read than questions that don’t include any newlines.
+
 \bibliographystyle{ECA_jasa}

### 2017-09-30 exploratory analysis/summary_stats.Rmd
reorganized code
minor edits

@@
 
-library(ggplot2)
-library(survival)
-library(epiR)
-library(survminer)
-library(dplyr)
+library(ggplot2); library(survival); library(epiR); library(survminer); library(dplyr)
 ```
@@
 ```{r, echo = FALSE}
+library(survminer)
 ggsurvplot(KM, data = x, 
@@
            xlim = c(0, 100), break.x.by = 10,
-           ylim = c(0, 0.7), break.y.by = 0.1,
+           ylim = c(0, 1), break.y.by = 0.1,
            surv.plot.height = 1, ggtheme = theme_bw(), 

### 2017-09-30 model fitting/final_model.Rmd
minor edit
added code

--- 2017-08-31 model fitting/final_model.Rmd
@@
 trains <- list(train1, train2, train3, train4, train5)
+trains <- purrr::map(trains, ~as.data.frame(.))
 tests <- list(test1, test2, test3, test4, test5)
+tests <- purrr::map(tests, ~as.data.frame(.))
 

### 2017-10-04 Article submission/roughdraft.tex
created separate folder for article submission

--- 2017-09-30 literature reviews/roughdraft.tex
@@
 
-    Community-driven online question and answer forums (CQA) are becoming widley used sources of information.
+    Community-driven online question and answer forums (CQA) are becoming widely used sources of information.
 These online platforms allow for anyone to ask or answer a question.
@@
 
-    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017.
+    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017, the date the data was downloaded.
 We worked exclusively with questions in English.
-Of the questions in the data set, 4,951, or 63.8\%, recieved an answer before the data was downloaded.
+Of the questions in the data set, 4,951, or 63.8\%, recieved an answer.
 Questions that remained unanswered were considered right-censored.
@@
 
-Questions were categorized based off of the devices it pertains to.
+\begin{itemize}
+  \item Questions were categorized based off of the devices it pertains to.
 Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other.
@@
 Table B shows the percentage of questions within each device category.
-
-Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.
-
-Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question.
-
-Whether or not the question's title ends in a question mark.
-
-Whether or not the question's title begins with a "Wh" word (e.g. "What", "Where").
-
-Whether or not the question's text contains any end punctuation marks (. ? !).
-
-Whether or not the question's text is in all lower case.
-
-Whether or not the asker updated the question's text (e.g., edited or added information) sometime after posting it.
-
-Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
-
-Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please'').
-
-Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
-
-The day of the week the question was posted.
-
-The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night.
+  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.
+  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. 
+  \item Whether or not the question's title ends in a question mark.
+  \item Whether or not the question's title begins with a "Wh" word (e.g. "What", "Where"). 
+  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
+  \item Whether or not the question's text is in all lower case. 
+  \item Whether or not the asker updated the question's text (e.g., edited or added information) sometime after posting it. 
+  \item Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
+  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). 
+  \item Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
+  \item The day of the week the question was posted. 
+  \item The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night. 
+\end{itemize}
 
@@
 
-The average frequency, or proportion of times a tag appeared in all of the data, for all of a question's user-defined tags. Questions without tags were assigned a value of 0 for this variable.
-
-The average number of characters in each question's tags.
-
-The number of characters in the question's text.
-
-The number of characters in the user-defined device name.
-
-The ratio of the number of newlines to the number of characters in the question's text.
+\begin{itemize}
+  \item The average frequency, or proportion of times a tag appeared in all of the data, for all of a question's user-defined tags.
+Questions without tags were assigned a value of 0 for this variable.
+  \item The average number of characters in each question's tags. 
+  \item The number of characters in the question's text. 
+  \item The number of characters in the user-defined device name. 
+  \item The ratio of the number of newlines to the number of characters in the question's text.
+\end{itemize}
 
@@
 
-5-fold cross-validation was used to assess predictive performance metrics. Each training data set contained 6,208 questions. Test data sets contained 1,552 questions.
+5-fold cross-validation was used to assess predictive performance. Training data sets contained 6,208 questions. Test data sets contained 1,552 questions.
 
@@
 To assess prediction performance, those predicted ratios were entered into a separate cox regression model as the explanatory variable with the question's answer times as the survival time value.
-The resulting hazard ratio, R-square statistic, partial loglikelihood and p-value, Somers' Dxy and Concordance statistic for that model were used as indicators of the prediction model's performance.
-If the performance assessing model gave a significant results, this would indicate that the predicted hazard ratio is signficantly associated with survival time, and that our prediction model performs well.
+The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistic for that model were used as indicators of the prediction model's performance.
+If this model gave significant results, this would indicate that the predicted hazard ratio is signficantly associated with survival time, and that our prediction model performs well.
 Somers' Dxy and Concordance statistics are measures of how well the model can rank predictions.
@@
 These metrics were also computed for predictions on the training data itself.
-For each iteration, there was no signficant difference between the metrics computed on the training data predictions, and the metrics computed on the test data.
+For each of the five iterations, there was no signficant difference between the metrics computed on the training data predictions, and the metrics computed on the test data.
 Table C shows average metrics for training and test data predictions.
@@
 The final model, including all variables described above, was fit to the full data set.
-The proportional hazards assumption was assessed by using the cox.zph function of the survival package in R.
+The proportional hazards assumption was assessed by using the cox.zph function of the survival package in R (expand on this, don't mention function name).
 This test is based on the correlation between scaled Schoenfeld residuals and a function of time.
 Signficant p-values of this test indicate a possible violation of the proportional hazard assumption.
-For our model, the "Apple Product" level of the device category variable had the lowest p-value of 0.01.
-The next lowest p-values hovered around 0.04, for variables like device_length, and the Camera and Game Console levels of category.
+For our model, the ``Apple Product'' level of the device category variable had the lowest p-value of 0.01.
+The next lowest p-values hovered around 0.04, for variables like device\_length, and the Camera and Game Console levels of category.
 As Apple Product was the only major violation of this assumption, and stratifying on this variable substantially decreased the predictive power, this assumption was considered to be fine (rewrite this).
@@
 Assessing the martingale residuals for each quantitative predictor indicated that the functional form appears to be adequate.
-
-Assessing the deviance residuals shows that a considerable amount of questions have residuals with an absolute value of well over 2.5.
-However, removing those questions from the data set and and refitting the model with cross-validation techniques resulted in worse predictive accuracy.
-
-Assessing the score residuals for each predictor indicated that some questions might a strong influence on the fit of the model.
-However, similar to the case with the deviance residuals, refitting the model without those certain questions with cross-validation techniques resulted in worse predictive performance.
+Assessing the deviance residuals indicated that a considerable amount of questions were not predicted well by the model.
+Assessing the score residuals showed that some questions might have a strong influence on the fit of the model.
+However, in both cases, fitting the model without such questions resulted in worse predicted performance.
 
@@
 
-Stratification on the time of day the question was posted.
-
-Square root of the average frequency of a question's tags.
-
-Quadratic polynomial on the length of the question's text.
-
-Restricted cubic splines on the number of characters in the device name, the average length of a question's tags, and the ratio of newlines to number of characters in a question's text.
+\begin{itemize}
+  \item Stratification on the time of day the question was posted. 
+  \item Square root of the average frequency of a question's tags. 
+  \item Quadratic polynomial on the length of the question's text. 
+  \item Restricted cubic splines on the number of characters in the device name, the average length of a question's tags, and the ratio of newlines to number of characters in a question's text.
 Knots assigned to these variables were 5, 4, 4, respectively.
+\end{itemize}
 
@@
 
-While the model itself overall is significant, the metrics for the models predictive accuracy are not impressive.
-This indicates that perhaps a different model might perform better as a model to predict the survival time for questions.
-Or, a model with more quantitative variables might preform better as well.
-
-The variables described above were entered into the final cox regression model with these variable transformation
-
-Stratification on ampm: prior analysis of initial cox regression models indicated that this variable violated the proportional hazard assumption. Stratification resolved this violation.
-
-Square root of avg\_tag\_score: Viewing the distribution of answer times against the original avg\_tag\_score variable indicated heavy right skewing.
-Taking the square root of this variable decreases some of this skewing.
-
-Quadratic polynomial on text_length
-
-Restricted cubic splines were included for device_length, avg_tag_length, and newline_ratio.
-The method for fitting these variables was applied from \citep{Harrell2015}.
-Initially, these variables were fit as restricted cubic splines with 5 knots.
-The model with the lowest AIC included 5, 4, and 4 knots for device_length, avg_tag_length and newline_ratio, respectively.
-As such, this was the final form for these quantitative variables.
+While the model is significant overall, the metrics for the model's predictive accuracy are not impressive.
+This indicates that perhaps a different model might perform better in predicting the answer times for questions.
+Another suggestion is that a model with more quantitative variables might perform better as well.
 
@@
 The data contained the original category variable as defined by iFixit.
-This category variable contained NAs (how many), a result of the asker creating a question for a device not already in the website's data base.
-These missing values were coded to ``Other'' in the new categorization variable.
+This category variable contained NAs (include how many), a result of the asker creating a question for a device not already on the website's data base.
+Questions that made the device clear were categorized accordingly.
+However there were a number of questions that did not explicitly declare the device their question pertained too.
+These questions were categorized as ``Other''.
 All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category.
@@
 
-  These variables were created based on the intuition that certain topics might be more popular among the answering community, and that questions concerning these topics might recieve an answer faster than questions that don't.
-It was also based on the flip side of this idea, that certain topics might not be popular, or that some topics might be too narrow or specific and would be common among questions with long answer times or those that remained unanswered.
-To investigate this intuition, contain_answered and contain_unanswered were created.
+  These variables were created based on the intuition that certain topics might be more popular, and even unpopular, among the answering community, and that questions concerning these topics might recieve an answer faster, or slower, than questions that don't.
 
   To create these variables, the data was separated between answered and unanswered questions.
-Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions.
-These lists contained every word within the question's titles and the frequency, or number of times they occured in their respective data set.
-For each of these lists, rules were applied to determine if a word could be considered ``frequently use''.
-For frequently used words in answered questions, that word would have to appear in more than 1\% of the titles, and would have to appear in answered questions more than it appeared in unanswered questions.
-To determine the latter part, a ratio of proportions was calculated.
+Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions--containing every word within the question's titles and the frequency or the number of time they occured among answered and unanswered questions.
+For ``frequently-used'' words in answered questions, that word would have to appear in more than 1\% of answered question's titles, and would have to appear in answered questions more than it appeared in unanswered questions.
+To determine the latter, a ratio of proportions was assessed.
 This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
 As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20).
-As for unanswered questions, to be considered ``frequently'' used, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1).
+As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1).
 Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list.
 The resulting list for answered questions was 111 words, and 32 words in uanswered questions.
-Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, repsectively.
+Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.
 
@@
 !).
-This variable was created to investigate the intuition that run-on sentences, or sentences with no end punctuation marks, may take longer to receive an answer.
-
-Text\_all\_lower
-
-A logical variable indicating true if the text of the question is in all lower case.
+This variable was created to investigate if run-on sentences, or sentences with no end punctuation, take longer to receive an answer.
 
@@
 
-The frequency or “score” of a tag is defined as the proportion of times that tag appears in the entire data set.
-Avg\_tag\_score is the average of all of a question’s tag “scores” or frequencies.
-This variable was created to investigate if questions that include popular tags, or tags that are frequently used and thus have a high "score", also have faster answer times.
+This variable was created to investigate the idea that some tags are more popular, or widely used than other, and that including such tags might increase the likelihood of that question recieving an answer.
+This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
+If a question has a higher average, than at least one of it's tags are frequently used.
 This variable was created based off of findings from \cite{Bhat2014}.
-
-Avg\_tag\_length
-
-The average number of characters in each question's user-defined tags.
-If a question did not include a tag, this variable was set to 0.
-This variable, like the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
-For example, question 390989 includes tag: “i need to repair the headset because i can not find the bluetoot” and is 64 characters long, while question 410254 includes tags "sound", "sound driver" and "speaker" and has an average tag length of 8 characters.
-It's hypothesized that users who use the tagging system correctly, as in the latter example, recieve answers quicker than the user in the former.
 
@@
 
+Avg\_tag\_length
+
+The average number of characters in each question's user-defined tags.
+If a question did not include a tag, this variable was set to 0.
+This variable, like the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
+For example, question 390989 includes tag: “i need to repair the headset because i can not find the bluetoot” and is 64 characters long, while question 410254 includes tags "sound", "sound driver" and "speaker" and has an average tag length of 8 characters.
+It is hypothesized that users who use the tagging system correctly, as with the latter user, receive answers quicker than the former user.
+
 Newline\_ratio
@@
 This ratio of the number of newlines to the number of characters in the question's text.
-This variable was based on the intuition that question's that include newlines in the text, are easier to read and thus have faster answer times.
-long text and also include newlines are generally easier to read than questions that don’t include any newlines.
+This variable was based on the intuition that question's that include newlines in the text are easier to read and thus have faster answer times.
+Questions with long text that also include newlines are generally easier to read than questions that don’t include any.
 

### 2017-10-05 presentation.tex
added presentation files

\documentclass{beamer}

\usepackage[utf8]{inputenc}
\usepackage{lmodern}% http://ctan.org/pkg/lm
\usepackage[demo]{graphicx}

%Information to be included in the title page:
\title{Survival Analysis of iFixit's Online Question and Answer Forum}
\author{Lisa Oshita}
\institute{Bill and Linda Frost Fund\\
Frost Research Fellow\\
Recipient of the Frost Undergraduate Student Research Award}
\date{2017}

\begin{document}

\frame{\titlepage}

%background information on iFixit
\begin{frame}
\frametitle{iFixit}
  \begin{itemize}
    \item Founded in 2003 by two engineering students here at Cal Poly 
    \item Provides over 30,000 free repair guides
    \item Sells specialized tools/parts needed for repair 
  \end{itemize}
\end{frame}

\begin{frame}
  \begin{figure}
  \centering
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{question}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{answer}
    \end{subfigure}
  \end{figure}
\end{frame}

%some descriptive statistics of the data + answer times
%Longest answer time: 2159.022 hours (36 days)
%Shortest answer time: 0.008 hours (0.5 minutes) 
\begin{frame}

\frametitle{The Data}

  \begin{columns}
      \begin{column}{0.5\textwidth}
          \begin{figure}
            \includegraphics[width = 1.0\textwidth]{answersdist} 
          \end{figure}
      \end{column}
      \begin{column}{0.5\textwidth}
          \begin{figure}
            \includegraphics[width = 1.0\textwidth]{kmcurve}
          \end{figure}
      \end{column}
  \end{columns}

\bigskip

  \begin{itemize}
      \item 7,760 questions posted between April 8, 2017 to July 7, 2017
      \item 63.8\% recieved an answer by the download date
      \item Median survival time, the time at which 50\% of the questions in the data recieved an answer, is 9.16 hours
  \end{itemize}

\end{frame}

% describe how I analyzed the data  
% test data = 6,208 questions, training data = 1,552 questions
\begin{frame}
\frametitle{Methods}

  \begin{itemize}
      \item Used text mining and string manipulation techniques to create variables
      \item 5-fold cross validation: 5 training and test data sets 
      \item Assessed performance metrics
      \item Stratified on the time of day the question was posted
      \item Included splines on quantitative variables like the average length of a question's tags
  \end{itemize}

\end{frame}

% describe results of fitting model to full data 
\begin{frame}
\frametitle{Results}

  \begin{itemize}
      \item r-square = 0.155
  \bigskip
      \item Interpretations of coefficients:
      \begin{itemize}
          \bigskip
          \item Estimated hazard of receiving an answer is 155\% higher \\ (95\% CI (131.1\%, 182.8\%)) 
          for questions pertaining to Apple products than the hazard for questions about Android and Other Phones,
          controlling for other predictors.
          \bigskip
          \item Estimated hazard of receiving an answer is 31.3\% higher \\ (95\% CI (22.3\%, 40.8\%)) 
          for questions with titles that end in a question mark than for those without, 
          controlling for other predictors.

      \end{itemize}
  \end{itemize}

\end{frame}

% apple product: HR = 2.554, p-value <0.0001
% contain_unanswered -0.2708   0.0341 -7.94  <0.0001

\begin{frame}
\frametitle{Limitations}

  \begin{itemize}
      \item Low predictive power 
      \item More categorical variables than quantitative 
      \item Inconsistent data - there aren't any rules defining how a question should be asked
      \smallskip
      \begin{itemize}
          \item Incorrect use of the tagging system: "someone sat on it :(", "everything is wrong"
          \item Incorrectly defining the device: "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One"
      \end{itemize}
  \end{itemize}

\end{frame}

\end{document}

### 2017-10-11 Article submission/roughdraft.tex
added an abstract + some edits to the introduction

@@
 
+\section{Abstract}
+
+Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information.
+These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday.
+There are forums that cover a broad range of topics, like Yahoo!
+Answers, and forums focused on specific topics, like computer programming-focused Stack Overflow.
+An example of the latter is iFixit's CQA, Answers.
+As the main goal of iFixit is to teach people to fix their own devices by providing them with the knowledge and tools necessary, Answers---featuring questions related specifically to device repair---is a valuable source of information for this community.
+Thus, it's important that questions receive answers, and receive them quickly.
+This paper presents a survival analysis on the time until a question recieves its first answer.
+We developed a cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time.
+Though our model was signficant, its predictive accuracy was low.
+Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products receiving answers faster than others), and factors related to the question's title (e.g., whether or not it's phrased as a question, or if it contains terms considered ``unpopular'').
+For future studies, our findings can be applied to other models and further analysis of answer times in CQA.
+
 \section{Introduction}
@@
 On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers.
-Forums liek these 2 recieve around 40 million visits every month.
-These online question and answer forums are clearnly becoming popular sources of information.
+Forums like these 2 receive around 40 million visits every month.
+These online question and answer forums are clearly becoming popular sources of information.
 
@@
 iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo.
-What began as a small business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions.
-iFixit also sells the specialized tools and parts used in their repair guides, specialized tools like an iPhone 7 batter adhesive strip or a Nexus 9 LCD screen and digitizer.
-The main goal of this company is to teach people how to fix their own devices, and in extending the lifetime of their own devices, they save money and cut down on electronic waste.
-As such, this company helps thousands of people fix their devices everyday.
+What began as a business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions.
+iFixit also sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or a Nexus 9 LCD digitizers.
+The main goal of this company is to provide people with the help and tools they might need to repair their devices, and in teaching people how to extend the lifetime of their devices, it allows people to save money and cut down on electronic waste.
 
-    Along with repair guides and tool sales, another important component of this company is their online question and answer forum called Answers.
+    Along with repair guides and tool sales, another important component of this company is the online question and answer forum, Answers.
 This platform features questions related to device repair, featuring over 9,000 devices and over 100,000 solutions and answers.
-Questions on this forum range from broken devices like a jammed zipper on a Patagonia jacket, to a shattered iPhone 6 plus screen.
+Questions on this forum range from broken devices like a jammed zippers to shattered iPhone screens.
 This forum is an integral part in teaching people how to fix their own devices.
@@
 As such, investigation of response times would be both beneficial and informative.
-Analysis can reveal factors within the forum that affect how quickly questions get answers.
+Analysis can reveal factors within the forum and from elements of the questions, that affect how quickly questions get answers.
+Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.
 
-    Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.
     However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers.
@@
 This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum.
-It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the survival probability of a question.
+It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the failure probability of a question.
 

### 2017-11-01 Article submission/roughdraft.tex
edits

@@
 Answers, and forums focused on specific topics, like computer programming-focused Stack Overflow.
-An example of the latter is iFixit's CQA, Answers.
-As the main goal of iFixit is to teach people to fix their own devices by providing them with the knowledge and tools necessary, Answers---featuring questions related specifically to device repair---is a valuable source of information for this community.
-Thus, it's important that questions receive answers, and receive them quickly.
-This paper presents a survival analysis on the time until a question recieves its first answer.
-We developed a cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time.
-Though our model was signficant, its predictive accuracy was low.
-Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products receiving answers faster than others), and factors related to the question's title (e.g., whether or not it's phrased as a question, or if it contains terms considered ``unpopular'').
-For future studies, our findings can be applied to other models and further analysis of answer times in CQA.
+An example of the latter is iFixit's Answers forum.
+As the main goal of iFixit is to enable people to fix their own devices by providing them with the knowledge and tools necessary, the Answers forum, which features questions related specifically to device repair, is a valuable source of information for this community.
+Thus, it is important that questions receive timely answers.
+This paper presents a survival analysis on the time until a question receives its first answer.
+We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time.
+Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$).
+Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
+Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.
 
@@
     The CQA analyzed in this paper is iFixit's Answers forum.
-iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo.
-What began as a business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions.
-iFixit also sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or a Nexus 9 LCD digitizers.
-The main goal of this company is to provide people with the help and tools they might need to repair their devices, and in teaching people how to extend the lifetime of their devices, it allows people to save money and cut down on electronic waste.
+Founded in 2003 by two engineering students at the California Polytechnic State University in San Luis Obispo, iFixit now helps thousands of people repair their broken devices everyday.
+The company provides over 30,000 free online repair guides with pictures and step-by-step instructions, and sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or Nexus 9 LCD digitizers.
+The main goal of this company is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.
 
-    Along with repair guides and tool sales, another important component of this company is the online question and answer forum, Answers.
-This platform features questions related to device repair, featuring over 9,000 devices and over 100,000 solutions and answers.
-Questions on this forum range from broken devices like a jammed zippers to shattered iPhone screens.
-This forum is an integral part in teaching people how to fix their own devices.
-If people run into problems, they can always trust that they have a large community to turn to for help.
-Thus it's important, for both the individuals as well as iFixit, that askers get prompt answers.
-Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of Answers and iFixit.
+    As the goal of this company is to provide people with the knowledge necessary to repair their devices, an important part of this company is their CQA, called Answers.
+This platform features questions related specifically to device repair, with over 9,000 device topics and over 100,000 solutions.
+As many rely on this forum and the community of people who provide answers, for help with their own device repairs, it's important that these users receive timely answers.
+Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of the Answers forum.
 As such, investigation of response times would be both beneficial and informative.
-Analysis can reveal factors within the forum and from elements of the questions, that affect how quickly questions get answers.
+Analysis can reveal factors within the forum and from elements of the questions that affect how quickly questions are answered.
 Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.
 
-    However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers.
-A majority of the research focuses on assessing and predicting the question and answer quality.
+    However, to the best of our knowledge, analysis and prediction of answer times on CQAs have not been thoroughly investigated.
+A majority of the existing research focuses on assessing and predicting question and answer quality.
 As such, there is need for further analysis of response times in these forums.
@@
 Questions that remained unanswered were considered right-censored.
-The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum recieves an answer.
+The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum receives an answer.
 Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer.
-We are only considering the time until the question recieves its first answer.
-The time until answer value for right-censored questions, questions that did not recieve an answer, is defined as the time from when the question was posted, to the time the data was downloaded.
-Figure a shows the distribution of answer times for all questions in the data set.
+We are only considering the time until the question receives its first answer.
+The time until answer value for right-censored questions, questions that did not receive an answer, is defined as the time from when the question was posted, to the time the data was downloaded.
+Figure a shows the distribution of these answer times for all questions in the data set.
 
-    The following statistics were calculated from Kaplan-Meier estimates of survival probabilities for each question in the data.
+    The following statistics were calculated from Kaplan-Meier estimates of questions survival probability.
+In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t.
 As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions.
-In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t.
-For questions in this data set, the mean survival time, or the average time until a question recieves its first answer is 775.75 hours, or 32.32 days.
-The median survival time, the time at which 50\% of the questions in the data recieved an answer is 9.16 hours.
+For questions in this data set, the mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours.
 Table 1 provides more percentiles of survival time.
     Figure A shows the Kaplan-Meier Curve for all questions in the data.
-The curve indicates that around 100 hours, the probability that a question recieves an answer after that time hovers around 0.35.
+The curve indicates that around 100 hours after question is posted, the probability that a question receives an answer after that time hovers around 0.35.
 The survival probability never reaches 0 due to the large amount of unanswered questions.
@@
 
-    The data contained information about each question's title, text, and device, from which we created the following variables to use in the cox regression model.
+    The data contained information about each question's title, text, and device, from which we created the following variables to use in the Cox regression model.
 
-The time until a question recieves its first answer, as described above, was calculated as the time from the time the question was posted to the time the first answer was received in hours.
+The time until a question receives its first answer was calculated as the time, in hours, from the time the question was posted to the time the first answer was received.
 If the question did not receive an answer, the time until answer value was calculated as the time from when the question was posted, to the time the data was downloaded, July 7, 2017 at 2:41 PM PDT.
-The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered by the time the data set was downloaded.
+The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered.
 
@@
 \begin{itemize}
-  \item Questions were categorized based off of the devices it pertains to.
+  \item Device category the question pertains to.
 Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other.
-Home, Vehicle, Other.
 Table B shows the percentage of questions within each device category.
@@
   \item Whether or not the question's title ends in a question mark.
-  \item Whether or not the question's title begins with a "Wh" word (e.g. "What", "Where"). 
+  \item Whether or not the question's title begins with a ``Wh'' word (e.g. ``What'', ``Where''). 
   \item Whether or not the question's text contains any end punctuation marks (. ? !). 
   \item Whether or not the question's text is in all lower case. 
-  \item Whether or not the asker updated the question's text (e.g., edited or added information) sometime after posting it. 
+  \item Whether or not the asker edited or added information to the questions text sometime after posting it. 
   \item Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
-  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). 
+  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). (don't like the way this is worded) 
   \item Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
@@
 
-5-fold cross-validation was used to assess predictive performance. Training data sets contained 6,208 questions. Test data sets contained 1,552 questions.
-
-For each iteration of cross-validation, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data.
-To assess prediction performance, those predicted ratios were entered into a separate cox regression model as the explanatory variable with the question's answer times as the survival time value.
-The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistic for that model were used as indicators of the prediction model's performance.
-If this model gave significant results, this would indicate that the predicted hazard ratio is signficantly associated with survival time, and that our prediction model performs well.
-Somers' Dxy and Concordance statistics are measures of how well the model can rank predictions.
-(add to this) The concept behind these metrics came from \cite{Chen}.
-These metrics were also computed for predictions on the training data itself.
-For each of the five iterations, there was no signficant difference between the metrics computed on the training data predictions, and the metrics computed on the test data.
-Table C shows average metrics for training and test data predictions.
-The metrics taken into consideration was the average of all metrics computed on test data.
+5-fold cross-validation was used to assess predictive performance.
+Training data sets contained 6,208 questions.
+Test data sets contained 1,552 questions.
+For each iteration, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data.
+To assess prediction performance, those predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time.
+The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistics for that model were used as indicators of the prediction model's performance.
+Significant statistics for this model would indicate that the predicted hazard ratio is signficantly associated with survival time and that our modle performs well.
+The concept behind these metrics came from \cite{Chen}.
+These metrics were also computed for predictions on the training data.
+For each of the five iterations, there was no signficant difference between the metrics computed on the training data prediction, and the metrics computed ont he test data.
+Table C shows the average metrics for training and test data predictions.
+The metrics evaluated were the average of all metrics computed on the test data.
 Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.
+(should I explain more about Somers' Dxy and Concordance?)
 
 \section{Results and Discussion}
-
-The final model, including all variables described above, was fit to the full data set.
-The proportional hazards assumption was assessed by using the cox.zph function of the survival package in R (expand on this, don't mention function name).
-This test is based on the correlation between scaled Schoenfeld residuals and a function of time.
-Signficant p-values of this test indicate a possible violation of the proportional hazard assumption.
-For our model, the ``Apple Product'' level of the device category variable had the lowest p-value of 0.01.
-The next lowest p-values hovered around 0.04, for variables like device\_length, and the Camera and Game Console levels of category.
-As Apple Product was the only major violation of this assumption, and stratifying on this variable substantially decreased the predictive power, this assumption was considered to be fine (rewrite this).
-
-Assessing the martingale residuals for each quantitative predictor indicated that the functional form appears to be adequate.
-Assessing the deviance residuals indicated that a considerable amount of questions were not predicted well by the model.
-Assessing the score residuals showed that some questions might have a strong influence on the fit of the model.
-However, in both cases, fitting the model without such questions resulted in worse predicted performance.
 
@@
   \item Quadratic polynomial on the length of the question's text. 
-  \item Restricted cubic splines on the number of characters in the device name, the average length of a question's tags, and the ratio of newlines to number of characters in a question's text.
-Knots assigned to these variables were 5, 4, 4, respectively.
+  \item Restricted cubic spline with 5 knots on the number of characters in the device name.
+  \item Restricted cubic spline with 4 knots on the average number of characters in a question's tags.
+  \item Restricted cubic spline with 4 knots on the ratio of newlines to the number of characters in a question's text. 
 \end{itemize}
 
-The final model gave an AIC value of 69945.32.
-The partial loglikelihood ratio test statistic was 1307.15 with a p-value of 0.
+Assessing the indepenedence between the model's Schoenfeld residuals and time indicated that the ``Apple Product'' category of the device variable violated the proportional hazards assumption.
+Other variables at risk for violation included the Camera and Game Console categories of devices, and the number of characters in the user-defined device name.
+As ``Apple Product'' was the only major violation of this assumption, and stratifying on this variable substantially decreased predictive power, these variables were left as is.
+Visually assessing martingale residuals for each quantitative predictor indicated that functional form for each appeared to be adequate.
+Assessing the deviance residuals indicated that a considerable amount of questions were not predicted well by the model.
+Similarily, assessing the score residuals showed that some questions might have an influence on the fit of the model.
+However, fitting the model without questions identified by score and deviance residuals to be either poorly predicted or highly influential, resulted in worse predictive performance.
+Hence, all questions were left in the data set.
+
+The partial likelihood ratio test statistic was 1307.15 with a p-value of 0.
 The R-squared value for this model is 0.1555.
-Variables that proved to be significant predictors with a p-value of less than 0.01 are: new_category (apple product, camera, game console, home, pc, and vehical), contain_unanswered, title_quesitonmark, update, prior_effort, avg_tag_score and the spline on avg_tag_length.
+Significant predictors with a p-value of less than 0.01 are: the Apple product, Camera, Game Console, Home, PC, and Vehicle categories of the device variable, whether or not the question's text contained at least one term considered ``frequently used'' among answered questions, whether or not question's title ended in question mark, whether or not the asker edited the question's text after posting, whether or not the asker made effort prior to posting the question to find their own solution, the average frequency of a question's tags, and average number of characters for a question's tags.
 Include some interpretations of the hazard ratio?
 
-While the model is significant overall, the metrics for the model's predictive accuracy are not impressive.
-This indicates that perhaps a different model might perform better in predicting the answer times for questions.
-Another suggestion is that a model with more quantitative variables might perform better as well.
+While the model is significant overall, it's predictive accuracy is low.
+Table blah shows metrics for the model fit to the full data set.
+One possible explanation for this is the high number of categorical variables included in the model.
+Including more quantitative variables may improve predictive accuracy.
+The data we analyzed for this model presented some limitations.
+Currently, askers have a considerable amount of freedom in the way they ask a question.
+As a result many have incorrectly specified various input fields when asking their question.
+For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''.
+Generally, tags are not more than a couple key words that describe the topic of the question.
+Many askers on this forum included lengthy and somewhat ambiguous tags in their question.
+Another issue was the incorrect naming of the device the asker's question was about.
+A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One".
+The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributes to the model's low predictive accuracy.
+
+\section{Conclusion}
 

### 2017-11-01 presentation/presentation.tex
added acknowledgements slide

--- 2017-10-05 presentation.tex
@@
 \author{Lisa Oshita}
-\institute{Bill and Linda Frost Fund\\
-Frost Research Fellow\\
-Recipient of the Frost Undergraduate Student Research Award}
+\institute{California Polytechnic State University, San Luis Obispo}
 \date{2017}
@@
 \begin{frame}
-  \begin{figure}
-  \centering
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\linewidth]{question}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \includegraphics[width=1\linewidth]{answer}
-    \end{subfigure}
-  \end{figure}
+\begin{flushleft}
+\includegraphics[width=0.7\textwidth]{question.png}\\
+\end{flushleft}
+\vskip1ex
+\begin{flushright}
+\includegraphics[width=0.7\textwidth]{answer.png}
+\end{flushright}
 \end{frame}
 
-%some descriptive statistics of the data + answer times
-%Longest answer time: 2159.022 hours (36 days)
-%Shortest answer time: 0.008 hours (0.5 minutes) 
 \begin{frame}
@@
       \item 7,760 questions posted between April 8, 2017 to July 7, 2017
-      \item 63.8\% recieved an answer by the download date
-      \item Median survival time, the time at which 50\% of the questions in the data recieved an answer, is 9.16 hours
+      \item 63.8\% received an answer by the download date
+      \item Median survival time, the time at which 50\% of the questions in the data received an answer, is 9.16 hours
   \end{itemize}
@@
 
+%background information on iFixit
+\begin{frame}
+\frametitle{Acknowledgements}
+  \begin{itemize}
+    \item Dr. Shannon Pileggi
+    \item Anthony Pileggi
+    \item Bill and Linda Frost Fund\\
+          Frost Research Fellow\\
+          Recipient of the Frost Undergraduate Student Research Award
+  \end{itemize}
+\end{frame}
+
 \end{document}

### 2017-11-07 Article submission/roughdraft.tex
edited materials, methods, results, discussion

@@
 These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday.
-There are forums that cover a broad range of topics, like Yahoo!
-Answers, and forums focused on specific topics, like computer programming-focused Stack Overflow.
-An example of the latter is iFixit's Answers forum.
-As the main goal of iFixit is to enable people to fix their own devices by providing them with the knowledge and tools necessary, the Answers forum, which features questions related specifically to device repair, is a valuable source of information for this community.
+There are forums that cover a broad range of topics, like \textit{Yahoo!
+Answers}, and forums focused on specific topics, like computer programming-focused \textit{Stack Overflow}.
+An example of the latter is iFixit's \textit{Answers} forum.
+The \textit{Answers} forum features questions asked by users specifically related to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices.
 Thus, it is important that questions receive timely answers.
@@
     Community-driven online question and answer forums (CQA) are becoming widely used sources of information.
-These online platforms allow for anyone to ask or answer a question.
-It provides a place for people of all backgrounds and levels of expertise to provide input on a certain question.
+These online platforms allow for anyone to ask or answer a question, regardless of their background or expertise level.
 One popular CQA is Yahoo!
@@
 Forums like these 2 receive around 40 million visits every month.
-These online question and answer forums are clearly becoming popular sources of information.
 
-    The CQA analyzed in this paper is iFixit's Answers forum.
-Founded in 2003 by two engineering students at the California Polytechnic State University in San Luis Obispo, iFixit now helps thousands of people repair their broken devices everyday.
+    The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
+Founded in 2003, iFixit helps thousands of people repair their broken devices everyday.
 The company provides over 30,000 free online repair guides with pictures and step-by-step instructions, and sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or Nexus 9 LCD digitizers.
-The main goal of this company is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.
+The mission of iFixit is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.
 
-    As the goal of this company is to provide people with the knowledge necessary to repair their devices, an important part of this company is their CQA, called Answers.
-This platform features questions related specifically to device repair, with over 9,000 device topics and over 100,000 solutions.
-As many rely on this forum and the community of people who provide answers, for help with their own device repairs, it's important that these users receive timely answers.
-Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of the Answers forum.
-As such, investigation of response times would be both beneficial and informative.
-Analysis can reveal factors within the forum and from elements of the questions that affect how quickly questions are answered.
-Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.
+    As not all possible repairs are covered in the published repair guides, and users may have questions related to repair guides, iFixit's \textit{Answers} forum is another important resource.
+This platform features over 9,000 device topics and over 100,000 solutions.
+Questions on this forum range from broken devices like a jammed zipper to shattered iPhone screens.
+As many rely on this forum for help with repairs, it is important that users receive timely answers.
+Fast response times will enhance user engagement and generate more web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum.
+Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved.
 
-    However, to the best of our knowledge, analysis and prediction of answer times on CQAs have not been thoroughly investigated.
+    However, to the best of our knowledge, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated.
 A majority of the existing research focuses on assessing and predicting question and answer quality.
 As such, there is need for further analysis of response times in these forums.
-This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum.
-It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the failure probability of a question.
+This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum.
+In order to determine factors significantly related to answer time predict the failure probability of a question.
 
@@
 
-    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
+    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model to analyze response times of questions posted on \textit{Stack Overflow}, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
 
-    \citep{Mamykina2011} found that the swift answer times of Stack Overflow's community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.
+    \citep{Mamykina2011} found that the swift answer times of \textit{Stack Overflow's} community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.
 
-    \citep{Asaduzzaman2013} analyzed unanswered questions on Stack Overflow to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.
+    \citep{Asaduzzaman2013} analyzed unanswered questions on \textit{Stack Overflow} to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.
 
@@
 
-    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017, the date the data was downloaded.
-We worked exclusively with questions in English.
-Of the questions in the data set, 4,951, or 63.8\%, recieved an answer.
-Questions that remained unanswered were considered right-censored.
-The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum receives an answer.
-Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer.
-We are only considering the time until the question receives its first answer.
-The time until answer value for right-censored questions, questions that did not receive an answer, is defined as the time from when the question was posted, to the time the data was downloaded.
-Figure a shows the distribution of these answer times for all questions in the data set.
+good question ex: id 408124, 406786 (answered)
+bad question ex: id 410310, 405882 (unanswered)
 
-    The following statistics were calculated from Kaplan-Meier estimates of questions survival probability.
-In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t.
-As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions.
-For questions in this data set, the mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days.
-The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours.
-Table 1 provides more percentiles of survival time.
-    Figure A shows the Kaplan-Meier Curve for all questions in the data.
-The curve indicates that around 100 hours after question is posted, the probability that a question receives an answer after that time hovers around 0.35.
-The survival probability never reaches 0 due to the large amount of unanswered questions.
-
-    Variables created:
-
-    The data contained information about each question's title, text, and device, from which we created the following variables to use in the Cox regression model.
-
-The time until a question receives its first answer was calculated as the time, in hours, from the time the question was posted to the time the first answer was received.
-If the question did not receive an answer, the time until answer value was calculated as the time from when the question was posted, to the time the data was downloaded, July 7, 2017 at 2:41 PM PDT.
-The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered.
+The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded).
+Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date the question was posted, date the first answer was received.
+Variables derived:
 
@@
 \begin{itemize}
-  \item Device category the question pertains to.
-Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other.
-Table B shows the percentage of questions within each device category.
-  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.
-  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. 
+  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other.
+  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. 
+  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. 
   \item Whether or not the question's title ends in a question mark.
-  \item Whether or not the question's title begins with a ``Wh'' word (e.g. ``What'', ``Where''). 
+  \item Whether or not the question's title begins with a ``Wh'' word (``Why'', ``Which'', ``When'', ``Who'', ``What'', ``Where''). 
   \item Whether or not the question's text contains any end punctuation marks (. ? !). 
@@
   \item The number of characters in the user-defined device name. 
-  \item The ratio of the number of newlines to the number of characters in the question's text.
+  \item The ratio of the number of line breaks to the number of characters in the question's text.
 \end{itemize}
@@
 
-Univariate analyses for each variable of interest were performed on one of the training data sets.
-Variables with a p-value of less than 0.01 were entered into the final model.
-As the goal of this model is prediction, it was decided that all variables would be kept in the model to maintain predictive power.
+    Questions analyzed were restricted to those posted in English (97\% of the full data).
+The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer.
+Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer.
+For questions that remained unanswered by the time the data was downloaded, the time until event value is defined as the time since posting to the time the data was downloaded.
+These questions were considered right censored, meaning that the exact answer time for these questions is unknown and greater than the recorded answer time (these questions can still receive an answer after the data was downloaded, and would then have a higher answer time than what is recorded in the data).
 
-5-fold cross-validation was used to assess predictive performance.
-Training data sets contained 6,208 questions.
-Test data sets contained 1,552 questions.
-For each iteration, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data.
-To assess prediction performance, those predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time.
+As there was a considerable amount of unanswered or right-censored questions, Kaplan-Meier estimates of survival probability, which adjust to the presence of these right censored observations, were assessed prior to model fitting.
+This method factors in the number of questions that have not been answered on each ordered time interval, based on complete answer times.
+The estimates of survival probablity is the product of all probabilities up to that intervals time (fix this paragraph!!!!).
+As such, these estimates are roughly equivalent to the conditional probability that a randomly selected question receives an answer in the next moment in time, given that it has not received an answer yet.
+From these estimates, curves were constructed to examine the survival experience of questions, and mean and median percentiles of survival times were calculated.
+
+Five-fold cross-validation was used to identify potentially signficant variables and to assess model perofmrance.
+(explain cross-validation better, and why 5 fold was chosen) The full data was split into five training and five test data sets.
+Each training data set contained 6,208 questions, and each test data set contained 1,552 questions.
+To identify variables potentially associated with answer time, univariate analysis was performed on one of the training data sets.
+Each variable was entered into a Cox regression model as the single predictor with the answer time as the survival time.
+Variables with p-values of less than 0.01 for the likelihood ratio test were taken into consideration.
+
+Variables identified in univariate analysis as signficant were entered into a Cox regression model.
+To assess predictive performance, cross-validation methods were used.
+For each iteration, the model was fit to one of the training data sets.
+The resulting model was then used to calculate predicted hazard ratios on the corresponding test data.
+To assess prediction performance, the predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time.
 The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistics for that model were used as indicators of the prediction model's performance.
-Significant statistics for this model would indicate that the predicted hazard ratio is signficantly associated with survival time and that our modle performs well.
+Significant statistics for this model indicate that the predicted hazard ratio is signficantly associated with survival time and that our model performs well.
 The concept behind these metrics came from \cite{Chen}.
 These metrics were also computed for predictions on the training data.
+The metrics taken into consideration were the averages of all metrics computed on the test data.
+
+The model with the lowest AIC statistic, and most consistent performance metrics (there wasn't significant change across iterations) was taken as the final model.
+
+To assess the adequacy of functional forms of variables, Martingale residuals were assessed in plots.
+
+Deviance residuals were assessed. Score residuals
+
+Applying splines (using frank harrel's method)
+
+To assess proportional hazards assumption, cox.zph function was used in r, assesses correlation between scaled Schoenfeld residuals and time.
+
+\section{Results} 
+(7,760 questions total), percent answered 
+Figure a shows the distribution of answer times for all questions in the data set. 
+summary stats from KM estimates
+    The following statistics were calculated from Kaplan-Meier (explain what KM is) estimates of questions survival probability.
+As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions.
+For questions analyzed, the mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours.
+Table 1 provides more percentiles of survival time.
+
+        Figure A shows the Kaplan-Meier Curve for all questions in the data.
+The curve indicates that around 100 hours after question is posted, the probability that a question receives an answer after that time hovers around 0.35.
+The survival probability never reaches 0 due to the large amount of unanswered questions.
+
+results from univariate analysis
+
+results of metrics 
         For each of the five iterations, there was no signficant difference between the metrics computed on the training data prediction, and the metrics computed ont he test data.
@@
 
-\section{Results and Discussion}
-
+final model selected (with variables and transformations) 
 The final model included all variables described above, along with the following transformations:
@@
 \end{itemize}
+The partial likelihood ratio test statistic was 1307.15 with a p-value of 0.
+The R-squared value for this model is 0.1555.
+Significant predictors with a p-value of less than 0.01 are: the Apple product, Camera, Game Console, Home, PC, and Vehicle categories of the device variable, whether or not the question's text contained at least one term considered ``frequently used'' among answered questions, whether or not question's title ended in question mark, whether or not the asker edited the question's text after posting, whether or not the asker made effort prior to posting the question to find their own solution, the average frequency of a question's tags, and average number of characters for a question's tags.
+Include some interpretations of the hazard ratio?
+
+While the model is significant overall, it's predictive accuracy is low.
+Table blah shows metrics for the model fit to the full data set.
+One possible explanation for this is the high number of categorical variables included in the model.
+Including more quantitative variables may improve predictive accuracy.
+
+assessing assumptions
 
@@
 
-The partial likelihood ratio test statistic was 1307.15 with a p-value of 0.
-The R-squared value for this model is 0.1555.
-Significant predictors with a p-value of less than 0.01 are: the Apple product, Camera, Game Console, Home, PC, and Vehicle categories of the device variable, whether or not the question's text contained at least one term considered ``frequently used'' among answered questions, whether or not question's title ended in question mark, whether or not the asker edited the question's text after posting, whether or not the asker made effort prior to posting the question to find their own solution, the average frequency of a question's tags, and average number of characters for a question's tags.
-Include some interpretations of the hazard ratio?
+\section{Discussion}
 
-While the model is significant overall, it's predictive accuracy is low.
-Table blah shows metrics for the model fit to the full data set.
-One possible explanation for this is the high number of categorical variables included in the model.
-Including more quantitative variables may improve predictive accuracy.
 The data we analyzed for this model presented some limitations.
@@
 Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.
+
+111 terms found to be ``frequently-used'' among answered questions (ordered from highest frequency): 
+screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top
+
+32 terms found to be ``frequently-used'' among unanswered questions (ordered from highest frequency):
+sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit
 

### 2017-11-09 Article submission/roughdraft.tex
edited introduction, materials, methods, added conclusion + acknowledgement section

@@
 On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers.
-Forums like these 2 receive around 40 million visits every month.
+Forums like these receive around 40 million visits every month.
 
     The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit helps thousands of people repair their broken devices everyday.
-The company provides over 30,000 free online repair guides with pictures and step-by-step instructions, and sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or Nexus 9 LCD digitizers.
+Founded in 2003, iFixit helps thousands of people repair their broken devices everyday, by providing over 30,000 free online repair guides and by selling the specialized tools and parts needed for such repairs.
 The mission of iFixit is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.
 
-    As not all possible repairs are covered in the published repair guides, and users may have questions related to repair guides, iFixit's \textit{Answers} forum is another important resource.
-This platform features over 9,000 device topics and over 100,000 solutions.
-Questions on this forum range from broken devices like a jammed zipper to shattered iPhone screens.
+    As not all possible repairs are covered in the published repair guides, and users may have questions related to those guides, iFixit's \textit{Answers} forum is another important resource.
+This platform features questions related to over 9,000 devices with over 100,000 solutions.
+Questions range from broken devices like jammed zippers to shattered iPhone screens.
 As many rely on this forum for help with repairs, it is important that users receive timely answers.
@@
 
-    However, to the best of our knowledge, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated.
-A majority of the existing research focuses on assessing and predicting question and answer quality.
-As such, there is need for further analysis of response times in these forums.
-This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum.
-In order to determine factors significantly related to answer time predict the failure probability of a question.
+    However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated.
+A majority of existing research focuses on assessing and predicting question and answer quality.
+Therefore, there is need for further analysis of response times in these forums.
+This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``failure'' probability of a question.
 
@@
   \item Whether or not the question's text is in all lower case. 
-  \item Whether or not the asker edited or added information to the questions text sometime after posting it. 
-  \item Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
-  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). (don't like the way this is worded) 
-  \item Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
+  \item Whether or not the user edited or added information to the question's text sometime after posting it.
+  \item Whether or not the user included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
+  \item Whether or not the user was courteous in asking the question (e.g., ``Thank you'', ``please'').
+  \item Whether or not the user made an effort to solve the problem on their own, prior to asking the question.
   \item The day of the week the question was posted. 
@@
 \begin{itemize}
-  \item The average frequency, or proportion of times a tag appeared in all of the data, for all of a question's user-defined tags.
-Questions without tags were assigned a value of 0 for this variable.
+  \item The average tag ``score'' for all of a question's tags.
+Score is defined as the proportion of times a tag appears in all of the data.
+Questions without tags were assigned an average tag score of 0.
   \item The average number of characters in each question's tags. 
@@
 The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer.
-Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer.
-For questions that remained unanswered by the time the data was downloaded, the time until event value is defined as the time since posting to the time the data was downloaded.
-These questions were considered right censored, meaning that the exact answer time for these questions is unknown and greater than the recorded answer time (these questions can still receive an answer after the data was downloaded, and would then have a higher answer time than what is recorded in the data).
+For questions that were unanswered by the time the data was downloaded, the time until event value was defined as the time since posting to the time the data was downloaded.
+These questions were considered right censored, meaning that the exact answer time for these questions is unknown (these questions can still receive an answer after the data was downloaded, and would then have a higher observed answer time than what is in the data).
 
-As there was a considerable amount of unanswered or right-censored questions, Kaplan-Meier estimates of survival probability, which adjust to the presence of these right censored observations, were assessed prior to model fitting.
-This method factors in the number of questions that have not been answered on each ordered time interval, based on complete answer times.
-The estimates of survival probablity is the product of all probabilities up to that intervals time (fix this paragraph!!!!).
-As such, these estimates are roughly equivalent to the conditional probability that a randomly selected question receives an answer in the next moment in time, given that it has not received an answer yet.
+Prior to model fitting, Kaplan-Meier estimates of survival probability were assessed.
+This method adjusts to the presence of unanswered, or right-censored questions.
+Kaplan-Meier estimates factor in the number of questions that have not been answered on each ordered interval of complete answer times.
+The estimates of survival probablities are the products of all probabilities up to that interval's time (fix this explanation).
 From these estimates, curves were constructed to examine the survival experience of questions, and mean and median percentiles of survival times were calculated.
 
-Five-fold cross-validation was used to identify potentially signficant variables and to assess model perofmrance.
-(explain cross-validation better, and why 5 fold was chosen) The full data was split into five training and five test data sets.
+Five-fold cross-validation was used for model building.
+The full data was split into five training and five test data sets.
 Each training data set contained 6,208 questions, and each test data set contained 1,552 questions.
 To identify variables potentially associated with answer time, univariate analysis was performed on one of the training data sets.
-Each variable was entered into a Cox regression model as the single predictor with the answer time as the survival time.
-Variables with p-values of less than 0.01 for the likelihood ratio test were taken into consideration.
+Each variable of interest was entered into a Cox regression model as the single predictor.
+Variables with likelihood ratio test p-values of less than 0.01 were entered into the final model.
 
-Variables identified in univariate analysis as signficant were entered into a Cox regression model.
-To assess predictive performance, cross-validation methods were used.
-For each iteration, the model was fit to one of the training data sets.
-The resulting model was then used to calculate predicted hazard ratios on the corresponding test data.
+After identifying potentially signficant predictors, the full model's performance was assessed with cross-validation.
+For each iteration, the model was built on one of the training data sets, and then used to calculate predicted hazard ratios on the corresponding test data.
 To assess prediction performance, the predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time.
-The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistics for that model were used as indicators of the prediction model's performance.
-Significant statistics for this model indicate that the predicted hazard ratio is signficantly associated with survival time and that our model performs well.
+The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's prefromance.
+Signficant statistics would indicate a signficant association between survival time and predicted hazard.
+Somers' Dxy and Concordance statistics measured the model's predictive discrimination.
+Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard.
+Somers' Dxy is the difference between those concordance and discordant probabilities.
 The concept behind these metrics came from \cite{Chen}.
-These metrics were also computed for predictions on the training data.
-The metrics taken into consideration were the averages of all metrics computed on the test data.
+These metrics were computed for each training and test data set.
 
-The model with the lowest AIC statistic, and most consistent performance metrics (there wasn't significant change across iterations) was taken as the final model.
+To select the final model, the model with the lowest AIC statistic and most consistent performance metrics, in that the values did not change substantially from training to test data sets, was selected.
 
-To assess the adequacy of functional forms of variables, Martingale residuals were assessed in plots.
+To assess model adequacy, model residuals were examined.
+Martingale residuals plots were evaluated for each continuous predictor to assess the functional form.
+Martingale residuals are the differences between the observed number of answers received by question i, and the expected number of answers experienced by question i under the model.
+Deviance residuals, which are transformed martingale residuals with a mean of 0 and roughly normal distribution, were assessed to check for outliers, or questions with outcomes that are poorly predicted by the model.
+Score residuals, which are a measure of the approximate change in the parameter estimates that would occur if the ith question were removed from the sample, were assessed to acheck for influential questions, or questions that highly effect the parameter estimates.
 
-Deviance residuals were assessed. Score residuals
+After assessing model residuals, splines and other transformations were applied to variables.
+Restricted cubic splines were applied to continuous predictors using the method outline in \cite{Harrell2015}.
+As our data was fairly large (>100), splines of 5 knots were initially fit to each continuous predictor.
+A higher number of knots were assigned to predictors with lower p-values in the model, those thought to be more important.
+The optimal number of knots for each spline was determined by the model with the lowest AIC statistic.
+Other transformations (i.e.
+square root and polynomial terms) were also applied to variables.
 
-Applying splines (using frank harrel's method)
-
-To assess proportional hazards assumption, cox.zph function was used in r, assesses correlation between scaled Schoenfeld residuals and time.
+An assumption upon which Cox regression models are built, is the assumption of porportional hazards, or that the effect of predictors on hazard doesn't depend on time.
+To assess this assumption, the correlations between scaled Schoenfeld resiudals and a function of time were evaluated.
+Schoenfeld residuals are the differences between observed and expected predictor values for each question with a complete answer time (each question that received an answer).
+Signficant results from this test would indicate that a predictor has violated this assumption.
 
 \section{Results}
-(7,760 questions total), percent answered 
-Figure a shows the distribution of answer times for all questions in the data set. 
-summary stats from KM estimates
-    The following statistics were calculated from Kaplan-Meier (explain what KM is) estimates of questions survival probability.
-As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions.
-For questions analyzed, the mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days.
+
+  Of 7,760 questions, 63.8\% received an answer by the download date.
+Figure a shows the distribution of answer times for all questions, grouped by whether or not the question was answered.
+The following statistics were calculated from Kaplan-Meier estiamtes of survival probability.
+The mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days.
 The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours.
 Table 1 provides more percentiles of survival time.
-
-        Figure A shows the Kaplan-Meier Curve for all questions in the data.
-The curve indicates that around 100 hours after question is posted, the probability that a question receives an answer after that time hovers around 0.35.
+Figure B shows the Kaplan-Meier curve for all questions in the data.
+The curve indicates that at around 100 hours after a question is posted, the probability that a question receives an answer after that time hovers around 0.35.
 The survival probability never reaches 0 due to the large amount of unanswered questions.
 
-results from univariate analysis
+After performing univariate analysis, the predictors with partial likelihood ratio test p-values of less than 0.01 were entered into the final model.
+Results for univariate analysis can be seen in table 2 (results in pvalues dataframe).
+Each variable was entered into the Cox regression model.
 
-results of metrics 
-        For each of the five iterations, there was no signficant difference between the metrics computed on the training data prediction, and the metrics computed ont he test data.
-Table C shows the average metrics for training and test data predictions.
-The metrics evaluated were the average of all metrics computed on the test data.
-Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.
-(should I explain more about Somers' Dxy and Concordance?)
+The metrics for each iteration of cross validation are in table 3.
+Although not impressively high, the metrics did not vary substantially from test to training data, indicating that the model does not overfit.
 
-final model selected (with variables and transformations) 
-The final model included all variables described above, along with the following transformations:
-
+The final model selected contained variables defined above as well as the following transformations: 
 \begin{itemize}
@@
 \end{itemize}
-The partial likelihood ratio test statistic was 1307.15 with a p-value of 0.
-The R-squared value for this model is 0.1555.
-Significant predictors with a p-value of less than 0.01 are: the Apple product, Camera, Game Console, Home, PC, and Vehicle categories of the device variable, whether or not the question's text contained at least one term considered ``frequently used'' among answered questions, whether or not question's title ended in question mark, whether or not the asker edited the question's text after posting, whether or not the asker made effort prior to posting the question to find their own solution, the average frequency of a question's tags, and average number of characters for a question's tags.
-Include some interpretations of the hazard ratio?
 
-While the model is significant overall, it's predictive accuracy is low.
-Table blah shows metrics for the model fit to the full data set.
-One possible explanation for this is the high number of categorical variables included in the model.
-Including more quantitative variables may improve predictive accuracy.
+Results for this model can be found in table z.
 
-assessing assumptions
-
-Assessing the indepenedence between the model's Schoenfeld residuals and time indicated that the ``Apple Product'' category of the device variable violated the proportional hazards assumption.
-Other variables at risk for violation included the Camera and Game Console categories of devices, and the number of characters in the user-defined device name.
-As ``Apple Product'' was the only major violation of this assumption, and stratifying on this variable substantially decreased predictive power, these variables were left as is.
-Visually assessing martingale residuals for each quantitative predictor indicated that functional form for each appeared to be adequate.
-Assessing the deviance residuals indicated that a considerable amount of questions were not predicted well by the model.
-Similarily, assessing the score residuals showed that some questions might have an influence on the fit of the model.
-However, fitting the model without questions identified by score and deviance residuals to be either poorly predicted or highly influential, resulted in worse predictive performance.
-Hence, all questions were left in the data set.
+Assessing residuals for model adequacy indicated that assumptions were met.
+Score and deviance residuals showed that there were a few questions that were outliers or highly influenced the fit of the model.
+However, refitting the model without those questions resulted in worse predictive accuracy.
+Assessing the proportional hazards assumption indicated that the ``Apple Products'' level of device category was the only probable variable that violated the assumption, but as stratifying on device category substantially reduced predictive accuracy, it was left as is.
 
@@
 
+(Discuss importance of findings, not repeat them. A combined results + discussion section is often appropriate) 
 The data we analyzed for this model presented some limitations.
@@
 \section{Conclusion}
+
+This study developed a Cox regression model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
+Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, whether or not the user updated the question's text after the initial posting, whether or not the user indicated that he or she made an effort prior to answer their question prior to posting it (how should I write out that different knots of the splines were signficant).
+While overall the model was signficant, its predictive performance was considerably low.
+
+\section{Acknowledgement}
+
+This research is supported by the Bill and Linda Frost fund.
 

### 2017-11-11 Article submission/roughdraft.tex
revised methods section

@@
   \item Whether or not the question's title ends in a question mark.
-  \item Whether or not the question's title begins with a ``Wh'' word (``Why'', ``Which'', ``When'', ``Who'', ``What'', ``Where''). 
   \item Whether or not the question's text contains any end punctuation marks (. ? !). 
@@
   \item Whether or not the user edited or added information to the question's text sometime after posting it.
-  \item Whether or not the user included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
-  \item Whether or not the user was courteous in asking the question (e.g., ``Thank you'', ``please'').
   \item Whether or not the user made an effort to solve the problem on their own, prior to asking the question.
   \item The day of the week the question was posted. 
-  \item The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night. 
 \end{itemize}
@@
 The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer.
-For questions that were unanswered by the time the data was downloaded, the time until event value was defined as the time since posting to the time the data was downloaded.
-These questions were considered right censored, meaning that the exact answer time for these questions is unknown (these questions can still receive an answer after the data was downloaded, and would then have a higher observed answer time than what is in the data).
+For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
+These questions were considered right censored, meaning that the exact answer times for these questions are higher than the recorded times (questions can still receive answers after the download date).
 
-Prior to model fitting, Kaplan-Meier estimates of survival probability were assessed.
-This method adjusts to the presence of unanswered, or right-censored questions.
-Kaplan-Meier estimates factor in the number of questions that have not been answered on each ordered interval of complete answer times.
-The estimates of survival probablities are the products of all probabilities up to that interval's time (fix this explanation).
-From these estimates, curves were constructed to examine the survival experience of questions, and mean and median percentiles of survival times were calculated.
+Survival was defined as the event that a question remains unanswered beyond a certain time, t.
+Estimates of survival probability were generated with the Kaplan-Meier method (cite).
+This method adjusts to the presence of right-censored, or unanswered questions.
+Estimates factor in the number of questions that have not been answered on each ordered interval of complete answer times.
+The estimates of survival probablity are the products of all probabilities up to that interval's time (fix this explanation).
+From these estimates, survival curves were constructed to examine the survival experience of questions.
+Mean, median and other percentiles of survival times were also generated.
 
 Five-fold cross-validation was used for model building.
-The full data was split into five training and five test data sets.
-Each training data set contained 6,208 questions, and each test data set contained 1,552 questions.
-To identify variables potentially associated with answer time, univariate analysis was performed on one of the training data sets.
-Each variable of interest was entered into a Cox regression model as the single predictor.
-Variables with likelihood ratio test p-values of less than 0.01 were entered into the final model.
+The full data was split into five training and five test sets.
+Each training set contained 6,208 questions, and each test set contained 1,552 questions.
+Univariate analysis, performed on one of the training sets, was used to identify variables to include in the full Cox proportional hazards model.
+Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed.
+Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model.
 
-After identifying potentially signficant predictors, the full model's performance was assessed with cross-validation.
-For each iteration, the model was built on one of the training data sets, and then used to calculate predicted hazard ratios on the corresponding test data.
-To assess prediction performance, the predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time.
-The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's prefromance.
-Signficant statistics would indicate a signficant association between survival time and predicted hazard.
-Somers' Dxy and Concordance statistics measured the model's predictive discrimination.
+In each fold of cross-validation, the full model, with variables found to be signficant in univariate analysis, was built on one of the training sets and used to generate predicted hazard ratios on the corresponding test sets.
+To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time.
+The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance (cite).
+Signficant statistics would indicate high predictive accuracy.
+Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination (cite).
 Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard.
-Somers' Dxy is the difference between those concordance and discordant probabilities.
-The concept behind these metrics came from \cite{Chen}.
-These metrics were computed for each training and test data set.
+Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
+Somers' Dxy is the difference between the model's concordance statistic and discordance (0.5) (cite).
+These metrics were computed for each training and test set.
+The average of metrics across test sets was evaluated.
 
@@
 \begin{itemize}
-  \item Stratification on the time of day the question was posted. 
   \item Square root of the average frequency of a question's tags. 

### 2017-11-11 Article submission/roughdraft.tex
revised methods + results

@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-These questions were considered right censored, meaning that the exact answer times for these questions are higher than the recorded times (questions can still receive answers after the download date).
+These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times (questions can still receive answers after the download date).
 
-Survival was defined as the event that a question remains unanswered beyond a certain time, t.
+Survival was defined as the event that a question does not receive an answer beyond a certain time, t.
 Estimates of survival probability were generated with the Kaplan-Meier method (cite).
@@
 
-Five-fold cross-validation was used for model building.
+As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution).
+To build the model, five-fold cross-validation was used.
 The full data was split into five training and five test sets.
@@
 To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time.
-The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance (cite).
+The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}.
 Signficant statistics would indicate high predictive accuracy.
-Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination (cite).
+Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination.
 Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard.
 Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
-Somers' Dxy is the difference between the model's concordance statistic and discordance (0.5) (cite).
+Somers' Dxy is the difference between the model's concordance statistic and discordance (0.5) \citep{Harrell2015}.
 These metrics were computed for each training and test set.
-The average of metrics across test sets was evaluated.
+The averages of metrics across test sets were evaluated.
+The final model was selected based on AIC statistics and signficance of prediction metrics, as well as how consistent those metrics were across training and test sets.
+The final model was then fit to the full data and the same metrics were computed and compared.
 
-To select the final model, the model with the lowest AIC statistic and most consistent performance metrics, in that the values did not change substantially from training to test data sets, was selected.
+Plots of Martingale residuals, the differences between observed number of answers received by each question and the expected number of answers expereinced by each question under the model, were evaluated to assess functional form of each continuous predictor.
+Deviance residuals, transformed Martingale residuals with a mean of 0 and approximately normal distribution, were assessed to identify questions poorly predicted by the model.
+Score residuals, a measure of the approximate change in parameter estimates that would occur if a question were removed from the sample, were assessed to check for questions that highly effect parameter estimates.
 
-To assess model adequacy, model residuals were examined.
-Martingale residuals plots were evaluated for each continuous predictor to assess the functional form.
-Martingale residuals are the differences between the observed number of answers received by question i, and the expected number of answers experienced by question i under the model.
-Deviance residuals, which are transformed martingale residuals with a mean of 0 and roughly normal distribution, were assessed to check for outliers, or questions with outcomes that are poorly predicted by the model.
-Score residuals, which are a measure of the approximate change in the parameter estimates that would occur if the ith question were removed from the sample, were assessed to acheck for influential questions, or questions that highly effect the parameter estimates.
+As the data analyzed was fairly large, restricted cubic splines were applied to all continuous predictors \citep{Harrell2015}.
+Splines of five knots were initially fit to each.
+The optimal number of knots for each predictor was determined based on the model AIC statistic.
+A higher number of knots were assigned to predictors hypothesized to be more signficant, those with lower model p-values.
 
-After assessing model residuals, splines and other transformations were applied to variables.
-Restricted cubic splines were applied to continuous predictors using the method outline in \cite{Harrell2015}.
-As our data was fairly large (>100), splines of 5 knots were initially fit to each continuous predictor.
-A higher number of knots were assigned to predictors with lower p-values in the model, those thought to be more important.
-The optimal number of knots for each spline was determined by the model with the lowest AIC statistic.
-Other transformations (i.e.
-square root and polynomial terms) were also applied to variables.
-
-An assumption upon which Cox regression models are built, is the assumption of porportional hazards, or that the effect of predictors on hazard doesn't depend on time.
-To assess this assumption, the correlations between scaled Schoenfeld resiudals and a function of time were evaluated.
-Schoenfeld residuals are the differences between observed and expected predictor values for each question with a complete answer time (each question that received an answer).
-Signficant results from this test would indicate that a predictor has violated this assumption.
+Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for each question that received an answer, and a function of time were examined to assess the proportional hazards assumption that underlies a Cox proportional hazards model.
+Proportional hazards assumes that the effect of predictors on hazard does not depend on time.
+Significant correlations would indicate that a predictor has violated this assumption.
 
@@
   Of 7,760 questions, 63.8\% received an answer by the download date.
-Figure a shows the distribution of answer times for all questions, grouped by whether or not the question was answered.
-The following statistics were calculated from Kaplan-Meier estiamtes of survival probability.
-The mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days.
-The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours.
+Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
+The following statistics were calculated from Kaplan-Meier estimates of survival probability.
+The mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions in the data received an answer was 9.16 hours.
 Table 1 provides more percentiles of survival time.
 Figure B shows the Kaplan-Meier curve for all questions in the data.
-The curve indicates that at around 100 hours after a question is posted, the probability that a question receives an answer after that time hovers around 0.35.
-The survival probability never reaches 0 due to the large amount of unanswered questions.
+The curve indicates that at around 100 hours after a question is posted, survival probability remains constant at around 0.35.
 
-After performing univariate analysis, the predictors with partial likelihood ratio test p-values of less than 0.01 were entered into the final model.
-Results for univariate analysis can be seen in table 2 (results in pvalues dataframe).
-Each variable was entered into the Cox regression model.
+Predictors with p-values less than 0.01 in univariate analysis are in table b, and were included in the full Cox model for cross-validation.
+Average metrics for test and training sets are in table c.
+Although not impressively high, metrics did not change substantially from training to test set, indicating that the model does not overfit.
+Restricted cubic splines were fit to continous predictors.
+Splines of five knots were fit to the average frequency of question's tags as well as to the number of characters in the user-defined device name.
+Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text.
+Results of cross-validation for the model including the splines are in table d.
+As refitting the model without insignificant predictors did not effect predictive performance, all variables were included.
+The final model, with all variables described above including splines, was fit to the full data.
 
-The metrics for each iteration of cross validation are in table 3.
-Although not impressively high, the metrics did not vary substantially from test to training data, indicating that the model does not overfit.
-
-The final model selected contained variables defined above as well as the following transformations: 
-\begin{itemize}
-  \item Square root of the average frequency of a question's tags. 
-  \item Quadratic polynomial on the length of the question's text. 
-  \item Restricted cubic spline with 5 knots on the number of characters in the device name.
-  \item Restricted cubic spline with 4 knots on the average number of characters in a question's tags.
-  \item Restricted cubic spline with 4 knots on the ratio of newlines to the number of characters in a question's text. 
-\end{itemize}
-
-Results for this model can be found in table z.
-
-Assessing residuals for model adequacy indicated that assumptions were met.
-Score and deviance residuals showed that there were a few questions that were outliers or highly influenced the fit of the model.
-However, refitting the model without those questions resulted in worse predictive accuracy.
-Assessing the proportional hazards assumption indicated that the ``Apple Products'' level of device category was the only probable variable that violated the assumption, but as stratifying on device category substantially reduced predictive accuracy, it was left as is.
+Score and deviance residuals of the final model identified outliers and highly influential questions.
+However, because refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data.
+Assessing the proportional hazards assumption indicated that several levels of the device category predictor were in violation.
+But as stratifying on this predictor substantially decreased predictive accuracy, the variable was left as is.
+Statistics and parameter coefficients of the final model are in table c.
 

### 2017-11-13 article submission/data/import the data.Rmd
rearranged files

---
title: "Practice"
author: "Shannon Pileggi"
date: "June 23, 2017"
output: html_document
---

#Import data

```{r}
#getwd() identifies the working directory associated with this Git Hub project

#file.path() creates a file path name that concatenates the working directory with the sub folder for the data, and also automatically adjusts the direction of slashes for your operating system
dir <- file.path(getwd(),"data")

#Now we append the name of the data set to the directory
out <- read.csv(file.path(dir, "answers_data.csv"))

summary(out)

```

### 2017-11-13 article submission/graphics.Rmd
rearranged files

---
title: "Tables/Graphs for Article"
author: "Lisa Oshita"
date: "11/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
list <- oshitar::variable_setup(out)
x <- list[[1]]
```

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
                   rcs(avg_tag_score, 5) + rcs(text_length, 4) + rcs(device_length, 5) + 
                   rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
```

### Distribution of answer times (Figure 1)

```{r}
x$Answered <- NA
x$Answered[x$answered == 1] <- "Answered"
x$Answered[x$answered == 0] <- "Unanswered"

ggplot(x, aes(x = time_until_answer, fill = Answered)) +
  geom_histogram(bins = 15, alpha = 0.5, position = "identity") + 
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 15),
        plot.title = element_text(size = 17),
        legend.position = c(0.8, 0.8),
        legend.text = element_text(size = 13)) + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_x_continuous("Time (hrs)") + 
  scale_y_continuous("Number of Questions") + 
  ggtitle("Distribution of Answer Times")
```

### KM Curve (Figure 2)

```{r}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
KM <- survfit(surv_object ~ 1, conf.type = "log-log")

# dashed line indicates the median survival time
ggsurvplot(KM, data = x, 
           risk.table = FALSE, 
           cumevents = FALSE, 
           conf.int = TRUE, conf.int.style = "step", 
           censor = FALSE,
           surv.median.line = "hv", 
           xlab = "Time (hours)", 
           xlim = c(0, 200), break.x.by = 20,
           ylim = c(0, 1), break.y.by = 0.1,
           surv.plot.height = 1, ggtheme = theme_bw(), 
           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE,
           title = "Kaplan-Meier Curve for all Questions",
           legend = "none")
```

### Table of percentiles (Table 1)

```{r}
q <- quantile(KM, c(0.25, 0.50, 0.55, 0.58, 0.60, 0.64)) # 64% is largest available survival probability
quantiles <- q$quantile
quantilesdf <- data.frame(Percent = names(quantiles), Time = round(quantiles, 2))
colnames(quantilesdf) <- c("Percent Answered", "Time (Hours)")
quantilesdf
```

### Univariate analysis results (Table 2) see univariate_analysis file

### Average CV metrics (Table 3 + 4) 
```{r}
# function for cross validation
crossval <- function(vars, train, test) {
  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
  model <- rms::cph(as.formula(formula), data = train)

  train[["predictions"]] <- exp(predict(model, type = "lp"))
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

  # predicting on test data
  test[["predictions"]] <- exp(predict(model, newdata = test, type = "lp"))

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             R2 = round(metric$stats[8], 2),
                             AIC = stats::AIC(metric1, k = 2),
                             Dxy = round(metric1$stats[9],2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

  # returns data frame with train/test metrics 
  statistics <- rbind(train_metrics, test_metrics)
  rownames(statistics) <- c("Training Data", "Test Data")
  return(statistics)
}

# function to average performance metrics, takes list of output from crossval
get_avgmetrics <- function(list) {
  avg <- rbind(train_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][1,]))), test_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][2,]))))
  return(avg)
}

trains <- list(train1, train2, train3, train4, train5)
trains <- purrr::map(trains, ~as.data.frame(.))
tests <- list(test1, test2, test3, test4, test5)
tests <- purrr::map(tests, ~as.data.frame(.))

# ------------------------------------------
# without splines
vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + avg_tag_score + text_length + device_length + avg_tag_length + newline_ratio"

cv_results <- purrr::map2(trains, tests, ~crossval(vars, .x, .y))
avg_results <- get_avgmetrics(cv_results)
avg_results

# ------------------------------------------
# with splines
vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(text_length, 4) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"

cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
avg_results1 <- get_avgmetrics(cv_results1)
avg_results1
```

# residuals

```{r}
final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                  contain_unanswered + contain_answered + title_questionmark + 
                  text_contain_punct + text_all_lower + update + prior_effort + weekday + 
                  sqrt(avg_tag_score) + rcs(text_length, 4) + rcs(device_length, 5) + 
                  rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                  data = x, x = TRUE, 
                  y = TRUE, surv = TRUE)
final

x$mart <- residuals(final, type = "martingale")

ggplot(x, aes(x = avg_tag_score, y = mart)) + 
  geom_point() + 
  geom_smooth() + 
  ggtitle(paste("Martingale Residuals for average_tag_score")) + 
  scale_x_continuous("Average Tag Score (square root)")

plotm <- function(var) {
  ggplot(x, aes(x = x[[var]], y = mart)) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Martingale Residuals for", var)) + 
    scale_x_continuous(var)
}
plotm("avg_tag_score")
plotm("text_length")
plotm("device_length")
plotm("avg_tag_length")
plotm("newline_ratio")

```

# final model on full data (table 5)

```{r}
# model statistics + parameters
# figure out how to get p-values 
parameterdf <- data.frame(variable = names(final$coefficients),
                          coefficients = round(unname(final$coefficients), 3))
parameterdf

modelstats <- data.frame(statistic = names(final$stats), 
                         value = round(unname(final$stats), 3))
modelstats

# ------------------------------------------
# cross-validation metrics 
x$predictions <- exp(predict(final, type = "lp"))

metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(metric, k = 2) # 83125.55

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics 
```

### 2017-11-13 Article submission/roughdraft.tex
edited results

@@
     However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated.
-A majority of existing research focuses on assessing and predicting question and answer quality.
-Therefore, there is need for further analysis of response times in these forums.
-This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``failure'' probability of a question.
+As the majority of existing research focuses on assessing and predicting question and answer quality, there is need for further analysis of response times in these forums.
+This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.
 
@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times (questions can still receive answers after the download date).
+These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).
 
@@
 Each training set contained 6,208 questions, and each test set contained 1,552 questions.
-Univariate analysis, performed on one of the training sets, was used to identify variables to include in the full Cox proportional hazards model.
+Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model.
 Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed.
@@
 Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
-The following statistics were calculated from Kaplan-Meier estimates of survival probability.
-The mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
+Figure B shows the Kaplan-Meier curve of survival probability for all questions in the data.
+The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
 The median survival time, the time at which 50\% of the questions in the data received an answer was 9.16 hours.
-Table 1 provides more percentiles of survival time.
-Figure B shows the Kaplan-Meier curve for all questions in the data.
-The curve indicates that at around 100 hours after a question is posted, survival probability remains constant at around 0.35.
+Table 1 provides additional percentiles of survival time.
 
-Predictors with p-values less than 0.01 in univariate analysis are in table b, and were included in the full Cox model for cross-validation.
+Predictors with p-values less than 0.01 in univariate analysis, shown in table b, were included in the full Cox model for cross-validation.
 Average metrics for test and training sets are in table c.
 Although not impressively high, metrics did not change substantially from training to test set, indicating that the model does not overfit.
+Examining model parameters of the training models showed that the the average frequency of a question's tags had an extremely high coefficient (> 20).
+To address this, a square root transformation was applied.
 Restricted cubic splines were fit to continous predictors.
-Splines of five knots were fit to the average frequency of question's tags as well as to the number of characters in the user-defined device name.
+A spline of five knots was fit to the number of characters in the user-defined device name.
 Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text.

### 2017-11-13 Article submission/roughdraft.tex
edited results

@@
 
-Predictors with p-values less than 0.01 in univariate analysis, shown in table b, were included in the full Cox model for cross-validation.
-Average metrics for test and training sets are in table c.
-Although not impressively high, metrics did not change substantially from training to test set, indicating that the model does not overfit.
-Examining model parameters of the training models showed that the the average frequency of a question's tags had an extremely high coefficient (> 20).
-To address this, a square root transformation was applied.
-Restricted cubic splines were fit to continous predictors.
+Predictors with p-values less than 0.01 in univariate analysis are shown in table b.
+The univariate model for the average frequency of a question's tags displayed an extrememly high hazard coefficient (33.8).
+To address this, a square root transformation was used on the variable, bringing the hazard coefficient to 4.2.
+Average performance metrics for the full model and its predictions for test and training sets, found in table c, were considerably low.
+However, metrics did not change substantially from training to test set, indicating that the model does not overfit.
 A spline of five knots was fit to the number of characters in the user-defined device name.

### 2017-11-13 model fitting/final_model.Rmd
edited final model

@@
 out <- read.csv(file.path(dir, "answers_data.csv"))
-x <- oshitar::variable_setup(out)
+list <- oshitar::variable_setup(out)
+x <- list[[1]]
+x1 <- as.data.frame(x)
 
@@
 ```
+
+##### Cross validation
 
@@
 
-#### Variables:
-
-* new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, degree = 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)
-* device_length has 5 knots since hypothesized that it's a better predictor, others only have 4 (reccomended in Regression Modelling Strategies text)
-
-```{r, echo = FALSE}
-# build model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
-
-trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
-AIC(trainmodel, k = 2) # 54421.88
-trainmodel
-```
-
-##### Assessing residuals/PH assumption
-
-```{r, echo = FALSE}
-#----Martingale residuals----------------------------------------------
-train1$mart <- residuals(trainmodel, type = "martingale")
-
-ggplot(train1, aes(x = sqrt(avg_tag_score), y = mart)) + 
-  geom_point() + 
-  geom_smooth(method = "loess") + 
-  ggtitle(paste("Martingale Residuals for sqrt(average_tag_score)")) + 
-  scale_x_continuous("Average Tag Score (square root)") 
-# functional form seems adequate
-
-#----Deviance residuals------------------------------------------------
-train1$deviance <- residuals(trainmodel, type = "deviance")
-ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
-  geom_point() + 
-  scale_x_continuous("Question index") + 
-  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
-  ggtitle("Deviance Residuals")
-# identify questions with residuals > |2.5| (questions poorly predicted by the model)
-
-# examining all questions with > |2.5|
-outliers <- train1 %>%
-  dplyr::filter(abs(deviance) > 2.5)
-# 117 questions in training data set have deviance residuals > 2.5 
-# all were answered with time_until_answer < 1 hr (except for 2 which have time_until_answer > 1050 hours)
-
-#----Schoenfeld residuals----------------------------------------------
-schoen <- as.data.frame(residuals(trainmodel, type = "schoenfeld"))
-schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)
-
-# function to plot schoenfeld residuals for each predictor
-plot_schoen <- function(var) {
-  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
-    geom_point() + 
-    geom_smooth() + 
-    ggtitle(paste("Schoenfeld Residuals for", var)) + 
-    scale_y_continuous("Residuals")
-}
-purrr::map(names(schoen)[-ncol(schoen)], plot_schoen)
-
-# formal test of PH assumption 
-options(scipen=999)
-ph_test <- data.frame(predictors = rownames(cox.zph(trainmodel)$table), cox.zph(trainmodel)$table) 
-rownames(ph_test) = NULL
-ph_test <- ph_test %>% arrange(p) 
-# first term of device_length, Apple Product, Camera, Game Console violate PH (stratifying on new_category decreases predictive ability)
-
-#----Score residuals--------------------------------------------------
-# check for influential observations
-score <- as.data.frame(residuals(trainmodel, type = "score"))
-
-# function to plot score residuals
-plot_score <- function(column) {
-  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
-    geom_point() + 
-    geom_smooth() + 
-    ggtitle(paste("Score residuals for", column)) + 
-    scale_y_continuous("Score Residuals") + 
-    scale_x_continuous("Question index")
-}
-
-purrr::map(names(score), ~plot_score(.))
-# tried removing influential questions and doing cross validation: models fit on data with influential questions removed didn't perform as well on the test data compared to models fit on full data
-
-```
-
-##### Cross validation
-
 ```{r, functions for cv, include = FALSE}
-# function to perform cross validation, vars should be string: "new_category + new_user..."
+# function for cross validation, vars should be string: "new_category + new_user..."
 crossval <- function(vars, train, test) {
@@
 
+vars3 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + rcs(avg_tag_score, 5) + rcs(text_length, 4) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"
+
+vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + avg_tag_score + text_length + device_length + avg_tag_length + newline_ratio"
+
 trains <- list(train1, train2, train3, train4, train5)
@@
 
-(cv_results <- purrr::map2(trains, tests, ~crossval(vars, .x, .y)))
+(cv_results <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y)))
+avg_1 <- get_avgmetrics(cv_results)
+avg_1
 
-get_avgmetrics(cv_results)
-get_avgdiff(cv_results) # metrics don't change that much between fitting model on training and test data sets
+(cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y)))
+avg_2 <- get_avgmetrics(cv_results1)
+avg_2
+
+avg_1; avg_2
 ```
@@
 ```{r, echo = FALSE}
-dd <- datadist(x)
+dd <- datadist(x1)
 options(datadist = "dd")
-final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
+final1 <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                                contain_unanswered + contain_answered + title_questionmark + 
@@
                              y = TRUE, surv = TRUE)
+final1
+AIC(final1, k = 2) # 69945.32
+(val <- rms::validate(final1, method = "crossvalidation", bw = F, dxy = TRUE, u = 0.5))
+
+final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
+                  contain_unanswered + contain_answered + title_questionmark + 
+                  text_contain_punct + text_all_lower + update + prior_effort + weekday + 
+                  rcs(avg_tag_score, 5) + rcs(text_length, 4) + rcs(device_length, 5) + 
+                  rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
+                  data = x1, x = TRUE, 
+                  y = TRUE, surv = TRUE)
 final
-  AIC(final, k = 2) # 69945.32
-
-validation <- rms::validate(final, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
-validation
+AIC(final, k = 2)
 ```
@@
 ```
+
+##### Assessing residuals/PH assumption
+
+```{r, echo = FALSE}
+#----Martingale residuals----------------------------------------------
+train1$mart <- residuals(trainmodel, type = "martingale")
+
+ggplot(train1, aes(x = sqrt(avg_tag_score), y = mart)) + 
+  geom_point() + 
+  geom_smooth(method = "loess") + 
+  ggtitle(paste("Martingale Residuals for sqrt(average_tag_score)")) + 
+  scale_x_continuous("Average Tag Score (square root)") 
+# functional form seems adequate
+
+#----Deviance residuals------------------------------------------------
+train1$deviance <- residuals(trainmodel, type = "deviance")
+ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
+  geom_point() + 
+  scale_x_continuous("Question index") + 
+  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
+  ggtitle("Deviance Residuals")
+# identify questions with residuals > |2.5| (questions poorly predicted by the model)
+
+# examining all questions with > |2.5|
+outliers <- train1 %>%
+  dplyr::filter(abs(deviance) > 2.5)
+# 117 questions in training data set have deviance residuals > 2.5 
+# all were answered with time_until_answer < 1 hr (except for 2 which have time_until_answer > 1050 hours)
+
+#----Schoenfeld residuals----------------------------------------------
+schoen <- as.data.frame(residuals(trainmodel, type = "schoenfeld"))
+schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)
+
+# function to plot schoenfeld residuals for each predictor
+plot_schoen <- function(var) {
+  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Schoenfeld Residuals for", var)) + 
+    scale_y_continuous("Residuals")
+}
+purrr::map(names(schoen)[-ncol(schoen)], plot_schoen)
+
+# formal test of PH assumption 
+options(scipen=999)
+ph_test <- data.frame(predictors = rownames(cox.zph(finalz)$table), cox.zph(finalz)$table) 
+rownames(ph_test) = NULL
+ph_test <- ph_test %>% arrange(p) 
+# first term of device_length, Apple Product, Camera, Game Console violate PH (stratifying on new_category decreases predictive ability)
+
+#----Score residuals--------------------------------------------------
+# check for influential observations
+score <- as.data.frame(residuals(trainmodel, type = "score"))
+
+# function to plot score residuals
+plot_score <- function(column) {
+  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
+    geom_point() + 
+    geom_smooth() + 
+    ggtitle(paste("Score residuals for", column)) + 
+    scale_y_continuous("Score Residuals") + 
+    scale_x_continuous("Question index")
+}
+
+purrr::map(names(score), ~plot_score(.))
+# tried removing influential questions and doing cross validation: models fit on data with influential questions removed didn't perform as well on the test data compared to models fit on full data
+
+```

### 2017-11-13 model fitting/univariate_analysis.Rmd
added code for graphic to include in article

@@
 ```{r, include = FALSE}
-x <- oshitar::setup()
-library(survival)
-library(stringr)
-library(rebus)
-library(dplyr)
-library(stats)
-library(ggplot2)
+dir <- file.path(getwd(),"data")
+out <- read.csv(file.path(dir, "answers_data.csv"))
+list <- oshitar::variable_setup(out)
+x <- list[[1]]
+
+library(survival); library(stringr); library(rebus)
+library(dplyr); library(stats); library(ggplot2)
 ```
@@
 
-* cross validation paths stored in splitPlan
-* set seed for reproducible results
-
 ```{r, echo = FALSE}
 set.seed(444)
-splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
-str(splitPlan)
+plan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
 ```
 
-### Analysis on test data
+### Analysis on training data
 
-```{r, data and text variables, include = FALSE}
-train1 <- x[splitPlan[[1]]$train, ]
+```{r, include = FALSE}
+train1 <- x[plan[[1]]$train, ]
 
-pvalues <- data.frame(variable = character(), pvalue = numeric())
+pvalues <- data.frame(variable = character(), 
+                      pvalue = numeric())
 
-#function to get summary of cox model + append pvalue of variable from loglik test to data frame
+# function to get summary of cox model + append pvalue of variable from loglik test to df
+#===================================================================
 get_pvalue <- function(variable, factor = FALSE) {
@@
   summary <- summary(coxmodel)
-  df <- data.frame(variable = variable, pvalue = unname(summary$logtest[[3]]))
+  df <- data.frame(variable = variable, 
+                   pvalue = unname(summary$logtest[[3]]))
   pvalues <- rbind(pvalues, df)
@@
 pvalues <- get_pvalue("n_images")
-
-# new_n_images (recoding to group questions with >= 6 images) 
-train1$new_n_images <- as.character(train1$n_images)
-train1$new_n_images[train1$n_images >= 6] <- ">= 6"
-pvalues <- get_pvalue("new_n_images")
-
 pvalues <- get_pvalue("n_tags", factor = TRUE)
@@
 pvalues <- get_pvalue("weekday")
-pvalues <- get_pvalue("hour", factor = TRUE)
 pvalues <- get_pvalue("ampm")
@@
 pvalues <- get_pvalue("device_length")
-pvalues <- get_pvalue("text_till_punct")
 pvalues <- get_pvalue("text_contain_punct")
@@
 pvalues <- get_pvalue("avg_tag_score")
-pvalues <- get_pvalue("num_freq_tags")
 pvalues <- get_pvalue("contain_unanswered")
@@
 #===================================================================
-
 # title_length
@@
 pvalues <- get_pvalue_new("title_length_sqrt", fit = sqrt_title)
-
-# quadratic/cubic terms
 
@@
 #===================================================================
-
 # text_length
@@
 
-# quadratic/cubic terms
-
 text2 <- coxph(Surv(time_until_answer, answered) ~ text_length + I(text_length^2), data = train1)
@@
 #===================================================================
-
 # device_length
@@
 pvalues <- get_pvalue_new("device_length_sqrt", fit = sqrt_dev)
-
-# quadratic/cubic terms
 
@@
 #===================================================================
-
 # newline_ratio
@@
 pvalues <- get_pvalue_new("newline_ratio_sqrt", fit = fit8)
-
-# quadratic/cubic terms
 
@@
 #===================================================================
-
 # avg_tag_length
@@
 pvalues <- get_pvalue_new("avg_tag_length_sqrt", fit = fit10)
-
-# quadratic/cubic terms
 
@@
 #===================================================================
-
 # avg_tag_score
@@
 pvalues <- get_pvalue_new("avg_tag_score_sqrt", fit = fit12)
-
-# quadratic/cubic terms
 
@@
 options(scipen=999)
-(pvalues <- pvalues %>%
-  arrange(pvalue))
+pvalues <- pvalues %>% arrange(pvalue)
 ```
+
+### Include in the article
+
+```{r}
+train1 <- x[plan[[1]]$train, ]
+
+pvalues <- data.frame(variable = character(), 
+                      pvalue = numeric())
+
+# function to get summary of cox model + append pvalue of variable from loglik test to df
+# ---------------------------------------------------------------------------------------
+get_pvalue <- function(variable, factor = FALSE) {
+  if (factor == FALSE){
+    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
+  } else {
+    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
+  }
+  summary <- summary(coxmodel)
+  df <- data.frame(variable = variable, 
+                   pvalue = unname(summary$logtest[[3]]))
+  pvalues <- rbind(pvalues, df)
+  return(pvalues)
+}
+# ---------------------------------------------------------------------------------------
+
+pvalues <- get_pvalue("new_category")
+pvalues <- get_pvalue("new_user")
+pvalues <- get_pvalue("title_questionmark")
+pvalues <- get_pvalue("text_contain_punct")
+pvalues <- get_pvalue("weekday")
+pvalues <- get_pvalue("title_length")
+pvalues <- get_pvalue("text_length")
+pvalues <- get_pvalue("device_length")
+pvalues <- get_pvalue("text_all_lower")
+pvalues <- get_pvalue("prior_effort")
+pvalues <- get_pvalue("update")
+pvalues <- get_pvalue("newline_ratio")
+pvalues <- get_pvalue("avg_tag_length")
+pvalues <- get_pvalue("avg_tag_score")
+pvalues <- get_pvalue("contain_unanswered")
+pvalues <- get_pvalue("contain_answered")
+
+options(scipen=999)
+pvalues <- pvalues %>% arrange(pvalue)
+
+rms::cph(Surv(time_until_answer, answered) ~ avg_tag_score, data = x)
+rms::cph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = x)
+```

### 2017-11-15 Article submission/roughdraft.tex
edited intro + appendix

@@
 
-Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information.
-These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday.
-There are forums that cover a broad range of topics, like \textit{Yahoo!
-Answers}, and forums focused on specific topics, like computer programming-focused \textit{Stack Overflow}.
+Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday.
+Forums can cover a broad range of topics, like \textit{Yahoo!
+Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}.
 An example of the latter is iFixit's \textit{Answers} forum.
-The \textit{Answers} forum features questions asked by users specifically related to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices.
-Thus, it is important that questions receive timely answers.
+The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices.
+As such, it is important that questions receive timely answers.
 This paper presents a survival analysis on the time until a question receives its first answer.
@@
 These online platforms allow for anyone to ask or answer a question, regardless of their background or expertise level.
-One popular CQA is Yahoo!
-Answers, featuring questions of all topics and expertise levels.
-On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers.
-Forums like these receive around 40 million visits every month.
+Forums can receive around 40 million visits every month.
 
     The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit helps thousands of people repair their broken devices everyday, by providing over 30,000 free online repair guides and by selling the specialized tools and parts needed for such repairs.
-The mission of iFixit is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.
+Founded in 2003, iFixit's mission is to enable people to repair their broken devices, effectively saving them money and reducing electronic waste.
+The company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
 
     As not all possible repairs are covered in the published repair guides, and users may have questions related to those guides, iFixit's \textit{Answers} forum is another important resource.
-This platform features questions related to over 9,000 devices with over 100,000 solutions.
+This platform features questions pertaining to over 9,000 devices with over 100,000 solutions.
 Questions range from broken devices like jammed zippers to shattered iPhone screens.
@@
 Currently, askers have a considerable amount of freedom in the way they ask a question.
-As a result many have incorrectly specified various input fields when asking their question.
+As a result many incorrectly specify various input fields.
 For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''.
 Generally, tags are not more than a couple key words that describe the topic of the question.
-Many askers on this forum included lengthy and somewhat ambiguous tags in their question.
-Another issue was the incorrect naming of the device the asker's question was about.
+Many users on this forum included lengthy and somewhat ambiguous tags in their question.
+Another issue was the incorrect naming of the device the user's question was about.
 A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One".
-The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributes to the model's low predictive accuracy.
+The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributed to the model's low predictive accuracy.
 
@@
 
-The data contained the original category variable as defined by iFixit.
+The original device categorization variable, as defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+This variable also contained a considerable amount of NAs (1954, or 25.2\% of all questions).
+NAs are a result of users asking questions for devices not already in the website's database, or from the user incorrectly defining the device.
+
 This category variable contained NAs (include how many), a result of the asker creating a question for a device not already on the website's data base.

### 2017-11-15 Article submission/roughdraft.tex
edited results

@@
   \item The average tag ``score'' for all of a question's tags.
-Score is defined as the proportion of times a tag appears in all of the data.
+A tag score is defined as the proportion of times a tag appears in all of the data.
 Questions without tags were assigned an average tag score of 0.
@@
 
-Survival was defined as the event that a question does not receive an answer beyond a certain time, t.
-Estimates of survival probability were generated with the Kaplan-Meier method (cite).
-This method adjusts to the presence of right-censored, or unanswered questions.
-Estimates factor in the number of questions that have not been answered on each ordered interval of complete answer times.
-The estimates of survival probablity are the products of all probabilities up to that interval's time (fix this explanation).
-From these estimates, survival curves were constructed to examine the survival experience of questions.
-Mean, median and other percentiles of survival times were also generated.
+Survival was defined as the event that a question did not receive an answer beyond a certain time, t.
+Estimates of survival probability were generated with the Kaplan-Meier method (cite), which adjusts to the presence of right-censored, or unanswered questions.
+This method factors in the number of questions that have not been answered on each ordered interval of complete answer times.
+Estimates of survival probablity are the products of all probabilities up to that interval's time (redo this).
+From these estimates, survival curves were constructed to examine the survival experience of questions, and mean, median and other percentiles of survival times were also generated.
 
-As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution).
+As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)).
 To build the model, five-fold cross-validation was used.
@@
 Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model.
-Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed.
-Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model.
+Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied.
+Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed.
+Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.
 
@@
 Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
-Somers' Dxy is the difference between the model's concordance statistic and discordance (0.5) \citep{Harrell2015}.
+Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}.
 These metrics were computed for each training and test set.
 The averages of metrics across test sets were evaluated.
-The final model was selected based on AIC statistics and signficance of prediction metrics, as well as how consistent those metrics were across training and test sets.
+The final model was selected based on AIC statistics and the signficance of prediction metrics, as well as how consistent those metrics were across training and test sets.
 The final model was then fit to the full data and the same metrics were computed and compared.
 
-Plots of Martingale residuals, the differences between observed number of answers received by each question and the expected number of answers expereinced by each question under the model, were evaluated to assess functional form of each continuous predictor.
-Deviance residuals, transformed Martingale residuals with a mean of 0 and approximately normal distribution, were assessed to identify questions poorly predicted by the model.
+Plots of Martingale residuals, the differences between observed number of answers received by each question and the expected number of answers expererienced by each question under the model, were evaluated to assess functional form of each continuous predictor.
+Deviance residuals, which are transformed Martingale residuals with a mean of 0 and an approximately normal distribution, were assessed to identify questions poorly predicted by the model.
 Score residuals, a measure of the approximate change in parameter estimates that would occur if a question were removed from the sample, were assessed to check for questions that highly effect parameter estimates.
 
-As the data analyzed was fairly large, restricted cubic splines were applied to all continuous predictors \citep{Harrell2015}.
+Restricted cubic splines were applied to all continuous predictors \citep{Harrell2015}.
 Splines of five knots were initially fit to each.
+A higher number of knots were assigned to predictors hypothesized to be more signficant, those with lower model p-values.
 The optimal number of knots for each predictor was determined based on the model AIC statistic.
-A higher number of knots were assigned to predictors hypothesized to be more signficant, those with lower model p-values.
 
-Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for each question that received an answer, and a function of time were examined to assess the proportional hazards assumption that underlies a Cox proportional hazards model.
+Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that underlies a Cox model.
 Proportional hazards assumes that the effect of predictors on hazard does not depend on time.
-Significant correlations would indicate that a predictor has violated this assumption.
+Significant correlations indicate that a predictor has violated this assumption.
 
@@
 
-  Of 7,760 questions, 63.8\% received an answer by the download date.
+  Of 7,760 questions, 4,651 (63.8\%) received an answer by the download date.
+The shortest answer time was 0.01 hours.
+The longest was 2159.02 hrs (89.96 days).
 Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
 Figure B shows the Kaplan-Meier curve of survival probability for all questions in the data.
+The curve indicates that 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
 The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
-The median survival time, the time at which 50\% of the questions in the data received an answer was 9.16 hours.
+The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
 Table 1 provides additional percentiles of survival time.
 
-Predictors with p-values less than 0.01 in univariate analysis are shown in table b.
-The univariate model for the average frequency of a question's tags displayed an extrememly high hazard coefficient (33.8).
-To address this, a square root transformation was used on the variable, bringing the hazard coefficient to 4.2.
-Average performance metrics for the full model and its predictions for test and training sets, found in table c, were considerably low.
-However, metrics did not change substantially from training to test set, indicating that the model does not overfit.
-A spline of five knots was fit to the number of characters in the user-defined device name.
-Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text.
-Results of cross-validation for the model including the splines are in table d.
-As refitting the model without insignificant predictors did not effect predictive performance, all variables were included.
+As the distributions of continuous predictors were extremely right-skewed, the following transformations were applied:
+
+Log transformation
+\begin{itemize}
+  \item number of characters in a question's text
+\end{itemize}
+
+Square root transformations
+\begin{itemize}
+  \item The average score of a question's tags.
+  \item The average number of characters in a question's tags.
+  \item The number of characters in a question's user-defined device name.
+  \item The ratio of the number of line breaks to the number of characters in the question's text.
+\end{itemize}
+
+Predictors with p-values less than 0.01 are shown in Table b.
+All transformed continuous and categorical predictors were entered into the full model for cross-validation.
+Average performance metrics for test and training sets, found in table c, were considerably low.
+However, metrics did not change substantially from training to test sets, indicating that the model does not overfit.
+The following restricted cubic splines were applied continuous variables:
+
+4 knots
+\begin{itemize}
+  \item number of characters in the user-defined device name
+\end{itemize}
+
+3 knots
+\begin{itemize}
+  \item number of characters in a question's text
+  \item square root of the average number of characters in a question's tags
+  \item ratio of number of line breaks to the number of characters in a question's text
+\end{itemize}
+
+Results of cross-validation for the model including splines are in table d.
+As refitting the model without insignificant predictors and reperforming cross-validation did not change predictive accuracy, all variables were included.
 The final model, with all variables described above including splines, was fit to the full data.
@@
 However, because refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data.
-Assessing the proportional hazards assumption indicated that several levels of the device category predictor were in violation.
+Assessing the proportional hazards assumption indicated that several predictors were in violation.
+P-values for the correlation between predictors schoenfeld residuals and time are shown in table e.
 But as stratifying on this predictor substantially decreased predictive accuracy, the variable was left as is.
 Statistics and parameter coefficients of the final model are in table c.
+Metrics for the final model's performance on the full data, though considerably low, are not different from the metrics computed in cross-validation.
 

### 2017-11-25 article submission/draft1.Rnw
added draft in Sweave format

--- 2017-11-15 Article submission/roughdraft.tex
@@
-\documentclass[12pt]{article}
-\usepackage{natbib}  % used for citations
-\usepackage[parfill]{parskip} %used for formatting style of text
-
-% Sets margins to 1 in
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-.5in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1.3in}%
-\addtolength{\topmargin}{-.8in}%
-
-%-----------------------------------------------------------------------------------
-\title{Rough Draft}
-\author{Lisa Oshita}
-\date{}
-%-----------------------------------------------------------------------------------
+\documentclass{article}
 
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
-\maketitle
+<< echo = FALSE >>=
+# setting up model
+dir <- file.path(getwd(),"data")
+x <- read.csv(file.path(dir, "dat.csv"))
 
-\section{Abstract}
+model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)
+
+# -------------------------------------------------------------------------------
+set.seed(444)
+splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
+
+train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
+train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
+train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
+train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
+train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
+@
+
+\section*{Abstract}
 
@@
 We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time.
-Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$).
+Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
 Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
@@
 
-\section{Introduction}
+\section*{Introduction}
 
@@
 Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved.
-
 However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated.
@@
 
-\section{Related Work}
+\section*{Related Work}
 
@@
 
-\section{Materials}
+\section*{Materials}
 
@@
 
-\section{Methods}
+\section*{Methods}
 
-    Questions analyzed were restricted to those posted in English (97\% of the full data).
-The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer.
+Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data).
+The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
@@
 Survival was defined as the event that a question did not receive an answer beyond a certain time, t.
-Estimates of survival probability were generated with the Kaplan-Meier method (cite), which adjusts to the presence of right-censored, or unanswered questions.
-This method factors in the number of questions that have not been answered on each ordered interval of complete answer times.
-Estimates of survival probablity are the products of all probabilities up to that interval's time (redo this).
-From these estimates, survival curves were constructed to examine the survival experience of questions, and mean, median and other percentiles of survival times were also generated.
+Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions (cite).
+From these estimates, survival curves were constructed to examine the survival experience of questions.
+Mean, median and other percentiles of survival times were also generated.
 
@@
 The full data was split into five training and five test sets.
-Each training set contained 6,208 questions, and each test set contained 1,552 questions.
+Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
 Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model.
@@
 
-\section{Results}
+<<include = FALSE>>=
+answered <- sum(x$answered)
+percentans <- round((answered / nrow(x)) * 100, 1) 
+shortest <- round(min(x$time_until_answer) * 60, 2) 
+longest <- round(max(x$time_until_answer), 2)
+longest_d <- round(longest / 24, 2) 
+@
 
-  Of 7,760 questions, 4,651 (63.8\%) received an answer by the download date.
-The shortest answer time was 0.01 hours.
-The longest was 2159.02 hrs (89.96 days).
-Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
-Figure B shows the Kaplan-Meier curve of survival probability for all questions in the data.
-The curve indicates that 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
-The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
-The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
-Table 1 provides additional percentiles of survival time.
+\section*{Results}
+
+  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
+The shortest answer time was \Sexpr{shortest} hours.
+The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
+Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
+
+\begin{figure}[h!]
+  \includegraphics[scale=1]{times_dist.pdf}
+  \caption{Distribution of answer times}
+  \label{fig:answertimes}
+\end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[scale=1]{kmcurve.pdf}
+  \caption{Kaplan-Meier curve for all questions}
+  \label{fig:kmcurve}
+\end{figure}
+
+<<include = FALSE>>=
+surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
+KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
+stats <- summary(KM)$table
+mean <- round(unname(stats[5]), 2) 
+median <- round(unname(stats[7]), 2)
+@
+
+% latex table generated in R 3.4.1 by xtable 1.8-2 package
+% Fri Nov 24 17:16:56 2017
+\begin{table}[ht]
+\centering
+\begin{tabular}{rlr}
+  \hline
+  Percent \\ Answered & Time (hours) \\ 
+  \hline
+  25 & 0.88 \\ 
+  50 & 9.16 \\ 
+  55 & 18.38 \\ 
+  58 & 33.71 \\ 
+  60 & 59.47 \\ 
+  64 & 683.19 \\ 
+   \hline
+\end{tabular}
+\label{table:quantiles}
+\end{table}
+
+  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data.
+The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low.
+The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days.
+The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.
+Table ~\ref{table:quantiles} provides additional percentiles of survival time.
 
@@
 
-\section{Discussion}
+\section*{Discussion}
 
@@
 
-\section{Conclusion}
+\section*{Conclusion}
 
@@
 
-\section{Acknowledgement}
+\section*{Acknowledgement}
 

### 2017-11-25 article submission/draft1.tex
added draft in Sweave format

--- 2017-11-25 article submission/draft1.Rnw
@@
 
+\usepackage{Sweave}
 \begin{document}
-\SweaveOpts{concordance=TRUE}
-
-<< echo = FALSE >>=
-# setting up model
-dir <- file.path(getwd(),"data")
-x <- read.csv(file.path(dir, "dat.csv"))
-
-model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)
-
-# -------------------------------------------------------------------------------
-set.seed(444)
-splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
-
-train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
-train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
-train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
-train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
-train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
-@
+\input{draft1-concordance}
 
@@
 We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time.
-Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
+Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$).
 Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
@@
 
-Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data).
+Questions analyzed were restricted to those posted in English (7760 questions, 97\% of the full data).
 The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
@@
 The full data was split into five training and five test sets.
-Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
+Each training set contained 6208 questions, and each test set contained 1552 questions.
 Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model.
@@
 
-<<include = FALSE>>=
-answered <- sum(x$answered)
-percentans <- round((answered / nrow(x)) * 100, 1) 
-shortest <- round(min(x$time_until_answer) * 60, 2) 
-longest <- round(max(x$time_until_answer), 2)
-longest_d <- round(longest / 24, 2) 
-@
+\begin{Schunk}
+\begin{Sinput}
+> answered <- sum(x$answered)
+> percentans <- round((answered / nrow(x)) * 100, 1) 
+> shortest <- round(min(x$time_until_answer) * 60, 2) 
+> longest <- round(max(x$time_until_answer), 2)
+> longest_d <- round(longest / 24, 2) 
+\end{Sinput}
+\end{Schunk}
 
@@
 
-  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
-The shortest answer time was \Sexpr{shortest} hours.
-The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
+  Of 7760 questions, 4951 (63.8}\%) received an answer by the download date.
+The shortest answer time was 0.5 hours.
+The longest was 2159.02 hours (89.96 days).
 Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
@@
 
-<<include = FALSE>>=
-surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
-KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
-stats <- summary(KM)$table
-mean <- round(unname(stats[5]), 2) 
-median <- round(unname(stats[7]), 2)
-@
+\begin{Schunk}
+\begin{Sinput}
+> surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
+> KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
+> stats <- summary(KM)$table
+> mean <- round(unname(stats[5]), 2) 
+> median <- round(unname(stats[7]), 2)
+\end{Sinput}
+\end{Schunk}
 
@@
 The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low.
-The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days.
-The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.
+The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
 Table ~\ref{table:quantiles} provides additional percentiles of survival time.

### 2017-11-25 article submission/graphics.Rmd
added draft in Sweave format

@@
 x <- list[[1]]
+library(rms); library(survival); library(ggplot2)
 ```
@@
                    text_contain_punct + text_all_lower + update + prior_effort + weekday +
-                   rcs(avg_tag_score, 5) + rcs(text_length, 4) + rcs(device_length, 5) + 
-                   rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
+                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 3) + rcs(log10(text_length), 3) +
+                   rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3), 
                    data = x, 
@@
                    surv = TRUE)
+model
 ```
@@
 
+```{r}
+set.seed(444)
+splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
+
+train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
+train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
+train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
+train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
+train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
+
+pvalues <- data.frame(variable = character(), 
+                      pvalue = numeric())
+
+# function to get summary of cox model + append pvalue of variable from loglik test to df
+# ---------------------------------------------------------------------------------------
+get_pvalue <- function(variable, factor = FALSE) {
+  if (factor == FALSE){
+    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
+  } else {
+    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
+  }
+  summary <- summary(coxmodel)
+  df <- data.frame(variable = variable, 
+                   pvalue = unname(summary$logtest[[3]]))
+  pvalues <- rbind(pvalues, df)
+  return(pvalues)
+}
+# ---------------------------------------------------------------------------------------
+
+pvalues <- get_pvalue("new_category")
+pvalues <- get_pvalue("new_user")
+pvalues <- get_pvalue("title_questionmark")
+pvalues <- get_pvalue("text_contain_punct")
+pvalues <- get_pvalue("weekday")
+pvalues <- get_pvalue("text_length")
+pvalues <- get_pvalue("device_length")
+train1$logdevice <- log10(train1$device_length)
+train1$sqrtdevice <- sqrt(train1$device_length)
+pvalues <- get_pvalue("sqrtdevice")
+pvalues <- get_pvalue("text_all_lower")
+pvalues <- get_pvalue("prior_effort")
+pvalues <- get_pvalue("update")
+pvalues <- get_pvalue("newline_ratio")
+train1$sqrtnewline <- sqrt(train1$newline_ratio)
+pvalues <- get_pvalue("sqrtnewline")
+train1$sqrt <- sqrt(train1$avg_tag_length)
+pvalues <- get_pvalue("sqrt")
+pvalues <- get_pvalue("avg_tag_score")
+pvalues <- get_pvalue("contain_unanswered")
+pvalues <- get_pvalue("contain_answered")
+train1$logtext <- log10(train1$text_length)
+pvalues <- get_pvalue("logtext")
+options(scipen=999)
+pvalues <- pvalues %>% arrange(pvalue)
+pvalues
+
+rms::cph(Surv(time_until_answer, answered) ~ avg_tag_score, data = x)
+rms::cph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = x)
+rms::cph(Surv(time_until_answer, answered) ~ avg_tag_length, data = train1)
+
+rms::cph(Surv(time_until_answer, answered) ~ sqrt(newline_ratio), data = train1)
+
+ggplot(train1, aes(x = logtext)) + 
+  geom_histogram()
+ggplot(train1, aes(x = text_length)) + geom_histogram()
+ggplot(train1, aes(x = log10(device_length))) + geom_histogram()
+ggplot(train1, aes(x = sqrt(newline_ratio))) + geom_histogram()
+```
+
 ### Average CV metrics (Table 3 + 4) 
@@
 
-trains <- list(train1, train2, train3, train4, train5)
-trains <- purrr::map(trains, ~as.data.frame(.))
-tests <- list(test1, test2, test3, test4, test5)
-tests <- purrr::map(tests, ~as.data.frame(.))
-
 # ------------------------------------------
 # without splines
-vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + avg_tag_score + text_length + device_length + avg_tag_length + newline_ratio"
+vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + text_length + device_length + sqrt(avg_tag_length) + newline_ratio"
 
@@
 # with splines
-vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(text_length, 4) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"
+vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 3) + rcs(sqrt(avg_tag_length), 3) + rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3)"
 
@@
 
-# residuals
+```{r}
+avg_results1
+```
+
+### residuals
 
 ```{r}
-final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
-                  contain_unanswered + contain_answered + title_questionmark + 
-                  text_contain_punct + text_all_lower + update + prior_effort + weekday + 
-                  sqrt(avg_tag_score) + rcs(text_length, 4) + rcs(device_length, 5) + 
-                  rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
-                  data = x, x = TRUE, 
-                  y = TRUE, surv = TRUE)
-final
-
-x$mart <- residuals(final, type = "martingale")
+x$mart <- residuals(model, type = "martingale")
 
@@
 }
-plotm("avg_tag_score")
+
+x$sqrt_length <- sqrt(x$avg_tag_length)
+x$sqrt_score <- sqrt(x$avg_tag_score)
+
+plotm("sqrt_score")
 plotm("text_length")
 plotm("device_length")
-plotm("avg_tag_length")
+plotm("sqrt_length")
 plotm("newline_ratio")
-
 ```
@@
 # figure out how to get p-values 
-parameterdf <- data.frame(variable = names(final$coefficients),
-                          coefficients = round(unname(final$coefficients), 3))
+parameterdf <- data.frame(variable = names(model$coefficients),
+                          coefficients = round(unname(model$coefficients), 3))
 parameterdf
 
-modelstats <- data.frame(statistic = names(final$stats), 
-                         value = round(unname(final$stats), 3))
+modelstats <- data.frame(statistic = names(model$stats), 
+                         value = round(unname(model$stats), 3))
 modelstats
@@
 # cross-validation metrics 
-x$predictions <- exp(predict(final, type = "lp"))
+x$predictions <- exp(predict(model, type = "lp"))
 
 metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
-AIC(metric, k = 2) # 83125.55
+AIC(metric, k = 2) # 83124.21
 
@@
 final_metrics
+
+# ------------------------------------------
+ph <- cox.zph(model)
+ph_test <- data.frame(predictors = rownames(ph$table), ph$table)
+rownames(ph_test) = NULL
+ph_test <- ph_test %>% arrange(p) 
+ph_test
 ```
+
+```{r}
+final_metrics
+```

### 2017-11-26 article submission/draft1.Rnw
added univariate analysis tables

@@
 \documentclass{article}
-
+\usepackage{multirow}
 \begin{document}
@@
 model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)
-
-# -------------------------------------------------------------------------------
-set.seed(444)
-splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
-
-train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
-train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
-train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
-train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
-train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
 @
@@
 
+<< echo = FALSE >>=
+set.seed(444)
+splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
+
+train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
+train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
+train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
+train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
+train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
+@
+
 Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data).
@@
 
-<<include = FALSE>>=
+\section*{Results}
+
+<< echo = FALSE >>=
 answered <- sum(x$answered)
@@
 @
-
-\section*{Results}
-
-  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
-The shortest answer time was \Sexpr{shortest} hours.
-The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
-Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
 
@@
 
-<<include = FALSE>>=
+  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
+The shortest answer time was \Sexpr{shortest} hours.
+The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
+Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
+
+<< echo = FALSE >>=
 surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
@@
 
-% latex table generated in R 3.4.1 by xtable 1.8-2 package
-% Fri Nov 24 17:16:56 2017
 \begin{table}[ht]
@@
   \hline
-  Percent \\ Answered & Time (hours) \\ 
+ Percent\\ Answered & Time (hrs) \\ 
   \hline
@@
 \end{tabular}
+\caption{Table of Kaplan-Meier estimated quantiles of survival time}
 \label{table:quantiles}
@@
 The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.
-Table ~\ref{table:quantiles} provides additional percentiles of survival time.
+Table \ref{table:quantiles} provides additional percentiles of survival time.
 
-As the distributions of continuous predictors were extremely right-skewed, the following transformations were applied:
+\begin{table}[ht]
+\centering
+\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
+\begin{tabular}{|p{12cm}|p{2cm}|}
+  \hline
+  Predictor & p-value \\ 
+  \hline \hline
+  Log transformation of the number of characters in a question's text* & 0.00 \\ 
+  \hline
+  Square root transformation of the number of characters in a question's text* & 0.00 \\ 
+  \hline
+  Number of characters in a question's text (untransformed) & 0.00 \\
+  \hline
+  Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text* & 0.00 \\ 
+  \hline
+  Square root transformation of the average frequency ``score'' of a question's tags* & 0.00 \\ 
+  \hline
+  Average frequency ``score'' of a question's tags (untransformed) & 0.00 \\ 
+  \hline
+  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 0.00 \\ 
+  \hline
+  Square root transformation of the number of characters in the user-defined device title* & 0.00 \\ 
+  \hline
+  Square root transformation of the average number of characters in a question's tags* & 0.00 \\ 
+  \hline
+  Number of characters in the user-defined device title (untransformed) & 0.01 \\ 
+  \hline
+  Average number of characters in a question's tags (untransformed) & 0.03 \\ 
+   \hline
+\end{tabular}
+\label{table:qresults}
+\end{table}
 
-Log transformation
-\begin{itemize}
-  \item number of characters in a question's text
-\end{itemize}
+\begin{table}[ht]
+\centering
+\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
+\begin{tabular}{|p{12cm}|p{2cm}|}
+  \hline
+ Predictor & p-value \\ 
+  \hline \hline
+  Device category & 0.00 \\
+  \hline
+  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
+  \hline
+  Whether or not the question's title ended in a questionmark & 0.00 \\ 
+  \hline
+  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
+  \hline
+  Day of the week the question was posted & 0.00 \\ 
+  \hline
+  Whether or not the question's text is in all lower case & 0.00 \\ 
+  \hline
+  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
+  \hline
+  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
+  \hline
+  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
+  \hline
+  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
+   \hline
+\end{tabular}
+\label{table:cresults}
+\end{table}
 
-Square root transformations
-\begin{itemize}
-  \item The average score of a question's tags.
-  \item The average number of characters in a question's tags.
-  \item The number of characters in a question's user-defined device name.
-  \item The ratio of the number of line breaks to the number of characters in the question's text.
-\end{itemize}
+Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+All categorical predictors were entered into the full model.
+Restricted cubic splines were fit to all * quantitative variables.
 
-Predictors with p-values less than 0.01 are shown in Table b.
-All transformed continuous and categorical predictors were entered into the full model for cross-validation.
+\begin{table}[ht]
+\centering
+\caption{Determining the optimal k number of splines for each predictor} 
+\begin{tabular}{| p{5cm} | l | l | l |}
+  \hline
+  Predictor & K & p-value & AIC \\ 
+  \hline
+  \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
+  & 0 & 0.00 & 65862.83 \\ 
+  & 5* & 0.00 & 65862.02 \\ 
+  & 4 & 0.00 & 65863.35 \\ 
+  & 3 & 0.00 & 65862.08 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
+  & 0 & 0.00 & 65890.28 \\ 
+  & 5 & 0.00 & 65884.70 \\ 
+  & 4 & 0.00 & 65882.98 \\ 
+  & 3* & 0.00 & 65881.93 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
+  & 0* & 0.00 & 65890.75 \\ 
+  & 5 & 0.00 & 65891.69 \\ 
+  & 4 & 0.00 & 65891.75 \\ 
+  & 3 & 0.00 & 65892.35 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
+  & 0 & 0.00 & 65922.76 \\ 
+  & 5* & 0.00 & 65853.56 \\ 
+  & 4 & 0.00 & 65882.07 \\ 
+  & 3 & 0.00 & 65881.39 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
+  & 0 & 0.00 & 65923.26 \\ 
+  & 5 & 0.00 & 65912.11 \\ 
+  & 4* & 0.00 & 65910.10 \\ 
+  & 3 & 0.00 & 65912.38 \\ 
+   \hline
+\end{tabular}
+\label{table:splines}
+\end{table}
+
+Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model for cross-validation.
+
 Average performance metrics for test and training sets, found in table c, were considerably low.
@@
 The following restricted cubic splines were applied continuous variables:
-
-4 knots
-\begin{itemize}
-  \item number of characters in the user-defined device name
-\end{itemize}
-
-3 knots
-\begin{itemize}
-  \item number of characters in a question's text
-  \item square root of the average number of characters in a question's tags
-  \item ratio of number of line breaks to the number of characters in a question's text
-\end{itemize}
 

### 2017-11-26 article submission/draft1.tex
added univariate analysis tables

@@
 \documentclass{article}
-
+\usepackage{multirow}
 \usepackage{Sweave}
@@
 
-\begin{Schunk}
-\begin{Sinput}
-> answered <- sum(x$answered)
-> percentans <- round((answered / nrow(x)) * 100, 1) 
-> shortest <- round(min(x$time_until_answer) * 60, 2) 
-> longest <- round(max(x$time_until_answer), 2)
-> longest_d <- round(longest / 24, 2) 
-\end{Sinput}
-\end{Schunk}
-
 \section*{Results}
-
-  Of 7760 questions, 4951 (63.8}\%) received an answer by the download date.
-The shortest answer time was 0.5 hours.
-The longest was 2159.02 hours (89.96 days).
-Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-> surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
-> KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
-> stats <- summary(KM)$table
-> mean <- round(unname(stats[5]), 2) 
-> median <- round(unname(stats[7]), 2)
-\end{Sinput}
-\end{Schunk}
+  Of 7760 questions, 4951 (63.8}\%) received an answer by the download date.
+The shortest answer time was 0.5 hours.
+The longest was 2159.02 hours (89.96 days).
+Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
 
-% latex table generated in R 3.4.1 by xtable 1.8-2 package
-% Fri Nov 24 17:16:56 2017
 \begin{table}[ht]
@@
 The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
-Table ~\ref{table:quantiles} provides additional percentiles of survival time.
+Table \ref{table:quantiles} provides additional percentiles of survival time.
 
-As the distributions of continuous predictors were extremely right-skewed, the following transformations were applied:
+\begin{table}[ht]
+\centering
+\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
+\begin{tabular}{|p{12cm}|p{2cm}|}
+  \hline
+  Predictor & p-value \\ 
+  \hline \hline
+  Log transformation of the number of characters in a question's text* & 0.00 \\ 
+  \hline
+  Square root transformation of the number of characters in a question's text* & 0.00 \\ 
+  \hline
+  Number of characters in a question's text (untransformed) & 0.00 \\
+  \hline
+  Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text* & 0.00 \\ 
+  \hline
+  Square root transformation of the average frequency ``score'' of a question's tags* & 0.00 \\ 
+  \hline
+  Average frequency ``score'' of a question's tags (untransformed) & 0.00 \\ 
+  \hline
+  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 0.00 \\ 
+  \hline
+  Square root transformation of the number of characters in the user-defined device title* & 0.00 \\ 
+  \hline
+  Square root transformation of the average number of characters in a question's tags* & 0.00 \\ 
+  \hline
+  Number of characters in the user-defined device title (untransformed) & 0.01 \\ 
+  \hline
+  Average number of characters in a question's tags (untransformed) & 0.03 \\ 
+   \hline
+\end{tabular}
+\label{table:qresults}
+\end{table}
 
-Log transformation
-\begin{itemize}
-  \item number of characters in a question's text
-\end{itemize}
+\begin{table}[ht]
+\centering
+\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
+\begin{tabular}{|p{12cm}|p{2cm}|}
+  \hline
+ Predictor & p-value \\ 
+  \hline \hline
+  Device category & 0.00 \\
+  \hline
+  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
+  \hline
+  Whether or not the question's title ended in a questionmark & 0.00 \\ 
+  \hline
+  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
+  \hline
+  Day of the week the question was posted & 0.00 \\ 
+  \hline
+  Whether or not the question's text is in all lower case & 0.00 \\ 
+  \hline
+  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
+  \hline
+  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
+  \hline
+  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
+  \hline
+  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
+   \hline
+\end{tabular}
+\label{table:cresults}
+\end{table}
 
-Square root transformations
-\begin{itemize}
-  \item The average score of a question's tags.
-  \item The average number of characters in a question's tags.
-  \item The number of characters in a question's user-defined device name.
-  \item The ratio of the number of line breaks to the number of characters in the question's text.
-\end{itemize}
+Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+All categorical predictors were entered into the full model.
+Restricted cubic splines were fit to all * quantitative variables.
 
-Predictors with p-values less than 0.01 are shown in Table b.
-All transformed continuous and categorical predictors were entered into the full model for cross-validation.
+\begin{table}[ht]
+\centering
+\caption{Determining the optimal k number of splines for each predictor} 
+\begin{tabular}{| p{5cm} | l | l | l |}
+  \hline
+  Predictor & K & p-value & AIC \\ 
+  \hline
+  \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
+  & 0 & 0.00 & 65862.83 \\ 
+  & 5* & 0.00 & 65862.02 \\ 
+  & 4 & 0.00 & 65863.35 \\ 
+  & 3 & 0.00 & 65862.08 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
+  & 0 & 0.00 & 65890.28 \\ 
+  & 5 & 0.00 & 65884.70 \\ 
+  & 4 & 0.00 & 65882.98 \\ 
+  & 3* & 0.00 & 65881.93 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
+  & 0* & 0.00 & 65890.75 \\ 
+  & 5 & 0.00 & 65891.69 \\ 
+  & 4 & 0.00 & 65891.75 \\ 
+  & 3 & 0.00 & 65892.35 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
+  & 0 & 0.00 & 65922.76 \\ 
+  & 5* & 0.00 & 65853.56 \\ 
+  & 4 & 0.00 & 65882.07 \\ 
+  & 3 & 0.00 & 65881.39 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
+  & 0 & 0.00 & 65923.26 \\ 
+  & 5 & 0.00 & 65912.11 \\ 
+  & 4* & 0.00 & 65910.10 \\ 
+  & 3 & 0.00 & 65912.38 \\ 
+   \hline
+\end{tabular}
+\label{table:splines}
+\end{table}
+
+Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model for cross-validation.
+
 Average performance metrics for test and training sets, found in table c, were considerably low.

### 2017-11-26 article submission/graphics.Rmd
added latex tables

@@
 x <- list[[1]]
-library(rms); library(survival); library(ggplot2)
-```
-
-```{r}
-model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
-                   contain_unanswered + contain_answered + title_questionmark + 
-                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
-                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 3) + rcs(log10(text_length), 3) +
-                   rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3), 
-                   data = x, 
-                   x = TRUE, y = TRUE, 
-                   surv = TRUE)
-model
+library(rms); library(survival); library(ggplot2); library(dplyr)
 ```
@@
 ```{r}
-x$Answered <- NA
-x$Answered[x$answered == 1] <- "Answered"
-x$Answered[x$answered == 0] <- "Unanswered"
+# x$Answered <- NA
+# x$Answered[x$answered == 1] <- "Answered"
+# x$Answered[x$answered == 0] <- "Unanswered"
 
@@
   geom_histogram(bins = 15, alpha = 0.5, position = "identity") + 
-  theme(axis.text = element_text(size = 13),
-        axis.title = element_text(size = 15),
-        plot.title = element_text(size = 17),
-        legend.position = c(0.8, 0.8),
-        legend.text = element_text(size = 13)) + 
   guides(fill = guide_legend(title = NULL)) + 
   scale_x_continuous("Time (hrs)") + 
-  scale_y_continuous("Number of Questions") + 
-  ggtitle("Distribution of Answer Times")
+  scale_y_continuous("Number of Questions")
+
+ggsave("times_dist.pdf", width = 8, height = 5)
 ```
@@
            tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE,
-           title = "Kaplan-Meier Curve for all Questions",
            legend = "none")
+
+ggsave("kmcurve.pdf", width = 8, height = 5)
 ```
@@
 ```{r}
-q <- quantile(KM, c(0.25, 0.50, 0.55, 0.58, 0.60, 0.64)) # 64% is largest available survival probability
-quantiles <- q$quantile
-quantilesdf <- data.frame(Percent = names(quantiles), Time = round(quantiles, 2))
-colnames(quantilesdf) <- c("Percent Answered", "Time (Hours)")
-quantilesdf
+# 64% is largest available survival probability
+quantiles <- quantile(KM, c(0.25, 0.50, 0.55, 0.58, 0.60, 0.64))$quantile 
+quantilesdf <- data.frame(Percent = names(quantiles), 
+                          Time = round(quantiles, 2))
+colnames(quantilesdf) <- c(paste("Percent", "\n", "Answered", sep = ""), "Time (hours)")
+rownames(quantilesdf) <- NULL
+
+xtable::xtable(quantilesdf, label = "table:quantile")
+```
+
+```{r}
+model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
+                   contain_unanswered + contain_answered + title_questionmark + 
+                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
+                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 3) + rcs(log10(text_length), 3) +
+                   rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3), 
+                   data = x, 
+                   x = TRUE, y = TRUE, 
+                   surv = TRUE)
+model
 ```
@@
 
-pvalues <- data.frame(variable = character(), 
-                      pvalue = numeric())
-
-# function to get summary of cox model + append pvalue of variable from loglik test to df
 # ---------------------------------------------------------------------------------------
-get_pvalue <- function(variable, factor = FALSE) {
-  if (factor == FALSE){
-    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
-  } else {
-    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
-  }
-  summary <- summary(coxmodel)
-  df <- data.frame(variable = variable, 
-                   pvalue = unname(summary$logtest[[3]]))
-  pvalues <- rbind(pvalues, df)
-  return(pvalues)
+get_pvalue <- function(var) { 
+  formula <- paste("Surv(time_until_answer, answered) ~ ", var, sep = "")
+  model <- cph(stats::as.formula(formula), data = train1)
+  df <- data.frame(variable = var, 
+                   pvalue = unname(model$stats[5]))
+  return(df)
 }
 # ---------------------------------------------------------------------------------------
+# categorical predictors 
+categorical <- list("new_category", "new_user", "title_questionmark", 
+                    "text_contain_punct", "weekday", "text_all_lower", 
+                    "prior_effort", "update", "contain_unanswered", 
+                    "contain_answered")
+c_pvalue <- purrr::map_dfr(categorical, ~get_pvalue(.))
 
-pvalues <- get_pvalue("new_category")
-pvalues <- get_pvalue("new_user")
-pvalues <- get_pvalue("title_questionmark")
-pvalues <- get_pvalue("text_contain_punct")
-pvalues <- get_pvalue("weekday")
-pvalues <- get_pvalue("text_length")
-pvalues <- get_pvalue("device_length")
-train1$logdevice <- log10(train1$device_length)
-train1$sqrtdevice <- sqrt(train1$device_length)
-pvalues <- get_pvalue("sqrtdevice")
-pvalues <- get_pvalue("text_all_lower")
-pvalues <- get_pvalue("prior_effort")
-pvalues <- get_pvalue("update")
-pvalues <- get_pvalue("newline_ratio")
-train1$sqrtnewline <- sqrt(train1$newline_ratio)
-pvalues <- get_pvalue("sqrtnewline")
-train1$sqrt <- sqrt(train1$avg_tag_length)
-pvalues <- get_pvalue("sqrt")
-pvalues <- get_pvalue("avg_tag_score")
-pvalues <- get_pvalue("contain_unanswered")
-pvalues <- get_pvalue("contain_answered")
-train1$logtext <- log10(train1$text_length)
-pvalues <- get_pvalue("logtext")
+xtable::xtable(c_pvalue, 
+               caption = "Univariate analysis results for categorical predictors, 
+                          ordered by increasing p-values", 
+               label = "table:cresults")
+
+# ---------------------------------------------------------------------------------------
+# quantitative predictors + transformations 
+text_length <- list("text_length", "sqrt(text_length)", "log10(text_length)")
+txt_pvalue <- purrr::map_dfr(text_length, ~get_pvalue(.))
+
+dev_length <- list("device_length", "sqrt(device_length)") # log10 does not work 
+dev_pvalue <- purrr::map_dfr(dev_length, ~get_pvalue(.))
+
+newline <- list("newline_ratio", "sqrt(newline_ratio)") #log10 doens't work
+newline_pvalue <- purrr::map_dfr(newline, ~get_pvalue(.))
+
+tag_length <- list("avg_tag_length", "sqrt(avg_tag_length)")
+taglength_pvalue <- purrr::map_dfr(tag_length, ~get_pvalue(.))
+
+tag_score <- list("avg_tag_score", "sqrt(avg_tag_score)")
+tagscore_pvalue <- purrr::map_dfr(tag_score, ~get_pvalue(.))
+
+univ_results <- rbind(txt_pvalue, dev_pvalue, newline_pvalue, taglength_pvalue, tagscore_pvalue)
+
 options(scipen=999)
-pvalues <- pvalues %>% arrange(pvalue)
-pvalues
+univ_results <- univ_results %>% arrange(pvalue)
 
-rms::cph(Surv(time_until_answer, answered) ~ avg_tag_score, data = x)
-rms::cph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = x)
-rms::cph(Surv(time_until_answer, answered) ~ avg_tag_length, data = train1)
+xtable::xtable(x = univ_results, 
+               caption = "Univariate analysis results", 
+               label = "table:qresults")
 
-rms::cph(Surv(time_until_answer, answered) ~ sqrt(newline_ratio), data = train1)
+# ---------------------------------------------------------------------------------------
+# choosing number of knots for splines
+fit_splines <- function(var) { 
+  none <- paste("Surv(time_until_answer, answered) ~ ", var, sep = "")
+  model <- cph(stats::as.formula(none), data = train1)
+  df <- data.frame(variable = "none", 
+                   pvalue = unname(model$stats[5]), 
+                   AIC = AIC(model, k = 2))
 
-ggplot(train1, aes(x = logtext)) + 
-  geom_histogram()
-ggplot(train1, aes(x = text_length)) + geom_histogram()
-ggplot(train1, aes(x = log10(device_length))) + geom_histogram()
-ggplot(train1, aes(x = sqrt(newline_ratio))) + geom_histogram()
+  f5 <- paste("Surv(time_until_answer, answered) ~ rcs(", var, ", 5)", sep = "")
+  k5 <- cph(stats::as.formula(f5), data = train1)
+  df5 <- data.frame(variable = "5 knots", 
+                    pvalue = unname(k5$stats[5]), 
+                    AIC = AIC(k5, k = 2))
+
+  f4 <- paste("Surv(time_until_answer, answered) ~ rcs(", var, ", 4)", sep = "")
+  k4 <- cph(stats::as.formula(f4), data = train1)
+  df4 <- data.frame(variable = "4 knots", 
+                    pvalue = unname(k4$stats[5]), 
+                    AIC = AIC(k4, k = 2))
+
+  f3 <- paste("Surv(time_until_answer, answered) ~ rcs(", var, ", 3)", sep = "")
+  k3 <- cph(stats::as.formula(f3), data = train1)
+  df3 <- data.frame(variable = "3 knots", 
+                   pvalue = unname(k3$stats[5]), 
+                   AIC = AIC(k3, k = 2))
+  return(rbind(df, df5, df4, df3))
+}
+# ---------------------------------------------------------------------------------------
+txt <- fit_splines("log10(text_length)") # 3 knots or none
+newline <- fit_splines("sqrt(newline_ratio)") # 3 knots
+tagscore <- fit_splines("sqrt(avg_tag_score)") # 5 knots or none 
+device <- fit_splines("sqrt(device_length)") # 5 knots
+taglength <- fit_splines("sqrt(avg_tag_length)") # 4 knots
+txt
+newline
+tagscore
+device
+taglength
+
+splinedf <- rbind(txt, newline, tagscore, device, taglength)
+
+xtable::xtable(splinedf, caption = "Determining the optimal number of splines for each predictor", label = "table:splines")
 ```
@@
 ### Average CV metrics (Table 3 + 4)
+
 ```{r}

### 2017-11-29 article submission/draft1.Rnw
added table of results from final model

@@
 
-Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data).
+Questions analyzed were restricted to those posted in English.
 The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
@@
 
-  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
+  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data).
+Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
 The shortest answer time was \Sexpr{shortest} hours.
@@
   \hline
-  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
+  Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.00 \\ 
    \hline
@@
 
-Average performance metrics for test and training sets, found in table c, were considerably low.
+\begin{table}[ht]
+\centering
+\caption{Average performance metrics for training and test sets} 
+\begin{tabular}{rrrrrrrr}
+  \hline
+ & HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
+  \hline
+  Training Set & 2.00 & 959.49 & 0.00 & 0.14 & 64729.80 & 0.27 & 0.64 \\ 
+  Test Set & 1.96 & 225.44 & 0.00 & 0.14 & 13453.18 & 0.26 & 0.63 \\ 
+   \hline
+\end{tabular}
+\label{table:cv}
+\end{table}
+
+Average performance metrics for test and training sets, found in Table \ref{table:cv}, were considerably low.
 However, metrics did not change substantially from training to test sets, indicating that the model does not overfit.
-The following restricted cubic splines were applied continuous variables:
+The final model, with all variables described above including splines, was fit to the full data.
 
-Results of cross-validation for the model including splines are in table d.
-As refitting the model without insignificant predictors and reperforming cross-validation did not change predictive accuracy, all variables were included.
-The final model, with all variables described above including splines, was fit to the full data.
+\begin{table}[ht]
+\centering
+\caption{P-values for final model fit to the full data} 
+\begin{tabular}{|p{12cm}|p{1cm}|}
+  \hline
+Predictor & p \\ 
+  \hline \hline
+Device Category & 0.00 \\ 
+  \hline
+Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
+  \hline
+Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\
+  \hline
+Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.22 \\ 
+  \hline
+Whether or not the question's title ended in a questionmark & 0.00 \\ 
+  \hline
+Whether or not the question's text contained at least one end punctuation mark & 0.53 \\ 
+  \hline
+Whether or not the question's text is in all lower case & 0.01 \\ 
+  \hline
+Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\ 
+  \hline
+Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.01 \\ 
+  \hline
+Day of the week the question was posted & 0.00 \\ 
+  \hline
+Square root transformation of the average frequency ``score'' of a question's tags & 0.00 \\ 
+  \hline
+Square root transformation of the average number of characters in a question's tags & 0.05 \\ 
+Nonlinear & 0.08 \\ 
+  \hline
+Square root transformation of the number of characters in a question's text & 0.43 \\ 
+Nonlinear & 0.46 \\ 
+  \hline
+Square root transformation of the number of characters in the user-defined device title & 0.28 \\ 
+Nonlinear & 0.42 \\ 
+  \hline
+Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 0.36 \\ 
+Nonlinear & 0.62 \\ 
+   \hline
+\end{tabular}
+\label{table:pvalues}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rlr}
+  \hline
+ & variable & coefficients \\ 
+  \hline
+1 & new\_category=Apple Product & 0.93 \\ 
+  2 & new\_category=Camera & -0.26 \\ 
+  3 & new\_category=Electronics & -0.08 \\ 
+  4 & new\_category=Game Console & 0.21 \\ 
+  5 & new\_category=Home & 0.39 \\ 
+  6 & new\_category=Other & -0.11 \\ 
+  7 & new\_category=PC & 0.43 \\ 
+  8 & new\_category=Tablet & -0.15 \\ 
+  9 & new\_category=Vehicle & 0.38 \\ 
+  10 & new\_user=1 & -0.10 \\ 
+  11 & contain\_unanswered & -0.27 \\ 
+  12 & contain\_answered & 0.05 \\ 
+  13 & title\_questionmark & 0.25 \\ 
+  14 & text\_contain\_punct & 0.03 \\ 
+  15 & text\_all\_lower & -0.18 \\ 
+  16 & update & 0.28 \\ 
+  17 & prior\_effort & -0.09 \\ 
+  18 & weekday=Monday & 0.01 \\ 
+  19 & weekday=Saturday & -0.07 \\ 
+  20 & weekday=Sunday & -0.11 \\ 
+  21 & weekday=Thursday & 0.03 \\ 
+  22 & weekday=Tuesday & 0.09 \\ 
+  23 & weekday=Wednesday & 0.10 \\ 
+  24 & avg\_tag\_score & 2.23 \\ 
+  25 & avg\_tag\_length & -0.08 \\ 
+  26 & avg\_tag\_length' & 0.58 \\ 
+  27 & avg\_tag\_length'' & -1.52 \\ 
+  28 & text\_length & -0.08 \\ 
+  29 & text\_length' & -0.36 \\ 
+  30 & text\_length'' & 2.39 \\ 
+  31 & text\_length''' & -3.69 \\ 
+  32 & device\_length & -0.07 \\ 
+  33 & device\_length' & 0.18 \\ 
+  34 & device\_length'' & -0.27 \\ 
+  35 & device\_length''' & 0.21 \\ 
+  36 & newline\_ratio & 0.12 \\ 
+  37 & newline\_ratio' & 0.36 \\ 
+   \hline
+\end{tabular}
+\caption{Coefficients for predictors in the final model} 
+\label{table:coefficients}
+\end{table}
 
@@
 The resulting list for answered questions was 111 words, and 32 words in uanswered questions.
-Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.
+Contain\_answered and contain\_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.
 
@@
 sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit
-
-Title\_questionmark and title\_beginwh
-
-These two variables were created to determine if stating the title in the form of a question is associated with faster answer times.
-Title_questionmark is a logical variable indicating true if the question's title ends with a question mark.
-Title_beginwh is a logical variable indicating true if the title begins with a “wh” word (e.g.
-"what", "when").
-These variables were created based off of the findings from \citep{Bhat2014}.
 
@@
 This variable was created based off of findings from \cite{Bhat2014}.
-
-Ampm (change name)
-
-The time of day the question was posted.
-If the question was posted between 5am and 12pm, it was categorized as ``morning''.
-If it was posted between 12pm and 5pm, it was categorized as ``afternoon'', between 5pm and 8am- ``evening'', and 8pm and 5 am, ``night''
 

### 2017-11-29 article submission/draft1.tex
added table of results from final model

@@
 
-Questions analyzed were restricted to those posted in English (7760 questions, 97\% of the full data).
+Questions analyzed were restricted to those posted in English.
 The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
@@
 
-  Of 7760 questions, 4951 (63.8}\%) received an answer by the download date.
+  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data).
+Of those questions, 4951 (63.8}\%) received an answer by the download date.
 The shortest answer time was 0.5 hours.

### 2017-11-29 article submission/graphics.Rmd
added table of results from final model

@@
                    text_contain_punct + text_all_lower + update + prior_effort + weekday +
-                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 3) + rcs(log10(text_length), 3) +
-                   rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3), 
+                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 4) + rcs(log10(text_length), 5) +
+                   rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3), 
                    data = x, 
@@
                    surv = TRUE)
-model
 ```
@@
 train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
+
+trains <- list(train1, train2, train3, train4, train5)
+trains <- purrr::map(trains, ~as.data.frame(.))
+tests <- list(test1, test2, test3, test4, test5)
+tests <- purrr::map(tests, ~as.data.frame(.))
 
@@
 }
-
+# ------------------------------------------
 # function to average performance metrics, takes list of output from crossval
@@
 }
+# ------------------------------------------
 
-# ------------------------------------------
-# without splines
-vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + text_length + device_length + sqrt(avg_tag_length) + newline_ratio"
-
-cv_results <- purrr::map2(trains, tests, ~crossval(vars, .x, .y))
-avg_results <- get_avgmetrics(cv_results)
-avg_results
-
-# ------------------------------------------
-# with splines
-vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 3) + rcs(sqrt(avg_tag_length), 3) + rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3)"
+vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + rcs(sqrt(avg_tag_length), 4) + rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3)"
 
@@
 avg_results1
+xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv")
+```
+
+# final model on full data
+
+```{r}
+# model statistics + parameters
+# figure out how to get p-values 
+parameterdf <- data.frame(variable = names(model$coefficients),
+                          coefficients = round(unname(model$coefficients), 3))
+parameterdf
+xtable::xtable(parameterdf, caption = "Coefficients for predictors in the final model",
+               label = "table:coefficients")
+# ------------------------------------------
+pvalues <- as.matrix(anova(model))[,3]
+pvaluedf <- data.frame(variable = names(pvalues), 
+                       pvalue = unname(pvalues))
+xtable::xtable(pvaluedf, caption = "P-values for final model fit to the full data",
+               label = "table:pvalues")
+
+modelstats <- data.frame(statistic = names(model$stats), 
+                         value = round(unname(model$stats), 3))
+modelstats
+# ------------------------------------------
+
+# ------------------------------------------
+# cross-validation metrics 
+x$predictions <- exp(predict(model, type = "lp"))
+
+metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
+AIC(metric, k = 2) # 83124.21
+
+final_metrics <- data.frame(HR = exp(metric$coefficients), 
+                              LR = round(metric$stats[3],2), 
+                              pval = round(metric$stats[5],2),
+                              R2 = round(metric$stats[8], 2),
+                              AIC = stats::AIC(metric, k = 2),
+                              Dxy = round(metric$stats[9],2), 
+                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
+final_metrics
+
+# ------------------------------------------
+ph <- cox.zph(model)
+ph_test <- data.frame(predictors = rownames(ph$table), ph$table)
+rownames(ph_test) = NULL
+ph_test <- ph_test %>% arrange(p) 
+ph_test
 ```
@@
 ```{r}
-avg_results1
+final_metrics
+pvalues
+anova(model)
 ```
@@
 ```
-
-# final model on full data (table 5)
-
-```{r}
-# model statistics + parameters
-# figure out how to get p-values 
-parameterdf <- data.frame(variable = names(model$coefficients),
-                          coefficients = round(unname(model$coefficients), 3))
-parameterdf
-
-modelstats <- data.frame(statistic = names(model$stats), 
-                         value = round(unname(model$stats), 3))
-modelstats
-
-# ------------------------------------------
-# cross-validation metrics 
-x$predictions <- exp(predict(model, type = "lp"))
-
-metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
-AIC(metric, k = 2) # 83124.21
-
-final_metrics <- data.frame(HR = exp(metric$coefficients), 
-                              LR = round(metric$stats[3],2), 
-                              pval = round(metric$stats[5],2),
-                              R2 = round(metric$stats[8], 2),
-                              AIC = stats::AIC(metric, k = 2),
-                              Dxy = round(metric$stats[9],2), 
-                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
-final_metrics
-
-# ------------------------------------------
-ph <- cox.zph(model)
-ph_test <- data.frame(predictors = rownames(ph$table), ph$table)
-rownames(ph_test) = NULL
-ph_test <- ph_test %>% arrange(p) 
-ph_test
-```
-
-```{r}
-final_metrics
-```

### 2017-12-13 article submission/draft1.Rnw
fixed appendix, added tables

--- 2017-11-26 article submission/draft1.Rnw
@@
   \item Whether or not the user made an effort to solve the problem on their own, prior to asking the question.
-  \item The day of the week the question was posted. 
+  \item Day of the week the question was posted. 
 \end{itemize}
@@
 \begin{itemize}
-  \item The average tag ``score'' for all of a question's tags.
+  \item Average tag ``score'' for all of a question's tags.
 A tag score is defined as the proportion of times a tag appears in all of the data.
 Questions without tags were assigned an average tag score of 0.
-  \item The average number of characters in each question's tags. 
-  \item The number of characters in the question's text. 
-  \item The number of characters in the user-defined device name. 
-  \item The ratio of the number of line breaks to the number of characters in the question's text.
+  \item Average number of characters in each question's tags. 
+  \item Number of characters in the question's text. 
+  \item Number of characters in the user-defined device name. 
+  \item Ratio of the number of line breaks to the number of characters in the question's text.
 \end{itemize}
@@
 
-Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data).
-The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
+Questions analyzed were restricted to those posted in English.
+Time until event was defined as the time since posting until a question received its first answer.
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).
+These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times in the data (questions can still receive answers after the download date).
 
@@
 Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
-Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model.
-Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied.
-Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed.
-Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.
+Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model.
+Distributions of continuous variables were assessed.
+Each categorical and continuous predictor, both with and without square root and log transformations, were entered into separate univariate Cox models and strength of association with answer times were assessed.
+Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model.
+For continuous predictors, the lowest p-value was used to determine if and which transformation was necessary.
+To determine whether or not splines on continuous predictors were necessary, as well as the optimum number of knots, univariate analysis was again performed.
+Continuous variables (with transformations found to be necessary in the previous univariate analysis) were again fit to separate univariate Cox models with: no splines and restricted cubic splines of three, four, and five knots.
+AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{}Harrell2015.
+All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.
 
-In each fold of cross-validation, the full model, with variables found to be signficant in univariate analysis, was built on one of the training sets and used to generate predicted hazard ratios on the corresponding test sets.
-To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time.
+In each fold of cross-validation, the full model was built on one training set and used to generate predicted hazard ratios on the corresponding test set.
+To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time.
 The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}.
-Signficant statistics would indicate high predictive accuracy.
+Signficant results would indicate high predictive accuracy.
 Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination.
@@
 Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}.
-These metrics were computed for each training and test set.
-The averages of metrics across test sets were evaluated.
-The final model was selected based on AIC statistics and the signficance of prediction metrics, as well as how consistent those metrics were across training and test sets.
+Metrics were computed for each training and test set.
+Averages of metrics across test sets were evaluated.
 The final model was then fit to the full data and the same metrics were computed and compared.
 
-Plots of Martingale residuals, the differences between observed number of answers received by each question and the expected number of answers expererienced by each question under the model, were evaluated to assess functional form of each continuous predictor.
-Deviance residuals, which are transformed Martingale residuals with a mean of 0 and an approximately normal distribution, were assessed to identify questions poorly predicted by the model.
-Score residuals, a measure of the approximate change in parameter estimates that would occur if a question were removed from the sample, were assessed to check for questions that highly effect parameter estimates.
-
-Restricted cubic splines were applied to all continuous predictors \citep{Harrell2015}.
-Splines of five knots were initially fit to each.
-A higher number of knots were assigned to predictors hypothesized to be more signficant, those with lower model p-values.
-The optimal number of knots for each predictor was determined based on the model AIC statistic.
-
-Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that underlies a Cox model.
-Proportional hazards assumes that the effect of predictors on hazard does not depend on time.
+Martingale residuals were evaluated to assess functional form of each continuous predictor.
+Deviance residuals were used to identify outliers, or questions poorly predicted by the model.
+Score residuals were used to identify questions that highly effected parameter estimates.
+Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time.
 Significant correlations indicate that a predictor has violated this assumption.
@@
 
+% Distribution of answer times
 \begin{figure}[h!]
@@
 
+% Kaplan-Meier curve
 \begin{figure}[h!]
@@
 
+% Table of percentiles 
 \begin{table}[ht]
@@
 
-  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data.
-The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low.
+  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability for all questions in the data.
+The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
 The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days.
@@
 
+% Univariate analysis on quantitative predictors
 \begin{table}[ht]
@@
   \hline \hline
-  Log transformation of the number of characters in a question's text* & 0.00 \\ 
+  *Log transformation of the number of characters in a question's text & 0.00 \\ 
   \hline
-  Square root transformation of the number of characters in a question's text* & 0.00 \\ 
+  *Square root transformation of the number of characters in a question's text & 0.00 \\ 
   \hline
@@
   \hline
-  Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text* & 0.00 \\ 
+  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 0.00 \\ 
   \hline
-  Square root transformation of the average frequency ``score'' of a question's tags* & 0.00 \\ 
+  *Square root transformation of the average frequency ``score'' of a question's tags & 0.00 \\ 
   \hline
@@
   \hline
-  Square root transformation of the number of characters in the user-defined device title* & 0.00 \\ 
+  *Square root transformation of the number of characters in the user-defined device title & 0.00 \\ 
   \hline
-  Square root transformation of the average number of characters in a question's tags* & 0.00 \\ 
+  *Square root transformation of the average number of characters in a question's tags & 0.00 \\ 
   \hline
@@
 
+% Univariate analysis on categorical predictors
 \begin{table}[ht]
@@
 Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
-All categorical predictors were entered into the full model.
+All categorical predictors and all * of quantitative predictors were entered into the full model.
 Restricted cubic splines were fit to all * quantitative variables.
 
+% Splines
 \begin{table}[ht]
@@
 
-Average performance metrics for test and training sets, found in table c, were considerably low.
+% Cross-validation metrics
+\begin{table}[ht]
+\centering
+\caption{Average performance metrics for training and test sets} 
+\begin{tabular}{rrrrrrrr}
+  \hline
+ & HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
+  \hline
+  Training Set & 2.00 & 959.49 & 0.00 & 0.14 & 64729.80 & 0.27 & 0.64 \\ 
+  Test Set & 1.96 & 225.44 & 0.00 & 0.14 & 13453.18 & 0.26 & 0.63 \\ 
+   \hline
+\end{tabular}
+\label{table:cv}
+\end{table}
+
+% Final metrics for full data 
+\begin{table}[ht]
+\centering
+\caption{Performance metrics for model fit to the full data} 
+\begin{tabular}{rrrrrrrr}
+  \hline
+  HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
+  \hline
+  2.00 & 1192.32 & 0.00 & 0.14 & 83128.28 & 0.27 & 0.63 \\ 
+   \hline
+\end{tabular}
+\label{table:finalmetrics}
+\end{table}
+
+Average performance metrics for test and training sets, found in Table \ref{table:cv}, were considerably low.
 However, metrics did not change substantially from training to test sets, indicating that the model does not overfit.
-The following restricted cubic splines were applied continuous variables:
-
-Results of cross-validation for the model including splines are in table d.
-As refitting the model without insignificant predictors and reperforming cross-validation did not change predictive accuracy, all variables were included.
 The final model, with all variables described above including splines, was fit to the full data.
 
-Score and deviance residuals of the final model identified outliers and highly influential questions.
-However, because refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data.
+% Final model on full data
+\begin{table}[ht]
+\centering
+\caption{Coefficients for predictors in the final model} 
+\begin{tabular}{|p{1.5cm}|p{6cm}|p{2.5cm}|p{2.5cm}|}
+  \hline
+ Variable &  Levels & Hazard Ratios & p-value \\ 
+  \hline
+  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.93 & \multirow{ 9 }{ 1.5cm }{ <0.0001 }\\ 
+  & Camera & -0.26 & \\ 
+  & Electronics & -0.08 &\\ 
+  & Game Console & 0.21 &\\ 
+  & Home & 0.39 &\\ 
+  & Other & -0.11 &\\ 
+  & PC & 0.43 &\\ 
+  & Tablet & -0.15 &\\ 
+  & Vehicle & 0.38 &\\
+  \hline
+  & Whether or not the user had been a member for less than one day before the question was posted & -0.10 & 0.0048 \\
+  \hline
+  & Whether or not the question's title contains terms considered to be frequently used among unanswered questions & -0.27 & <0.0001 \\ 
+  \hline
+  & Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.05 & 0.2235\\ 
+  \hline
+  & Whether or not the question's title ended in a questionmark & 0.25 & <0.0001\\ 
+  \hline
+  & Whether or not the question's text contained at least one end punctuation mark & 0.03 & 0.5348\\ 
+  \hline
+  & Whether or not the question's text is in all lower case & -0.18 & 0.0052 \\ 
+  \hline
+  & Whether or not the user edited or added information to the question's text sometime after posting it & 0.28 & 0.0009 \\ 
+  \hline
+  & Whether or not the user made an effort to solve the problem on their own, prior to asking the question & -0.09 & 0.0137 \\ 
+  \hline
+  \multirow{ 6 }{ 2 cm }{ Day of the Week } & Monday & 0.01 & \multirow{ 6 }{ 1.5cm }{ 0.0004 }\\ 
+  & Saturday & -0.07 & \\ 
+  & Sunday & -0.11 & \\ 
+  & Thursday & 0.03 & \\ 
+  & Tuesday & 0.09 & \\ 
+  & Wednesday & 0.10 & \\ 
+  \hline
+  & Square root transformation of the average frequency ``score'' of a question's tags & 2.23 & 0.0020 \\ 
+  \hline
+  \multirow{ 3 }{ 2cm }{ Square root transformation of the average number of characters in a question's tags } & _ & -0.08 & 0.0457\\ 
+  & avg\_tag\_length' & 0.58 & Nonlinear \\ 
+  & avg\_tag\_length'' & -1.52 & 0.0804\\ 
+  \hline
+  & text\_length & -0.08 \\ 
+  & text\_length' & -0.36 \\ 
+  & text\_length'' & 2.39 \\
+  & text\_length''' & -3.69 \\ 
+  \hline
+  & device\_length & -0.07 \\ 
+  & device\_length' & 0.18 \\ 
+  & device\_length'' & -0.27 \\ 
+  & device\_length''' & 0.21 \\ 
+  \hline
+  & newline\_ratio & 0.12 \\ 
+  & newline\_ratio' & 0.36 \\ 
+   \hline
+\end{tabular}
+\label{table:coefficients}
+\end{table}
+
+Score and deviance residuals of the final model identified outliers and highly influential questions, respectively.
+However, as refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data.
 Assessing the proportional hazards assumption indicated that several predictors were in violation.
-P-values for the correlation between predictors schoenfeld residuals and time are shown in table e.
-But as stratifying on this predictor substantially decreased predictive accuracy, the variable was left as is.
-Statistics and parameter coefficients of the final model are in table c.
-Metrics for the final model's performance on the full data, though considerably low, are not different from the metrics computed in cross-validation.
+Final model statistics and parameter coefficients are in Table \ref{table:coefficients}.
+Metrics for the final model's performance on the full data, found in \ref{table:finalmetrics}, though considerably low, are not different from the metrics computed in cross-validation.
 
@@
 
-This study developed a Cox regression model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
+This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
 Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, whether or not the user updated the question's text after the initial posting, whether or not the user indicated that he or she made an effort prior to answer their question prior to posting it (how should I write out that different knots of the splines were signficant).
@@
 
-device
+Device category
 
-The original device categorization variable, as defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
-This variable also contained a considerable amount of NAs (1954, or 25.2\% of all questions).
-NAs are a result of users asking questions for devices not already in the website's database, or from the user incorrectly defining the device.
+Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+Of all questions in the data, 1954 questions (25.2\%) contained missing values for this variable.
+Missing values were a result of users creating questions for devices not already in the website's database, or from the user incorrectly defining the device name.
+For questions with missing values, key words were searched for in device titles to recategorize accordingly.
+Remaining questions with ambiguous or completely missing device titles were categorized as ``Other''.
+The following modifications were made to the original variable: All Apple products (e.g., iPhones, iMacs, Apple watches) were categorized as ``Apple Product''.
+Remaining phones in the original ``Phones'' category were categorized as ``Android/Other Phone''.
+Appliance and Household categories of the original variable were merged into ``Home''.
+``Car and Truck'' were added to ``Vehicle''.
+Any category that contained less than 2\% of all questions were categorized as ``Other''.
+All other categories remained the same as the original variable.
+Final categories included: Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.
 
-This category variable contained NAs (include how many), a result of the asker creating a question for a device not already on the website's data base.
-Questions that made the device clear were categorized accordingly.
-However there were a number of questions that did not explicitly declare the device their question pertained too.
-These questions were categorized as ``Other''.
-All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category.
-After pulling out iPhones from the original ``Phones'' category, the remaining phones were categorized as ``AndroidOther Phone''.
-Appliance and Household categories of the original variable were merged into ``Home''.
-``Car and Truck'' were added to the ``Vehicle''.
-Lastly, any category that contained less than 2\% of the questions were categorized as ``Other''.
-All other categories remained the same as the original category.
-The final categories in the new categorization variable were Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.
+Whether or not the question's title contains terms considered to be frequently used among unanswered/answered questions
 
-contain answered and unanswered
+Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively.
 
-  These variables were created based on the intuition that certain topics might be more popular, and even unpopular, among the answering community, and that questions concerning these topics might recieve an answer faster, or slower, than questions that don't.
+These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
+Similarly, certain topics might be unpopular.
+Thus, questions pertaining to those topics might receive answers slower (cite).
 
-  To create these variables, the data was separated between answered and unanswered questions.
-Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions--containing every word within the question's titles and the frequency or the number of time they occured among answered and unanswered questions.
-For ``frequently-used'' words in answered questions, that word would have to appear in more than 1\% of answered question's titles, and would have to appear in answered questions more than it appeared in unanswered questions.
-To determine the latter, a ratio of proportions was assessed.
-This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
-As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20).
-As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1).
-Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list.
-The resulting list for answered questions was 111 words, and 32 words in uanswered questions.
-Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.
+The data was separated between answered and unanswered questions.
+For the data frame containing answered questions, text mining techniques were used to create a list with every word within questions' titles and the frequency, or number of times they occurred among answered questions.
+The same was performed for the data frame containing unanswered questions.
+``Frequently-used'' words in answered questions were defined as those that appeared in more than 1\% of answered questions' titles, and appeared in more answered questions than in unanswered questions.
+To determine the latter, a ratio of frequencies, or proportions of times a word occurs, was assessed.
+The ratio was calculated as the proportion of time a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
+As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered frequently-used among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
+As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of unanswered question's titles and occur in more unanswered questions than answered questions.
+As there was some overlap between words in each list and the device categories, every word that matched a device name was removed from the lists.
+The resulting list for answered questions contained 111 words.
+The list for unanswered questions contained 32 words.
 
-111 terms found to be ``frequently-used'' among answered questions (ordered from highest frequency): 
+``Frequently-used'' terms among answered questions (ordered by decreasing frequency): 
 screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top
 
-32 terms found to be ``frequently-used'' among unanswered questions (ordered from highest frequency):
+``Frequently-used'' terms among unanswered questions (ordered by decreasing frequency):
 sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit
 
-Title\_questionmark and title\_beginwh
+Whether or not the question's title ended in a questionmark
 
-These two variables were created to determine if stating the title in the form of a question is associated with faster answer times.
-Title_questionmark is a logical variable indicating true if the question's title ends with a question mark.
-Title_beginwh is a logical variable indicating true if the title begins with a “wh” word (e.g.
-"what", "when").
-These variables were created based off of the findings from \citep{Bhat2014}.
+A logical variable indicating true if the question's title ends in a questionmark.
+This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.
 
-Text\_contain\_punct
+Whether or not the question's text contained at least one end punctuation mark
 
-A logical variable indicating true if the question’s text contains any end punctuation marks (.
-?
-!).
-This variable was created to investigate if run-on sentences, or sentences with no end punctuation, take longer to receive an answer.
+A logical variable indicating true if the question’s text contains any end punctuation marks (``.'', ``?'', ``!'').
+This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.
 
-Prior\_effort
+Whether or not the user made an effort to solve the problem on their own, prior to asking the question
 
-Logical variable indicating true if the asker used words that indicate prior effort or research was done before asking the question (e.g.
+Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g.
 ``tried'', ``attempted'', ``tested'').
@@
 
-Ampm (change name)
+Average frequency ``score'' of a question's tags
 
-The time of day the question was posted.
-If the question was posted between 5am and 12pm, it was categorized as ``morning''.
-If it was posted between 12pm and 5pm, it was categorized as ``afternoon'', between 5pm and 8am- ``evening'', and 8pm and 5 am, ``night''
-
-Avg\_tag\_score
-
-This variable was created to investigate the idea that some tags are more popular, or widely used than other, and that including such tags might increase the likelihood of that question recieving an answer.
+This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving a faster answer.
 This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
@@
 
-Device\_length
+Number of characters in the user-defined device title
 
-The number of characters in the user-defined device variable.
-This variable was included to capture when a user incorrectly inputs the device name.
-For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One” and is 136 characters long.
-11 questions in this data set also didn’t include any device.
-This variable was created based on the intuition that users who incorrectly define their devices make it harder for answerers to discern the topic of their question, and thus have longer answer times or might not recieve an answer.
+This variable was included to capture when a user incorrectly defines the device name.
+For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”, and is 136 characters long.
+11 questions in the data also did not include any device title.
+This variable was created based on the intuition that users who incorrectly define their devices, or do not include any device title, make it difficult for the answering community to discern the question's topic, and thus have longer answer times or remain unanswered.
 
-Avg\_tag\_length
+Average number of characters in a question's tags
 
-The average number of characters in each question's user-defined tags.
-If a question did not include a tag, this variable was set to 0.
-This variable, like the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
-For example, question 390989 includes tag: “i need to repair the headset because i can not find the bluetoot” and is 64 characters long, while question 410254 includes tags "sound", "sound driver" and "speaker" and has an average tag length of 8 characters.
-It is hypothesized that users who use the tagging system correctly, as with the latter user, receive answers quicker than the former user.
+This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
+For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters.
+Question 410254 includes tags "sound", "sound driver" and "speaker" and has an average of 8 characters per tag.
+It is hypothesized that users who correctly define tags, as with the latter user, receive answers quicker than the former.
 
-Newline\_ratio
+Ratio of the number of line breaks to the number of characters in a question's text
 
-This ratio of the number of newlines to the number of characters in the question's text.
-This variable was based on the intuition that question's that include newlines in the text are easier to read and thus have faster answer times.
-Questions with long text that also include newlines are generally easier to read than questions that don’t include any.
+This variable was based on the hypothesis that question's that include line breaks in the text are generally easier to read than questions that don't include any, and thus have faster answer times.
 

### 2017-12-13 article submission/draft1.tex
fixed appendix, added tables

@@
 Questions analyzed were restricted to those posted in English.
-The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
+Time until event was defined as the time since posting until a question received its first answer.
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).
+These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times in the data (questions can still receive answers after the download date).
 
@@
 Each training set contained 6208 questions, and each test set contained 1552 questions.
-Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model.
-Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied.
-Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed.
-Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.
+Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model.
+Distributions of continuous variables were assessed.
+Each categorical and continuous predictor, both with and without square root and log transformations, were entered into separate univariate Cox models and strength of association with answer times were assessed.
+Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model.
+For continuous predictors, the lowest p-value was used to determine if and which transformation was necessary.
+To determine whether or not splines on continuous predictors were necessary, as well as the optimum number of knots, univariate analysis was again performed.
+Continuous variables (with transformations found to be necessary in the previous univariate analysis) were again fit to separate univariate Cox models with: no splines and restricted cubic splines of three, four, and five knots.
+AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{}Harrell2015.
+All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.
 
-In each fold of cross-validation, the full model, with variables found to be signficant in univariate analysis, was built on one of the training sets and used to generate predicted hazard ratios on the corresponding test sets.
-To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time.
+In each fold of cross-validation, the full model was built on one training set and used to generate predicted hazard ratios on the corresponding test set.
+To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time.
 The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}.
-Signficant statistics would indicate high predictive accuracy.
+Signficant results would indicate high predictive accuracy.
 Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination.
@@
 
-  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data.
-The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low.
+  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability for all questions in the data.
+The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
 The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
@@
 
+% Cross-validation metrics
 \begin{table}[ht]
@@
 
+% Final metrics for full data 
+\begin{table}[ht]
+\centering
+\caption{Performance metrics for model fit to the full data} 
+\begin{tabular}{rrrrrrrr}
+  \hline
+  HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
+  \hline
+  2.00 & 1192.32 & 0.00 & 0.14 & 83128.28 & 0.27 & 0.63 \\ 
+   \hline
+\end{tabular}
+\label{table:finalmetrics}
+\end{table}
+
 Average performance metrics for test and training sets, found in Table \ref{table:cv}, were considerably low.
@@
 
+% Final model on full data
 \begin{table}[ht]
 \centering
-\caption{P-values for final model fit to the full data} 
-\begin{tabular}{|p{12cm}|p{1cm}|}
+\caption{Coefficients for predictors in the final model} 
+\begin{tabular}{|p{1.5cm}|p{6cm}|p{2.5cm}|p{2.5cm}|}
   \hline
-Predictor & p \\ 
-  \hline \hline
-Device Category & 0.00 \\ 
+ Variable &  Levels & Hazard Ratios & p-value \\ 
   \hline
-Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
+  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.93 & \multirow{ 9 }{ 1.5cm }{ <0.0001 }\\ 
+  & Camera & -0.26 & \\ 
+  & Electronics & -0.08 &\\ 
+  & Game Console & 0.21 &\\ 
+  & Home & 0.39 &\\ 
+  & Other & -0.11 &\\ 
+  & PC & 0.43 &\\ 
+  & Tablet & -0.15 &\\ 
+  & Vehicle & 0.38 &\\
   \hline
-Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\
+  & Whether or not the user had been a member for less than one day before the question was posted & -0.10 & 0.0048 \\
   \hline
-Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.22 \\ 
+  & Whether or not the question's title contains terms considered to be frequently used among unanswered questions & -0.27 & <0.0001 \\ 
   \hline
-Whether or not the question's title ended in a questionmark & 0.00 \\ 
+  & Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.05 & 0.2235\\ 
   \hline
-Whether or not the question's text contained at least one end punctuation mark & 0.53 \\ 
+  & Whether or not the question's title ended in a questionmark & 0.25 & <0.0001\\ 
   \hline
-Whether or not the question's text is in all lower case & 0.01 \\ 
+  & Whether or not the question's text contained at least one end punctuation mark & 0.03 & 0.5348\\ 
   \hline
-Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\ 
+  & Whether or not the question's text is in all lower case & -0.18 & 0.0052 \\ 
   \hline
-Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.01 \\ 
+  & Whether or not the user edited or added information to the question's text sometime after posting it & 0.28 & 0.0009 \\ 
   \hline
-Day of the week the question was posted & 0.00 \\ 
+  & Whether or not the user made an effort to solve the problem on their own, prior to asking the question & -0.09 & 0.0137 \\ 
   \hline
-Square root transformation of the average frequency ``score'' of a question's tags & 0.00 \\ 
+  \multirow{ 6 }{ 2 cm }{ Day of the Week } & Monday & 0.01 & \multirow{ 6 }{ 1.5cm }{ 0.0004 }\\ 
+  & Saturday & -0.07 & \\ 
+  & Sunday & -0.11 & \\ 
+  & Thursday & 0.03 & \\ 
+  & Tuesday & 0.09 & \\ 
+  & Wednesday & 0.10 & \\ 
   \hline
-Square root transformation of the average number of characters in a question's tags & 0.05 \\ 
-Nonlinear & 0.08 \\ 
+  & Square root transformation of the average frequency ``score'' of a question's tags & 2.23 & 0.0020 \\ 
   \hline
-Square root transformation of the number of characters in a question's text & 0.43 \\ 
-Nonlinear & 0.46 \\ 
+  \multirow{ 3 }{ 2cm }{ Square root transformation of the average number of characters in a question's tags } & _ & -0.08 & 0.0457\\ 
+  & avg\_tag\_length' & 0.58 & Nonlinear \\ 
+  & avg\_tag\_length'' & -1.52 & 0.0804\\ 
   \hline
-Square root transformation of the number of characters in the user-defined device title & 0.28 \\ 
-Nonlinear & 0.42 \\ 
+  & text\_length & -0.08 \\ 
+  & text\_length' & -0.36 \\ 
+  & text\_length'' & 2.39 \\
+  & text\_length''' & -3.69 \\ 
   \hline
-Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 0.36 \\ 
-Nonlinear & 0.62 \\ 
+  & device\_length & -0.07 \\ 
+  & device\_length' & 0.18 \\ 
+  & device\_length'' & -0.27 \\ 
+  & device\_length''' & 0.21 \\ 
+  \hline
+  & newline\_ratio & 0.12 \\ 
+  & newline\_ratio' & 0.36 \\ 
    \hline
 \end{tabular}
-\label{table:pvalues}
-\end{table}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{rlr}
-  \hline
- & variable & coefficients \\ 
-  \hline
-1 & new\_category=Apple Product & 0.93 \\ 
-  2 & new\_category=Camera & -0.26 \\ 
-  3 & new\_category=Electronics & -0.08 \\ 
-  4 & new\_category=Game Console & 0.21 \\ 
-  5 & new\_category=Home & 0.39 \\ 
-  6 & new\_category=Other & -0.11 \\ 
-  7 & new\_category=PC & 0.43 \\ 
-  8 & new\_category=Tablet & -0.15 \\ 
-  9 & new\_category=Vehicle & 0.38 \\ 
-  10 & new\_user=1 & -0.10 \\ 
-  11 & contain\_unanswered & -0.27 \\ 
-  12 & contain\_answered & 0.05 \\ 
-  13 & title\_questionmark & 0.25 \\ 
-  14 & text\_contain\_punct & 0.03 \\ 
-  15 & text\_all\_lower & -0.18 \\ 
-  16 & update & 0.28 \\ 
-  17 & prior\_effort & -0.09 \\ 
-  18 & weekday=Monday & 0.01 \\ 
-  19 & weekday=Saturday & -0.07 \\ 
-  20 & weekday=Sunday & -0.11 \\ 
-  21 & weekday=Thursday & 0.03 \\ 
-  22 & weekday=Tuesday & 0.09 \\ 
-  23 & weekday=Wednesday & 0.10 \\ 
-  24 & avg\_tag\_score & 2.23 \\ 
-  25 & avg\_tag\_length & -0.08 \\ 
-  26 & avg\_tag\_length' & 0.58 \\ 
-  27 & avg\_tag\_length'' & -1.52 \\ 
-  28 & text\_length & -0.08 \\ 
-  29 & text\_length' & -0.36 \\ 
-  30 & text\_length'' & 2.39 \\ 
-  31 & text\_length''' & -3.69 \\ 
-  32 & device\_length & -0.07 \\ 
-  33 & device\_length' & 0.18 \\ 
-  34 & device\_length'' & -0.27 \\ 
-  35 & device\_length''' & 0.21 \\ 
-  36 & newline\_ratio & 0.12 \\ 
-  37 & newline\_ratio' & 0.36 \\ 
-   \hline
-\end{tabular}
-\caption{Coefficients for predictors in the final model} 
 \label{table:coefficients}
@@
 
-Score and deviance residuals of the final model identified outliers and highly influential questions.
-However, because refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data.
+Score and deviance residuals of the final model identified outliers and highly influential questions, respectively.
+However, as refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data.
 Assessing the proportional hazards assumption indicated that several predictors were in violation.
-P-values for the correlation between predictors schoenfeld residuals and time are shown in table e.
-But as stratifying on this predictor substantially decreased predictive accuracy, the variable was left as is.
-Statistics and parameter coefficients of the final model are in table c.
-Metrics for the final model's performance on the full data, though considerably low, are not different from the metrics computed in cross-validation.
+Final model statistics and parameter coefficients are in Table \ref{table:coefficients}.
+Metrics for the final model's performance on the full data, found in \ref{table:finalmetrics}, though considerably low, are not different from the metrics computed in cross-validation.
 

### 2017-12-15 article submission/draft1.Rnw
edited methods, fixed rounding on pvalues, edited appendix

@@
 << echo = FALSE >>=
-# setting up model
+# importing data 
 dir <- file.path(getwd(),"data")
@@
 Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.
+
+%----------------------------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------------------------
+
 \section*{Related Work}
@@
 \citep{Asaduzzaman2013} analyzed unanswered questions on \textit{Stack Overflow} to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.
+
+%----------------------------------------------------------------------------------------------------
 
@@
 \begin{itemize}
-  \item Average tag ``score'' for all of a question's tags.
-A tag score is defined as the proportion of times a tag appears in all of the data.
-Questions without tags were assigned an average tag score of 0.
+  \item Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. 
   \item Average number of characters in each question's tags. 
@@
 
+%----------------------------------------------------------------------------------------------------
+
 \section*{Methods}
-
-<< echo = FALSE >>=
-set.seed(444)
-splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
-
-train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
-train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
-train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
-train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
-train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
-@
 
@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times in the data (questions can still receive answers after the download date).
+Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).
 
@@
 To build the model, five-fold cross-validation was used.
-The full data was split into five training and five test sets.
-Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
-Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model.
-Distributions of continuous variables were assessed.
-Each categorical and continuous predictor, both with and without square root and log transformations, were entered into separate univariate Cox models and strength of association with answer times were assessed.
+The full data was split into five training sets and five test sets.
+Univariate analysis, performed on one training set, was used to identify variables and transformations to potentially include in the final Cox model.
+Distributions of all continuous predictors, both with and without square root and log transformations, were assessed.
+Each categorical and continuous predictor, both untransformed and transformed, were entered into separate univariate Cox models, and strength of association with answer times were assessed.
 Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model.
-For continuous predictors, the lowest p-value was used to determine if and which transformation was necessary.
-To determine whether or not splines on continuous predictors were necessary, as well as the optimum number of knots, univariate analysis was again performed.
-Continuous variables (with transformations found to be necessary in the previous univariate analysis) were again fit to separate univariate Cox models with: no splines and restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{}Harrell2015.
+For continuous predictors, the p-value was used to determine which form of the predictor to include---transformed or untransformed.
+To investigate the use of splines on continuous predictors, univariate analysis was again performed.
+Continuous variables (with transformations previously found to be necessary) were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines.
+AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{Harrell2015}.
 All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.
 
-In each fold of cross-validation, the full model was built on one training set and used to generate predicted hazard ratios on the corresponding test set.
+In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
 To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time.
-The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}.
+The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance \citep{Chen}.
 Signficant results would indicate high predictive accuracy.
@@
 Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}.
-Metrics were computed for each training and test set.
+These metrics were computed for each iteration on every training and test set.
 Averages of metrics across test sets were evaluated.
@@
 Score residuals were used to identify questions that highly effected parameter estimates.
-Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time.
-Significant correlations indicate that a predictor has violated this assumption.
+Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time.
+Significant correlations would indicate that a predictor has violated this assumption.
+
+%----------------------------------------------------------------------------------------------------
 
@@
 << echo = FALSE >>=
+# for inline code 
 answered <- sum(x$answered)
@@
 The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
-Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
+Figure ~\ref{fig:answertimes} shows that the distribution of answer times for all questions is extremely right-skewed.
 
 << echo = FALSE >>=
+# Kaplan-Meier survival estimates
 surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
 KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
+
 stats <- summary(KM)$table
@@
   \hline
-  *Square root transformation of the number of characters in a question's text & 0.00 \\ 
+  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ 
   \hline
-  Number of characters in a question's text (untransformed) & 0.00 \\
+  Number of characters in a question's text (untransformed) & 6.9472e-12 \\
   \hline
-  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 0.00 \\ 
+  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ 
   \hline
-  *Square root transformation of the average frequency ``score'' of a question's tags & 0.00 \\ 
+  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ 
   \hline
-  Average frequency ``score'' of a question's tags (untransformed) & 0.00 \\ 
+  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ 
   \hline
-  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 0.00 \\ 
+  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ 
   \hline
-  *Square root transformation of the number of characters in the user-defined device title & 0.00 \\ 
+  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ 
   \hline
-  *Square root transformation of the average number of characters in a question's tags & 0.00 \\ 
+  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ 
   \hline
-  Number of characters in the user-defined device title (untransformed) & 0.01 \\ 
+  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ 
   \hline
-  Average number of characters in a question's tags (untransformed) & 0.03 \\ 
+  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ 
    \hline
@@
   \hline
-  Whether or not the question's title ended in a questionmark & 0.00 \\ 
-  \hline
-  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
-  \hline
-  Day of the week the question was posted & 0.00 \\ 
-  \hline
-  Whether or not the question's text is in all lower case & 0.00 \\ 
-  \hline
-  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
-  \hline
-  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
-  \hline
   Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
   \hline
-  Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.00 \\ 
+  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ 
+  \hline
+  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ 
+  \hline
+  Whether or not the question's text is in all lower case & 1.5400e-7 \\ 
+  \hline
+  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ 
+  \hline
+  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\
+  \hline
+  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ 
+  \hline
+  Day of the week the question was posted & 7.8677e-4 \\ 
    \hline
@@
 
-Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
-All categorical predictors and all * of quantitative predictors were entered into the full model.
-Restricted cubic splines were fit to all * quantitative variables.
+<< echo = FALSE >>=
+set.seed(444)
+splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
+
+train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
+train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
+train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
+train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
+train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
+@
+
+Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
+Results of univariate analyis, performed on one training set, for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+All categorical predictors, as well as all continuous predictors marked with * were entered into the full model.
 
@@
 \caption{Determining the optimal k number of splines for each predictor} 
-\begin{tabular}{| p{5cm} | l | l | l |}
+\begin{tabular}{| p{5cm} | l | l |}
   \hline
-  Predictor & K & p-value & AIC \\ 
+  Predictor & K & AIC \\ 
   \hline
   \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
-  & 0 & 0.00 & 65862.83 \\ 
-  & 5* & 0.00 & 65862.02 \\ 
-  & 4 & 0.00 & 65863.35 \\ 
-  & 3 & 0.00 & 65862.08 \\ 
+  & 0 & 65862.83 \\ 
+  & 5* & 65862.02 \\ 
+  & 4 & 65863.35 \\ 
+  & 3 & 65862.08 \\ 
   \hline
   \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
-  & 0 & 0.00 & 65890.28 \\ 
-  & 5 & 0.00 & 65884.70 \\ 
-  & 4 & 0.00 & 65882.98 \\ 
-  & 3* & 0.00 & 65881.93 \\ 
+  & 0 & 65890.28 \\ 
+  & 5 & 65884.70 \\ 
+  & 4 & 65882.98 \\ 
+  & 3* & 65881.93 \\ 
   \hline
   \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
-  & 0* & 0.00 & 65890.75 \\ 
-  & 5 & 0.00 & 65891.69 \\ 
-  & 4 & 0.00 & 65891.75 \\ 
-  & 3 & 0.00 & 65892.35 \\ 
+  & 0* & 65890.75 \\ 
+  & 5 & 65891.69 \\ 
+  & 4 & 65891.75 \\ 
+  & 3 & 65892.35 \\ 
   \hline
   \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
-  & 0 & 0.00 & 65922.76 \\ 
-  & 5* & 0.00 & 65853.56 \\ 
-  & 4 & 0.00 & 65882.07 \\ 
-  & 3 & 0.00 & 65881.39 \\ 
+  & 0 & 65922.76 \\ 
+  & 5* & 65853.56 \\ 
+  & 4 & 65882.07 \\ 
+  & 3 & 65881.39 \\ 
   \hline
   \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
-  & 0 & 0.00 & 65923.26 \\ 
-  & 5 & 0.00 & 65912.11 \\ 
-  & 4* & 0.00 & 65910.10 \\ 
-  & 3 & 0.00 & 65912.38 \\ 
+  & 0 & 65923.26 \\ 
+  & 5 & 65912.11 \\ 
+  & 4* & 65910.10 \\ 
+  & 3 & 65912.38 \\ 
    \hline
@@
 
-Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model for cross-validation.
+Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model.
 
@@
   \hline
-  Training Set & 2.00 & 959.49 & 0.00 & 0.14 & 64729.80 & 0.27 & 0.64 \\ 
-  Test Set & 1.96 & 225.44 & 0.00 & 0.14 & 13453.18 & 0.26 & 0.63 \\ 
+  Training Sets & 2.0164 & 937.2018 & 0.0000 & 0.1401 & 64752.0898 & 0.2693 & 0.6346 \\ 
+  Test Sets & 1.9761 & 220.0417 & 0.0000 & 0.1401 & 13458.5808 & 0.2584 & 0.6292 \\
    \hline
@@
   \hline
-  2.00 & 1192.32 & 0.00 & 0.14 & 83128.28 & 0.27 & 0.63 \\ 
+  2.0010 & 1192.3234 & 0.0000 & 0.1424 & 83128.2780 & 0.2698 & 0.6349 \\ 
    \hline
@@
   \hline
-  & text\_length & -0.08 \\ 
-  & text\_length' & -0.36 \\ 
-  & text\_length'' & 2.39 \\
-  & text\_length''' & -3.69 \\ 
+  \multirow{ 4 }{ 2cm }{Log transformation of the number of characters in a question's text} & text length & -0.08 & 0.4344
+  & text\_length' & -0.36 & Nonlinear \\ 
+  & text\_length'' & 2.39 & 0.4578 \\
+  & text\_length''' & -3.69 & \\ 
   \hline
-  & device\_length & -0.07 \\ 
-  & device\_length' & 0.18 \\ 
-  & device\_length'' & -0.27 \\ 
-  & device\_length''' & 0.21 \\ 
+  \multirow{ 4 }{ 2cm }{ Square root transformation of the number of characters in a question's device title} & device length & -0.07 & 0.2790 \\
+  & device\_length' & 0.18 & Nonlinear \\ 
+  & device\_length'' & -0.27 & 0.4185\\ 
+  & device\_length''' & 0.21 & \\ 
   \hline
-  & newline\_ratio & 0.12 \\ 
-  & newline\_ratio' & 0.36 \\ 
+  \multirow{ 2 }{ 2cm }{ Square root transformation of the ratio of number of line breaks to number of characters in a question's text} & line break & 0.12 & 0.3569 \\
+  & newline\_ratio' & 0.36 & Nonlinear: 0.6191 \\ 
    \hline
@@
 Metrics for the final model's performance on the full data, found in \ref{table:finalmetrics}, though considerably low, are not different from the metrics computed in cross-validation.
+
+%----------------------------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------------------------
+
 \section*{Conclusion}
@@
 
+%----------------------------------------------------------------------------------------------------
+
 \section*{Acknowledgement}
@@
 This research is supported by the Bill and Linda Frost fund.
+
+%----------------------------------------------------------------------------------------------------
 

### 2017-12-15 article submission/draft1.tex
edited methods, fixed rounding on pvalues, edited appendix

@@
 
+%----------------------------------------------------------------------------------------------------
+
 \section*{Methods}
@@
 To build the model, five-fold cross-validation was used.
-The full data was split into five training and five test sets.
-Each training set contained 6208 questions, and each test set contained 1552 questions.
-Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model.
-Distributions of continuous variables were assessed.
-Each categorical and continuous predictor, both with and without square root and log transformations, were entered into separate univariate Cox models and strength of association with answer times were assessed.
+The full data was split into five training sets and five test sets.
+Univariate analysis, performed on one training set, was used to identify variables and transformations to potentially include in the final Cox model.
+Distributions of all continuous predictors, both with and without square root and log transformations, were assessed.
+Each categorical and continuous predictor, both untransformed and transformed, were entered into separate univariate Cox models, and strength of association with answer times were assessed.
 Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model.
-For continuous predictors, the lowest p-value was used to determine if and which transformation was necessary.
-To determine whether or not splines on continuous predictors were necessary, as well as the optimum number of knots, univariate analysis was again performed.
-Continuous variables (with transformations found to be necessary in the previous univariate analysis) were again fit to separate univariate Cox models with: no splines and restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{}Harrell2015.
+For continuous predictors, the p-value was used to determine which form of the predictor to include---transformed or untransformed.
+To investigate the use of splines on continuous predictors, univariate analysis was again performed.
+Continuous variables (with transformations previously found to be necessary) were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines.
+AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{Harrell2015}.
 All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.
 
-In each fold of cross-validation, the full model was built on one training set and used to generate predicted hazard ratios on the corresponding test set.
+In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
 To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time.
-The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}.
+The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance \citep{Chen}.
 Signficant results would indicate high predictive accuracy.
@@
 The longest was 2159.02 hours (89.96 days).
-Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.
+Figure ~\ref{fig:answertimes} shows that the distribution of answer times for all questions is extremely right-skewed.
 
@@
 
-Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
-All categorical predictors and all * of quantitative predictors were entered into the full model.
-Restricted cubic splines were fit to all * quantitative variables.
+Each training set contained 6208 questions, and each test set contained 1552 questions.
+Results of univariate analyis, performed on one training set, for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+All categorical predictors, as well as all continuous predictors marked with * were entered into the full model.
 
@@
 
+%----------------------------------------------------------------------------------------------------
+
 \section*{Conclusion}
 
-This study developed a Cox regression model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
+This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
 Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, whether or not the user updated the question's text after the initial posting, whether or not the user indicated that he or she made an effort prior to answer their question prior to posting it (how should I write out that different knots of the splines were signficant).
 While overall the model was signficant, its predictive performance was considerably low.
+
+%----------------------------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------------------------
+
 \section{Appendix}
 
-device
+Device category
 
-The original device categorization variable, as defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
-This variable also contained a considerable amount of NAs (1954, or 25.2\% of all questions).
-NAs are a result of users asking questions for devices not already in the website's database, or from the user incorrectly defining the device.
+Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+Of all questions in the data, 1954 questions (25.2\%) contained missing values for this variable.
+Missing values were a result of users creating questions for devices not already in the website's database, or from the user incorrectly defining the device name.
+For questions with missing values, key words were searched for in device titles to recategorize accordingly.
+Remaining questions with ambiguous or completely missing device titles were categorized as ``Other''.
+The following modifications were made to the original variable: All Apple products (e.g., iPhones, iMacs, Apple watches) were categorized as ``Apple Product''.
+Remaining phones in the original ``Phones'' category were categorized as ``Android/Other Phone''.
+Appliance and Household categories of the original variable were merged into ``Home''.
+``Car and Truck'' were added to ``Vehicle''.
+Any category that contained less than 2\% of all questions were categorized as ``Other''.
+All other categories remained the same as the original variable.
+Final categories included: Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.
 
-This category variable contained NAs (include how many), a result of the asker creating a question for a device not already on the website's data base.
-Questions that made the device clear were categorized accordingly.
-However there were a number of questions that did not explicitly declare the device their question pertained too.
-These questions were categorized as ``Other''.
-All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category.
-After pulling out iPhones from the original ``Phones'' category, the remaining phones were categorized as ``AndroidOther Phone''.
-Appliance and Household categories of the original variable were merged into ``Home''.
-``Car and Truck'' were added to the ``Vehicle''.
-Lastly, any category that contained less than 2\% of the questions were categorized as ``Other''.
-All other categories remained the same as the original category.
-The final categories in the new categorization variable were Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.
+Whether or not the question's title contains terms considered to be frequently used among unanswered/answered questions
 
-contain answered and unanswered
+Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively.
 
-  These variables were created based on the intuition that certain topics might be more popular, and even unpopular, among the answering community, and that questions concerning these topics might recieve an answer faster, or slower, than questions that don't.
+These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
+Similarly, certain topics might be unpopular.
+Thus, questions pertaining to those topics might receive answers slower (cite).
 
-  To create these variables, the data was separated between answered and unanswered questions.
-Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions--containing every word within the question's titles and the frequency or the number of time they occured among answered and unanswered questions.
-For ``frequently-used'' words in answered questions, that word would have to appear in more than 1\% of answered question's titles, and would have to appear in answered questions more than it appeared in unanswered questions.
-To determine the latter, a ratio of proportions was assessed.
-This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
-As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20).
-As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1).
-Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list.
-The resulting list for answered questions was 111 words, and 32 words in uanswered questions.
-Contain\_answered and contain\_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.
+The data was separated between answered and unanswered questions.
+For the data frame containing answered questions, text mining techniques were used to create a list with every word within questions' titles and the frequency, or number of times they occurred among answered questions.
+The same was performed for the data frame containing unanswered questions.
+``Frequently-used'' words in answered questions were defined as those that appeared in more than 1\% of answered questions' titles, and appeared in more answered questions than in unanswered questions.
+To determine the latter, a ratio of frequencies, or proportions of times a word occurs, was assessed.
+The ratio was calculated as the proportion of time a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
+As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered frequently-used among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
+As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of unanswered question's titles and occur in more unanswered questions than answered questions.
+As there was some overlap between words in each list and the device categories, every word that matched a device name was removed from the lists.
+The resulting list for answered questions contained 111 words.
+The list for unanswered questions contained 32 words.
 
-111 terms found to be ``frequently-used'' among answered questions (ordered from highest frequency): 
+``Frequently-used'' terms among answered questions (ordered by decreasing frequency): 
 screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top
 
-32 terms found to be ``frequently-used'' among unanswered questions (ordered from highest frequency):
+``Frequently-used'' terms among unanswered questions (ordered by decreasing frequency):
 sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit
 
-Text\_contain\_punct
+Whether or not the question's title ended in a questionmark
 
-A logical variable indicating true if the question’s text contains any end punctuation marks (.
-?
-!).
-This variable was created to investigate if run-on sentences, or sentences with no end punctuation, take longer to receive an answer.
+A logical variable indicating true if the question's title ends in a questionmark.
+This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.
 
-Prior\_effort
+Whether or not the question's text contained at least one end punctuation mark
 
-Logical variable indicating true if the asker used words that indicate prior effort or research was done before asking the question (e.g.
+A logical variable indicating true if the question’s text contains any end punctuation marks (``.'', ``?'', ``!'').
+This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.
+
+Whether or not the user made an effort to solve the problem on their own, prior to asking the question
+
+Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g.
 ``tried'', ``attempted'', ``tested'').
@@
 
-Avg\_tag\_score
+Average frequency ``score'' of a question's tags
 
-This variable was created to investigate the idea that some tags are more popular, or widely used than other, and that including such tags might increase the likelihood of that question recieving an answer.
+This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving a faster answer.
 This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.

### 2017-12-15 article submission/graphics.Rmd
edited rounding on tables

@@
 
+### Model on full data
+
 ```{r}
@@
                    surv = TRUE)
+model
 ```
 
-### Univariate analysis results (Table 2) see univariate_analysis file
+### Univariate analysis results
 
@@
 
+c_pvalue <- c_pvalue %>% arrange(pvalue)
+
 xtable::xtable(c_pvalue, 
@@
 
-options(scipen=999)
 univ_results <- univ_results %>% arrange(pvalue)
@@
 taglength <- fit_splines("sqrt(avg_tag_length)") # 4 knots
-txt
-newline
-tagscore
-device
-taglength
 
@@
 
-xtable::xtable(splinedf, caption = "Determining the optimal number of splines for each predictor", label = "table:splines")
+xtable::xtable(splinedf, caption = "Determining the optimal number of splines for each predictor", label = "table:splines", digits = -16)
 ```
@@
   train_metrics <- data.frame(HR = exp(metric$coefficients), 
-                              LR = round(metric$stats[3],2), 
-                              pval = round(metric$stats[5],2),
-                              R2 = round(metric$stats[8], 2),
+                              LR = metric$stats[3], 
+                              pval = metric$stats[5],
+                              R2 = metric$stats[8],
                               AIC = stats::AIC(metric, k = 2),
-                              Dxy = round(metric$stats[9],2), 
+                              Dxy = metric$stats[9], 
                               Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)
@@
   test_metrics <- data.frame(HR = exp(metric1$coefficients), 
-                             LR = round(metric1$stats[3],2), 
-                             pval = round(metric1$stats[5],2), 
-                             R2 = round(metric$stats[8], 2),
+                             LR = metric1$stats[3], 
+                             pval = metric1$stats[5], 
+                             R2 = metric$stats[8],
                              AIC = stats::AIC(metric1, k = 2),
-                             Dxy = round(metric1$stats[9],2), 
+                             Dxy = metric1$stats[9], 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)
@@
 avg_results1
-xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv")
+xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv", digits = 4)
 ```
@@
 modelstats
-# ------------------------------------------
 
@@
 metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
-AIC(metric, k = 2) # 83124.21
 
 final_metrics <- data.frame(HR = exp(metric$coefficients), 
-                              LR = round(metric$stats[3],2), 
-                              pval = round(metric$stats[5],2),
-                              R2 = round(metric$stats[8], 2),
+                              LR = metric$stats[3], 
+                              pval = metric$stats[5],
+                              R2 = metric$stats[8],
                               AIC = stats::AIC(metric, k = 2),
-                              Dxy = round(metric$stats[9],2), 
+                              Dxy = metric$stats[9], 
                               Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
 final_metrics
+xtable::xtable(final_metrics, caption = "Performance metrics for model fit to the full data", label = "table:finalmetrics", digits = 4)
 

### 2017-12-22 article submission/draft1.Rnw
added citations

@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).
+Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \citep{Kleinbaum2011}.
 
 Survival was defined as the event that a question did not receive an answer beyond a certain time, t.
-Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions (cite).
+Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \citep{Bland1998}.
 From these estimates, survival curves were constructed to examine the survival experience of questions.
@@
 
-As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)).
+As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution) \citep{Moore2010}.
 To build the model, five-fold cross-validation was used.
-The full data was split into five training sets and five test sets.
-Univariate analysis, performed on one training set, was used to identify variables and transformations to potentially include in the final Cox model.
-Distributions of all continuous predictors, both with and without square root and log transformations, were assessed.
-Each categorical and continuous predictor, both untransformed and transformed, were entered into separate univariate Cox models, and strength of association with answer times were assessed.
-Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model.
-For continuous predictors, the p-value was used to determine which form of the predictor to include---transformed or untransformed.
+The full data was split into five training sets and five test sets \citep{sensitivity}.
+On one training set, distributions of all continuous variables were assessed and square root or log transformations were applied as necessary.
+Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model \citep{Hammer}.
+Each categorical and continuous predictor was entered into separate univariate Cox models, and strength of association with answer times was assessed.
+Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model.
 To investigate the use of splines on continuous predictors, univariate analysis was again performed.
-Continuous variables (with transformations previously found to be necessary) were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines.
+Continuous variables were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines.
 AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{Harrell2015}.
 All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.
+No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model harmed predictive accuracy, more so than leaving all predictors in.
 
@@
 To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time.
-The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance \citep{Chen}.
+The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance.
 Signficant results would indicate high predictive accuracy.
-Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination.
+Concordance statistics and Somers' Dxy were also assessed to measure the model's discriminative ability \citep{Chen}.
 Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard.
 Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
-Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}.
+Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5.
+A Somers' Dxy statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \citep{Harrell2015}.
 These metrics were computed for each iteration on every training and test set.
@@
 
-Martingale residuals were evaluated to assess functional form of each continuous predictor.
-Deviance residuals were used to identify outliers, or questions poorly predicted by the model.
-Score residuals were used to identify questions that highly effected parameter estimates.
-Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time.
-Significant correlations would indicate that a predictor has violated this assumption.
+Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \citep{therneau}.
+Significant correlations would indicate that a predictor has violated this assumption .
 

### 2017-12-29 article submission/draft1.Rnw
edited abstract, introduction, appendix

@@
 
-Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday.
-Forums can cover a broad range of topics, like \textit{Yahoo!
-Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}.
-An example of the latter is iFixit's \textit{Answers} forum.
-The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices.
-As such, it is important that questions receive timely answers.
-This paper presents a survival analysis on the time until a question receives its first answer.
-We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time.
-Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
-Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
-Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.
+Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge.
+Thousands of questions and answers are posted everyday.
+One such example of a CQA is iFixit's \textit{Answers} forum.
+This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users.
+A reliable measure of the health of these CQAs is question response time.
+Fast response times enhance user engagement and satisfaction, and increase web traffic.
+This paper presents a survival analysis of response time, or the time until a question receives its first answer.
+A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
+Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
+Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
+Future studies can investigate if factors identified as signifcant can be generalized to other CQAs.
 
@@
 
-Community-driven online question and answer forums (CQA) are becoming widely used sources of information.
-These online platforms allow for anyone to ask or answer a question, regardless of their background or expertise level.
-Forums can receive around 40 million visits every month.
+Community-driven online question and answer forums (CQA) are becoming widely-used sources of information.
+These online platforms feature thousands of user-posted questions and answers, and can receive millions of visits every month.
+The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
+Founded in 2003, iFixit's mission is to equip users with the knowledge and tools to repair their broken devices, as part of an effort to save money and reduce electronic waste.
+This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
 
-The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit's mission is to enable people to repair their broken devices, effectively saving them money and reducing electronic waste.
-The company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
-
-As not all possible repairs are covered in the published repair guides, and users may have questions related to those guides, iFixit's \textit{Answers} forum is another important resource.
-This platform features questions pertaining to over 9,000 devices with over 100,000 solutions.
-Questions range from broken devices like jammed zippers to shattered iPhone screens.
-As many rely on this forum for help with repairs, it is important that users receive timely answers.
-Fast response times will enhance user engagement and generate more web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum.
-Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved.
-However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated.
+As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is another important resource.
+This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions.
+As thousands of users rely on this forum for information, it is important that users receive timely answers.
+Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum.
+Analysis of response times can reveal factors that affect how quickly questions receive answered, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.
+However, analysis and prediction of response times on CQAs have not been thoroughly investigated.
 As the majority of existing research focuses on assessing and predicting question and answer quality, there is need for further analysis of response times in these forums.
-This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.
+This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.
 
@@
 
-In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model to analyze response times of questions posted on \textit{Stack Overflow}, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
+In regards to investigation of forum response times \cite{Bhat2014} developed a classification model to analyze response times of questions posted on \textit{Stack Overflow}, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
 
-\citep{Mamykina2011} found that the swift answer times of \textit{Stack Overflow's} community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.
+\cite{Mamykina2011} found that the swift answer times of \textit{Stack Overflow's} community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.
 
-\citep{Asaduzzaman2013} analyzed unanswered questions on \textit{Stack Overflow} to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.
+\cite{Asaduzzaman2013} analyzed unanswered questions on \textit{Stack Overflow} to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.
 
@@
 The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded).
-Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date the question was posted, date the first answer was received.
+Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date the question was posted, and date the first answer was received.
 Variables derived:
@@
 \begin{itemize}
-  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other.
+  \item Day of the week the question was posted. 
+  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle
+  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
+  \item Whether or not the question's text is in all lower case. 
   \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. 
@@
   \item Whether or not the question's title ends in a question mark.
-  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
-  \item Whether or not the question's text is in all lower case. 
   \item Whether or not the user edited or added information to the question's text sometime after posting it.
   \item Whether or not the user made an effort to solve the problem on their own, prior to asking the question.
-  \item Day of the week the question was posted. 
 \end{itemize}
@@
 \begin{itemize}
+  \item Average number of characters in each question's tags. 
   \item Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. 
-  \item Average number of characters in each question's tags. 
   \item Number of characters in the question's text. 
@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \citep{Kleinbaum2011}.
+Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \cite{Kleinbaum2011}.
 
 Survival was defined as the event that a question did not receive an answer beyond a certain time, t.
-Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \citep{Bland1998}.
+Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}.
 From these estimates, survival curves were constructed to examine the survival experience of questions.
@@
 
-As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution) \citep{Moore2010}.
+As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions (Cox models are not based on an assumption of the shape of the underlying probability distribution) \cite{Moore2010}.
 To build the model, five-fold cross-validation was used.
-The full data was split into five training sets and five test sets \citep{sensitivity}.
-On one training set, distributions of all continuous variables were assessed and square root or log transformations were applied as necessary.
-Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model \citep{Hammer}.
-Each categorical and continuous predictor was entered into separate univariate Cox models, and strength of association with answer times was assessed.
+The full data was split into five training sets and five test sets \cite{Rodriguez2010}.
+Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
+Each continuous predictor, with and without log and square root transformations, as well as each categorical predictor, was entereed into univarite Cox models, and strength of association with response times was assessed.
 Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model.
-To investigate the use of splines on continuous predictors, univariate analysis was again performed.
-Continuous variables were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines.
-AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{Harrell2015}.
-All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.
+Univariate analysis was again performed on each continuous predictor to investigate the use of splines.
+Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
+AIC statistics were used to determine whether or not to include restricted cubic splines for a predictor, as well as the optimum number of knots \cite{Harrell2015}.
+All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation.
 No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model harmed predictive accuracy, more so than leaving all predictors in.
@@
 In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
-To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time.
-The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance.
-Signficant results would indicate high predictive accuracy.
-Concordance statistics and Somers' Dxy were also assessed to measure the model's discriminative ability \citep{Chen}.
-Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard.
+To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
+The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' Dxy, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
+Signficant results from this model would indicate high predictive accuracy.
+The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
+The p-value for this statistic was calculated from the X2 distribution \cite{find}.
+Concordance statistics and Somers' Dxy are a measure of the model's discriminative ability.
+Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio.
 Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
 Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5.
-A Somers' Dxy statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \citep{Harrell2015}.
+A Somers' Dxy statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}.
 These metrics were computed for each iteration on every training and test set.
-Averages of metrics across test sets were evaluated.
+Averages of metrics across training and test sets were evaluated.
 The final model was then fit to the full data and the same metrics were computed and compared.
 
-Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \citep{therneau}.
-Significant correlations would indicate that a predictor has violated this assumption .
+Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}.
+Significant correlations would indicate that a predictor has violated this assumption.
+
+To convert the final model's predicted hazard ratios to predicted survival probability, an r function was used.
 
@@
 % Distribution of answer times
-\begin{figure}[h!]
+\begin{figure}[!htbp]
   \includegraphics[scale=1]{times_dist.pdf}
@@
 % Kaplan-Meier curve
-\begin{figure}[h!]
+\begin{figure}[!htbp]
   \includegraphics[scale=1]{kmcurve.pdf}
@@
 % Table of percentiles 
-\begin{table}[ht]
+\begin{table}[!h]
 \centering
@@
 % Univariate analysis on quantitative predictors
-\begin{table}[ht]
+\begin{table}[!htbp]
 \centering
@@
 % Univariate analysis on categorical predictors
-\begin{table}[ht]
+\begin{table}[!htbp]
 \centering
@@
 Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
-Results of univariate analyis, performed on one training set, for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
-All categorical predictors, as well as all continuous predictors marked with * were entered into the full model.
+Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+All categorical predictors and all continuous predictors marked with * were entered into the full model.
 
 % Splines
-\begin{table}[ht]
+\begin{table}[!htbp]
 \centering
@@
 
-Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model.
+Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Knots marked * were included in the final model.
 
 % Cross-validation metrics
-\begin{table}[ht]
+\begin{table}[!htbp]
 \centering
@@
   \hline
- & HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
+ & HR & LR & pval & R2 & Dxy & Concordance \\ 
   \hline
-  Training Sets & 2.0164 & 937.2018 & 0.0000 & 0.1401 & 64752.0898 & 0.2693 & 0.6346 \\ 
-  Test Sets & 1.9761 & 220.0417 & 0.0000 & 0.1401 & 13458.5808 & 0.2584 & 0.6292 \\
+  Training Sets & 2.0164 & 937.2018 & 0.0000 & 0.1401 & 0.2693 & 0.6346 \\ 
+  Test Sets & 1.9761 & 220.0417 & 0.0000 & 0.1401 & 0.2584 & 0.6292 \\
    \hline
@@
 % Final metrics for full data 
-\begin{table}[ht]
+\begin{table}[!htbp]
 \centering
@@
   \hline
-  HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
+  HR & LR & pval & R2 & Dxy & Concordance \\ 
   \hline
-  2.0010 & 1192.3234 & 0.0000 & 0.1424 & 83128.2780 & 0.2698 & 0.6349 \\ 
+  2.0010 & 1192.3234 & 0.0000 & 0.1424 & 0.2698 & 0.6349 \\ 
    \hline
@@
 % Final model on full data
-\begin{table}[ht]
+\begin{table}[!htbp]
 \centering
@@
 
-Score and deviance residuals of the final model identified outliers and highly influential questions, respectively.
-However, as refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data.
 Assessing the proportional hazards assumption indicated that several predictors were in violation.
 Final model statistics and parameter coefficients are in Table \ref{table:coefficients}.
-Metrics for the final model's performance on the full data, found in \ref{table:finalmetrics}, though considerably low, are not different from the metrics computed in cross-validation.
+Metrics for the final model's performance on the full data are found in \ref{table:finalmetrics}.
+The partial likelihood ratio and chi-square p-value indicate that the model as a whole is significantly associated with response time.
+However, the model's R^2 statistic is considerably low.
+Somers' Dxy and Concordance statistic are also low, and indicate low discriminative ability.
+Though metrics are low, metrics on the full data are not different from metrics computed in cross-validation, indicating that the model was not overfit.
 
-%----------------------------------------------------------------------------------------------------
-
-\section*{Discussion}
-
-(Discuss importance of findings, not repeat them. A combined results + discussion section is often appropriate) 
-The data we analyzed for this model presented some limitations.
-Currently, askers have a considerable amount of freedom in the way they ask a question.
-As a result many incorrectly specify various input fields.
-For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''.
-Generally, tags are not more than a couple key words that describe the topic of the question.
-Many users on this forum included lengthy and somewhat ambiguous tags in their question.
-Another issue was the incorrect naming of the device the user's question was about.
-A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One".
-The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributed to the model's low predictive accuracy.
+The data analyzed for this model presented limitations, and may explain the model's low predictive accuracy.
+Many users on the CQA incorrectly specified the device name in their question (e.g.
+``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
+Many users also incorrectly used the tagging system---including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please\!\!\!\!\!''(tags are generally a couple key words that describe the topic of the question).
+These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low R^2 and concordance statistics.
 
@@
 
-\section{Appendix}
+\section*{Appendix}
+
+<<>>=
+# answered question id = 397414
+index <- which(x$id == 397414)
+
+# unanswered question id = 399971
+index2 <- which(x$id == 399971)
+@
+%--------------------------------------------------
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
+  \hline
+ Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
+  \hline
+  iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago.
+Have done the whole rice thing and seen huge difference in it.
+However, only one side of my screen works and it is the one side which I need to unlock the phone.
+What would be the best way forward?
+& 1 & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\
+   \hline
+\end{tabular}
+\caption{Example of an answered question}
+\label{table:answered_q}
+\end{table}
+%--------------------------------------------------
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
+  \hline
+ Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
+  \hline
+  android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & 0 & 2017-05-23 07:35:12 GMT & NA & NA \\ 
+   \hline
+\end{tabular}
+\caption{Example of an unanswered question}
+\label{table:unanswered_q}
+\end{table}
+%--------------------------------------------------
 
@@
 Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
-Of all questions in the data, 1954 questions (25.2\%) contained missing values for this variable.
-Missing values were a result of users creating questions for devices not already in the website's database, or from the user incorrectly defining the device name.
-For questions with missing values, key words were searched for in device titles to recategorize accordingly.
-Remaining questions with ambiguous or completely missing device titles were categorized as ``Other''.
-The following modifications were made to the original variable: All Apple products (e.g., iPhones, iMacs, Apple watches) were categorized as ``Apple Product''.
-Remaining phones in the original ``Phones'' category were categorized as ``Android/Other Phone''.
-Appliance and Household categories of the original variable were merged into ``Home''.
-``Car and Truck'' were added to ``Vehicle''.
-Any category that contained less than 2\% of all questions were categorized as ``Other''.
-All other categories remained the same as the original variable.
-Final categories included: Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.
+Device titles were parsed and certain categories were combined or separated to create a new category variable.
+Categories in the final variable included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
+Under original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category.
+Missing values were a result of users creating questions for devices creating questions for devices not already in the website's database, or from the user incorrectly defining the device name.
+For questions with missing categories, key words were searched for in device titles to recategorize accordingly.
 
-Whether or not the question's title contains terms considered to be frequently used among unanswered/answered questions
+Whether or not the question's title contains terms considered to be frequently used among answered/unanswered questions
 
@@
 These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
-Similarly, certain topics might be unpopular.
-Thus, questions pertaining to those topics might receive answers slower (cite).
+Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do (cite).
 
-The data was separated between answered and unanswered questions.
-For the data frame containing answered questions, text mining techniques were used to create a list with every word within questions' titles and the frequency, or number of times they occurred among answered questions.
+To create the variables, the data was separated between answered and unanswered questions.
+For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the frequency, or proportion of times those words occurred among all answered questions' titles.
 The same was performed for the data frame containing unanswered questions.
-``Frequently-used'' words in answered questions were defined as those that appeared in more than 1\% of answered questions' titles, and appeared in more answered questions than in unanswered questions.
+``Frequently-used'' words in answered questions were defined as those that appeared in more than 1\% of all answered questions' titles, and appeared in more answered questions than in unanswered questions.
 To determine the latter, a ratio of frequencies, or proportions of times a word occurs, was assessed.
 The ratio was calculated as the proportion of time a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
-As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered frequently-used among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
-As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of unanswered question's titles and occur in more unanswered questions than answered questions.
-As there was some overlap between words in each list and the device categories, every word that matched a device name was removed from the lists.
+As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
+Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions.
+As there was some overlap between ``frequently-used'' words in each list and the device categories, every word that matched a device name was removed from the lists.
 The resulting list for answered questions contained 111 words.
@@
 
-``Frequently-used'' terms among answered questions (ordered by decreasing frequency): 
-screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top
-
-``Frequently-used'' terms among unanswered questions (ordered by decreasing frequency):
-sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit
+\begin{table}[!htbp]
+\centering
+\caption{Lists of ``frequently-used'' terms among answered and unanswered questions' titles, ordered by decreasing frequency}
+\begin{tabular}{|p{4cm}|p{8cm}|}
+  \hline
+ ``Frequently-used'' terms among answered questions & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
+  \hline
+  ``Frequently-used'' terms among unanswered questions & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\
+   \hline
+\end{tabular}
+\label{table:frequent_terms}
+\end{table}
 
@@
 
-This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving a faster answer.
+This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving an answer faster.
 This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
@@
 
+\bibliography{questions}
 \bibliographystyle{ECA_jasa}
-\bibliography{questions}
 

### 2017-12-29 article submission/draft1.tex
edited abstract, introduction, appendix

@@
 
-Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday.
-Forums can cover a broad range of topics, like \textit{Yahoo!
-Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}.
-An example of the latter is iFixit's \textit{Answers} forum.
-The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices.
-As such, it is important that questions receive timely answers.
-This paper presents a survival analysis on the time until a question receives its first answer.
-We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time.
-Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$).
-Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
-Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.
+Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge.
+Thousands of questions and answers are posted everyday.
+One such example of a CQA is iFixit's \textit{Answers} forum.
+This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users.
+A reliable measure of the health of these CQAs is question response time.
+Fast response times enhance user engagement and satisfaction, and increase web traffic.
+This paper presents a survival analysis of response time, or the time until a question receives its first answer.
+A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
+Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).
+Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
+Future studies can investigate if factors identified as signifcant can be generalized to other CQAs.
 
@@
 Each training set contained 6208 questions, and each test set contained 1552 questions.
-Results of univariate analyis, performed on one training set, for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
-All categorical predictors, as well as all continuous predictors marked with * were entered into the full model.
+Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+All categorical predictors and all continuous predictors marked with * were entered into the full model.
 
 % Splines
-\begin{table}[ht]
+\begin{table}[!htbp]
 \centering
@@
 
-\section{Appendix}
+\section*{Appendix}
+
+\begin{Schunk}
+\begin{Sinput}
+> # answered question id = 397414
+> index <- which(x$id == 397414)
+> # unanswered question id = 399971
+> index2 <- which(x$id == 399971)
+\end{Sinput}
+\end{Schunk}
+%--------------------------------------------------
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
+  \hline
+ Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
+  \hline
+  iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago.
+Have done the whole rice thing and seen huge difference in it.
+However, only one side of my screen works and it is the one side which I need to unlock the phone.
+What would be the best way forward?
+& 1 & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\
+   \hline
+\end{tabular}
+\caption{Example of an answered question}
+\label{table:answered_q}
+\end{table}
+%--------------------------------------------------
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
+  \hline
+ Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
+  \hline
+  android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & 0 & 2017-05-23 07:35:12 GMT & NA & NA \\ 
+   \hline
+\end{tabular}
+\caption{Example of an unanswered question}
+\label{table:unanswered_q}
+\end{table}
+%--------------------------------------------------
 

### 2018-01-02 article/draft1.Rnw
added new file

--- 2017-12-29 article submission/draft1.Rnw
@@
 Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
-Future studies can investigate if factors identified as signifcant can be generalized to other CQAs.
+Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.
 
-%----------------------------------------------------------------------------------------------------
+%===================================================================================================
+%===================================================================================================
 
@@
 Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum.
-Analysis of response times can reveal factors that affect how quickly questions receive answered, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.
+Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.
+
 However, analysis and prediction of response times on CQAs have not been thoroughly investigated.
-As the majority of existing research focuses on assessing and predicting question and answer quality, there is need for further analysis of response times in these forums.
+There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality.
 This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.
 
-%----------------------------------------------------------------------------------------------------
+%===================================================================================================
+%===================================================================================================
 
@@
 
-In regards to investigation of forum response times \cite{Bhat2014} developed a classification model to analyze response times of questions posted on \textit{Stack Overflow}, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.
+With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies related to information sciences.
+Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow}, using both tag-based and textual features.
+Analysis determine that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors of response time.
+\cite{Mahmud} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses.
+\cite{Rechavi2011} analyzed response times and satisfaction rates for questions posted on \textit{Yahoo Answers!}, and determined that the fastest times were between users who did not follow each other, while the longest times were between users who were mutual friends in the social network.
+\cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length and whether or not the question contained code, and user features, like the number of questions asked and answered by the user prior to posting.
+The analysis presented in this paper seeks to analyze response time through survival analysis methods, methods that have not yet been investigated or applied to CQAs.
 
-\cite{Mamykina2011} found that the swift answer times of \textit{Stack Overflow's} community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.
+The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts.
+\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features (surface, lexical, syntactic, forum-specific, and similarity (relatedness of a post to the topic of the forum) features).
+\cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality.
+Wikipedia articles can represent the same kind of user-generated content featured on CQAs.
+On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}.
+A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question and answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a}.
+\cite{Ravi2014} presented a slightly different approach by analyzing the content of posts and utilizing latent topic models to predict quality.
+\cite{Anderson2012} developed models to the long term value of a question and its answers on \textit{Stack Overflow}.
+The present analysis combines both textual and non-textual features of questions on iFixit's \textit{Answers} forum in a Cox regression model to predict survival probability of questions.
 
-\cite{Asaduzzaman2013} analyzed unanswered questions on \textit{Stack Overflow} to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.
-
-%----------------------------------------------------------------------------------------------------
+%===================================================================================================
+%===================================================================================================
 
@@
 
-good question ex: id 408124, 406786 (answered)
-bad question ex: id 410310, 405882 (unanswered)
+% Table of categorical predictors
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{|p{10cm}|}
+  \hline
+  Day of the week the question was posted \\ \hline
+  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
+  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
+  Whether or not the question's text is in all lower case \\ \hline
+  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. \\ \hline
+  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. \\ \hline
+  Whether or not the question's title ends in a question mark \\ \hline
+  Whether or not the user edited or added information to the question's text sometime after posting it \\ \hline
+  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
+\end{tabular}
+\caption{Categorical predictors derived}
+\label{table:categorical}
+\end{table}
+
+% Table of quantitative predictors
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{|p{10cm}|}
+  \hline
+  Average number of characters in each question's tags\\ \hline
+  Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. \\ \hline
+  Number of characters in the question's text \\ \hline
+  Number of characters in the user-defined device name \\ \hline
+  Ratio of the number of line breaks to the number of characters in the question's text \\ \hline
+\end{tabular}
+\caption{Continuous predictors derived}
+\label{table:continuous}
+\end{table}
 
 The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded).
-Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date the question was posted, and date the first answer was received.
-Variables derived:
+Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time when the question was posted, and date and time when the first answer was received.
+Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}.
+See appendix for information on how predictors were created.
 
-Categorical Variables:
-
-\begin{itemize}
-  \item Day of the week the question was posted. 
-  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle
-  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
-  \item Whether or not the question's text is in all lower case. 
-  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. 
-  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. 
-  \item Whether or not the question's title ends in a question mark.
-  \item Whether or not the user edited or added information to the question's text sometime after posting it.
-  \item Whether or not the user made an effort to solve the problem on their own, prior to asking the question.
-\end{itemize}
-
-Numeric Variables:
-
-\begin{itemize}
-  \item Average number of characters in each question's tags. 
-  \item Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. 
-  \item Number of characters in the question's text. 
-  \item Number of characters in the user-defined device name. 
-  \item Ratio of the number of line breaks to the number of characters in the question's text.
-\end{itemize}
-
-%----------------------------------------------------------------------------------------------------
+%===================================================================================================
+%===================================================================================================
 
@@
 Questions analyzed were restricted to those posted in English.
-Time until event was defined as the time since posting until a question received its first answer.
+The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
@@
 
-As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions (Cox models are not based on an assumption of the shape of the underlying probability distribution) \cite{Moore2010}.
-To build the model, five-fold cross-validation was used.
-The full data was split into five training sets and five test sets \cite{Rodriguez2010}.
+As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}.
+To build the model, five-fold cross-validation was used \cite{Rodriguez2010}.
 Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
-Each continuous predictor, with and without log and square root transformations, as well as each categorical predictor, was entereed into univarite Cox models, and strength of association with response times was assessed.
+Each predictor was entered into univarite Cox models, and strength of association with response times was assessed.
 Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model.
+Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include into the final model.
 Univariate analysis was again performed on each continuous predictor to investigate the use of splines.
 Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine whether or not to include restricted cubic splines for a predictor, as well as the optimum number of knots \cite{Harrell2015}.
+AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}.
 All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation.
-No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model harmed predictive accuracy, more so than leaving all predictors in.
+No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than leaving all predictors in.
 
@@
 
-To convert the final model's predicted hazard ratios to predicted survival probability, an r function was used.
+To obtain predicted survival probabilities using the model, the predictSurvProb function was used from the pec package.
+This function uses the Cox model and a vector of times to compute predicted survival probabilities.
 
-%----------------------------------------------------------------------------------------------------
+%===================================================================================================
+%===================================================================================================
 
-\section*{Results}
+\section*{Results and Discussion}
 
@@
   \includegraphics[scale=1]{times_dist.pdf}
-  \caption{Distribution of answer times}
+  \caption{Distribution of response times}
   \label{fig:answertimes}
@@
 Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
-The shortest answer time was \Sexpr{shortest} hours.
+The shortest response time was \Sexpr{shortest} hours.
 The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
-Figure ~\ref{fig:answertimes} shows that the distribution of answer times for all questions is extremely right-skewed.
+Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
 
@@
 \end{tabular}
-\caption{Table of Kaplan-Meier estimated quantiles of survival time}
+\caption{Kaplan-Meier estimated quantiles of survival time}
 \label{table:quantiles}
@@
 \centering
-\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
+\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
 \begin{tabular}{|p{12cm}|p{2cm}|}
@@
   \hline \hline
-  *Log transformation of the number of characters in a question's text & 0.00 \\ 
-  \hline
-  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ 
-  \hline
-  Number of characters in a question's text (untransformed) & 6.9472e-12 \\
-  \hline
-  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ 
-  \hline
-  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ 
-  \hline
-  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ 
-  \hline
-  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ 
-  \hline
-  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ 
-  \hline
-  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ 
-  \hline
-  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ 
-  \hline
-  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ 
-   \hline
+  *Log transformation of the number of characters in a question's text & 0.00 \\ \hline
+  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ \hline
+  Number of characters in a question's text (untransformed) & 6.9472e-12 \\\hline
+  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ \hline
+  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ \hline
+  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ \hline
+  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ \hline
+  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ \hline
+  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ \hline
+  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ \hline
+  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ \hline
 \end{tabular}
@@
   \hline \hline
-  Device category & 0.00 \\
-  \hline
-  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
-  \hline
-  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
-  \hline
-  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ 
-  \hline
-  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ 
-  \hline
-  Whether or not the question's text is in all lower case & 1.5400e-7 \\ 
-  \hline
-  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ 
-  \hline
-  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\
-  \hline
-  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ 
-  \hline
-  Day of the week the question was posted & 7.8677e-4 \\ 
-   \hline
+  Day of the week the question was posted & 7.8677e-4 \\ \hline
+  Device category & 0.00 \\ \hline
+  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ \hline
+  Whether or not the question's text is in all lower case & 1.5400e-7 \\ \hline
+  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ \hline
+  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ \hline
+  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ \hline
+  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ \hline
+  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ \hline
+  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\ \hline
+
 \end{tabular}
 \label{table:cresults}
+\end{table}
+
+% Univariate analysis on quantitative predictors
+\begin{table}[!htbp]
+\centering
+\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
+\begin{tabular}{| p{5cm} | l | l |}
+  \hline
+  Predictor & Transformation & p-value \\ 
+  \hline
+  \multirow{3}{5cm}{Average number of characters in each questions tags}
+  & Untransformed & 2.6115e-2 \\ 
+  & Log & NA \\
+  & Square root & 2.9999e-4 \\ \hline
+  \multirow{3}{5cm}{Average frequency score of a question’s tags}
+  & Untransformed & 1.2706e-08 \\
+  & Log & NA \\
+  & Square root & 1.4642e-11 \\ \hline
+  \multirow{3}{5cm}{Number of characters in a question's text}
+  & Untransformed & 6.9472e-12 \\
+  & Log & 0.00 \\
+  & Square root & 1.1102e-16 \\ \hline
+  \multirow{3}{5cm}{Number of characters in the user-defined device title}
+  & Untransformed & 6.5304e-3 \\
+  & Log & NA \\
+  & Square root & 2.2914e-4 \\ \hline
+  \multirow{3}{5cm}{Ratio of the number of line breaks to the number of characters in a question's text} 
+  & Untransformed & 1.3988e-7 \\
+  & Log & NA \\
+  & Square root & 1.1488e-11 \\ \hline
+\end{tabular}
+\label{table:qresults}
 \end{table}
@@
 Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
-All categorical predictors and all continuous predictors marked with * were entered into the full model.
+All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
 
@@
 
-Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Knots marked * were included in the final model.
+Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Values of knots marked with an asterisk (*) were included in the final model.
 
@@
 
-Average performance metrics for test and training sets, found in Table \ref{table:cv}, were considerably low.
-However, metrics did not change substantially from training to test sets, indicating that the model does not overfit.
-The final model, with all variables described above including splines, was fit to the full data.
+Average performance metrics for test and training sets and in Table \ref{table:cv}.
+Partial likelihood ratio statistics and p-values indicate that the model as a whole is signficantly associated with response time.
+However, its R^2 statistic and discrimination indexes are considerably low.
+Metrics did not change significantly from training to test sets, indicating that the model was not overfit.
 
@@
 
-Assessing the proportional hazards assumption indicated that several predictors were in violation.
+Assessing the proportional hazards assumption indicated that several predictors were in violation, results can be found in Table \ref{table:ph_assumption}.
 Final model statistics and parameter coefficients are in Table \ref{table:coefficients}.
-Metrics for the final model's performance on the full data are found in \ref{table:finalmetrics}.
-The partial likelihood ratio and chi-square p-value indicate that the model as a whole is significantly associated with response time.
-However, the model's R^2 statistic is considerably low.
-Somers' Dxy and Concordance statistic are also low, and indicate low discriminative ability.
-Though metrics are low, metrics on the full data are not different from metrics computed in cross-validation, indicating that the model was not overfit.
+Metrics for the final model's performance on the full data are found in \ref{table:finalmetrics}, and are consistent with the metrics found in cross validation---the model as a whole is significantly associated with response time, but has a low $R^2$ statistic and indicates low discriminative ability.
+Individual predictors found to be significant (alpha = 0.001) are: device category, whether or not the question's text contains ``frequently-used'' terms among unanswered questions, whether or not the questions title ends in a questionmark, whether or not the user updated the question after posting it.
 
@@
 ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
-Many users also incorrectly used the tagging system---including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please\!\!\!\!\!''(tags are generally a couple key words that describe the topic of the question).
-These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low R^2 and concordance statistics.
+Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!''(tags are generally a couple key words that describe the topic of the question).
+These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low R^2 and discrimination indexes.
 
-%----------------------------------------------------------------------------------------------------
+Future studies can further investigate if the predictors found to be significant in this study can be generalized to other CQAs.
+
+%===================================================================================================
+%===================================================================================================
 
@@
 This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, whether or not the user updated the question's text after the initial posting, whether or not the user indicated that he or she made an effort prior to answer their question prior to posting it (how should I write out that different knots of the splines were signficant).
+Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, and whether or not the user updated the question's text after the initial posting.
 While overall the model was signficant, its predictive performance was considerably low.
 
-%----------------------------------------------------------------------------------------------------
+%===================================================================================================
+%===================================================================================================
 
@@
 
-%----------------------------------------------------------------------------------------------------
+%===================================================================================================
+%===================================================================================================
 
@@
 
-<<>>=
+<< echo = FALSE >>=
 # answered question id = 397414
@@
 @
-%--------------------------------------------------
+
+% Table to display an answered question---------------------------------
 \begin{table}[!htbp]
@@
 \end{table}
-%--------------------------------------------------
+
+% Table to display an unanswered question-------------------------------
 \begin{table}[!htbp]
@@
 \end{table}
-%--------------------------------------------------
+%-----------------------------------------------------------------------
 
@@
 
-Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
-Device titles were parsed and certain categories were combined or separated to create a new category variable.
+\begin{itemize}
+  \item Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+Device titles were parsed and certain categories were combined or separated to create a new device categorization.
 Categories in the final variable included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
 Under original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category.
-Missing values were a result of users creating questions for devices creating questions for devices not already in the website's database, or from the user incorrectly defining the device name.
+Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.
 For questions with missing categories, key words were searched for in device titles to recategorize accordingly.
+\end{itemize}
+
+%-----------------------------------------------------------------------
 
@@
 
-Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively.
-
-These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
-Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do (cite).
-
-To create the variables, the data was separated between answered and unanswered questions.
+\begin{itemize}
+  \item Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively. 
+  \item These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
+Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do not (cite).
+  \item To create the variables, the data was separated between answered and unanswered questions.
 For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the frequency, or proportion of times those words occurred among all answered questions' titles.
@@
 The list for unanswered questions contained 32 words.
+Lists can be found in Table \ref{table:frequent_terms}
+\end{itemize}
 
+%--------Table with list of frequently used words------------------------
 \begin{table}[!htbp]
@@
 
+%-----------------------------------------------------------------------
+
 Whether or not the question's title ended in a questionmark
 
-A logical variable indicating true if the question's title ends in a questionmark.
-This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.
+\begin{itemize}
+  \item This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.
+\end{itemize}
+
+%-----------------------------------------------------------------------
 
@@
 
-A logical variable indicating true if the question’s text contains any end punctuation marks (``.'', ``?'', ``!'').
-This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.
+\begin{itemize}
+  \item This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer. 
+\end{itemize}
+
+%-----------------------------------------------------------------------
 
@@
 
-Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g.
+\begin{itemize}
+  \item Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g.
 ``tried'', ``attempted'', ``tested'').
 This variable was created based off of findings from \cite{Bhat2014}.
+\end{itemize}
+
+%-----------------------------------------------------------------------
 
@@
 
-This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving an answer faster.
+\begin{itemize}
+  \item This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving an answer faster.
 This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
@@
 This variable was created based off of findings from \cite{Bhat2014}.
+\end{itemize}
+
+%-----------------------------------------------------------------------
 
@@
 
-This variable was included to capture when a user incorrectly defines the device name.
+\begin{itemize}
+  \item This variable was included to capture when a user incorrectly defines the device name.
 For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”, and is 136 characters long.
@@
 This variable was created based on the intuition that users who incorrectly define their devices, or do not include any device title, make it difficult for the answering community to discern the question's topic, and thus have longer answer times or remain unanswered.
+\end{itemize}
+
+%-----------------------------------------------------------------------
 
@@
 
-This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
+\begin{itemize}
+  \item This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
 For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters.
@@
 It is hypothesized that users who correctly define tags, as with the latter user, receive answers quicker than the former.
+\end{itemize}
+
+%-----------------------------------------------------------------------
 
@@
 
-This variable was based on the hypothesis that question's that include line breaks in the text are generally easier to read than questions that don't include any, and thus have faster answer times.
+\begin{itemize}
+  \item This variable was based on the hypothesis that question's that include line breaks in the text are generally easier to read than questions that don't include any, and thus have faster answer times.
+\end{itemize}
 

### 2018-01-02 article/draft1.tex
added new file

--- 2018-01-02 article/draft1.Rnw
@@
 \usepackage{multirow}
+\usepackage{Sweave}
 \begin{document}
-\SweaveOpts{concordance=TRUE}
-
-<< echo = FALSE >>=
-# importing data 
-dir <- file.path(getwd(),"data")
-x <- read.csv(file.path(dir, "dat.csv"))
-
-model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)
-@
+\input{draft1-concordance}
 
@@
 A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
-Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
+Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).
 Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
@@
 
-<< echo = FALSE >>=
-# for inline code 
-answered <- sum(x$answered)
-percentans <- round((answered / nrow(x)) * 100, 1) 
-shortest <- round(min(x$time_until_answer) * 60, 2) 
-longest <- round(max(x$time_until_answer), 2)
-longest_d <- round(longest / 24, 2) 
-@
-
 % Distribution of answer times
@@
 
-  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data).
-Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
-The shortest response time was \Sexpr{shortest} hours.
-The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
+  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data).
+Of those questions, 4951 (63.8}\%) received an answer by the download date.
+The shortest response time was 0.5 hours.
+The longest was 2159.02 hours (89.96 days).
 Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
-
-<< echo = FALSE >>=
-# Kaplan-Meier survival estimates
-surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
-KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
-
-stats <- summary(KM)$table
-mean <- round(unname(stats[5]), 2) 
-median <- round(unname(stats[7]), 2)
-@
 
@@
 The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
-The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days.
-The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.
+The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
 Table \ref{table:quantiles} provides additional percentiles of survival time.
@@
 
-<< echo = FALSE >>=
-set.seed(444)
-splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
-
-train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
-train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
-train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
-train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
-train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
-@
-
-Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
+Each training set contained 6208 questions, and each test set contained 1552 questions.
 Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
@@
 
-<< echo = FALSE >>=
-# answered question id = 397414
-index <- which(x$id == 397414)
-
-# unanswered question id = 399971
-index2 <- which(x$id == 399971)
-@
-
 % Table to display an answered question---------------------------------

### 2018-01-02 article/graphics.Rmd
added new file

--- 2017-12-15 article submission/graphics.Rmd
@@
 
-### Distribution of answer times (Figure 1)
+### Distribution of answer times
 
 ```{r}
-# x$Answered <- NA
-# x$Answered[x$answered == 1] <- "Answered"
-# x$Answered[x$answered == 0] <- "Unanswered"
+x$Answered <- NA
+x$Answered[x$answered == 1] <- "Answered"
+x$Answered[x$answered == 0] <- "Unanswered"
 
@@
   scale_x_continuous("Time (hrs)") + 
-  scale_y_continuous("Number of Questions")
+  scale_y_continuous("Number of Questions") + 
+  theme(text = element_text(size = 25),
+        axis.text = element_text(size = 15))
 
@@
 
-### KM Curve (Figure 2)
+### KM Curve
 
@@
 KM <- survfit(surv_object ~ 1, conf.type = "log-log")
-
+library(survminer)
 # dashed line indicates the median survival time
@@
            tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE,
-           legend = "none")
+           legend = "none",
+           font.x = 25, font.y = 25, font.tickslab = 15)
 
@@
 
-### Table of percentiles (Table 1)
+### Table of percentiles
 
@@
 tests <- purrr::map(tests, ~as.data.frame(.))
-
 # ---------------------------------------------------------------------------------------
@@
                    pvalue = unname(model$stats[5]))
+  df <- df %>% arrange(pvalue)
   return(df)
 }
-# ---------------------------------------------------------------------------------------
+```
+
+```{r}
 # categorical predictors 
@@
 
-dev_length <- list("device_length", "sqrt(device_length)") # log10 does not work 
+dev_length <- list("device_length", "sqrt(device_length)", "log10(device_length + 1)") 
 dev_pvalue <- purrr::map_dfr(dev_length, ~get_pvalue(.))
 
-newline <- list("newline_ratio", "sqrt(newline_ratio)") #log10 doens't work
+newline <- list("newline_ratio", "sqrt(newline_ratio)", "log10(newline_ratio + 1)")
 newline_pvalue <- purrr::map_dfr(newline, ~get_pvalue(.))
 
-tag_length <- list("avg_tag_length", "sqrt(avg_tag_length)")
+tag_length <- list("avg_tag_length", "sqrt(avg_tag_length)", "log10(avg_tag_length + 1)")
 taglength_pvalue <- purrr::map_dfr(tag_length, ~get_pvalue(.))
 
-tag_score <- list("avg_tag_score", "sqrt(avg_tag_score)")
+tag_score <- list("avg_tag_score", "sqrt(avg_tag_score)", "log10(avg_tag_score + 1)")
 tagscore_pvalue <- purrr::map_dfr(tag_score, ~get_pvalue(.))
@@
 
+vars2 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + log10(avg_tag_score + 1) + rcs(log10(text_length), 5) + rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + rcs(log10(newline_ratio + 1), 3)"
+
 cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
+cv_results2 <- purrr::map2(trains, tests, ~crossval(vars2, .x, .y))
+avg_results2 <- get_avgmetrics(cv_results2)
+avg_results2
 avg_results1 <- get_avgmetrics(cv_results1)
@@
 xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv", digits = 4)
+```
+
+```{r}
+avg_results2
 ```

### 2018-01-03 article/draft1.Rnw
combined univariate results tables

@@
 A reliable measure of the health of these CQAs is question response time.
-Fast response times enhance user engagement and satisfaction, and increase web traffic.
-This paper presents a survival analysis of response time, or the time until a question receives its first answer.
+Fast response times enhance user engagement and satisfaction and increase web traffic.
+This paper presents a survival analysis of the time until a question receives its first answer.
 A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
-Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
 Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.
@@
 Community-driven online question and answer forums (CQA) are becoming widely-used sources of information.
-These online platforms feature thousands of user-posted questions and answers, and can receive millions of visits every month.
+These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month.
 The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
@@
 
-As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is another important resource.
+As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users.
 This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions.
@@
 Analysis determine that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors of response time.
-\cite{Mahmud} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses.
-\cite{Rechavi2011} analyzed response times and satisfaction rates for questions posted on \textit{Yahoo Answers!}, and determined that the fastest times were between users who did not follow each other, while the longest times were between users who were mutual friends in the social network.
-\cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length and whether or not the question contained code, and user features, like the number of questions asked and answered by the user prior to posting.
-The analysis presented in this paper seeks to analyze response time through survival analysis methods, methods that have not yet been investigated or applied to CQAs.
+\cite{Mahmud2013} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses.
+Both \cite{Bhat2014} and \cite{Mahmud2013} restrict analysis to questions for which the response time is observed, ignoring unanswered questions; meanwhile \cite{Asaduzzaman2013} focused exclusively on characteristics of unanswered questions.
+\cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length, and user features like the number of questions asked and answered by the user prior to posting.
+The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
 
@@
 \cite{Ravi2014} presented a slightly different approach by analyzing the content of posts and utilizing latent topic models to predict quality.
-\cite{Anderson2012} developed models to the long term value of a question and its answers on \textit{Stack Overflow}.
+\cite{Anderson2012} developed models to the predict the long term value of a question and its answers on \textit{Stack Overflow}.
 The present analysis combines both textual and non-textual features of questions on iFixit's \textit{Answers} forum in a Cox regression model to predict survival probability of questions.
@@
   Whether or not the question's text is in all lower case \\ \hline
-  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. \\ \hline
-  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. \\ \hline
+  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See Appendix for a complete list of these terms. \\ \hline
+  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See Appendix for a complete list of these terms. \\ \hline
   Whether or not the question's title ends in a question mark \\ \hline
-  Whether or not the user edited or added information to the question's text sometime after posting it \\ \hline
-  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
+  Whether or not the user edited or added information to the question's text sometime after posting it. \\ \hline
+  Whether or not the user made an effort to solve the problem prior to asking the question. \\ \hline
 \end{tabular}
@@
 
-The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded).
+The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded).
 Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time when the question was posted, and date and time when the first answer was received.
 Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}.
-See appendix for information on how predictors were created.
+See Appendix for more details on variable derivation.
 
@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \cite{Kleinbaum2011}.
+Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.
 
-Survival was defined as the event that a question did not receive an answer beyond a certain time, t.
+Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}.
 Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}.
@@
 All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation.
-No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than leaving all predictors in.
+No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.
 
@@
 To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
-The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' Dxy, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
+The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
 Signficant results from this model would indicate high predictive accuracy.
 The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
-The p-value for this statistic was calculated from the X2 distribution \cite{find}.
-Concordance statistics and Somers' Dxy are a measure of the model's discriminative ability.
+The p-value for this statistic was calculated from the $Ichi^2$ distribution \cite{find}.
+Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability.
 Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio.
 Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
-Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5.
-A Somers' Dxy statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}.
+Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5.
+A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}.
 These metrics were computed for each iteration on every training and test set.
@@
 
-To obtain predicted survival probabilities using the model, the predictSurvProb function was used from the pec package.
+To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package.
 This function uses the Cox model and a vector of times to compute predicted survival probabilities.
@@
 
-% Univariate analysis on quantitative predictors
+% Univariate analysis results
 \begin{table}[!htbp]
@@
 \caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
-\begin{tabular}{|p{12cm}|p{2cm}|}
-  \hline
-  Predictor & p-value \\ 
-  \hline \hline
-  *Log transformation of the number of characters in a question's text & 0.00 \\ \hline
-  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ \hline
-  Number of characters in a question's text (untransformed) & 6.9472e-12 \\\hline
-  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ \hline
-  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ \hline
-  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ \hline
-  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ \hline
-  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ \hline
-  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ \hline
-  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ \hline
-  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ \hline
-\end{tabular}
-\label{table:qresults}
-\end{table}
-
-% Univariate analysis on categorical predictors
-\begin{table}[!htbp]
-\centering
-\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
-\begin{tabular}{|p{12cm}|p{2cm}|}
-  \hline
- Predictor & p-value \\ 
-  \hline \hline
-  Day of the week the question was posted & 7.8677e-4 \\ \hline
-  Device category & 0.00 \\ \hline
-  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ \hline
-  Whether or not the question's text is in all lower case & 1.5400e-7 \\ \hline
-  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ \hline
-  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ \hline
-  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ \hline
-  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ \hline
-  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ \hline
-  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\ \hline
-
-\end{tabular}
-\label{table:cresults}
-\end{table}
-
-% Univariate analysis on quantitative predictors
-\begin{table}[!htbp]
-\centering
-\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
-\begin{tabular}{| p{5cm} | l | l |}
+\begin{tabular}{| p{5cm} | p{2.5cm} | p{2cm} |}
   \hline
@@
   \hline
-  \multirow{3}{5cm}{Average number of characters in each questions tags}
-  & Untransformed & 2.6115e-2 \\ 
-  & Log & NA \\
-  & Square root & 2.9999e-4 \\ \hline
-  \multirow{3}{5cm}{Average frequency score of a question’s tags}
-  & Untransformed & 1.2706e-08 \\
-  & Log & NA \\
-  & Square root & 1.4642e-11 \\ \hline
-  \multirow{3}{5cm}{Number of characters in a question's text}
-  & Untransformed & 6.9472e-12 \\
-  & Log & 0.00 \\
-  & Square root & 1.1102e-16 \\ \hline
-  \multirow{3}{5cm}{Number of characters in the user-defined device title}
-  & Untransformed & 6.5304e-3 \\
-  & Log & NA \\
-  & Square root & 2.2914e-4 \\ \hline
-  \multirow{3}{5cm}{Ratio of the number of line breaks to the number of characters in a question's text} 
-  & Untransformed & 1.3988e-7 \\
-  & Log & NA \\
-  & Square root & 1.1488e-11 \\ \hline
+  \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
+  & Untransformed & 1.270620e-08 \\
+  & Log + 1 & 1.186521e-08 \\
+  & *Square root & 1.464184e-11 \\ \hline
+  \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
+  & Untransformed & 2.611529e-02 \\ 
+  & *Log + 1 & 6.018542e-05 \\
+  & Square root & 2.999917e-04 \\ \hline
+  \multirow{ 3 }{ 5cm }{ Number of characters in a question's text }
+  & Untransformed & 6.947221e-12 \\
+  & *Log & 0.000000e+00 \\
+  & Square root & 1.110223e-16 \\ \hline
+  \multirow{ 3 }{ 5cm }{ Number of characters in the user-defined device title }
+  & Untransformed & 6.530431e-03 \\
+  & *Log + 1 & 1.912977e-05 \\
+  & Square root & 2.291424e-04 \\ \hline
+  \multirow{ 3 }{ 5cm }{ Ratio of the number of line breaks to the number of characters in a question's text } 
+  & Untransformed & 1.398819e-07 \\
+  & Log + 1 & 1.092952e-07 \\
+  & *Square root & 1.148792e-11 \\ \hline
+  \multicolumn{ 2 }{ |l| }{ *Day of the week the question was posted } & 7.867705e-04 \\ \hline
+  \multicolumn{ 2 }{ |l| }{ *Device category } & 0.000000e+00 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
+  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
+  \multicolumn{2}{| p{7.5cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
+  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
+  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
+  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
+  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
 \end{tabular}
-\label{table:qresults}
+\label{table:univariate_results}
 \end{table}
@@
 Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
-Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}.
 All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

### 2018-01-03 article/draft1.tex
combined univariate results tables

@@
 A reliable measure of the health of these CQAs is question response time.
-Fast response times enhance user engagement and satisfaction, and increase web traffic.
-This paper presents a survival analysis of response time, or the time until a question receives its first answer.
+Fast response times enhance user engagement and satisfaction and increase web traffic.
+This paper presents a survival analysis of the time until a question receives its first answer.
 A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).
-Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
 Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.
@@
 Each training set contained 6208 questions, and each test set contained 1552 questions.
-Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively.
+Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}.
 All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

### 2018-01-03 article/draft1.Rnw
reformatted tables + appendix

@@
 Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}.
+As several continuous predictors contained zeros as values, the log transformation was applied after adding one.
 All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
@@
 \centering
-\caption{Determining the optimal k number of splines for each predictor} 
 \begin{tabular}{| p{5cm} | l | l |}
@@
   \hline
-  \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
+  \multirow{ 4 }{ 5cm }{ Log transformation of the number of characters in a question's text } 
   & 0 & 65862.83 \\ 
-  & 5* & 65862.02 \\ 
+  & *5 & 65862.02 \\ 
   & 4 & 65863.35 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
+  \multirow{ 4 }{ 5 cm }{ Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text }
   & 0 & 65890.28 \\ 
@@
   & 4 & 65882.98 \\ 
-  & 3* & 65881.93 \\ 
+  & *3 & 65881.93 \\ 
   \hline
-  \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
-  & 0* & 65890.75 \\ 
+  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average frequency ``score'' of a question's tags }
+  & *0 & 65890.75 \\ 
   & 5 & 65891.69 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
-  & 0 & 65922.76 \\ 
-  & 5* & 65853.56 \\ 
-  & 4 & 65882.07 \\ 
-  & 3 & 65881.39 \\ 
+  \multirow{ 4 }{ 5 cm }{ Log transformation of the number of characters in the user-defined device title + 1 }
+  & 0 & 65918.06 \\ 
+  & *5 & 65847.34 \\ 
+  & 4 & 65880.89 \\ 
+  & 3 & 65898.00 \\ 
   \hline
-  \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
-  & 0 & 65923.26 \\ 
-  & 5 & 65912.11 \\ 
-  & 4* & 65910.10 \\ 
-  & 3 & 65912.38 \\ 
+  \multirow{ 4 }{ 5 cm }{ Log transformation of the average number of characters in a question's tags + 1 }
+  & 0 & 65920.24 \\ 
+  & 5 & 65911.20 \\ 
+  & *4 & 65910.81 \\ 
+  & 3 & 65914.98 \\ 
    \hline
 \end{tabular}
+\caption{Determining the optimal k number of splines for each predictor} 
 \label{table:splines}
@@
 \centering
-\caption{Average performance metrics for training and test sets} 
-\begin{tabular}{rrrrrrrr}
+\begin{tabular}{| r | r | r | r | r  | r | r | r |}
   \hline
- & HR & LR & pval & R2 & Dxy & Concordance \\ 
+ & HR & LR & p-value & $R^2$ & \textit{Dxy} & Concordance \\ 
   \hline
-  Training Sets & 2.0164 & 937.2018 & 0.0000 & 0.1401 & 0.2693 & 0.6346 \\ 
-  Test Sets & 1.9761 & 220.0417 & 0.0000 & 0.1401 & 0.2584 & 0.6292 \\
+  Training Sets & 2.015619 & 936.6705 & 0.0000 & 0.1400518 & 0.2691182 & 0.6345591 \\ 
+  Test Sets & 1.975100 & 219.8065 & 0.0000 & 0.1400518 & 0.2579717 & 0.6289859 \\
+  Full Data & 2.01843 & 1164.784 & 0.0000 & 0.1393817 & 0.2680962 & 0.6340481 \\ 
    \hline
 \end{tabular}
+\caption{Performance Metrics} 
 \label{table:cv}
-\end{table}
-
-% Final metrics for full data 
-\begin{table}[!htbp]
-\centering
-\caption{Performance metrics for model fit to the full data} 
-\begin{tabular}{rrrrrrrr}
-  \hline
-  HR & LR & pval & R2 & Dxy & Concordance \\ 
-  \hline
-  2.0010 & 1192.3234 & 0.0000 & 0.1424 & 0.2698 & 0.6349 \\ 
-   \hline
-\end{tabular}
-\label{table:finalmetrics}
 \end{table}
@@
 Partial likelihood ratio statistics and p-values indicate that the model as a whole is signficantly associated with response time.
-However, its R^2 statistic and discrimination indexes are considerably low.
+However, its $R^2$ statistic and discrimination indexes are considerably low.
 Metrics did not change significantly from training to test sets, indicating that the model was not overfit.
+Metrics for the final model's performance on the full data, also found in \ref{table:cv}, are consistent with metrics found in cross validation.
 
@@
 Final model statistics and parameter coefficients are in Table \ref{table:coefficients}.
-Metrics for the final model's performance on the full data are found in \ref{table:finalmetrics}, and are consistent with the metrics found in cross validation---the model as a whole is significantly associated with response time, but has a low $R^2$ statistic and indicates low discriminative ability.
 Individual predictors found to be significant (alpha = 0.001) are: device category, whether or not the question's text contains ``frequently-used'' terms among unanswered questions, whether or not the questions title ends in a questionmark, whether or not the user updated the question after posting it.
+
+%===================================================================================================
+%===================================================================================================
+
+\section*{Conclusion}
+
+This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
+Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, and whether or not the user updated the question's text after the initial posting.
+While overall the model was signficant, its predictive performance was considerably low.
 
@@
 
-\section*{Conclusion}
-
-This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, and whether or not the user updated the question's text after the initial posting.
-While overall the model was signficant, its predictive performance was considerably low.
-
-%===================================================================================================
-%===================================================================================================
-
 \section*{Acknowledgement}
 
-This research is supported by the Bill and Linda Frost fund.
+This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
+Special thanks also goes to iFixit for providing access to the data and for all the help and assistance in its analysis.
 
@@
 
-<< echo = FALSE >>=
-# answered question id = 397414
-index <- which(x$id == 397414)
+% -----------------------------------------------------------
+\subsection*{Posted questions}
 
-# unanswered question id = 399971
-index2 <- which(x$id == 399971)
-@
-
-% Table to display an answered question---------------------------------
+% answered question id = 397414
+% unanswered question id = 399971
+% Table to display questions
 \begin{table}[!htbp]
 \centering
-\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
+\begin{tabular}{| p{2cm} | p{2cm} | p{3cm} | p{6cm} | {2cm} | {2cm} | {2cm} | {2cm} |}
   \hline
- Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
+ Answered & Device & Title & Text & New User? & Date Posted & First Answer Date & Response Time \\
   \hline
-  iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago.
+  Yes & iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago.
 Have done the whole rice thing and seen huge difference in it.
@@
 What would be the best way forward?
-& 1 & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\
+& Yes & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\ \hline
+  No & android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & No & 2017-05-23 07:35:12 GMT & NA & NA \\
    \hline
 \end{tabular}
-\caption{Example of an answered question}
-\label{table:answered_q}
+\caption{Answered and unanswered questions}
+\label{table:questions}
 \end{table}
 
-% Table to display an unanswered question-------------------------------
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
-  \hline
- Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
-  \hline
-  android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & 0 & 2017-05-23 07:35:12 GMT & NA & NA \\ 
-   \hline
-\end{tabular}
-\caption{Example of an unanswered question}
-\label{table:unanswered_q}
-\end{table}
-%-----------------------------------------------------------------------
+Table \ref{table:questions} provides an example of an answered and unanswered question. All input fields in the table are as the user entered it.
 
-Device category
+% -----------------------------------------------------------
 
-\begin{itemize}
-  \item Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+\subsection*{Variable Derivation}
+
+\subsubsection*{Device Categorization}
+
+Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
 Device titles were parsed and certain categories were combined or separated to create a new device categorization.
@@
 For questions with missing categories, key words were searched for in device titles to recategorize accordingly.
-\end{itemize}
 
-%-----------------------------------------------------------------------
+\subsubsection*{Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}
 
-Whether or not the question's title contains terms considered to be frequently used among answered/unanswered questions
+These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
+Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do not (cite).
 
-\begin{itemize}
-  \item Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively. 
-  \item These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
-Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do not (cite).
-  \item To create the variables, the data was separated between answered and unanswered questions.
+To create the variables, the data was separated between answered and unanswered questions.
 For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the frequency, or proportion of times those words occurred among all answered questions' titles.
@@
 Lists can be found in Table \ref{table:frequent_terms}
-\end{itemize}
 
-%--------Table with list of frequently used words------------------------
+%Table with list of frequently used words
 \begin{table}[!htbp]
@@
 
-%-----------------------------------------------------------------------
+\subsubsection*{Whether or not the question's title ended in a questionmark}
 
-Whether or not the question's title ended in a questionmark
+This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.
 
-\begin{itemize}
-  \item This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.
-\end{itemize}
+\subsubsection*{Whether or not the question's text contained at least one end punctuation mark}
 
-%-----------------------------------------------------------------------
+This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.
 
-Whether or not the question's text contained at least one end punctuation mark
+\subsubsection*{Whether or not the user made an effort to solve the problem on their own, prior to asking the question}
 
-\begin{itemize}
-  \item This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer. 
-\end{itemize}
-
-%-----------------------------------------------------------------------
-
-Whether or not the user made an effort to solve the problem on their own, prior to asking the question
-
-\begin{itemize}
-  \item Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g.
+Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g.
 ``tried'', ``attempted'', ``tested'').
 This variable was created based off of findings from \cite{Bhat2014}.
-\end{itemize}
 
-%-----------------------------------------------------------------------
+\subsubsection*{Average frequency ``score'' of a question's tags}
 
-Average frequency ``score'' of a question's tags
-
-\begin{itemize}
-  \item This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving an answer faster.
+This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving an answer faster.
 This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
@@
 This variable was created based off of findings from \cite{Bhat2014}.
-\end{itemize}
 
-%-----------------------------------------------------------------------
+\subsubsection*{Number of characters in the user-defined device title}
 
-Number of characters in the user-defined device title
-
-\begin{itemize}
-  \item This variable was included to capture when a user incorrectly defines the device name.
+This variable was included to capture when a user incorrectly defines the device name.
 For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”, and is 136 characters long.
@@
 This variable was created based on the intuition that users who incorrectly define their devices, or do not include any device title, make it difficult for the answering community to discern the question's topic, and thus have longer answer times or remain unanswered.
-\end{itemize}
 
-%-----------------------------------------------------------------------
+\subsubsection*{Average number of characters in a question's tags}
 
-Average number of characters in a question's tags
-
-\begin{itemize}
-  \item This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
+This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
 For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters.
@@
 It is hypothesized that users who correctly define tags, as with the latter user, receive answers quicker than the former.
-\end{itemize}
 
-%-----------------------------------------------------------------------
+\subsubsection*{Ratio of the number of line breaks to the number of characters in a question's text}
 
-Ratio of the number of line breaks to the number of characters in a question's text
-
-\begin{itemize}
-  \item This variable was based on the hypothesis that question's that include line breaks in the text are generally easier to read than questions that don't include any, and thus have faster answer times.
-\end{itemize}
+This variable was based on the hypothesis that question's that include line breaks in the text are generally easier to read than questions that don't include any, and thus have faster answer times.
 

### 2018-01-03 article/draft1.tex
reformatted tables + appendix

@@
 
-% Table to display an answered question---------------------------------
+% -----------------------------------------------------------
+\subsection*{Posted questions}
+
+% answered question id = 397414
+% unanswered question id = 399971
+% Table to display questions
 \begin{table}[!htbp]
 \centering
-\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
+\begin{tabular}{| p{2cm} | p{2cm} | p{3cm} | p{6cm} | {2cm} | {2cm} | {2cm} | {2cm} |}
   \hline
- Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
+ Answered & Device & Title & Text & New User? & Date Posted & First Answer Date & Response Time \\
   \hline
-  iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago.
+  Yes & iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago.
 Have done the whole rice thing and seen huge difference in it.

### 2018-01-03 article/graphics.Rmd
reformatted tables + appendix

@@
 tagscore <- fit_splines("sqrt(avg_tag_score)") # 5 knots or none 
-device <- fit_splines("sqrt(device_length)") # 5 knots
-taglength <- fit_splines("sqrt(avg_tag_length)") # 4 knots
+device <- fit_splines("log10(device_length + 1)") # 5 knots
+taglength <- fit_splines("log10(avg_tag_length + 1)") # 4 knots
 
@@
 
-vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + rcs(sqrt(avg_tag_length), 4) + rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3)"
+vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + rcs(sqrt(newline_ratio), 3)"
 
-vars2 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + log10(avg_tag_score + 1) + rcs(log10(text_length), 5) + rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + rcs(log10(newline_ratio + 1), 3)"
-
-cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
-cv_results2 <- purrr::map2(trains, tests, ~crossval(vars2, .x, .y))
-avg_results2 <- get_avgmetrics(cv_results2)
-avg_results2
-avg_results1 <- get_avgmetrics(cv_results1)
+cv_results <- purrr::map2(trains, tests, ~crossval(vars, .x, .y))
+avg_results1 <- get_avgmetrics(cv_results)
 avg_results1
-xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv", digits = 4)
-```
-
-```{r}
-avg_results2
 ```
@@
 ```
-
-### residuals
-
-```{r}
-x$mart <- residuals(model, type = "martingale")
-
-ggplot(x, aes(x = avg_tag_score, y = mart)) + 
-  geom_point() + 
-  geom_smooth() + 
-  ggtitle(paste("Martingale Residuals for average_tag_score")) + 
-  scale_x_continuous("Average Tag Score (square root)")
-
-plotm <- function(var) {
-  ggplot(x, aes(x = x[[var]], y = mart)) + 
-    geom_point() + 
-    geom_smooth() + 
-    ggtitle(paste("Martingale Residuals for", var)) + 
-    scale_x_continuous(var)
-}
-
-x$sqrt_length <- sqrt(x$avg_tag_length)
-x$sqrt_score <- sqrt(x$avg_tag_score)
-
-plotm("sqrt_score")
-plotm("text_length")
-plotm("device_length")
-plotm("sqrt_length")
-plotm("newline_ratio")
-```

### 2018-01-03 article/draft1.Rnw
added section numbers, reformatted example questions table

@@
 \SweaveOpts{concordance=TRUE}
+
+\makeatletter
+\DeclareRobustCommand\bfseries{%
+  \not@math@alphabet\bfseries\mathbf
+  \fontseries\bfdefault\selectfont
+  \boldmath % <-- added
+}
+\makeatother
 
@@
 
-\section*{Introduction}
+\section*{1. Introduction}
 
@@
 
-\section*{Related Work}
+\section*{2. Related Work}
 
@@
 
-\section*{Materials}
+\section*{3. Materials}
 
@@
 \end{tabular}
-\caption{Categorical predictors derived}
+\caption{Categorical variables derived}
 \label{table:categorical}
@@
 \end{tabular}
-\caption{Continuous predictors derived}
+\caption{Continuous variables derived}
 \label{table:continuous}
@@
 
-\section*{Methods}
+\section*{4. Methods}
 
@@
 The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
-The p-value for this statistic was calculated from the $Ichi^2$ distribution \cite{find}.
+The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}.
 Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability.
@@
 
-\section*{Results and Discussion}
+\section*{5. Results}
 
@@
 \centering
-\begin{tabular}{rlr}
+\begin{tabular}{| l | l |}
   \hline
- Percent\\ Answered & Time (hrs) \\ 
+ \textbf{Percent Answered} & \textbf{Time (hrs)} \\ 
   \hline
@@
 \centering
-\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
-\begin{tabular}{| p{5cm} | p{2.5cm} | p{2cm} |}
+\begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
   \hline
-  Predictor & Transformation & p-value \\ 
+  \textbf{Predictor} & \textbf{Transformation} & \textbf{p-value} \\ 
   \hline
@@
   \multicolumn{ 2 }{ |l| }{ *Device category } & 0.000000e+00 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
-  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
-  \multicolumn{2}{| p{7.5cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
-  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
-  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
+  \multicolumn{ 2 }{ |p{7.75cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
+  \multicolumn{2}{| p{7.75cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
 \end{tabular}
+\caption{Univariate analysis results} 
 \label{table:univariate_results}
@@
   \hline
-  Predictor & K & AIC \\ 
+  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
   \hline
@@
   & 0 & 65862.83 \\ 
-  & *5 & 65862.02 \\ 
+  & \textbf{*}5 & 65862.02 \\ 
   & 4 & 65863.35 \\ 
@@
   & 4 & 65882.98 \\ 
-  & *3 & 65881.93 \\ 
+  & \textbf{*}3 & 65881.93 \\ 
   \hline
   \multirow{ 4 }{ 5 cm }{ Square root transformation of the average frequency ``score'' of a question's tags }
-  & *0 & 65890.75 \\ 
+  & \textbf{*}0 & 65890.75 \\ 
   & 5 & 65891.69 \\ 
@@
   & 0 & 65918.06 \\ 
-  & *5 & 65847.34 \\ 
+  & \textbf{*}5 & 65847.34 \\ 
   & 4 & 65880.89 \\ 
@@
   & 5 & 65911.20 \\ 
-  & *4 & 65910.81 \\ 
+  & \textbf{*}4 & 65910.81 \\ 
   & 3 & 65914.98 \\ 
@@
   \hline
- & HR & LR & p-value & $R^2$ & \textit{Dxy} & Concordance \\ 
+ & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
   \hline
-  Training Sets & 2.015619 & 936.6705 & 0.0000 & 0.1400518 & 0.2691182 & 0.6345591 \\ 
-  Test Sets & 1.975100 & 219.8065 & 0.0000 & 0.1400518 & 0.2579717 & 0.6289859 \\
-  Full Data & 2.01843 & 1164.784 & 0.0000 & 0.1393817 & 0.2680962 & 0.6340481 \\ 
+  \textbf{Training Sets} & 2.015619 & 936.6705 & 0.0000 & 0.1400518 & 0.2691182 & 0.6345591 \\ 
+  \textbf{Test Sets} & 1.975100 & 219.8065 & 0.0000 & 0.1400518 & 0.2579717 & 0.6289859 \\
+  \textbf{Full Data} & 2.01843 & 1164.784 & 0.0000 & 0.1393817 & 0.2680962 & 0.6340481 \\ 
    \hline
@@
 \centering
-\caption{Coefficients for predictors in the final model} 
 \begin{tabular}{|p{1.5cm}|p{6cm}|p{2.5cm}|p{2.5cm}|}
   \hline
- Variable &  Levels & Hazard Ratios & p-value \\ 
+ \textbf{Variable} & \textbf{Levels} & \textbf{Hazard Ratios} & \textbf{p-value} \\ 
   \hline
@@
 \end{tabular} 
+\caption{Coefficients for predictors in the final model} 
 \label{table:coefficients}
@@
 
-\section*{Conclusion}
+\section*{6. Conclusion}
 
@@
 Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!''(tags are generally a couple key words that describe the topic of the question).
-These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low R^2 and discrimination indexes.
+These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low $R^2$ and discrimination indexes.
 
@@
 
-\section*{Acknowledgement}
+\section*{7. Acknowledgement}
 
@@
 
-\section*{Appendix}
+\section*{8. Appendix}
 
 % -----------------------------------------------------------
-\subsection*{Posted questions}
+\subsection*{8.1 Posted questions}
 
@@
 \centering
-\begin{tabular}{| p{2cm} | p{2cm} | p{3cm} | p{6cm} | {2cm} | {2cm} | {2cm} | {2cm} |}
+\begin{tabular}{| l | l | p{6cm} | l |}
   \hline
- Answered & Device & Title & Text & New User? & Date Posted & First Answer Date & Response Time \\
+ \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\
   \hline
-  Yes & iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago.
+  Yes & iPhone 6 & iPhone water damage, touch screen issue &  2017-05-10 21:50:48 GMT \\ \cline{2 - 4}
+  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
+  & Yes & So I dropped my iPhone in water 4 days ago.
 Have done the whole rice thing and seen huge difference in it.
@@
 What would be the best way forward?
-& Yes & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\ \hline
-  No & android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & No & 2017-05-23 07:35:12 GMT & NA & NA \\
+& 2017-05-10 23:12:27 GMT \\ \cline{4 - 4}
+  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
+  & & & 1.361 \\ \cline{4-4} \hline
+  \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\ \cline{1 - 4}
+  No & android tablet & ccccaaaan you help me fix my touch screen & 2017-05-23 07:35:12 GMT \\ \cline{2 - 4}
+  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
+  & No & touch screen not worki & NA \\ \cline{4 - 4}
+  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
+  & & & NA \\ 
    \hline
@@
 
-Table \ref{table:questions} provides an example of an answered and unanswered question. All input fields in the table are as the user entered it.
+Table \ref{table:questions} provides an example of an answered and unanswered question. All fields in the table are shown as the user entered it.
 
@@
 
-\subsection*{Variable Derivation}
+\subsection*{8.2 Variable Derivation}
 
-\subsubsection*{Device Categorization}
+\subsubsection*{8.2.1 Device Categorization}
 
 Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
-Device titles were parsed and certain categories were combined or separated to create a new device categorization.
-Categories in the final variable included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
-Under original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category.
+Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model.
+Categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
+Under the original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category.
 Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.
 For questions with missing categories, key words were searched for in device titles to recategorize accordingly.
+All other questions with ambiguous device titles were categorized as Other.
 
-\subsubsection*{Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}
+\subsubsection*{8.2.2 Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}
 
@@
 
-%Table with list of frequently used words
+% Table with list of frequently used words
 \begin{table}[!htbp]
 \centering
-\caption{Lists of ``frequently-used'' terms among answered and unanswered questions' titles, ordered by decreasing frequency}
 \begin{tabular}{|p{4cm}|p{8cm}|}
   \hline
- ``Frequently-used'' terms among answered questions & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
+ \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
   \hline
-  ``Frequently-used'' terms among unanswered questions & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\
+  \textbf{Frequently-used terms among unanswered questions} & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\
    \hline
 \end{tabular}
+\caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
 \label{table:frequent_terms}
@@
 
-\subsubsection*{Whether or not the question's title ended in a questionmark}
+\subsubsection*{8.2.3 Whether or not the question's title ended in a question mark}
 
@@
 
-\subsubsection*{Whether or not the question's text contained at least one end punctuation mark}
+\subsubsection*{8.2.4 Whether or not the question's text contained at least one end punctuation mark}
 
@@
 
-\subsubsection*{Whether or not the user made an effort to solve the problem on their own, prior to asking the question}
+\subsubsection*{8.2.5 Whether or not the user made an effort to solve the problem on their own, prior to asking the question}
 
@@
 
-\subsubsection*{Average frequency ``score'' of a question's tags}
+\subsubsection*{8.2.6 Average frequency ``score'' of a question's tags}
 
@@
 
-\subsubsection*{Number of characters in the user-defined device title}
+\subsubsection*{8.2.7 Number of characters in the user-defined device title}
 
@@
 
-\subsubsection*{Average number of characters in a question's tags}
+\subsubsection*{8.2.8 Average number of characters in a question's tags}
 
@@
 
-\subsubsection*{Ratio of the number of line breaks to the number of characters in a question's text}
+\subsubsection*{8.2.9 Ratio of the number of line breaks to the number of characters in a question's text}
 

### 2018-01-03 article/draft1.tex
added section numbers, reformatted example questions table

@@
 \input{draft1-concordance}
+
+\makeatletter
+\DeclareRobustCommand\bfseries{%
+  \not@math@alphabet\bfseries\mathbf
+  \fontseries\bfdefault\selectfont
+  \boldmath % <-- added
+}
+\makeatother
 

### 2018-01-03 article/draft1.Rnw
added new predictor - day

@@
   \hline
-  \textbf{Predictor} & \textbf{Transformation} & \textbf{p-value} \\ 
-  \hline
+  \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
+  \hline \hline
   \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
@@
   & Log + 1 & 1.186521e-08 \\
-  & *Square root & 1.464184e-11 \\ \hline
+  & \textbf{*}Square root & 1.464184e-11 \\ \hline
   \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
   & Untransformed & 2.611529e-02 \\ 
-  & *Log + 1 & 6.018542e-05 \\
+  & \textbf{*}Log + 1 & 6.018542e-05 \\
   & Square root & 2.999917e-04 \\ \hline
@@
   & Untransformed & 6.947221e-12 \\
-  & *Log & 0.000000e+00 \\
+  & \textbf{*}Log & 0.000000e+00 \\
   & Square root & 1.110223e-16 \\ \hline
@@
   & Untransformed & 6.530431e-03 \\
-  & *Log + 1 & 1.912977e-05 \\
+  & \textbf{*}Log + 1 & 1.912977e-05 \\
   & Square root & 2.291424e-04 \\ \hline
@@
   & Log + 1 & 1.092952e-07 \\
-  & *Square root & 1.148792e-11 \\ \hline
-  \multicolumn{ 2 }{ |l| }{ *Day of the week the question was posted } & 7.867705e-04 \\ \hline
-  \multicolumn{ 2 }{ |l| }{ *Device category } & 0.000000e+00 \\ \hline
-  \multicolumn{ 2 }{ |p{7.75cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
-  \multicolumn{2}{| p{7.75cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
+  & \textbf{*}Square root & 1.148792e-11 \\ \hline \hline
+  \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
+  \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
+  \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
+  \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
+  \multicolumn{2}{| p{7.75cm}|}{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
+  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
 \end{tabular}
@@
   \hline
-  \textbf{Training Sets} & 2.015619 & 936.6705 & 0.0000 & 0.1400518 & 0.2691182 & 0.6345591 \\ 
-  \textbf{Test Sets} & 1.975100 & 219.8065 & 0.0000 & 0.1400518 & 0.2579717 & 0.6289859 \\
-  \textbf{Full Data} & 2.01843 & 1164.784 & 0.0000 & 0.1393817 & 0.2680962 & 0.6340481 \\ 
+  \textbf{Training Sets} & 2.027030 & 937.3877 & 0.0000 & 0.1401511 & 0.2683734 & 0.6341867 \\ 
+  \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
+  \textbf{Full Data} & 2.028512 & 1165.441 & 0.0000 & 0.1394545 & 0.2675286 & 0.6337643 \\ 
    \hline
@@
 This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-Special thanks also goes to iFixit for providing access to the data and for all the help and assistance in its analysis.
+Special thanks also goes to iFixit for providing access to the CQA data and for the help and assistance in its analysis.
 

### 2018-01-03 article/graphics.Rmd
added new predictor - day

@@
 x <- list[[1]]
+
 library(rms); library(survival); library(ggplot2); library(dplyr)
@@
                    contain_unanswered + contain_answered + title_questionmark + 
-                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
+                   text_contain_punct + text_all_lower + update + prior_effort + day +
                    sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 4) + rcs(log10(text_length), 5) +
@@
 categorical <- list("new_category", "new_user", "title_questionmark", 
-                    "text_contain_punct", "weekday", "text_all_lower", 
+                    "text_contain_punct", "day", "text_all_lower", 
                     "prior_effort", "update", "contain_unanswered", 
@@
 
-vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + rcs(sqrt(newline_ratio), 3)"
+vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + day + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + rcs(sqrt(newline_ratio), 3)"
 

### 2018-01-03 article/draft1.Rnw
reformat full model results table

@@
   \hline
-  Day of the week the question was posted \\ \hline
   Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
+  If the question was posted on the weekend or on a weekday \\ \hline
   Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
@@
 \centering
-\begin{tabular}{|p{1.5cm}|p{6cm}|p{2.5cm}|p{2.5cm}|}
+\begin{tabular}{|p{1.5cm} p{4cm}| l | l | l |}
   \hline
- \textbf{Variable} & \textbf{Levels} & \textbf{Hazard Ratios} & \textbf{p-value} \\ 
+ \textbf{Variable} & & \textbf{Hazard Ratio (SE)} & \textbf{95\% CI} & \textbf{p-value}\\ \hline
+  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & & <0.0001 \\ 
+  & Camera & -0.3199 (0.0476) & & \\ 
+  & Electronics & -0.0138 (0.0904) & & \\ 
+  & Game Console & 0.2458 (0.0784) & & \\ 
+  & Home & 0.3368 (0.0697) & & \\ 
+  & Other & -0.1304 (0.0555) & & \\ 
+  & PC & 0.2818 (0.0597) & & \\ 
+  & Tablet & -0.1566 (0.0815) & & \\ 
+  & Vehicle & 0.4056 (0.0695) & & \\ 
   \hline
-  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.93 & \multirow{ 9 }{ 1.5cm }{ <0.0001 }\\ 
-  & Camera & -0.26 & \\ 
-  & Electronics & -0.08 &\\ 
-  & Game Console & 0.21 &\\ 
-  & Home & 0.39 &\\ 
-  & Other & -0.11 &\\ 
-  & PC & 0.43 &\\ 
-  & Tablet & -0.15 &\\ 
-  & Vehicle & 0.38 &\\
-  \hline
-  & Whether or not the user had been a member for less than one day before the question was posted & -0.10 & 0.0048 \\
-  \hline
-  & Whether or not the question's title contains terms considered to be frequently used among unanswered questions & -0.27 & <0.0001 \\ 
-  \hline
-  & Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.05 & 0.2235\\ 
-  \hline
-  & Whether or not the question's title ended in a questionmark & 0.25 & <0.0001\\ 
-  \hline
-  & Whether or not the question's text contained at least one end punctuation mark & 0.03 & 0.5348\\ 
-  \hline
-  & Whether or not the question's text is in all lower case & -0.18 & 0.0052 \\ 
-  \hline
-  & Whether or not the user edited or added information to the question's text sometime after posting it & 0.28 & 0.0009 \\ 
-  \hline
-  & Whether or not the user made an effort to solve the problem on their own, prior to asking the question & -0.09 & 0.0137 \\ 
-  \hline
-  \multirow{ 6 }{ 2 cm }{ Day of the Week } & Monday & 0.01 & \multirow{ 6 }{ 1.5cm }{ 0.0004 }\\ 
-  & Saturday & -0.07 & \\ 
-  & Sunday & -0.11 & \\ 
-  & Thursday & 0.03 & \\ 
-  & Tuesday & 0.09 & \\ 
-  & Wednesday & 0.10 & \\ 
-  \hline
-  & Square root transformation of the average frequency ``score'' of a question's tags & 2.23 & 0.0020 \\ 
-  \hline
-  \multirow{ 3 }{ 2cm }{ Square root transformation of the average number of characters in a question's tags } & _ & -0.08 & 0.0457\\ 
-  & avg\_tag\_length' & 0.58 & Nonlinear \\ 
-  & avg\_tag\_length'' & -1.52 & 0.0804\\ 
-  \hline
-  \multirow{ 4 }{ 2cm }{Log transformation of the number of characters in a question's text} & text length & -0.08 & 0.4344
-  & text\_length' & -0.36 & Nonlinear \\ 
-  & text\_length'' & 2.39 & 0.4578 \\
-  & text\_length''' & -3.69 & \\ 
-  \hline
-  \multirow{ 4 }{ 2cm }{ Square root transformation of the number of characters in a question's device title} & device length & -0.07 & 0.2790 \\
-  & device\_length' & 0.18 & Nonlinear \\ 
-  & device\_length'' & -0.27 & 0.4185\\ 
-  & device\_length''' & 0.21 & \\ 
-  \hline
-  \multirow{ 2 }{ 2cm }{ Square root transformation of the ratio of number of line breaks to number of characters in a question's text} & line break & 0.12 & 0.3569 \\
-  & newline\_ratio' & 0.36 & Nonlinear: 0.6191 \\ 
-   \hline
+  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331) & & <0.0001 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 0.6204 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 0.0061 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 0.2604 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340) & & <0.0001 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & <0.0001 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 0.0005 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 0.0033 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 0.0453 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average frequency score of a question's tags } & 2.2609 (0.7196) & & 0.0017 \\ \hline
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average tag length } & -0.0814 (0.0309) & & \\
+  & '' & 0.5945 (0.2661) & & \\
+  & ''' & -1.5879 (0.7231) & & \\
+
+  % \multirow{ 3 }{ 2cm }{ Square root of the average tag length } & _ & -0.08 & 0.0457\\ 
+  % & avg\_tag\_length' & 0.58 & Nonlinear \\ 
+  % & avg\_tag\_length'' & -1.52 & 0.0804\\ 
+  % \hline
+  % \multirow{ 4 }{ 2cm }{Log transformation of the number of characters in a question's text} & text length & -0.08 & 0.4344
+  % & text\_length' & -0.36 & Nonlinear \\ 
+  % & text\_length'' & 2.39 & 0.4578 \\
+  % & text\_length''' & -3.69 & \\ 
+  % \hline
+  % \multirow{ 4 }{ 2cm }{ Square root transformation of the number of characters in a question's device title} & device length & -0.07 & 0.2790 \\
+  % & device\_length' & 0.18 & Nonlinear \\ 
+  % & device\_length'' & -0.27 & 0.4185\\ 
+  % & device\_length''' & 0.21 & \\ 
+  % \hline
+  % \multirow{ 2 }{ 2cm }{ Square root transformation of the ratio of number of line breaks to number of characters in a question's text} & line break & 0.12 & 0.3569 \\
+  % & newline\_ratio' & 0.36 & Nonlinear: 0.6191 \\ 
+  %  \hline
 \end{tabular} 

### 2018-01-03 article/draft1.Rnw
edited table 7

@@
   \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average frequency score of a question's tags } & 2.2609 (0.7196) & & 0.0017 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average tag length } & -0.0814 (0.0309) & & \\
-  & '' & 0.5945 (0.2661) & & \\
-  & ''' & -1.5879 (0.7231) & & \\
+  \multicolumn{ 2 }{ |p{5.5cm}| }{ \multirow{3}{*}{Square root of the average tag length} } & -0.0814 (0.0309) & & \\
+  & & 0.5945 (0.2661) & & \\
+  & & -1.5879 (0.7231) & & \\ \hline
 

### 2018-01-04 article/graphics.Rmd
added data frame of hazard ratios + CI

@@
                    surv = TRUE)
+model
+
 ```
@@
 ```{r}
-# model statistics + parameters
-# figure out how to get p-values 
-parameterdf <- data.frame(variable = names(model$coefficients),
-                          coefficients = round(unname(model$coefficients), 3))
-parameterdf
-xtable::xtable(parameterdf, caption = "Coefficients for predictors in the final model",
-               label = "table:coefficients")
 # ------------------------------------------
+# coefficient p-values
 pvalues <- as.matrix(anova(model))[,3]
@@
                        pvalue = unname(pvalues))
-xtable::xtable(pvaluedf, caption = "P-values for final model fit to the full data",
-               label = "table:pvalues")
-
+pvaluedf
+# ------------------------------------------
 modelstats <- data.frame(statistic = names(model$stats), 
@@
 modelstats
+
+# ------------------------------------------
+# data frame with coefficients, HR and confidence intervals
+# SE of all coefficients 
+se <- c(0.0476, 0.0904, 0.0784, 0.0830, 0.0697, 0.0555, 0.0597, 0.0815, 0.0695, 0.0364, 0.0340, 0.0422, 0.0332, 0.0499, 0.0645, 0.0857, 0.0362, 0.0331, 0.7196, 0.0309, 0.2661, 0.7231, 0.1856, 0.8452, 4.1706, 6.8975, 0.0714, 0.9724, 2.3149, 2.3255, 0.4776, 0.7265)
+
+coefficientsdf <- data.frame(coefficients = names(model$coefficients), 
+                             beta = as.numeric(unname(model$coefficients)),
+                             SE = se,
+                             HR = exp(coefficientsdf$beta),
+                             upper = exp(coefficientsdf$beta + (1.96*coefficientsdf$SE)),
+                             lower = exp(coefficientsdf$beta - (1.96*coefficientsdf$SE))
+                             )
+
+coefficientsdf
 
@@
 # ------------------------------------------
+# proportional hazards assumptions
 ph <- cox.zph(model)
@@
 ph_test
+
 ```
-
-```{r}
-final_metrics
-pvalues
-anova(model)
-```

### 2018-01-04 article/draft1.Rnw
edited table 7 + added interpretations to results section

--- 2018-01-03 article/draft1.Rnw
@@
 \usepackage{multirow}
+\usepackage{color,soul}
 \begin{document}
@@
 \centering
-\begin{tabular}{|p{1.5cm} p{4cm}| l | l | l |}
+\begin{tabular}{|p{3.5cm} p{4cm}| c | l | c |}
   \hline
- \textbf{Variable} & & \textbf{Hazard Ratio (SE)} & \textbf{95\% CI} & \textbf{p-value}\\ \hline
-  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & & <0.0001 \\ 
+ \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{95\% CI} & \textbf{p-value} \\ \hline
+  \multirow{ 9 }{ 3.5 cm }{ Device Category } & Apple Product & \hl{0.9346} (0.0476) & & 0.000000e+00 \\ 
   & Camera & -0.3199 (0.0476) & & \\ 
@@
   \hline
-  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331) & & <0.0001 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 0.6204 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 0.0061 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 0.2604 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340) & & <0.0001 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & <0.0001 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 0.0005 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 0.0033 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 0.0453 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average frequency score of a question's tags } & 2.2609 (0.7196) & & 0.0017 \\ \hline
-  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average tag length } & -0.0814 (0.0309) & & \\
-  & '' & 0.5945 (0.2661) & & \\
-  & ''' & -1.5879 (0.7231) & & \\
-
-  % \multirow{ 3 }{ 2cm }{ Square root of the average tag length } & _ & -0.08 & 0.0457\\ 
-  % & avg\_tag\_length' & 0.58 & Nonlinear \\ 
-  % & avg\_tag\_length'' & -1.52 & 0.0804\\ 
-  % \hline
-  % \multirow{ 4 }{ 2cm }{Log transformation of the number of characters in a question's text} & text length & -0.08 & 0.4344
-  % & text\_length' & -0.36 & Nonlinear \\ 
-  % & text\_length'' & 2.39 & 0.4578 \\
-  % & text\_length''' & -3.69 & \\ 
-  % \hline
-  % \multirow{ 4 }{ 2cm }{ Square root transformation of the number of characters in a question's device title} & device length & -0.07 & 0.2790 \\
-  % & device\_length' & 0.18 & Nonlinear \\ 
-  % & device\_length'' & -0.27 & 0.4185\\ 
-  % & device\_length''' & 0.21 & \\ 
-  % \hline
-  % \multirow{ 2 }{ 2cm }{ Square root transformation of the ratio of number of line breaks to number of characters in a question's text} & line break & 0.12 & 0.3569 \\
-  % & newline\_ratio' & 0.36 & Nonlinear: 0.6191 \\ 
-  %  \hline
+  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & \hl{-0.1334} (0.0331) & & 5.525114e-05 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 6.204270e-01 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 6.065638e-03 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 2.604130e-01 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & \hl{-0.2808} (0.0340) & & 1.110223e-16 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & 9.880985e-15 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 5.027830e-04 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 3.300423e-03 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 4.534803e-02 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average frequency score of a question's tags } & 2.2609 (0.7196) & & 1.679666e-03 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{3}{*}{Square root of the average tag length} } & -0.0814 (0.0309) & & \\
+  & & 0.5945 (0.2661) & & \\
+  & & -1.5879 (0.7231) & & \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of text length} } & -0.0619 (0.1856) & & \\
+  & & -0.5052 (0.8452) & & \\
+  & & 2.9957 (4.1706) & & \\
+  & & -4.4755 (6.8975) & & \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of device title length} } & -0.0488 (0.0714) & & \\
+  & & -0.4348 (0.9724) & & \\
+  & & 1.2208 (2.3149) & & \\
+  & & -1.3199 (2.3255) & & \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{2}{*}{Square root of the ratio of the number of line breaks to text length} } & -0.0076 (0.4776) & & \\
+  & & 0.4345 (0.7265) & & \\ \hline
 \end{tabular} 
@@
 
-Assessing the proportional hazards assumption indicated that several predictors were in violation, results can be found in Table \ref{table:ph_assumption}.
-Final model statistics and parameter coefficients are in Table \ref{table:coefficients}.
-Individual predictors found to be significant (alpha = 0.001) are: device category, whether or not the question's text contains ``frequently-used'' terms among unanswered questions, whether or not the questions title ends in a questionmark, whether or not the user updated the question after posting it.
+% Final model statistics
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{| r | r |}
+  \hline
+  \textbf{LR} & 1266.073 \\ \hline
+  \textbf{p-value} & 0 \\ \hline
+  \textbf{$R^2$} & 0.151 \\ \hline
+  \textbf{\textit{Dxy}} & 0.268 \\ \hline
+\end{tabular}
+\caption{Final model statistics} 
+\label{table:final model}
+\end{table}
+
+Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
+Interpretations of the coefficients highlighted above:
+
+\begin{itemize}
+  \item The estimated hazard of receiving an answer is 154.6\% (95\% CI (131.9\%, 179.5\%)) higher for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer for questions posted on the weekend is 12.5\% (95\% CI (6.6\%, 18.0\%)) lower than the hazard for questions posted on a weekday, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 24.5\% (95\% CI (19.3\%, 29.3\%)) lower for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+\end{itemize}
+
+See Table \ref{table:coefficients} for the full list of model coefficients. Table \ref{table:final model} displays statistics for the final model.
 

### 2018-01-04 article/draft1.tex
edited table 7 + added interpretations to results section

--- 2018-01-03 article/draft1.tex
@@
 \usepackage{multirow}
+\usepackage{color,soul}
 \usepackage{Sweave}

### 2018-01-04 article/draft1.Rnw
added user + forum suggestions to the conclusion

@@
 
-model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)
+model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + 
+                   contain_unanswered + contain_answered + title_questionmark + 
+                   text_contain_punct + text_all_lower + update + prior_effort + day +
+                   sqrt(avg_tag_score) + rms::rcs(sqrt(avg_tag_length), 4) + rms::rcs(log10(text_length), 5) +
+                   rms::rcs(sqrt(device_length), 5) + rms::rcs(sqrt(newline_ratio), 3), 
+                   data = x, 
+                   x = TRUE, y = TRUE, 
+                   surv = TRUE)
 @
@@
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))).
 Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.
@@
 
-\section*{5. Results}
+\section*{5. Results and Discussion}
 
@@
   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
-  \multicolumn{2}{| p{7.75cm}|}{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
@@
 Metrics did not change significantly from training to test sets, indicating that the model was not overfit.
-Metrics for the final model's performance on the full data, also found in \ref{table:cv}, are consistent with metrics found in cross validation.
+Metrics for the final model's performance on the full data, also found in \ref{table:cv}, are consistent with metrics found in cross validation and indicate low predictive accuracy.
 
@@
 
+Results and coefficients of the final model reveal how users can ask a question in order to decrease response time.
+Findings indicate that users should phrase the title in the form of a question, use correct grammar (e.g.
+punctuation and capitalization), include specific and concise tags, and post the question on a weekday.
+
+Regarding the model's weak predictive accuracy, it may be explained by limitations in the data.
+Many users asking a question incorrectly specified the device name (e.g.
+``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
+Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic).
+It is likely that these inconsistencies contributed to the final model's low predictive power.
+This, along with the results of the final model, reveal some of the ways that the CQA can be structured to improve analysis and decrease response time.
+As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
+For example, instead of allowing users to enter any device name or tag, which leaves room for user error, the CQA can restrict the tags or devices that users can include to a drop down list.
+The CQA can also include more tips to guide users asking questions.
+Establishing and implementing a more restrictive CQA structure can help users to ask understandable and clear questions and decrease response time, as well as create a set of consistent questions for better analysis.
+
 %===================================================================================================
@@
 This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, and whether or not the user updated the question's text after the initial posting.
+Predictors found to be signficant in the model included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a questionmark.
 While overall the model was signficant, its predictive performance was considerably low.
-
-The data analyzed for this model presented limitations, and may explain the model's low predictive accuracy.
-Many users on the CQA incorrectly specified the device name in their question (e.g.
-``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
-Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!''(tags are generally a couple key words that describe the topic of the question).
-These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low $R^2$ and discrimination indexes.
-
-Future studies can further investigate if the predictors found to be significant in this study can be generalized to other CQAs.
 
@@
 This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-Special thanks also goes to iFixit for providing access to the CQA data and for the help and assistance in its analysis.
+Special thanks goes to iFixit for providing access to the CQA data and for the help and assistance in its analysis.
 
@@
 
-% -----------------------------------------------------------
+% --------------------------------------------------------------------------------------------------
 \subsection*{8.1 Posted questions}
@@
 
-Table \ref{table:questions} provides an example of an answered and unanswered question. All fields in the table are shown as the user entered it.
+Table \ref{table:questions} provides an example of an answered and unanswered question. All fields in the table are shown as the users entered it.
 
-% -----------------------------------------------------------
+% ------------------------------------------------------------------------------------------------
 
@@
 
-\subsubsection*{8.2.2 Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.2 Whether or not the question's text contained at least one end punctuation mark}
+
+This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.
+
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.3 Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}
 
@@
 
-\subsubsection*{8.2.3 Whether or not the question's title ended in a question mark}
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.4 Whether or not the question's title ended in a question mark}
 
@@
 
-\subsubsection*{8.2.4 Whether or not the question's text contained at least one end punctuation mark}
-
-This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.
+% ------------------------------------------------------------------------
 
@@
 This variable was created based off of findings from \cite{Bhat2014}.
+
+% ------------------------------------------------------------------------
 
@@
 
-\subsubsection*{8.2.7 Number of characters in the user-defined device title}
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.7 Average number of characters in a question's tags}
+
+This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
+For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters.
+Question 410254 includes tags "sound", "sound driver" and "speaker" and has an average of 8 characters per tag.
+It is hypothesized that users who correctly define tags, as with the latter user, receive answers quicker than the former.
+
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.8 Number of characters in the user-defined device title}
 
@@
 
-\subsubsection*{8.2.8 Average number of characters in a question's tags}
-
-This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
-For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters.
-Question 410254 includes tags "sound", "sound driver" and "speaker" and has an average of 8 characters per tag.
-It is hypothesized that users who correctly define tags, as with the latter user, receive answers quicker than the former.
+% ------------------------------------------------------------------------
 
@@
 
+% ------------------------------------------------------------------------
+
 \bibliography{questions}

### 2018-01-04 article/draft1.tex
added user + forum suggestions to the conclusion

@@
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))).
 Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

### 2018-01-04 article/draft1.Rnw
edited appendix + added citations

@@
 
-These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not.
-Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do not (cite).
+These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not.
+Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than qustions that do not.
+This variable was created based off of methods from \cite{Correa2013} and \cite{Ravi2014}.
 
@@
 
-This variable was created based on the hypothesis that questions with titles in the form of questions receive answers faster than those that do not.
+This variable was created to investigate if questions with titles in the form of questions receive answers faster than those that do not \citep{Bhat2014}.
 
@@
 
-Logical variable indicating true if the asker included words in the question's text that indicate prior effort or research was done before asking the question (e.g.
-``tried'', ``attempted'', ``tested'').
-This variable was created based off of findings from \cite{Bhat2014}.
+Logical variable indicating true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting.
+Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
+This variable was created based off of findings and methods from \cite{Bhat2014} \cite{Harper2008}.
 
@@
 
-This variable was created to investigate the idea that some tags are more ``popular'', or widely used than other tags, and that including such tags might increase the likelihood of that question receiving an answer faster.
+This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
 This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
@@
 
-This variable, similar to the device-length variable, was created to capture when a user correctly or incorrectly used the tagging system.
+This variable was created to capture when a user correctly or incorrectly used the tagging system.
 For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters.
 Question 410254 includes tags "sound", "sound driver" and "speaker" and has an average of 8 characters per tag.
-It is hypothesized that users who correctly define tags, as with the latter user, receive answers quicker than the former.
+It is hypothesized that questions with correctly defined tags, as with the latter example, have faster response times.
 
@@
 11 questions in the data also did not include any device title.
-This variable was created based on the intuition that users who incorrectly define their devices, or do not include any device title, make it difficult for the answering community to discern the question's topic, and thus have longer answer times or remain unanswered.
+This variable was created to investigate if questions with incorrectly defined device names make it difficult for the answering community to discern the question's topic, and thus have longer response times or remain unanswered.
 
@@
 
-This variable was based on the hypothesis that question's that include line breaks in the text are generally easier to read than questions that don't include any, and thus have faster answer times.
+This variable was based on the hypothesis that questions that include line breaks in the text are easier to read than questions that don't include any, and thus have shorter response times.
 

### 2018-01-04 article/draft1.Rnw
edited intro + related works sections

@@
 Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge.
-Thousands of questions and answers are posted everyday.
+Thousands of questions and answers are posted by users everyday.
 One such example of a CQA is iFixit's \textit{Answers} forum.
@@
 This paper presents a survival analysis of the time until a question receives its first answer.
-A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
+A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time.
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
@@
 As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users.
-This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions.
+This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 100,000 solutions.
 As thousands of users rely on this forum for information, it is important that users receive timely answers.
-Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum.
-Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.
+Fast response times enhance user experience and thus increase web traffic, which is valuable to the reputation and longevity of iFixit's \textit{Answers} forum.
+Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.
 
@@
 
-With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies related to information sciences.
-Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow}, using both tag-based and textual features.
-Analysis determine that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors of response time.
-\cite{Mahmud2013} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses.
-Both \cite{Bhat2014} and \cite{Mahmud2013} restrict analysis to questions for which the response time is observed, ignoring unanswered questions; meanwhile \cite{Asaduzzaman2013} focused exclusively on characteristics of unanswered questions.
-\cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length, and user features like the number of questions asked and answered by the user prior to posting.
+With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies.
+Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow} using features of the questions.
+Analysis determined that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors.
+\cite{Mahmud2013} approached response time analysis with a different method, and proposed models to predict response times of questions posted on Twitter based on exponential distributions and built from users' previous wait times for responses.
+In contrast, \cite{Asaduzzaman2013} focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered using both textual features of the questions and characteristics of the user.
+All research mentioned restricted analysis to either questions for which response times were observed, or to questions that remained unanswered.
 The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
@@
 The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts.
-\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features (surface, lexical, syntactic, forum-specific, and similarity (relatedness of a post to the topic of the forum) features).
-\cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality.
-Wikipedia articles can represent the same kind of user-generated content featured on CQAs.
+\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features of the questions.
+\cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
 On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}.
-A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question and answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a}.
-\cite{Ravi2014} presented a slightly different approach by analyzing the content of posts and utilizing latent topic models to predict quality.
-\cite{Anderson2012} developed models to the predict the long term value of a question and its answers on \textit{Stack Overflow}.
-The present analysis combines both textual and non-textual features of questions on iFixit's \textit{Answers} forum in a Cox regression model to predict survival probability of questions.
+A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}.
+All research previously mentioned restricted analysis to predicting either question quality or answer quality.
+\cite{Anderson2012} presented models to predict the long term value or quality of questions as well as its answers on \textit{Stack Overflow}.
+The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating high quality questions also lead to faster response times.
+(fix this section)
 

### 2018-01-04 article/draft1.tex
edited intro + related works sections

@@
 This paper presents a survival analysis of the time until a question receives its first answer.
-A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
+A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time.
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).

### 2018-01-08 article/draft1.Rnw
edited related works

@@
 
-With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies.
-Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow} using features of the questions.
-Analysis determined that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors.
-\cite{Mahmud2013} approached response time analysis with a different method, and proposed models to predict response times of questions posted on Twitter based on exponential distributions and built from users' previous wait times for responses.
-In contrast, \cite{Asaduzzaman2013} focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered using both textual features of the questions and characteristics of the user.
+With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies.
+Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
+\cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
+\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered.
 All research mentioned restricted analysis to either questions for which response times were observed, or to questions that remained unanswered.
@@
 
-The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts.
-\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features of the questions.
-\cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}.
+The majority of existing research has been focused on predicting question and answer quality.
+\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
+\cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
+\cite{H.fu} instead found that non-textual features, like revision and comment count on an answer or the number of points a user has, were the most useful indicators of answer quality.
 A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}.
-All research previously mentioned restricted analysis to predicting either question quality or answer quality.
-\cite{Anderson2012} presented models to predict the long term value or quality of questions as well as its answers on \textit{Stack Overflow}.
-The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating high quality questions also lead to faster response times.
+\cite{Anderson} took analysis further and presented models to predict the long term value of questions as well as the answers it receives.
+The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating that a question is of high quality, can also lead to faster response times.
 (fix this section)

### 2018-01-08 article/draft1.Rnw
proofread + revisions

@@
 
-Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge.
+Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced knowledge.
 Thousands of questions and answers are posted by users everyday.
@@
 The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit's mission is to equip users with the knowledge and tools to repair their broken devices, as part of an effort to save money and reduce electronic waste.
+Founded in 2003, iFixit's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to save money and reduce electronic waste.
 This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
@@
 
-However, analysis and prediction of response times on CQAs have not been thoroughly investigated.
+However, analysis and prediction of response times on CQAs has not been thoroughly investigated.
 There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality.
-This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.
+This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the survival probability of a question.
 
@@
 \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered.
-All research mentioned restricted analysis to either questions for which response times were observed, or to questions that remained unanswered.
+However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
 The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
@@
 The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded).
-Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time when the question was posted, and date and time when the first answer was received.
+Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received.
 Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}.
@@
 Questions analyzed were restricted to those posted in English.
-The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
+The time until event variable used in survival analysis was defined as the time since posting until a question receives its first answer.
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
@@
 Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
-Each predictor was entered into univarite Cox models, and strength of association with response times was assessed.
+Each predictor was entered into univarite Cox models and strength of association with response times was assessed.
 Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model.
-Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include into the final model.
+Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model.
 Univariate analysis was again performed on each continuous predictor to investigate the use of splines.
@@
 AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}.
-All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation.
+All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
 No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.
@@
 Signficant results from this model would indicate high predictive accuracy.
-The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
+The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
 The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}.
@@
 
-  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data).
-Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date.
+  Of 8,025 questions in the full data set, \Sexpr{format(nrow(x), big.mark = ",")} were in English (97\% of the full data).
+Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date.
 The shortest response time was \Sexpr{shortest} hours.
-The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days).
+The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days).
 Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
@@
 
-  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability for all questions in the data.
+  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
 The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
@@
 
-Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions.
-Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}.
-As several continuous predictors contained zeros as values, the log transformation was applied after adding one.
+Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions, and each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
+Results of univariate analysis performed on one training set are shown in Table \ref{table:univariate_results}.
+For continuous predictors that contained zeros, one was added to each observation before applying log transformations.
 All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
@@
 Metrics did not change significantly from training to test sets, indicating that the model was not overfit.
-Metrics for the final model's performance on the full data, also found in \ref{table:cv}, are consistent with metrics found in cross validation and indicate low predictive accuracy.
+Metrics for the final model's performance on the full data, also found in Table \ref{table:cv}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
 
@@
 Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
-Interpretations of the coefficients highlighted above:
+
+Interpretations of the coefficients highlighted in Table \ref{table:coefficients}:
 
@@
 As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
-For example, instead of allowing users to enter any device name or tag, which leaves room for user error, the CQA can restrict the tags or devices that users can include to a drop down list.
+Allowing users to enter any device name or tag leaves room for user error.
+Instead, the CQA can restrict the tags or devices that users can include to a drop-down list.
 The CQA can also include more tips to guide users asking questions.
-Establishing and implementing a more restrictive CQA structure can help users to ask understandable and clear questions and decrease response time, as well as create a set of consistent questions for better analysis.
+Establishing and implementing a more restrictive framework for asking questions can help users ask understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
 
@@
 This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be signficant in the model included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a questionmark.
+Predictors found to be signficant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a questionmark.
 While overall the model was signficant, its predictive performance was considerably low.
@@
   & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
-  & & & 1.361 \\ \cline{4-4} \hline
+  & & & 1.361 \\ \cline{4-4} \hline \hline
   \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\ \cline{1 - 4}
@@
 
-Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+Original device categories defined by iFixit included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
 Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model.
-Categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
-Under the original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category.
+Final categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
+Under the original device categorization, 1,954 questions (25.2\% of 7,760) were categorized incorrectly and indicated an NA for its category.
 Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.

### 2018-01-08 article/draft1.tex
proofread + revisions

@@
 
-  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data).
-Of those questions, 4951 (63.8}\%) received an answer by the download date.
+  Of 8,025 questions in the full data set, 7,760 were in English (97\% of the full data).
+Of those questions, 4,951 (63.8}\%) received an answer by the download date.
 The shortest response time was 0.5 hours.
-The longest was 2159.02 hours (89.96 days).
+The longest was 2,159.02 hours (89.96 days).
 Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
@@
 
-Each training set contained 6208 questions, and each test set contained 1552 questions.
-Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}.
-As several continuous predictors contained zeros as values, the log transformation was applied after adding one.
+Each training set contained 6,208 questions, and each test set contained 1,552 questions.
+Results of univariate analysis performed on one training set are shown in Table \ref{table:univariate_results}.
+For continuous predictors that contained zeros, one was added to each observation before applying log transformations.
 All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

### 2018-01-09 article/draft1.Rnw
proofread + revisions

@@
                     contain_unanswered + contain_answered + title_questionmark + 
-                   text_contain_punct + text_all_lower + update + prior_effort + day +
-                   sqrt(avg_tag_score) + rms::rcs(sqrt(avg_tag_length), 4) + rms::rcs(log10(text_length), 5) +
-                   rms::rcs(sqrt(device_length), 5) + rms::rcs(sqrt(newline_ratio), 3), 
+                    text_contain_punct + text_all_lower + update + prior_effort + 
+                    day + sqrt(avg_tag_score) + rms::rcs(log10(text_length), 5) + 
+                    rms::rcs(log10(avg_tag_length + 1), 4) + rms::rcs(log10(device_length + 1), 5) + 
+                    rms::rcs(sqrt(newline_ratio), 3), 
                    data = x, 
@@
 
-\section*{Abstract}
+\section*{Abstract} % fix the hazard ratios!!!!
 
-Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced knowledge.
-Thousands of questions and answers are posted by users everyday.
+Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information.
 One such example of a CQA is iFixit's \textit{Answers} forum.
 This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users.
-A reliable measure of the health of these CQAs is question response time.
-Fast response times enhance user engagement and satisfaction and increase web traffic.
+An important aspect of these CQAs, for both users and the forum, is question response time.
 This paper presents a survival analysis of the time until a question receives its first answer.
-A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time.
+A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)).
 Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.
@@
 
-Community-driven online question and answer forums (CQA) are becoming widely-used sources of information.
+Community-driven online question and answer forums are becoming widely-used sources of information.
 These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month.
@@
 As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users.
-This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 100,000 solutions.
+This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 100,000 user-posted solutions.
 As thousands of users rely on this forum for information, it is important that users receive timely answers.
-Fast response times enhance user experience and thus increase web traffic, which is valuable to the reputation and longevity of iFixit's \textit{Answers} forum.
-Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.
+Fast response times have been shown to be associated with user satisfaction and in turn increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
+Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask questions to minimize response times and for how the forum design can be improved.
 
@@
 There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality.
-This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the survival probability of a question.
+This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict the survival probability of a question.
 
@@
 \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
-\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered.
-However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
-The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
+\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered.
+All research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
+The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
 
@@
 \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
-\cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-\cite{H.fu} instead found that non-textual features, like revision and comment count on an answer or the number of points a user has, were the most useful indicators of answer quality.
-A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}.
-\cite{Anderson} took analysis further and presented models to predict the long term value of questions as well as the answers it receives.
-The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating that a question is of high quality, can also lead to faster response times.
-(fix this section)
+\cite{Blumenstock} also determined that textual features, e.g.
+word count, was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
+\cite{H.fu} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
+A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}.
+The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.
 
@@
   \hline
-  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
-  If the question was posted on the weekend or on a weekday \\ \hline
+  Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
+  If the question was posted on a weekend or on a weekday \\ \hline
   Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
   Whether or not the question's text is in all lower case \\ \hline
-  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See Appendix for a complete list of these terms. \\ \hline
-  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See Appendix for a complete list of these terms. \\ \hline
+  Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \hline
+  Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \hline
   Whether or not the question's title ends in a question mark \\ \hline
-  Whether or not the user edited or added information to the question's text sometime after posting it. \\ \hline
-  Whether or not the user made an effort to solve the problem prior to asking the question. \\ \hline
+  Whether or not the user edited or added information to the question's text after posting it \\ \hline
+  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
 \end{tabular}
@@
   \hline
-  Average number of characters in each question's tags\\ \hline
-  Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. \\ \hline
-  Number of characters in the question's text \\ \hline
-  Number of characters in the user-defined device name \\ \hline
-  Ratio of the number of line breaks to the number of characters in the question's text \\ \hline
+  Average number of characters in each question's tags (Average tag length) \\ \hline
+  Average frequency for all of a question's tags.
+Frequency defined as the proportion of times a tag appears in all of the data.
+Questions without tags were assigned a value of 0 (Average tag frequency) \\ \hline
+  Number of characters in the question's text (Text length) \\ \hline
+  Number of characters in the user-defined device name (Device name length) \\ \hline
+  Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
 \end{tabular}
@@
 Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received.
+See Appendix for examples of answered and unanswered questions.
 Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}.
@@
 
-In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
+In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
 To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
-The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
+The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
 Signficant results from this model would indicate high predictive accuracy.
@@
 
-To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package.
+To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R.
 This function uses the Cox model and a vector of times to compute predicted survival probabilities.
@@
   \hline \hline
-  \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
+  \multirow{ 3 }{ 5cm }{ Average tag frequency }
   & Untransformed & 1.270620e-08 \\
@@
   & \textbf{*}Square root & 1.464184e-11 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
+  \multirow{ 3 }{ 5cm }{ Average tag length }
   & Untransformed & 2.611529e-02 \\ 
@@
   & Square root & 2.999917e-04 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Number of characters in a question's text }
-  & Untransformed & 6.947221e-12 \\
-  & \textbf{*}Log & 0.000000e+00 \\
-  & Square root & 1.110223e-16 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Number of characters in the user-defined device title }
+  \multirow{ 3 }{ 5cm }{ Device name length }
   & Untransformed & 6.530431e-03 \\
@@
   & Square root & 2.291424e-04 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Ratio of the number of line breaks to the number of characters in a question's text } 
+  \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
   & Untransformed & 1.398819e-07 \\
   & Log + 1 & 1.092952e-07 \\
-  & \textbf{*}Square root & 1.148792e-11 \\ \hline \hline
+  & \textbf{*}Square root & 1.148792e-11 \\ 
+  \multirow{ 3 }{ 5cm }{ Text length }
+  & Untransformed & 6.947221e-12 \\
+  & \textbf{*}Log & 0.000000e+00 \\
+  & Square root & 1.110223e-16 \\ \hline \hline
   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
@@
   \hline
-  \multirow{ 4 }{ 5cm }{ Log transformation of the number of characters in a question's text } 
+  \multirow{ 4 }{ 5cm }{ Log transformation of text length } 
   & 0 & 65862.83 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text }
+  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
   & 0 & 65890.28 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average frequency ``score'' of a question's tags }
+  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
   & \textbf{*}0 & 65890.75 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Log transformation of the number of characters in the user-defined device title + 1 }
+  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
   & 0 & 65918.06 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Log transformation of the average number of characters in a question's tags + 1 }
+  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
   & 0 & 65920.24 \\ 
@@
 
-Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Values of knots marked with an asterisk (*) were included in the final model.
+Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
 
@@
   \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
-  \textbf{Full Data} & 2.028512 & 1165.441 & 0.0000 & 0.1394545 & 0.2675286 & 0.6337643 \\ 
+  \textbf{Full Data} & 2.028051 & 1165.0321 & 0.0000 & 0.1394092 & 0.2672884 & 0.6336442 \\ 
    \hline
@@
 
-Average performance metrics for test and training sets and in Table \ref{table:cv}.
-Partial likelihood ratio statistics and p-values indicate that the model as a whole is signficantly associated with response time.
-However, its $R^2$ statistic and discrimination indexes are considerably low.
-Metrics did not change significantly from training to test sets, indicating that the model was not overfit.
+Average performance metrics for test and training sets are in Table \ref{table:cv}.
+Partial likelihood ratios and p-values indicate that the model as a whole is signficantly associated with response time.
+However, $R^2$ statistics and discrimination indexes are considerably low.
 Metrics for the final model's performance on the full data, also found in Table \ref{table:cv}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
+Results for training, test, and the full data did not change significantly, indicating that the model was not overfit.
 
@@
   \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 4.534803e-02 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average frequency score of a question's tags } & 2.2609 (0.7196) & & 1.679666e-03 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{3}{*}{Square root of the average tag length} } & -0.0814 (0.0309) & & \\
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196) & & 1.679666e-03 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{3}{*}{Square root of average tag length} } & -0.0814 (0.0309) & & \\
   & & 0.5945 (0.2661) & & \\
@@
   & & -4.4755 (6.8975) & & \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of device title length} } & -0.0488 (0.0714) & & \\
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of device name length} } & -0.0488 (0.0714) & & \\
   & & -0.4348 (0.9724) & & \\
@@
   & & -1.3199 (2.3255) & & \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{2}{*}{Square root of the ratio of the number of line breaks to text length} } & -0.0076 (0.4776) & & \\
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{2}{*}{Square root of line break to text length ratio} } & -0.0076 (0.4776) & & \\
   & & 0.4345 (0.7265) & & \\ \hline
@@
   \hline
-  \textbf{LR} & 1266.073 \\ \hline
+  \textbf{LR} & 1265.291 \\ \hline
   \textbf{p-value} & 0 \\ \hline
-  \textbf{$R^2$} & 0.151 \\ \hline
-  \textbf{\textit{Dxy}} & 0.268 \\ \hline
+  \textbf{$R^2$} & 0.150 \\ \hline
+  \textbf{\textit{Dxy}} & 0.267 \\ \hline
 \end{tabular}
@@
 \begin{itemize}
-  \item The estimated hazard of receiving an answer is 154.6\% (95\% CI (131.9\%, 179.5\%)) higher for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer for questions posted on the weekend is 12.5\% (95\% CI (6.6\%, 18.0\%)) lower than the hazard for questions posted on a weekday, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer is 24.5\% (95\% CI (19.3\%, 29.3\%)) lower for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 154.1\% (95\% CI (131.5\%, 180.0\%)) higher for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer for questions posted on a weekend is 12.5\% (95\% CI (6.7\%, 18.0\%)) lower than the hazard for questions posted on a weekday, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 24.5\% (95\% CI (19.3\%, 29.4\%)) lower for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
 \end{itemize}
@@
 
-Results and coefficients of the final model reveal how users can ask a question in order to decrease response time.
-Findings indicate that users should phrase the title in the form of a question, use correct grammar (e.g.
+Results and coefficients of the final model reveal how users can ask questions in order to decrease response time.
+Findings suggest that users should phrase the title in the form of a question, use correct grammar (e.g.
 punctuation and capitalization), include specific and concise tags, and post the question on a weekday.
 
-Regarding the model's weak predictive accuracy, it may be explained by limitations in the data.
+The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design.
 Many users asking a question incorrectly specified the device name (e.g.
-``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
+A user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
 Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic).
@@
 As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
-Allowing users to enter any device name or tag leaves room for user error.
+Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above.
 Instead, the CQA can restrict the tags or devices that users can include to a drop-down list.
@@
 To create the variables, the data was separated between answered and unanswered questions.
-For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the frequency, or proportion of times those words occurred among all answered questions' titles.
+For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the proportion of times those words occurred among all answered questions' titles, defined as the frequency.
 The same was performed for the data frame containing unanswered questions.
-``Frequently-used'' words in answered questions were defined as those that appeared in more than 1\% of all answered questions' titles, and appeared in more answered questions than in unanswered questions.
-To determine the latter, a ratio of frequencies, or proportions of times a word occurs, was assessed.
-The ratio was calculated as the proportion of time a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
+``Frequently-used'' words in answered questions were defined as those that appeared in 1\% or more of all answered questions' titles, and appeared in more answered questions than in unanswered questions.
+To determine the latter, a ratio of frequencies was assessed.
+The ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
 As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
 Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions.
-As there was some overlap between ``frequently-used'' words in each list and the device categories, every word that matched a device name was removed from the lists.
+As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
 The resulting list for answered questions contained 111 words.
@@
 
-This variable was created to investigate if questions with titles in the form of questions receive answers faster than those that do not \citep{Bhat2014}.
+This variable was created to investigate if questions with titles in the form of questions receive answers faster than those that do not \cite{Bhat2014}.
 
@@
 
-\subsubsection*{8.2.6 Average frequency ``score'' of a question's tags}
+\subsubsection*{8.2.6 Average tag frequency}
 
@@
 
-\subsubsection*{8.2.7 Average number of characters in a question's tags}
+\subsubsection*{8.2.7 Average tag length}
 
-This variable was created to capture when a user correctly or incorrectly used the tagging system.
-For example, question 390989 included the tag tag: “i need to repair the headset because i can not find the bluetoot”, which is 64 characters.
-Question 410254 includes tags "sound", "sound driver" and "speaker" and has an average of 8 characters per tag.
-It is hypothesized that questions with correctly defined tags, as with the latter example, have faster response times.
+This variable was created to investigate if questions with correctly defined tags have faster response times than questions that do not include tags or incorrectly use the tagging system.
+It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
 
@@
 
-\subsubsection*{8.2.8 Number of characters in the user-defined device title}
+\subsubsection*{8.2.8 Device name length}
 
-This variable was included to capture when a user incorrectly defines the device name.
-For example, the device variable for question 390271 is, “Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One”, and is 136 characters long.
-11 questions in the data also did not include any device title.
-This variable was created to investigate if questions with incorrectly defined device names make it difficult for the answering community to discern the question's topic, and thus have longer response times or remain unanswered.
+This variable was created to investigate if questions with correctly defind device names have faster response times than questions that do not include a name or are incorrectly defined.
+Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names make it difficult for the answering community to discern the question's topic, and thus have slower response times.
 
@@
 
-\subsubsection*{8.2.9 Ratio of the number of line breaks to the number of characters in a question's text}
+\subsubsection*{8.2.9 Line break to text length ratio}
 
-This variable was based on the hypothesis that questions that include line breaks in the text are easier to read than questions that don't include any, and thus have shorter response times.
+This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that don't include any, and thus have shorter response times.
 

### 2018-01-09 article/draft1.tex
proofread + revisions

@@
 
-\section*{Abstract}
+\section*{Abstract} % fix the hazard ratios!!!!
 
-Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced knowledge.
-Thousands of questions and answers are posted by users everyday.
+Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information.
 One such example of a CQA is iFixit's \textit{Answers} forum.
 This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users.
-A reliable measure of the health of these CQAs is question response time.
-Fast response times enhance user engagement and satisfaction and increase web traffic.
+An important aspect of these CQAs, for both users and the forum, is question response time.
 This paper presents a survival analysis of the time until a question receives its first answer.
-A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time.
+A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)).
 Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

### 2018-01-09 article/graphics.Rmd
commented out x$Answered
updated model, computed CI for hazard

@@
                     contain_unanswered + contain_answered + title_questionmark + 
-                   text_contain_punct + text_all_lower + update + prior_effort + day +
-                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 4) + rcs(log10(text_length), 5) +
-                   rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3), 
+                    text_contain_punct + text_all_lower + update + prior_effort + 
+                    day + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + 
+                    rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + 
+                    rcs(sqrt(newline_ratio), 3), 
                    data = x, 
@@
 model
-
 ```
@@
 # SE of all coefficients 
-se <- c(0.0476, 0.0904, 0.0784, 0.0830, 0.0697, 0.0555, 0.0597, 0.0815, 0.0695, 0.0364, 0.0340, 0.0422, 0.0332, 0.0499, 0.0645, 0.0857, 0.0362, 0.0331, 0.7196, 0.0309, 0.2661, 0.7231, 0.1856, 0.8452, 4.1706, 6.8975, 0.0714, 0.9724, 2.3149, 2.3255, 0.4776, 0.7265)
+se <- c(0.0476, 0.0904, 0.0784, 0.0830, 0.0697, 0.0555, 0.0597, 0.0815, 0.0695, 0.0364, 0.0340, 0.0422, 0.0332, 0.0499, 0.0645, 0.0857, 0.0362, 0.0331, 0.7204, 0.1856, 0.8452, 4.1705, 6.8973, 0.1062, 0.6381, 2.5243, 0.2496, 2.5575, 7.4036, 10.2644, 0.4776, 0.7266)
 
@@
 
-coefficientsdf
+# putting CI in percentage form 
+options(scipen = 99999)
+coefficientsdf$upper_p <- NA; coefficientsdf$lower_p <- NA
+
+upper <- coefficientsdf$upper > 1
+coefficientsdf$upper_p[upper == TRUE] <- (coefficientsdf$upper[upper == TRUE] - 1) * 100
+coefficientsdf$upper_p[upper == FALSE] <- (1 - coefficientsdf$upper[upper == FALSE]) * 100
+coefficientsdf$lower_p[upper == TRUE] <- (coefficientsdf$lower[upper == TRUE] - 1) * 100
+coefficientsdf$lower_p[upper == FALSE] <- (1 - coefficientsdf$lower[upper == FALSE]) * 100
 

### 2018-01-10 article/draft1.Rnw
minor revisions

@@
 An important aspect of these CQAs, for both users and the forum, is question response time.
-This paper presents a survival analysis of the time until a question receives its first answer.
+This paper presents a survival analysis of the time until a question receives it's first response.
 A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
@@
 Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)).
-Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.
+Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.
 
@@
 
-Community-driven online question and answer forums are becoming widely-used sources of information.
-These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month.
+Community-driven online question and answer forums have become widely-used sources of information.
+These online platforms feature thousands of user-posted questions and answers and receive millions of visits every month.
 The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
 Founded in 2003, iFixit's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to save money and reduce electronic waste.
-This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
+This company provides over 30,000 free online repair guides and sells specialized tools and parts needed for such repairs.
 
@@
 As thousands of users rely on this forum for information, it is important that users receive timely answers.
-Fast response times have been shown to be associated with user satisfaction and in turn increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
-Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask questions to minimize response times and for how the forum design can be improved.
+Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
+Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.
 
-However, analysis and prediction of response times on CQAs has not been thoroughly investigated.
+However, analysis and prediction of response times on CQAs have not been thoroughly investigated.
 There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality.
@@
 \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
-\cite{Blumenstock} also determined that textual features, e.g.
-word count, was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
+\cite{Blumenstock} also determined that textual features (e.g.
+word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
 \cite{H.fu} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
@@
 
-The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded).
+The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download).
 Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received.

### 2018-01-12 article/draft1.Rnw
combined table 1, removed percentiles table, univariate results table

@@
 
-% Table of categorical predictors
+% Table of derived predictors
 \begin{table}[!htbp]
 \centering
-\begin{tabular}{|p{10cm}|}
+\begin{tabular}{| p{2cm} | p{10cm} |}
   \hline
-  Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
-  If the question was posted on a weekend or on a weekday \\ \hline
-  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
-  Whether or not the question's text is in all lower case \\ \hline
-  Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \hline
-  Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \hline
-  Whether or not the question's title ends in a question mark \\ \hline
-  Whether or not the user edited or added information to the question's text after posting it \\ \hline
-  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
+  \multirow{9}{2cm}{Categorical Variables} & Device category the question pertains to.
+Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
+  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
+  & Whether or not the question's text contains any end punctuation marks (. ? !) \\ \cline{2-2}
+  & Whether or not the question's text is in all lower case \\ \cline{2-2}
+  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \cline{2-2}
+  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \cline{2-2}
+  & Whether or not the question's title ends in a question mark \\ \cline{2-2}
+  & Whether or not the user edited or added information to the question's text after posting it \\ \cline{2-2}
+  & Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
+  \multirow{5}{2cm}{Continuous Variables} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
+  & Average frequency for all of a question's tags.
+Frequency defined as the proportion of times a tag appears in all of the data.
+Questions without tags were assigned a value of 0 (Average tag frequency) \\ \cline{2-2}
+  & Number of characters in the question's text (Text length) \\ \cline{2-2}
+  & Number of characters in the user-defined device name (Device name length) \\ \cline{2-2}
+  & Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
 \end{tabular}
-\caption{Categorical variables derived}
-\label{table:categorical}
-\end{table}
-
-% Table of quantitative predictors
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{|p{10cm}|}
-  \hline
-  Average number of characters in each question's tags (Average tag length) \\ \hline
-  Average frequency for all of a question's tags.
-Frequency defined as the proportion of times a tag appears in all of the data.
-Questions without tags were assigned a value of 0 (Average tag frequency) \\ \hline
-  Number of characters in the question's text (Text length) \\ \hline
-  Number of characters in the user-defined device name (Device name length) \\ \hline
-  Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
-\end{tabular}
-\caption{Continuous variables derived}
-\label{table:continuous}
+\caption{Categorical and Continuous variables derived}
+\label{table:variables}
 \end{table}
@@
 See Appendix for examples of answered and unanswered questions.
-Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}.
+Variables derived can be found in Table \ref{table:variables}.
 See Appendix for more details on variable derivation.
@@
 Questions analyzed were restricted to those posted in English.
-The time until event variable used in survival analysis was defined as the time since posting until a question receives its first answer.
+The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
@@
 Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
-Each predictor was entered into univarite Cox models and strength of association with response times was assessed.
-Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model.
+Each predictor was entered into univariate Cox models and strength of association with response times was assessed.
+Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.
 Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model.
@@
 In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
-To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
+To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
 The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
@@
 The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
-The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}.
+The p-value for this statistic was calculated from the $chi^2$ distribution \cite{Oakes1981}.
 Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability.
-Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio.
+Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard.
 Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
@@
 Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}.
-Significant correlations would indicate that a predictor has violated this assumption.
+Significant correlations would indicate a predictor has violated this assumption.
 
-To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R.
+To compute predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R.
 This function uses the Cox model and a vector of times to compute predicted survival probabilities.
@@
 
-  Of 8,025 questions in the full data set, \Sexpr{format(nrow(x), big.mark = ",")} were in English (97\% of the full data).
+  Of 8,025 questions in the full data, \Sexpr{format(nrow(x), big.mark = ",")} were in English (97\% of the full data).
 Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date.
@@
 
-% Table of percentiles 
-\begin{table}[!h]
-\centering
-\begin{tabular}{| l | l |}
-  \hline
- \textbf{Percent Answered} & \textbf{Time (hrs)} \\ 
-  \hline
-  25 & 0.88 \\ 
-  50 & 9.16 \\ 
-  55 & 18.38 \\ 
-  58 & 33.71 \\ 
-  60 & 59.47 \\ 
-  64 & 683.19 \\ 
-   \hline
-\end{tabular}
-\caption{Kaplan-Meier estimated quantiles of survival time}
-\label{table:quantiles}
-\end{table}
-
   Figure ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
@@
 The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.
-Table \ref{table:quantiles} provides additional percentiles of survival time.
 
-% Univariate analysis results
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
-  \hline
-  \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
-  \hline \hline
-  \multirow{ 3 }{ 5cm }{ Average tag frequency }
-  & Untransformed & 1.270620e-08 \\
-  & Log + 1 & 1.186521e-08 \\
-  & \textbf{*}Square root & 1.464184e-11 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Average tag length }
-  & Untransformed & 2.611529e-02 \\ 
-  & \textbf{*}Log + 1 & 6.018542e-05 \\
-  & Square root & 2.999917e-04 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Device name length }
-  & Untransformed & 6.530431e-03 \\
-  & \textbf{*}Log + 1 & 1.912977e-05 \\
-  & Square root & 2.291424e-04 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
-  & Untransformed & 1.398819e-07 \\
-  & Log + 1 & 1.092952e-07 \\
-  & \textbf{*}Square root & 1.148792e-11 \\ 
-  \multirow{ 3 }{ 5cm }{ Text length }
-  & Untransformed & 6.947221e-12 \\
-  & \textbf{*}Log & 0.000000e+00 \\
-  & Square root & 1.110223e-16 \\ \hline \hline
-  \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
-  \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
-  \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
-  \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
-\end{tabular}
-\caption{Univariate analysis results} 
-\label{table:univariate_results}
-\end{table}
+% % Univariate analysis results
+% \begin{table}[!htbp]
+% \centering
+% \begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
+%   \hline
+%   \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
+%   \hline \hline
+%   \multirow{ 3 }{ 5cm }{ Average tag frequency }
+%   & Untransformed & 1.270620e-08 \\
+%   & Log + 1 & 1.186521e-08 \\
+%   & \textbf{*}Square root & 1.464184e-11 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Average tag length }
+%   & Untransformed & 2.611529e-02 \\ 
+%   & \textbf{*}Log + 1 & 6.018542e-05 \\
+%   & Square root & 2.999917e-04 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Device name length }
+%   & Untransformed & 6.530431e-03 \\
+%   & \textbf{*}Log + 1 & 1.912977e-05 \\
+%   & Square root & 2.291424e-04 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
+%   & Untransformed & 1.398819e-07 \\
+%   & Log + 1 & 1.092952e-07 \\
+%   & \textbf{*}Square root & 1.148792e-11 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Text length }
+%   & Untransformed & 6.947221e-12 \\
+%   & \textbf{*}Log & 0.000000e+00 \\
+%   & Square root & 1.110223e-16 \\ \hline \hline
+%   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
+%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
+%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
+%   \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
+% \end{tabular}
+% \caption{Univariate analysis results} 
+% \label{table:univariate_results}
+% \end{table}
 
@@
 Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions, and each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
-Results of univariate analysis performed on one training set are shown in Table \ref{table:univariate_results}.
-For continuous predictors that contained zeros, one was added to each observation before applying log transformations.
-All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
+Univariate analysis performed on one training set indicated that all cateogorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
+All continuous predictors, except for device length and average tag length, also resulted in univariate p-values of less than 0.001.
+Applying either square root or log transformations to continuous variables resulted in univariate p-values of less than 0.001.
+For continuous predictors that contained zeros, one was added to each observation before applying the log transformation.
+The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
+All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.
 
@@
 \end{tabular}
-\caption{Performance Metrics} 
+\caption{Performance Metrics. HR: Hazard Ratio, LR: Partial Likelihood Ratio} 
 \label{table:cv}
@@
 \centering
-\begin{tabular}{|p{3.5cm} p{4cm}| c | l | c |}
+\begin{tabular}{|p{3cm} p{4cm}| c | c |}
   \hline
- \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{95\% CI} & \textbf{p-value} \\ \hline
-  \multirow{ 9 }{ 3.5 cm }{ Device Category } & Apple Product & \hl{0.9346} (0.0476) & & 0.000000e+00 \\ 
-  & Camera & -0.3199 (0.0476) & & \\ 
-  & Electronics & -0.0138 (0.0904) & & \\ 
-  & Game Console & 0.2458 (0.0784) & & \\ 
-  & Home & 0.3368 (0.0697) & & \\ 
-  & Other & -0.1304 (0.0555) & & \\ 
-  & PC & 0.2818 (0.0597) & & \\ 
-  & Tablet & -0.1566 (0.0815) & & \\ 
-  & Vehicle & 0.4056 (0.0695) & & \\ 
+ \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
+  \multirow{ 9 }{ 3 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
+  & Camera & -0.3199 (0.0476) & \\ 
+  & Electronics & -0.0138 (0.0904)  & \\ 
+  & Game Console & 0.2458 (0.0784)  & \\ 
+  & Home & 0.3368 (0.0697) &  \\ 
+  & Other & -0.1304 (0.0555)  & \\ 
+  & PC & 0.2818 (0.0597) &  \\ 
+  & Tablet & -0.1566 (0.0815)  & \\ 
+  & Vehicle & 0.4056 (0.0695)  & \\ 
   \hline
-  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & \hl{-0.1334} (0.0331) & & 5.525114e-05 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 6.204270e-01 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 6.065638e-03 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 2.604130e-01 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & \hl{-0.2808} (0.0340) & & 1.110223e-16 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & 9.880985e-15 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 5.027830e-04 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 3.300423e-03 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 4.534803e-02 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196) & & 1.679666e-03 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{3}{*}{Square root of average tag length} } & -0.0814 (0.0309) & & \\
-  & & 0.5945 (0.2661) & & \\
-  & & -1.5879 (0.7231) & & \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of text length} } & -0.0619 (0.1856) & & \\
-  & & -0.5052 (0.8452) & & \\
-  & & 2.9957 (4.1706) & & \\
-  & & -4.4755 (6.8975) & & \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of device name length} } & -0.0488 (0.0714) & & \\
-  & & -0.4348 (0.9724) & & \\
-  & & 1.2208 (2.3149) & & \\
-  & & -1.3199 (2.3255) & & \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{2}{*}{Square root of line break to text length ratio} } & -0.0076 (0.4776) & & \\
-  & & 0.4345 (0.7265) & & \\ \hline
+  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331)  & <0.0001 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & 0.6127 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) &  0.0060 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) &  0.2596 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340)  & <0.0001 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) &  <0.0001 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857)  & 0.0005 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364)  & 0.0031 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362)  & 0.0448 \\ \hline
+  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196)  & 0.0020 \\ \hline
 \end{tabular} 
-\caption{Coefficients for predictors in the final model} 
+\caption{Coefficients for predictors in the final model.Continous predictors with restricted cubic splines are not shown. } 
 \label{table:coefficients}

### 2018-01-12 article/draft1.tex
combined table 1, removed percentiles table, univariate results table

@@
 
-  Of 8,025 questions in the full data set, 7,760 were in English (97\% of the full data).
+  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
 Of those questions, 4,951 (63.8}\%) received an answer by the download date.
@@
 The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
-Table \ref{table:quantiles} provides additional percentiles of survival time.
 
-% Univariate analysis results
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
-  \hline
-  \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
-  \hline \hline
-  \multirow{ 3 }{ 5cm }{ Average tag frequency }
-  & Untransformed & 1.270620e-08 \\
-  & Log + 1 & 1.186521e-08 \\
-  & \textbf{*}Square root & 1.464184e-11 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Average tag length }
-  & Untransformed & 2.611529e-02 \\ 
-  & \textbf{*}Log + 1 & 6.018542e-05 \\
-  & Square root & 2.999917e-04 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Device name length }
-  & Untransformed & 6.530431e-03 \\
-  & \textbf{*}Log + 1 & 1.912977e-05 \\
-  & Square root & 2.291424e-04 \\ \hline
-  \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
-  & Untransformed & 1.398819e-07 \\
-  & Log + 1 & 1.092952e-07 \\
-  & \textbf{*}Square root & 1.148792e-11 \\ 
-  \multirow{ 3 }{ 5cm }{ Text length }
-  & Untransformed & 6.947221e-12 \\
-  & \textbf{*}Log & 0.000000e+00 \\
-  & Square root & 1.110223e-16 \\ \hline \hline
-  \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
-  \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
-  \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
-  \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
-  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
-\end{tabular}
-\caption{Univariate analysis results} 
-\label{table:univariate_results}
-\end{table}
+% % Univariate analysis results
+% \begin{table}[!htbp]
+% \centering
+% \begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
+%   \hline
+%   \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
+%   \hline \hline
+%   \multirow{ 3 }{ 5cm }{ Average tag frequency }
+%   & Untransformed & 1.270620e-08 \\
+%   & Log + 1 & 1.186521e-08 \\
+%   & \textbf{*}Square root & 1.464184e-11 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Average tag length }
+%   & Untransformed & 2.611529e-02 \\ 
+%   & \textbf{*}Log + 1 & 6.018542e-05 \\
+%   & Square root & 2.999917e-04 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Device name length }
+%   & Untransformed & 6.530431e-03 \\
+%   & \textbf{*}Log + 1 & 1.912977e-05 \\
+%   & Square root & 2.291424e-04 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
+%   & Untransformed & 1.398819e-07 \\
+%   & Log + 1 & 1.092952e-07 \\
+%   & \textbf{*}Square root & 1.148792e-11 \\ \hline
+%   \multirow{ 3 }{ 5cm }{ Text length }
+%   & Untransformed & 6.947221e-12 \\
+%   & \textbf{*}Log & 0.000000e+00 \\
+%   & Square root & 1.110223e-16 \\ \hline \hline
+%   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
+%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
+%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
+%   \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
+%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
+% \end{tabular}
+% \caption{Univariate analysis results} 
+% \label{table:univariate_results}
+% \end{table}
 
 Each training set contained 6,208 questions, and each test set contained 1,552 questions.
-Results of univariate analysis performed on one training set are shown in Table \ref{table:univariate_results}.
-For continuous predictors that contained zeros, one was added to each observation before applying log transformations.
-All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
+Univariate analysis performed on one training set indicated that all cateogorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
+All continuous predictors, except for device length and average tag length, also resulted in univariate p-values of less than 0.001.
+Applying either square root or log transformations to continuous variables resulted in univariate p-values of less than 0.001.
+For continuous predictors that contained zeros, one was added to each observation before applying the log transformation.
+The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
+All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.
 

### 2018-01-12 model fitting/univariate_analysis.Rmd
combined table 1, removed percentiles table, univariate results table

@@
 pvalues <- get_pvalue("weekday")
-pvalues <- get_pvalue("title_length")
 pvalues <- get_pvalue("text_length")
@@
 pvalues <- pvalues %>% arrange(pvalue)
+pvalues
 

### 2018-01-12 article/graphics.Rmd
removed table of percentiles

@@
 ggsave("kmcurve.pdf", width = 8, height = 5)
-```
-
-### Table of percentiles
-
-```{r}
-# 64% is largest available survival probability
-quantiles <- quantile(KM, c(0.25, 0.50, 0.55, 0.58, 0.60, 0.64))$quantile 
-quantilesdf <- data.frame(Percent = names(quantiles), 
-                          Time = round(quantiles, 2))
-colnames(quantilesdf) <- c(paste("Percent", "\n", "Answered", sep = ""), "Time (hours)")
-rownames(quantilesdf) <- NULL
-
-xtable::xtable(quantilesdf, label = "table:quantile")
 ```
@@
 
+options(scipen = 99999)
 univ_results <- univ_results %>% arrange(pvalue)
-
-xtable::xtable(x = univ_results, 
-               caption = "Univariate analysis results", 
-               label = "table:qresults")
 

### 2018-01-13 article/draft1.Rnw
discussed final model statistics in text, reformatted table of questions

@@
 \usepackage{color,soul}
+
+\usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
 \begin{document}
@@
 
-% Final model statistics
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{| r | r |}
-  \hline
-  \textbf{LR} & 1265.291 \\ \hline
-  \textbf{p-value} & 0 \\ \hline
-  \textbf{$R^2$} & 0.150 \\ \hline
-  \textbf{\textit{Dxy}} & 0.267 \\ \hline
-\end{tabular}
-\caption{Final model statistics} 
-\label{table:final model}
-\end{table}
-
 Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
 
-Interpretations of the coefficients highlighted in Table \ref{table:coefficients}:
+The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value = 0). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
+
+The following are interpretations of select hazard coefficients in Table \ref{table:coefficients}.
+Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not received an answer by that time.
 
@@
 \end{itemize}
-
-See Table \ref{table:coefficients} for the full list of model coefficients. Table \ref{table:final model} displays statistics for the final model.
 
@@
 This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-Special thanks goes to iFixit for providing access to the CQA data and for the help and assistance in its analysis.
+We also thank iFixit for providing access to the CQA data and for analysis assistance.
 
@@
 % unanswered question id = 399971
-% Table to display questions
+
 \begin{table}[!htbp]
 \centering
-\begin{tabular}{| l | l | p{6cm} | l |}
+\begin{tabular}{|L{7cm}|L{7cm}|}
 \hline
- \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\
-  \hline
-  Yes & iPhone 6 & iPhone water damage, touch screen issue &  2017-05-10 21:50:48 GMT \\ \cline{2 - 4}
-  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
-  & Yes & So I dropped my iPhone in water 4 days ago.
+\textbf{Device} & iPhone 6 \\ \hline
+\textbf{Title} & iPhone water damage, touch screen issue \\ \hline
+\textbf{Text} & So I dropped my iPhone in water 4 days ago.
 Have done the whole rice thing and seen huge difference in it.
@@
 What would be the best way forward?
-& 2017-05-10 23:12:27 GMT \\ \cline{4 - 4}
-  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
-  & & & 1.361 \\ \cline{4-4} \hline \hline
-  \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\ \cline{1 - 4}
-  No & android tablet & ccccaaaan you help me fix my touch screen & 2017-05-23 07:35:12 GMT \\ \cline{2 - 4}
-  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
-  & No & touch screen not worki & NA \\ \cline{4 - 4}
-  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
-  & & & NA \\ 
-   \hline
+\\ \hline
+\textbf{Tags} & touchscreen, water damage \\ \hline
+\textbf{Response Time (hrs)} & 1.361 \\ \hline 
+\textbf{Device Category} & Apple Product \\ \hline
+\textbf{Day Posted} & Weekday \\ \hline
+\textbf{Text length (characters)} & 241 \\ \hline
+\textbf{Device name length (characters)} & 8 \\ \hline
+\textbf{Average tag length (characters)} & 11.5 \\ \hline
+\textbf{Title end in a question mark?} & False \\ \hline
+\textbf{Text in all lower case?} & False \\ \hline
+\textbf{Text contain end punctuation?} & True \\ \hline
+\textbf{User update question after posting?} & False \\ \hline
+\textbf{User indicate prior effort?} & False \\ \hline
+\textbf{Line break to text length ratio} & 0 \\ \hline
+\textbf{Average tag frequency} & 0.0097 \\ \hline
+\textbf{Frequently-used answered words?} & True \\ \hline
+\textbf{Frequently-used unanswered words?} & False \\ \hline \hline
+% next question
+\textbf{Device} & android tablet \\ \hline
+\textbf{Title} & ccccaaaan you help me fix my touch screen \\ \hline
+\textbf{Text} & touch screen not worki \\ \hline
+\textbf{Tags} & NA \\ \hline
+\textbf{Response Time (hrs)} & NA \\ \hline 
+\textbf{Device Category} & Tablet \\ \hline
+\textbf{Day Posted} & Weekday \\ \hline
+\textbf{Text length (characters)} & 81 \\ \hline
+\textbf{Device name length (characters)} & 18 \\ \hline
+\textbf{Average tag length (characters)} & 47 \\ \hline
+\textbf{Title end in a question mark?} & False \\ \hline
+\textbf{Text in all lower case?} & True \\ \hline
+\textbf{Text contain end punctuation?} & False \\ \hline
+\textbf{User update question after posting?} & False \\ \hline
+\textbf{User indicate prior effort?} & False \\ \hline
+\textbf{Line break to text length ratio} & 0 \\ \hline
+\textbf{Average tag frequency} & 0 \\ \hline
+\textbf{Frequently-used answered words?} & True \\ \hline
+\textbf{Frequently-used unanswered words?} & True \\ \hline \hline
 \end{tabular}
-\caption{Answered and unanswered questions}
+\caption{Answered and Unanswered questions}
 \label{table:questions}
@@
 \centering
-\begin{tabular}{|p{4cm}|p{8cm}|}
+\begin{tabular}{|L{4cm}|p{8cm}|}
   \hline

### 2018-01-13 article/draft1.tex
discussed final model statistics in text, reformatted table of questions

@@
 \usepackage{color,soul}
+
+\usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
 \usepackage{Sweave}

### 2018-01-14 article/draft1.Rnw
reformated tables of splines and final model results, changed rounding in table of metrics

@@
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
+\usepackage{caption}
 
@@
 
-\section*{Abstract} % fix the hazard ratios!!!!
+\section*{Abstract}
 
@@
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))).
 Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.
@@
 However, analysis and prediction of response times on CQAs have not been thoroughly investigated.
-There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality.
-This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict the survival probability of a question.
+There is need for further analysis of forum response times, as the majority of existing research focuses on assessing and predicting question or answer quality.
+This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict survival probabilities of questions.
 
@@
 \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered.
-All research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
+Howerver, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
 The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
@@
 \centering
-\begin{tabular}{| p{2cm} | p{10cm} |}
+\begin{tabular}{| L{2cm} | L{10cm} |}
   \hline
-  \multirow{9}{2cm}{Categorical Variables} & Device category the question pertains to.
+  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to.
 Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
   & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
-  & Whether or not the question's text contains any end punctuation marks (. ? !) \\ \cline{2-2}
-  & Whether or not the question's text is in all lower case \\ \cline{2-2}
-  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \cline{2-2}
-  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \cline{2-2}
-  & Whether or not the question's title ends in a question mark \\ \cline{2-2}
-  & Whether or not the user edited or added information to the question's text after posting it \\ \cline{2-2}
-  & Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
-  \multirow{5}{2cm}{Continuous Variables} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
+  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
+  & If the question's text is in all lower case \\ \cline{2-2}
+  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
+  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
+  & If the question's title ends in a question mark \\ \cline{2-2}
+  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
+  & If the user made an effort to solve the problem prior to asking the question \\ \hline
+  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
   & Average frequency for all of a question's tags.
@@
 \end{tabular}
-\caption{Categorical and Continuous variables derived}
+\caption{Categorical and continuous variables derived}
 \label{table:variables}
@@
 The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download).
-Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received.
-See Appendix for examples of answered and unanswered questions.
+Variables in the data included: device name and category, title, text, tags, If the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received.
+See Appendix for an example of an answered and unanswered question.
 Variables derived can be found in Table \ref{table:variables}.
-See Appendix for more details on variable derivation.
+See Appendix for details on variable derivation.
 
@@
 From these estimates, survival curves were constructed to examine the survival experience of questions.
-Mean, median and other percentiles of survival times were also generated.
+Mean and median survival times were also generated.
 
@@
 All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
-No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.
+No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
 
@@
 
-% % Univariate analysis results
-% \begin{table}[!htbp]
-% \centering
-% \begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
-%   \hline
-%   \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
-%   \hline \hline
-%   \multirow{ 3 }{ 5cm }{ Average tag frequency }
-%   & Untransformed & 1.270620e-08 \\
-%   & Log + 1 & 1.186521e-08 \\
-%   & \textbf{*}Square root & 1.464184e-11 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Average tag length }
-%   & Untransformed & 2.611529e-02 \\ 
-%   & \textbf{*}Log + 1 & 6.018542e-05 \\
-%   & Square root & 2.999917e-04 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Device name length }
-%   & Untransformed & 6.530431e-03 \\
-%   & \textbf{*}Log + 1 & 1.912977e-05 \\
-%   & Square root & 2.291424e-04 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
-%   & Untransformed & 1.398819e-07 \\
-%   & Log + 1 & 1.092952e-07 \\
-%   & \textbf{*}Square root & 1.148792e-11 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Text length }
-%   & Untransformed & 6.947221e-12 \\
-%   & \textbf{*}Log & 0.000000e+00 \\
-%   & Square root & 1.110223e-16 \\ \hline \hline
-%   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
-%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
-%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
-%   \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
-% \end{tabular}
-% \caption{Univariate analysis results} 
-% \label{table:univariate_results}
-% \end{table}
-
 << echo = FALSE >>=
@@
 
-train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
-train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
-train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
-train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
-train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
+train1 <- x[splitPlan[[1]]$train, ]
+test1 <- x[splitPlan[[1]]$app, ]
 @
 
-Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions, and each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
-Univariate analysis performed on one training set indicated that all cateogorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
-All continuous predictors, except for device length and average tag length, also resulted in univariate p-values of less than 0.001.
-Applying either square root or log transformations to continuous variables resulted in univariate p-values of less than 0.001.
-For continuous predictors that contained zeros, one was added to each observation before applying the log transformation.
+Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions.
+Each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
+Univariate analysis performed on one training set indicated that all categorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
+Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001.
+Applying either square root or log transformations resulted in univariate p-values of less than 0.001.
+For those that contained zeros, one was added to each observation before applying the log transformation.
 The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
@@
 \centering
-\begin{tabular}{| p{5cm} | l | l |}
+\begin{tabular}{| L{5cm} | l | l |}
   \hline
   \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
+  & \textbf{*}0 & 65890.75 \\ 
+  & 5 & 65891.69 \\ 
+  & 4 & 65891.75 \\ 
+  & 3 & 65892.35 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
+  & 0 & 65920.24 \\ 
+  & 5 & 65911.20 \\ 
+  & \textbf{*}4 & 65910.81 \\ 
+  & 3 & 65914.98 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
+  & 0 & 65918.06 \\ 
+  & \textbf{*}5 & 65847.34 \\ 
+  & 4 & 65880.89 \\ 
+  & 3 & 65898.00 \\ 
+  \hline
+  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
+  & 0 & 65890.28 \\ 
+  & 5 & 65884.70 \\ 
+  & 4 & 65882.98 \\ 
+  & \textbf{*}3 & 65881.93 \\ 
   \hline
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
-  & 0 & 65890.28 \\ 
-  & 5 & 65884.70 \\ 
-  & 4 & 65882.98 \\ 
-  & \textbf{*}3 & 65881.93 \\ 
-  \hline
-  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
-  & \textbf{*}0 & 65890.75 \\ 
-  & 5 & 65891.69 \\ 
-  & 4 & 65891.75 \\ 
-  & 3 & 65892.35 \\ 
-  \hline
-  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
-  & 0 & 65918.06 \\ 
-  & \textbf{*}5 & 65847.34 \\ 
-  & 4 & 65880.89 \\ 
-  & 3 & 65898.00 \\ 
-  \hline
-  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
-  & 0 & 65920.24 \\ 
-  & 5 & 65911.20 \\ 
-  & \textbf{*}4 & 65910.81 \\ 
-  & 3 & 65914.98 \\ 
-   \hline
 \end{tabular}
-\caption{Determining the optimal k number of splines for each predictor} 
+\caption{Determining the optimal k number of splines for each continuous predictor} 
 \label{table:splines}
@@
   \hline
-  \textbf{Training Sets} & 2.027030 & 937.3877 & 0.0000 & 0.1401511 & 0.2683734 & 0.6341867 \\ 
-  \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
-  \textbf{Full Data} & 2.028051 & 1165.0321 & 0.0000 & 0.1394092 & 0.2672884 & 0.6336442 \\ 
+  \textbf{Training Sets} & 2.03 & 937.39 & 0 & 0.14 & 0.27 & 0.63 \\ 
+  \textbf{Test Sets} & 1.99 & 220.83 & 0 & 0.14 & 0.26 & 0.63 \\
+  \textbf{Full Data} & 2.03 & 1165.03 & 0 & 0.14 & 0.28 & 0.63 \\ 
    \hline
 \end{tabular}
-\caption{Performance Metrics. HR: Hazard Ratio, LR: Partial Likelihood Ratio} 
+\caption{Performance Metrics. \\ HR: Hazard Ratio, LR: Partial Likelihood Ratio} 
 \label{table:cv}
@@
 \centering
-\begin{tabular}{|p{3cm} p{4cm}| c | c |}
+\begin{tabular}{|l L{4cm}| c | c |}
   \hline
  \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
-  \multirow{ 9 }{ 3 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
+  Device Category & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
                   & Camera & -0.3199 (0.0476) & \\ 
@@
                   & Tablet & -0.1566 (0.0815)  & \\ 
-  & Vehicle & 0.4056 (0.0695)  & \\ 
-  \hline
-  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331)  & <0.0001 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & 0.6127 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) &  0.0060 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) &  0.2596 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340)  & <0.0001 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) &  <0.0001 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857)  & 0.0005 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364)  & 0.0031 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362)  & 0.0448 \\ \hline
-  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196)  & 0.0020 \\ \hline
+                  & Vehicle & 0.4056 (0.0695)  & \\ \hline
+  \multicolumn{2}{|l|}{Weekend or weekday} & -0.1334 (0.0331)  & <0.0001 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the question's text contains end punctuation marks} & 0.0247 (0.0499) & 0.6127 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the question's text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the question's title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the user edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the user had been a member for less than one day before posting the question} & -0.1069 (0.0364)  & 0.0031 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{If the user made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
 \end{tabular} 
-\caption{Coefficients for predictors in the final model.Continous predictors with restricted cubic splines are not shown. } 
+\caption{Coefficients for predictors in the final model. Continous predictors fit with restricted cubic splines are not shown.} 
 \label{table:coefficients}
@@
 The following are interpretations of select hazard coefficients in Table \ref{table:coefficients}.
-Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not received an answer by that time.
+Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
 
@@
 The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design.
-Many users asking a question incorrectly specified the device name (e.g.
+Many users incorrectly specified the device name (e.g.
 A user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
@@
 The CQA can also include more tips to guide users asking questions.
-Establishing and implementing a more restrictive framework for asking questions can help users ask understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
+Implementing a more restrictive framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
 
@@
 
-\section*{7. Acknowledgement}
+\section*{7. Acknowledgements}
 
@@
 \textbf{Frequently-used answered words?} & True \\ \hline
-\textbf{Frequently-used unanswered words?} & True \\ \hline \hline
+\textbf{Frequently-used unanswered words?} & True \\ \hline
 \end{tabular}
-\caption{Answered and Unanswered questions}
+\caption{Answered and unanswered questions}
 \label{table:questions}
@@
 
-\subsubsection*{8.2.1 Device Categorization}
+\subsubsection*{8.2.1 Average tag frequency}
+
+This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
+This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
+If a question has a higher average, than at least one of its tags are considered frequently-used.
+This variable was created based off of findings from \cite{Bhat2014}.
+
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.2 Average tag length}
+
+This variable was created to investigate if questions with correctly defined tags have faster response times than questions that do not include tags or incorrectly use the tagging system.
+It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
+
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.3 Device Categorization}
 
@@
 
-\subsubsection*{8.2.2 Whether or not the question's text contained at least one end punctuation mark}
+\subsubsection*{8.2.4 Device name length}
+
+This variable was created to investigate if questions with correctly defind device names have faster response times than questions that do not include a name or are incorrectly defined.
+Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names make it difficult for the answering community to discern the question's topic, and thus have slower response times.
+
+% ------------------------------------------------------------------------
+
+\subsubsection*{8.2.6 If the question's text contains end punctuation marks}
 
@@
 
-\subsubsection*{8.2.3 Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}
+\subsubsection*{8.2.7 If the question's title contains terms considered frequently-used among answered/unanswered questions}
 
@@
 
-% Table with list of frequently used words
+% Table with list of frequently-used words
 \begin{table}[!htbp]
 \centering
-\begin{tabular}{|L{4cm}|p{8cm}|}
+\begin{tabular}{|L{4cm}|L{8cm}|}
   \hline
@@
 
-\subsubsection*{8.2.4 Whether or not the question's title ended in a question mark}
+\subsubsection*{8.2.8 If the question's title ends in a question mark}
 
@@
 
-\subsubsection*{8.2.5 Whether or not the user made an effort to solve the problem on their own, prior to asking the question}
+\subsubsection*{8.2.9 If the user made an effort to solve the problem prior to asking the question}
 
@@
 
-\subsubsection*{8.2.6 Average tag frequency}
-
-This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
-This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
-If a question has a higher average, than at least one of it's tags are frequently used.
-This variable was created based off of findings from \cite{Bhat2014}.
-
-% ------------------------------------------------------------------------
-
-\subsubsection*{8.2.7 Average tag length}
-
-This variable was created to investigate if questions with correctly defined tags have faster response times than questions that do not include tags or incorrectly use the tagging system.
-It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
-
-% ------------------------------------------------------------------------
-
-\subsubsection*{8.2.8 Device name length}
-
-This variable was created to investigate if questions with correctly defind device names have faster response times than questions that do not include a name or are incorrectly defined.
-Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names make it difficult for the answering community to discern the question's topic, and thus have slower response times.
-
-% ------------------------------------------------------------------------
-
-\subsubsection*{8.2.9 Line break to text length ratio}
+\subsubsection*{8.2.5 Line break to text length ratio}
 

### 2018-01-14 article/draft1.tex
reformated tables of splines and final model results, changed rounding in table of metrics

@@
 Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))).
 Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.
@@
 
-% % Univariate analysis results
-% \begin{table}[!htbp]
-% \centering
-% \begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
-%   \hline
-%   \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
-%   \hline \hline
-%   \multirow{ 3 }{ 5cm }{ Average tag frequency }
-%   & Untransformed & 1.270620e-08 \\
-%   & Log + 1 & 1.186521e-08 \\
-%   & \textbf{*}Square root & 1.464184e-11 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Average tag length }
-%   & Untransformed & 2.611529e-02 \\ 
-%   & \textbf{*}Log + 1 & 6.018542e-05 \\
-%   & Square root & 2.999917e-04 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Device name length }
-%   & Untransformed & 6.530431e-03 \\
-%   & \textbf{*}Log + 1 & 1.912977e-05 \\
-%   & Square root & 2.291424e-04 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
-%   & Untransformed & 1.398819e-07 \\
-%   & Log + 1 & 1.092952e-07 \\
-%   & \textbf{*}Square root & 1.148792e-11 \\ \hline
-%   \multirow{ 3 }{ 5cm }{ Text length }
-%   & Untransformed & 6.947221e-12 \\
-%   & \textbf{*}Log & 0.000000e+00 \\
-%   & Square root & 1.110223e-16 \\ \hline \hline
-%   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
-%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
-%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
-%   \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
-%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
-% \end{tabular}
-% \caption{Univariate analysis results} 
-% \label{table:univariate_results}
-% \end{table}
-
-Each training set contained 6,208 questions, and each test set contained 1,552 questions.
-Univariate analysis performed on one training set indicated that all cateogorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
-All continuous predictors, except for device length and average tag length, also resulted in univariate p-values of less than 0.001.
-Applying either square root or log transformations to continuous variables resulted in univariate p-values of less than 0.001.
-For continuous predictors that contained zeros, one was added to each observation before applying the log transformation.
+Each training set contained 6,208 questions.
+Each test set contained 1,552 questions.
+Univariate analysis performed on one training set indicated that all categorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
+Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001.
+Applying either square root or log transformations resulted in univariate p-values of less than 0.001.
+For those that contained zeros, one was added to each observation before applying the log transformation.
 The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.

### 2018-01-14 article/graphics.Rmd
added data frame of final model hazard, SE, CI

@@
 # ------------------------------------------
-# data frame with coefficients, HR and confidence intervals
+# df with coefficients, HR and confidence intervals
 # SE of all coefficients 
@@
                              beta = as.numeric(unname(model$coefficients)),
-                             SE = se,
-                             HR = exp(coefficientsdf$beta),
-                             upper = exp(coefficientsdf$beta + (1.96*coefficientsdf$SE)),
-                             lower = exp(coefficientsdf$beta - (1.96*coefficientsdf$SE))
+                             SE = se
                              )
+coefficientsdf$HR <- exp(coefficientsdf$beta)
+coefficientsdf$upper <- exp(coefficientsdf$beta + (1.96 * coefficientsdf$SE))
+coefficientsdf$lower <- exp(coefficientsdf$beta - (1.96*coefficientsdf$SE))
 
@@
 final_metrics
-xtable::xtable(final_metrics, caption = "Performance metrics for model fit to the full data", label = "table:finalmetrics", digits = 4)
 
@@
 ph_test
-
 ```

### 2018-01-14 article/draft1.Rnw
spell checked

@@
 \usepackage{color,soul}
-
 \usepackage{array}
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
 \usepackage{caption}
@@
 A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
-Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
+Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
 Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))).
-Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.
+Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
 
@@
 \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered.
-Howerver, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
+However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
 The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
@@
 
-As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}.
+As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}.
 To build the model, five-fold cross-validation was used \cite{Rodriguez2010}.
@@
 AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}.
-All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
+All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
 No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
@@
 The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
-Signficant results from this model would indicate high predictive accuracy.
+Significant results from this model would indicate high predictive accuracy.
 The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
@@
 Each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
-Univariate analysis performed on one training set indicated that all categorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
+Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001.
 Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001.
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
+  \multirow{4}{5 cm}{Square root transformation of the average tag frequency} 
   & \textbf{*}0 & 65890.75 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
+  \multirow{4}{5 cm}{Log transformation of average tag length + 1}
   & 0 & 65920.24 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
+  \multirow{4}{5 cm}{Log transformation of device name length + 1}
   & 0 & 65918.06 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
+  \multirow{4}{5 cm}{Square root transformation of line breaks to text length ratio}
   & 0 & 65890.28 \\ 
@@
   \hline
-  \multirow{ 4 }{ 5cm }{ Log transformation of text length } 
+  \multirow{4}{5cm}{Log transformation of text length} 
   & 0 & 65862.83 \\ 
@@
 Average performance metrics for test and training sets are in Table \ref{table:cv}.
-Partial likelihood ratios and p-values indicate that the model as a whole is signficantly associated with response time.
+Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time.
 However, $R^2$ statistics and discrimination indexes are considerably low.
 Metrics for the final model's performance on the full data, also found in Table \ref{table:cv}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
-Results for training, test, and the full data did not change significantly, indicating that the model was not overfit.
+Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
 
@@
 \end{tabular} 
-\caption{Coefficients for predictors in the final model. Continous predictors fit with restricted cubic splines are not shown.} 
+\caption{Coefficients for predictors in the final model. Continuous predictors fit with restricted cubic splines are not shown.} 
 \label{table:coefficients}
@@
 This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be signficant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a questionmark.
-While overall the model was signficant, its predictive performance was considerably low.
+Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
+While overall the model was significant, its predictive performance was considerably low.
 
@@
 Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.
-For questions with missing categories, key words were searched for in device titles to recategorize accordingly.
+For questions with missing categories, key words were searched for in device titles to re-categorize accordingly.
 All other questions with ambiguous device titles were categorized as Other.
@@
 
-This variable was created to investigate if questions with correctly defind device names have faster response times than questions that do not include a name or are incorrectly defined.
+This variable was created to investigate if questions with correctly defined device names have faster response times than questions that do not include a name or are incorrectly defined.
 Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names make it difficult for the answering community to discern the question's topic, and thus have slower response times.
@@
 These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not.
-Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than qustions that do not.
+Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not.
 This variable was created based off of methods from \cite{Correa2013} and \cite{Ravi2014}.
@@
 To determine the latter, a ratio of frequencies was assessed.
-The ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions.
+The ratio was calculated as the proportion of times a word occurred among answered questions, to the proportion of times a word occurred in unanswered questions.
 As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
@@
   \hline
- \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
+ \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, LCD, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
   \hline

### 2018-01-14 article/draft1.tex
spell checked

@@
 A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
-Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$).
+Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$).
 Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))).
-Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.
+Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
 
@@
 Each test set contained 1,552 questions.
-Univariate analysis performed on one training set indicated that all categorical predictors were signficant with partial likelihood ratio p-values of less than 0.001.
+Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001.
 Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001.

### 2018-01-16 article/draft1.tex
reformatted table 5

@@
                   & Vehicle & 0.4056 (0.0695)  & \\ \hline
-  \multicolumn{2}{|l|}{Weekend or weekday} & -0.1334 (0.0331)  & <0.0001 \\ \hline
   \multicolumn{2}{|L{7.5cm}|}{If the question's text contains end punctuation marks} & 0.0247 (0.0499) & 0.6127 \\ \hline
@@
   \multicolumn{2}{|L{7.5cm}|}{If the user made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
+  \multicolumn{2}{|l|}{Weekend or weekday} & -0.1334 (0.0331)  & <0.0001 \\ \hline
   \multicolumn{2}{|L{7.5cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
@@
 \centering
-\begin{tabular}{|L{7cm}|L{7cm}|}
+\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
 \hline
-\textbf{Device} & iPhone 6 \\ \hline
-\textbf{Title} & iPhone water damage, touch screen issue \\ \hline
+\textbf{Device} & iPhone 6 & android tablet \\ \hline
+\textbf{Title} & iPhone water damage, touch screen issue & ccccaaaan you help me fix my touch screen \\ \hline
 \textbf{Text} & So I dropped my iPhone in water 4 days ago.
@@
 What would be the best way forward?
-\\ \hline
-\textbf{Tags} & touchscreen, water damage \\ \hline
-\textbf{Response Time (hrs)} & 1.361 \\ \hline 
-\textbf{Device Category} & Apple Product \\ \hline
-\textbf{Day Posted} & Weekday \\ \hline
-\textbf{Text length (characters)} & 241 \\ \hline
-\textbf{Device name length (characters)} & 8 \\ \hline
-\textbf{Average tag length (characters)} & 11.5 \\ \hline
-\textbf{Title end in a question mark?} & False \\ \hline
-\textbf{Text in all lower case?} & False \\ \hline
-\textbf{Text contain end punctuation?} & True \\ \hline
-\textbf{User update question after posting?} & False \\ \hline
-\textbf{User indicate prior effort?} & False \\ \hline
-\textbf{Line break to text length ratio} & 0 \\ \hline
-\textbf{Average tag frequency} & 0.0097 \\ \hline
-\textbf{Frequently-used answered words?} & True \\ \hline
-\textbf{Frequently-used unanswered words?} & False \\ \hline \hline
-% next question
-\textbf{Device} & android tablet \\ \hline
-\textbf{Title} & ccccaaaan you help me fix my touch screen \\ \hline
-\textbf{Text} & touch screen not worki \\ \hline
-\textbf{Tags} & NA \\ \hline
-\textbf{Response Time (hrs)} & NA \\ \hline 
-\textbf{Device Category} & Tablet \\ \hline
-\textbf{Day Posted} & Weekday \\ \hline
-\textbf{Text length (characters)} & 81 \\ \hline
-\textbf{Device name length (characters)} & 18 \\ \hline
-\textbf{Average tag length (characters)} & 47 \\ \hline
-\textbf{Title end in a question mark?} & False \\ \hline
-\textbf{Text in all lower case?} & True \\ \hline
-\textbf{Text contain end punctuation?} & False \\ \hline
-\textbf{User update question after posting?} & False \\ \hline
-\textbf{User indicate prior effort?} & False \\ \hline
-\textbf{Line break to text length ratio} & 0 \\ \hline
-\textbf{Average tag frequency} & 0 \\ \hline
-\textbf{Frequently-used answered words?} & True \\ \hline
-\textbf{Frequently-used unanswered words?} & True \\ \hline
+& touch screen not worki\\ \hline
+\textbf{Tags} & touchscreen, water damage & NA\\ \hline
+\textbf{Response Time (hrs)} & 1.361 & NA \\ \hline 
+\textbf{Device Category} & Apple Product & Tablet \\ \hline
+\textbf{Day Posted} & Weekday & Weekday \\ \hline
+\textbf{Text length (characters)} & 241 & 81 \\ \hline
+\textbf{Device name length (characters)} & 8 & 18\\ \hline
+\textbf{Average tag length (characters)} & 11.5 & 47 \\ \hline
+\textbf{Average tag frequency} & 0.0097 & 0 \\ \hline
+\textbf{Text contain end punctuation?} & True & False \\ \hline
+\textbf{Text in all lower case?} & False & True \\ \hline
+\textbf{Title end in a question mark?} & False & False \\ \hline
+\textbf{Line break to text length ratio} & 0 & 0 \\ \hline
+\textbf{User indicate prior effort?} & False & False \\ \hline
+\textbf{User update question after posting?} & False & False \\ \hline
+\textbf{Frequently-used answered words?} & True & True \\ \hline
+\textbf{Frequently-used unanswered words?} & False & False \\ \hline
 \end{tabular}

### 2018-01-22 article/draft1.tex
edits from Shannon

--- 2018-01-14 article/draft1.tex
@@
 This paper presents a survival analysis of the time until a question receives it's first response.
-A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
+A Cox proportional hazards model was developed to identify variables associated with response time.
 Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$).
@@
 \cite{H.fu} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
-A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}.
+A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
 The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.
@@
   & If the user made an effort to solve the problem prior to asking the question \\ \hline
-  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
-  & Average frequency for all of a question's tags.
-Frequency defined as the proportion of times a tag appears in all of the data.
-Questions without tags were assigned a value of 0 (Average tag frequency) \\ \cline{2-2}
-  & Number of characters in the question's text (Text length) \\ \cline{2-2}
-  & Number of characters in the user-defined device name (Device name length) \\ \cline{2-2}
-  & Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
+  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
+  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
+  & Number of characters in the question's text (text length) \\ \cline{2-2}
+  & Number of characters in the user-defined device name dDevice name length) \\ \cline{2-2}
+  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
 \end{tabular}
@@
 The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download).
-Variables in the data included: device name and category, title, text, tags, If the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received.
-See Appendix for an example of an answered and unanswered question.
+Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received.
 Variables derived can be found in Table \ref{table:variables}.
-See Appendix for details on variable derivation.
+The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table \ref{table:questions}.
 
@@
 Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
-Each predictor was entered into univariate Cox models and strength of association with response times was assessed.
+Each predictor was entered into univariate Cox models and the evidence of association with response times was assessed.
 Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.
@@
 Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}.
+AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \cite{Harrell2015}.
 All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
@@
 The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
-The p-value for this statistic was calculated from the $chi^2$ distribution \cite{Oakes1981}.
+The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}.
 Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability.
@@
 
-To compute predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R.
+All computation was executed under \texttt{R} version 3.4.3.
+\hl{Package for KM curve?} To compute predicted survival probabilities using the model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package in R.
 This function uses the Cox model and a vector of times to compute predicted survival probabilities.
+\hl{Include reference for data and functions in oshitaR pacakge?}
 
@@
 The longest was 2,159.02 hours (89.96 days).
-Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
+Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
 
-  Figure ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
+  Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
 The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
@@
 This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
-This variable is the average frequency, or proportion of times a question's tags appear in all of the data set.
-If a question has a higher average, than at least one of its tags are considered frequently-used.
+This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set.
+Questions without tags were assigned a value of 0.
+If a question has a higher average, then at least one of its tags are considered frequently-used.
 This variable was created based off of findings from \cite{Bhat2014}.

### 2018-01-22 article/draft1.Rnw
Shannon's edits

@@
 This paper presents a survival analysis of the time until a question receives it's first response.
-A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time.
+A Cox proportional hazards model was developed to identify variables associated with response time.
 Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
@@
 The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days).
-Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
+Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
 
@@
 
-  Figure ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
+  Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
 The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
@@
 
-Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions.
-Each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
+Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions; each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
 Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001.
@@
 Applying either square root or log transformations resulted in univariate p-values of less than 0.001.
-For those that contained zeros, one was added to each observation before applying the log transformation.
-The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
+For variables that contained zeros, one was added to each observation before applying the log transformation.
+The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
 All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.
@@
 \end{tabular}
-\caption{Determining the optimal k number of splines for each continuous predictor} 
+\caption{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
 \label{table:splines}
@@
   \hline
-  \textbf{Training Sets} & 2.03 & 937.39 & 0 & 0.14 & 0.27 & 0.63 \\ 
-  \textbf{Test Sets} & 1.99 & 220.83 & 0 & 0.14 & 0.26 & 0.63 \\
-  \textbf{Full Data} & 2.03 & 1165.03 & 0 & 0.14 & 0.28 & 0.63 \\ 
+  \textbf{Training Sets} & 2.03 & 937.39  & \hl{0} & 0.14 & 0.27 & 0.63 \\ 
+  \textbf{Test Sets}     & 1.99 & 220.83  & \hl{0} & 0.14 & 0.26 & 0.63 \\
+  \textbf{Full Data}     & 2.03 & 1165.03 & \hl{0} & 0.14 & 0.28 & 0.63 \\ 
    \hline
 \end{tabular}
-\caption{Performance Metrics. \\ HR: Hazard Ratio, LR: Partial Likelihood Ratio} 
+\caption{Performance metrics \hl{of final model?}. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
 \label{table:cv}
@@
 
-The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value = 0). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
+The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value \hl{= 0}). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
 
@@
 Many users incorrectly specified the device name (e.g.
-A user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
+a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
 Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic).
 It is likely that these inconsistencies contributed to the final model's low predictive power.
-This, along with the results of the final model, reveal some of the ways that the CQA can be structured to improve analysis and decrease response time.
+This, along with the results of the final model, reveal some of the ways that the CQA can be structured to potentially decrease response times.
 As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
@@
 The CQA can also include more tips to guide users asking questions.
-Implementing a more restrictive framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
+Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
 
@@
 \end{table}
-
-Table \ref{table:questions} provides an example of an answered and unanswered question. All fields in the table are shown as the users entered it.
+Table \ref{table:questions} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
+All fields in device, title, text, and tags are shown as the users entered it.
 
@@
 
-\subsubsection*{8.2.3 Device Categorization}
+\subsubsection*{8.2.3 Device categorization}
 
@@
 This variable was created to investigate if questions with correctly defined device names have faster response times than questions that do not include a name or are incorrectly defined.
-Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names make it difficult for the answering community to discern the question's topic, and thus have slower response times.
+Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names (often lengthy) make it difficult for the answering community to discern the question's topic, and thus have slower response times.
 
@@
 
-This variable was created to investigate if run-on sentences, sentences with no end punctuation, take longer to receive an answer.
+This variable was created to investigate if sentences with no end punctuation take longer to receive an answer.
 
@@
 As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
-The resulting list for answered questions contained 111 words.
-The list for unanswered questions contained 32 words.
-Lists can be found in Table \ref{table:frequent_terms}
-
+Table \ref{table:frequentterms} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
 % Table with list of frequently-used words
@@
 \caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
-\label{table:frequent_terms}
+\label{table:frequentterms}
 \end{table}
@@
 
-This variable was created to investigate if questions with titles in the form of questions receive answers faster than those that do not \cite{Bhat2014}.
+This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \cite{Bhat2014}.
 
@@
 
-Logical variable indicating true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting.
+This variable indicates true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting.
 Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
-This variable was created based off of findings and methods from \cite{Bhat2014} \cite{Harper2008}.
+This variable was created based off of findings and methods from \citep{Bhat2014} and \citep{Harper2008}.
 
@@
 This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that don't include any, and thus have shorter response times.
+\hl{What is an optimal/desirable/good ratio versus bad?}
 

### 2018-01-22 article/draft1.tex
Shannon's edits

@@
 
-Each training set contained 6,208 questions.
-Each test set contained 1,552 questions.
+Each training set contained 6,208 questions; each test set contained 1,552 questions.
 Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001.

### 2018-01-23 article/draft1.Rnw
edits

@@
 All computation was executed under \texttt{R} version 3.4.3.
-\hl{Package for KM curve?} To compute predicted survival probabilities using the model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package in R.
+Kaplan-Meier estimates of survival probability were computed with the \texttt{Surv} and \texttt{survfit} functions of the \texttt{Survival} package in R.
+To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package.
 This function uses the Cox model and a vector of times to compute predicted survival probabilities.
-\hl{Include reference for data and functions in oshitaR pacakge?}
+Data used for this analysis can be found in the \texttt{oshitar} package.
+The function \texttt{variable\_setup} of the \texttt{oshitar} package was used to set up all necessary variables in the data.
 
@@
   \hline
-  \textbf{Training Sets} & 2.03 & 937.39  & \hl{0} & 0.14 & 0.27 & 0.63 \\ 
-  \textbf{Test Sets}     & 1.99 & 220.83  & \hl{0} & 0.14 & 0.26 & 0.63 \\
-  \textbf{Full Data}     & 2.03 & 1165.03 & \hl{0} & 0.14 & 0.28 & 0.63 \\ 
+  \textbf{Training Sets} & 2.03 & 937.39  & <0.0001 & 0.14 & 0.27 & 0.63 \\ 
+  \textbf{Test Sets}     & 1.99 & 220.83  & <0.0001 & 0.14 & 0.26 & 0.63 \\
+  \textbf{Full Data}     & 2.03 & 1165.03 & <0.0001 & 0.14 & 0.28 & 0.63 \\ 
    \hline
 \end{tabular}
-\caption{Performance metrics \hl{of final model?}. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
+\caption{Performance metrics of final model (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
 \label{table:cv}
@@
                   & Vehicle & 0.4056 (0.0695)  & \\ \hline
-  \multicolumn{2}{|l|}{Weekend or weekday} & -0.1334 (0.0331)  & <0.0001 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the question's text contains end punctuation marks} & 0.0247 (0.0499) & 0.6127 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the question's text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the question's title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the user edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the user had been a member for less than one day before posting the question} & -0.1069 (0.0364)  & 0.0031 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{If the user made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
+  \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & <0.0001 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{Text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{User was a member for less than one day before posting} & -0.1069 (0.0364)  & 0.0031 \\ \hline
+  \multicolumn{2}{|L{7.5cm}|}{User made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
   \multicolumn{2}{|L{7.5cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
 \end{tabular} 
-\caption{Coefficients for predictors in the final model. Continuous predictors fit with restricted cubic splines are not shown.} 
+\caption{Coefficients for predictors in the final model (Continuous predictors fit with restricted cubic splines are not shown)} 
 \label{table:coefficients}
@@
 
-The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value \hl{= 0}). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
+The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value <0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
 
@@
 Instead, the CQA can restrict the tags or devices that users can include to a drop-down list.
-The CQA can also include more tips to guide users asking questions.
+The CQA can also include additional tips to guide users asking questions.
 Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
@@
 
-\subsubsection*{8.2.6 If the question's text contains end punctuation marks}
+\subsubsection*{8.2.6 If the question's text contains end punctuation}
 
@@
 
-This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that don't include any, and thus have shorter response times.
-\hl{What is an optimal/desirable/good ratio versus bad?}
+This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that do not include any, and thus have shorter response times.
+Questions with a ratio of 0 tend to include either short, ambiguous texts (e.g.
+"Start button not working.") or long and lengthy texts, and tend to remain unanswered or have slower response times.
+Questions with a ratio of greater than 0 tend to have faster response times.
 

### 2018-01-26 article/draft1.Rnw
resolved issue with text

@@
 An important aspect of these CQAs, for both users and the forum, is question response time.
-This paper presents a survival analysis of the time until a question receives it's first response.
+This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
 A Cox proportional hazards model was developed to identify variables associated with response time.
-Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$).
+Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$).
 Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))).
@@
 The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to save money and reduce electronic waste.
-This company provides over 30,000 free online repair guides and sells specialized tools and parts needed for such repairs.
+Founded in 2003, iFixit provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
+This company's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to help them save money and reduce electronic waste.
 
@@
 \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
-\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered.
+\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered.
 However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
@@
   & Number of characters in the question's text (text length) \\ \cline{2-2}
-  & Number of characters in the user-defined device name dDevice name length) \\ \cline{2-2}
+  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
   & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
@@
 To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package.
-This function uses the Cox model and a vector of times to compute predicted survival probabilities.
+This function uses the Cox model and a vector of times to compute predictions.
 Data used for this analysis can be found in the \texttt{oshitar} package.
@@
 The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
-The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days.
-The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.
+The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
+The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
 
@@
 Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001.
-Applying either square root or log transformations resulted in univariate p-values of less than 0.001.
+Applying either square root or log transformations to all continuous predictors resulted in univariate p-values of less than 0.001.
 For variables that contained zeros, one was added to each observation before applying the log transformation.
@@
 \end{tabular}
-\caption{Performance metrics of final model (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
+\caption{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
 \label{table:cv}
@@
 Many users incorrectly specified the device name (e.g.
-a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all.
+a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name.
 Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic).
 It is likely that these inconsistencies contributed to the final model's low predictive power.
-This, along with the results of the final model, reveal some of the ways that the CQA can be structured to potentially decrease response times.
+This, along with the results of the final model, reveal some of the ways the CQA can be structured to potentially decrease response times.
 As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
@@
 Instead, the CQA can restrict the tags or devices that users can include to a drop-down list.
-The CQA can also include additional tips to guide users asking questions.
+The CQA can also include more tips to guide users asking questions.
 Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
@@
 \end{table}
+
 Table \ref{table:questions} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
@@
 Table \ref{table:frequentterms} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
+
 % Table with list of frequently-used words

### 2018-01-26 article/draft1.tex
resolved issue with text

@@
 An important aspect of these CQAs, for both users and the forum, is question response time.
-This paper presents a survival analysis of the time until a question receives it's first response.
+This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
 A Cox proportional hazards model was developed to identify variables associated with response time.

### 2018-01-26 article/draft1.Rnw
added Android/Other Phone (reference) line to table 4

@@
 \centering
-\begin{tabular}{|l L{4cm}| c | c |}
+\begin{tabular}{|l L{5.5cm}| c | c |}
   \hline
@@
                   & Tablet & -0.1566 (0.0815)  & \\ 
-                  & Vehicle & 0.4056 (0.0695)  & \\ \hline
+                  & Vehicle & 0.4056 (0.0695)  & \\
+                  & Android/Other Phone (reference) & --- & \\ \hline
   \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & <0.0001 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{Text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{User was a member for less than one day before posting} & -0.1069 (0.0364)  & 0.0031 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{User made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
-  \multicolumn{2}{|L{7.5cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
+  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
+  \multicolumn{2}{|l|}{Text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.1069 (0.0364)  & 0.0031 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
 \end{tabular} 

### 2018-01-27 article/draft1.tex
reformatted tex file to elsarticle class

@@
-\documentclass{article}
+\documentclass[preprint]{elsarticle}
+
+\usepackage{lineno,hyperref}
+\modulolinenumbers[5]
+
+% for table formatting
 \usepackage{multirow}
-\usepackage{color,soul}
 \usepackage{array}
@@
 
-\usepackage{Sweave}
+%===================================================================================================
+%===================================================================================================
+
 \begin{document}
-\input{draft1-concordance}
 
-\makeatletter
-\DeclareRobustCommand\bfseries{%
-  \not@math@alphabet\bfseries\mathbf
-  \fontseries\bfdefault\selectfont
-  \boldmath % <-- added
-}
-\makeatother
+\begin{frontmatter}
+\title{Survival Analysis of Questions Posted on iFixit's Answers forum}
 
-\section*{Abstract}
+\author[cp]{L.K.~Oshita\corref{cor1}}
+\cortext[cor1]{Corresponding author}
+\ead{l.oshita@yahoo.com}
 
+\author[ifixit]{A.~Pileggi}
+\author[cp]{S.~Pileggi}
+
+\address[cp]{California Polytechnic State University, San Luis Obispo, CA 93407, United States}
+\address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
+
+\begin{abstract} 
 Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information.
@@
 Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
+\end{abstract}
+
+\begin{keyword}
+cox regression \sep response time \sep survival analysis \sep survival probabilty \sep Q\&A forum 
+\end{keyword}
+
+\end{frontmatter}
 
@@
 
-\section*{1. Introduction}
+\section{Introduction}
 
@@
 
-\section*{2. Related Work}
+\section{Related Work}
 
@@
 \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
-\cite{Blumenstock} also determined that textual features (e.g.
+\cite{Blumenstock2008} also determined that textual features (e.g.
 word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-\cite{H.fu} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
+\cite{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
 A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
@@
 
-\section*{3. Materials}
+\section{Materials}
 
@@
 \centering
-\begin{tabular}{| L{2cm} | L{10cm} |}
+\begin{tabular}{|L{2cm}|L{10cm}|}
   \hline
@@
 
-\section*{4. Methods}
+\section{Methods}
 
@@
 
-\section*{5. Results and Discussion}
+\section{Results and Discussion}
 
@@
 \begin{figure}[!htbp]
-  \includegraphics[scale=1]{times_dist.pdf}
+  \includegraphics[scale=0.5]{times_dist.pdf}
   \caption{Distribution of response times}
@@
 \begin{figure}[!htbp]
-  \includegraphics[scale=1]{kmcurve.pdf}
+  \includegraphics[scale=0.5]{kmcurve.pdf}
   \caption{Kaplan-Meier curve for all questions}
@@
   Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
-Of those questions, 4,951 (63.8}\%) received an answer by the download date.
+Of those questions, 4,951 (63.8\%) received an answer by the download date.
 The shortest response time was 0.5 hours.
@@
 \centering
-\begin{tabular}{| r | r | r | r | r  | r | r | r |}
+\begin{tabular}{|r|r|r|r|r|r|r|r|}
   \hline
@@
   \hline
-  \textbf{Training Sets} & 2.03 & 937.39  & <0.0001 & 0.14 & 0.27 & 0.63 \\ 
-  \textbf{Test Sets}     & 1.99 & 220.83  & <0.0001 & 0.14 & 0.26 & 0.63 \\
-  \textbf{Full Data}     & 2.03 & 1165.03 & <0.0001 & 0.14 & 0.28 & 0.63 \\ 
+  \textbf{Training Sets} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
+  \textbf{Test Sets}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
+  \textbf{Full Data}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
    \hline
@@
 \centering
-\begin{tabular}{|l L{5.5cm}| c | c |}
+\begin{tabular}{|l L{5.5cm}|c|c|}
   \hline
  \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
-  Device Category & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
+  Device Category & Apple Product & 0.9346 (0.0476) & \textless0.0001 \\ 
                   & Camera & -0.3199 (0.0476) & \\ 
@@
                   & Android/Other Phone (reference) & --- & \\ \hline
-  \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & <0.0001 \\ \hline
+  \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & \textless0.0001 \\ \hline
   \multicolumn{2}{|l|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
@@
   \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & \textless0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  \textless0.0001 \\ \hline
   \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
@@
 \end{tabular} 
-\caption{Coefficients for predictors in the final model (Continuous predictors fit with restricted cubic splines are not shown)} 
+\caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
 \label{table:coefficients}
@@
 
-The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value <0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
+The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
 
@@
 
-\section*{6. Conclusion}
+\section{Conclusion}
 
@@
 
-\section*{7. Acknowledgements}
+\section{Acknowledgements}
 
@@
 
-\section*{8. Appendix}
+\section{Appendix}
 
 % --------------------------------------------------------------------------------------------------
-\subsection*{8.1 Posted questions}
+\subsection{Posted questions}
 
@@
 
-\subsection*{8.2 Variable Derivation}
+\subsection{Variable Derivation}
 
-\subsubsection*{8.2.1 Average tag frequency}
+\subsubsection{Average tag frequency}
 
@@
 
-\subsubsection*{8.2.2 Average tag length}
+\subsubsection{Average tag length}
 
@@
 
-\subsubsection*{8.2.3 Device categorization}
+\subsubsection{Device categorization}
 
@@
 
-\subsubsection*{8.2.4 Device name length}
+\subsubsection{Device name length}
 
@@
 
-\subsubsection*{8.2.6 If the question's text contains end punctuation}
+\subsubsection{If the question's text contains end punctuation}
 
@@
 
-\subsubsection*{8.2.7 If the question's title contains terms considered frequently-used among answered/unanswered questions}
+\subsubsection{If the question's title contains terms considered frequently-used among answered/unanswered questions}
 
@@
 
-\subsubsection*{8.2.8 If the question's title ends in a question mark}
+\subsubsection{If the question's title ends in a question mark}
 
@@
 
-\subsubsection*{8.2.9 If the user made an effort to solve the problem prior to asking the question}
+\subsubsection{If the user made an effort to solve the problem prior to asking the question}
 
@@
 
-\subsubsection*{8.2.5 Line break to text length ratio}
+\subsubsection{Line break to text length ratio}
 
@@
 
+\section*{References}
+
+\bibliographystyle{elsarticle-num}
 \bibliography{questions}
-\bibliographystyle{ECA_jasa}
 

### 2018-01-27 article/draft1.Rnw
changed Sweave to knitr

@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+%\SweaveOpts{concordance=TRUE}
 
@@
 
-  Of 8,025 questions in the full data, \Sexpr{format(nrow(x), big.mark = ",")} were in English (97\% of the full data).
+  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
 Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date.
@@
 \centering
-\begin{tabular}{|l L{5.5cm}| c | c |}
+\begin{tabular}{|l L{5.5cm}|c|c|}
   \hline

### 2018-01-28 article/draft1.Rnw
update Rnw file to elsarticle class

@@
-\documentclass{article}
+\documentclass[preprint]{elsarticle}
+
+\usepackage{lineno,hyperref}
+\modulolinenumbers[5]
+
 \usepackage{multirow}
@@
 \begin{document}
-%\SweaveOpts{concordance=TRUE}
 
+% puts R2 in bold in table 3
 \makeatletter
@@
 
-\section*{Abstract}
+\begin{frontmatter}
+\title{Survival Analysis of Questions Posted on iFixit's Answers forum}
 
+\author[cp]{L.K.~Oshita\corref{cor1}}
+\cortext[cor1]{Corresponding author}
+\ead{l.oshita@yahoo.com}
+
+\author[ifixit]{A.~Pileggi}
+\author[cp]{S.~Pileggi}
+
+\address[cp]{California Polytechnic State University, San Luis Obispo, CA 93407, United States}
+\address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
+
+\begin{abstract} 
 Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information.
@@
   Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
-Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date.
+Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}\%) received an answer by the download date.
 The shortest response time was \Sexpr{shortest} hours.
@@
  \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
-  Device Category & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
+  Device Category & Apple Product & 0.9346 (0.0476) & \textless0.0001 \\ 
                   & Camera & -0.3199 (0.0476) & \\ 

### 2018-01-28 article/draft1.Rnw
commented out captions in figures
changed citation references

@@
-\documentclass[preprint]{elsarticle}
+\documentclass[preprint, authoryear]{elsarticle}
 
@@
 As thousands of users rely on this forum for information, it is important that users receive timely answers.
-Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
+Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \citep{Rechavi2011}.
 Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.
@@
 With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies.
-Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
-\cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
-\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered.
+Regarding analysis of response times, \citet{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
+\citet{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
+\citet{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered.
 However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
@@
 The majority of existing research has been focused on predicting question and answer quality.
-\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
-\cite{Blumenstock2008} also determined that textual features (e.g.
+\citet{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
+\citet{Blumenstock2008} also determined that textual features (e.g.
 word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-\cite{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
-A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
+\citet{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
+A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \citep{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
 The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.
@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.
+Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \citep{Kleinbaum2011}.
 
 Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}.
-Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}.
+Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \citep{Bland1998}.
 From these estimates, survival curves were constructed to examine the survival experience of questions.
@@
 
-As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}.
-To build the model, five-fold cross-validation was used \cite{Rodriguez2010}.
-Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
+As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \citep{Moore2010}.
+To build the model, five-fold cross-validation was used \citep{Rodriguez2010}.
+Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \citep{Hammermeister1979}.
 Each predictor was entered into univariate Cox models and the evidence of association with response times was assessed.
@@
 Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \cite{Harrell2015}.
+AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \citep{Harrell2015}.
 All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
-No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
+No variable selection was used after identifying significant predictors in univariate analysis, as \citet{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
 
@@
 To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
-The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
+The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \citep{Chen}.
 Significant results from this model would indicate high predictive accuracy.
 The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
-The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}.
+The p-value for this statistic was calculated from the $\chi^2$ distribution \citep{Oakes1981}.
 Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability.
@@
 Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5.
-A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}.
+A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \citep{Harrell2015}.
 These metrics were computed for each iteration on every training and test set.
@@
 
-Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}.
+Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \citep{Grambsch1994}.
 Significant correlations would indicate a predictor has violated this assumption.
@@
   \includegraphics[scale=0.5]{times_dist.pdf}
-  \caption{Distribution of response times}
   \label{fig:answertimes}
 \end{figure}
+% \caption{Distribution of response times}
 
@@
   \includegraphics[scale=0.5]{kmcurve.pdf}
-  \caption{Kaplan-Meier curve for all questions}
   \label{fig:kmcurve}
 \end{figure}
+% \caption{Kaplan-Meier curve for all questions}
 
@@
 If a question has a higher average, then at least one of its tags are considered frequently-used.
-This variable was created based off of findings from \cite{Bhat2014}.
+This variable was created based off of findings from \citet{Bhat2014}.
 
@@
 Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not.
-This variable was created based off of methods from \cite{Correa2013} and \cite{Ravi2014}.
+This variable was created based off of methods from \citet{Correa2013} and \citet{Ravi2014}.
 
@@
 
-This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \cite{Bhat2014}.
+This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \citep{Bhat2014}.
 
@@
 Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
-This variable was created based off of findings and methods from \citep{Bhat2014} and \citep{Harper2008}.
+This variable was created based off of findings and methods from \citet{Bhat2014} and \citet{Harper2008}.
 
@@
 
-\bibliographystyle{elsarticle-num}
+\bibliographystyle{plainnat}
+% \bibliogrpahystyle{elsarticle-harv}
+% \bibliographystyle{model2-names.bst}\biboptions{authoryear}
 \bibliography{questions}

### 2018-01-28 article/draft1.tex
returned to elsarticle class
update Rnw file to elsarticle class
commented out captions in figures
changed citation references

@@
-\documentclass[preprint]{elsarticle}
+\documentclass[preprint, authoryear]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 
-% for table formatting
 \usepackage{multirow}
+\usepackage{color,soul}
 \usepackage{array}
@@
 \usepackage{caption}
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\begin{document}
 
-%===================================================================================================
-%===================================================================================================
-
-\begin{document}
+% puts R2 in bold in table 3
+\makeatletter
+\DeclareRobustCommand\bfseries{%
+  \not@math@alphabet\bfseries\mathbf
+  \fontseries\bfdefault\selectfont
+  \boldmath % <-- added
+}
+\makeatother
 

### 2018-02-07 app/server.R
updated app with new model

@@ -4,13 +4,14 @@ library(shiny); library(survival); library(rms)
 x <- as.data.frame(read.csv("data/finaldata.csv", head = TRUE)); x <- x[,-1]
 
 model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
-                               contain_unanswered + contain_answered + title_questionmark + 
-                               title_beginwh + text_contain_punct + text_all_lower + update + 
-                               greeting + gratitude + prior_effort + weekday + strat(ampm) + 
-                               sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + 
-                               rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
-                             data = x, x = TRUE, 
-                             y = TRUE, surv = TRUE)
+                    contain_unanswered + contain_answered + title_questionmark + 
+                    text_contain_punct + text_all_lower + update + prior_effort + 
+                    day + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + 
+                    rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + 
+                    rcs(sqrt(newline_ratio), 3), 
+                  data = x, 
+                  x = TRUE, y = TRUE, 
+                  surv = TRUE)
 
 #-----------------------------------------------------------------------------
 shinyServer(
@@ -19,13 +20,13 @@ shinyServer(
     #-------Renders summary statistics of input data-------------------------- 
     output$sum_stats <- renderTable({
       req(input$file1)
-      df <- as.data.frame(read.csv(input$file1$datapath)) # look into reactive function
+      df <- as.data.frame(read.csv(input$file1$datapath)) 
       data <- oshitar::variable_setup(df)
         
       summarydf <- data.frame(nrow(data), 
-                              round(median(data$time_until_answer),2), 
-                              round(sum(data$answered)/nrow(data),2),
-                              round(mean(data$time_until_answer),2),
+                              round(median(data$time_until_answer), 2), 
+                              round(sum(data$answered)/nrow(data), 2),
+                              round(mean(data$time_until_answer), 2),
                               round(max(data$time_until_answer), 2),
                               round(min(data$time_until_answer), 2)
                               )
@@ -54,7 +55,8 @@ shinyServer(
       data <- oshitar::variable_setup(df)
       
       if(input$km == TRUE) {
[…]

### 2018-02-07 app/ui.R

@@ -36,7 +36,7 @@ shinyUI(fluidPage(
                    tableOutput("contents"),
                    br(),
                    tableOutput("estimates")
-                     )
+                 )
                  )
                ),
       tabPanel("Calculate Predicted Failure", 

### 2018-03-01 article/draft1.Rnw
changed citations back to default
article comments/edits (from Anthony)

@@
-\documentclass[preprint, authoryear]{elsarticle}
+\documentclass[preprint]{elsarticle}
 
@@
 \title{Survival Analysis of Questions Posted on iFixit's Answers forum}
+% Survival Analysis of Questions Posted on the iFixit Answers forum
+% --> apostrophy in title looks a little weird to me, but I don't mind either way
 
@@
 The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
+Founded in 2003, iFixit provides over 35,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
 This company's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to help them save money and reduce electronic waste.
@@
 As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users.
-This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 100,000 user-posted solutions.
+This platform features questions pertaining to over 10,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 120,000 user-posted solutions.
 As thousands of users rely on this forum for information, it is important that users receive timely answers.
@@
 
+% Unless we are planning to make the oshitar package available on cran, it might be better to setup a GIST with a clean version of the data and the variable_setup() function.
+Or we should at least link to the github repo instead: https://github.com/loshita/oshitar
+
 %===================================================================================================
@@
 shortest <- round(min(x$time_until_answer) * 60, 2) 
-longest <- round(max(x$time_until_answer), 2)
-longest_d <- round(longest / 24, 2) 
+longest <- round(max(x$time_until_answer))
+longest_d <- round(longest / 24, 1) 
 @
@@
 
+% Heyyy this is a dynamic document, why not make these images in-line? :-()
+
   Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
-Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}\%) received an answer by the download date.
+Of those questions, \Sexpr{scales::comma(answered)} (\Sexpr{percentans}\%) received an answer by the download date.
 The shortest response time was \Sexpr{shortest} hours.
@@
 Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
+
+% fyi you can use scales::comma(val) to format numbers too
 
@@
 The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
-The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days.
-The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.
+The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 776 hours, or 32.3 days.
+The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.2 hours.
 
@@
 
+% cool, I like this table!
+% --> can we write the Predictor column more mathematically?
+% --> e.g., $\sqrt{\textnormal{average tag frequency}}$
+% --> e.g., $\log\left({\textnormal{average tag length} + 1}\right)$
+% also, the 'K' column might align better if we put the * to the right
+
 Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
@@
 
+% This table looks nice, but the code is brutal and not reproducible.  I feel compelled to point out 'xtable' or 'stargazer' for auto-generated latex tables like this using R.
+
+% I think we should use 2 digits for coefficients and 3 digits for SE/p-value terms
+
 Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
@@
 \begin{itemize}
-  \item The estimated hazard of receiving an answer is 154.1\% (95\% CI (131.5\%, 180.0\%)) higher for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer for questions posted on a weekend is 12.5\% (95\% CI (6.7\%, 18.0\%)) lower than the hazard for questions posted on a weekday, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer is 24.5\% (95\% CI (19.3\%, 29.4\%)) lower for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 154.1\% higher (95\% CI (131.5\%, 180.0\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer for questions posted on a weekend is 12.5\% lower (95\% CI (6.7\%, 18.0\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 24.5\% lower (95\% CI (19.3\%, 29.4\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
 \end{itemize}
@@
 
+% If there ever was a good time to use a wordlcloud, I think this is it!! Just sayin...
+% library(wordcloud)
+
 % ------------------------------------------------------------------------
@@
 
-\bibliographystyle{plainnat}
+\bibliographystyle{elsarticle-num-names}
+% \bibliographystyle{plainnat}
 % \bibliogrpahystyle{elsarticle-harv}
-% \bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
 \bibliography{questions}

### 2018-03-06 article/draft1.Rnw
reformat predictor column of table 2, add more inline code, fix rounding

@@
 
-<< echo = FALSE >>=
+<< include = FALSE >>=
+# load libraries
+library(magrittr)
+library(dplyr)
+library(rebus)
+
 # importing data 
@@
                    surv = TRUE)
+
+# creating data frame with model coefficients + HR + 95% CI
+model_coefs <- data.frame(vars = names(model$coefficients), 
+                          beta = unname(model$coefficients)) %>% mutate(HR = exp(beta))
+model_var <- as.data.frame(model$var)
+
+# extracting SE from variance matrix
+model_coefs$SE <- 0
+for (i in 1:32) {
+  model_coefs$SE[i] <- sqrt(model_var[i, i])
+}
+
+# 95% CI
+model_coefs$upper <- exp(model_coefs$beta + (1.96 * model_coefs$SE))
+model_coefs$lower <- exp(model_coefs$beta - (1.96 * model_coefs$SE))
+
+# rounding 
+model_coefs$beta <- round(model_coefs$beta, 2)
+model_coefs$HR <- round(model_coefs$HR, 2)
+model_coefs$SE <- round(model_coefs$SE, 3)
+model_coefs$upper <- round(model_coefs$upper, 2)
+model_coefs$lower <- round(model_coefs$lower, 2)
+
+# removing continuous predictors with splines 
+model_coefs <- model_coefs[-which(stringr::str_detect(model_coefs$vars, 
+                                                      pattern = rebus::or(START %R% "text_length",
+                                                                          START %R% "avg_tag_length",
+                                                                          START %R% "device_length",
+                                                                          START %R% "newline_ratio"))), ]
+
+# to include in abstract
+# HR and confidence intervals
+a <- which(stringr::str_detect(model_coefs$vars, pattern = "Apple Product"))
+appleHR <- model_coefs$HR[a]
+appleUpper <- model_coefs$upper[a]
+appleLower <- model_coefs$lower[a]
+
+t <- which(stringr::str_detect(model_coefs$vars, pattern = "questionmark"))
+titleHR <- model_coefs$HR[t]
+titleUpper <- model_coefs$upper[t]
+titleLower <- model_coefs$lower[t]
+
+w <- which(stringr::str_detect(model_coefs$vars, pattern = "Weekend"))
+dayHR <- model_coefs$HR[w]
+dayUpper <- model_coefs$upper[w]
+dayLower <- model_coefs$lower[w]
+
+# model R2
+r2 <- round(model$stats[which(names(model$stats) == "R2")], 2)
 @
@@
 \begin{frontmatter}
-\title{Survival Analysis of Questions Posted on iFixit's Answers forum}
-% Survival Analysis of Questions Posted on the iFixit Answers forum
-% --> apostrophy in title looks a little weird to me, but I don't mind either way
+\title{Survival Analysis of Questions Posted on the iFixit Answers forum}
 
@@
 A Cox proportional hazards model was developed to identify variables associated with response time.
-Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))).
+Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{r2}$).
+Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = \Sexpr{appleHR}, 95\% CI = (\Sexpr{appleLower}, \Sexpr{appleUpper})), factors related to the question's title (e.g., if it was phrased as a question (HR = \Sexpr{titleHR}, 95\% CI = (\Sexpr{titleLower}, \Sexpr{titleUpper}))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = \Sexpr{dayHR}, 95\% CI = (\Sexpr{dayLower}, \Sexpr{dayUpper}))).
 Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
@@
 
-  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
+  Of 8,025 questions in the full data, \Sexpr{scales::comma(nrow(x))} were in English (97\% of the full data).
 Of those questions, \Sexpr{scales::comma(answered)} (\Sexpr{percentans}\%) received an answer by the download date.
 The shortest response time was \Sexpr{shortest} hours.
-The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days).
+The longest was \Sexpr{scales::comma(longest)} hours (\Sexpr{scales::comma(longest_d)} days).
 Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
@@
 stats <- summary(KM)$table
-mean <- round(unname(stats[5]), 2) 
-median <- round(unname(stats[7]), 2)
+mean <- round(unname(stats[5])) 
+mean_d <- round(mean/24, 1)
+med <- round(unname(stats[7]), 1)
 @
@@
 The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
-The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 776 hours, or 32.3 days.
-The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.2 hours.
+The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{mean_d} days.
+The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{med} hours.
 
@@
 
-Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions; each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions.
+Each training set contained \Sexpr{scales::comma(nrow(train1))} questions; each test set contained \Sexpr{scales::comma(nrow(test1))} questions.
 Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001.
@@
 
-% Splines
+% Splines Square root transformation of the average tag frequency
 \begin{table}[!htbp]
@@
   \hline
-  \multirow{4}{5 cm}{Square root transformation of the average tag frequency} 
-  & \textbf{*}0 & 65890.75 \\ 
+  \multirow{4}{5 cm}{$\sqrt{\textnormal{average tag frequency}}$} 
+  & 0\textbf{*} & 65890.75 \\ 
   & 5 & 65891.69 \\ 
@@
   \hline
-  \multirow{4}{5 cm}{Log transformation of average tag length + 1}
+  \multirow{4}{5 cm}{$\log\left({\textnormal{average tag length} + 1}\right)$}
   & 0 & 65920.24 \\ 
   & 5 & 65911.20 \\ 
-  & \textbf{*}4 & 65910.81 \\ 
+  & 4\textbf{*} & 65910.81 \\ 
   & 3 & 65914.98 \\ 
   \hline
-  \multirow{4}{5 cm}{Log transformation of device name length + 1}
+  \multirow{4}{5 cm}{$\log\left({\textnormal{device length} + 1}\right)$}
   & 0 & 65918.06 \\ 
-  & \textbf{*}5 & 65847.34 \\ 
+  & 5\textbf{*} & 65847.34 \\ 
   & 4 & 65880.89 \\ 
@@
   \hline
-  \multirow{4}{5 cm}{Square root transformation of line breaks to text length ratio}
+  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks : text length}}$}
   & 0 & 65890.28 \\ 
@@
   & 4 & 65882.98 \\ 
-  & \textbf{*}3 & 65881.93 \\ 
+  & 3\textbf{*} & 65881.93 \\ 
   \hline
-  \multirow{4}{5cm}{Log transformation of text length} 
+  \multirow{4}{5cm}{$\log\left({\textnormal{text length}}\right)$} 
   & 0 & 65862.83 \\ 
-  & \textbf{*}5 & 65862.02 \\ 
+  & 5\textbf{*} & 65862.02 \\ 
   & 4 & 65863.35 \\ 
@@
 % --> e.g., $\sqrt{\textnormal{average tag frequency}}$
-% --> e.g., $\log\left({\textnormal{average tag length} + 1}\right)$
+% --> e.g., $\log\left({\textnormal{device length} + 1}\right)$
 % also, the 'K' column might align better if we put the * to the right
@@
  \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
-  Device Category & Apple Product & 0.9346 (0.0476) & \textless0.0001 \\ 
-                  & Camera & -0.3199 (0.0476) & \\ 
-                  & Electronics & -0.0138 (0.0904)  & \\ 
-                  & Game Console & 0.2458 (0.0784)  & \\ 
-                  & Home & 0.3368 (0.0697) &  \\ 
-                  & Other & -0.1304 (0.0555)  & \\ 
-                  & PC & 0.2818 (0.0597) &  \\ 
-                  & Tablet & -0.1566 (0.0815)  & \\ 
-                  & Vehicle & 0.4056 (0.0695)  & \\
+  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
+                  & Camera & -0.32 (0.090) & \\ 
+                  & Electronics & -0.01 (0.078)  & \\ 
+                  & Game Console & 0.24 (0.083)  & \\ 
+                  & Home & 0.34 (0.070) &  \\ 
+                  & Other & -0.13 (0.056)  & \\ 
+                  & PC & 0.28 (0.060) &  \\ 
+                  & Tablet & -0.16 (0.081)  & \\ 
+                  & Vehicle & 0.40 (0.069)  & \\
                   & Android/Other Phone (reference) & --- & \\ \hline
-  \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & \textless0.0001 \\ \hline
-  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
-  \multicolumn{2}{|l|}{Text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & \textless0.0001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  \textless0.0001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.1069 (0.0364)  & 0.0031 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
+  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
+  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
+  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
 \end{tabular} 
@@
 
+<< echo = FALSE >>=
+LR <- unname(round(model$stats[which(names(model$stats) == "Model L.R.")], 2))
+dxy <- unname(round(model$stats[which(names(model$stats) == "Dxy")], 2))
+@
+
 Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
 
-The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
+As a whole, the final model was significant with a partial likelihood ratio of \Sexpr{LR} (p-value \textless0.0001). Its $R^2$ statistic was \Sexpr{r2}, and Somers' \textit{Dxy} was \Sexpr{dxy}.
 
@@
 
+<< echo = FALSE >>=
+apple_p <- (appleHR - 1) * 100
+apple_p_l <- (appleLower - 1) * 100
+apple_p_u <- (appleUpper - 1) * 100
+
+day_p <- (1 - dayHR) * 100
+day_p_u <- (1 - dayLower) * 100
+day_p_l <- (1 - dayUpper) * 100
+
+u <- which(stringr::str_detect(model_coefs$vars, pattern = "contain_unanswered"))
+unansw_p <- (1 - model_coefs$HR[u]) * 100
+unansw_p_l <- (1 - model_coefs$upper[u]) * 100
+unansw_p_u <- (1 - model_coefs$lower[u]) * 100
+@
+
 \begin{itemize}
-  \item The estimated hazard of receiving an answer is 154.1\% higher (95\% CI (131.5\%, 180.0\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer for questions posted on a weekend is 12.5\% lower (95\% CI (6.7\%, 18.0\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer is 24.5\% lower (95\% CI (19.3\%, 29.4\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is \Sexpr{apple_p}\% higher (95\% CI (\Sexpr{apple_p_l}\%, \Sexpr{apple_p_u}\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is \Sexpr{unansw_p}\% lower (95\% CI (\Sexpr{unansw_p_l}\%, \Sexpr{unansw_p_u}\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer for questions posted on a weekend is \Sexpr{day_p}\% lower (95\% CI (\Sexpr{day_p_l}\%, \Sexpr{day_p_u}\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
 \end{itemize}

### 2018-03-06 article/draft1.tex
changed citations back to default
reformat predictor column of table 2, add more inline code, fix rounding

@@
-\documentclass[preprint, authoryear]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[preprint]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth
@@
 \begin{frontmatter}
-\title{Survival Analysis of Questions Posted on iFixit's Answers forum}
+\title{Survival Analysis of Questions Posted on the iFixit Answers forum}
 
@@
 
+% Heyyy this is a dynamic document, why not make these images in-line? :-()
+
   Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
@@
 The shortest response time was 0.5 hours.
-The longest was 2,159.02 hours (89.96 days).
+The longest was 2,159 hours (90 days).
 Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
+
+% fyi you can use scales::comma(val) to format numbers too
 
@@
 \end{table}
+
+% cool, I like this table!
+% --> can we write the Predictor column more mathematically?
+% --> e.g., $\sqrt{\textnormal{average tag frequency}}$
+% --> e.g., $\log\left({\textnormal{device length} + 1}\right)$
+% also, the 'K' column might align better if we put the * to the right
 
@@
 
+% This table looks nice, but the code is brutal and not reproducible.  I feel compelled to point out 'xtable' or 'stargazer' for auto-generated latex tables like this using R.
+
+% I think we should use 2 digits for coefficients and 3 digits for SE/p-value terms
+
 Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
 
-The final model, as a whole, was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.267.
+As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
 
@@
 \begin{itemize}
-  \item The estimated hazard of receiving an answer is 154.1\% (95\% CI (131.5\%, 180.0\%)) higher for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer for questions posted on a weekend is 12.5\% (95\% CI (6.7\%, 18.0\%)) lower than the hazard for questions posted on a weekday, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer is 24.5\% (95\% CI (19.3\%, 29.4\%)) lower for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer for questions posted on a weekend is 13\% lower (95\% CI (7\%, 18\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
 \end{itemize}

### 2018-03-06 article/graphics.Rmd
updated how data is read in
added code to extract SE of model coefficients

@@
 out <- read.csv(file.path(dir, "answers_data.csv"))
-list <- oshitar::variable_setup(out)
-x <- list[[1]]
+x <- oshitar::variable_setup(out)
 
@@
                    surv = TRUE)
-model
+
+model_coefs <- data.frame(vars = names(model$coefficients), 
+                          beta = unname(model$coefficients)) %>% mutate(HR = exp(beta))
+model_var <- as.data.frame(model$var)
+
+model_coefs$SE <- 0
+for (i in 1:32) {
+  model_coefs$SE[i] <- sqrt(model_var[i, i])
+}
+
+model_coefs$upper <- exp(model_coefs$beta + (1.96 * model_coefs$SE))
+model_coefs$lower <- exp(model_coefs$beta - (1.96 * model_coefs$SE))
 ```

### 2018-03-10 article/draft1.Rnw
edit caption to table 5, change data reference to Mendeley, change figure reference to kmcurve.eps

@@
 This function uses the Cox model and a vector of times to compute predictions.
-Data used for this analysis can be found in the \texttt{oshitar} package.
-The function \texttt{variable\_setup} of the \texttt{oshitar} package was used to set up all necessary variables in the data.
-
-% Unless we are planning to make the oshitar package available on cran, it might be better to setup a GIST with a clean version of the data and the variable_setup() function.
-Or we should at least link to the github repo instead: https://github.com/loshita/oshitar
+Data used for this analysis can be found here(Mendeley citation).
+Cited data includes all variables used in the model.
+Code for variable setup and analysis is available upon request.
 
@@
   \label{fig:answertimes}
+% \caption{Distribution of response times}
 \end{figure}
-% \caption{Distribution of response times}
 
@@
 \begin{figure}[!htbp]
-  \includegraphics[scale=0.5]{kmcurve.pdf}
+  \includegraphics[scale=0.5]{kmcurve.eps}
   \label{fig:kmcurve}
+% \caption{Kaplan-Meier curve for all questions}
 \end{figure}
-% \caption{Kaplan-Meier curve for all questions}
-
-% Heyyy this is a dynamic document, why not make these images in-line? :-()
 
@@
 Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
-The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
+The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low.
 The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{mean_d} days.
@@
 \end{table}
-
-% cool, I like this table!
-% --> can we write the Predictor column more mathematically?
-% --> e.g., $\sqrt{\textnormal{average tag frequency}}$
-% --> e.g., $\log\left({\textnormal{device length} + 1}\right)$
-% also, the 'K' column might align better if we put the * to the right
 
@@
 This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's text contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
+Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
 While overall the model was significant, its predictive performance was considerably low.
@@
 \end{tabular}
-\caption{Answered and unanswered questions}
+\caption{Examples of an answered question (left) and an unanswered question (right)}
 \label{table:questions}

### 2018-03-10 article/draft1.tex
edit caption for Table 5
edit caption for table 5, change data reference

@@
 Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
-The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low.
+The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low.
 The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 776 hours, or 32.3 days.

### 2018-03-10 article/draft1.Rnw
change table labels and figure file names

@@
 \caption{Categorical and continuous variables derived}
-\label{table:variables}
+\label{table:1}
 \end{table}
@@
 Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received.
-Variables derived can be found in Table \ref{table:variables}.
-The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table \ref{table:questions}.
+Variables derived can be found in Table \ref{table:1}.
+The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table \ref{table:5}.
 
@@
 \begin{figure}[!htbp]
-  \includegraphics[scale=0.5]{times_dist.pdf}
+  \includegraphics[scale=0.5]{FIG1.pdf}
   \label{fig:answertimes}
@@
 \begin{figure}[!htbp]
-  \includegraphics[scale=0.5]{kmcurve.eps}
+  \includegraphics[scale=0.5]{FIG2.eps}
   \label{fig:kmcurve}
@@
 \caption{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
-\label{table:splines}
+\label{table:2}
 \end{table}
 
-Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
+Table \ref{table:2} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
 
@@
 \caption{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
-\label{table:cv}
+\label{table:3}
 \end{table}
 
-Average performance metrics for test and training sets are in Table \ref{table:cv}.
+Average performance metrics for test and training sets are in Table \ref{table:3}.
 Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time.
 However, $R^2$ statistics and discrimination indexes are considerably low.
-Metrics for the final model's performance on the full data, also found in Table \ref{table:cv}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
+Metrics for the final model's performance on the full data, also found in Table \ref{table:3}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
 Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
@@
 \caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
-\label{table:coefficients}
+\label{table:4}
 \end{table}
@@
 
-The following are interpretations of select hazard coefficients in Table \ref{table:coefficients}.
+The following are interpretations of select hazard coefficients in Table \ref{table:4}.
 Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
@@
 \caption{Examples of an answered question (left) and an unanswered question (right)}
-\label{table:questions}
+\label{table:5}
 \end{table}
 
-Table \ref{table:questions} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
+Table \ref{table:5} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
 All fields in device, title, text, and tags are shown as the users entered it.
@@
 As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
-Table \ref{table:frequentterms} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
+Table \ref{table:6} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
 
@@
 \caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
-\label{table:frequentterms}
+\label{table:6}
 \end{table}
-
-% If there ever was a good time to use a wordlcloud, I think this is it!! Just sayin...
-% library(wordcloud)
 

### 2018-03-10 article/graphics.Rmd
convert kmcurve figure to eps file
change figure file formats + file names

@@
 ```{r}
-# x$Answered <- NA
-# x$Answered[x$answered == 1] <- "Answered"
-# x$Answered[x$answered == 0] <- "Unanswered"
+x$Answered <- NA
+x$Answered[x$answered == 1] <- "Answered"
+x$Answered[x$answered == 0] <- "Unanswered"
 
@@
   scale_y_continuous("Number of Questions") + 
-  theme(text = element_text(size = 25),
-        axis.text = element_text(size = 15))
+  theme(text = element_text(size = 10),
+        axis.text = element_text(size = 10))
 
-ggsave("times_dist.pdf", width = 8, height = 5)
+ggsave("FIG1.pdf", width = 8, height = 5) # eps files don't work with transparency, submit as pdf instead
 ```
@@
            legend = "none",
-           font.x = 25, font.y = 25, font.tickslab = 15)
+           font.x = 10, font.y = 10, font.tickslab = 10)
 
-ggsave("kmcurve.pdf", width = 8, height = 5)
+ggsave("FIG2.eps", width = 8, height = 5)
 ```

### 2018-03-10 article/draft1.Rnw
added Vitae section, added to Acknowledgements section, removed captions from figures

@@
   \label{fig:answertimes}
-% \caption{Distribution of response times}
 \end{figure}
@@
   \label{fig:kmcurve}
-% \caption{Kaplan-Meier curve for all questions}
 \end{figure}
@@
 Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
-
-% fyi you can use scales::comma(val) to format numbers too
 
@@
 
-% This table looks nice, but the code is brutal and not reproducible.  I feel compelled to point out 'xtable' or 'stargazer' for auto-generated latex tables like this using R.
-
-% I think we should use 2 digits for coefficients and 3 digits for SE/p-value terms
-
 << echo = FALSE >>=
@@
 
+\section{Vitae}
+
+Lisa Oshita is a senior undergraduate student at the California Polytechnic State University in San Luis Obispo, majoring in statistics...
+
+\section{Author Contributions}
+
+All authors contributed to the analysis featured in this paper and have edited and approved of the final article.
+
 \section{Acknowledgements}
@@
 This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-We also thank iFixit for providing access to the CQA data and for analysis assistance.
+This sponsor was not involved in any aspect of this paper's analysis.
+We also thank iFixit for providing access to the CQA data.
 
@@
 \bibliographystyle{elsarticle-num-names}
-% \bibliographystyle{plainnat}
-% \bibliogrpahystyle{elsarticle-harv}
-
 \bibliography{questions}

### 2018-03-10 article/draft1.tex
added Vitae section, added to Acknowledgements section, removed captions from figures

@@
 
-% This table looks nice, but the code is brutal and not reproducible.  I feel compelled to point out 'xtable' or 'stargazer' for auto-generated latex tables like this using R.
-
-% I think we should use 2 digits for coefficients and 3 digits for SE/p-value terms
-
 Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.

### 2018-03-11 article/draft1.Rnw
added to Vitae section

@@
 
-Lisa Oshita is a senior undergraduate student at the California Polytechnic State University in San Luis Obispo, majoring in statistics...
+Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo.
+Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo.
+Anthony Pileggi is a Data Scientist at iFixit.
 

### 2018-03-12 article/draft1.Rnw
added declaration of interest to Vitae section, added packaged to remove auto-hyphenation
updated address in title page
comment out code for figures

@@
 \usepackage{caption}
+
+\usepackage[none]{hyphenat} % to cancel auto-hyphenation
 
@@
 
-\address[cp]{California Polytechnic State University, San Luis Obispo, CA 93407, United States}
+\address[cp]{Department of Statistics, California Polytechnic State University, San Luis Obispo, CA 93407, United States}
 \address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
@@
 % Distribution of answer times
-\begin{figure}[!htbp]
-  \includegraphics[scale=0.5]{FIG1.pdf}
-  \label{fig:answertimes}
-\end{figure}
-
-% Kaplan-Meier curve
-\begin{figure}[!htbp]
-  \includegraphics[scale=0.5]{FIG2.eps}
-  \label{fig:kmcurve}
-\end{figure}
+% \begin{figure}[!htbp]
+%   \includegraphics[scale=0.5]{FIG1.pdf}
+%   \label{fig:1}
+% \end{figure}
+% 
+% % Kaplan-Meier curve
+% \begin{figure}[!htbp]
+%   \includegraphics[scale=0.5]{FIG2.eps}
+%   \label{fig:2}
+% \end{figure}
 
@@
 The longest was \Sexpr{scales::comma(longest)} hours (\Sexpr{scales::comma(longest_d)} days).
-Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
+Figure \ref{fig:1} shows the distribution of response times for all questions analyzed.
 
@@
 
-Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
+Figure \ref{fig:2} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
 The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low.
@@
 Anthony Pileggi is a Data Scientist at iFixit.
+Declarations of interest: none.
 

### 2018-03-12 article/draft1.tex
added declaration of interest to Vitae section, added packaged to remove auto-hyphenation
updated address in title page
comment out code for figures

@@
 \usepackage{caption}
+
+\usepackage[none]{hyphenat} % to cancel auto-hyphenation
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 The longest was 2,159 hours (90 days).
-Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.
+Figure \ref{fig:1} shows the distribution of response times for all questions analyzed.
 
-Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
+Figure \ref{fig:2} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
 The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low.

### 2018-03-16 article/manuscript.Rnw
file renaming, edit keywords, change colon to divisor in Table 2

--- 2018-03-12 article/draft1.Rnw
@@
 \begin{keyword}
-cox regression \sep response time \sep survival analysis \sep survival probabilty \sep Q\&A forum 
+Cox regression \sep CQA forum \sep response time \sep survival analysis \sep survival probabilty 
 \end{keyword}
@@
 \end{frontmatter}
-
-%===================================================================================================
-%===================================================================================================
 
@@
 
-%===================================================================================================
-%===================================================================================================
-
 \section{Related Work}
@@
 The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.
-
-%===================================================================================================
-%===================================================================================================
 
@@
 The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table \ref{table:5}.
-
-%===================================================================================================
-%===================================================================================================
 
@@
 
-%===================================================================================================
-%===================================================================================================
-
 \section{Results and Discussion}
@@
 The longest was \Sexpr{scales::comma(longest)} hours (\Sexpr{scales::comma(longest_d)} days).
-Figure \ref{fig:1} shows the distribution of response times for all questions analyzed.
+Figure 1 shows the distribution of response times for all questions analyzed.
 
@@
 
-Figure \ref{fig:2} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
+Figure 2 shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
 The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low.
@@
   \hline
-  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks : text length}}$}
+  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks / text length}}$}
   & 0 & 65890.28 \\ 
@@
 
-%===================================================================================================
-%===================================================================================================
-
 \section{Conclusion}
@@
 While overall the model was significant, its predictive performance was considerably low.
-
-%===================================================================================================
-%===================================================================================================
 
@@
 
-%===================================================================================================
-%===================================================================================================
-
 \section{Appendix}
 
-% --------------------------------------------------------------------------------------------------
 \subsection{Posted questions}
-
-% answered question id = 397414
-% unanswered question id = 399971
 
@@
 
-% ------------------------------------------------------------------------------------------------
-
 \subsection{Variable Derivation}
@@
 
-% ------------------------------------------------------------------------
-
 \subsubsection{Average tag length}
@@
 It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
-
-% ------------------------------------------------------------------------
 
@@
 
-% ------------------------------------------------------------------------
-
 \subsubsection{Device name length}
@@
 
-% ------------------------------------------------------------------------
-
 \subsubsection{If the question's text contains end punctuation}
@@
 This variable was created to investigate if sentences with no end punctuation take longer to receive an answer.
-
-% ------------------------------------------------------------------------
 
@@
 
-% ------------------------------------------------------------------------
-
 \subsubsection{If the question's title ends in a question mark}
@@
 This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \citep{Bhat2014}.
-
-% ------------------------------------------------------------------------
 
@@
 This variable was created based off of findings and methods from \citet{Bhat2014} and \citet{Harper2008}.
-
-% ------------------------------------------------------------------------
 
@@
 
-% ------------------------------------------------------------------------
-
 \section*{References}
@@
 \bibliographystyle{elsarticle-num-names}
-\bibliography{questions}
+\bibliography{references}
 

### 2018-03-16 article/manuscript.tex
file renaming, edit keywords, change colon to divisor in Table 2

--- 2018-03-12 article/draft1.tex
@@
 The longest was 2,159 hours (90 days).
-Figure \ref{fig:1} shows the distribution of response times for all questions analyzed.
+Figure 1 shows the distribution of response times for all questions analyzed.
 
-Figure \ref{fig:2} shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
+Figure 2 shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
 The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low.

### 2018-04-03 article/manuscript.Rnw
add DOI for Mendeley data
change forum to uppercase in title

@@
 \begin{frontmatter}
-\title{Survival Analysis of Questions Posted on the iFixit Answers forum}
+\title{Survival Analysis of Questions Posted on the iFixit Answers Forum}
 
@@
 This function uses the Cox model and a vector of times to compute predictions.
-Data used for this analysis can be found here(Mendeley citation).
-Cited data includes all variables used in the model.
+Data used for this analysis was published on Mendeley Data (DOI: 10.17632/shfkj785yb.1).
 Code for variable setup and analysis is available upon request.

### 2018-04-26 CSM_poster/main.tex
csm poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.1 (14/06/14)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage{pifont} % for dings

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{Survival Analysis of Questions Posted on the iFixit Answers Forum} % Poster title

\author{Lisa Oshita\footnote{Frost Research Fellow, recipient of the Frost Undergraduate Student Research Award}, Anthony Pileggi, Shannon Pileggi} % Author(s)

\institute{Department of Statistics, California Polytechnic State University} % Institution(s)

%----------------------------------------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\begin{alertblock}{Overview}

\textcolor{dblue!70}{\ding{228}} iFixit's online question and answer forum, \textit{Answers}, features over 120,000 user-asked questions related specifically to device repair. Analysis of question response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how forum design can be improved.

\textcolor{dblue!70}{\ding{228}} \underline{Objective} Develop a Cox proportional hazards model to predict the survival probability, defined as the probability that a question remains unanswered beyond a certain time \textit{t}, of questions on the forum, with the goal of identifying variables signficantly associated with response time.

\end{alertblock}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{Materials}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received. Fourteen variables, capturing textual and user information of each question, were derived from the data.

% \textcolor{dblue!70}{\ding{228}} Device category the question pertains to
% 
% \textcolor{dblue!70}{\ding{228}} If the question was posted on a weekend or on a weekday
% 
% \textcolor{dblue!70}{\ding{228}} If the question's text contains end punctuation marks (. ? !)
% 
% \textcolor{dblue!70}{\ding{228}} If the question's text is in all lower case
% 
% \textcolor{dblue!70}{\ding{228}} If the question's title contains at least one word considered to be ``frequently-used'' among answered questions
% 
% \textcolor{dblue!70}{\ding{228}} If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question
% 
% \textcolor{dblue!70}{\ding{228}} If the question's title ends in a question mark
% 
% \textcolor{dblue!70}{\ding{228}} If the user edited or added information to the question's text after posting it
% 
% \textcolor{dblue!70}{\ding{228}} If the suer made an effort to solve the problem prior to asking the question
% 
% \textcolor{dblue!70}{\ding{228}} Average tag length
% 
% \textcolor{dblue!70}{\ding{228}} Average tag frequency
% 
% \textcolor{dblue!70}{\ding{228}} Text length
% 
% \textcolor{dblue!70}{\ding{228}} Title length
% 
% \textcolor{dblue!70}{\ding{228}} Number of line breaks to text length ratio

\end{block}

%------------------------------------------------

\begin{figure}
\includegraphics[width=1\linewidth]{FIG1.pdf}
\caption{Distribution of response times}
\label{fig1}
\end{figure}

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column

\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------
\begin{block}{Model Building}

\textcolor{dblue!70}{\ding{228}} Univariate analysis was used to identify which variables, as well as the optimal form of continuous variables (if transformations and splines should be used), to include in the final Cox model for five fold cross-validation.

\textcolor{dblue!70}{\ding{228}} In each iteration of cross-validation, the model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were averaged over each iteration and assessed as indicators of the model's performance.

\textcolor{dblue!70}{\ding{228}} The final model was fit to the full data and the proportional hazards assumption was assessed. 
\end{block}

\begin{block}{Results}

Of 7,760 questions in English, 4,951 (63.8\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2,159 hours (90 days). Figure 1 shows the distribution of response times for all questions analyzed.

Univariate analysis determined that all categorical predictors were signficantly associated with response time. The following transformations were made to continous variables:

\textcolor{dblue!70}{\ding{228}} $\sqrt{\textnormal{average tag frequency}}$

\textcolor{dblue!70}{\ding{228}} $\log\left({\textnormal{average tag length} + 1}\right)$, spline of 4 knots

\textcolor{dblue!70}{\ding{228}} $\log\left({\textnormal{device length} + 1}\right)$, spline of 5 knots

\textcolor{dblue!70}{\ding{228}} $\sqrt{\textnormal{line breaks / text length}}$, spline of 3 knots

\textcolor{dblue!70}{\ding{228}} $\log\left({\textnormal{text length}}\right)$, spline of 5 knots

Average performance metrics for test sets, training sets, as well as the full model are in Table \ref{table:1}. Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time. However, $R^2$ statistics and discrimination indexes are considerably low.

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.1

\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	Results
%----------------------------------------------------------------------------------------

% \begin{figure}
% \includegraphics[width=0.99\linewidth]{FIG2.eps}
% \caption{Kaplan-Meier estimated survival probability curve. Median survival time indicated by the dotted line. }
% \end{figure}

\begin{block}

Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.

\end{block}

\begin{table}[!htbp]
\centering
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\ 
  \hline
  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance metrics. (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)} 
\label{table:1}
\end{table}

\begin{block}

Table 2 displays the coefficients for predictors in the final model fit to the full data. As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.

Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.

The following are interpretations of select hazard coefficients in Table 2. Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.

\textcolor{dblue!70}{\ding{228}} The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.

\textcolor{dblue!70}{\ding{228}} The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2 - any content after this will now take up 2 columns width

%----------------------------------------------------------------------------------------
%	IMPORTANT RESULT
%----------------------------------------------------------------------------------------

% \begin{alertblock}{Important Result}
% 
% Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit.
% 
% \end{alertblock}

%----------------------------------------------------------------------------------------

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again

\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
%----------------------------------------------------------------------------------------

\end{column} % End of column 2.1

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

% \begin{block}{Results}
% 
% 
% 
% Nunc tempus venenatis facilisis. Curabitur suscipit consequat eros non porttitor. Sed a massa dolor, id ornare enim:
% 
% \begin{table}
% \vspace{2ex}
% \begin{tabular}{l l l}
% \toprule
% \textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
% \midrule
% Treatment 1 & 0.0003262 & 0.562 \\
% Treatment 2 & 0.0015681 & 0.910 \\
% Treatment 3 & 0.0009271 & 0.296 \\
% \bottomrule
% \end{tabular}
% \caption{Table caption}
% \end{table}
% 
% \end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2

\end{column} % End of the second column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Discussion}

The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design. Many users incorrectly specified the device names and tags. It is likely that these inconsistencies contributed to the final model's low predictive power. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions by restricting the tags or devices that users can include to a drop-down list. The CQA can also include more tips to guide users asking questions. Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

\end{block}

\begin{block}{Conclusion}

Predictors found to be significant in the final Cox regression model included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark. While overall the model was significant, its predictive performance was considerably low.

\end{block}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

% \begin{block}{Additional Information}
% 
% Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum. 
% \begin{itemize}
% \item Curabitur pellentesque dignissim
% \item Eu facilisis est tempus quis
% \item Duis porta consequat lorem
% \end{itemize}
% 
% \end{block}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

% \begin{block}{References}
% 
% \nocite{*} % Insert publications even if they are not cited in the poster
% \small{\bibliographystyle{unsrt}
% \bibliography{sample}\vspace{0.75in}}
% 
% \end{block}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

\begin{block}{Acknowledgements}

\small{\rmfamily{This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. We also thank iFixit for providing access to the CQA data.}} \\

\end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

% \setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
% \setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
% 
% \begin{alertblock}{Contact Information}
% 
% \begin{itemize}
% \item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
% \item Email: \href{mailto:john@smith.com}{john@smith.com}
% \item Phone: +1 (000) 111 1111
% \end{itemize}
% 
% \end{alertblock}
% 
% \begin{center}
% \begin{tabular}{ccc}
% \includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
% \end{tabular}
% \end{center}

%----------------------------------------------------------------------------------------

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2018-04-26 article/graphics.Rmd
increased size of font for poster

@@
   scale_y_continuous("Number of Questions") + 
-  theme(text = element_text(size = 10),
-        axis.text = element_text(size = 10))
+  theme(text = element_text(size = 20),
+        axis.text = element_text(size = 20))
 
@@
            xlim = c(0, 200), break.x.by = 20,
-           ylim = c(0, 1), break.y.by = 0.1,
+           ylim = c(0, 1), break.y.by = 0.2,
            surv.plot.height = 1, ggtheme = theme_bw(), 
@@
            legend = "none",
-           font.x = 10, font.y = 10, font.tickslab = 10)
+           font.x = 20, font.y = 20, font.tickslab = 20)
 

### 2018-04-27 CSM_poster/main.tex
more poster edits

@@
 
+\setbeamertemplate{caption}[numbered]{}
+
 \usepackage{pifont} % for dings
+
+% puts R2 in bold in table 3
+\makeatletter
+\DeclareRobustCommand\bfseries{%
+  \not@math@alphabet\bfseries\mathbf
+  \fontseries\bfdefault\selectfont
+  \boldmath % <-- added
+}
+\makeatother
 
@@
 
-\textcolor{dblue!70}{\ding{228}} \underline{Objective} Develop a Cox proportional hazards model to predict the survival probability, defined as the probability that a question remains unanswered beyond a certain time \textit{t}, of questions on the forum, with the goal of identifying variables signficantly associated with response time.
+\textcolor{dblue!70}{\ding{228}} \underline{Objective} Develop a Cox proportional hazards model to predict the survival probability (probability that a question remains unanswered beyond a certain time \textit{t}), of questions on the forum, with the goal of identifying variables significantly associated with response time.
 
@@
 
-\begin{block}{Materials}
+\begin{block}{Data}
 
-The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download).
-Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received.
-Fourteen variables, capturing textual and user information of each question, were derived from the data.
+Data analyzed contained 7,760 questions posted from April 2017 to July 2017.
+63.8\% received an answer.
+Shortest response time was 0.5 hours; longest was 2,159 hours (90 days).
+Figure 1 shows the distribution of response times for questions analyzed.
 
-% \textcolor{dblue!70}{\ding{228}} Device category the question pertains to
-% 
-% \textcolor{dblue!70}{\ding{228}} If the question was posted on a weekend or on a weekday
-% 
-% \textcolor{dblue!70}{\ding{228}} If the question's text contains end punctuation marks (. ? !)
-% 
-% \textcolor{dblue!70}{\ding{228}} If the question's text is in all lower case
-% 
-% \textcolor{dblue!70}{\ding{228}} If the question's title contains at least one word considered to be ``frequently-used'' among answered questions
-% 
-% \textcolor{dblue!70}{\ding{228}} If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question
-% 
-% \textcolor{dblue!70}{\ding{228}} If the question's title ends in a question mark
-% 
-% \textcolor{dblue!70}{\ding{228}} If the user edited or added information to the question's text after posting it
-% 
-% \textcolor{dblue!70}{\ding{228}} If the suer made an effort to solve the problem prior to asking the question
-% 
-% \textcolor{dblue!70}{\ding{228}} Average tag length
-% 
-% \textcolor{dblue!70}{\ding{228}} Average tag frequency
-% 
-% \textcolor{dblue!70}{\ding{228}} Text length
-% 
-% \textcolor{dblue!70}{\ding{228}} Title length
-% 
-% \textcolor{dblue!70}{\ding{228}} Number of line breaks to text length ratio
+Original variables in the data include: device name and category, question title, text, tags, new user status, post date and answer date.
+Fourteen variables, capturing textual and user information, were derived from the data.
 
@@
 %----------------------------------------------------------------------------------------
-\begin{block}{Model Building}
 
-\textcolor{dblue!70}{\ding{228}} Univariate analysis was used to identify which variables, as well as the optimal form of continuous variables (if transformations and splines should be used), to include in the final Cox model for five fold cross-validation.
+\begin{block}{Methods}
 
-\textcolor{dblue!70}{\ding{228}} In each iteration of cross-validation, the model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
-To assess performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
-The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were averaged over each iteration and assessed as indicators of the model's performance.
+\textcolor{dblue!70}{\ding{228}} \underline{Univariate Analysis} Used to identify which variables, as well as the optimal form of continuous variables (if transformations and restricted cubic splines should be applied), to include in the model.
 
-\textcolor{dblue!70}{\ding{228}} The final model was fit to the full data and the proportional hazards assumption was assessed. 
+\textcolor{dblue!70}{\ding{228}} \underline{Five Fold Cross-Validation} In each iteration, the model was built on the training set and used to predict hazard ratios on the test set.
+
+\textcolor{dblue!70}{\ding{228}} \underline{Assessing Performance} Predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
+Resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were averaged over each iteration and assessed as performance indicators.
+
+\textcolor{dblue!70}{\ding{228}} \underline{Final Model} The model was fit to the full data and proportional hazards assumption was assessed.
+
 \end{block}
 
-\begin{block}{Results}
+%----------------------------------------------------------------------------------------
+%	MODEL BUILDING RESULTS
+%----------------------------------------------------------------------------------------
 
-Of 7,760 questions in English, 4,951 (63.8\%) received an answer by the download date.
-The shortest response time was 0.5 hours.
-The longest was 2,159 hours (90 days).
-Figure 1 shows the distribution of response times for all questions analyzed.
+\begin{block}{Model Building Results}
 
-Univariate analysis determined that all categorical predictors were signficantly associated with response time. The following transformations were made to continous variables:
+Univariate analysis determined that all categorical predictors should be retained. Table \ref{table:continuous} shows the form of continuous predictors included in the final model.
 
-\textcolor{dblue!70}{\ding{228}} $\sqrt{\textnormal{average tag frequency}}$
+\renewcommand{\arraystretch}{1.2} % to increase the spacing between table rows
+\begin{table}[!htbp]
+\vspace{2ex}
+\begin{tabular}{| l | c |}
+    \hline
+    \textbf{Predictor} & \textbf{Knots} \\
+    \hline
+    $\sqrt{\textnormal{average tag frequency}}$ & 0 \\
+    $\log\left({\textnormal{average tag length} + 1}\right)$ & 4 \\
+    $\sqrt{\textnormal{line breaks / text length}}$ & 5 \\
+    $\sqrt{\textnormal{line breaks / text length}}$ & 3 \\
+    $\log\left({\textnormal{text length}}\right)$ & 5 \\
+    \hline
+\end{tabular}
+\caption{Form of continuous predictors included in the final model (knots indicates the number of knots included in restricted cubic splines}
+\label{table:continuous}
+\end{table}
 
-\textcolor{dblue!70}{\ding{228}} $\log\left({\textnormal{average tag length} + 1}\right)$, spline of 4 knots
-
-\textcolor{dblue!70}{\ding{228}} $\log\left({\textnormal{device length} + 1}\right)$, spline of 5 knots
-
-\textcolor{dblue!70}{\ding{228}} $\sqrt{\textnormal{line breaks / text length}}$, spline of 3 knots
-
-\textcolor{dblue!70}{\ding{228}} $\log\left({\textnormal{text length}}\right)$, spline of 5 knots
-
-Average performance metrics for test sets, training sets, as well as the full model are in Table \ref{table:1}.
-Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time.
-However, $R^2$ statistics and discrimination indexes are considerably low.
+Table \ref{table:1} displays the average performance metrics for models fit to test and training sets in cross-validation, as well as metrics for the model fit to the full data.
+Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
 
@@
 %----------------------------------------------------------------------------------------
-%	Results
+%	FINAL MODEL RESULTS
 %----------------------------------------------------------------------------------------
 
-% \begin{figure}
-% \includegraphics[width=0.99\linewidth]{FIG2.eps}
-% \caption{Kaplan-Meier estimated survival probability curve. Median survival time indicated by the dotted line. }
-% \end{figure}
+\begin{block}{Final Model Results}
 
-\begin{block}
+As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
 
-Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
-
-\end{block}
+Predictors found to be significant in the final model include: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
 
 \begin{table}[!htbp]
-\centering
-\begin{tabular}{|r|r|r|r|r|r|r|r|}
+\vspace{3ex}
+\begin{tabular}{|r|r|r|r|r|r|r|r|} % FIX THE R2 HERE 
   \hline
@@
 \end{tabular}
-\caption{Performance metrics. (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)} 
+\caption{Performance metrics (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)} 
 \label{table:1}
@@
 
-\begin{block}
+Assessing the proportional hazards assumption indicated that several levels of the device categorization variable violated the assumption.
 
-Table 2 displays the coefficients for predictors in the final model fit to the full data.
-As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001).
-Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
+\end{block}
 
-Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
+%----------------------------------------------------------------------------------------
+%	INTERPRETING HAZARD
+%----------------------------------------------------------------------------------------
 
-The following are interpretations of select hazard coefficients in Table 2.
+\begin{block}{Interpreting Hazard}
+
 Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
+Table \ref{table:hr} contains interpretations of select hazard coefficients of the final model.
 
-\textcolor{dblue!70}{\ding{228}} The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+\end{block}
 
-\textcolor{dblue!70}{\ding{228}} The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+%----------------------------------------------------------------------------------------
+%	SUGGESTIONS
+%----------------------------------------------------------------------------------------
+
+\begin{block}{Suggestions}
+
+Results from this analysis lead to suggestions for changes in CQA design.
+Many users incorrectly specified device names and tags (e.g.
+a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One'').
 
@@
 
-%----------------------------------------------------------------------------------------
-%	IMPORTANT RESULT
-%----------------------------------------------------------------------------------------
-
-% \begin{alertblock}{Important Result}
-% 
-% Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit.
-% 
-% \end{alertblock}
-
-%----------------------------------------------------------------------------------------
-
 \begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again
@@
 \begin{column}{\onecolwid} % The second column within column 2 (column 2.2)
-
-%----------------------------------------------------------------------------------------
-%	RESULTS
-%----------------------------------------------------------------------------------------
-
-% \begin{block}{Results}
-% 
-% 
-% 
-% Nunc tempus venenatis facilisis. Curabitur suscipit consequat eros non porttitor. Sed a massa dolor, id ornare enim:
-% 
-% \begin{table}
-% \vspace{2ex}
-% \begin{tabular}{l l l}
-% \toprule
-% \textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
-% \midrule
-% Treatment 1 & 0.0003262 & 0.562 \\
-% Treatment 2 & 0.0015681 & 0.910 \\
-% Treatment 3 & 0.0009271 & 0.296 \\
-% \bottomrule
-% \end{tabular}
-% \caption{Table caption}
-% \end{table}
-% 
-% \end{block}
-
-%----------------------------------------------------------------------------------------
 
@@
 %----------------------------------------------------------------------------------------
-%	CONCLUSION
+%	HAZARD INTERPRETATIONS + SUGGESTIONS 
 %----------------------------------------------------------------------------------------
 
-\begin{block}{Discussion}
+\begin{block}
 
-The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design.
-Many users incorrectly specified the device names and tags.
+\renewcommand{\arraystretch}{1.15} % to increase the spacing between table rows
+\begin{table}[!htbp]
+\begin{tabular}{|p{26cm}|} 
+  \hline
+  The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+\\ \hline
+  The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+\\ \hline
+  The estimated hazard of receiving an answer for questions posted on a weekend is 13\% lower (95\% CI (7\%, 18\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
+\\ \hline
+  \hline
+\end{tabular}
+\caption{Hazard coefficient interpretations} 
+\label{table:hr}
+\end{table}
+
 It is likely that these inconsistencies contributed to the final model's low predictive power.
-As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions by restricting the tags or devices that users can include to a drop-down list.
+This, along with the results of the final model, reveal some ways the CQA can be structured to potentially decrease response times.
+As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions by restricting tags or devices users can include to a drop-down list.
 The CQA can also include more tips to guide users asking questions.
@@
 \end{block}
-
-\begin{block}{Conclusion}
-
-Predictors found to be significant in the final Cox regression model included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
-While overall the model was significant, its predictive performance was considerably low.
-
-\end{block}
-
-%----------------------------------------------------------------------------------------
-%	ADDITIONAL INFORMATION
-%----------------------------------------------------------------------------------------
-
-% \begin{block}{Additional Information}
-% 
-% Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum. 
-% \begin{itemize}
-% \item Curabitur pellentesque dignissim
-% \item Eu facilisis est tempus quis
-% \item Duis porta consequat lorem
-% \end{itemize}
-% 
-% \end{block}
-
-%----------------------------------------------------------------------------------------
-%	REFERENCES
-%----------------------------------------------------------------------------------------
-
-% \begin{block}{References}
-% 
-% \nocite{*} % Insert publications even if they are not cited in the poster
-% \small{\bibliographystyle{unsrt}
-% \bibliography{sample}\vspace{0.75in}}
-% 
-% \end{block}
 

### 2018-04-27 CSM_poster/main.tex
convert final model results to bulleted list

@@
 
-As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
+\underline{Final model statistics}
 
-Predictors found to be significant in the final model include: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
+\textcolor{dblue!70}{\ding{228}} PLR $=$ 1265.29 (p-value \textless0.0001)
+
+\textcolor{dblue!70}{\ding{228}} $R^2 =$ 0.15
+
+\textcolor{dblue!70}{\ding{228}} Somers' \textit{Dxy} $=$ 0.27
+
+\underline{Significant Predictors} Device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, whether or not the question's title ends in a question mark.
 

### 2018-04-27 CSM_poster/main.tex
remove contact info
edit method section

@@
 \textcolor{dblue!70}{\ding{228}} \underline{Assessing Performance} Predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
-Resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were averaged over each iteration and assessed as performance indicators.
+Resulting Nagelkerke's $R^2$, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio (PLR) and p-value, were averaged over each iteration and assessed as performance indicators.
 
@@
 
-%----------------------------------------------------------------------------------------
-%	CONTACT INFORMATION
-%----------------------------------------------------------------------------------------
-
-% \setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
-% \setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
-% 
-% \begin{alertblock}{Contact Information}
-% 
-% \begin{itemize}
-% \item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
-% \item Email: \href{mailto:john@smith.com}{john@smith.com}
-% \item Phone: +1 (000) 111 1111
-% \end{itemize}
-% 
-% \end{alertblock}
-% 
-% \begin{center}
-% \begin{tabular}{ccc}
-% \includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
-% \end{tabular}
-% \end{center}
-
-%----------------------------------------------------------------------------------------
-
 \end{column} % End of the third column

### 2018-05-03 CSM_poster/main.tex
test commit
more edits

@@
 \makeatother
+
+\usepackage{multirow}
+\usepackage{color,soul}
+\usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 
@@
 
-\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
+\addtobeamertemplate{block end}{}{\vspace*{0.5ex}} % White space under blocks
 \addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks
@@
 
-\textcolor{dblue!70}{\ding{228}} iFixit's online question and answer forum, \textit{Answers}, features over 120,000 user-asked questions related specifically to device repair.
+\vspace{0.5ex}
+
+iFixit's online question and answer forum, \textit{Answers}, features over 120,000 user-asked questions related specifically to device repair.
 Analysis of question response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how forum design can be improved.
 
-\textcolor{dblue!70}{\ding{228}} \underline{Objective} Develop a Cox proportional hazards model to predict the survival probability (probability that a question remains unanswered beyond a certain time \textit{t}), of questions on the forum, with the goal of identifying variables significantly associated with response time.
+\vspace{2ex}
+
+\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Objective}} Develop a Cox proportional hazards model to predict the survival probability (probability that a question remains unanswered beyond a certain time \textit{t}), of questions on the forum, with the goal of identifying variables significantly associated with response time.
+
+\vspace{0.5ex}
 
@@
 
-Data analyzed contained 7,760 questions posted from April 2017 to July 2017.
-63.8\% received an answer.
-Shortest response time was 0.5 hours; longest was 2,159 hours (90 days).
-Figure 1 shows the distribution of response times for questions analyzed.
+\textcolor{dblue!70}{\ding{228}} 7,760 questions from April 2017 to July 2017.
 
-Original variables in the data include: device name and category, question title, text, tags, new user status, post date and answer date.
-Fourteen variables, capturing textual and user information, were derived from the data.
+\vspace{0.5ex}
 
-\end{block}
+\textcolor{dblue!70}{\ding{228}} 63.8\% received an answer
 
-%------------------------------------------------
+\vspace{0.5ex}
+
+\textcolor{dblue!70}{\ding{228}} Shortest response time: 0.5 hours
+
+\vspace{0.5ex}
+
+\textcolor{dblue!70}{\ding{228}} Longest response time: 2,159 hours (90 days)
 
 \begin{figure}
+\vspace{2ex}
 \includegraphics[width=1\linewidth]{FIG1.pdf}
@@
 \end{figure}
+
+Original variables include: device, question title, text, tags, new user status, post date and answer date. Fourteen variables, capturing textual and user information, were derived.
+
+\end{block}
+
+%----------------------------------------------------------------------------------------
+
+\end{column} % End of the first column
+
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+\begin{column}{\onecolwid} % The first column
+
+%----------------------------------------------------------------------------------------
+%	METHODS
+%----------------------------------------------------------------------------------------
+
+\begin{block}{Methods}
+
+\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Univariate Analysis}}
+
+\vspace{0.5ex}
+
+Used to identify which variables, as well as the optimal form of continuous variables (if transformations and restricted cubic splines should be applied), to include in the model.
+
+\vspace{1ex}
+
+\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Five Fold Cross-Validation}}
+
+\vspace{0.5ex}
+
+In each iteration, the model was built on the training set and used to predict hazard ratios on the test set.
+
+\vspace{1ex}
+
+\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Assess Performance}}
+
+\vspace{0.5ex}
+
+Predicted hazard ratios were entered into separate Cox models as the single predictor.
+Resulting $R^2$, concordance, Somers' \textit{Dxy}, partial likelihood ratio (PLR) and p-value, were averaged over each iteration and assessed.
+
+\vspace{1ex}
+
+\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Final Model}}
+
+\vspace{0.5ex}
+
+The model was fit to the full data and proportional hazards assumption was assessed.
+
+\vspace{1.5ex}
+
+\end{block}
+
+%----------------------------------------------------------------------------------------
+%	RESULTS
+%----------------------------------------------------------------------------------------
+
+\begin{block}{Cross-Validation Results}
+
+Table \ref{table:1} displays average performance metrics achieved in cross-validation, as well as for the model fit to the full data.
+
+\begin{table}[!htbp]
+\vspace{3ex}
+\begin{tabular}{|r|r|r|r|r|r|r|r|}
+  \hline
+  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\
+  \hline
+  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\
+  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
+  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\
+  \hline
+\end{tabular}
+\caption{Performance metrics (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
+\label{table:1}
+\end{table}
+\end{block}
+
+\begin{block}{Final Model Statistics}
+
+\textcolor{dblue!70}{\ding{228}} PLR $=$ 1265.29 (p-value \textless0.0001)
+
+\vspace{0.5ex}
+
+\textcolor{dblue!70}{\ding{228}} $R^2 =$ 0.15
+
+\vspace{0.5ex}
+
+\textcolor{dblue!70}{\ding{228}} Somers' \textit{Dxy} $=$ 0.27
+
+\vspace{0.5ex}
+
+\textcolor{dblue!70}{\ding{228}} Several levels of the device categorization variable violated the proportional hazards assumption
+
+\end{block}
 
@@
 %----------------------------------------------------------------------------------------
-%	METHODS
+
+%----------------------------------------------------------------------------------------
+%	INTERPRETING HAZARD
 %----------------------------------------------------------------------------------------
 
-\begin{block}{Methods}
+\begin{block}{Interpreting Hazard}
 
-\textcolor{dblue!70}{\ding{228}} \underline{Univariate Analysis} Used to identify which variables, as well as the optimal form of continuous variables (if transformations and restricted cubic splines should be applied), to include in the model.
+Controlling for all other predictors, the estimated hazard of receiving an answer is:
 
-\textcolor{dblue!70}{\ding{228}} \underline{Five Fold Cross-Validation} In each iteration, the model was built on the training set and used to predict hazard ratios on the test set.
+\vspace{1ex}
 
-\textcolor{dblue!70}{\ding{228}} \underline{Assessing Performance} Predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time.
-Resulting Nagelkerke's $R^2$, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio (PLR) and p-value, were averaged over each iteration and assessed as performance indicators.
+\textcolor{dblue!70}{\ding{228}} 154\% higher (95\% CI (132\%, 179\%)) for Apple products vs. Android/other phones
 
-\textcolor{dblue!70}{\ding{228}} \underline{Final Model} The model was fit to the full data and proportional hazards assumption was assessed.
+\vspace{0.75ex}
 
-\end{block}
+\textcolor{dblue!70}{\ding{228}} 13\% lower (95\% CI (7\%, 18\%)) for questions posted on the weekend vs. weekday
 
-%----------------------------------------------------------------------------------------
-%	MODEL BUILDING RESULTS
-%----------------------------------------------------------------------------------------
-
-\begin{block}{Model Building Results}
-
-Univariate analysis determined that all categorical predictors should be retained. Table \ref{table:continuous} shows the form of continuous predictors included in the final model.
-
-\renewcommand{\arraystretch}{1.2} % to increase the spacing between table rows
-\begin{table}[!htbp]
-\vspace{2ex}
-\begin{tabular}{| l | c |}
-    \hline
-    \textbf{Predictor} & \textbf{Knots} \\
-    \hline
-    $\sqrt{\textnormal{average tag frequency}}$ & 0 \\
-    $\log\left({\textnormal{average tag length} + 1}\right)$ & 4 \\
-    $\sqrt{\textnormal{line breaks / text length}}$ & 5 \\
-    $\sqrt{\textnormal{line breaks / text length}}$ & 3 \\
-    $\log\left({\textnormal{text length}}\right)$ & 5 \\
-    \hline
-\end{tabular}
-\caption{Form of continuous predictors included in the final model (knots indicates the number of knots included in restricted cubic splines}
-\label{table:continuous}
-\end{table}
-
-Table \ref{table:1} displays the average performance metrics for models fit to test and training sets in cross-validation, as well as metrics for the model fit to the full data.
-Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
+\vspace{1ex}
 
@@
 %----------------------------------------------------------------------------------------
-%	FINAL MODEL RESULTS
-%----------------------------------------------------------------------------------------
 
-\begin{block}{Final Model Results}
+\begin{block}{Forum Design Suggestions}
 
-\underline{Final model statistics}
+\textcolor{dblue!70}{\ding{228}} Rather than allowing users to enter any tag or device name, restrict options to a drop-down list
 
-\textcolor{dblue!70}{\ding{228}} PLR $=$ 1265.29 (p-value \textless0.0001)
+\vspace{0.5ex}
 
-\textcolor{dblue!70}{\ding{228}} $R^2 =$ 0.15
-
-\textcolor{dblue!70}{\ding{228}} Somers' \textit{Dxy} $=$ 0.27
-
-\underline{Significant Predictors} Device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, whether or not the question's title ends in a question mark.
-
-\begin{table}[!htbp]
-\vspace{3ex}
-\begin{tabular}{|r|r|r|r|r|r|r|r|} % FIX THE R2 HERE 
-  \hline
-  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\ 
-  \hline
-  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
-  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
-  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
-  \hline
-\end{tabular}
-\caption{Performance metrics (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)} 
-\label{table:1}
-\end{table}
-
-Assessing the proportional hazards assumption indicated that several levels of the device categorization variable violated the assumption.
-
-\end{block}
-
-%----------------------------------------------------------------------------------------
-%	INTERPRETING HAZARD
-%----------------------------------------------------------------------------------------
-
-\begin{block}{Interpreting Hazard}
-
-Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
-Table \ref{table:hr} contains interpretations of select hazard coefficients of the final model.
-
-\end{block}
-
-%----------------------------------------------------------------------------------------
-%	SUGGESTIONS
-%----------------------------------------------------------------------------------------
-
-\begin{block}{Suggestions}
-
-Results from this analysis lead to suggestions for changes in CQA design.
-Many users incorrectly specified device names and tags (e.g.
-a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One'').
+\textcolor{dblue!70}{\ding{228}} Include more tips to guide users when asking questions
 
@@
 
-\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again
+%----------------------------------------------------------------------------------------
+\begin{block}{Final Model Coefficients}
 
-\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
-%----------------------------------------------------------------------------------------
-
-\end{column} % End of column 2.1
-
-\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)
-
-\end{column} % End of column 2.2
-
-\end{columns} % End of the split of column 2
-
-\end{column} % End of the second column
-
-\begin{column}{\sepwid}\end{column} % Empty spacer column
-
-\begin{column}{\onecolwid} % The third column
-
-%----------------------------------------------------------------------------------------
-%	HAZARD INTERPRETATIONS + SUGGESTIONS 
-%----------------------------------------------------------------------------------------
-
-\begin{block}
-
-\renewcommand{\arraystretch}{1.15} % to increase the spacing between table rows
 \begin{table}[!htbp]
-\begin{tabular}{|p{26cm}|} 
+% \centering
+\begin{tabular}{|L{10cm} L{17.5cm}|c|c|}
   \hline
-  The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
-\\ \hline
-  The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
-\\ \hline
-  The estimated hazard of receiving an answer for questions posted on a weekend is 13\% lower (95\% CI (7\%, 18\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
-\\ \hline
-  \hline
+ \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
+  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
+                  & Camera & -0.32 (0.090) & \\ 
+                  & Electronics & -0.01 (0.078)  & \\ 
+                  & Game Console & 0.24 (0.083)  & \\ 
+                  & Home & 0.34 (0.070) &  \\ 
+                  & Other & -0.13 (0.056)  & \\ 
+                  & PC & 0.28 (0.060) &  \\ 
+                  & Tablet & -0.16 (0.081)  & \\ 
+                  & Vehicle & 0.40 (0.069)  & \\
+                  & Android/Other Phone (reference) & --- & \\ \hline
+  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
+  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
+  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
+  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
+  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
+  \multicolumn{2}{|L{30cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
+  \multicolumn{2}{|L{30cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
+  \multicolumn{2}{|L{30cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
+  \multicolumn{2}{|L{30cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
+  \multicolumn{2}{|L{30cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
 \end{tabular} 
-\caption{Hazard coefficient interpretations} 
-\label{table:hr}
+\caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
+\label{table:4}
 \end{table}
 
-It is likely that these inconsistencies contributed to the final model's low predictive power.
-This, along with the results of the final model, reveal some ways the CQA can be structured to potentially decrease response times.
-As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions by restricting tags or devices users can include to a drop-down list.
-The CQA can also include more tips to guide users asking questions.
-Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
-
 \end{block}
-
-%----------------------------------------------------------------------------------------
-%	ACKNOWLEDGEMENTS
-%----------------------------------------------------------------------------------------
-
-\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color
 
@@
 
-\end{column} % End of the third column
+%----------------------------------------------------------------------------------------
 
+\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again
+
+\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
+
+%----------------------------------------------------------------------------------------
+
+\end{column} % End of column 2.1
+
+\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)
+
+% \begin{block}{Acknowledgements}
+% 
+% \small{\rmfamily{This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
+We also thank iFixit for providing access to the CQA data.}} \\
+% 
+% \end{block}
+
+%----------------------------------------------------------------------------------------
+
+\end{column} % End of column 2.2
+
+\end{columns} % End of the split of column 2
+
+\end{column} % End of the second column
+
+% \begin{column}{\sepwid}\end{column} % Empty spacer column
+
+%----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
+%	ACKNOWLEDGEMENTS
+%----------------------------------------------------------------------------------------
+
+% \setbeamercolor{block title}{fg=red,bg=white} % Change the block title color
+
+% \begin{block}{Acknowledgements}
+% 
+% \small{\rmfamily{This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
+We also thank iFixit for providing access to the CQA data.}} \\
+% 
+% \end{block}
+% 
+% \end{column} % End of the third column
+% 
 \end{columns} % End of all the columns in the poster

### 2018-05-03 CSM_poster/main.tex
edits

@@
 \usepackage{pifont} % for dings
+
+\usepackage{caption}
 
@@
 
-\addtobeamertemplate{block end}{}{\vspace*{0.5ex}} % White space under blocks
+\addtobeamertemplate{block end}{}{\vspace*{0ex}} % White space under blocks
 \addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks
 
-\setlength{\belowcaptionskip}{2ex} % White space under figures
+\setlength{\belowcaptionskip}{0ex} % White space under figures
 \setlength\belowdisplayshortskip{2ex} % White space under equations
@@
 
+\vspace{0.5ex}
+
+\textcolor{dblue!70}{\ding{228}} Median response time: 8.79 hours
+
+\end{block}
+
 \begin{figure}
-\vspace{2ex}
+\captionsetup{skip=40pt}
+\vspace{4ex}
 \includegraphics[width=1\linewidth]{FIG1.pdf}
@@
 \end{figure}
-
-Original variables include: device, question title, text, tags, new user status, post date and answer date. Fourteen variables, capturing textual and user information, were derived.
-
-\end{block}
 
@@
 
+\begin{figure}
+\captionsetup{skip=30pt}
+\includegraphics[width=1\linewidth]{question}
+\caption{Example of a question posted on the forum}
+\label{fig1}
+\end{figure}
+
+\vspace{2ex}
+
 \begin{block}{Methods}
@@
 
-Used to identify which variables, as well as the optimal form of continuous variables (if transformations and restricted cubic splines should be applied), to include in the model.
+Used to identify which variables to include
 
@@
 
-In each iteration, the model was built on the training set and used to predict hazard ratios on the test set.
-
-\vspace{1ex}
-
-\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Assess Performance}}
+Model was built on the training set and used to predict hazard ratios on the test set
 
@@
 
-Predicted hazard ratios were entered into separate Cox models as the single predictor.
-Resulting $R^2$, concordance, Somers' \textit{Dxy}, partial likelihood ratio (PLR) and p-value, were averaged over each iteration and assessed.
+Predicted hazard ratios were entered into separate Cox models; resulting statistics were averaged over each iteration and assessed
+
+% \vspace{1ex}
+% 
+% \textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Assess Performance}} 
+% 
+% \vspace{0.5ex}
 
@@
 
-The model was fit to the full data and proportional hazards assumption was assessed.
+Model was fit to the full data and proportional hazards assumption was assessed
 
@@
 
-\begin{block}{Cross-Validation Results}
-
-Table \ref{table:1} displays average performance metrics achieved in cross-validation, as well as for the model fit to the full data.
+% \begin{block}{Cross-Validation Results}
+% 
+% \end{block}
 
 \begin{table}[!htbp]
+\captionsetup{skip=40pt}
 \vspace{3ex}
@@
 \end{tabular}
-\caption{Performance metrics (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
+\caption{Performance metrics achieved in cross-validation and for the model fit to the full data (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
 \label{table:1}
 \end{table}
-\end{block}
+
+\vspace{2ex}
 
@@
 
-\textcolor{dblue!70}{\ding{228}} PLR $=$ 1265.29 (p-value \textless0.0001)
+\textcolor{dblue!70}{\ding{228}} LR $=$ 1265.29 (p-value \textless0.0001)
 
@@
 
-\begin{block}{Interpreting Hazard}
-
-Controlling for all other predictors, the estimated hazard of receiving an answer is:
-
-\vspace{1ex}
-
-\textcolor{dblue!70}{\ding{228}} 154\% higher (95\% CI (132\%, 179\%)) for Apple products vs. Android/other phones
-
-\vspace{0.75ex}
-
-\textcolor{dblue!70}{\ding{228}} 13\% lower (95\% CI (7\%, 18\%)) for questions posted on the weekend vs. weekday
-
-\vspace{1ex}
-
-\end{block}
-
 %----------------------------------------------------------------------------------------
@@
 
-\begin{block}{Forum Design Suggestions}
-
-\textcolor{dblue!70}{\ding{228}} Rather than allowing users to enter any tag or device name, restrict options to a drop-down list
-
-\vspace{0.5ex}
-
-\textcolor{dblue!70}{\ding{228}} Include more tips to guide users when asking questions
-
-\end{block}
-
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\begin{block}{Final Model Coefficients}
 
 \begin{table}[!htbp]
-% \centering
+\captionsetup{width=0.85\textwidth, skip=50pt}
+\centering
 \begin{tabular}{|L{10cm} L{17.5cm}|c|c|}
@@
 \end{tabular} 
-\caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
+\caption{Coefficients for predictors in the final model (Continuous predictors fit with restricted cubic splines (text length, average tag length, device name length, ratio of number of newlines to text length) are not shown)}
 \label{table:4}
 \end{table}
-
-\end{block}
-
-\begin{block}{Acknowledgements}
-
-\small{\rmfamily{This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-We also thank iFixit for providing access to the CQA data.}} \\
-
-\end{block}
 
@@
 
+\begin{block}{Select Interpretations}
+
+Controlling for all other predictors, the estimated hazard of receiving an answer is:
+
+\vspace{1ex}
+
+\textcolor{dblue!70}{\ding{228}} 154\% higher (95\% CI (132\%, 179\%)) for Apple products vs. Android/other phones
+
+\vspace{1ex}
+
+\textcolor{dblue!70}{\ding{228}} 13\% lower (95\% CI (7\%, 18\%)) for questions posted on the weekend vs. weekday
+
+\vspace{1ex}
+
+\textcolor{dblue!70}{\ding{228}} 25\% lower (95\% CI (19\%, 29\%)) for questions with titles containing at least one frequently-used word among unanswered question titles vs otherwise
+
+\end{block}
+
 %----------------------------------------------------------------------------------------
@@
 
-% \begin{block}{Acknowledgements}
-% 
-% \small{\rmfamily{This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-We also thank iFixit for providing access to the CQA data.}} \\
-% 
-% \end{block}
+\begin{block}{Forum Design Suggestions}
+
+\textcolor{dblue!70}{\ding{228}} Rather than allowing users to enter any tag or device name, restrict options to a drop-down list
+
+\vspace{0.5ex}
+
+\textcolor{dblue!70}{\ding{228}} Include more tips to guide users when asking questions
+
+\end{block}
+
+\vspace{1ex}
+
+\begin{block}{Acknowledgements}
+
+This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. We also thank iFixit for providing access to the \textit{Answers} data.
+
+\end{block}
 

### 2018-05-03 CSM_poster/main.tex
edits

@@
 
-iFixit's online question and answer forum, \textit{Answers}, features over 120,000 user-asked questions related specifically to device repair.
+iFixit's online Q\&A forum, \textit{Answers}, features over 120,000 questions related specifically to device repair.
 Analysis of question response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how forum design can be improved.
@@
 
-\textcolor{dblue!70}{\ding{228}} Longest response time: 2,159 hours (90 days)
+\textcolor{dblue!70}{\ding{228}} Median response time: 8.79 hours
 
@@
 
-\textcolor{dblue!70}{\ding{228}} Median response time: 8.79 hours
+\textcolor{dblue!70}{\ding{228}} Longest response time: 2,159 hours (90 days)
 
@@
 \begin{figure}
-\captionsetup{skip=30pt}
-\includegraphics[width=1\linewidth]{question}
+\captionsetup{skip=25pt}
+\includegraphics[width=1.08\linewidth]{question}
 \caption{Example of a question posted on the forum}
@@
 
-Model was built on the training set and used to predict hazard ratios on the test set
+Model was built on training sets and used to predict hazard ratios on test sets
 
@@
 
-Predicted hazard ratios were entered into separate Cox models; resulting statistics were averaged over each iteration and assessed
+Predicted hazard ratios were entered into separate Cox models; resulting metrics were averaged over each iteration and assessed
 
@@
 
-Model was fit to the full data and proportional hazards assumption was assessed
+Model was fit to the full data and proportional hazards (PH) assumption was assessed
 
@@
 \captionsetup{skip=40pt}
-\vspace{3ex}
+\vspace{2ex}
 \begin{tabular}{|r|r|r|r|r|r|r|r|}
@@
 
-\textcolor{dblue!70}{\ding{228}} Several levels of the device categorization variable violated the proportional hazards assumption
+\textcolor{dblue!70}{\ding{228}} Device category violated the PH assumption
 
@@
 
-\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column
-
-\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)
-
 %----------------------------------------------------------------------------------------
 
-%----------------------------------------------------------------------------------------
-%	INTERPRETING HAZARD
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-
-\end{column} % End of column 2.1
-
-\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)
-
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-
-\end{column} % End of column 2.2
-
-\end{columns} % End of the split of column 2 - any content after this will now take up 2 columns width
-
-%----------------------------------------------------------------------------------------
+\begin{block}{Final Model Coefficients}
+\end{block}
 
 \begin{table}[!htbp]
-\captionsetup{width=0.85\textwidth, skip=50pt}
+\captionsetup{width=0.85\textwidth, skip=40pt}
 \centering
@@
 \end{tabular} 
-\caption{Coefficients for predictors in the final model (Continuous predictors fit with restricted cubic splines (text length, average tag length, device name length, ratio of number of newlines to text length) are not shown)}
-\label{table:4}
+\caption{Not shown: continuous predictors fit with restricted cubic splines (text length, average tag length, device name length, ratio of number of newlines to text length)} 
 \end{table}
@@
 
-\vspace{0.5ex}
+\vspace{0.75ex}
 
-\textcolor{dblue!70}{\ding{228}} Include more tips to guide users when asking questions
+\textcolor{dblue!70}{\ding{228}} Include tips to guide users asking questions
 
@@
 
-This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. We also thank iFixit for providing access to the \textit{Answers} data.
+\textcolor{dblue!70}{\ding{228}} Research was supported by the Bill and Linda Frost fund of California Polytechnic State University, San Luis Obispo.
+We also thank iFixit for providing access to the \textit{Answers} data.
 

### 2018-05-03 CSM_poster/main.tex
adjust spacing
spacing adjustments

@@
 
+\vspace{1.5ex}
+
 \begin{block}{Data}
@@
 
-\vspace{2ex}
+\vspace{2.5ex}
 
@@
 
-\vspace{0.5ex}
+\vspace{0.25ex}
 
@@
 
-\vspace{1ex}
+\vspace{0.25ex}
 
@@
 
-% \vspace{1ex}
-% 
-% \textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Assess Performance}} 
-% 
-% \vspace{0.5ex}
-
-\vspace{1ex}
+\vspace{0.25ex}
 
@@
 
-\vspace{1.5ex}
+\vspace{2.5ex}
 
@@
 \captionsetup{skip=40pt}
-\vspace{2ex}
+\vspace{2.5ex}
 \begin{tabular}{|r|r|r|r|r|r|r|r|}
@@
 
-\vspace{2ex}
+\vspace{3ex}
 
@@
 
-\vspace{0.5ex}
+\vspace{0.35ex}
 
@@
 
+\vspace{1.8ex}
+
 %----------------------------------------------------------------------------------------
@@
 
-\textcolor{dblue!70}{\ding{228}} 25\% lower (95\% CI (19\%, 29\%)) for questions with titles containing at least one frequently-used word among unanswered question titles vs otherwise
+\textcolor{dblue!70}{\ding{228}} 25\% lower (95\% CI (19\%, 29\%)) for questions with titles containing at least one frequently-used word among unanswered questions vs otherwise
 
@@
 
-\vspace{1ex}
+\vspace{3ex}
 
@@
 
-\textcolor{dblue!70}{\ding{228}} Research was supported by the Bill and Linda Frost fund of California Polytechnic State University, San Luis Obispo.
-We also thank iFixit for providing access to the \textit{Answers} data.
+\small{\rmfamily{Research was supported by the Bill and Linda Frost fund of California Polytechnic State University, San Luis Obispo.
+We also thank iFixit for providing access to the \textit{Answers} data.}} \\
 

### 2018-07-25 article/manuscript.Rnw
add files/changes for new submission

@@
-\documentclass[preprint]{elsarticle}
+\documentclass[]{interact}
 
-\usepackage{lineno,hyperref}
-\modulolinenumbers[5]
+% \usepackage{lineno,hyperref}
+% \modulolinenumbers[5]
 
@@
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\usepackage{caption}
+% \usepackage{caption}
 
@@
 
-\begin{frontmatter}
 \title{Survival Analysis of Questions Posted on the iFixit Answers Forum}
 
-\author[cp]{L.K.~Oshita\corref{cor1}}
-\cortext[cor1]{Corresponding author}
-\ead{l.oshita@yahoo.com}
+\author{
+\name{L.K.Oshita\textsuperscript{a}\thanks{CONTACT L.K.Oshita. Email: l.oshita@yahoo.com}, A.Pileggi\textsuperscript{b}}
+\affil{\textsuperscript{a}iFixit; )
+}
 
-\author[ifixit]{A.~Pileggi}
-\author[cp]{S.~Pileggi}
+\maketitle
 
-\address[cp]{Department of Statistics, California Polytechnic State University, San Luis Obispo, CA 93407, United States}
-\address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
+% \author[cp]{L.K.~Oshita\corref{cor1}}
+% \cortext[cor1]{Corresponding author}
+% \ead{l.oshita@yahoo.com}
+
+% \author[ifixit]{A.~Pileggi}
+% \author[cp]{S.~Pileggi}
+
+% \address[cp]{Department of Statistics, California Polytechnic State University, San Luis Obispo, CA 93407, United States}
+% \address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
 
 \begin{abstract} 
-Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information.
-One such example of a CQA is iFixit's \textit{Answers} forum.
-This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users.
-An important aspect of these CQAs, for both users and the forum, is question response time.
+iFixit's community driven online question and answer forum (CQA), \textif{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair.
+This platform allows users to ask questions regarding repairs, and for both repair experts and everyday users to provide answers and feedback.
 This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
@@
 
-\begin{keyword}
+\begin{keywords}
 Cox regression \sep CQA forum \sep response time \sep survival analysis \sep survival probabilty 
-\end{keyword}
-
-\end{frontmatter}
+\end{keywords}
 
@@
 
-Community-driven online question and answer forums have become widely-used sources of information.
-These online platforms feature thousands of user-posted questions and answers and receive millions of visits every month.
+Community-driven online question and answer forums feature thousands of user-posted questions and answers and receive millions of visits every month.
+As such, they have become widely-used sources of information.
 The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit provides over 35,000 free online repair guides and sells the specialized tools and parts needed for such repairs.
-This company's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to help them save money and reduce electronic waste.
+Founded in 2003, iFixit equips users with the knowledge and tools necessary to both repair their broken devices and reduce electronic waste, by providing over 35,000 free online repair guides.
 
@@
 However, analysis and prediction of response times on CQAs have not been thoroughly investigated.
-There is need for further analysis of forum response times, as the majority of existing research focuses on assessing and predicting question or answer quality.
+There is need for further analysis in this area, as the majority of existing research focuses on assessing and predicting question or answer quality.
 This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict survival probabilities of questions.
@@
 % Table of derived predictors
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{|L{2cm}|L{10cm}|}
+\begin{table}%[!htbp]
+\tbl{Categorical and continuous variables derived}
+% \centering
+{\begin{tabular}{|L{2cm}|L{10cm}|}
   \hline
@@
   & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
-\end{tabular}
-\caption{Categorical and continuous variables derived}
+\end{tabular}}
+% \caption{Categorical and continuous variables derived}
 \label{table:1}
@@
 % Splines Square root transformation of the average tag frequency
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{| L{5cm} | l | l |}
+\begin{table}% [!htbp]
+% \centering
+\tbl{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
+{\begin{tabular}{| L{5cm} | l | l |}
   \hline
@@
   \hline
-\end{tabular}
-\caption{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
+\end{tabular}}
 \label{table:2}
@@
 \begin{table}[!htbp]
-\centering
-\begin{tabular}{|r|r|r|r|r|r|r|r|}
+% \centering
+\tbl{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)}
+{\begin{tabular}{|r|r|r|r|r|r|r|r|}
   \hline
@@
    \hline
-\end{tabular}
-\caption{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
+\end{tabular}}
 \label{table:3}
@@
 \begin{table}[!htbp]
-\centering
-\begin{tabular}{|l L{5.5cm}|c|c|}
+% \centering
+\tbl{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
+{\begin{tabular}{|l L{5.5cm}|c|c|}
   \hline
@@
   \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
-\end{tabular} 
-\caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
+\end{tabular}}
 \label{table:4}
@@
 \begin{table}[!htbp]
-\centering
-\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
+% \centering
+\tbl{Examples of an answered question (left) and an unanswered question (right)}
+{\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
 \hline
@@
 \textbf{Frequently-used unanswered words?} & False & False \\ \hline
-\end{tabular}
-\caption{Examples of an answered question (left) and an unanswered question (right)}
+\end{tabular}}
 \label{table:5}
@@
 \begin{table}[!htbp]
-\centering
-\begin{tabular}{|L{4cm}|L{8cm}|}
+% \centering
+\tbl{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
+{\begin{tabular}{|L{4cm}|L{8cm}|}
   \hline
@@
    \hline
-\end{tabular}
-\caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
+\end{tabular}}
 \label{table:6}

### 2018-07-25 article/manuscript.tex
add files/changes for new submission

@@
-\documentclass[preprint]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[]{interact}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth
@@
 
-\usepackage{lineno,hyperref}
-\modulolinenumbers[5]
+% \usepackage{lineno,hyperref}
+% \modulolinenumbers[5]
 

### 2018-09-17 article/manuscript.Rnw
format manuscript for new submission

@@
 \usepackage[none]{hyphenat} % to cancel auto-hyphenation
+
+\usepackage[numbers,sort&compress]{natbib} % for reference/citation formating
+\bibpunct[, ]{[}{]}{,}{n}{,}{,}
+\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
 
@@
 \author{
-\name{L.K.Oshita\textsuperscript{a}\thanks{CONTACT L.K.Oshita. Email: l.oshita@yahoo.com}, A.Pileggi\textsuperscript{b}}
-\affil{\textsuperscript{a}iFixit; )
+\name{Lisa Oshita\textsuperscript{a}\thanks{CONTACT Lisa Oshita Email: l.oshita@yahoo.com}, Anthony Pileggi\textsuperscript{b}, Shannon Pileggi\textsuperscript{a}}
+\affil{\textsuperscript{a}Department of Statistics, California Polytechnic State University, CA, 93407; \textsuperscript{b}iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
 }
@@
 
-% \author[cp]{L.K.~Oshita\corref{cor1}}
-% \cortext[cor1]{Corresponding author}
-% \ead{l.oshita@yahoo.com}
-
-% \author[ifixit]{A.~Pileggi}
-% \author[cp]{S.~Pileggi}
-
-% \address[cp]{Department of Statistics, California Polytechnic State University, San Luis Obispo, CA 93407, United States}
-% \address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
-
 \begin{abstract} 
-iFixit's community driven online question and answer forum (CQA), \textif{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair.
+iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair.
 This platform allows users to ask questions regarding repairs, and for both repair experts and everyday users to provide answers and feedback.
@@
 \begin{keywords}
-Cox regression \sep CQA forum \sep response time \sep survival analysis \sep survival probabilty 
+Cox regression; CQA forum; response time; survival analysis; survival probabilty 
 \end{keywords}
@@
 
-Community-driven online question and answer forums feature thousands of user-posted questions and answers and receive millions of visits every month.
+Community-driven online question and answer forums feature thousands of user-generated questions and answers and receive millions of visits every month.
 As such, they have become widely-used sources of information.
@@
 
-As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users.
-This platform features questions pertaining to over 10,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 120,000 user-posted solutions.
+As not all possible repairs are covered in the published guides and users may have additional questions, iFixit's \textit{Answers} forum is an important resource for users.
+This platform features questions pertaining to over 10,000 devices, ranging from zippers to air conditioners and phone screens, with over 120,000 user-posted solutions.
 As thousands of users rely on this forum for information, it is important that users receive timely answers.
-Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \citep{Rechavi2011}.
+Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
 Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.
@@
 With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies.
-Regarding analysis of response times, \citet{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
-\citet{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
-\citet{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered.
+Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
+\cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
+\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered.
 However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
@@
 The majority of existing research has been focused on predicting question and answer quality.
-\citet{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
-\citet{Blumenstock2008} also determined that textual features (e.g.
+\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
+\cite{Blumenstock2008} also determined that textual features (e.g.
 word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-\citet{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
-A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \citep{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
+\cite{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
+A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
 The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.
@@
 \section{Materials}
-
-% Table of derived predictors
-\begin{table}%[!htbp]
-\tbl{Categorical and continuous variables derived}
-% \centering
-{\begin{tabular}{|L{2cm}|L{10cm}|}
-  \hline
-  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to.
-Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
-  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
-  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
-  & If the question's text is in all lower case \\ \cline{2-2}
-  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
-  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
-  & If the question's title ends in a question mark \\ \cline{2-2}
-  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
-  & If the user made an effort to solve the problem prior to asking the question \\ \hline
-  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
-  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
-  & Number of characters in the question's text (text length) \\ \cline{2-2}
-  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
-  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
-\end{tabular}}
-% \caption{Categorical and continuous variables derived}
-\label{table:1}
-\end{table}
 
@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \citep{Kleinbaum2011}.
+Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.
 
 Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}.
-Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \citep{Bland1998}.
+Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}.
 From these estimates, survival curves were constructed to examine the survival experience of questions.
@@
 
-As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \citep{Moore2010}.
-To build the model, five-fold cross-validation was used \citep{Rodriguez2010}.
-Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \citep{Hammermeister1979}.
+As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}.
+To build the model, five-fold cross-validation was used \cite{Rodriguez2010}.
+Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
 Each predictor was entered into univariate Cox models and the evidence of association with response times was assessed.
@@
 Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \citep{Harrell2015}.
+AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \cite{Harrell2015}.
 All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
-No variable selection was used after identifying significant predictors in univariate analysis, as \citet{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
+No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
 
@@
 To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
-The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \citep{Chen}.
+The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
 Significant results from this model would indicate high predictive accuracy.
 The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
-The p-value for this statistic was calculated from the $\chi^2$ distribution \citep{Oakes1981}.
+The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}.
 Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability.
@@
 Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5.
-A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \citep{Harrell2015}.
+A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}.
 These metrics were computed for each iteration on every training and test set.
@@
 
-Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \citep{Grambsch1994}.
+Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}.
 Significant correlations would indicate a predictor has violated this assumption.
@@
 
-\section{Results and Discussion}
+\section{Results}
 
@@
 
-% Splines Square root transformation of the average tag frequency
-\begin{table}% [!htbp]
-% \centering
-\tbl{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
-{\begin{tabular}{| L{5cm} | l | l |}
-  \hline
-  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
-  \hline
-  \multirow{4}{5 cm}{$\sqrt{\textnormal{average tag frequency}}$} 
-  & 0\textbf{*} & 65890.75 \\ 
-  & 5 & 65891.69 \\ 
-  & 4 & 65891.75 \\ 
-  & 3 & 65892.35 \\ 
-  \hline
-  \multirow{4}{5 cm}{$\log\left({\textnormal{average tag length} + 1}\right)$}
-  & 0 & 65920.24 \\ 
-  & 5 & 65911.20 \\ 
-  & 4\textbf{*} & 65910.81 \\ 
-  & 3 & 65914.98 \\ 
-  \hline
-  \multirow{4}{5 cm}{$\log\left({\textnormal{device length} + 1}\right)$}
-  & 0 & 65918.06 \\ 
-  & 5\textbf{*} & 65847.34 \\ 
-  & 4 & 65880.89 \\ 
-  & 3 & 65898.00 \\ 
-  \hline
-  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks / text length}}$}
-  & 0 & 65890.28 \\ 
-  & 5 & 65884.70 \\ 
-  & 4 & 65882.98 \\ 
-  & 3\textbf{*} & 65881.93 \\ 
-  \hline
-  \multirow{4}{5cm}{$\log\left({\textnormal{text length}}\right)$} 
-  & 0 & 65862.83 \\ 
-  & 5\textbf{*} & 65862.02 \\ 
-  & 4 & 65863.35 \\ 
-  & 3 & 65862.08 \\ 
-  \hline
-\end{tabular}}
-\label{table:2}
-\end{table}
-
 Table \ref{table:2} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
-
-% Cross-validation metrics
-\begin{table}[!htbp]
-% \centering
-\tbl{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)}
-{\begin{tabular}{|r|r|r|r|r|r|r|r|}
-  \hline
- & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
-  \hline
-  \textbf{Training Sets} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
-  \textbf{Test Sets}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
-  \textbf{Full Data}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
-   \hline
-\end{tabular}}
-\label{table:3}
-\end{table}
 
@@
 Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
-
-% Final model on full data
-\begin{table}[!htbp]
-% \centering
-\tbl{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
-{\begin{tabular}{|l L{5.5cm}|c|c|}
-  \hline
- \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
-  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
-                  & Camera & -0.32 (0.090) & \\ 
-                  & Electronics & -0.01 (0.078)  & \\ 
-                  & Game Console & 0.24 (0.083)  & \\ 
-                  & Home & 0.34 (0.070) &  \\ 
-                  & Other & -0.13 (0.056)  & \\ 
-                  & PC & 0.28 (0.060) &  \\ 
-                  & Tablet & -0.16 (0.081)  & \\ 
-                  & Vehicle & 0.40 (0.069)  & \\
-                  & Android/Other Phone (reference) & --- & \\ \hline
-  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
-  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
-  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
-\end{tabular}}
-\label{table:4}
-\end{table}
 
@@
 
-\section{Conclusion}
+\section{Discussion}
 
@@
 
-\section{Vitae}
-
-Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo.
+% \section{Vitae}
+% 
+% Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo.
 Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo.
@@
 
-\section{Author Contributions}
+% \section{Author Contributions}
+% 
+% All authors contributed to the analysis featured in this paper and have edited and approved of the final article.
 
-All authors contributed to the analysis featured in this paper and have edited and approved of the final article.
+\section*{Acknowledgements}
 
-\section{Acknowledgements}
+ We would like to thank iFixit for providing access to the CQA data.
 
-This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-This sponsor was not involved in any aspect of this paper's analysis.
-We also thank iFixit for providing access to the CQA data.
+\section*{Disclosure Statement}
 
-\section{Appendix}
+We wish to confirm that there are no known conflicts of interest associated with this publication.
 
-\subsection{Posted questions}
+\section*{Funding}
 
-\begin{table}[!htbp]
+This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. This sponsor was not involved in any aspect of this paper's analysis.
+
+\bibliographystyle{tfs}
+\bibliography{references}
+
+\section{Appendices}
+
+\appendix
+
+\section{Posted questions}
+
+Table \ref{table:5} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
+All fields in device, title, text, and tags are shown as the users entered it.
+
+\section{Variable Derivation}
+
+\subsection{Average tag frequency}
+
+This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
+This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set.
+Questions without tags were assigned a value of 0.
+If a question has a higher average, then at least one of its tags are considered frequently-used.
+This variable was created based off of findings from \cite{Bhat2014}.
+
+\subsection{Average tag length}
+
+This variable was created to investigate if questions with correctly defined tags have faster response times than questions that do not include tags or incorrectly use the tagging system.
+It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
+
+\subsection{Device categorization}
+
+Original device categories defined by iFixit included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model.
+Final categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
+Under the original device categorization, 1,954 questions (25.2\% of 7,760) were categorized incorrectly and indicated an NA for its category.
+Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.
+For questions with missing categories, key words were searched for in device titles to re-categorize accordingly.
+All other questions with ambiguous device titles were categorized as Other.
+
+\subsection{Device name length}
+
+This variable was created to investigate if questions with correctly defined device names have faster response times than questions that do not include a name or are incorrectly defined.
+Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names (often lengthy) make it difficult for the answering community to discern the question's topic, and thus have slower response times.
+
+\subsection{If the question's text contains end punctuation}
+
+This variable was created to investigate if sentences with no end punctuation take longer to receive an answer.
+
+\subsection{If the question's title contains terms considered frequently-used among answered/unanswered questions}
+
+These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not.
+Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not.
+This variable was created based off of methods from \cite{Correa2013} and \cite{Ravi2014}.
+
+To create the variables, the data was separated between answered and unanswered questions.
+For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the proportion of times those words occurred among all answered questions' titles, defined as the frequency.
+The same was performed for the data frame containing unanswered questions.
+``Frequently-used'' words in answered questions were defined as those that appeared in 1\% or more of all answered questions' titles, and appeared in more answered questions than in unanswered questions.
+To determine the latter, a ratio of frequencies was assessed.
+The ratio was calculated as the proportion of times a word occurred among answered questions, to the proportion of times a word occurred in unanswered questions.
+As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
+Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions.
+As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
+Table \ref{table:6} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
+
+\subsection{If the question's title ends in a question mark}
+
+This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \cite{Bhat2014}.
+
+\subsection{If the user made an effort to solve the problem prior to asking the question}
+
+This variable indicates true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting.
+Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
+This variable was created based off of findings and methods from \cite{Bhat2014} and \cite{Harper2008}.
+
+\subsection{Line break to text length ratio}
+
+This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that do not include any, and thus have shorter response times.
+Questions with a ratio of 0 tend to include either short, ambiguous texts (e.g.
+"Start button not working.") or long and lengthy texts, and tend to remain unanswered or have slower response times.
+Questions with a ratio of greater than 0 tend to have faster response times.
+
+\end{appendix}
+
+% Table of derived predictors
+\begin{table}[p]%[!htbp]
+\tbl{Categorical and continuous variables derived}
+% \centering
+{\begin{tabular}{|L{2cm}|L{10cm}|}
+  \hline
+  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to.
+Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
+  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
+  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
+  & If the question's text is in all lower case \\ \cline{2-2}
+  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
+  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
+  & If the question's title ends in a question mark \\ \cline{2-2}
+  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
+  & If the user made an effort to solve the problem prior to asking the question \\ \hline
+  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
+  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
+  & Number of characters in the question's text (text length) \\ \cline{2-2}
+  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
+  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
+\end{tabular}}
+% \caption{Categorical and continuous variables derived}
+\label{table:1}
+\end{table}
+
+% Splines Square root transformation of the average tag frequency
+\begin{table}% [!htbp]
+% \centering
+\tbl{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
+{\begin{tabular}{| L{5cm} | l | l |}
+  \hline
+  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
+  \hline
+  \multirow{4}{5 cm}{$\sqrt{\textnormal{average tag frequency}}$} 
+  & 0\textbf{*} & 65890.75 \\ 
+  & 5 & 65891.69 \\ 
+  & 4 & 65891.75 \\ 
+  & 3 & 65892.35 \\ 
+  \hline
+  \multirow{4}{5 cm}{$\log\left({\textnormal{average tag length} + 1}\right)$}
+  & 0 & 65920.24 \\ 
+  & 5 & 65911.20 \\ 
+  & 4\textbf{*} & 65910.81 \\ 
+  & 3 & 65914.98 \\ 
+  \hline
+  \multirow{4}{5 cm}{$\log\left({\textnormal{device length} + 1}\right)$}
+  & 0 & 65918.06 \\ 
+  & 5\textbf{*} & 65847.34 \\ 
+  & 4 & 65880.89 \\ 
+  & 3 & 65898.00 \\ 
+  \hline
+  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks / text length}}$}
+  & 0 & 65890.28 \\ 
+  & 5 & 65884.70 \\ 
+  & 4 & 65882.98 \\ 
+  & 3\textbf{*} & 65881.93 \\ 
+  \hline
+  \multirow{4}{5cm}{$\log\left({\textnormal{text length}}\right)$} 
+  & 0 & 65862.83 \\ 
+  & 5\textbf{*} & 65862.02 \\ 
+  & 4 & 65863.35 \\ 
+  & 3 & 65862.08 \\ 
+  \hline
+\end{tabular}}
+\label{table:2}
+\end{table}
+
+% Cross-validation metrics
+\begin{table}%[!htbp]
+% \centering
+\tbl{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)}
+{\begin{tabular}{|r|r|r|r|r|r|r|r|}
+  \hline
+ & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
+  \hline
+  \textbf{Training Sets} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
+  \textbf{Test Sets}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
+  \textbf{Full Data}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
+   \hline
+\end{tabular}}
+\label{table:3}
+\end{table}
+
+% Final model on full data
+\begin{table}%[!htbp]
+% \centering
+\tbl{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
+{\begin{tabular}{|l L{5.5cm}|c|c|}
+  \hline
+ \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
+  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
+                  & Camera & -0.32 (0.090) & \\ 
+                  & Electronics & -0.01 (0.078)  & \\ 
+                  & Game Console & 0.24 (0.083)  & \\ 
+                  & Home & 0.34 (0.070) &  \\ 
+                  & Other & -0.13 (0.056)  & \\ 
+                  & PC & 0.28 (0.060) &  \\ 
+                  & Tablet & -0.16 (0.081)  & \\ 
+                  & Vehicle & 0.40 (0.069)  & \\
+                  & Android/Other Phone (reference) & --- & \\ \hline
+  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
+  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
+  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
+  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
+\end{tabular}}
+\label{table:4}
+\end{table}
+
+\begin{table}%[!htbp]
 % \centering
@@
 
-Table \ref{table:5} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
-All fields in device, title, text, and tags are shown as the users entered it.
-
-\subsection{Variable Derivation}
-
-\subsubsection{Average tag frequency}
-
-This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
-This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set.
-Questions without tags were assigned a value of 0.
-If a question has a higher average, then at least one of its tags are considered frequently-used.
-This variable was created based off of findings from \citet{Bhat2014}.
-
-\subsubsection{Average tag length}
-
-This variable was created to investigate if questions with correctly defined tags have faster response times than questions that do not include tags or incorrectly use the tagging system.
-It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
-
-\subsubsection{Device categorization}
-
-Original device categories defined by iFixit included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
-Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model.
-Final categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
-Under the original device categorization, 1,954 questions (25.2\% of 7,760) were categorized incorrectly and indicated an NA for its category.
-Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.
-For questions with missing categories, key words were searched for in device titles to re-categorize accordingly.
-All other questions with ambiguous device titles were categorized as Other.
-
-\subsubsection{Device name length}
-
-This variable was created to investigate if questions with correctly defined device names have faster response times than questions that do not include a name or are incorrectly defined.
-Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names (often lengthy) make it difficult for the answering community to discern the question's topic, and thus have slower response times.
-
-\subsubsection{If the question's text contains end punctuation}
-
-This variable was created to investigate if sentences with no end punctuation take longer to receive an answer.
-
-\subsubsection{If the question's title contains terms considered frequently-used among answered/unanswered questions}
-
-These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not.
-Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not.
-This variable was created based off of methods from \citet{Correa2013} and \citet{Ravi2014}.
-
-To create the variables, the data was separated between answered and unanswered questions.
-For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the proportion of times those words occurred among all answered questions' titles, defined as the frequency.
-The same was performed for the data frame containing unanswered questions.
-``Frequently-used'' words in answered questions were defined as those that appeared in 1\% or more of all answered questions' titles, and appeared in more answered questions than in unanswered questions.
-To determine the latter, a ratio of frequencies was assessed.
-The ratio was calculated as the proportion of times a word occurred among answered questions, to the proportion of times a word occurred in unanswered questions.
-As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
-Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions.
-As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
-Table \ref{table:6} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
-
 % Table with list of frequently-used words
@@
 
-\subsubsection{If the question's title ends in a question mark}
-
-This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \citep{Bhat2014}.
-
-\subsubsection{If the user made an effort to solve the problem prior to asking the question}
-
-This variable indicates true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting.
-Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
-This variable was created based off of findings and methods from \citet{Bhat2014} and \citet{Harper2008}.
-
-\subsubsection{Line break to text length ratio}
-
-This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that do not include any, and thus have shorter response times.
-Questions with a ratio of 0 tend to include either short, ambiguous texts (e.g.
-"Start button not working.") or long and lengthy texts, and tend to remain unanswered or have slower response times.
-Questions with a ratio of greater than 0 tend to have faster response times.
-
-\section*{References}
-
-\bibliographystyle{elsarticle-num-names}
-\bibliography{references}
-
 \end{document}

### 2018-09-17 article/manuscript.tex
format manuscript for new submission

@@
 \usepackage[none]{hyphenat} % to cancel auto-hyphenation
+
+\usepackage[numbers,sort&compress]{natbib} % for reference/citation formating
+\bibpunct[, ]{[}{]}{,}{n}{,}{,}
+\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.
+
+Table \ref{table:2} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
+
+Average performance metrics for test and training sets are in Table \ref{table:3}.
+Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time.
+However, $R^2$ statistics and discrimination indexes are considerably low.
+Metrics for the final model's performance on the full data, also found in Table \ref{table:3}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
+Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
+
+Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
+
+As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
+
+The following are interpretations of select hazard coefficients in Table \ref{table:4}.
+Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
+
+\begin{itemize}
+  \item The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
+  \item The estimated hazard of receiving an answer for questions posted on a weekend is 13\% lower (95\% CI (7\%, 18\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
+\end{itemize}
+
+Results and coefficients of the final model reveal how users can ask questions in order to decrease response time.
+Findings suggest that users should phrase the title in the form of a question, use correct grammar (e.g.
+punctuation and capitalization), include specific and concise tags, and post the question on a weekday.
+
+The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design.
+Many users incorrectly specified the device name (e.g.
+a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name.
+Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic).
+It is likely that these inconsistencies contributed to the final model's low predictive power.
+This, along with the results of the final model, reveal some of the ways the CQA can be structured to potentially decrease response times.
+As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
+Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above.
+Instead, the CQA can restrict the tags or devices that users can include to a drop-down list.
+The CQA can also include more tips to guide users asking questions.
+Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
+
+\section{Discussion}
+
+This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
+Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
+While overall the model was significant, its predictive performance was considerably low.
+
+% \section{Vitae}
+% 
+% Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo.
+Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo.
+Anthony Pileggi is a Data Scientist at iFixit.
+Declarations of interest: none.
+
+% \section{Author Contributions}
+% 
+% All authors contributed to the analysis featured in this paper and have edited and approved of the final article.
+
+\section*{Acknowledgements}
+
+ We would like to thank iFixit for providing access to the CQA data.
+
+\section*{Disclosure Statement}
+
+We wish to confirm that there are no known conflicts of interest associated with this publication.
+
+\section*{Funding}
+
+This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. This sponsor was not involved in any aspect of this paper's analysis.
+
+\bibliographystyle{tfs}
+\bibliography{references}
+
+\section{Appendices}
+
+\appendix
+
+\section{Posted questions}
+
+Table \ref{table:5} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
+All fields in device, title, text, and tags are shown as the users entered it.
+
+\section{Variable Derivation}
+
+\subsection{Average tag frequency}
+
+This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
+This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set.
+Questions without tags were assigned a value of 0.
+If a question has a higher average, then at least one of its tags are considered frequently-used.
+This variable was created based off of findings from \cite{Bhat2014}.
+
+\subsection{Average tag length}
+
+This variable was created to investigate if questions with correctly defined tags have faster response times than questions that do not include tags or incorrectly use the tagging system.
+It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
+
+\subsection{Device categorization}
+
+Original device categories defined by iFixit included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
+Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model.
+Final categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
+Under the original device categorization, 1,954 questions (25.2\% of 7,760) were categorized incorrectly and indicated an NA for its category.
+Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.
+For questions with missing categories, key words were searched for in device titles to re-categorize accordingly.
+All other questions with ambiguous device titles were categorized as Other.
+
+\subsection{Device name length}
+
+This variable was created to investigate if questions with correctly defined device names have faster response times than questions that do not include a name or are incorrectly defined.
+Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names (often lengthy) make it difficult for the answering community to discern the question's topic, and thus have slower response times.
+
+\subsection{If the question's text contains end punctuation}
+
+This variable was created to investigate if sentences with no end punctuation take longer to receive an answer.
+
+\subsection{If the question's title contains terms considered frequently-used among answered/unanswered questions}
+
+These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not.
+Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not.
+This variable was created based off of methods from \cite{Correa2013} and \cite{Ravi2014}.
+
+To create the variables, the data was separated between answered and unanswered questions.
+For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the proportion of times those words occurred among all answered questions' titles, defined as the frequency.
+The same was performed for the data frame containing unanswered questions.
+``Frequently-used'' words in answered questions were defined as those that appeared in 1\% or more of all answered questions' titles, and appeared in more answered questions than in unanswered questions.
+To determine the latter, a ratio of frequencies was assessed.
+The ratio was calculated as the proportion of times a word occurred among answered questions, to the proportion of times a word occurred in unanswered questions.
+As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
+Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions.
+As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
+Table \ref{table:6} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
+
+\subsection{If the question's title ends in a question mark}
+
+This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \cite{Bhat2014}.
+
+\subsection{If the user made an effort to solve the problem prior to asking the question}
+
+This variable indicates true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting.
+Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
+This variable was created based off of findings and methods from \cite{Bhat2014} and \cite{Harper2008}.
+
+\subsection{Line break to text length ratio}
+
+This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that do not include any, and thus have shorter response times.
+Questions with a ratio of 0 tend to include either short, ambiguous texts (e.g.
+"Start button not working.") or long and lengthy texts, and tend to remain unanswered or have slower response times.
+Questions with a ratio of greater than 0 tend to have faster response times.
+
+\end{appendix}
+
+% Table of derived predictors
+\begin{table}[p]%[!htbp]
+\tbl{Categorical and continuous variables derived}
+% \centering
+{\begin{tabular}{|L{2cm}|L{10cm}|}
+  \hline
+  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to.
+Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
+  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
+  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
+  & If the question's text is in all lower case \\ \cline{2-2}
+  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
+  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
+  & If the question's title ends in a question mark \\ \cline{2-2}
+  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
+  & If the user made an effort to solve the problem prior to asking the question \\ \hline
+  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
+  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
+  & Number of characters in the question's text (text length) \\ \cline{2-2}
+  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
+  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
+\end{tabular}}
+% \caption{Categorical and continuous variables derived}
+\label{table:1}
+\end{table}
 
@@
 
-Table \ref{table:2} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
-
 % Cross-validation metrics
-\begin{table}[!htbp]
+\begin{table}%[!htbp]
 % \centering
@@
 
-Average performance metrics for test and training sets are in Table \ref{table:3}.
-Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time.
-However, $R^2$ statistics and discrimination indexes are considerably low.
-Metrics for the final model's performance on the full data, also found in Table \ref{table:3}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
-Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
-
 % Final model on full data
-\begin{table}[!htbp]
+\begin{table}%[!htbp]
 % \centering
@@
 
-Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
-
-As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
-
-The following are interpretations of select hazard coefficients in Table \ref{table:4}.
-Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
-
-\begin{itemize}
-  \item The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer for questions posted on a weekend is 13\% lower (95\% CI (7\%, 18\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
-\end{itemize}
-
-Results and coefficients of the final model reveal how users can ask questions in order to decrease response time.
-Findings suggest that users should phrase the title in the form of a question, use correct grammar (e.g.
-punctuation and capitalization), include specific and concise tags, and post the question on a weekday.
-
-The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design.
-Many users incorrectly specified the device name (e.g.
-a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name.
-Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic).
-It is likely that these inconsistencies contributed to the final model's low predictive power.
-This, along with the results of the final model, reveal some of the ways the CQA can be structured to potentially decrease response times.
-As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
-Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above.
-Instead, the CQA can restrict the tags or devices that users can include to a drop-down list.
-The CQA can also include more tips to guide users asking questions.
-Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
-
-\section{Conclusion}
-
-This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
-While overall the model was significant, its predictive performance was considerably low.
-
-\section{Vitae}
-
-Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo.
-Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo.
-Anthony Pileggi is a Data Scientist at iFixit.
-Declarations of interest: none.
-
-\section{Author Contributions}
-
-All authors contributed to the analysis featured in this paper and have edited and approved of the final article.
-
-\section{Acknowledgements}
-
-This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo.
-This sponsor was not involved in any aspect of this paper's analysis.
-We also thank iFixit for providing access to the CQA data.
-
-\section{Appendix}
-
-\subsection{Posted questions}
-
-\begin{table}[!htbp]
+\begin{table}%[!htbp]
 % \centering

### 2018-09-18 article/manuscript.Rnw
edit abstract + introduction

@@
 }
+\makeatother
+
+\makeatletter % for spacing figures at the end of the document
+\@fpsep\textheight
 \makeatother
@@
 \begin{abstract} 
-iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair.
-This platform allows users to ask questions regarding repairs, and for both repair experts and everyday users to provide answers and feedback.
+iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for users to ask questions related specifically to device repair, and for both repair experts and everyday users to provide answers and feedback.
 This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
@@
 
-Community-driven online question and answer forums feature thousands of user-generated questions and answers and receive millions of visits every month.
-As such, they have become widely-used sources of information.
-The CQA analyzed in this paper is iFixit's \textit{Answers} forum.
-Founded in 2003, iFixit equips users with the knowledge and tools necessary to both repair their broken devices and reduce electronic waste, by providing over 35,000 free online repair guides.
-
-As not all possible repairs are covered in the published guides and users may have additional questions, iFixit's \textit{Answers} forum is an important resource for users.
-This platform features questions pertaining to over 10,000 devices, ranging from zippers to air conditioners and phone screens, with over 120,000 user-posted solutions.
-As thousands of users rely on this forum for information, it is important that users receive timely answers.
-Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
-Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.
+Founded in 2003, iFixit teaches thousands of users across the globe how to fix their own broken devices.
+This company provides over 40,000 free online repair guides and hosts a CQA, the \textit{Answers} forum, featuring questions pertaining to over 11,000 devices with over 130,000 user-posted solutions.
+One critical key feature of CQAs like \textit{Answers} is question response times.
+Fast response times have been shown to be associated with positive user experience and increased web traffic---factors that are extremely valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
+Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask questions to minimize response times and for how forum design can be improved.
 
@@
 Questions analyzed were restricted to those posted in English.
-The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer.
+Time until event was defined as the time since posting until a question received its first answer.
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
@@
 Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}.
-Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}.
-From these estimates, survival curves were constructed to examine the survival experience of questions.
+Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored observations, or unanswered questions \cite{Bland1998}.
+From these estimates, survival curves were constructed to examine the overall survival experience of questions.
 Mean and median survival times were also generated.
 
-As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}.
-To build the model, five-fold cross-validation was used \cite{Rodriguez2010}.
+As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict question survival probability \cite{Moore2010}.
+To build the model, the full data was partitioned into five separate sets \cite{Rodriguez2010}.
 Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
-Each predictor was entered into univariate Cox models and the evidence of association with response times was assessed.
+For this process, each predictor was entered into univariate Cox models and evidence of association with response times was assessed.
 Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.
-Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model.
-Univariate analysis was again performed on each continuous predictor to investigate the use of splines.
-Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \cite{Harrell2015}.
-All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation.
-No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
+Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include.
+Univariate analysis was again performed on each continuous predictor---each predictor, with the transformation previously found necessary, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
+AIC statistics were used to determine if splines should be used, as well as the optimal number of knots \cite{Harrell2015}.
+All significant categorical and continuous predictors, in final form, were included in the model for five-fold cross-validation.
+% Variable selection was not used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
 
 In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
-To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
+To assess performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
 The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
@@
 
+\section{Discussion}
+
 Results and coefficients of the final model reveal how users can ask questions in order to decrease response time.
@@
 punctuation and capitalization), include specific and concise tags, and post the question on a weekday.
+
+% Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
 
@@
 The CQA can also include more tips to guide users asking questions.
-Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.
-
-\section{Discussion}
-
-This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time.
-Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
-While overall the model was significant, its predictive performance was considerably low.
+Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response times, as well as create a set of consistent questions for improved analysis.
 
@@
 
-This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times.
-This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set.
+This variable was created to investigate if including popular or widely-used tags in a question can lead to faster response times, based off of findings from \cite{Bhat2014}.
+This was computed as the average frequency, or proportion of times a question's tags appear in all of the data set.
 Questions without tags were assigned a value of 0.
 If a question has a higher average, then at least one of its tags are considered frequently-used.
-This variable was created based off of findings from \cite{Bhat2014}.
 
@@
 
-This variable indicates true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting.
+This variable indicates true if the asker included words in the question's text that indicate that the user made prior effort to find the solution before posting.
 Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
@@
 
-\end{appendix}
+\section{Tables}
 
@@
 % Splines Square root transformation of the average tag frequency
-\begin{table}% [!htbp]
+\begin{table}[p]% [!htbp]
 % \centering
@@
 % Cross-validation metrics
-\begin{table}%[!htbp]
+\begin{table}[p]%[!htbp]
 % \centering
@@
 % Final model on full data
-\begin{table}%[!htbp]
+\begin{table}[p]%[!htbp]
 % \centering
@@
 
-\begin{table}%[!htbp]
+\begin{table}[p]%[!htbp]
 % \centering
@@
 % Table with list of frequently-used words
-\begin{table}[!htbp]
+\begin{table}[p]%[!htbp]
 % \centering

### 2018-09-18 article/manuscript.tex
edit abstract + introduction

@@
 
+\makeatletter % for spacing figures at the end of the document
+\@fpsep\textheight
+\makeatother
+
 \title{Survival Analysis of Questions Posted on the iFixit Answers Forum}

### 2018-09-18 article/manuscript.Rnw
edit introduction + methods sections

@@
 \begin{abstract} 
-iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for users to ask questions related specifically to device repair, and for both repair experts and everyday users to provide answers and feedback.
+iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer questions related specifically to device repair.
 This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
@@
 Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored observations, or unanswered questions \cite{Bland1998}.
-From these estimates, survival curves were constructed to examine the overall survival experience of questions.
-Mean and median survival times were also generated.
+From these estimates, survival curves were constructed to examine the overall question survival experience.
+Mean and median survival times were also computed.
 
@@
 Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.
-Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include.
-Univariate analysis was again performed on each continuous predictor---each predictor, with the transformation previously found necessary, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots.
-AIC statistics were used to determine if splines should be used, as well as the optimal number of knots \cite{Harrell2015}.
+Transformations and restricted cubic splines were also explored through a similar process.
+The combination of which transformation, square root or log-transformed, and restricted cubic spline with three, four, or five knots, were selected for each continuous predictor based on the AIC statistic \cite{Harrell2015}.
 All significant categorical and continuous predictors, in final form, were included in the model for five-fold cross-validation.
-% Variable selection was not used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.
 
-In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set.
+In each iteration of cross-validation, the full model was built on the training set and used to compute predicted hazard ratios on the corresponding test set.
 To assess performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
 The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
-Significant results from this model would indicate high predictive accuracy.
-The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
+The partial likelihood ratio is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
 The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}.

### 2018-09-18 article/manuscript.Rnw
add keyword, spell check, edit grammar

@@
 Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
-\end{abstract}
+\end{abstract} % 174 words
 
 \begin{keywords}
-Cox regression; CQA forum; response time; survival analysis; survival probabilty 
+Cox regression; CQA forum; response time; survival analysis; survival probabilty; Kaplan-Meier; 
 \end{keywords}
@@
 
-Founded in 2003, iFixit teaches thousands of users across the globe how to fix their own broken devices.
+Founded in 2003, iFixit teaches thousands of users around the globe how to fix their own broken devices.
 This company provides over 40,000 free online repair guides and hosts a CQA, the \textit{Answers} forum, featuring questions pertaining to over 11,000 devices with over 130,000 user-posted solutions.
@@
 word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-\cite{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
+\cite{Fu2015} instead found non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
 A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
-The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.
+The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate a question is of high quality also lead to faster response times.
 
@@
 For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.
+Such questions were considered right-censored, meaning exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.
 
@@
 Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored observations, or unanswered questions \cite{Bland1998}.
-From these estimates, survival curves were constructed to examine the overall question survival experience.
+From these estimates, survival curves were constructed to examine overall survival experience.
 Mean and median survival times were also computed.
@@
 To build the model, the full data was partitioned into five separate sets \cite{Rodriguez2010}.
-Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
+Univariate analysis, performed on one set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
 For this process, each predictor was entered into univariate Cox models and evidence of association with response times was assessed.
@@
 To assess performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
-The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}.
+The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of performance indicators \cite{Chen}.
 The partial likelihood ratio is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
@@
 These metrics were computed for each iteration on every training and test set.
-Averages of metrics across training and test sets were evaluated.
+Averages across training and test sets were evaluated.
 The final model was then fit to the full data and the same metrics were computed and compared.
@@
 Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}.
-Significant correlations would indicate a predictor has violated this assumption.
+Significant correlations would indicate a violation of this assumption.
 
@@
 The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
-All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.
 
@@
 Metrics for the final model's performance on the full data, also found in Table \ref{table:3}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
-Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.
+Results for training, test, and the full data did not change significantly, indicating that the model was not overfit.
 
@@
 Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above.
-Instead, the CQA can restrict the tags or devices that users can include to a drop-down list.
+Instead, the CQA can restrict the tags or devices users can include to a drop-down list.
 The CQA can also include more tips to guide users asking questions.
@@
 
-This variable indicates true if the asker included words in the question's text that indicate that the user made prior effort to find the solution before posting.
+This variable indicates true if the asker included words in the question's text that indicate the user made prior effort to find the solution before posting.
 Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.

### 2018-09-18 article/manuscript.Rnw
comment out related work section

@@
 \begin{abstract} 
-iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer questions related specifically to device repair.
+iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer device repair-related questions.
 This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
@@
 \begin{keywords}
-Cox regression; CQA forum; response time; survival analysis; survival probabilty; Kaplan-Meier; 
+Cox regression; CQA forum; Kaplan-Meier method; response time; survival analysis; survival probabilty;  
 \end{keywords}
@@
 
-\section{Related Work}
-
-With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies.
+% \section{Related Work}
+% 
+% With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies.
 Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
@@
 The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
-
-The majority of existing research has been focused on predicting question and answer quality.
+% 
+% The majority of existing research has been focused on predicting question and answer quality.
 \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.

### 2018-09-18 article/manuscript.Rnw
add Related work as subsection of Introduction

--- 2018-09-18 article/manuscript.Rnw
@@
 
-\section{Related Work}
+\subsection{Related Work}
 
@@
 
-As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict question survival probability \cite{Moore2010}.
-To build the model, the full data was partitioned into five separate sets \cite{Rodriguez2010}.
+As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was built to predict question survival probability \cite{Moore2010}.
+To construct the model, the full data was partitioned into five separate sets \cite{Rodriguez2010}.
 Univariate analysis, performed on one set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
-For this process, each predictor was entered into univariate Cox models and evidence of association with response times was assessed.
+For this process, each predictor was entered into separate Cox models and evidence of association with response times was assessed.
 Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.
@@
 To assess performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
-The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of performance indicators \cite{Chen}.
-The partial likelihood ratio is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model.
+The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as performance indicators \cite{Chen}.
+The partial likelihood ratio is a ratio of the log partial likelihood function evaluated at the parameter estimates (equivalent to a goodness of fit measure of the model with predictors) and the log partial likelihood function for the null model without predictors and only the baseline hazard function (equivalent to a goodness of fit measure for the null model).
 The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}.
@@
 Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5.
-A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}.
+A value of 0 indicates random predictions, while a value of 1 indicates perfect predictions \cite{Harrell2015}.
 These metrics were computed for each iteration on every training and test set.
@@
 Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001.
-Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001.
-Applying either square root or log transformations to all continuous predictors resulted in univariate p-values of less than 0.001.
-For variables that contained zeros, one was added to each observation before applying the log transformation.
+Continuous predictors, excluding device length and average tag length, also resulted in p-values of less than 0.001.
+Applying either square root or log transformations to all continuous predictors resulted in p-values of less than 0.001.
 The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
@@
 
-As a whole, the final model was significant with a partial likelihood ratio of \Sexpr{LR} (p-value \textless0.0001). Its $R^2$ statistic was \Sexpr{r2}, and Somers' \textit{Dxy} was \Sexpr{dxy}.
+The final model trained on the full data set was significant with a partial likelihood ratio of \Sexpr{LR} (p-value \textless0.0001).
+Its $R^2$ statistic was \Sexpr{r2}, and Somers' \textit{Dxy} was \Sexpr{dxy}.
 

### 2018-09-18 article/manuscript.tex
add Related work as subsection of Introduction

--- 2018-09-18 article/manuscript.tex
@@
 
-As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
+The final model trained on the full data set was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
 

### 2018-09-18 article/graphics.Rmd
add code for converting images to tiff format

@@
 
+tiff("Figure 1.tiff", res = 300, width = 3000, height = 1500)
 ggplot(x, aes(x = time_until_answer, fill = Answered)) +
@@
         axis.text = element_text(size = 20))
+dev.off()
 
@@
 library(survminer)
+
+tiff("Figure 2.tiff", res = 300, width = 3000, height = 1500)
 # dashed line indicates the median survival time
@@
            font.x = 20, font.y = 20, font.tickslab = 20)
+dev.off()
 
-ggsave("FIG2.eps", width = 8, height = 5)
+# ggsave("FIG2.eps", width = 8, height = 5)
 ```

### 2018-09-18 article/tables.tex
move tables to separate tex files for submission

--- 2018-09-18 article/manuscript.tex
@@
 \makeatother
-
-\title{Survival Analysis of Questions Posted on the iFixit Answers Forum}
-
-\author{
-\name{Lisa Oshita\textsuperscript{a}\thanks{CONTACT Lisa Oshita Email: l.oshita@yahoo.com}, Anthony Pileggi\textsuperscript{b}, Shannon Pileggi\textsuperscript{a}}
-\affil{\textsuperscript{a}Department of Statistics, California Polytechnic State University, CA, 93407; \textsuperscript{b}iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
-}
-
-\maketitle
-
-\begin{abstract} 
-iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer device repair-related questions.
-This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
-A Cox proportional hazards model was developed to identify variables associated with response time.
-Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$).
-Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))).
-Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
-\end{abstract} % 174 words
-
-\begin{keywords}
-Cox regression; CQA forum; Kaplan-Meier method; response time; survival analysis; survival probabilty;  
-\end{keywords}
-
-\section{Introduction}
-
-Founded in 2003, iFixit teaches thousands of users around the globe how to fix their own broken devices.
-This company provides over 40,000 free online repair guides and hosts a CQA, the \textit{Answers} forum, featuring questions pertaining to over 11,000 devices with over 130,000 user-posted solutions.
-One critical key feature of CQAs like \textit{Answers} is question response times.
-Fast response times have been shown to be associated with positive user experience and increased web traffic---factors that are extremely valuable to the reputation and longevity of the CQA \cite{Rechavi2011}.
-Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask questions to minimize response times and for how forum design can be improved.
-
-However, analysis and prediction of response times on CQAs have not been thoroughly investigated.
-There is need for further analysis in this area, as the majority of existing research focuses on assessing and predicting question or answer quality.
-This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict survival probabilities of questions.
-
-\subsection{Related Work}
-
-With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies.
-Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
-\cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
-\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered.
-However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
-The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
-
-The majority of existing research has been focused on predicting question and answer quality.
-\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
-\cite{Blumenstock2008} also determined that textual features (e.g.
-word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-\cite{Fu2015} instead found non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
-A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
-The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate a question is of high quality also lead to faster response times.
-
-\section{Materials}
-
-The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download).
-Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received.
-Variables derived can be found in Table \ref{table:1}.
-The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table \ref{table:5}.
-
-\section{Methods}
-
-Questions analyzed were restricted to those posted in English.
-Time until event was defined as the time since posting until a question received its first answer.
-For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded.
-Such questions were considered right-censored, meaning exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.
-
-Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}.
-Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored observations, or unanswered questions \cite{Bland1998}.
-From these estimates, survival curves were constructed to examine overall survival experience.
-Mean and median survival times were also computed.
-
-As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was built to predict question survival probability \cite{Moore2010}.
-To construct the model, the full data was partitioned into five separate sets \cite{Rodriguez2010}.
-Univariate analysis, performed on one set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}.
-For this process, each predictor was entered into separate Cox models and evidence of association with response times was assessed.
-Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.
-Transformations and restricted cubic splines were also explored through a similar process.
-The combination of which transformation, square root or log-transformed, and restricted cubic spline with three, four, or five knots, were selected for each continuous predictor based on the AIC statistic \cite{Harrell2015}.
-All significant categorical and continuous predictors, in final form, were included in the model for five-fold cross-validation.
-
-In each iteration of cross-validation, the full model was built on the training set and used to compute predicted hazard ratios on the corresponding test set.
-To assess performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time.
-The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as performance indicators \cite{Chen}.
-The partial likelihood ratio is a ratio of the log partial likelihood function evaluated at the parameter estimates (equivalent to a goodness of fit measure of the model with predictors) and the log partial likelihood function for the null model without predictors and only the baseline hazard function (equivalent to a goodness of fit measure for the null model).
-The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}.
-Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability.
-Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard.
-Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions.
-Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5.
-A value of 0 indicates random predictions, while a value of 1 indicates perfect predictions \cite{Harrell2015}.
-These metrics were computed for each iteration on every training and test set.
-Averages across training and test sets were evaluated.
-The final model was then fit to the full data and the same metrics were computed and compared.
-
-Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}.
-Significant correlations would indicate a violation of this assumption.
-
-All computation was executed under \texttt{R} version 3.4.3.
-Kaplan-Meier estimates of survival probability were computed with the \texttt{Surv} and \texttt{survfit} functions of the \texttt{Survival} package in R.
-To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package.
-This function uses the Cox model and a vector of times to compute predictions.
-Data used for this analysis was published on Mendeley Data (DOI: 10.17632/shfkj785yb.1).
-Code for variable setup and analysis is available upon request.
-
-\section{Results}
-
-% Distribution of answer times
-% \begin{figure}[!htbp]
-%   \includegraphics[scale=0.5]{FIG1.pdf}
-%   \label{fig:1}
-% \end{figure}
-% 
-% % Kaplan-Meier curve
-% \begin{figure}[!htbp]
-%   \includegraphics[scale=0.5]{FIG2.eps}
-%   \label{fig:2}
-% \end{figure}
-
-  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data).
-Of those questions, 4,951 (63.8\%) received an answer by the download date.
-The shortest response time was 0.5 hours.
-The longest was 2,159 hours (90 days).
-Figure 1 shows the distribution of response times for all questions analyzed.
-
-Figure 2 shows the Kaplan-Meier estimated survival probability curve for all questions in the data.
-The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low.
-The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 776 hours, or 32.3 days.
-The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.2 hours.
-
-Each training set contained 6,208 questions; each test set contained 1,552 questions.
-Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001.
-Continuous predictors, excluding device length and average tag length, also resulted in p-values of less than 0.001.
-Applying either square root or log transformations to all continuous predictors resulted in p-values of less than 0.001.
-The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length.
-
-Table \ref{table:2} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
-
-Average performance metrics for test and training sets are in Table \ref{table:3}.
-Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time.
-However, $R^2$ statistics and discrimination indexes are considerably low.
-Metrics for the final model's performance on the full data, also found in Table \ref{table:3}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
-Results for training, test, and the full data did not change significantly, indicating that the model was not overfit.
-
-Assessing the proportional hazards assumption indicated that several levels of the device categorization variable, specifically Apple Product, Camera, Game Console, and Other, violated the assumption.
-
-The final model trained on the full data set was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.
-
-The following are interpretations of select hazard coefficients in Table \ref{table:4}.
-Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
-
-\begin{itemize}
-  \item The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors.
-  \item The estimated hazard of receiving an answer for questions posted on a weekend is 13\% lower (95\% CI (7\%, 18\%)) than the hazard for questions posted on a weekday, controlling for all other predictors.
-\end{itemize}
-
-\section{Discussion}
-
-Results and coefficients of the final model reveal how users can ask questions in order to decrease response time.
-Findings suggest that users should phrase the title in the form of a question, use correct grammar (e.g.
-punctuation and capitalization), include specific and concise tags, and post the question on a weekday.
-
-% Predictors found to be significant included: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.
-
-The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design.
-Many users incorrectly specified the device name (e.g.
-a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name.
-Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic).
-It is likely that these inconsistencies contributed to the final model's low predictive power.
-This, along with the results of the final model, reveal some of the ways the CQA can be structured to potentially decrease response times.
-As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions.
-Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above.
-Instead, the CQA can restrict the tags or devices users can include to a drop-down list.
-The CQA can also include more tips to guide users asking questions.
-Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response times, as well as create a set of consistent questions for improved analysis.
-
-% \section{Vitae}
-% 
-% Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo.
-Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo.
-Anthony Pileggi is a Data Scientist at iFixit.
-Declarations of interest: none.
-
-% \section{Author Contributions}
-% 
-% All authors contributed to the analysis featured in this paper and have edited and approved of the final article.
-
-\section*{Acknowledgements}
-
- We would like to thank iFixit for providing access to the CQA data.
-
-\section*{Disclosure Statement}
-
-We wish to confirm that there are no known conflicts of interest associated with this publication.
-
-\section*{Funding}
-
-This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. This sponsor was not involved in any aspect of this paper's analysis.
-
-\bibliographystyle{tfs}
-\bibliography{references}
-
-\section{Appendices}
-
-\appendix
-
-\section{Posted questions}
-
-Table \ref{table:5} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
-All fields in device, title, text, and tags are shown as the users entered it.
-
-\section{Variable Derivation}
-
-\subsection{Average tag frequency}
-
-This variable was created to investigate if including popular or widely-used tags in a question can lead to faster response times, based off of findings from \cite{Bhat2014}.
-This was computed as the average frequency, or proportion of times a question's tags appear in all of the data set.
-Questions without tags were assigned a value of 0.
-If a question has a higher average, then at least one of its tags are considered frequently-used.
-
-\subsection{Average tag length}
-
-This variable was created to investigate if questions with correctly defined tags have faster response times than questions that do not include tags or incorrectly use the tagging system.
-It is hypothesized that questions with ambiguous or lengthy tags make it difficult for the answering community to discern the question's topic, and thus have slower response times or remain unanswered.
-
-\subsection{Device categorization}
-
-Original device categories defined by iFixit included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle.
-Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model.
-Final categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle.
-Under the original device categorization, 1,954 questions (25.2\% of 7,760) were categorized incorrectly and indicated an NA for its category.
-Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name.
-For questions with missing categories, key words were searched for in device titles to re-categorize accordingly.
-All other questions with ambiguous device titles were categorized as Other.
-
-\subsection{Device name length}
-
-This variable was created to investigate if questions with correctly defined device names have faster response times than questions that do not include a name or are incorrectly defined.
-Similar to the average tag length variable, it is hypothesized that questions with incorrectly defined device names (often lengthy) make it difficult for the answering community to discern the question's topic, and thus have slower response times.
-
-\subsection{If the question's text contains end punctuation}
-
-This variable was created to investigate if sentences with no end punctuation take longer to receive an answer.
-
-\subsection{If the question's title contains terms considered frequently-used among answered/unanswered questions}
-
-These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not.
-Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not.
-This variable was created based off of methods from \cite{Correa2013} and \cite{Ravi2014}.
-
-To create the variables, the data was separated between answered and unanswered questions.
-For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the proportion of times those words occurred among all answered questions' titles, defined as the frequency.
-The same was performed for the data frame containing unanswered questions.
-``Frequently-used'' words in answered questions were defined as those that appeared in 1\% or more of all answered questions' titles, and appeared in more answered questions than in unanswered questions.
-To determine the latter, a ratio of frequencies was assessed.
-The ratio was calculated as the proportion of times a word occurred among answered questions, to the proportion of times a word occurred in unanswered questions.
-As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20).
-Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions.
-As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
-Table \ref{table:6} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
-
-\subsection{If the question's title ends in a question mark}
-
-This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \cite{Bhat2014}.
-
-\subsection{If the user made an effort to solve the problem prior to asking the question}
-
-This variable indicates true if the asker included words in the question's text that indicate the user made prior effort to find the solution before posting.
-Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.
-This variable was created based off of findings and methods from \cite{Bhat2014} and \cite{Harper2008}.
-
-\subsection{Line break to text length ratio}
-
-This variable was created to investigate if questions that include line breaks in the text are easier to read than questions that do not include any, and thus have shorter response times.
-Questions with a ratio of 0 tend to include either short, ambiguous texts (e.g.
-"Start button not working.") or long and lengthy texts, and tend to remain unanswered or have slower response times.
-Questions with a ratio of greater than 0 tend to have faster response times.
-
-\section{Tables}
 

### 2018-09-18 article/graphics.Rmd
edit final manuscript submission

@@
 
-tiff("Figure 1.tiff", res = 300, width = 3000, height = 1500)
+jpeg("Figure 1.jpeg", res = 300, width = 3000, height = 1500)
 ggplot(x, aes(x = time_until_answer, fill = Answered)) +
@@
 
-ggsave("FIG1.pdf", width = 8, height = 5) # eps files don't work with transparency, submit as pdf instead
+# ggsave("FIG1.pdf", width = 8, height = 5) # eps files don't work with transparency, submit as pdf instead
 ```
@@
 
-tiff("Figure 2.tiff", res = 300, width = 3000, height = 1500)
+jpeg("Figure 2.jpeg", res = 300, width = 3000, height = 1500)
 # dashed line indicates the median survival time

### 2018-09-18 article/manuscript.Rnw
edit final manuscript submission

@@
 
-\usepackage{multirow}
-\usepackage{color,soul}
-\usepackage{array}
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+% \usepackage{multirow}
+% \usepackage{color,soul}
+% \usepackage{array}
+% \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 % \usepackage{caption}
@@
 % puts R2 in bold in table 3
-\makeatletter
-\DeclareRobustCommand\bfseries{%
-  \not@math@alphabet\bfseries\mathbf
-  \fontseries\bfdefault\selectfont
-  \boldmath % <-- added
-}
-\makeatother
-
-\makeatletter % for spacing figures at the end of the document
-\@fpsep\textheight
-\makeatother
+% \makeatletter
+% \DeclareRobustCommand\bfseries{%
+%   \not@math@alphabet\bfseries\mathbf
+%   \fontseries\bfdefault\selectfont
+%   \boldmath % <-- added
+% }
+% \makeatother
+% 
+% \makeatletter % for spacing figures at the end of the document
+% \@fpsep\textheight
+% \makeatother
 
@@
 Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received.
-Variables derived can be found in Table \ref{table:1}.
-The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table \ref{table:5}.
+Variables derived can be found in Table 1.
+The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table 5.
 
@@
 
-Table \ref{table:2} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
+Table 2 shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.
 
-Average performance metrics for test and training sets are in Table \ref{table:3}.
+Average performance metrics for test and training sets are in Table 3.
 Partial likelihood ratios and p-values indicate that the model as a whole is significantly associated with response time.
 However, $R^2$ statistics and discrimination indexes are considerably low.
-Metrics for the final model's performance on the full data, also found in Table \ref{table:3}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
+Metrics for the final model's performance on the full data, also found in Table 3, are consistent with metrics found in cross-validation and indicate low predictive accuracy.
 Results for training, test, and the full data did not change significantly, indicating that the model was not overfit.
@@
 
-The following are interpretations of select hazard coefficients in Table \ref{table:4}.
+The following are interpretations of select hazard coefficients in Table 4.
 Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.
@@
 
-Table \ref{table:5} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
+Table 5 provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet).
 All fields in device, title, text, and tags are shown as the users entered it.
@@
 As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists.
-Table \ref{table:6} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
+Table 6 contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).
 
@@
 
-\section{Tables}
-
-% Table of derived predictors
-\begin{table}[p]%[!htbp]
-\tbl{Categorical and continuous variables derived}
-% \centering
-{\begin{tabular}{|L{2cm}|L{10cm}|}
-  \hline
-  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to.
-Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
-  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
-  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
-  & If the question's text is in all lower case \\ \cline{2-2}
-  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
-  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
-  & If the question's title ends in a question mark \\ \cline{2-2}
-  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
-  & If the user made an effort to solve the problem prior to asking the question \\ \hline
-  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
-  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
-  & Number of characters in the question's text (text length) \\ \cline{2-2}
-  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
-  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
-\end{tabular}}
-% \caption{Categorical and continuous variables derived}
-\label{table:1}
-\end{table}
-
-% Splines Square root transformation of the average tag frequency
-\begin{table}[p]% [!htbp]
-% \centering
-\tbl{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
-{\begin{tabular}{| L{5cm} | l | l |}
-  \hline
-  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
-  \hline
-  \multirow{4}{5 cm}{$\sqrt{\textnormal{average tag frequency}}$} 
-  & 0\textbf{*} & 65890.75 \\ 
-  & 5 & 65891.69 \\ 
-  & 4 & 65891.75 \\ 
-  & 3 & 65892.35 \\ 
-  \hline
-  \multirow{4}{5 cm}{$\log\left({\textnormal{average tag length} + 1}\right)$}
-  & 0 & 65920.24 \\ 
-  & 5 & 65911.20 \\ 
-  & 4\textbf{*} & 65910.81 \\ 
-  & 3 & 65914.98 \\ 
-  \hline
-  \multirow{4}{5 cm}{$\log\left({\textnormal{device length} + 1}\right)$}
-  & 0 & 65918.06 \\ 
-  & 5\textbf{*} & 65847.34 \\ 
-  & 4 & 65880.89 \\ 
-  & 3 & 65898.00 \\ 
-  \hline
-  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks / text length}}$}
-  & 0 & 65890.28 \\ 
-  & 5 & 65884.70 \\ 
-  & 4 & 65882.98 \\ 
-  & 3\textbf{*} & 65881.93 \\ 
-  \hline
-  \multirow{4}{5cm}{$\log\left({\textnormal{text length}}\right)$} 
-  & 0 & 65862.83 \\ 
-  & 5\textbf{*} & 65862.02 \\ 
-  & 4 & 65863.35 \\ 
-  & 3 & 65862.08 \\ 
-  \hline
-\end{tabular}}
-\label{table:2}
-\end{table}
-
-% Cross-validation metrics
-\begin{table}[p]%[!htbp]
-% \centering
-\tbl{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)}
-{\begin{tabular}{|r|r|r|r|r|r|r|r|}
-  \hline
- & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
-  \hline
-  \textbf{Training Sets} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
-  \textbf{Test Sets}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
-  \textbf{Full Data}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
-   \hline
-\end{tabular}}
-\label{table:3}
-\end{table}
-
-% Final model on full data
-\begin{table}[p]%[!htbp]
-% \centering
-\tbl{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
-{\begin{tabular}{|l L{5.5cm}|c|c|}
-  \hline
- \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
-  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
-                  & Camera & -0.32 (0.090) & \\ 
-                  & Electronics & -0.01 (0.078)  & \\ 
-                  & Game Console & 0.24 (0.083)  & \\ 
-                  & Home & 0.34 (0.070) &  \\ 
-                  & Other & -0.13 (0.056)  & \\ 
-                  & PC & 0.28 (0.060) &  \\ 
-                  & Tablet & -0.16 (0.081)  & \\ 
-                  & Vehicle & 0.40 (0.069)  & \\
-                  & Android/Other Phone (reference) & --- & \\ \hline
-  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
-  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
-  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
-  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
-\end{tabular}}
-\label{table:4}
-\end{table}
-
-\begin{table}[p]%[!htbp]
-% \centering
-\tbl{Examples of an answered question (left) and an unanswered question (right)}
-{\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
-\hline
-\textbf{Device} & iPhone 6 & android tablet \\ \hline
-\textbf{Title} & iPhone water damage, touch screen issue & ccccaaaan you help me fix my touch screen \\ \hline
-\textbf{Text} & So I dropped my iPhone in water 4 days ago.
-Have done the whole rice thing and seen huge difference in it.
-However, only one side of my screen works and it is the one side which I need to unlock the phone.
-What would be the best way forward?
-& touch screen not worki\\ \hline
-\textbf{Tags} & touchscreen, water damage & NA\\ \hline
-\textbf{Response Time (hrs)} & 1.361 & NA \\ \hline 
-\textbf{Device Category} & Apple Product & Tablet \\ \hline
-\textbf{Day Posted} & Weekday & Weekday \\ \hline
-\textbf{Text length (characters)} & 241 & 81 \\ \hline
-\textbf{Device name length (characters)} & 8 & 18\\ \hline
-\textbf{Average tag length (characters)} & 11.5 & 47 \\ \hline
-\textbf{Average tag frequency} & 0.0097 & 0 \\ \hline
-\textbf{Text contain end punctuation?} & True & False \\ \hline
-\textbf{Text in all lower case?} & False & True \\ \hline
-\textbf{Title end in a question mark?} & False & False \\ \hline
-\textbf{Line break to text length ratio} & 0 & 0 \\ \hline
-\textbf{User indicate prior effort?} & False & False \\ \hline
-\textbf{User update question after posting?} & False & False \\ \hline
-\textbf{Frequently-used answered words?} & True & True \\ \hline
-\textbf{Frequently-used unanswered words?} & False & False \\ \hline
-\end{tabular}}
-\label{table:5}
-\end{table}
-
-% Table with list of frequently-used words
-\begin{table}[p]%[!htbp]
-% \centering
-\tbl{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
-{\begin{tabular}{|L{4cm}|L{8cm}|}
-  \hline
- \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, LCD, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
-  \hline
-  \textbf{Frequently-used terms among unanswered questions} & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\
-   \hline
-\end{tabular}}
-\label{table:6}
-\end{table}
-
 \end{document}

### 2018-09-18 article/manuscript.tex
edit final manuscript submission

@@
 \begin{keywords}
-Cox regression; CQA forum; Kaplan-Meier method; response time; survival analysis; survival probabilty;  
+Cox regression; CQA forum; Kaplan-Meier method; response time; survival analysis; survival probability;  
 \end{keywords}
@@
 
-This variable indicates true if the asker included words in the question's text that indicate the user made prior effort to find the solution before posting.
+This variable indicates true if the user included words in the question's text that indicate the user made prior effort to find the solution before posting.
 Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted.

### 2018-12-21 article/application_note.tex
add files for resubmission

--- 2018-09-18 article/manuscript.tex
@@
 iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer device repair-related questions.
-This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response.
-A Cox proportional hazards model was developed to identify variables associated with response time.
+As the time until a question receives its first response is an important aspect of CQAs and, at present, has not been thoroughly investigated, this paper presents a survival analysis of response times of questions posted on iFixit's \textit{Answers} forum.
+A Cox proportional hazards model was developed to identify signficanlty associated variables.
 Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$).
@@
 
-Founded in 2003, iFixit teaches thousands of users around the globe how to fix their own broken devices.
+Founded in 2003, iFixit teaches thousands of users how to fix their own broken devices.
 This company provides over 40,000 free online repair guides and hosts a CQA, the \textit{Answers} forum, featuring questions pertaining to over 11,000 devices with over 130,000 user-posted solutions.
@@
 
-\subsection{Related Work}
+\subsection{Relevant Data}
 
-With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies.
-Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}.
-\cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions.
-\cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered.
-However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered.
-The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.
-
-The majority of existing research has been focused on predicting question and answer quality.
-\cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions.
-\cite{Blumenstock2008} also determined that textual features (e.g.
-word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs).
-\cite{Fu2015} instead found non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality.
-A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}.
-The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate a question is of high quality also lead to faster response times.
-
-\section{Materials}
-
-The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download).
+The data analyzed contains 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download).
 Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received.
@@
 
-\section{Methods}
+\section{Methodology}
 
@@
 
-\section{Results}
-
-% Distribution of answer times
-% \begin{figure}[!htbp]
-%   \includegraphics[scale=0.5]{FIG1.pdf}
-%   \label{fig:1}
-% \end{figure}
-% 
-% % Kaplan-Meier curve
-% \begin{figure}[!htbp]
-%   \includegraphics[scale=0.5]{FIG2.eps}
-%   \label{fig:2}
-% \end{figure}
+\section{Application of Methodology}
 
@@
 
-\section{Discussion}
+\section{Conclusion and Discussion}
 
